### 2022-05-17 GeneralizedTractabilty.tex
Initial Overleaf Import

\documentclass{article}
\usepackage{amsmath,amssymb, amsthm, booktabs, mathtools}
\usepackage[utf8]{inputenc}
\input{FJHDef.tex}

\title{Generalized Tractability}
\author{Fred J. Hickernell, Peter Kritzer and Henryk Wo\'zniakwoski}
\date{December 2018}

%\DeclareMathOperator{\comp}{comp}
\DeclareMathOperator{\SOL}{SOL}
\DeclareMathOperator{\APP}{APP}

%\theoremstyle{theorem}
\newtheorem{theorem}{Theorem}
\theoremstyle{definition}
\newtheorem{definition}{Definition}

\begin{document}

\maketitle

\section{Introduction}

Let $\cf_d$ and $\cg_d$ Hilbert spaces, and $\SOL_d : \cf_d \to \cg_d$ be a linear solution operator with adjoint $\SOL_d^*$ such that $\SOL_d^*\SOL_d : \cf_d \to \cf_d$ has eigenvalues and orthonormal eigenvectors  
\[
\lambda_{\max} \ge \lambda_{1,d} \ge \lambda_{2,d} \ge \cdots, \qquad u_{1,d}, u_{2,d}, \ldots, 
\]
The goal is to find an approximate solution, $\APP_d:\cb_d \times (0,\infty) \to \cg_d$ satisfying $\norm[\cg_d]{\SOL_d(f) - \APP_d(f,\varepsilon)} \le \varepsilon$, where $\cb_d$ is the unit ball in $\cf_d$ and $\APP_d(f,\varepsilon)$ is allowed to depend on arbitrary linear functionals.  In this case the optimal solution is 
\[
\APP_d(f,\varepsilon) = \sum_{i=1}^n \SOL(u_i) \ip[\cf_d]{f}{u_i},
\]
and the complexity of our linear problem is
\[
\comp(\varepsilon, d) = \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon^2\}.
\]

Let let $\phi : (0,\infty) \times [0,\Delta] \to (0,\infty)$ and $\{\psi : \naturals  \times [0,\Delta] \to (0,\infty)\}$ be positive functions that are increasing in both arguments, e.g., 
\[
(x,\delta) \mapsto x^{p + \delta} \ (p >0), \qquad (x,\delta) \mapsto (1 + \delta) \log(1+x)
\]
which satisfy
\begin{equation*}
    \lim_{\delta \downarrow 0} \phi(x,\delta) = \phi(x,0) =: \phi(x), \qquad 
    \lim_{\delta \downarrow 0} \psi(x,\delta) = \psi(x,0) =: \psi(x).
\end{equation*}

\begin{definition}
If for all $\delta_1, \delta_2 \in (0,\Delta]$ there exist the functions $\phi$ and $\psi$ satisfying the conditions listed above, and there exists $C_1 : (0,\Delta]^2 \to (0,\infty)$  with 
\begin{multline*}
    \comp(\varepsilon, d) \le \phi(\varepsilon^{-1},\delta_1)\psi(d,\delta_2) + C_1(\delta_1, \delta_2) \\
    \forall \delta_1, \delta_2 \in (0,\Delta], \quad  \varepsilon \in (0, 1], \quad \forall d \in \naturals
\end{multline*}
then we call a problem $\phi$-$\psi$-tractable.
\end{definition}

Some specific examples include 
\begin{equation*}
    \begin{array}{r@{\qquad}c@{\qquad}c}
    & \phi(x,\delta) & \psi(x,\delta) \\
    \toprule
    \text{strong algebraic tractability} & C_2(x,\delta) x^{p+\delta} & 1\\
    \text{ algebraic tractability} & C_2(x,\delta) x^{p+\delta} & x^{q+\delta}\\
    \text{strong exponential tractability} &(p+\delta) \log(1 + x) & 1 \\
    \text{ exponential tractability} &(p+\delta) \log(1 + x) &  x^{q+\delta} \\
    & 
    \end{array}
\end{equation*}

\section{Main Result}
\begin{theorem} A problem is $\phi$-$\psi$-tractable iff there exists a  $C_3 : (0,\Delta]^2 \to (0,\infty)$
\begin{equation} \label{eq:tractiff}
    \sup_{d \in \naturals} \frac{1}{\psi(d,\delta_2)} \sum_{i = C_3(\delta_1,\delta_2)}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1/2},\delta_1)} \le 1 \qquad \forall \delta_1, \delta_2 \in (0,\Delta]
\end{equation}
\end{theorem}
\begin{proof}
Fix $\delta_1 \in (0,\Delta]$.  Because $\phi$ is increasing in its arguments, it follows that the complexity may be equivalently expressed as 
\begin{align*}
    \comp(\varepsilon, d) &= \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon^2\} \\
    &= \min \biggl\{n \in \natzero : \frac{1}{\phi(\lambda_{n+1, d}^{-1/2},\delta_1)} \le \frac{1}{\phi(\varepsilon^{-1},\delta_1)} \biggr\}.
\end{align*}

Since the $\lambda_{i,d}$ are non-increasing it follows that the $\phi(\lambda_{i, d}^{-1/2},\delta_1)$ are also non-increasing.  In particular, for all $n \in \naturals$,
\begin{align*}
    \MoveEqLeft{\lambda_{n+1,d} \le \lambda_{n,d} \le \cdots \le \lambda_{1,d}} \\
    & \implies \frac{1}{\phi(\lambda_{n+1, d}^{-1/2},\delta_1)} \le \frac{1}{\phi(\lambda_{n, d}^{-1/2},\delta_1)} \le \cdots \le \frac{1}{\phi(\lambda_{1, d}^{-1/2},\delta_1)} \\
    & \implies \frac{1}{\phi(\lambda_{n+1, d}^{-1/2},\delta_1)} 
    \le \frac 1n \sum_{i=1}^n  \frac{1}{\phi(\lambda_{i, d}^{-1/2},\delta_1)} 
    \le \frac 1n \sum_{i=1}^\infty  \frac{1}{\phi(\lambda_{i, d}^{-1/2},\delta_1)}.
\end{align*}
Thus, we can conclude that 
\begin{align*}
    n \ge \phi(\varepsilon^{-1},\delta_1) \sum_{i=1}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1/2},\delta_1)}
    & \implies 
  \frac 1n \sum_{i=1}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1/2},\delta_1)} \le  \frac{1}{\phi(\varepsilon^{-1},\delta_1)} \\
   & \implies   \frac{1}{\phi(\lambda_{n+1, d}^{-1/2},\delta_1)} \le \frac{1}{\phi(\varepsilon^{-1},\delta_1)}.
\end{align*}
This implies an upper bound on the complexity of
\begin{align*}
       \MoveEqLeft{\comp(\varepsilon,d)} \\
       &\le 1 + \phi(\varepsilon^{-1},\delta_1) \sum_{i=1}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1/2},\delta_1)} \\
       & = 1 + \phi(\varepsilon^{-1},\delta_1) \left [ \sum_{i=1}^{C_3(\delta_1,\delta_2)-1} \frac{1}{\phi(\lambda_{i, d}^{-1/2},\delta_1)}  + \sum_{i=C_3(\delta_1,\delta_2)}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1/2},\delta_1)} \right ] \\
       & \le \underbrace{1+  \phi(\varepsilon^{-1},\delta_1) \frac{C_3(\delta_1,\delta_2)-1}{\phi(\lambda_{\max}^{-1/2},\delta_1)}}_{C_1(\delta_1,\delta_2)}
       +  \phi(\varepsilon^{-1},\delta_1) \psi(d,\delta_2) 
        \qquad \text{by \eqref{eq:tractiff}} \\
\end{align*}
This verifies the sufficient condition.

The proof is done.
\end{proof}

\end{document}

### 2022-05-22 GeneralizedTractabilityVerB.tex
Updates from Overleaf

--- 2022-05-17 GeneralizedTractabilty.tex
@@
 \title{Generalized Tractability}
-\author{Fred J. Hickernell, Peter Kritzer and Henryk Wo\'zniakwoski}
+\author{Fred J. Hickernell, Peter Kritzer, Onyekachi Osisiogu, and \\ Henryk Wo\'zniakwoski}
 \date{December 2018}
@@
 \[
-\lambda_{\max} \ge \lambda_{1,d} \ge \lambda_{2,d} \ge \cdots, \qquad u_{1,d}, u_{2,d}, \ldots, 
+\lambda_{\max}^2 \ge \lambda_{1,d}^2 \ge \lambda_{2,d}^2 \ge \cdots, \qquad u_{1,d}, u_{2,d}, \ldots, 
 \]
-The goal is to find an approximate solution, $\APP_d:\cb_d \times (0,\infty) \to \cg_d$ satisfying $\norm[\cg_d]{\SOL_d(f) - \APP_d(f,\varepsilon)} \le \varepsilon$, where $\cb_d$ is the unit ball in $\cf_d$ and $\APP_d(f,\varepsilon)$ is allowed to depend on arbitrary linear functionals.
-In this case the optimal solution is
+This means that the $\lambda_{i,d}$ are the singular values of the $\SOL_d$. The goal is to find an approximate solution, $\APP_d:\cb_d \times (0,\infty) \to \cg_d$ satisfying 
+\[
+\norm[\cg_d]{\SOL_d(f) - \APP_d(f,\varepsilon)} \le \varepsilon,
+\]
+where $\cb_d$ is the unit ball in $\cf_d$ and $\APP_d(f,\varepsilon)$ is allowed to depend on arbitrary linear functionals.  In this case the optimal solution is 
 \[
@@
 \]
+
+Certain kinds of common notions of tractability are 
+\begin{equation*}
+    \begin{array}{r@{\qquad}c@{\qquad}c}
+    & \comp(\varepsilon, d)\\
+    \toprule
+    \text{strong algebraic tractability} & \Theta(\varepsilon^{-p})\\
+    \text{ algebraic tractability} & \Theta(\varepsilon^{-p}d^{q})\\
+    \text{strong exponential tractability} & \log(1 + \varepsilon^{-p})\\
+    \text{ exponential tractability} &(p+\delta) \log(1 + x) &  x^{q+\delta} \\
+    & 
+    \end{array}
+\end{equation*}
 

### 2022-09-19 GeneralizedTractabilityVerB.tex
Updates from Overleaf

@@
 \author{Fred J. Hickernell, Peter Kritzer, Onyekachi Osisiogu, and \\ Henryk Wo\'zniakwoski}
-\date{December 2018}
+\date{\today}
 
@@
 \]
-This means that the $\lambda_{i,d}$ are the singular values of the $\SOL_d$. The goal is to find an approximate solution, $\APP_d:\cb_d \times (0,\infty) \to \cg_d$ satisfying 
+This means that the non-negative $\lambda_{i,d}$ are the singular values of the $\SOL_d$. The goal is to find an approximate solution, $\APP_d:\cb_d \times (0,\infty) \to \cg_d$ satisfying 
 \[
@@
 \[
-\comp(\varepsilon, d) = \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon^2\}.
+\comp(\varepsilon, d) = \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon\}.
 \]
@@
     \text{ algebraic tractability} & \Theta(\varepsilon^{-p}d^{q})\\
-    \text{strong exponential tractability} & \log(1 + \varepsilon^{-p})\\
-    \text{ exponential tractability} &(p+\delta) \log(1 + x) &  x^{q+\delta} \\
-    & 
+    \text{strong exponential tractability} &  \Theta\bigl([\log(1 + \varepsilon^{-1})]^p\bigr)\\
+    \text{ exponential tractability} & \Theta\bigl([\log(1 + \varepsilon^{-1})]^p  d^{q}\bigr)
     \end{array}
 \end{equation*}
+Let let $\phi : (0,\infty) \times (0,\infty] \to (0,\infty)$ and $\psi : \naturals  \times (0,\Delta) \to (0,\infty)$ be positive-valued functions that are strictly increasing in both arguments, e.g.,
+\[
+(x,p) \mapsto x^{p}, \qquad (x,p) \mapsto [\log(1+x)]^p.
+\]
 
-Let let $\phi : (0,\infty) \times [0,\Delta] \to (0,\infty)$ and $\{\psi : \naturals  \times [0,\Delta] \to (0,\infty)\}$ be positive functions that are increasing in both arguments, e.g., 
-\[
-(x,\delta) \mapsto x^{p + \delta} \ (p >0), \qquad (x,\delta) \mapsto (1 + \delta) \log(1+x)
-\]
-which satisfy
+All the examples of tractability above are of the form $\comp(\varepsilon, d) = \Theta \bigl( \phi(\varepsilon^{-1},p) \psi(d,q)\bigr)$.  Note, we define the $\Theta$ notation as follows
 \begin{equation*}
-    \lim_{\delta \downarrow 0} \phi(x,\delta) = \phi(x,0) =: \phi(x), \qquad 
-    \lim_{\delta \downarrow 0} \psi(x,\delta) = \psi(x,0) =: \psi(x).
+     g(\varepsilon,d) = \Theta\bigl(\phi(\varepsilon^{-1},p) \bigr) \text{ means } 
+    \lim_{\varepsilon \to 0} \frac{g(\varepsilon,d)}{\phi(\varepsilon^{-1},p')}
+           \begin{cases} < \infty, & p'> p,  \\ 
+          =\infty, & p' < p.\end{cases}
 \end{equation*}
+\begin{multline*}
+     g(\varepsilon,d) = \Theta\bigl(\phi(\varepsilon^{-1},p) \psi(d,q) \bigr) \text{ means } \\
+    \lim_{\substack{\varepsilon \to 0 \\ d \to \infty}} \frac{g(\varepsilon,d)}{\phi(\varepsilon^{-1},p') \psi(d,q')}
+          \begin{cases} < \infty, & p'> p, \  q' > q,  \\ 
+          =\infty, & p' < p, \ q' < q.\end{cases}
+\end{multline*}
 
 \begin{definition}
-If for all $\delta_1, \delta_2 \in (0,\Delta]$ there exist the functions $\phi$ and $\psi$ satisfying the conditions listed above, and there exists $C_1 : (0,\Delta]^2 \to (0,\infty)$  with 
-\begin{multline*}
-    \comp(\varepsilon, d) \le \phi(\varepsilon^{-1},\delta_1)\psi(d,\delta_2) + C_1(\delta_1, \delta_2) \\
-    \forall \delta_1, \delta_2 \in (0,\Delta], \quad  \varepsilon \in (0, 1], \quad \forall d \in \naturals
-\end{multline*}
-then we call a problem $\phi$-$\psi$-tractable.
+If there exist the functions $\phi$ and $\psi$ satisfying the conditions listed above and there exist positive numbers $p$ and $q$ with
+\[
+\comp(\varepsilon, d)  = \Theta\bigl(\phi(\varepsilon^{-1},p) \psi(d,q) \bigr),
+\]
+then we call a problem $\phi$-$\psi$-tractable with exponents $p$ and $q$.  If there exists a function there $\phi$ satisfying the conditions above and a positive numbers $p$
+\[
+\comp(\varepsilon, d)  = \Theta\bigl(\phi(\varepsilon^{-1},p) \bigr)
+\]
+then we call a problem strongly $\phi$-tractable with expontent $p$
 \end{definition}
 
-Some specific examples include 
-\begin{equation*}
-    \begin{array}{r@{\qquad}c@{\qquad}c}
-    & \phi(x,\delta) & \psi(x,\delta) \\
-    \toprule
-    \text{strong algebraic tractability} & C_2(x,\delta) x^{p+\delta} & 1\\
-    \text{ algebraic tractability} & C_2(x,\delta) x^{p+\delta} & x^{q+\delta}\\
-    \text{strong exponential tractability} &(p+\delta) \log(1 + x) & 1 \\
-    \text{ exponential tractability} &(p+\delta) \log(1 + x) &  x^{q+\delta} \\
-    & 
-    \end{array}
-\end{equation*}
-
 \section{Main Result}
-\begin{theorem} A problem is $\phi$-$\psi$-tractable iff there exists a  $C_3 : (0,\Delta]^2 \to (0,\infty)$
+\begin{theorem} A problem is $\phi$-$\psi$-tractable iff there exists a  $C : (0,\infty)^2 \to \naturals$
 \begin{equation} \label{eq:tractiff}
-    \sup_{d \in \naturals} \frac{1}{\psi(d,\delta_2)} \sum_{i = C_3(\delta_1,\delta_2)}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1/2},\delta_1)} \le 1 \qquad \forall \delta_1, \delta_2 \in (0,\Delta]
+    \sup_{d \in \naturals} \frac{1}{\psi(d,q)} \sum_{i = C(p,q)}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1/2},p)} \le 1 \qquad \forall p,q \in (0,\infty)
 \end{equation}

### 2022-10-05 GeneralizedTractabilityVerB.tex
Updates from Overleaf

@@
 \usepackage[utf8]{inputenc}
+\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
+\usepackage[notref,notcite]{showkeys}
 \input{FJHDef.tex}
@@
 \title{Generalized Tractability}
-\author{Fred J. Hickernell, Peter Kritzer, Onyekachi Osisiogu, and \\ Henryk Wo\'zniakwoski}
+\author{\fred{Fred J. Hickernell}, \peter{Peter Kritzer}, \kachi{Onyekachi Osisiogu}, and \\ Henryk Wo\'zniakwoski}
 \date{\today}
@@
 \newtheorem{definition}{Definition}
+
+\allowdisplaybreaks
+
+\newcommand{\fred}[1]{\begingroup\color{blue}#1\endgroup}
+\newcommand{\peter}[1]{\begingroup\color{purple}#1\endgroup}
+\newcommand{\kachi}[1]{\begingroup\color{ForestGreen}#1\endgroup}
 
@@
     \toprule
-    \text{strong algebraic tractability} & \Theta(\varepsilon^{-p})\\
-    \text{ algebraic tractability} & \Theta(\varepsilon^{-p}d^{q})\\
-    \text{strong exponential tractability} &  \Theta\bigl([\log(1 + \varepsilon^{-1})]^p\bigr)\\
-    \text{ exponential tractability} & \Theta\bigl([\log(1 + \varepsilon^{-1})]^p  d^{q}\bigr)
+    \text{strong polynomial algebraic  tractability} & \Theta(\varepsilon^{-p})\\
+    \text{polynomial algebraic tractability} & \Theta(\varepsilon^{-p}d^{q})\\
+    \text{strong polynomial exponential tractability} &  \Theta\bigl([\log(1 + \varepsilon^{-1})]^p\bigr)\\
+    \text{polynomial exponential tractability} & \Theta\bigl([\log(1 + \varepsilon^{-1})]^p  d^{q}\bigr)
     \end{array}
 \end{equation*}
-Let let $\phi : (0,\infty) \times (0,\infty] \to (0,\infty)$ and $\psi : \naturals  \times (0,\Delta) \to (0,\infty)$ be positive-valued functions that are strictly increasing in both arguments, e.g.,
+Let let $\phi : (0,\infty) \times (0,\infty) \to (0,\infty)$ and $\psi : \naturals  \times (0,\infty) \to (0,\infty)$ \peter{(PETER: why do we need $\Delta$ here, and cannot simply use $\infty$?)} be positive-valued functions that are strictly increasing in both arguments, e.g.,
 \[
@@
 \end{multline*}
+\peter{(PETER: what would happen if $p'<p$ and $q'\ge q$ or the other way around?)}
 
@@
 \]
-then we call a problem $\phi$-$\psi$-tractable with exponents $p$ and $q$.  If there exists a function there $\phi$ satisfying the conditions above and a positive numbers $p$
+then we call a problem $\phi$-$\psi$-tractable with exponents $p$ and $q$.  If there exists a function there $\phi$ satisfying the conditions above and a positive number $p$
 \[
@@
 \]
-then we call a problem strongly $\phi$-tractable with expontent $p$
+then we call a problem strongly $\phi$-tractable with exponent $p$.
 \end{definition}
@@
 \begin{equation} \label{eq:tractiff}
-    \sup_{d \in \naturals} \frac{1}{\psi(d,q)} \sum_{i = C(p,q)}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1/2},p)} \le 1 \qquad \forall p,q \in (0,\infty)
+    \sup_{d \in \naturals} \frac{1}{\psi(d,q)} \sum_{i = C(p,q)}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)} \le 1 \qquad \forall p,q \in (0,\infty).
 \end{equation}
@@
 \begin{proof}
-Fix $\delta_1 \in (0,\Delta]$.  Because $\phi$ is increasing in its arguments, it follows that the complexity may be equivalently expressed as 
+Fix $p \in (0,\infty)$.  Because $\phi$ is increasing in its arguments, it follows that the complexity may be equivalently expressed as 
 \begin{align*}
-    \comp(\varepsilon, d) &= \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon^2\} \\
-    &= \min \biggl\{n \in \natzero : \frac{1}{\phi(\lambda_{n+1, d}^{-1/2},\delta_1)} \le \frac{1}{\phi(\varepsilon^{-1},\delta_1)} \biggr\}.
+    \comp(\varepsilon, d) &= \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon\} \\
+    &= \min \biggl\{n \in \natzero : \frac{1}{\phi(\lambda_{n+1, d}^{-1},p)} \le \frac{1}{\phi(\varepsilon^{-1},p)} \biggr\}.
 \end{align*}
 
-Since the $\lambda_{i,d}$ are non-increasing it follows that the $\phi(\lambda_{i, d}^{-1/2},\delta_1)$ are also non-increasing.  In particular, for all $n \in \naturals$,
+Since the $\lambda_{i,d}$ are non-increasing it follows that the $\phi(\lambda_{i, d}^{-1},p)$ are non-decreasing.  In particular, for all $n \in \naturals$,
 \begin{align*}
     \MoveEqLeft{\lambda_{n+1,d} \le \lambda_{n,d} \le \cdots \le \lambda_{1,d}} \\
-    & \implies \frac{1}{\phi(\lambda_{n+1, d}^{-1/2},\delta_1)} \le \frac{1}{\phi(\lambda_{n, d}^{-1/2},\delta_1)} \le \cdots \le \frac{1}{\phi(\lambda_{1, d}^{-1/2},\delta_1)} \\
-    & \implies \frac{1}{\phi(\lambda_{n+1, d}^{-1/2},\delta_1)} 
-    \le \frac 1n \sum_{i=1}^n  \frac{1}{\phi(\lambda_{i, d}^{-1/2},\delta_1)} 
-    \le \frac 1n \sum_{i=1}^\infty  \frac{1}{\phi(\lambda_{i, d}^{-1/2},\delta_1)}.
+    & \implies \frac{1}{\phi(\lambda_{n+1, d}^{-1},p)} \le \frac{1}{\phi(\lambda_{n, d}^{-1},p)} \le \cdots \le \frac{1}{\phi(\lambda_{1, d}^{-1},p)} \\
+    & \implies \frac{1}{\phi(\lambda_{n+1, d}^{-1},p)} 
+    \le \frac 1n \sum_{i=1}^n  \frac{1}{\phi(\lambda_{i, d}^{-1},p)} 
+    \le \frac 1n \sum_{i=1}^\infty  \frac{1}{\phi(\lambda_{i, d}^{-1},p)}.
 \end{align*}
@@
 \begin{align*}
-    n \ge \phi(\varepsilon^{-1},\delta_1) \sum_{i=1}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1/2},\delta_1)}
+    n \ge \phi(\varepsilon^{-1},p) \sum_{i=1}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)}
     & \implies 
-  \frac 1n \sum_{i=1}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1/2},\delta_1)} \le  \frac{1}{\phi(\varepsilon^{-1},\delta_1)} \\
-   & \implies   \frac{1}{\phi(\lambda_{n+1, d}^{-1/2},\delta_1)} \le \frac{1}{\phi(\varepsilon^{-1},\delta_1)}.
+  \frac 1n \sum_{i=1}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)} \le  \frac{1}{\phi(\varepsilon^{-1},p)} \\
+   & \implies   \frac{1}{\phi(\lambda_{n+1, d}^{-1},p)} \le \frac{1}{\phi(\varepsilon^{-1},p)}.
 \end{align*}
@@
        \MoveEqLeft{\comp(\varepsilon,d)} \\
-       &\le 1 + \phi(\varepsilon^{-1},\delta_1) \sum_{i=1}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1/2},\delta_1)} \\
-       & = 1 + \phi(\varepsilon^{-1},\delta_1) \left [ \sum_{i=1}^{C_3(\delta_1,\delta_2)-1} \frac{1}{\phi(\lambda_{i, d}^{-1/2},\delta_1)}  + \sum_{i=C_3(\delta_1,\delta_2)}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1/2},\delta_1)} \right ] \\
-       & \le \underbrace{1+  \phi(\varepsilon^{-1},\delta_1) \frac{C_3(\delta_1,\delta_2)-1}{\phi(\lambda_{\max}^{-1/2},\delta_1)}}_{C_1(\delta_1,\delta_2)}
-       +  \phi(\varepsilon^{-1},\delta_1) \psi(d,\delta_2) 
-        \qquad \text{by \eqref{eq:tractiff}} \\
+       &\le 1 + \phi(\varepsilon^{-1},p) \sum_{i=1}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)} \\
+       & = 1 + \phi(\varepsilon^{-1},p) \left [ \sum_{i=1}^{C_3(p,q)-1} \frac{1}{\phi(\lambda_{i, d}^{-1},p)}  + \sum_{i=C_3(p,q)}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)} \right ] \\
+       & \le 1+  \phi(\varepsilon^{-1},p) \underbrace{\frac{C_3(p,q)-1}{\phi(\lambda_{\max}^{-1},p)}}_{C_1(p,q)}
+       +  \phi(\varepsilon^{-1},p) \psi(d,q) 
+        \qquad \text{by \eqref{eq:tractiff}}. \\
 \end{align*}
+\kachi{KACHI: I no longer see $C_3$ and $C_1$ in this note.}\\
 This verifies the sufficient condition.

### 2023-03-10 GeneralizedTractability_230108.tex
Updates from Overleaf

\documentclass[11pt,a4paper]{article}
\usepackage{latexsym,amsfonts,amsmath,graphics,mathtools,amssymb,amsthm,booktabs}
\usepackage{epsfig}
%\usepackage[notref,notcite]{showkeys}
%\usepackage[active]{srcltx}
\usepackage{enumitem}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}

\usepackage{algorithmic}

%\input{common-macros}
%\input{common-macros2}

\input{FJHDef.tex}

\setlength{\textheight}{24cm} \setlength{\textwidth}{16cm}
\setlength{\hoffset}{-1.3cm} \setlength{\voffset}{-1.8cm}

\newcommand{\supp}{\operatorname{supp}}

\newcommand{\tpmod}[1]{{\;(\operatorname{mod}\;#1)}}

\DeclareMathOperator*{\esssup}{ess\,sup}

%\DeclareMathOperator{\comp}{comp}
\DeclareMathOperator{\SOL}{SOL}
\DeclareMathOperator{\APP}{APP}

\allowdisplaybreaks

\newcommand{\fred}[1]{\begingroup\color{blue}Fred: #1\endgroup}
\newcommand{\peter}[1]{\begingroup\color{purple}Peter: #1\endgroup}
\newcommand{\kachi}[1]{\begingroup\color{ForestGreen}#1\endgroup}

\begin{document}

\newtheorem{theorem}{Theorem}
\theoremstyle{definition}
\newtheorem{definition}{Definition}

\title{Generalized Tractability}
\author{\fred{Fred J. Hickernell}, \peter{Peter Kritzer}, \kachi{Onyekachi Osisiogu}, and \\ Henryk Wo\'zniakwoski}
\date{\today}

\maketitle

\section{Introduction}

Let $\cf_d$ and $\cg_d$ Hilbert spaces, and $\SOL_d : \cf_d \to \cg_d$ be a linear solution operator with adjoint $\SOL_d^*$ such that $\SOL_d^*\SOL_d : \cf_d \to \cf_d$ has eigenvalues and orthonormal eigenvectors  
\[
\lambda_{\max}^2 \ge \lambda_{1,d}^2 \ge \lambda_{2,d}^2 \ge \cdots, \qquad u_{1,d}, u_{2,d}, \ldots, 
\]
This means that the non-negative $\lambda_{i,d}$ are the singular values of the $\SOL_d$. The goal is to find an approximate solution, $\APP_d:\cb_d \times (0,\infty) \to \cg_d$ satisfying 
\[
\norm[\cg_d]{\SOL_d(f) - \APP_d(f,\varepsilon)} \le \varepsilon,
\]
where $\cb_d$ is the unit ball in $\cf_d$ and $\APP_d(f,\varepsilon)$ is allowed to depend on arbitrary linear functionals.  In this case, the optimal solution is 
\[
\APP_d(f,\varepsilon) = \sum_{i=1}^n \SOL(u_i) \ip[\cf_d]{f}{u_i},
\]
and the complexity of our linear problem is
\[
\comp(\varepsilon, d) = \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon\}.
\]

Certain kinds of common notions of tractability are 
\begin{equation*}
    \begin{array}{r@{\qquad}c@{\qquad}c}
    & \comp(\varepsilon, d)\\
    \toprule
    \text{strong polynomial algebraic  tractability} & \Theta(\varepsilon^{-p})\\
    \text{polynomial algebraic tractability} & \Theta(\varepsilon^{-p}d^{q})\\
    \text{strong polynomial exponential tractability} &  \Theta\bigl([\log(1 + \varepsilon^{-1})]^p\bigr)\\
    \text{polynomial exponential tractability} & \Theta\bigl([\log(1 + \varepsilon^{-1})]^p  d^{q}\bigr)
    \end{array}
\end{equation*}
Let $\phi : (0,\infty) \times (0,\infty) \to (0,\infty)$ and $\psi : \naturals  \times (0,\infty) \to (0,\infty)$ be positive-valued functions that are strictly increasing in both arguments, e.g., 
\[
(x,p) \mapsto x^{p}, \qquad (x,p) \mapsto [\log(1+x)]^p.
\]

All the examples of tractability above are of the form $\comp(\varepsilon, d) = \Theta \bigl( \phi(\varepsilon^{-1},p) \psi(d,q)\bigr)$.  
Note, we define the $\Theta$ notation as follows
\begin{equation*}
     g(\varepsilon,d) = \Theta\bigl(\phi(\varepsilon^{-1},p) \bigr) \text{ means } 
    \lim_{\varepsilon \to 0} \frac{g(\varepsilon,d)}{\phi(\varepsilon^{-1},p')}
           \begin{cases} < \infty, & p'> p,  \\ 
          =\infty, & p' < p.\end{cases}
\end{equation*}
\begin{multline*}
     g(\varepsilon,d) = \Theta\bigl(\phi(\varepsilon^{-1},p) \psi(d,q) \bigr) \text{ means } \\
    \lim_{\substack{\varepsilon \to 0 \\ d \to \infty}} \frac{g(\varepsilon,d)}{\phi(\varepsilon^{-1},p') \psi(d,q')}
          \begin{cases} < \infty, & p'> p, \  q' > q,  \\ 
          =\infty, & p' < p, \ q' < q.\end{cases}
\end{multline*}

\begin{definition}
If there exist the functions $\phi$ and $\psi$ satisfying the conditions listed above and there exist positive numbers $p$ and $q$ with
\[
\comp(\varepsilon, d)  = \Theta\bigl(\phi(\varepsilon^{-1},p) \psi(d,q) \bigr),
\]
then we call a problem $\phi$-$\psi$-tractable with exponents $p$ and $q$.  
If there exists a function $\phi$ satisfying the conditions above and a positive number $p$ such that 
\begin{equation}\label{eq:def_strong_tract}
\comp(\varepsilon, d)  = \Theta\bigl(\phi(\varepsilon^{-1},p) \bigr)
\end{equation}
then we call a problem strongly $\phi$-tractable with exponent $p$. The infimum $p^*$ of all exponents $p>0$ such that \eqref{eq:def_strong_tract} holds, 
is called the exponent of strong $\phi$-tractability. 
\end{definition}

\section{Main Results}
Suppose that, for any real $\tau_1, \tau_2>0$ and any $p,q>0$, it holds that
\begin{align*}
 (\phi(\varepsilon^{-1},p))^{\tau_1} &\le K_{p,\tau_1} \phi (\varepsilon^{-1},\tau_1 p)\\
  (\psi(d,q))^{\tau_2} &\le L_{q,\tau_2} \psi (d,\tau_2 q)\\
\end{align*}
for all $\varepsilon\in (0,1)$, where $K_{p,\tau_1}>0$ is a constant that may depend on $p$ and $\tau_1$, but is independent of $\varepsilon$, 
and where $L_{q,\tau_2}>0$ is a constant that may depend on $q$ and $\tau_2$, but is independent of $d$.

We first show the following result. 
\begin{theorem}\label{thm_main_strong_tract} 
A problem is strongly $\phi$-tractable iff there exists $p>0$ and an integer $C(p)\ge 0$ such that
\begin{equation} \label{eq:strong_tractiff}
     \sup_{d \in \naturals} \sum_{i = C(p)}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)} < \infty.
\end{equation}
If \eqref{eq:strong_tractiff} holds, then the exponent of strong $\phi$-tractability equals
\[
 p^* := \inf\{p>0\ \mbox{such that \eqref{eq:tractiff} holds}\}.
\]

\end{theorem}

\begin{proof}
We first show the sufficiency of \eqref{eq:strong_tractiff}. Suppose that \eqref{eq:strong_tractiff} holds for some $p>0$.  
Because $\phi$ is increasing in its arguments, it follows that the complexity may be equivalently expressed as 
\begin{align*}
    \comp(\varepsilon, d) &= \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon\} \\
    &= \min \biggl\{n \in \natzero : \frac{1}{\phi(\lambda_{n+1, d}^{-1},p)} \le \frac{1}{\phi(\varepsilon^{-1},p)} \biggr\}.
\end{align*}
Since the $\lambda_{i,d}$ are non-increasing it follows that the $\phi(\lambda_{i, d}^{-1},p)$ are non-decreasing. 
In particular, for all $n \in \naturals$,
\begin{align*}
    \MoveEqLeft{\lambda_{n+1,d} \le \lambda_{n,d} \le \cdots \le \lambda_{1,d}} \\
    & \implies \frac{1}{\phi(\lambda_{n+1, d}^{-1},p)} \le \frac{1}{\phi(\lambda_{n, d}^{-1},p)} \le \cdots \le \frac{1}{\phi(\lambda_{1, d}^{-1},p)} \\
    & \implies \frac{1}{\phi(\lambda_{n+1, d}^{-1},p)} 
    \le \frac 1n \sum_{i=1}^n  \frac{1}{\phi(\lambda_{i, d}^{-1},p)} 
    \le \frac 1n \sum_{i=1}^\infty  \frac{1}{\phi(\lambda_{i, d}^{-1},p)}.
\end{align*}
Thus, we can conclude that 
\begin{align*}
    n \ge \phi(\varepsilon^{-1},p) \sum_{i=1}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)}
    & \implies 
  \frac 1n \sum_{i=1}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)} \le  \frac{1}{\phi(\varepsilon^{-1},p')} \\
   & \implies   \frac{1}{\phi(\lambda_{n+1, d}^{-1},p)} \le \frac{1}{\phi(\varepsilon^{-1},p)}.
\end{align*}
This implies an upper bound on the complexity of
\begin{align*}
       \MoveEqLeft{\comp(\varepsilon,d)} \\
       &\le 1 + \phi(\varepsilon^{-1},p) \sum_{i=1}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)} \\
       & = 1 + \phi(\varepsilon^{-1}, p) \left [ \sum_{i=1}^{C(p)-1} \frac{1}{\phi(\lambda_{i, d}^{-1},p)}  
       + \underbrace{\sum_{i=C(p)}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)}}_{=:S_p <\infty\ \text{by \eqref{eq:tractiff}} }\right] \\
       & \le 1+ \phi(\varepsilon^{-1},p) \underbrace{\left(\frac{C(p)-1}{\phi(\lambda_{\max}^{-1},p)} + S_p\right)}_{=:C_1(p)}\\
       & = 1+ \phi(\varepsilon^{-1},p) C_1 (p),
\end{align*}
which means that we have strong $\phi$-tractability, and verifies sufficiency of \eqref{eq:strong_tractiff}.

\bigskip

For the exponent $p^*$ of $\phi$-tractability, we then obviously obtain 
\[
 p^* \le \inf\{p>0\ \mbox{such that \eqref{eq:strong_tractiff} holds}\}.
\]

\bigskip

Let us now show necessity of \eqref{eq:strong_tractiff}. Indeed, suppose that we have strong 
$\phi$-tractability. I.e., 
\[
\comp(\varepsilon,d)=\Theta (\phi(\varepsilon^{-1},p))
\]
for some $p>0$. This, in turn, means that there is a positive constant $K$ such that
\begin{equation}\label{eq_strong_tract_p'}
\comp(\varepsilon,d)\le K \phi(\varepsilon^{-1},p')
\end{equation}
for all $p'>p$.

Hence, for (possibly small) $\delta_p>0$, there exists a constant $K$ such that \eqref{eq_strong_tract_p'} holds for $p'=p+\delta_p$.

We know that
\[
\lambda_{\comp(\varepsilon,d)+1,d}\le \varepsilon.
\]
Since the eigenvalues $\lambda_{j,d}$ are non-increasing, we have
\begin{equation}\label{eq:lambda_K_strong}
\lambda_{\lfloor K \phi(\varepsilon^{-1},p')\rfloor +1,d}\le \varepsilon.
\end{equation}
Let
\[
j=j (\varepsilon):= \lfloor K \phi(\varepsilon^{-1},p')\rfloor +1.
\]
If we vary $\varepsilon\in (0,1]$, we see that $j=j_d^*, j_d^*+1, j_d^*+2,\ldots$, where 
\[
  j_d^*=\lfloor K \phi(1,p')\rfloor +1
\]
Note that
\[
j\le K \phi(\varepsilon^{-1},p')+1.
\]
Due to our assumptions, we know that 
$\phi(\cdot, p')$ is increasing in the first argument if 
we keep $p'$ fixed. Let $\phi_{p'}^{-1} (\cdot)$ be the inverse function of $\phi (\cdot, p')$ with respect to the first argument. 
ote that also $\phi_{p'}^{-1}$ is strictly increasing.

Then, 
\[
j \le K \phi(\varepsilon^{-1},p')+1
\]
is equivalent to
\[
\frac{j-1}{K} \le \phi(\varepsilon^{-1},p').
\]
By the monotonicity of $\phi_{p'}^{-1}$, the latter inequality holds if and only if
\[
  \phi_{p'}^{-1} \left(\frac{j-1}{K} \right)
  \le \varepsilon^{-1},
\]
or, equivalently,
\[
 \varepsilon \le \frac{1}{\phi_{p'}^{-1} \left(\frac{j-1}{K} \right)}.
\]
By using \eqref{eq:lambda_K_strong}, we derive
\[
 \lambda_{j,d}\le \frac{1}{\phi_{p'}^{-1} \left(\frac{j-1}{K} \right)}
\]
for all $j\ge j_d^*$, which is again equivalent to 
\[
\lambda_{j,d}^{-1}\ge \phi_{p'}^{-1} \left(\frac{j-1}{K} \right),
\]
which holds if and only if
\[ 
 \phi (\lambda_{j,d}^{-1}, p') \ge \frac{j-1}{K}.
\]
This implies, for any $\tau>1$, that 
\[ 
 (\phi (\lambda_{j,d}^{-1}, p'))^\tau \ge \frac{(j-1)^\tau}{K^\tau },
\]
which implies, due to our assumption on $\phi$, 
\[ 
 K_{p',\tau}\,\phi (\lambda_{j,d}^{-1}, \tau p') \ge \frac{(j-1)^\tau}{K^\tau }.
\]
This yields
\[
\sum_{j=j_d^*}^\infty \frac{1}{\phi (\lambda_{j,d}^{-1}, \tau p')} \le K_{p',\tau}\, K^\tau \sum_{j=j_d^*}^\infty \frac{1}{(j-1)^\tau}<\infty.
\]

Note, however, that 
\[
 j_d^* = \lfloor K \phi(1,p')\rfloor +1 \le \lfloor K \phi(1,\tau p')\rfloor +1
\]
Hence, we can find $C(\tau p')$ such that 
\[
 \sum_{j=C(\tau p')}^\infty \frac{1}{\phi (\lambda_{j,d}^{-1}, \tau p')}<\infty.
\]
This yields \eqref{eq:strong_tractiff} with $p$ replaced by $\tau p'$, and so we see necessity of $\eqref{eq:strong_tractiff}$.

\bigskip

Assume that $p^*$ is the $\varepsilon$-exponent of strong $\phi$-tractability. We already know from the first part of the proof that 
\[
 p^* \le \inf\{p>0\ \mbox{such that \eqref{eq:strong_tractiff} holds}\}.
\]
Suppose that we would have 
\[
 p^* < \inf\{p>0\ \mbox{such that \eqref{eq:strong_tractiff} holds}\}.
\]
Then, however, we could proceed as in the second part of the proof and show that 
\[
 \sum_{j=C(\tau p')}^\infty \frac{1}{\phi (\lambda_{j,d}^{-1}, \tau p')}<\infty.
\]
for any $\tau>1$, any $p'>p^*$, and a suitable $C(\tau p')$. By choosing $\tau$ sufficiently close to 1, and $p'$ sufficiently close to $p^*$, we then would 
obtain 
\[
 \tau p' < \inf\{p>0\ \mbox{such that \eqref{eq:strong_tractiff} holds}\},
\]
which is a contradiction. So, we must have 
\[
 p^* = \inf\{p>0\ \mbox{such that \eqref{eq:strong_tractiff} holds}\}.
\]

This concludes the proof of the theorem. 
\end{proof}

Next we show a theorem characterizing $\phi$-$\psi$-tractability. 
\begin{theorem}\label{thm_main_tract} 
A problem is $\phi$-$\psi$-tractable iff there exist $p,q>0$ and an integer $C(p,q) \ge 0$ such that
\begin{equation} \label{eq:tractiff}
     \sup_{d \in \naturals} \frac{1}{\psi(d,q)} \sum_{i = C(p,q)}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p))} < \infty.
\end{equation}
\end{theorem}
\begin{proof}
We first show the sufficiency of \eqref{eq:tractiff}. Suppose that \eqref{eq:tractiff} holds for some $p,q>0$. 
Because $\phi$ is increasing in its arguments, it follows that the complexity may be equivalently expressed as 
\begin{align*}
    \comp(\varepsilon, d) &= \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon\} \\
    &= \min \biggl\{n \in \natzero : \frac{1}{\phi(\lambda_{n+1, d}^{-1},p)} \le \frac{1}{\phi(\varepsilon^{-1},p)} \biggr\}.
\end{align*}

Since the $\lambda_{i,d}$ are non-increasing it follows that the $\phi(\lambda_{i, d}^{-1},p)$ are non-decreasing, and this holds for any $\tau>1$.  
In particular, for all $n \in \naturals$,
\begin{align*}
    \MoveEqLeft{\lambda_{n+1,d} \le \lambda_{n,d} \le \cdots \le \lambda_{1,d}} \\
    & \implies \frac{1}{\phi(\lambda_{n+1, d}^{-1},p)} \le \frac{1}{\phi(\lambda_{n, d}^{-1},p))} \le \cdots \le \frac{1}{\phi(\lambda_{1, d}^{-1},p)} \\
    & \implies \frac{1}{\phi(\lambda_{n+1, d}^{-1},p)} 
    \le \frac 1n \sum_{i=1}^n  \frac{1}{\phi(\lambda_{i, d}^{-1},p)} 
    \le \frac 1n \sum_{i=1}^\infty  \frac{1}{\phi(\lambda_{i, d}^{-1},p)}.
\end{align*}
Thus, we can conclude that 
\begin{align*}
    n \ge \phi(\varepsilon^{-1},p) \sum_{i=1}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)}
    & \implies 
  \frac 1n \sum_{i=1}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)} \le  \frac{1}{\phi(\varepsilon^{-1},p)} \\
   & \implies   \frac{1}{\phi(\lambda_{n+1, d}^{-1},p)} \le \frac{1}{\phi(\varepsilon^{-1},p)}.
\end{align*}
This implies an upper bound on the complexity of
\begin{align*}
       \MoveEqLeft{\comp(\varepsilon,d)} \\
       &\le 1 + \phi(\varepsilon^{-1},p) \sum_{i=1}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)} \\       
       & = 1 + \phi(\varepsilon^{-1},p) \left [ \sum_{i=1}^{C(p,q)-1} \frac{1}{\phi(\lambda_{i, d}^{-1},p)}  
       + \sum_{i=C(p,q)}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)} \right ] \\
       & \le 1+ \phi(\varepsilon^{-1},p) \underbrace{\frac{C(p,q)-1}{\phi(\lambda_{\max}^{-1},p)}}_{=:C_1(p,q)}
       +  \phi(\varepsilon^{-1},p) \psi(d,q)
        \qquad \text{by \eqref{eq:tractiff}} \\
        & \le 1+\phi(\varepsilon^{-1},p) \bigl[C_1(p,q) + \psi(d,q) \bigr].
\end{align*}
It follows that we have $\phi$-$\psi$-tractability, which shows sufficiency of \eqref{eq:tractiff}.

\bigskip

%---------------------------------------------------------------------
%---------------------------------------------------------------------

Let us now show necessity. Indeed, suppose that we have 
$\phi$-$\psi$-tractability with parameters $p$ and $q$. I.e., 
\[
\comp(\varepsilon,d)=\Theta (\phi(\varepsilon^{-1},p)\psi(d,q))
\]
for some $p,q>0$. This, in turn, means that there is a positive constant $K$ such that
\begin{equation}\label{eq_tract_p'q'}
\comp(\varepsilon,d)\le K \phi(\varepsilon^{-1},p')\psi(d,q')
\end{equation}
for all $p'>p$ and $q'>q$.

Hence, for (possibly small) $\delta_p>0$ and $\delta_q>0$, there exists a constant $K$ such that \eqref{eq_tract_p'q'} holds for $p'=p+\delta_p$ 
and $q'=q+\delta_q$.

We know that
\[
\lambda_{\comp(\varepsilon,d)+1,d}\le \varepsilon.
\]
Since the eigenvalues $\lambda_{j,d}$ are non-increasing, we have
\begin{equation}\label{eq:lambda_K}
\lambda_{\lfloor K \phi(\varepsilon^{-1},p')\psi(d,q')\rfloor +1,d}\le \varepsilon.
\end{equation}
Let
\[
j=j (\varepsilon):= \lfloor K \phi(\varepsilon^{-1},p')\psi(d,q')\rfloor +1.
\]
If we vary $\varepsilon\in (0,1]$, we see that $j=j_d^*, j_d^*+1, j_d^*+2,\ldots$, where 
\[
  j_d^*=\lfloor K \phi(1,p')\psi(d,q')\rfloor +1
\]
Note that
\[
j\le K \phi(\varepsilon^{-1},p')\psi(d,q') +1.
\]
Due to our assumptions, we know that 
$\phi(\cdot, p')$ is increasing in the first argument if 
we keep $p'$ fixed. Let $\phi_{p'}^{-1} (\cdot)$ be the inverse function of $\phi (\cdot, p')$ with respect to the first argument. Note that also $\phi_{p'}^{-1}$ is strictly increasing.

Then, 
\[
j \le K \phi(\varepsilon^{-1},p')\psi(d,q') +1
\]
is equivalent to
\[
\frac{j-1}{K \psi(d,q')} \le \phi(\varepsilon^{-1},p').
\]
By the monotonicity of $\phi_{p'}^{-1}$, the latter inequality holds if and only if
\[
  \phi_{p'}^{-1} \left(\frac{j-1}{K \psi(d,q')} \right)
  \le \varepsilon^{-1},
\]
or, equivalently,
\[
 \varepsilon \le \frac{1}{\phi_{p'}^{-1} \left(\frac{j-1}{K \psi(d,q')} \right)}.
\]
By using \eqref{eq:lambda_K}, we derive
\[
 \lambda_{j,d}\le \frac{1}{\phi_{p'}^{-1} \left(\frac{j-1}{K \psi(d,q')} \right)}
\]
for all $j\ge j_d^*$, which is again equivalent to 
\[
\lambda_{j,d}^{-1}\ge \phi_{p'}^{-1} \left(\frac{j-1}{K \psi(d,q')} \right),
\]
which holds if and only if
\[ 
 \phi (\lambda_{j,d}^{-1}, p') \ge \frac{j-1}{K \psi(d,q')}.
\]
This implies, for any $\tau>1$, that 
\[ 
 (\phi (\lambda_{j,d}^{-1}, p'))^\tau \ge \frac{(j-1)^\tau}{K^\tau (\psi(d,q'))^\tau},
\]
which yields
\[ 
 K_{p',\tau}\, \phi (\lambda_{j,d}^{-1}, \tau p') \ge (\phi (\lambda_{j,d}^{-1}, p'))^\tau 
 \ge \frac{(j-1)^\tau}{K^\tau (\psi(d,q'))^\tau}\ge \frac{(j-1)^\tau}{K^\tau\, L_{q',\tau}\, \psi(d,\tau q')}.
\]
This then implies
\[
\frac{1}{L_{q',\tau}\, \psi(d,\tau q')} \sum_{j=j_d^*}^\infty \frac{1}{\phi (\lambda_{j,d}^{-1}, \tau p')} 
\le K_{p',\tau}\, K^\tau \sum_{j=j_d^*}^\infty \frac{1}{(j-1)^\tau}<\infty.
\]
Note now that
\[
 j_d^* = \lfloor K \phi(1,p')\psi (1,q')\rfloor +1 \le \lfloor K\phi(1,\tau p')\psi (1,\tau q')\rfloor +1.
\]
So, there exists $C(\tau p',\tau q')$ such that 
\[
 \sum_{j=C(\tau p',\tau q')}^\infty \frac{1}{\phi (\lambda_{j,d}^{-1}, \tau p')}<\infty.
\]
This yields \eqref{eq:tractiff} with $p$ replaced by $\tau p'$ and $q$ replaced by $\tau q'$, and so we see necessity of $\eqref{eq:tractiff}$.

\end{proof}

\bigskip

\bigskip

\fred{We need to check the proof for 
\begin{itemize}
\item correctness
\item exponents
\item whether the additional assumptions are too restrictive and can be generalized
\item whether we need $\tau$ in the assumption
\end{itemize}}

\end{document}

### 2023-03-10 GeneralizedTractability_230209.tex
Updates from Overleaf

--- 2023-03-10 GeneralizedTractability_230108.tex
@@
 \section{Introduction}
+
+TODO: We need to check the relation of our work to that of Michael Gnewuch and Henryk.
+We do not need tensor product structure: do they need that assumption?
+The summation conditions on the eigenvalues might be a significant difference between our results and theirs.
+
+\medskip
+
+TODO: Check in how far our conditions coincide with existing conditions for less general tractability notions (polynomial tractability, etc.).
+
+\medskip
 
@@
 
-Let us now show necessity of \eqref{eq:strong_tractiff}. Indeed, suppose that we have strong 
+Let us now show the necessity of \eqref{eq:strong_tractiff}. Indeed, suppose that we have strong 
 $\phi$-tractability. I.e., 
@@
 Since the eigenvalues $\lambda_{j,d}$ are non-increasing, we have
-\begin{equation}\label{eq:lambda_K_strong}
+\begin{equation}\label{eq:lambda_K_strong3}
 \lambda_{\lfloor K \phi(\varepsilon^{-1},p')\rfloor +1,d}\le \varepsilon.
@@
 we keep $p'$ fixed. Let $\phi_{p'}^{-1} (\cdot)$ be the inverse function of $\phi (\cdot, p')$ with respect to the first argument. 
-ote that also $\phi_{p'}^{-1}$ is strictly increasing.
+Note that also $\phi_{p'}^{-1}$ is strictly increasing.
 
@@
 \]
-By using \eqref{eq:lambda_K_strong}, we derive
+By using \eqref{eq:lambda_K_strong3}, we derive
 \[
@@
 
-Next we show a theorem characterizing $\phi$-$\psi$-tractability. 
+Next, we show a theorem characterizing $\phi$-$\psi$-tractability. 
 \begin{theorem}\label{thm_main_tract} 
@@
 \]
-This yields \eqref{eq:tractiff} with $p$ replaced by $\tau p'$ and $q$ replaced by $\tau q'$, and so we see necessity of $\eqref{eq:tractiff}$.
+This yields \eqref{eq:tractiff} with $p$ replaced by $\tau p'$ and $q$ replaced by $\tau q'$, and so we see the necessity of $\eqref{eq:tractiff}$.
 
 \end{proof}
+\newpage
+\bigskip
+
+\kachi{
+Let $T$ be a tractability function defined as follows
+\[
+T :(0,\infty) \times \mathbb{N} \times [0,\infty) \times [0,\infty) \rightarrow [1,\infty)
+\] 
+strictly increasing in all variables.
+
+Also,
+\[
+[T(\varepsilon^{-1},d,p,q)]^\tau \le K_{p,q,\tau} T(\varepsilon^{-1},d,\tau p,\tau q)
+\]
+A problem is $T$-tractable with parameters $p$ and $q$ iff
+\begin{equation} \label{comp_def}
+\comp(\varepsilon,d) \le C(p,q) T(\varepsilon^{-1},d,p,q) \qquad \forall \varepsilon \in (0,\infty), \ d \in \mathbb{N}
+\end{equation}
+The  set of optimal parameters, $\mathcal{P}_{\text{opt}}$ is defined as
+\begin{multline}
+    \mathcal{P}_{\text{opt}} : = \{(p^*,q^*) : \eqref{comp_def} \text{ holds }\forall (p,q) \in [p^*,\infty) \times [q^*,\infty) \setminus (p^*,q^*) \\ 
+    \eqref{comp_def} \text{ fails } \forall (p,q) \in [0,p^*] \times [0,q^*] \setminus (p^*,q^*) \}
+\end{multline}
+
+\begin{theorem}\label{thm_main_tract2} 
+A problem is $T$-tractable with $q=0$ iff there exists $p>0$ and an integer $C(p) \ge 0$ such that
+\begin{equation} \label{eq:strong_tractiff3}
+     \sup_{d \in \naturals} \sum_{i = C(p)}^\infty \frac{1}{T(\lambda_{i,d}^{-1},1,p,0)} < \infty.
+\end{equation}
+%$ \frac{1}{\psi(d,q)}\frac{1}{\phi(\lambda_{i, d}^{-1},p))} $
+\end{theorem}
+
+If \eqref{eq:strong_tractiff3} holds, then the optimal $p$
+is defined as
+\[
+ p^* := \inf\{p>0\ \mbox{such that \eqref{comp_def} holds}\}.
+\]
+\bigskip
+\begin{proof}
+\textbf{Sufficient condition:}\\
+Given that $T$ is increasing in its arguments, we have the following equivalent expression 
+    \begin{align*}
+    \comp(\varepsilon, d) &= \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon\} \\
+    &= \min \biggl\{n \in \natzero : \frac{1}{T(\lambda_{n+1,d}^{-1},1,p,0)}\le \frac{1}{T(\varepsilon^{-1},1,p,0) }\biggr\}.
+\end{align*}
+Also since the $\lambda_{i,d}$ are non-increasing, it follows that the $T(\lambda_{i,d}^{-1},1,p,0)$ are non-decreasing. In particular, for all $n\in \mathbb{N}$, we have
+
+\begin{align*}
+    \MoveEqLeft{\lambda_{n+1,d} \le \lambda_{n,d} \le \cdots \le \lambda_{1,d}} \\
+    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},1,p,0)} \le \frac{1}{T(\lambda_{n, d}^{-1},1,p,0)} \le \cdots \le \frac{1}{T(\lambda_{1, d}^{-1},1,p,0)} \\
+    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},1,p,0) }
+    \le \frac 1n \sum_{i=1}^n  \frac{1}{T(\lambda_{i, d}^{-1},1,p,0) }
+    \le \frac 1n \sum_{i=1}^\infty  \frac{1}{T(\lambda_{i, d}^{-1},1,p,0)}.
+\end{align*}
+Thus, we can conclude that 
+\begin{align*}
+    n \ge T(\varepsilon^{-1},1,p,0) \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},1,p,0)}
+    & \implies 
+\frac 1n \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},1,p,0) }\le  T(\varepsilon^{-1},1,p,0) \\
+   & \implies   \frac{1}{T(\lambda_{n+1, d}^{-1},1,p,0)} \le \frac{1}{T(\varepsilon^{-1},1,p,0)}.
+\end{align*}
+
+This implies an upper bound on the complexity of
+\begin{align*}
+       \MoveEqLeft{\comp(\varepsilon,d)} \\
+       &\le 1 + T(\varepsilon^{-1},1,p,0) \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},1,p,0)} \\
+       & = 1 + T(\varepsilon^{-1},1, p,0) \left [ \sum_{i=1}^{C(p)-1} \frac{1}{T(\lambda_{i, d}^{-1},1,p,0)}
+       + \underbrace{\sum_{i=C(p)}^\infty \frac{1}{T(\lambda_{i, d}^{-1},1,p,0)}}_{=:S_p^* <\infty\ \text{by \eqref{eq:tractiff}} }\right] \\
+       & \le 1+ T(\varepsilon^{-1},1,p,0) \underbrace{\left[\frac{(C(p)-1)}{T(\lambda_{\max}^{-1},1,p,0)} + S_p^*\right]}_{=:C_2(p)}\\
+       & = 1+ T(\varepsilon^{-1},1,p,0) C_2 (p)
+\end{align*}
+which means that we have strong $T$-tractability, and verifies sufficiency of \eqref{eq:strong_tractiff3}.
 
@@
 
+\bigskip
+\noindent \textbf{Necessity condition:} \\
+Suppose that we have strong 
+$T$-tractability. That is, 
+\[
+\comp(\varepsilon,d)=\Theta (T(\varepsilon^{-1},1,p,0))
+\]
+for some $p>0$. This, in turn, means that there is a positive constant $K$ such that
+\begin{equation}\label{eq_strong_tract_p'3}
+\comp(\varepsilon,d)\le K T(\varepsilon^{-1},1,p',0)
+\end{equation}
+for all $p'>p$.
+
+\noindent This means for (possibly small) $\delta_p>0$, there exists a constant $K$ such that \eqref{eq_strong_tract_p'3} holds for $p'=p+\delta_p$.
+
+Since the eigenvalues $\lambda_{j,d}$ are non-increasing, we have
+\begin{equation}\label{eq:lambda_K_strong3}
+\lambda_{\lfloor K T(\varepsilon^{-1},1,p',0)\rfloor +1,d}\le \varepsilon.
+\end{equation}
+Let
+\[
+j=j (\varepsilon):= \lfloor K T(\varepsilon^{-1},1,p',0)\rfloor +1.
+\]
+
+Suppose we vary $\varepsilon\in (0,1]$, we have that $j=j_d^*, j_d^*+1, j_d^*+2,\ldots$, where 
+\[
+  j_d^*=\lfloor K T(1,1,p',0)\rfloor +1
+\]
+Note that
+\[
+j\le K T(\varepsilon^{-1},1,p',0)+1.
+\]
+Due to our assumptions, we know that 
+$T(\cdot,1, p',0)$ is increasing in the first argument if 
+we keep $p'$ fixed. Let $T_{p'}^{-1} (\cdot)$ be the inverse function of $T (\cdot,1, p',0)$ with respect to the first argument. Observe also that $T_{p'}^{-1}$ is strictly increasing.
+
+Then, 
+\[
+j \le K T(\varepsilon^{-1},1,p',0)+1
+\]
+is equivalent to
+\[
+\frac{j-1}{K} \le T(\varepsilon^{-1},1,p',0).
+\]
+By the monotonicity of $T_{p'}^{-1}$, the latter inequality holds if and only if
+\[
+  T_{p'}^{-1} \left(\frac{j-1}{K} \right)
+  \le \varepsilon^{-1},
+\]
+or, equivalently,
+\[
+ \varepsilon \le \frac{1}{T_{p'}^{-1} \left(\frac{j-1}{K} \right)}.
+\]
+By using \eqref{eq:lambda_K_strong3}, we derive
+\[
+ \lambda_{j,d}\le \frac{1}{T_{p'}^{-1} \left(\frac{j-1}{K} \right)}
+\]
+for all $j\ge j_d^*$, which is again equivalent to 
+\[
+\lambda_{j,d}^{-1}\ge T_{p'}^{-1} \left(\frac{j-1}{K} \right),
+\]
+which holds if and only if
+\[ 
+ T(\lambda_{j,d}^{-1},1, p',0) \ge \frac{j-1}{K}.
+\]
+This implies, for any $\tau>1$, that 
+\[ 
+ (T(\lambda_{j,d}^{-1},1, p',0))^\tau \ge \frac{(j-1)^\tau}{K^\tau },
+\]
+which implies, due to our assumption on $\phi$, 
+\[ 
+ K_{p',\tau}\,T (\lambda_{j,d}^{-1},1,\tau p',0) \ge \frac{(j-1)^\tau}{K^\tau }.
+\]
+This yields
+\[
+\sum_{j=j_d^*}^\infty \frac{1}{T (\lambda_{j,d}^{-1},1, \tau p',0)} \le K_{p',\tau}\, K^\tau \sum_{j=j_d^*}^\infty \frac{1}{(j-1)^\tau}<\infty.
+\]
+
+Note, however, that 
+\[
+ j_d^* = \lfloor K T(1,1,p',0)\rfloor +1 \le \lfloor K T(1,1,\tau p',0)\rfloor +1
+\]
+Hence, we can find $C(\tau p')$ such that 
+\[
+ \sum_{j=C(\tau p')}^\infty \frac{1}{T(\lambda_{j,d}^{-1},1, \tau p',0)}<\infty.
+\]
+This yields \eqref{eq:strong_tractiff3} with $p$ replaced by $\tau p'$, and so we see necessity of $\eqref{eq:strong_tractiff3}$.
+
+\end{proof}
+\bigskip
+\begin{theorem}\label{thm_main_strong_tract2} 
+A problem is $T$-tractable iff there exist $p,q>0$ and an integer $C(p,q) \ge 0$ such that
+\begin{equation} \label{eq:tractiff4}
+     \sup_{d \in \naturals} \sum_{i = C(p,q)}^\infty \frac{1}{T(\lambda^{-1}_{i,d},d,p,q)}< \infty.
+\end{equation}
+%$ \frac{1}{\psi(d,q)}\frac{1}{\phi(\lambda_{i, d}^{-1},p))} $
+
+\end{theorem}
+
+\begin{proof}
+    \textbf{Sufficient Condition:}\\ Suppose that \eqref{eq:tractiff4} holds for some $p,q>0$. 
+Because $T$ is increasing in its arguments, it follows that the complexity may be equivalently expressed as 
+\begin{align*}
+    \comp(\varepsilon, d) &= \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon\} \\
+    &= \min \biggl\{n \in \natzero : \frac{1}{T(\lambda_{n+1, d}^{-1},d,p,q)} \le \frac{1}{T(\varepsilon^{-1},d,p,q)} \biggr\}.
+\end{align*}
+
+Since the $\lambda_{i,d}$ are non-increasing it follows that the $\phi(\lambda_{i, d}^{-1},p)$ are non-decreasing, and this holds for any $\tau>1$.  
+In particular, for all $n \in \naturals$,
+\begin{align*}
+    \MoveEqLeft{\lambda_{n+1,d} \le \lambda_{n,d} \le \cdots \le \lambda_{1,d}} \\
+    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d,p,q)} \le \frac{1}{T(\lambda_{n, d}^{-1},d,p,q))} \le \cdots \le \frac{1}{T(\lambda_{1, d}^{-1},d,p,q)} \\
+    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d,p.q)} 
+    \le \frac 1n \sum_{i=1}^n  \frac{1}{T(\lambda_{i, d}^{-1},d,p,q)} 
+    \le \frac 1n \sum_{i=1}^\infty  \frac{1}{T(\lambda_{i, d}^{-1},d,p,q)}.
+\end{align*}
+Thus, we can conclude that 
+\begin{align*}
+    n \ge T(\varepsilon^{-1},d,p,q) \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d,p,q)}
+    & \implies 
+  \frac 1n \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d,p,q)} \le  \frac{1}{T(\varepsilon^{-1},d,p,q)} \\
+   & \implies   \frac{1}{T(\lambda_{n+1, d}^{-1},d,p,q)} \le \frac{1}{T(\varepsilon^{-1},d,p,q)}.
+\end{align*}
+This implies an upper bound on the complexity of
+\begin{align*}
+       \MoveEqLeft{\comp(\varepsilon,d)} \\
+       &\le 1 + T(\varepsilon^{-1},d,p,q) \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d,p,q)} \\       
+       & = 1 + T(\varepsilon^{-1},d,p,q) \left [ \sum_{i=1}^{C(p,q)-1} \frac{1}{T(\lambda_{i, d}^{-1},d,p,q)}  
+       + \sum_{i=C(p,q)}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d,p,q)} \right ] \\
+       & \le 1+ T(\varepsilon^{-1},d,p,q) \underbrace{\frac{C(p,q)-1}{T(\lambda_{\max}^{-1},d,p,q)}}_{=:C_1(p,q)}
+       +  T(\varepsilon^{-1},d,p,q) 
+        \qquad \text{by \eqref{eq:tractiff4}} \\
+        & \le 1+T(\varepsilon^{-1},d,p,q) \bigl[C_1(p,q) +1\bigr].
+\end{align*}
+It follows that we have $T$-tractability, which shows sufficiency of \eqref{eq:tractiff3}. \\
+
+\textbf{Necessity condition:}\\
+Suppose that we have 
+$T$-tractability with parameters $p$ and $q$. That is, 
+\[
+\comp(\varepsilon,d)=\Theta (T(\varepsilon^{-1},d,p,q))
+\]
+for some $p,q>0$. This, in turn, means that there is a positive constant $K$ such that
+\begin{equation}\label{eq_tract_p'q'4}
+\comp(\varepsilon,d)\le K T(\varepsilon^{-1},d,p',q')
+\end{equation}
+for all $p'>p$ and $q'>q$.
+
+Hence, for (possibly small) $\delta_p>0$ and $\delta_q>0$, there exists a constant $K$ such that \eqref{eq_tract_p'q'4} holds for $p'=p+\delta_p$ 
+and $q'=q+\delta_q$.
+
+We know that
+\[
+\lambda_{\comp(\varepsilon,d)+1,d}\le \varepsilon.
+\]
+Since the eigenvalues $\lambda_{j,d}$ are non-increasing, we have
+\begin{equation}\label{eq:lambda_K4}
+\lambda_{\lfloor K T(\varepsilon^{-1},d,p',q)\rfloor +1,d}\le \varepsilon.
+\end{equation}
+Let
+\[
+j=j (\varepsilon):= \lfloor K T(\varepsilon^{-1},d,p',q')\rfloor +1.
+\]
+If we vary $\varepsilon\in (0,1]$, we see that $j=j_d^*, j_d^*+1, j_d^*+2,\ldots$, where 
+\[
+  j_d^*=\lfloor K T(1,d,p',q')\rfloor +1
+\]
+Note that
+\[
+j\le K T(\varepsilon^{-1},d,p',q') +1.
+\]
+Due to our assumptions, we know that 
+$T(\cdot,d,p',q')$ is increasing in the first argument if 
+we keep $p'$ and $q'$ fixed. Let $T_{p',q'}^{-1} (\cdot)$ be the inverse function of $T(\cdot,d,p',q')$ with respect to the first argument. Note that also $T_{p',q'}^{-1}$ is strictly increasing.
+
+Then, 
+\[
+j \le K T(\varepsilon^{-1},d,p',q') +1
+\]
+is equivalent to
+\[
+\frac{j-1}{K } \le T(\varepsilon^{-1},d,p',q').
+\]
+By the monotonicity of $T_{p',q'}^{-1}$, the latter inequality holds if and only if
+\[
+  T_{p',q'}^{-1} \left(\frac{j-1}{K} \right)
+  \le \varepsilon^{-1},
+\]
+or, equivalently,
+\[
+ \varepsilon \le \frac{1}{T_{p',q'}^{-1} \left(\frac{j-1}{K} \right)}.
+\]
+By using \eqref{eq:lambda_K4}, we derive
+\[
+ \lambda_{j,d}\le \frac{1}{T_{p',q'}^{-1} \left(\frac{j-1}{K } \right)}
+\]
+for all $j\ge j_d^*$, which is again equivalent to 
+\[
+\lambda_{j,d}^{-1}\ge T_{p',q'}^{-1} \left(\frac{j-1}{K} \right),
+\]
+which holds if and only if
+\[ 
+T(\lambda_{j,d}^{-1},d, p',q') \ge \frac{j-1}{K}.
+\]
+This implies, for any $\tau>1$, that 
+\[ 
+ (T(\lambda_{j,d}^{-1},d, p',q'))^\tau \ge \frac{(j-1)^\tau}{K^\tau },
+\]
+which yields
+\[ 
+ K_{p',q',\tau}\, T (\lambda_{j,d}^{-1},d,\tau p',\tau q') \ge (T(\lambda_{j,d}^{-1},d, p',q'))^\tau 
+ \ge \frac{(j-1)^\tau}{K^\tau}.
+\]
+This then implies
+\[
+\sum_{j=j_d^*}^\infty \frac{1}{T(\lambda_{j,d}^{-1},d, \tau p',\tau q')} 
+\le K_{p',q',\tau}\, K^\tau \sum_{j=j_d^*}^\infty \frac{1}{(j-1)^\tau}<\infty.
+\]
+Note now that
+\[
+ j_d^* = \lfloor K T(1,1,p',q')\rfloor +1 \le \lfloor KT(1,1,\tau p',\tau q')\rfloor +1.
+\]
+So, there exists $C(\tau p',\tau q')$ such that 
+\[
+ \sum_{j=C(\tau p',\tau q')}^\infty \frac{1}{T(\lambda_{j,d}^{-1},d, \tau p',\tau q')}<\infty.
+\]
+This yields \eqref{eq:tractiff} with $p$ replaced by $\tau p'$ and $q$ replaced by $\tau q'$, and so we see the necessity of $\eqref{eq:tractiff4}$.
+
+\end{proof}
+}
 \bigskip
@@
 \item whether we need $\tau$ in the assumption
+\item Do we need non-decreasing or strictly increasing? 
 \end{itemize}}

### 2023-03-10 GeneralizedTractability_230310.tex
Rearrange old versions and create a new one

\documentclass[11pt,a4paper]{article}
\usepackage{latexsym,amsfonts,amsmath,graphics,mathtools,amssymb,amsthm,booktabs}
\usepackage{epsfig}
\usepackage[notref,notcite]{showkeys}
%\usepackage[active]{srcltx}
\usepackage{enumitem}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}

\usepackage{algorithmic}

%\input{common-macros}
%\input{common-macros2}

\input{FJHDef.tex}

\setlength{\textheight}{24cm} \setlength{\textwidth}{16cm}
\setlength{\hoffset}{-1.3cm} \setlength{\voffset}{-1.8cm}

\newcommand{\supp}{\operatorname{supp}}

\newcommand{\tpmod}[1]{{\;(\operatorname{mod}\;#1)}}

\DeclareMathOperator*{\esssup}{ess\,sup}

%\DeclareMathOperator{\comp}{comp}
\DeclareMathOperator{\SOL}{SOL}
\DeclareMathOperator{\APP}{APP}

\allowdisplaybreaks

\newcommand{\fred}[1]{\begingroup\color{blue}#1\endgroup}
\newcommand{\peter}[1]{\begingroup\color{purple}#1\endgroup}
\newcommand{\kachi}[1]{\begingroup\color{ForestGreen}#1\endgroup}

\begin{document}

\newtheorem{theorem}{Theorem}
\theoremstyle{definition}
\newtheorem{definition}{Definition}

\title{Generalized Tractability}
\author{\fred{Fred J. Hickernell}, \peter{Peter Kritzer}, \kachi{Onyekachi Osisiogu}, and \\ Henryk Wo\'zniakwoski}
\date{\today}

\maketitle

\section{Introduction}

TODO: We need to check the relation of our work to that of Michael Gnewuch and Henryk. We do not need tensor product structure: do they need that assumption? The summation conditions on the eigenvalues might be a significant difference between our results and theirs.

\medskip

TODO: Check in how far our conditions coincide with existing conditions for less general tractability notions (polynomial tractability, etc.).

\medskip

Let $\cf_d$ and $\cg_d$ Hilbert spaces, and $\SOL_d : \cf_d \to \cg_d$ be a linear solution operator with adjoint $\SOL_d^*$ such that $\SOL_d^*\SOL_d : \cf_d \to \cf_d$ has eigenvalues and orthonormal eigenvectors  
\[
\lambda_{\max}^2 \ge \lambda_{1,d}^2 \ge \lambda_{2,d}^2 \ge \cdots, \qquad u_{1,d}, u_{2,d}, \ldots, 
\]
This means that the non-negative $\lambda_{i,d}$ are the singular values of the $\SOL_d$. The goal is to find an approximate solution, $\APP_d:\cb_d \times (0,\infty) \to \cg_d$ satisfying 
\[
\norm[\cg_d]{\SOL_d(f) - \APP_d(f,\varepsilon)} \le \varepsilon,
\]
where $\cb_d$ is the unit ball in $\cf_d$ and $\APP_d(f,\varepsilon)$ is allowed to depend on arbitrary linear functionals.  In this case, the optimal solution is 
\[
\APP_d(f,\varepsilon) = \sum_{i=1}^n \SOL(u_i) \ip[\cf_d]{f}{u_i},
\]
and the complexity of our linear problem is
\[
\comp(\varepsilon, d) = \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon\}.
\]

Certain kinds of common notions of tractability are 
\begin{equation*}
    \begin{array}{r@{\qquad}c@{\qquad}c}
    & \comp(\varepsilon, d)\\
    \toprule
    \text{strong polynomial algebraic  tractability} & \Theta(\varepsilon^{-p})\\
    \text{polynomial algebraic tractability} & \Theta(\varepsilon^{-p}d^{q})\\
    \text{strong polynomial exponential tractability} &  \Theta\bigl([\log(1 + \varepsilon^{-1})]^p\bigr)\\
    \text{polynomial exponential tractability} & \Theta\bigl([\log(1 + \varepsilon^{-1})]^p  d^{q}\bigr)
    \end{array}
\end{equation*}

\section{Main Results}

Let $T$ be a tractability function defined as follows,
\[
T :(0,\infty) \times \mathbb{N} \times [0,\infty) \times [0,\infty) \rightarrow [1,\infty),
\] 
which is non-decreasing in all variables.

Also, {we assume that, for any choice of $p\in[0,\infty)$, $q\in [0,\infty)$, and $\tau\in (1,\infty)$,
\[
[T(\varepsilon^{-1},d,p,q)]^\tau \le K_{p,q,\tau} T(\varepsilon^{-1},d,\tau p,\tau q),
\]
where $K_{p,q,\tau}$ is a term that may depend on $p$, $q$, and $\tau$, but is independent of $\varepsilon$ and $d$.

Furthermore, we assume that, for any choice of $d\in\naturals$ and $p,q\in [0,\infty)$, 
the quantity $T(0,d,p,q):=\liminf_{\varepsilon\to\infty}T(\varepsilon^{-1},d,p,q)$ exists.

A problem is $T$-tractable with parameters $p$ and $q$ iff there exists a positive constant $C_{p,q}$ such that
\begin{equation} \label{comp_def}
\comp(\varepsilon,d) \le C_{p,q}\, T(\varepsilon^{-1},d,p,q) \qquad \forall \varepsilon \in (0,\infty), \ \forall d \in \mathbb{N}.
\end{equation}
The  set of optimal parameters, $\mathcal{P}_{\text{opt}}$ is defined as
\begin{multline}
    \mathcal{P}_{\text{opt}} : = \{(p^*,q^*) : \eqref{comp_def} \text{ holds }\forall (p,q) \in [p^*,\infty) \times [q^*,\infty) \setminus (p^*,q^*) \\ 
    \eqref{comp_def} \text{ fails } \forall (p,q) \in [0,p^*] \times [0,q^*] \setminus (p^*,q^*) \}.
\end{multline}

\begin{theorem}\label{thm_main_strong_tract2} 
A problem is $T$-tractable with $q=0$ iff there exists $p>0$ and an integer $L(p) > 0$ such that
\begin{equation} \label{eq:strong_tractiff3}
     S_p:=\sup_{d \in \naturals} \sum_{i = L(p)}^\infty \frac{1}{T(\lambda_{i,d}^{-1},1,p,0)} < \infty.
\end{equation}
If \eqref{eq:strong_tractiff3} holds, then $\mathcal{P}_{\text{opt}}=(p^*,0)$, where
\[
 p^* := \inf\{p>0\ \mbox{such that \eqref{eq:strong_tractiff3} holds}\}.
\]
\end{theorem}
\begin{proof}
\textbf{Sufficient condition:}\\
Given that $T$ is increasing in its arguments, we have the following equivalent expression, 
    \begin{align*}
    \comp(\varepsilon, d) &= \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon\} \\
    &= \min \biggl\{n \in \natzero : \frac{1}{T(\lambda_{n+1,d}^{-1},1,p,0)}\le \frac{1}{T(\varepsilon^{-1},1,p,0) }\biggr\}.
\end{align*}
Also since the $\lambda_{i,d}$ are non-increasing, it follows that the $T(\lambda_{i,d}^{-1},1,p,0)$ are non-decreasing. In particular, for all $n\in \mathbb{N}$, we have

\begin{align*}
    \MoveEqLeft{\lambda_{n+1,d} \le \lambda_{n,d} \le \cdots \le \lambda_{1,d}} \\
    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},1,p,0)} \le \frac{1}{T(\lambda_{n, d}^{-1},1,p,0)} \le \cdots \le \frac{1}{T(\lambda_{1, d}^{-1},1,p,0)} \\
    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},1,p,0) }
    \le \frac 1n \sum_{i=1}^n  \frac{1}{T(\lambda_{i, d}^{-1},1,p,0) }
    \le \frac 1n \sum_{i=1}^\infty  \frac{1}{T(\lambda_{i, d}^{-1},1,p,0)}.
\end{align*}
Thus, we can conclude that 
\begin{align*}
    n \ge T(\varepsilon^{-1},1,p,0) \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},1,p,0)}
    & \implies 
\frac 1n \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},1,p,0) }\le  T(\varepsilon^{-1},1,p,0) \\
   & \implies   \frac{1}{T(\lambda_{n+1, d}^{-1},1,p,0)} \le \frac{1}{T(\varepsilon^{-1},1,p,0)}.
\end{align*}

This implies an upper bound on the complexity of
\begin{align*}
       \MoveEqLeft{\comp(\varepsilon,d)} \\
       &\le 1 + T(\varepsilon^{-1},1,p,0) \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},1,p,0)} \\
       & = 1 + T(\varepsilon^{-1},1, p,0) \left [ \sum_{i=1}^{L(p)-1} \frac{1}{T(\lambda_{i, d}^{-1},1,p,0)}
       + \underbrace{\sum_{i=L(p)}^\infty \frac{1}{T(\lambda_{i, d}^{-1},1,p,0)}}_{=:S_p <\infty\ \text{by \eqref{eq:strong_tractiff3}} }\right] \\
       & \le 1+ T(\varepsilon^{-1},1,p,0) \underbrace{\left[\frac{(L(p)-1)}{T(\lambda_{\max}^{-1},1,p,0)} + S_p\right]}_{=:C_2(p)}\\
       & = 1+ T(\varepsilon^{-1},1,p,0) C_2 (p)\\
       &\le C_{p,0} T(\varepsilon^{-1},1,p,0),
\end{align*}
for some suitably chosen $C_{p,0}>0$. This means that we have strong $T$-tractability, and verifies sufficiency of \eqref{eq:strong_tractiff3}. 
As for $\mathcal{P}_{\text{opt}}$, we immediately see from the above argument that $\mathcal{P}_{\text{opt}}=(p^*,0)$, where
\[
 p^* \le \inf\{p>0\ \mbox{such that \eqref{eq:strong_tractiff3} holds}\}.
\]

\bigskip
\noindent \textbf{Necessary condition:} \\
Suppose that we have strong 
$T$-tractability. That is, for some $p>0$ there exists a positive constant $C_{p,0}$ such that
\[
\comp(\varepsilon,d)\le C_{p,0}\, T(\varepsilon^{-1},1,p,0)
\]
for all $\varepsilon\in (0,\infty)$.

% This, in turn, means that 
% \begin{equation}\label{eq_strong_tract_p'3}
% \comp(\varepsilon,d)\le C_{p,0} T(\varepsilon^{-1},1,p',0)
% \end{equation}
% for all $p'>p$. 
% 
% \noindent This means for (possibly small) $\delta_p>0$, there exists a constant $K$ such that \eqref{eq_strong_tract_p'3} holds for $p'=p+\delta_p$.

Since the eigenvalues $\lambda_{j,d}$ are non-increasing, we have
\begin{equation}\label{eq:lambda_K_strong3}
\lambda_{\lfloor C_{p,0}\, T(\varepsilon^{-1},1,p,0)\rfloor +1,d}\le \varepsilon.
\end{equation}
Let
\[
j=j (\varepsilon):= \lfloor C_{p,0}\, T(\varepsilon^{-1},1,p,0)\rfloor +1.
\]
When we vary $\varepsilon\in (0,\infty)$, we have that $j\in \{j_d^*, j_d^*+1, j_d^*+2,\ldots\}$, where 
\[
  j_d^*=\lfloor  T(0,1,p,0)\rfloor +1,
\]
by the monotonicity of $T$.

Note furthermore that we always have
\[
j=j(\varepsilon)\le C_{p,0}\, T(\varepsilon^{-1},1,p,0)+1.
\]
Due to our assumptions, we know that 
$T(\cdot,1, p,0)$ is increasing in the first argument if 
we keep $p$ fixed.

Then, by \eqref{eq:lambda_K_strong3},
\[
j \le C_{p,0} T(\varepsilon^{-1},1,p,0)+1\le C_{p,0} T(\lambda_{j,d}^{-1},1,p,0)+1,
\]
and the latter chain of inequalities holds for all $j\ge j_d^*$.

This implies
\[ 
 T(\lambda_{j,d}^{-1},1, p,0) \ge \frac{j-1}{C_{p,0}}.
\]
This, in turn, implies, for any $\tau>1$, that 
\[ 
 (T(\lambda_{j,d}^{-1},1, p,0))^\tau \ge \frac{(j-1)^\tau}{C_{p,0}^\tau },
\]
which yields, due to our assumption on $T$, 
\[ 
 K_{p,0,\tau}\,T (\lambda_{j,d}^{-1},1,\tau p,0) \ge \frac{(j-1)^\tau}{C_{p,0}^\tau},
\]
for some $K_{p,0,\tau}>0$.
This gives
\[
\sum_{j=j_d^*}^\infty \frac{1}{T (\lambda_{j,d}^{-1},1, \tau p,0)} \le K_{p,0,\tau}\, C_{p,0}^\tau
\sum_{j=j_d^*}^\infty \frac{1}{(j-1)^\tau} \le
\peter{K_{p,0,\tau}\, C_{p,0}^\tau\, \zeta (\tau) }< \infty,
\]
\peter{where by $\zeta(\cdot)$ we denote the Riemann zeta function. Consequently, 
\[
\sup_{d\in\naturals} \sum_{j=j_d^*}^\infty \frac{1}{T (\lambda_{j,d}^{-1},1, \tau p,0)} \le K_{p,0,\tau}\, C_{p,0}^\tau\, \zeta (\tau) < \infty.
\]
}

Note, however, that, \peter{for any $d\in\naturals$,}
\[
 j_d^* = \lfloor C_{p,0}\, T(0,1,p,0)\rfloor +1 \le \lfloor C_{p,0}\, T(0,1,\tau p,0)\rfloor +1
\]
Hence, we can find $L(\tau p)$, which is independent of $\varepsilon$ and $d$, such that 
\[
 \peter{\sup_{d\in\naturals}} \sum_{j=L(\tau p)}^\infty \frac{1}{T(\lambda_{j,d}^{-1},1, \tau p,0)}<\infty.
\]
This yields \eqref{eq:strong_tractiff3} with $p$ replaced by $\tau p$, and so we see necessity of $\eqref{eq:strong_tractiff3}$.

Assume that $\mathcal{P}_{\text{opt}}=(p^*,0)$. We already know from the first part of the proof that 
\[
 p^* \le \inf\{p>0\ \mbox{such that \eqref{eq:strong_tractiff3} holds}\}.
\]
Suppose that we would have 
\[
 p^* < \inf\{p>0\ \mbox{such that \eqref{eq:strong_tractiff3} holds}\}.
\]
\peter{Then, however, there exists a $p^\dag$ such that
\[
p^* < p^\dag < \inf\{p>0\ \mbox{such that \eqref{eq:strong_tractiff3} holds}\},
\]
and that the problem is $T$-tractable with parameters $q=0$ and $p^\dag$. }
We can proceed as in the second part of the proof and show that 
\[
 \sup_{d\in\naturals} \sum_{j=L(\tau \peter{p^\dag})}^\infty \frac{1}{T(\lambda_{j,d}^{-1},1, \tau \peter{p^\dag},0)}<\infty.
\]
for any $\tau>1$, and a suitable $L(\tau \peter{p^\dag})$. By choosing $\tau$ sufficiently close to 1, we then would 
obtain 
\[
 \tau \peter{p^\dag} < \inf\{p>0\ \mbox{such that \eqref{eq:strong_tractiff3} holds}\},
\]
which is a contradiction. So, we must have 
\[
 p^* = \inf\{p>0\ \mbox{such that \eqref{eq:strong_tractiff3} holds}\}.
\]

This concludes the proof of the theorem.

\end{proof}
\bigskip

\begin{theorem}\label{thm_main_tract2} 
A problem is $T$-tractable iff there exist $p,q>0$, and $q_1>0$ and a constant $L(p,q_1) > 0$ such that
\begin{equation} \label{eq:tractiff4}
     S_{p,q,q_1}:=\sup_{d \in \naturals} 
     \sum_{i = \lceil L(p,q_1)\, T(0,d,p,q_1) \rceil}^\infty \frac{1}{T(\lambda^{-1}_{i,d},d,p,q)}< \infty.
\end{equation}
\end{theorem}

\peter{(PETER: Do we also want to include a statement on the optimal parameters $p^*,q^*$?)}

\begin{proof}
    \textbf{Sufficient Condition:}\\ Suppose that \eqref{eq:tractiff4} holds for some $p,q>0$. 
Because $T$ is increasing in its arguments, it follows that the complexity may be equivalently expressed as 
\begin{align*}
    \comp(\varepsilon, d) &= \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon\} \\
    &= \min \biggl\{n \in \natzero : \frac{1}{T(\lambda_{n+1, d}^{-1},d,p,q)} \le \frac{1}{T(\varepsilon^{-1},d,p,q)} \biggr\}.
\end{align*}

Since the $\lambda_{i,d}$ are non-increasing it follows that the $\phi(\lambda_{i, d}^{-1},p)$ are non-decreasing.  
In particular, for all $n \in \naturals$,
\begin{align*}
    \MoveEqLeft{\lambda_{n+1,d} \le \lambda_{n,d} \le \cdots \le \lambda_{1,d}} \\
    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d,p,q)} \le \frac{1}{T(\lambda_{n, d}^{-1},d,p,q))} \le \cdots \le \frac{1}{T(\lambda_{1, d}^{-1},d,p,q)} \\
    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d,p.q)} 
    \le \frac 1n \sum_{i=1}^n  \frac{1}{T(\lambda_{i, d}^{-1},d,p,q)} 
    \le \frac 1n \sum_{i=1}^\infty  \frac{1}{T(\lambda_{i, d}^{-1},d,p,q)}.
\end{align*}
Thus, we can conclude that 
\begin{align*}
    n \ge T(\varepsilon^{-1},d,p,q) \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d,p,q)}
    & \implies 
  \frac 1n \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d,p,q)} \le  \frac{1}{T(\varepsilon^{-1},d,p,q)} \\
   & \implies   \frac{1}{T(\lambda_{n+1, d}^{-1},d,p,q)} \le \frac{1}{T(\varepsilon^{-1},d,p,q)}.
\end{align*}
This implies an upper bound on the complexity of
\begin{align*}
       \MoveEqLeft{\comp(\varepsilon,d)} \\
       &\le 1 + T(\varepsilon^{-1},d,p,q) \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d,p,q)} \\       
       & = 1 + T(\varepsilon^{-1},d,p,q) \left [ \sum_{i=1}^{\lceil L(p,q_1)\, T(0,d,p,q_1)\rceil -1} \frac{1}{T(\lambda_{i, d}^{-1},d,p,q)}  
       + \sum_{i=\lceil L(p,q_1)\, T(0,d,p,q_1) \rceil}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d,p,q)} \right ] \\
       & \le 1+ T(\varepsilon^{-1},d,p,q)\left[ \frac{\lceil L(p,q_1)\, T(0,d,p,q_1)\rceil-1}{T(\lambda_{\max}^{-1},d,p,q)} + S_{p,q,q_1}\right]
        \qquad \text{by \eqref{eq:tractiff4}} \\
       & \le 1+ T(\varepsilon^{-1},d,p,q)\left[L(p,q_1)\, T(0,d,p,q_1) + S_{p,q,q_1}\right]\\ 
       & \le 1+L(p,q_1)\,T(\varepsilon^{-1},d,p,q) T(0,d,p,q_1) + S_{p,q,q_1}\, T(\varepsilon^{-1},d,p,q)\\
       & \le 1+L(p,q_1)\,T(\varepsilon^{-1},d,p,q) T(\varepsilon^{-1},d,p,q_1) + S_{p,q,q_1}\, T(\varepsilon^{-1},d,p,q)\\
       & \le 1+L(p,q_1)\,T(\varepsilon^{-1},d,2p,2\max\{q,q_1\})  + S_{p,q}\, T(\varepsilon^{-1},d,p,q)  \\
       & \le C_{2p,2\max\{q,q_1\}} \,T(\varepsilon^{-1},d,2p,2\max\{q,q_1\})
\end{align*}
for some suitably chosen $C_{2p,2\max\{q,q_1\}}>0$. It follows that we have $T$-tractability, which shows sufficiency of \eqref{eq:tractiff4}. \\

\textbf{Necessary condition:}\\
Suppose that we have 
$T$-tractability. That is, for some $p>0$ and $q>0$, there exists a positive constant $C_{p,q}$ such that 
\[
\comp(\varepsilon,d)\le C_{p,q}\, (T(\varepsilon^{-1},d,p,q)
\]
for all $\varepsilon\in (0,\infty)$ and all $d\in\naturals$.

We know that
\[
\lambda_{\comp(\varepsilon,d)+1,d}\le \varepsilon.
\]
Since the eigenvalues $\lambda_{j,d}$ are non-increasing, we have
\begin{equation}\label{eq:lambda_K4}
\lambda_{\lfloor C_{p,q}\, T(\varepsilon^{-1},d,p,q)\rfloor +1,d}\le \varepsilon.
\end{equation}
Let
\[
j=j (\varepsilon):= \lfloor C_{p,q}\, T(\varepsilon^{-1},d,p,q)\rfloor +1.
\]
If we vary $\varepsilon\in (0,\infty)$, we see that $j=j_d^*, j_d^*+1, j_d^*+2,\ldots$, where 
\[
  j_d^*=\lfloor C_{p,q}\, T(0,d,p,q)\rfloor +1
\]
Note that
\[
j\le C_{p,q}\, T(\varepsilon^{-1},d,p,q) +1.
\]
Due to our assumptions, we know that 
$T(\cdot,d,p,q)$ is increasing in the first argument if 
we keep $p$ and $q$ fixed.

Then, by \eqref{eq:lambda_K4},
\[
j \le C_{p,q}\, T(\varepsilon^{-1},d,p,q) +1 \le C_{p,q}\, T(\lambda_{j,d}^{-1},d,p,q) +1,
\]
and the latter chain of inequalities holds for all $j\ge j_d^*$.

This implies
\[ 
T(\lambda_{j,d}^{-1},d, p,q) \ge \frac{j-1}{C_{p,q}}.
\]
This, in turn, implies, for any $\tau>1$, that 
\[ 
 (T(\lambda_{j,d}^{-1},d,p,q))^\tau \ge \frac{(j-1)^\tau}{C_{p,q}^\tau},
\]
which yields
\[ 
 K_{p,q,\tau}\, T (\lambda_{j,d}^{-1},d,\tau p,\tau q) \ge (T(\lambda_{j,d}^{-1},d, p,q))^\tau 
 \ge \frac{(j-1)^\tau}{C_{p,q}^\tau}.
\]
This then implies
\[
\sum_{j=j_d^*}^\infty \frac{1}{T(\lambda_{j,d}^{-1},d, \tau p,\tau q)} 
\le K_{p,q,\tau}\, C_{p,q}^\tau \sum_{j=j_d^*}^\infty \frac{1}{(j-1)^\tau}
\peter{\le K_{p,q,\tau}\, C_{p,q}^\tau \, \zeta(\tau)}
<\infty.
\]
\peter{
Consequently,
\[
\sup_{d\in\naturals} \sum_{j=j_d^*}^\infty \frac{1}{T(\lambda_{j,d}^{-1},d, \tau p,\tau q)} \le K_{p,q,\tau}\, C_{p,q}^\tau \, \zeta(\tau) < \infty.
\]
}
Note now that, \peter{for any $d\in\naturals$,}
\[
 j_d^* = \lfloor C_{p,q}\, T(0,d,p,q)\rfloor +1 \le \lfloor C_{p,q}^\tau\, T(0,d,\tau p,\tau q)\rfloor +1.
\]
So, there exists $L(\tau p,\tau q)$ such that 
\[
\peter{\sup_{d\in\naturals}}\,\, \sum_{j=\lceil L(\tau p,\tau q) T(0,d,\tau p,\tau q)\rceil}^\infty \frac{1}{T(\lambda_{j,d}^{-1},d, \tau p,\tau q)}<\infty.
\]

This yields \eqref{eq:tractiff4} with $p$ replaced by $\tau p$ and $q$ and $q_1$ replaced by $\tau q$, and so we see the necessity of $\eqref{eq:tractiff4}$.

\end{proof}

\section{Examples}

\paragraph{Example 1: Strong polynomial tractability}

Let $T: (0,\infty) \times \naturals \times [0,\infty) \times [0,\infty)\Rightarrow [1,\infty)$ 
be defined by 
\[
 T(\varepsilon^{-1},d,p,q)= (\max\{\varepsilon^{-1},1\})^p .
\]
Then Theorem \ref{thm_main_strong_tract2} yields the iff-condition
\[
 \sup_{d\in\naturals} \sum_{i=L(p)}^\infty (\min\{\lambda_{i,d},1\})^p < \infty.
\]
This essentially recovers the result on strong polynomial tractability in \cite[Theorem 5.1]{NW08}

\paragraph{Example 2: Polynomial tractability}

Let $T: (0,\infty) \times \naturals \times [0,\infty) \times [0,\infty)\Rightarrow [1,\infty)$ 
be defined by 
\[
 T(\varepsilon^{-1},d,p,q)= (\max\{\varepsilon^{-1},1\})^p\, d^q.
\]
Then Theorem \ref{thm_main_tract2} yields the iff-condition
\[
 \sup_{d\in\naturals} \sum_{i=L(p,q_1) d^{q_1}}^\infty (\min\{\lambda_{i,d},1\})^p d^{-q} < \infty.
\]
This essentially recovers the result on polynomial tractability in \cite[Theorem 5.1]{NW08}

\peter{(PETER: Add further examples (e.g., EXP- polynomial tractability, etc.)}

\bigskip

\fred{We need to check the proof for 
\begin{itemize}
\item correctness
\item exponents
\item whether the additional assumptions are too restrictive and can be generalized
\item whether we need $\tau$ in the assumption
\item Do we need non-decreasing or strictly increasing? 
\end{itemize}}
\begin{definition}[Weak Tractability]
If $n(\varepsilon,d)$ denotes the minimal number of function values needed to approximate all functions. We say that the problem is \emph{weakly tractable} if
    \[\lim_{\varepsilon^{-1}+d\rightarrow \infty} \frac{\ln n(\varepsilon,d)}{\varepsilon^{-1}+d} = 0\]
\end{definition}
\begin{definition}[Quasi-polynomial Tractability]
    The problem is \emph{quasi-polynomially tractable}, if there exist two constants $C, t> 0$ such that 
    \[
    n(\varepsilon,d) \leq C\exp\{t(1+\ln(1/\varepsilon))(1+\ln(d))\}
    \] for all $\varepsilon \in (0,1)$ and $d\in\mathbb{N}$.
\end{definition}
\begin{thebibliography}{99}

\bibitem{NW08} E.~Novak,H.~Wo\'zniakowski. \textit{Tractability of Multivariate Problems, Volume I: Linear Information}. 
European Mathematical Society Publishing House, Zurich, 2008.
 ×
\end{thebibliography}

\end{document}

### 2023-03-10 Older_versions/GeneralizedTractability(old_version).tex
Rearrange old versions and create a new one

--- 2023-03-10 GeneralizedTractability_230108.tex
@@
-\documentclass[11pt,a4paper]{article}
-\usepackage{latexsym,amsfonts,amsmath,graphics,mathtools,amssymb,amsthm,booktabs}
-\usepackage{epsfig}
-%\usepackage[notref,notcite]{showkeys}
-%\usepackage[active]{srcltx}
-\usepackage{enumitem}
+\documentclass{article}
+\usepackage{amsmath,amssymb, amsthm, booktabs, mathtools}
+\usepackage[utf8]{inputenc}
 \usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
-
-\usepackage{algorithmic}
-
-%\input{common-macros}
-%\input{common-macros2}
-
+\usepackage[notref,notcite]{showkeys}
 \input{FJHDef.tex}
 
-\setlength{\textheight}{24cm} \setlength{\textwidth}{16cm}
-\setlength{\hoffset}{-1.3cm} \setlength{\voffset}{-1.8cm}
-
-\newcommand{\supp}{\operatorname{supp}}
-
-\newcommand{\tpmod}[1]{{\;(\operatorname{mod}\;#1)}}
-
-\DeclareMathOperator*{\esssup}{ess\,sup}
+\title{Generalized Tractability}
+\author{\fred{Fred J. Hickernell}, \peter{Peter Kritzer}, \kachi{Onyekachi Osisiogu}, and \\ Henryk Wo\'zniakwoski}
+\date{\today}
 
@@
 
+%\theoremstyle{theorem}
+\newtheorem{theorem}{Theorem}
+\theoremstyle{definition}
+\newtheorem{definition}{Definition}
+
 \allowdisplaybreaks
@@
 \newcommand{\peter}[1]{\begingroup\color{purple}Peter: #1\endgroup}
-\newcommand{\kachi}[1]{\begingroup\color{ForestGreen}#1\endgroup}
+\newcommand{\kachi}[1]{\begingroup\color{ForestGreen}Kachi: #1\endgroup}
 
 \begin{document}
-
-\newtheorem{theorem}{Theorem}
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}
-
-\title{Generalized Tractability}
-\author{\fred{Fred J. Hickernell}, \peter{Peter Kritzer}, \kachi{Onyekachi Osisiogu}, and \\ Henryk Wo\'zniakwoski}
-\date{\today}
 
@@
 \]
-where $\cb_d$ is the unit ball in $\cf_d$ and $\APP_d(f,\varepsilon)$ is allowed to depend on arbitrary linear functionals.  In this case, the optimal solution is 
+where $\cb_d$ is the unit ball in $\cf_d$ and $\APP_d(f,\varepsilon)$ is allowed to depend on arbitrary linear functionals.  In this case the optimal solution is 
 \[
@@
 \end{equation*}
-Let $\phi : (0,\infty) \times (0,\infty) \to (0,\infty)$ and $\psi : \naturals  \times (0,\infty) \to (0,\infty)$ be positive-valued functions that are strictly increasing in both arguments, e.g., 
+Let let $\phi : (0,\infty) \times (0,\infty) \to (0,\infty)$ and $\psi : \naturals  \times (0,\infty) \to (0,\infty)$ be positive-valued functions that are strictly increasing in both arguments, e.g.,
 \[
@@
 
-All the examples of tractability above are of the form $\comp(\varepsilon, d) = \Theta \bigl( \phi(\varepsilon^{-1},p) \psi(d,q)\bigr)$.  
-Note, we define the $\Theta$ notation as follows
+All the examples of tractability above are of the form $\comp(\varepsilon, d) = \Theta \bigl( \phi(\varepsilon^{-1},p) \psi(d,q)\bigr)$.  Note, we define the $\Theta$ notation as follows
 \begin{equation*}
@@
 \]
-then we call a problem $\phi$-$\psi$-tractable with exponents $p$ and $q$.  
-If there exists a function $\phi$ satisfying the conditions above and a positive number $p$ such that 
-\begin{equation}\label{eq:def_strong_tract}
+then we call a problem $\phi$-$\psi$-tractable with exponents $p$ and $q$.  If there exists a function there $\phi$ satisfying the conditions above and a positive number $p$
+\[
 \comp(\varepsilon, d)  = \Theta\bigl(\phi(\varepsilon^{-1},p) \bigr)
-\end{equation}
-then we call a problem strongly $\phi$-tractable with exponent $p$. The infimum $p^*$ of all exponents $p>0$ such that \eqref{eq:def_strong_tract} holds, 
-is called the exponent of strong $\phi$-tractability. 
+\]
+then we call a problem strongly $\phi$-tractable with exponent $p$.
 \end{definition}
 
-\section{Main Results}
-Suppose that, for any real $\tau_1, \tau_2>0$ and any $p,q>0$, it holds that
-\begin{align*}
- (\phi(\varepsilon^{-1},p))^{\tau_1} &\le K_{p,\tau_1} \phi (\varepsilon^{-1},\tau_1 p)\\
-  (\psi(d,q))^{\tau_2} &\le L_{q,\tau_2} \psi (d,\tau_2 q)\\
-\end{align*}
-for all $\varepsilon\in (0,1)$, where $K_{p,\tau_1}>0$ is a constant that may depend on $p$ and $\tau_1$, but is independent of $\varepsilon$, 
-and where $L_{q,\tau_2}>0$ is a constant that may depend on $q$ and $\tau_2$, but is independent of $d$.
-
-We first show the following result. 
-\begin{theorem}\label{thm_main_strong_tract} 
-A problem is strongly $\phi$-tractable iff there exists $p>0$ and an integer $C(p)\ge 0$ such that
-\begin{equation} \label{eq:strong_tractiff}
-     \sup_{d \in \naturals} \sum_{i = C(p)}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)} < \infty.
-\end{equation}
-If \eqref{eq:strong_tractiff} holds, then the exponent of strong $\phi$-tractability equals
-\[
- p^* := \inf\{p>0\ \mbox{such that \eqref{eq:tractiff} holds}\}.
-\]
-
-\end{theorem}
-
-\begin{proof}
-We first show the sufficiency of \eqref{eq:strong_tractiff}. Suppose that \eqref{eq:strong_tractiff} holds for some $p>0$.  
-Because $\phi$ is increasing in its arguments, it follows that the complexity may be equivalently expressed as 
-\begin{align*}
-    \comp(\varepsilon, d) &= \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon\} \\
-    &= \min \biggl\{n \in \natzero : \frac{1}{\phi(\lambda_{n+1, d}^{-1},p)} \le \frac{1}{\phi(\varepsilon^{-1},p)} \biggr\}.
-\end{align*}
-Since the $\lambda_{i,d}$ are non-increasing it follows that the $\phi(\lambda_{i, d}^{-1},p)$ are non-decreasing. 
-In particular, for all $n \in \naturals$,
-\begin{align*}
-    \MoveEqLeft{\lambda_{n+1,d} \le \lambda_{n,d} \le \cdots \le \lambda_{1,d}} \\
-    & \implies \frac{1}{\phi(\lambda_{n+1, d}^{-1},p)} \le \frac{1}{\phi(\lambda_{n, d}^{-1},p)} \le \cdots \le \frac{1}{\phi(\lambda_{1, d}^{-1},p)} \\
-    & \implies \frac{1}{\phi(\lambda_{n+1, d}^{-1},p)} 
-    \le \frac 1n \sum_{i=1}^n  \frac{1}{\phi(\lambda_{i, d}^{-1},p)} 
-    \le \frac 1n \sum_{i=1}^\infty  \frac{1}{\phi(\lambda_{i, d}^{-1},p)}.
-\end{align*}
-Thus, we can conclude that 
-\begin{align*}
-    n \ge \phi(\varepsilon^{-1},p) \sum_{i=1}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)}
-    & \implies 
-  \frac 1n \sum_{i=1}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)} \le  \frac{1}{\phi(\varepsilon^{-1},p')} \\
-   & \implies   \frac{1}{\phi(\lambda_{n+1, d}^{-1},p)} \le \frac{1}{\phi(\varepsilon^{-1},p)}.
-\end{align*}
-This implies an upper bound on the complexity of
-\begin{align*}
-       \MoveEqLeft{\comp(\varepsilon,d)} \\
-       &\le 1 + \phi(\varepsilon^{-1},p) \sum_{i=1}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)} \\
-       & = 1 + \phi(\varepsilon^{-1}, p) \left [ \sum_{i=1}^{C(p)-1} \frac{1}{\phi(\lambda_{i, d}^{-1},p)}  
-       + \underbrace{\sum_{i=C(p)}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)}}_{=:S_p <\infty\ \text{by \eqref{eq:tractiff}} }\right] \\
-       & \le 1+ \phi(\varepsilon^{-1},p) \underbrace{\left(\frac{C(p)-1}{\phi(\lambda_{\max}^{-1},p)} + S_p\right)}_{=:C_1(p)}\\
-       & = 1+ \phi(\varepsilon^{-1},p) C_1 (p),
-\end{align*}
-which means that we have strong $\phi$-tractability, and verifies sufficiency of \eqref{eq:strong_tractiff}.
-
-\bigskip
-
-For the exponent $p^*$ of $\phi$-tractability, we then obviously obtain 
-\[
- p^* \le \inf\{p>0\ \mbox{such that \eqref{eq:strong_tractiff} holds}\}.
-\]
-
-\bigskip
-
-Let us now show necessity of \eqref{eq:strong_tractiff}. Indeed, suppose that we have strong 
-$\phi$-tractability. I.e., 
-\[
-\comp(\varepsilon,d)=\Theta (\phi(\varepsilon^{-1},p))
-\]
-for some $p>0$. This, in turn, means that there is a positive constant $K$ such that
-\begin{equation}\label{eq_strong_tract_p'}
-\comp(\varepsilon,d)\le K \phi(\varepsilon^{-1},p')
-\end{equation}
-for all $p'>p$.
-
-Hence, for (possibly small) $\delta_p>0$, there exists a constant $K$ such that \eqref{eq_strong_tract_p'} holds for $p'=p+\delta_p$.
-
-We know that
-\[
-\lambda_{\comp(\varepsilon,d)+1,d}\le \varepsilon.
-\]
-Since the eigenvalues $\lambda_{j,d}$ are non-increasing, we have
-\begin{equation}\label{eq:lambda_K_strong}
-\lambda_{\lfloor K \phi(\varepsilon^{-1},p')\rfloor +1,d}\le \varepsilon.
-\end{equation}
-Let
-\[
-j=j (\varepsilon):= \lfloor K \phi(\varepsilon^{-1},p')\rfloor +1.
-\]
-If we vary $\varepsilon\in (0,1]$, we see that $j=j_d^*, j_d^*+1, j_d^*+2,\ldots$, where 
-\[
-  j_d^*=\lfloor K \phi(1,p')\rfloor +1
-\]
-Note that
-\[
-j\le K \phi(\varepsilon^{-1},p')+1.
-\]
-Due to our assumptions, we know that 
-$\phi(\cdot, p')$ is increasing in the first argument if 
-we keep $p'$ fixed. Let $\phi_{p'}^{-1} (\cdot)$ be the inverse function of $\phi (\cdot, p')$ with respect to the first argument. 
-ote that also $\phi_{p'}^{-1}$ is strictly increasing.
-
-Then, 
-\[
-j \le K \phi(\varepsilon^{-1},p')+1
-\]
-is equivalent to
-\[
-\frac{j-1}{K} \le \phi(\varepsilon^{-1},p').
-\]
-By the monotonicity of $\phi_{p'}^{-1}$, the latter inequality holds if and only if
-\[
-  \phi_{p'}^{-1} \left(\frac{j-1}{K} \right)
-  \le \varepsilon^{-1},
-\]
-or, equivalently,
-\[
- \varepsilon \le \frac{1}{\phi_{p'}^{-1} \left(\frac{j-1}{K} \right)}.
-\]
-By using \eqref{eq:lambda_K_strong}, we derive
-\[
- \lambda_{j,d}\le \frac{1}{\phi_{p'}^{-1} \left(\frac{j-1}{K} \right)}
-\]
-for all $j\ge j_d^*$, which is again equivalent to 
-\[
-\lambda_{j,d}^{-1}\ge \phi_{p'}^{-1} \left(\frac{j-1}{K} \right),
-\]
-which holds if and only if
-\[ 
- \phi (\lambda_{j,d}^{-1}, p') \ge \frac{j-1}{K}.
-\]
-This implies, for any $\tau>1$, that 
-\[ 
- (\phi (\lambda_{j,d}^{-1}, p'))^\tau \ge \frac{(j-1)^\tau}{K^\tau },
-\]
-which implies, due to our assumption on $\phi$, 
-\[ 
- K_{p',\tau}\,\phi (\lambda_{j,d}^{-1}, \tau p') \ge \frac{(j-1)^\tau}{K^\tau }.
-\]
-This yields
-\[
-\sum_{j=j_d^*}^\infty \frac{1}{\phi (\lambda_{j,d}^{-1}, \tau p')} \le K_{p',\tau}\, K^\tau \sum_{j=j_d^*}^\infty \frac{1}{(j-1)^\tau}<\infty.
-\]
-
-Note, however, that 
-\[
- j_d^* = \lfloor K \phi(1,p')\rfloor +1 \le \lfloor K \phi(1,\tau p')\rfloor +1
-\]
-Hence, we can find $C(\tau p')$ such that 
-\[
- \sum_{j=C(\tau p')}^\infty \frac{1}{\phi (\lambda_{j,d}^{-1}, \tau p')}<\infty.
-\]
-This yields \eqref{eq:strong_tractiff} with $p$ replaced by $\tau p'$, and so we see necessity of $\eqref{eq:strong_tractiff}$.
-
-\bigskip
-
-Assume that $p^*$ is the $\varepsilon$-exponent of strong $\phi$-tractability. We already know from the first part of the proof that 
-\[
- p^* \le \inf\{p>0\ \mbox{such that \eqref{eq:strong_tractiff} holds}\}.
-\]
-Suppose that we would have 
-\[
- p^* < \inf\{p>0\ \mbox{such that \eqref{eq:strong_tractiff} holds}\}.
-\]
-Then, however, we could proceed as in the second part of the proof and show that 
-\[
- \sum_{j=C(\tau p')}^\infty \frac{1}{\phi (\lambda_{j,d}^{-1}, \tau p')}<\infty.
-\]
-for any $\tau>1$, any $p'>p^*$, and a suitable $C(\tau p')$. By choosing $\tau$ sufficiently close to 1, and $p'$ sufficiently close to $p^*$, we then would 
-obtain 
-\[
- \tau p' < \inf\{p>0\ \mbox{such that \eqref{eq:strong_tractiff} holds}\},
-\]
-which is a contradiction. So, we must have 
-\[
- p^* = \inf\{p>0\ \mbox{such that \eqref{eq:strong_tractiff} holds}\}.
-\]
-
-This concludes the proof of the theorem. 
-\end{proof}
-
-Next we show a theorem characterizing $\phi$-$\psi$-tractability. 
-\begin{theorem}\label{thm_main_tract} 
-A problem is $\phi$-$\psi$-tractable iff there exist $p,q>0$ and an integer $C(p,q) \ge 0$ such that
+\section{Main Result}
+\begin{theorem}\label{thm_main} 
+A problem is $\phi$-$\psi$-tractable with exponents $p$ and $q$ iff there exists a  $C : (0,\infty)^2 \to \naturals$
 \begin{equation} \label{eq:tractiff}
-     \sup_{d \in \naturals} \frac{1}{\psi(d,q)} \sum_{i = C(p,q)}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p))} < \infty.
+    \sup_{d \in \naturals} \frac{1}{\psi(d,q)} \sum_{i = C(p,q)}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)} \le 1 \qquad \forall p',q' \in (p,\infty)\times (q,\infty).
 \end{equation}
 \end{theorem}
+\peter{I am wondering whether it would be useful to also include something like "exponents of tractability".
+I.e., to define minimal $p$ and $q$ such that $\phi-\psi$-tractability holds.
+I am thinking so because maybe the condition in Theorem 1 should then be modified to hold for all $p'\ge p$ and all $q'\ge q$, and not more generally for all $p,q>0$ as it is now.}
+
+\fred{We may be able to patch up this proof with a condition like $$(\phi(\varepsilon^{-1},p))^{\tau} \le K_{p,\tau} \phi (\varepsilon^{-1},\tau p)$$}
 \begin{proof}
-We first show the sufficiency of \eqref{eq:tractiff}. Suppose that \eqref{eq:tractiff} holds for some $p,q>0$. 
-Because $\phi$ is increasing in its arguments, it follows that the complexity may be equivalently expressed as 
+Fix $p \in (0,\infty)$.  Because $\phi$ is increasing in its arguments, it follows that the complexity may be equivalently expressed as 
 \begin{align*}
@@
 
-Since the $\lambda_{i,d}$ are non-increasing it follows that the $\phi(\lambda_{i, d}^{-1},p)$ are non-decreasing, and this holds for any $\tau>1$.  
-In particular, for all $n \in \naturals$,
+Since the $\lambda_{i,d}$ are non-increasing it follows that the $\phi(\lambda_{i, d}^{-1},p)$ are non-decreasing.  In particular, for all $n \in \naturals$,
 \begin{align*}
     \MoveEqLeft{\lambda_{n+1,d} \le \lambda_{n,d} \le \cdots \le \lambda_{1,d}} \\
-    & \implies \frac{1}{\phi(\lambda_{n+1, d}^{-1},p)} \le \frac{1}{\phi(\lambda_{n, d}^{-1},p))} \le \cdots \le \frac{1}{\phi(\lambda_{1, d}^{-1},p)} \\
+    & \implies \frac{1}{\phi(\lambda_{n+1, d}^{-1},p)} \le \frac{1}{\phi(\lambda_{n, d}^{-1},p)} \le \cdots \le \frac{1}{\phi(\lambda_{1, d}^{-1},p)} \\
     & \implies \frac{1}{\phi(\lambda_{n+1, d}^{-1},p)} 
@@
        &\le 1 + \phi(\varepsilon^{-1},p) \sum_{i=1}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)} \\
-       & = 1 + \phi(\varepsilon^{-1},p) \left [ \sum_{i=1}^{C(p,q)-1} \frac{1}{\phi(\lambda_{i, d}^{-1},p)}  
-       + \sum_{i=C(p,q)}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)} \right ] \\
-       & \le 1+ \phi(\varepsilon^{-1},p) \underbrace{\frac{C(p,q)-1}{\phi(\lambda_{\max}^{-1},p)}}_{=:C_1(p,q)}
+       & = 1 + \phi(\varepsilon^{-1},p) \left [ \sum_{i=1}^{C_3(p,q)-1} \frac{1}{\phi(\lambda_{i, d}^{-1},p)}  + \sum_{i=C_3(p,q)}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)} \right ] \\
+       & \le 1+  \phi(\varepsilon^{-1},p) \underbrace{\frac{C_3(p,q)-1}{\phi(\lambda_{\max}^{-1},p)}}_{C_1(p,q)}
        +  \phi(\varepsilon^{-1},p) \psi(d,q) 
         \qquad \text{by \eqref{eq:tractiff}} \\
-        & \le 1+\phi(\varepsilon^{-1},p) \bigl[C_1(p,q) + \psi(d,q) \bigr].
+        & \le 1+  \phi(\varepsilon^{-1},p) \bigl[C_1(p,q) + \psi(d,q) \bigr].
 \end{align*}
-It follows that we have $\phi$-$\psi$-tractability, which shows sufficiency of \eqref{eq:tractiff}.
 
-\bigskip
+This verifies the sufficient condition.
 
-%---------------------------------------------------------------------
-%---------------------------------------------------------------------
+\peter{PETER: I try to give a proof of the necessary condition (but there is still a gap):
 
-Let us now show necessity. Indeed, suppose that we have 
-$\phi$-$\psi$-tractability with parameters $p$ and $q$. I.e., 
+Let us assume that we have $\phi$-$\psi$-tractability. I.e., 
 \[
-\comp(\varepsilon,d)=\Theta (\phi(\varepsilon^{-1},p)\psi(d,q))
+\comp(\varepsilon,d)=\Theta (\phi(\varepsilon^{-1},p),\psi(d,q))
 \]
@@
 
-Hence, for (possibly small) $\delta_p>0$ and $\delta_q>0$, there exists a constant $K$ such that \eqref{eq_tract_p'q'} holds for $p'=p+\delta_p$ 
+Hence, for (possibly small) $\delta_p>0$ and $\delta_q>0$, there eists a constant $K$ such that \eqref{eq_tract_p'q'} holds for $p'=p+\delta_p$ 
 and $q'=q+\delta_q$.
@@
 \begin{equation}\label{eq:lambda_K}
-\lambda_{\lfloor K \phi(\varepsilon^{-1},p')\psi(d,q')\rfloor +1,d}\le \varepsilon.
+\lambda_{\lfloor K \phi(\varepsilon^{-1},p'),\psi(d,q')\rfloor +1,d}\le \varepsilon.
 \end{equation}
@@
 \[
-j=j (\varepsilon):= \lfloor K \phi(\varepsilon^{-1},p')\psi(d,q')\rfloor +1.
+j=j (\varepsilon):= \lfloor K \phi(\varepsilon^{-1},p'),\psi(d,q')\rfloor +1.
 \]
@@
 \[
-  j_d^*=\lfloor K \phi(1,p')\psi(d,q')\rfloor +1
+  j_d^*=\lfloor K \phi(1,p'),\psi(d,q')\rfloor +1
 \]
@@
 \[
-j\le K \phi(\varepsilon^{-1},p')\psi(d,q') +1.
+j\le K \phi(\varepsilon^{-1},p'),\psi(d,q') +1.
 \]
@@
 \[
-j \le K \phi(\varepsilon^{-1},p')\psi(d,q') +1
+j \le K \phi(\varepsilon^{-1},p'),\psi(d,q') +1
+\]
+is equivalent to
+\[
+\frac{j-1}{K \psi(d,q')} \le \phi(\varepsilon^{-1},p').
+\]
+By the monotonicity of $\phi_{p'}^{-1}$, the latter inequality holds if and only if
+\[
+  \phi_{p'}^{-1} \left(\frac{j-1}{K \psi(d,q')} \right)
+  \le \varepsilon^{-1},
+\]
+or, equivalently,
+\[
+ \varepsilon \le \frac{1}{\phi_{p'}^{-1} \left(\frac{j-1}{K \psi(d,q')} \right)}.
+\]
+By using \eqref{eq:lambda_K}, we derive
+\[
+ \lambda_{j,d}\le \frac{1}{\phi_{p'}^{-1} \left(\frac{j-1}{K \psi(d,q')} \right)}
+\]
+for all $j\ge j_d^*$, which is again equivalent to 
+\[
+\lambda_{j,d}^{-1}\ge \phi_{p'}^{-1} \left(\frac{j-1}{K \psi(d,q')} \right),
+\]
+which holds if and only if
+\[ 
+ \phi (\lambda_{j,d}^{-1}, p') \ge \frac{j-1}{K \psi(d,q')}.
+\]
+This implies that 
+\[
+\frac{1}{\psi(d,q')} \sum_{j=j_d^*}^\infty \frac{1}{\phi (\lambda_{j,d}^{-1}, p')} \le K \sum_{j=j_d^*}^\infty \frac{1}{j-1}.
+\]
+If the series on the right hand side of the latter inequality would converge (which it obviously does not), then we would be done, since we could argue that we start the summation late enough that the series is less than $1/K$.
+Then we could argue that this estimate holds for all $d$, and therefore also for the supremum over all $d$.
+Also the sum of the first $j_d^*$ should be no problem to handle, as this should be bounded by a constant times $\psi (d,q')$.
+What we need is a suitable exponent of $j-1$.
+}
+\end{proof}
+
+\bigskip
+
+\peter{
+MODIFIED APPROACH:
+
+\bigskip
+
+\fred{We need to check the proof for 
+\begin{itemize}
+\item correctness
+\item exponents
+\item whether the additional assumptions are too restrictive and can be generalized
+\item whether we need $\tau$ in the assumption
+\end{itemize}}
+
+Let us make the following additional assumptions. Suppose that, for any real $\tau_1, \tau_2>0$ and any $p,q>0$, it holds that
+\begin{align*}
+ (\phi(\varepsilon^{-1},p))^{\tau_1} &\le K_{p,\tau_1} \phi (\varepsilon^{-1},\tau_1 p)\\
+  (\psi(d,q))^{\tau_2} &\le L_{q,\tau_2} \psi (d,\tau_2 q)\\
+\end{align*}
+for all $\varepsilon\in (0,1)$, where $K_{p,\tau_1}>0$ is a constant that may depend on $p$ and $\tau_1$, but is independent of $\varepsilon$, and where $L_{q,\tau_2}>0$ is a constant that may depend on $q$ and $\tau_2$, but is independent of $d$.
+
+\begin{theorem}\label{thm_main_modified}
+
+A problem is $\phi$-$\psi$-tractable with parameters $p$ and $q$ iff there exists a  $C : (0,\infty)^2 \to \naturals$  such that
+\begin{equation} \label{eq:tractiff_modified}
+    \sup_{d \in \naturals} \frac{1}{(\psi(d,q'))^\tau} \sum_{i = C(p',q')}^\infty \frac{1}{(\phi(\lambda_{i, d}^{-1},p'))^\tau} \le 1 \qquad \forall p',q' \in (p,\infty)\times (q,\infty),\ \forall \tau>1.
+\end{equation}
+\fred{And the left hand side is infinite if both $p' < p$ and $q' < q$?  Or just one?}
+\end{theorem}
+\begin{proof}
+We first show sufficiency of \eqref{eq:tractiff_modified}.
+Suppose that \eqref{eq:tractiff_modified} holds for some $p,q>0$.
+Fix $p'\in (p,\infty)$ and $q'\in (q,\infty)$.
+Because $\phi$ is increasing in its arguments, it follows that the complexity may be equivalently expressed as
+\begin{align*}
+    \comp(\varepsilon, d) &= \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon\} \\
+    &= \min \biggl\{n \in \natzero : \frac{1}{(\phi(\lambda_{n+1, d}^{-1},p'))^\tau} \le \frac{1}{(\phi(\varepsilon^{-1},p'))^\tau} \biggr\}.
+\end{align*}
+
+Since the $\lambda_{i,d}$ are non-increasing it follows that the $(\phi(\lambda_{i, d}^{-1},p))^\tau$ are non-decreasing, and this holds for any $\tau>1$.  In particular, for all $n \in \naturals$,
+\begin{align*}
+    \MoveEqLeft{\lambda_{n+1,d} \le \lambda_{n,d} \le \cdots \le \lambda_{1,d}} \\
+    & \implies \frac{1}{(\phi(\lambda_{n+1, d}^{-1},p'))^\tau} \le \frac{1}{(\phi(\lambda_{n, d}^{-1},p'))^\tau} \le \cdots \le \frac{1}{(\phi(\lambda_{1, d}^{-1},p'))^\tau} \\
+    & \implies \frac{1}{(\phi(\lambda_{n+1, d}^{-1},p'))^\tau} 
+    \le \frac 1n \sum_{i=1}^n  \frac{1}{(\phi(\lambda_{i, d}^{-1},p'))^\tau} 
+    \le \frac 1n \sum_{i=1}^\infty  \frac{1}{(\phi(\lambda_{i, d}^{-1},p'))^\tau}.
+\end{align*}
+Thus, we can conclude that 
+\begin{align*}
+    n \ge (\phi(\varepsilon^{-1},p'))^\tau \sum_{i=1}^\infty \frac{1}{(\phi(\lambda_{i, d}^{-1},p'))^\tau}
+    & \implies 
+  \frac 1n \sum_{i=1}^\infty \frac{1}{(\phi(\lambda_{i, d}^{-1},p'))^\tau} \le  \frac{1}{\phi((\varepsilon^{-1},p'))^\tau} \\
+   & \implies   \frac{1}{(\phi(\lambda_{n+1, d}^{-1},p'))^\tau} \le \frac{1}{(\phi(\varepsilon^{-1},p'))^\tau}.
+\end{align*}
+This implies an upper bound on the complexity of
+\begin{align*}
+       \MoveEqLeft{\comp(\varepsilon,d)} \\
+       &\le 1 + (\phi(\varepsilon^{-1},p'))^\tau \sum_{i=1}^\infty \frac{1}{(\phi(\lambda_{i, d}^{-1},p'))^\tau} \\
+       &\le 1 +K_{p',\tau} (\phi(\varepsilon^{-1},\tau p')) \sum_{i=1}^\infty \frac{1}{(\phi(\lambda_{i, d}^{-1},p'))^\tau} \\
+       & = 1 + K_{p',\tau}\phi(\varepsilon^{-1},\tau p') \left [ \sum_{i=1}^{C_3(p',q')-1} \frac{1}{(\phi(\lambda_{i, d}^{-1},p'))^\tau}  + \sum_{i=C_3(p',q')}^\infty \frac{1}{(\phi(\lambda_{i, d}^{-1},p'))^\tau} \right ] \\
+       & \le 1+ K_{p',\tau} (\phi(\varepsilon^{-1},\tau p')) \underbrace{\frac{C_3(p',q')-1}{(\phi(\lambda_{\max}^{-1},p'))^\tau}}_{C_1(p',q')}
+       +  K_{p',\tau}\phi(\varepsilon^{-1},\tau p') (\psi(d,q'))^\tau 
+        \qquad \text{by \eqref{eq:tractiff}} \\
+        & \le 1+ K_{p',\tau} \phi(\varepsilon^{-1},\tau p') \bigl[C_1(p',q') + L_{q',\tau}\psi(d,\tau q') \bigr].
+\end{align*}
+As $\tau$ can be arbitrarily close to 1, and $p'$ and $q'$ can be arbitrarily close to $p$ and $q$, respectively, it follows that we have $\phi$-$\psi$-tractability with parameters $p$ and $q$, which shows sufficiency of \eqref{eq:tractiff_modified}.
+
+Let us now show necessity. Indeed, suppose that we have 
+$\phi$-$\psi$-tractability with parameters $p$ and $q$. I.e., 
+\[
+\comp(\varepsilon,d)=\Theta (\phi(\varepsilon^{-1},p),\psi(d,q))
+\]
+for some $p,q>0$. This, in turn, means that there is a positive constant $K$ such that
+\begin{equation}\label{eq_tract_p'q'}
+\comp(\varepsilon,d)\le K \phi(\varepsilon^{-1},p'),\psi(d,q')
+\end{equation}
+for all $p'>p$ and $q'>q$.
+
+Hence, for (possibly small) $\delta_p>0$ and $\delta_q>0$, there eists a constant $K$ such that \eqref{eq_tract_p'q'} holds for $p'=p+\delta_p$ 
+and $q'=q+\delta_q$.
+
+We know that
+\[
+\lambda_{\comp(\varepsilon,d)+1,d}\le \varepsilon.
+\]
+Since the eigenvalues $\lambda_{j,d}$ are non-increasing, we have
+\begin{equation}\label{eq:lambda_K}
+\lambda_{\lfloor K \phi(\varepsilon^{-1},p'),\psi(d,q')\rfloor +1,d}\le \varepsilon.
+\end{equation}
+Let
+\[
+j=j (\varepsilon):= \lfloor K \phi(\varepsilon^{-1},p'),\psi(d,q')\rfloor +1.
+\]
+If we vary $\varepsilon\in (0,1]$, we see that $j=j_d^*, j_d^*+1, j_d^*+2,\ldots$, where 
+\[
+  j_d^*=\lfloor K \phi(1,p'),\psi(d,q')\rfloor +1
+\]
+Note that
+\[
+j\le K \phi(\varepsilon^{-1},p'),\psi(d,q') +1.
+\]
+Due to our assumptions, we know that 
+$\phi(\cdot, p')$ is increasing in the first argument if 
+we keep $p'$ fixed. Let $\phi_{p'}^{-1} (\cdot)$ be the inverse function of $\phi (\cdot, p')$ with respect to the first argument. Note that also $\phi_{p'}^{-1}$ is strictly increasing.
+
+Then, 
+\[
+j \le K \phi(\varepsilon^{-1},p'),\psi(d,q') +1
 \]
@@
 \[
- K_{p',\tau}\, \phi (\lambda_{j,d}^{-1}, \tau p') \ge (\phi (\lambda_{j,d}^{-1}, p'))^\tau 
- \ge \frac{(j-1)^\tau}{K^\tau (\psi(d,q'))^\tau}\ge \frac{(j-1)^\tau}{K^\tau\, L_{q',\tau}\, \psi(d,\tau q')}.
+\frac{1}{(\psi(d,q'))^\tau} \sum_{j=j_d^*}^\infty \frac{1}{(\phi (\lambda_{j,d}^{-1}, p'))^\tau} \le K^\tau \sum_{j=j_d^*}^\infty \frac{1}{(j-1)^\tau}.  \text{\fred{here we need the $\tau$}}
 \]
-This then implies
-\[
-\frac{1}{L_{q',\tau}\, \psi(d,\tau q')} \sum_{j=j_d^*}^\infty \frac{1}{\phi (\lambda_{j,d}^{-1}, \tau p')} 
-\le K_{p',\tau}\, K^\tau \sum_{j=j_d^*}^\infty \frac{1}{(j-1)^\tau}<\infty.
-\]
-Note now that
-\[
- j_d^* = \lfloor K \phi(1,p')\psi (1,q')\rfloor +1 \le \lfloor K\phi(1,\tau p')\psi (1,\tau q')\rfloor +1.
-\]
-So, there exists $C(\tau p',\tau q')$ such that 
-\[
- \sum_{j=C(\tau p',\tau q')}^\infty \frac{1}{\phi (\lambda_{j,d}^{-1}, \tau p')}<\infty.
-\]
-This yields \eqref{eq:tractiff} with $p$ replaced by $\tau p'$ and $q$ replaced by $\tau q'$, and so we see necessity of $\eqref{eq:tractiff}$.
-
+Now we could again argue that the first summation index on the right-hand side can be chosen small enough such that the series is not bigger than $1/(K^\tau)$.
+Also the sum of the first $j_d^*$ should be no problem to handle, as this should be bounded by a constant times $\psi (d,q')$.
+Note that now the series on the right-hand side certainly converges as $\tau>1$.
 \end{proof}
-
-\bigskip
-
-\bigskip
-
-\fred{We need to check the proof for 
-\begin{itemize}
-\item correctness
-\item exponents
-\item whether the additional assumptions are too restrictive and can be generalized
-\item whether we need $\tau$ in the assumption
-\end{itemize}}
+}
 

### 2023-03-10 Older_versions/GeneralizedTractabilityVerB.tex
Rearrange old versions and create a new one

--- 2023-03-10 Older_versions/GeneralizedTractability(old_version).tex
@@
 \newcommand{\peter}[1]{\begingroup\color{purple}Peter: #1\endgroup}
-\newcommand{\kachi}[1]{\begingroup\color{ForestGreen}Kachi: #1\endgroup}
+\newcommand{\kachi}[1]{\begingroup\color{ForestGreen}#1\endgroup}
 
@@
 \]
-where $\cb_d$ is the unit ball in $\cf_d$ and $\APP_d(f,\varepsilon)$ is allowed to depend on arbitrary linear functionals.  In this case the optimal solution is 
+where $\cb_d$ is the unit ball in $\cf_d$ and $\APP_d(f,\varepsilon)$ is allowed to depend on arbitrary linear functionals.  In this case, the optimal solution is 
 \[
@@
 \end{equation*}
-Let let $\phi : (0,\infty) \times (0,\infty) \to (0,\infty)$ and $\psi : \naturals  \times (0,\infty) \to (0,\infty)$ be positive-valued functions that are strictly increasing in both arguments, e.g.,
+Let $\phi : (0,\infty) \times (0,\infty) \to (0,\infty)$ and $\psi : \naturals  \times (0,\infty) \to (0,\infty)$ be positive-valued functions that are strictly increasing in both arguments, e.g., 
 \[
@@
 \end{multline*}
-\peter{(PETER: what would happen if $p'<p$ and $q'\ge q$ or the other way around?)}
 
@@
 \section{Main Result}
-\begin{theorem}\label{thm_main} 
-A problem is $\phi$-$\psi$-tractable with exponents $p$ and $q$ iff there exists a  $C : (0,\infty)^2 \to \naturals$
-\begin{equation} \label{eq:tractiff}
-    \sup_{d \in \naturals} \frac{1}{\psi(d,q)} \sum_{i = C(p,q)}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)} \le 1 \qquad \forall p',q' \in (p,\infty)\times (q,\infty).
-\end{equation}
-\end{theorem}
-\peter{I am wondering whether it would be useful to also include something like "exponents of tractability".
-I.e., to define minimal $p$ and $q$ such that $\phi-\psi$-tractability holds.
-I am thinking so because maybe the condition in Theorem 1 should then be modified to hold for all $p'\ge p$ and all $q'\ge q$, and not more generally for all $p,q>0$ as it is now.}
-
-\fred{We may be able to patch up this proof with a condition like $$(\phi(\varepsilon^{-1},p))^{\tau} \le K_{p,\tau} \phi (\varepsilon^{-1},\tau p)$$}
-\begin{proof}
-Fix $p \in (0,\infty)$.  Because $\phi$ is increasing in its arguments, it follows that the complexity may be equivalently expressed as 
-\begin{align*}
-    \comp(\varepsilon, d) &= \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon\} \\
-    &= \min \biggl\{n \in \natzero : \frac{1}{\phi(\lambda_{n+1, d}^{-1},p)} \le \frac{1}{\phi(\varepsilon^{-1},p)} \biggr\}.
-\end{align*}
-
-Since the $\lambda_{i,d}$ are non-increasing it follows that the $\phi(\lambda_{i, d}^{-1},p)$ are non-decreasing.  In particular, for all $n \in \naturals$,
-\begin{align*}
-    \MoveEqLeft{\lambda_{n+1,d} \le \lambda_{n,d} \le \cdots \le \lambda_{1,d}} \\
-    & \implies \frac{1}{\phi(\lambda_{n+1, d}^{-1},p)} \le \frac{1}{\phi(\lambda_{n, d}^{-1},p)} \le \cdots \le \frac{1}{\phi(\lambda_{1, d}^{-1},p)} \\
-    & \implies \frac{1}{\phi(\lambda_{n+1, d}^{-1},p)} 
-    \le \frac 1n \sum_{i=1}^n  \frac{1}{\phi(\lambda_{i, d}^{-1},p)} 
-    \le \frac 1n \sum_{i=1}^\infty  \frac{1}{\phi(\lambda_{i, d}^{-1},p)}.
-\end{align*}
-Thus, we can conclude that 
-\begin{align*}
-    n \ge \phi(\varepsilon^{-1},p) \sum_{i=1}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)}
-    & \implies 
-  \frac 1n \sum_{i=1}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)} \le  \frac{1}{\phi(\varepsilon^{-1},p)} \\
-   & \implies   \frac{1}{\phi(\lambda_{n+1, d}^{-1},p)} \le \frac{1}{\phi(\varepsilon^{-1},p)}.
-\end{align*}
-This implies an upper bound on the complexity of
-\begin{align*}
-       \MoveEqLeft{\comp(\varepsilon,d)} \\
-       &\le 1 + \phi(\varepsilon^{-1},p) \sum_{i=1}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)} \\
-       & = 1 + \phi(\varepsilon^{-1},p) \left [ \sum_{i=1}^{C_3(p,q)-1} \frac{1}{\phi(\lambda_{i, d}^{-1},p)}  + \sum_{i=C_3(p,q)}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)} \right ] \\
-       & \le 1+  \phi(\varepsilon^{-1},p) \underbrace{\frac{C_3(p,q)-1}{\phi(\lambda_{\max}^{-1},p)}}_{C_1(p,q)}
-       +  \phi(\varepsilon^{-1},p) \psi(d,q) 
-        \qquad \text{by \eqref{eq:tractiff}} \\
-        & \le 1+  \phi(\varepsilon^{-1},p) \bigl[C_1(p,q) + \psi(d,q) \bigr].
-\end{align*}
-
-This verifies the sufficient condition.
-
-\peter{PETER: I try to give a proof of the necessary condition (but there is still a gap):
-
-Let us assume that we have $\phi$-$\psi$-tractability. I.e., 
-\[
-\comp(\varepsilon,d)=\Theta (\phi(\varepsilon^{-1},p),\psi(d,q))
-\]
-for some $p,q>0$. This, in turn, means that there is a positive constant $K$ such that
-\begin{equation}\label{eq_tract_p'q'}
-\comp(\varepsilon,d)\le K \phi(\varepsilon^{-1},p')\psi(d,q')
-\end{equation}
-for all $p'>p$ and $q'>q$.
-
-Hence, for (possibly small) $\delta_p>0$ and $\delta_q>0$, there eists a constant $K$ such that \eqref{eq_tract_p'q'} holds for $p'=p+\delta_p$ 
-and $q'=q+\delta_q$.
-
-We know that
-\[
-\lambda_{\comp(\varepsilon,d)+1,d}\le \varepsilon.
-\]
-Since the eigenvalues $\lambda_{j,d}$ are non-increasing, we have
-\begin{equation}\label{eq:lambda_K}
-\lambda_{\lfloor K \phi(\varepsilon^{-1},p'),\psi(d,q')\rfloor +1,d}\le \varepsilon.
-\end{equation}
-Let
-\[
-j=j (\varepsilon):= \lfloor K \phi(\varepsilon^{-1},p'),\psi(d,q')\rfloor +1.
-\]
-If we vary $\varepsilon\in (0,1]$, we see that $j=j_d^*, j_d^*+1, j_d^*+2,\ldots$, where 
-\[
-  j_d^*=\lfloor K \phi(1,p'),\psi(d,q')\rfloor +1
-\]
-Note that
-\[
-j\le K \phi(\varepsilon^{-1},p'),\psi(d,q') +1.
-\]
-Due to our assumptions, we know that 
-$\phi(\cdot, p')$ is increasing in the first argument if 
-we keep $p'$ fixed. Let $\phi_{p'}^{-1} (\cdot)$ be the inverse function of $\phi (\cdot, p')$ with respect to the first argument. Note that also $\phi_{p'}^{-1}$ is strictly increasing.
-
-Then, 
-\[
-j \le K \phi(\varepsilon^{-1},p'),\psi(d,q') +1
-\]
-is equivalent to
-\[
-\frac{j-1}{K \psi(d,q')} \le \phi(\varepsilon^{-1},p').
-\]
-By the monotonicity of $\phi_{p'}^{-1}$, the latter inequality holds if and only if
-\[
-  \phi_{p'}^{-1} \left(\frac{j-1}{K \psi(d,q')} \right)
-  \le \varepsilon^{-1},
-\]
-or, equivalently,
-\[
- \varepsilon \le \frac{1}{\phi_{p'}^{-1} \left(\frac{j-1}{K \psi(d,q')} \right)}.
-\]
-By using \eqref{eq:lambda_K}, we derive
-\[
- \lambda_{j,d}\le \frac{1}{\phi_{p'}^{-1} \left(\frac{j-1}{K \psi(d,q')} \right)}
-\]
-for all $j\ge j_d^*$, which is again equivalent to 
-\[
-\lambda_{j,d}^{-1}\ge \phi_{p'}^{-1} \left(\frac{j-1}{K \psi(d,q')} \right),
-\]
-which holds if and only if
-\[ 
- \phi (\lambda_{j,d}^{-1}, p') \ge \frac{j-1}{K \psi(d,q')}.
-\]
-This implies that 
-\[
-\frac{1}{\psi(d,q')} \sum_{j=j_d^*}^\infty \frac{1}{\phi (\lambda_{j,d}^{-1}, p')} \le K \sum_{j=j_d^*}^\infty \frac{1}{j-1}.
-\]
-If the series on the right hand side of the latter inequality would converge (which it obviously does not), then we would be done, since we could argue that we start the summation late enough that the series is less than $1/K$.
-Then we could argue that this estimate holds for all $d$, and therefore also for the supremum over all $d$.
-Also the sum of the first $j_d^*$ should be no problem to handle, as this should be bounded by a constant times $\psi (d,q')$.
-What we need is a suitable exponent of $j-1$.
-}
-\end{proof}
-
-\bigskip
-
-\peter{
-MODIFIED APPROACH:
-
-\bigskip
-
-\fred{We need to check the proof for 
-\begin{itemize}
-\item correctness
-\item exponents
-\item whether the additional assumptions are too restrictive and can be generalized
-\item whether we need $\tau$ in the assumption
-\end{itemize}}
-
-Let us make the following additional assumptions. Suppose that, for any real $\tau_1, \tau_2>0$ and any $p,q>0$, it holds that
+Suppose that, for any real $\tau_1, \tau_2>0$ and any $p,q>0$, it holds that
 \begin{align*}
@@
 for all $\varepsilon\in (0,1)$, where $K_{p,\tau_1}>0$ is a constant that may depend on $p$ and $\tau_1$, but is independent of $\varepsilon$, and where $L_{q,\tau_2}>0$ is a constant that may depend on $q$ and $\tau_2$, but is independent of $d$.
-
-\begin{theorem}\label{thm_main_modified}
-
-A problem is $\phi$-$\psi$-tractable with parameters $p$ and $q$ iff there exists a  $C : (0,\infty)^2 \to \naturals$  such that
-\begin{equation} \label{eq:tractiff_modified}
+\begin{theorem}\label{thm_main} 
+A problem is $\phi$-$\psi$-tractable with exponents $p$ and $q$ iff there exists a  $C : (0,\infty)^2 \to \naturals$
+\begin{equation} \label{eq:tractiff}
      \sup_{d \in \naturals} \frac{1}{(\psi(d,q'))^\tau} \sum_{i = C(p',q')}^\infty \frac{1}{(\phi(\lambda_{i, d}^{-1},p'))^\tau} \le 1 \qquad \forall p',q' \in (p,\infty)\times (q,\infty),\ \forall \tau>1.
 \end{equation}
-\fred{And the left hand side is infinite if both $p' < p$ and $q' < q$?  Or just one?}
 \end{theorem}
+
 \begin{proof}
-We first show sufficiency of \eqref{eq:tractiff_modified}.
-Suppose that \eqref{eq:tractiff_modified} holds for some $p,q>0$.
+We first show the sufficiency of \eqref{eq:tractiff}.
+Suppose that \eqref{eq:tractiff} holds for some $p,q>0$.
 Fix $p'\in (p,\infty)$ and $q'\in (q,\infty)$.
@@
 \end{align*}
-As $\tau$ can be arbitrarily close to 1, and $p'$ and $q'$ can be arbitrarily close to $p$ and $q$, respectively, it follows that we have $\phi$-$\psi$-tractability with parameters $p$ and $q$, which shows sufficiency of \eqref{eq:tractiff_modified}.
+As $\tau$ can be arbitrarily close to 1, and $p'$ and $q'$ can be arbitrarily close to $p$ and $q$, respectively, it follows that we have $\phi$-$\psi$-tractability with parameters $p$ and $q$, which shows sufficiency of \eqref{eq:tractiff}.
+
+This verifies the sufficient condition.
+
+\bigskip
 
@@
 \[
-\comp(\varepsilon,d)=\Theta (\phi(\varepsilon^{-1},p),\psi(d,q))
+\comp(\varepsilon,d)=\Theta (\phi(\varepsilon^{-1},p)\psi(d,q))
 \]
@@
 \begin{equation}\label{eq_tract_p'q'}
-\comp(\varepsilon,d)\le K \phi(\varepsilon^{-1},p'),\psi(d,q')
+\comp(\varepsilon,d)\le K \phi(\varepsilon^{-1},p')\psi(d,q')
 \end{equation}
@@
 
-Hence, for (possibly small) $\delta_p>0$ and $\delta_q>0$, there eists a constant $K$ such that \eqref{eq_tract_p'q'} holds for $p'=p+\delta_p$ 
+Hence, for (possibly small) $\delta_p>0$ and $\delta_q>0$, there exists a constant $K$ such that \eqref{eq_tract_p'q'} holds for $p'=p+\delta_p$ 
 and $q'=q+\delta_q$.
@@
 \begin{equation}\label{eq:lambda_K}
-\lambda_{\lfloor K \phi(\varepsilon^{-1},p'),\psi(d,q')\rfloor +1,d}\le \varepsilon.
+\lambda_{\lfloor K \phi(\varepsilon^{-1},p')\psi(d,q')\rfloor +1,d}\le \varepsilon.
 \end{equation}
@@
 \[
-j=j (\varepsilon):= \lfloor K \phi(\varepsilon^{-1},p'),\psi(d,q')\rfloor +1.
+j=j (\varepsilon):= \lfloor K \phi(\varepsilon^{-1},p')\psi(d,q')\rfloor +1.
 \]
@@
 \[
-  j_d^*=\lfloor K \phi(1,p'),\psi(d,q')\rfloor +1
+  j_d^*=\lfloor K \phi(1,p')\psi(d,q')\rfloor +1
 \]
@@
 \[
-j\le K \phi(\varepsilon^{-1},p'),\psi(d,q') +1.
+j\le K \phi(\varepsilon^{-1},p')\psi(d,q') +1.
 \]
@@
 \[
-j \le K \phi(\varepsilon^{-1},p'),\psi(d,q') +1
+j \le K \phi(\varepsilon^{-1},p')\psi(d,q') +1
 \]
@@
 \[
-\frac{1}{(\psi(d,q'))^\tau} \sum_{j=j_d^*}^\infty \frac{1}{(\phi (\lambda_{j,d}^{-1}, p'))^\tau} \le K^\tau \sum_{j=j_d^*}^\infty \frac{1}{(j-1)^\tau}.  \text{\fred{here we need the $\tau$}}
+\frac{1}{(\psi(d,q'))^\tau} \sum_{j=j_d^*}^\infty \frac{1}{(\phi (\lambda_{j,d}^{-1}, p'))^\tau} \le K^\tau \sum_{j=j_d^*}^\infty \frac{1}{(j-1)^\tau}.
 \]
-Now we could again argue that the first summation index on the right-hand side can be chosen small enough such that the series is not bigger than $1/(K^\tau)$.
-Also the sum of the first $j_d^*$ should be no problem to handle, as this should be bounded by a constant times $\psi (d,q')$.
-Note that now the series on the right-hand side certainly converges as $\tau>1$.
+
 \end{proof}
-}
+
+\bigskip
+
+\bigskip
+
+\fred{We need to check the proof for 
+\begin{itemize}
+\item correctness
+\item exponents
+\item whether the additional assumptions are too restrictive and can be generalized
+\item whether we need $\tau$ in the assumption
+\end{itemize}}
 

### 2023-03-10 GeneralizedTractability_230310.tex
Fred M2 2023 Mac Updates

@@
 \end{equation*}
+\fred{We need to fix these so that the tractability function does not vanish as $\varepsilon \to \infty$.}
 
@@
 
+\subsection{Notation and fundamental definitions}
 Let $T$ be a tractability function defined as follows,
 \[
-T :(0,\infty) \times \mathbb{N} \times [0,\infty) \times [0,\infty) \rightarrow [1,\infty),
+T :(0,\infty) \times \mathbb{N} \times [0,\infty)^s \rightarrow [1,\infty),
 \]
-which is non-decreasing in all variables.
+A problem is $T$-tractable with parameter $\vp$ iff there exists a positive constant $C_{\vp}$ such that
+\begin{equation} \label{comp_def}
+	\comp(\varepsilon,d) \le C_{\vp}\, T(\varepsilon^{-1},d,\vp) \qquad \forall \varepsilon \in (0,\infty), \ \forall d \in \mathbb{N}.
+\end{equation}
 
-Also, {we assume that, for any choice of $p\in[0,\infty)$, $q\in [0,\infty)$, and $\tau\in (1,\infty)$,
-\[
-[T(\varepsilon^{-1},d,p,q)]^\tau \le K_{p,q,\tau} T(\varepsilon^{-1},d,\tau p,\tau q),
-\]
-where $K_{p,q,\tau}$ is a term that may depend on $p$, $q$, and $\tau$, but is independent of $\varepsilon$ and $d$.
+Note that the tractability function is bounded below away from zero even as $\varepsilon \to \infty$, so that the information based complexity is not expected to vanish under arbitrarily loose error requirements.
+For this definition of tractability to make sense we assume that
+\begin{equation}
+	T \text{ is non-decreasing in all variables}
+\end{equation}
+which implies that the problem does not become easier by decreasing the tolerance, $\varepsilon$, or increasing the dimension, $d$.
+Since $T(\cdot,d,\vp)$ is non-decreasing, we may define the following limit:
+\begin{equation}
+	T(0,d,\vp):=\lim_{\varepsilon\to\infty}T(\varepsilon^{-1},d,\vp).
+\end{equation}
+There is a technical assumption required for our analysis.  There exists a $K_{\vp,\tau}$ depending on $\vp$ and $\tau$, but  independent of $\varepsilon$ and $d$, such that
+\begin{equation} \label{eq:ptauassume}
+	[T(\varepsilon^{-1},d,\vp)]^\tau \le K_{\vp,\tau} T(\varepsilon^{-1},d,\tau \vp),   \quad \forall \varepsion \in (0,\infty), \ d \in \naturals, \ \vp\in[0,\infty)^s, \ \tau\in (1,\infty).
+\end{equation}
 
-Furthermore, we assume that, for any choice of $d\in\naturals$ and $p,q\in [0,\infty)$, 
-the quantity $T(0,d,p,q):=\liminf_{\varepsilon\to\infty}T(\varepsilon^{-1},d,p,q)$ exists.
+If \eqref{comp_def} holds for some $\vp$, it clearly holds for larger, $\vp$.  We are often interested in the optimal or smallest $\vp$ for which \eqref{comp_def} holds.
+The  set of optimal parameters, $\mathcal{P}_{\text{opt}}$ is defined as
+\begin{equation}
+	\mathcal{P}_{\text{opt}} : = \{\vp^* : \eqref{comp_def} \text{ holds }\forall \vp \in [\vp,\boldsymbol{\infty}) \setminus \{\vp^*\} \text{ and }
+	\eqref{comp_def} \text{ fails } \forall \vp \in [\vzero,\vp] \setminus \{\vp^*\} \}.
+\end{equation}
+In this article we allow $\vp$ to be a scalar or vector as the situation requires.
 
-A problem is $T$-tractable with parameters $p$ and $q$ iff there exists a positive constant $C_{p,q}$ such that
-\begin{equation} \label{comp_def}
-\comp(\varepsilon,d) \le C_{p,q}\, T(\varepsilon^{-1},d,p,q) \qquad \forall \varepsilon \in (0,\infty), \ \forall d \in \mathbb{N}.
-\end{equation}
-The  set of optimal parameters, $\mathcal{P}_{\text{opt}}$ is defined as
-\begin{multline}
-    \mathcal{P}_{\text{opt}} : = \{(p^*,q^*) : \eqref{comp_def} \text{ holds }\forall (p,q) \in [p^*,\infty) \times [q^*,\infty) \setminus (p^*,q^*) \\ 
-    \eqref{comp_def} \text{ fails } \forall (p,q) \in [0,p^*] \times [0,q^*] \setminus (p^*,q^*) \}.
-\end{multline}
+\subsection{Strong tractability}
 

### 2023-03-11 GeneralizedTractability_230310.tex
Fred M2 2023 Mac Updates

@@
 and the complexity of our linear problem is
-\[
+\begin{equation}\label{eq:comp_def}
 \comp(\varepsilon, d) = \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon\}.
-\]
-
-Certain kinds of common notions of tractability are
-\begin{equation*}
-    \begin{array}{r@{\qquad}c@{\qquad}c}
-    & \comp(\varepsilon, d)\\
-    \toprule
-    \text{strong polynomial algebraic  tractability} & \Theta(\varepsilon^{-p})\\
-    \text{polynomial algebraic tractability} & \Theta(\varepsilon^{-p}d^{q})\\
-    \text{strong polynomial exponential tractability} &  \Theta\bigl([\log(1 + \varepsilon^{-1})]^p\bigr)\\
-    \text{polynomial exponential tractability} & \Theta\bigl([\log(1 + \varepsilon^{-1})]^p  d^{q}\bigr)
-    \end{array}
-\end{equation*}
-\fred{We need to fix these so that the tractability function does not vanish as $\varepsilon \to \infty$.}
+\end{equation}
 
@@
 \]
+A tractability function is a simple function that provides an upper bound on the computational complexity of a problem
 A problem is $T$-tractable with parameter $\vp$ iff there exists a positive constant $C_{\vp}$ such that
-\begin{equation} \label{comp_def}
+\begin{equation} \label{eq:tract_def}
 	\comp(\varepsilon,d) \le C_{\vp}\, T(\varepsilon^{-1},d,\vp) \qquad \forall \varepsilon \in (0,\infty), \ \forall d \in \mathbb{N}.
+\end{equation}
+A problem is \emph{strongly}
+$T$-tractable with parameter $\vp$ iff the complexity is independent of the dimension, that is, there exists a positive constant $C_{\vp}$ such that
+\begin{equation} \label{eq:tract_def}
+	\comp(\varepsilon,d) \le C_{\vp}\, T(\varepsilon^{-1},1,\vp) \qquad \forall \varepsilon \in (0,\infty), \ \forall d \in \mathbb{N}.
 \end{equation}
@@
 \begin{equation} \label{eq:ptauassume}
-	[T(\varepsilon^{-1},d,\vp)]^\tau \le K_{\vp,\tau} T(\varepsilon^{-1},d,\tau \vp),   \quad \forall \varepsion \in (0,\infty), \ d \in \naturals, \ \vp\in[0,\infty)^s, \ \tau\in (1,\infty).
+	[T(\varepsilon^{-1},d,\vp)]^\tau \le K_{\vp,\tau} T(\varepsilon^{-1},d,\tau \vp),   \quad \forall \varepsilon \in (0,\infty), \ d \in \naturals, \ \vp\in[0,\infty)^s, \ \tau\in (1,\infty).
 \end{equation}
 
-If \eqref{comp_def} holds for some $\vp$, it clearly holds for larger, $\vp$.  We are often interested in the optimal or smallest $\vp$ for which \eqref{comp_def} holds.
+If \eqref{eq:tract_def} holds for some $\vp$, it clearly holds for larger, $\vp$.  We are often interested in the optimal or smallest $\vp$ for which \eqref{eq:tract_def} holds.
 The  set of optimal parameters, $\mathcal{P}_{\text{opt}}$ is defined as
 \begin{equation}
-	\mathcal{P}_{\text{opt}} : = \{\vp^* : \eqref{comp_def} \text{ holds }\forall \vp \in [\vp,\boldsymbol{\infty}) \setminus \{\vp^*\} \text{ and }
-	\eqref{comp_def} \text{ fails } \forall \vp \in [\vzero,\vp] \setminus \{\vp^*\} \}.
+	\mathcal{P}_{\text{opt}} : = \{\vp^* : \eqref{eq:tract_def} \text{ holds }\forall \vp \in [\vp,\boldsymbol{\infty}) \setminus \{\vp^*\} \text{ and }
+	\eqref{eq:tract_def} \text{ fails } \forall \vp \in [\vzero,\vp] \setminus \{\vp^*\} \}.
 \end{equation}
@@
 
+Certain common notions of tractability are covered by the general situation described above
+\begin{equation*}
+	\begin{array}{r@{\qquad}c@{\qquad}c}
+		& T(\varepsilon^{-1},d,\vp)\\
+		\toprule
+		\text{strong polynomial algebraic  tractability} & \max(1,\varepsilon^{-p})\\
+		\text{polynomial algebraic tractability} & \max(1,\varepsilon^{-p})d^{q}\\
+		\text{strong polynomial exponential tractability} &  [\max(1,\log(1 + \varepsilon^{-1})]^p\\
+		\text{polynomial exponential tractability} &
+		[\max(1,\log(1 + \varepsilon^{-1}))]^p  d^{q}
+	\end{array}
+\end{equation*}
+Here, $\vp = (p,q)$ in some cases.
+
+In the sections below we prove necessary and sufficient conditions on tractability as generally defined in \eqref{eq:tract_def}.
+These conditions  that involve the boundedness of sums defined in terms of $\{T(\lambda_{i,d}^{-1},\cdot, \cdot)\}_{i=1}^\infty$.
+In practice, it may be easier to verify whether or not these conditions hold than to deal with \eqref{eq:comp_def} directly.
+
 \subsection{Strong tractability}
 
+We first consider the simpler case when the complexity is essentially independent of the dimension, $d$.
+The proof also introduces the line of argument used for the case where there is $d$ dependence.
+
 \begin{theorem}\label{thm_main_strong_tract2}
-A problem is $T$-tractable with $q=0$ iff there exists $p>0$ and an integer $L(p) > 0$ such that
+A problem is strongly $T$-tractable iff there exists $\vp \in [\vzero, \boldsymbol{\infty})$ and an integer $L(\vp) > 0$ such that
 \begin{equation} \label{eq:strong_tractiff3}
-     S_p:=\sup_{d \in \naturals} \sum_{i = L(p)}^\infty \frac{1}{T(\lambda_{i,d}^{-1},1,p,0)} < \infty.
+     S_p:=\sup_{d \in \naturals} \sum_{i = L(\vp)}^\infty \frac{1}{T(\lambda_{i,d}^{-1},1,\vp)} < \infty.
 \end{equation}
-If \eqref{eq:strong_tractiff3} holds, then $\mathcal{P}_{\text{opt}}=(p^*,0)$, where
+If \eqref{eq:strong_tractiff3} holds for some $\vp$, then
 \[
- p^* := \inf\{p>0\ \mbox{such that \eqref{eq:strong_tractiff3} holds}\}.
+	\mathcal{P}_{\text{opt}} : = \{\vp^* : \eqref{eq:strong_tractiff3} \text{ holds }\forall \vp \in [\vp,\boldsymbol{\infty}) \setminus \{\vp^*\} \text{ and }
+\eqref{eq:strong_tractiff3} \text{ fails } \forall \vp \in [\vzero,\vp] \setminus \{\vp^*\} \}.
 \]
 \end{theorem}
+
 \begin{proof}
 \textbf{Sufficient condition:}\\
-Given that $T$ is increasing in its arguments, we have the following equivalent expression,
+Given that $T$ is increasing in its arguments, we have the following equivalent expression for the complexity:
     \begin{align*}
     \comp(\varepsilon, d) &= \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon\} \\
-    &= \min \biggl\{n \in \natzero : \frac{1}{T(\lambda_{n+1,d}^{-1},1,p,0)}\le \frac{1}{T(\varepsilon^{-1},1,p,0) }\biggr\}.
+    &= \min \biggl\{n \in \natzero : \frac{1}{T(\lambda_{n+1,d}^{-1},1,\vp)}\le \frac{1}{T(\varepsilon^{-1},1,\vp) }\biggr\}.
 \end{align*}
-Also since the $\lambda_{i,d}$ are non-increasing, it follows that the $T(\lambda_{i,d}^{-1},1,p,0)$ are non-decreasing. In particular, for all $n\in \mathbb{N}$, we have
+Also since the $\lambda_{i,d}$ are non-increasing, it follows that the $T(\lambda_{i,d}^{-1},1,\vp)$ are non-decreasing. In particular, for all $n\in \mathbb{N}$, we have
 
@@
     \MoveEqLeft{\lambda_{n+1,d} \le \lambda_{n,d} \le \cdots \le \lambda_{1,d}} \\
-    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},1,p,0)} \le \frac{1}{T(\lambda_{n, d}^{-1},1,p,0)} \le \cdots \le \frac{1}{T(\lambda_{1, d}^{-1},1,p,0)} \\
-    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},1,p,0) }
-    \le \frac 1n \sum_{i=1}^n  \frac{1}{T(\lambda_{i, d}^{-1},1,p,0) }
-    \le \frac 1n \sum_{i=1}^\infty  \frac{1}{T(\lambda_{i, d}^{-1},1,p,0)}.
+    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},1,\vp)} \le \frac{1}{T(\lambda_{n, d}^{-1},1,\vp)} \le \cdots \le \frac{1}{T(\lambda_{1, d}^{-1},1,\vp)} \\
+    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},1,\vp) }
+    \le \frac 1n \sum_{i=1}^n  \frac{1}{T(\lambda_{i, d}^{-1},1,\vp) }
+    \le \frac 1n \sum_{i=1}^\infty  \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}.
 \end{align*}
@@
 \begin{align*}
-    n \ge T(\varepsilon^{-1},1,p,0) \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},1,p,0)}
+    n \ge T(\varepsilon^{-1},1,\vp) \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}
     & \implies
-\frac 1n \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},1,p,0) }\le  T(\varepsilon^{-1},1,p,0) \\
-   & \implies   \frac{1}{T(\lambda_{n+1, d}^{-1},1,p,0)} \le \frac{1}{T(\varepsilon^{-1},1,p,0)}.
+\frac 1n \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},1,\vp) }\le  T(\varepsilon^{-1},1,\vp) \\
+   & \implies   \frac{1}{T(\lambda_{n+1, d}^{-1},1,\vp)} \le \frac{1}{T(\varepsilon^{-1},1,\vp)}.
 \end{align*}
@@
        \MoveEqLeft{\comp(\varepsilon,d)} \\
-       &\le 1 + T(\varepsilon^{-1},1,p,0) \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},1,p,0)} \\
-       & = 1 + T(\varepsilon^{-1},1, p,0) \left [ \sum_{i=1}^{L(p)-1} \frac{1}{T(\lambda_{i, d}^{-1},1,p,0)}
-       + \underbrace{\sum_{i=L(p)}^\infty \frac{1}{T(\lambda_{i, d}^{-1},1,p,0)}}_{=:S_p <\infty\ \text{by \eqref{eq:strong_tractiff3}} }\right] \\
-       & \le 1+ T(\varepsilon^{-1},1,p,0) \underbrace{\left[\frac{(L(p)-1)}{T(\lambda_{\max}^{-1},1,p,0)} + S_p\right]}_{=:C_2(p)}\\
-       & = 1+ T(\varepsilon^{-1},1,p,0) C_2 (p)\\
-       &\le C_{p,0} T(\varepsilon^{-1},1,p,0),
+       &\le 1 + T(\varepsilon^{-1},1,\vp) \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)} \\
+       & = 1 + T(\varepsilon^{-1},1, \vp) \left [ \sum_{i=1}^{L(p)-1} \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}
+       + \underbrace{\sum_{i=L(p)}^\infty \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}}_{=:S_p <\infty\ \text{by \eqref{eq:strong_tractiff3}} }\right] \\
+       & \le 1+ T(\varepsilon^{-1},1,\vp) \underbrace{\left[\frac{(L(p)-1)}{T(\lambda_{\max}^{-1},1,\vp)} + S_p\right]}_{=:C_2(p)}\\
+       & = 1+ T(\varepsilon^{-1},1,\vp) C_2 (p)\\
+       &\le C_{\vp} T(\varepsilon^{-1},1,\vp),
 \end{align*}
-for some suitably chosen $C_{p,0}>0$. This means that we have strong $T$-tractability, and verifies sufficiency of \eqref{eq:strong_tractiff3}.
+for some suitably chosen $C_{\vp}>0$. This means that we have strong $T$-tractability, and verifies sufficiency of \eqref{eq:strong_tractiff3}.
 As for $\mathcal{P}_{\text{opt}}$, we immediately see from the above argument that $\mathcal{P}_{\text{opt}}=(p^*,0)$, where
@@
 Suppose that we have strong
-$T$-tractability. That is, for some $p>0$ there exists a positive constant $C_{p,0}$ such that
+$T$-tractability. That is, for some $p>0$ there exists a positive constant $C_{\vp}$ such that
 \[
-\comp(\varepsilon,d)\le C_{p,0}\, T(\varepsilon^{-1},1,p,0)
+\comp(\varepsilon,d)\le C_{\vp}\, T(\varepsilon^{-1},1,\vp)
 \]
@@
 % \begin{equation}\label{eq_strong_tract_p'3}
-% \comp(\varepsilon,d)\le C_{p,0} T(\varepsilon^{-1},1,p',0)
+% \comp(\varepsilon,d)\le C_{\vp} T(\varepsilon^{-1},1,p',0)
 % \end{equation}
@@
 \begin{equation}\label{eq:lambda_K_strong3}
-\lambda_{\lfloor C_{p,0}\, T(\varepsilon^{-1},1,p,0)\rfloor +1,d}\le \varepsilon.
+\lambda_{\lfloor C_{\vp}\, T(\varepsilon^{-1},1,\vp)\rfloor +1,d}\le \varepsilon.
 \end{equation}
@@
 \[
-j=j (\varepsilon):= \lfloor C_{p,0}\, T(\varepsilon^{-1},1,p,0)\rfloor +1.
+j=j (\varepsilon):= \lfloor C_{\vp}\, T(\varepsilon^{-1},1,\vp)\rfloor +1.
 \]
@@
 \[
-  j_d^*=\lfloor  T(0,1,p,0)\rfloor +1,
+  j_d^*=\lfloor  T(0,1,\vp)\rfloor +1,
 \]
@@
 \[
-j=j(\varepsilon)\le C_{p,0}\, T(\varepsilon^{-1},1,p,0)+1.
+j=j(\varepsilon)\le C_{\vp}\, T(\varepsilon^{-1},1,\vp)+1.
 \]
 Due to our assumptions, we know that
-$T(\cdot,1, p,0)$ is increasing in the first argument if
+$T(\cdot,1, \vp)$ is increasing in the first argument if
 we keep $p$ fixed.
@@
 \[
-j \le C_{p,0} T(\varepsilon^{-1},1,p,0)+1\le C_{p,0} T(\lambda_{j,d}^{-1},1,p,0)+1,
+j \le C_{\vp} T(\varepsilon^{-1},1,\vp)+1\le C_{\vp} T(\lambda_{j,d}^{-1},1,\vp)+1,
 \]
@@
 \[
- T(\lambda_{j,d}^{-1},1, p,0) \ge \frac{j-1}{C_{p,0}}.
+ T(\lambda_{j,d}^{-1},1, \vp) \ge \frac{j-1}{C_{\vp}}.
 \]
@@
 \[
- (T(\lambda_{j,d}^{-1},1, p,0))^\tau \ge \frac{(j-1)^\tau}{C_{p,0}^\tau },
+ (T(\lambda_{j,d}^{-1},1, \vp))^\tau \ge \frac{(j-1)^\tau}{C_{\vp}^\tau },
 \]
@@
 \[
- K_{p,0,\tau}\,T (\lambda_{j,d}^{-1},1,\tau p,0) \ge \frac{(j-1)^\tau}{C_{p,0}^\tau},
+ K_{\vp,\tau}\,T (\lambda_{j,d}^{-1},1,\tau \vp) \ge \frac{(j-1)^\tau}{C_{\vp}^\tau},
 \]
-for some $K_{p,0,\tau}>0$.
+for some $K_{\vp,\tau}>0$.
 This gives
 \[
-\sum_{j=j_d^*}^\infty \frac{1}{T (\lambda_{j,d}^{-1},1, \tau p,0)} \le K_{p,0,\tau}\, C_{p,0}^\tau
+\sum_{j=j_d^*}^\infty \frac{1}{T (\lambda_{j,d}^{-1},1, \tau \vp)} \le K_{\vp,\tau}\, C_{\vp}^\tau
 \sum_{j=j_d^*}^\infty \frac{1}{(j-1)^\tau} \le
-\peter{K_{p,0,\tau}\, C_{p,0}^\tau\, \zeta (\tau) }< \infty,
+\peter{K_{\vp,\tau}\, C_{\vp}^\tau\, \zeta (\tau) }< \infty,
 \]
@@
 \[
-\sup_{d\in\naturals} \sum_{j=j_d^*}^\infty \frac{1}{T (\lambda_{j,d}^{-1},1, \tau p,0)} \le K_{p,0,\tau}\, C_{p,0}^\tau\, \zeta (\tau) < \infty.
+\sup_{d\in\naturals} \sum_{j=j_d^*}^\infty \frac{1}{T (\lambda_{j,d}^{-1},1, \tau \vp)} \le K_{\vp,\tau}\, C_{\vp}^\tau\, \zeta (\tau) < \infty.
 \]
@@
 \[
- j_d^* = \lfloor C_{p,0}\, T(0,1,p,0)\rfloor +1 \le \lfloor C_{p,0}\, T(0,1,\tau p,0)\rfloor +1
+ j_d^* = \lfloor C_{\vp}\, T(0,1,\vp)\rfloor +1 \le \lfloor C_{\vp}\, T(0,1,\tau \vp)\rfloor +1
 \]
@@
 \[
- \peter{\sup_{d\in\naturals}} \sum_{j=L(\tau p)}^\infty \frac{1}{T(\lambda_{j,d}^{-1},1, \tau p,0)}<\infty.
+ \peter{\sup_{d\in\naturals}} \sum_{j=L(\tau p)}^\infty \frac{1}{T(\lambda_{j,d}^{-1},1, \tau \vp)}<\infty.
 \]

### 2023-03-11 GeneralizedTractability_230310.tex
Fred M2 2023 Mac Updates

@@
 \]
-This means that the non-negative $\lambda_{i,d}$ are the singular values of the $\SOL_d$. The goal is to find an approximate solution, $\APP_d:\cb_d \times (0,\infty) \to \cg_d$ satisfying
+This means that the non-negative $\lambda_{i,d}$ are the singular values of the $\SOL_d$. To avoid trivial cases, we assume that there are an infinite number of positive eigenvalues.
+
+The goal is to find an approximate solution, $\APP_d:\cb_d \times (0,\infty) \to \cg_d$ satisfying
 \[
@@
 \begin{equation} \label{eq:tract_def}
-	\comp(\varepsilon,d) \le C_{\vp}\, T(\varepsilon^{-1},d,\vp) \qquad \forall \varepsilon \in (0,\infty), \ \forall d \in \mathbb{N}.
+	\comp(\varepsilon,d) \le C_{\vp}\, T(\varepsilon^{-1},d,\vp) \qquad \forall \varepsilon >0, \ d \in \mathbb{N}.
 \end{equation}
@@
 \begin{equation} \label{eq:tract_def}
-	\comp(\varepsilon,d) \le C_{\vp}\, T(\varepsilon^{-1},1,\vp) \qquad \forall \varepsilon \in (0,\infty), \ \forall d \in \mathbb{N}.
+	\comp(\varepsilon,d) \le C_{\vp}\, T(\varepsilon^{-1},1,\vp) \qquad \forall \varepsilon >0 , \ d \in \mathbb{N}.
 \end{equation}
@@
 For this definition of tractability to make sense we assume that
+\begin{subequations} \label{eq:Tconditions}
 \begin{equation}
@@
 which implies that the problem does not become easier by decreasing the tolerance, $\varepsilon$, or increasing the dimension, $d$.
+Since there are an infinite number of positive eigenvalues, it also make sense to assume that
+\begin{equation}
+	\lim_{\varepsilon \to 0} T(\varepsilon^{-1},d,\vp) = \infty \qquad \forall d \in \naturals, \ \vp \in [0,\infty)^s.
+\end{equation}
 Since $T(\cdot,d,\vp)$ is non-decreasing, we may define the following limit:
@@
 \end{equation}
+\end{subequations}
 
@@
 \begin{equation}
-	\mathcal{P}_{\text{opt}} : = \{\vp^* : \eqref{eq:tract_def} \text{ holds }\forall \vp \in [\vp,\boldsymbol{\infty}) \setminus \{\vp^*\} \text{ and }
+	\mathcal{P}_{\textup{opt}} : = \{\vp^* : \eqref{eq:tract_def} \text{ holds }\forall \vp \in [\vp,\boldsymbol{\infty}) \setminus \{\vp^*\} \text{ and }
 	\eqref{eq:tract_def} \text{ fails } \forall \vp \in [\vzero,\vp] \setminus \{\vp^*\} \}.
@@
 \begin{equation} \label{eq:strong_tractiff3}
-     S_p:=\sup_{d \in \naturals} \sum_{i = L(\vp)}^\infty \frac{1}{T(\lambda_{i,d}^{-1},1,\vp)} < \infty.
+     S(p):=\sup_{d \in \naturals} \sum_{i = L(\vp)}^\infty \frac{1}{T(\lambda_{i,d}^{-1},1,\vp)} < \infty.
 \end{equation}
@@
 \[
-	\mathcal{P}_{\text{opt}} : = \{\vp^* : \eqref{eq:strong_tractiff3} \text{ holds }\forall \vp \in [\vp,\boldsymbol{\infty}) \setminus \{\vp^*\} \text{ and }
-\eqref{eq:strong_tractiff3} \text{ fails } \forall \vp \in [\vzero,\vp] \setminus \{\vp^*\} \}.
+	\widetilde{\mathcal{P}}_{\textup{opt}} := \{\vp^* : \eqref{eq:strong_tractiff3} \text{ holds }\forall \vp \in [\vp,\boldsymbol{\infty}) \setminus \{\vp^*\} \text{ and }
+\eqref{eq:strong_tractiff3} \text{ fails } \forall \vp \in [\vzero,\vp] \setminus \{\vp^*\} \} = \mathcal{P}}_{\textup{opt}.
 \]
@@
 Given that $T$ is increasing in its arguments, we have the following equivalent expression for the complexity:
-    \begin{align*}
-    \comp(\varepsilon, d) &= \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon\} \\
-    &= \min \biggl\{n \in \natzero : \frac{1}{T(\lambda_{n+1,d}^{-1},1,\vp)}\le \frac{1}{T(\varepsilon^{-1},1,\vp) }\biggr\}.
-\end{align*}
+    \begin{equation*}
+    \comp(\varepsilon, d) &= \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon\} = \min \biggl\{n \in \natzero : \frac{1}{T(\lambda_{n+1,d}^{-1},1,\vp)}\le \frac{1}{T(\varepsilon^{-1},1,\vp) }\biggr\}.
+\end{equation*}
 Also since the $\lambda_{i,d}$ are non-increasing, it follows that the $T(\lambda_{i,d}^{-1},1,\vp)$ are non-decreasing. In particular, for all $n\in \mathbb{N}$, we have
@@
 Thus, we can conclude that
+\begin{equation*}
+    n \ge T(\varepsilon^{-1},1,\vp) \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}
+   \implies   \frac{1}{T(\lambda_{n+1, d}^{-1},1,\vp)} \le
+   \frac 1n \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},1,\vp) } \le \frac{1}{T(\varepsilon^{-1},1,\vp)}.
+\end{equation*}
+
+This inequality implies an upper bound on the complexity of
 \begin{align*}
-    n \ge T(\varepsilon^{-1},1,\vp) \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}
-    & \implies
-\frac 1n \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},1,\vp) }\le  T(\varepsilon^{-1},1,\vp) \\
-   & \implies   \frac{1}{T(\lambda_{n+1, d}^{-1},1,\vp)} \le \frac{1}{T(\varepsilon^{-1},1,\vp)}.
-\end{align*}
-
-This implies an upper bound on the complexity of
-\begin{align*}
-       \MoveEqLeft{\comp(\varepsilon,d)} \\
+       \comp(\varepsilon,d)
        &\le 1 + T(\varepsilon^{-1},1,\vp) \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)} \\
        & = 1 + T(\varepsilon^{-1},1, \vp) \left [ \sum_{i=1}^{L(p)-1} \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}
-       + \underbrace{\sum_{i=L(p)}^\infty \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}}_{=:S_p <\infty\ \text{by \eqref{eq:strong_tractiff3}} }\right] \\
-       & \le 1+ T(\varepsilon^{-1},1,\vp) \underbrace{\left[\frac{(L(p)-1)}{T(\lambda_{\max}^{-1},1,\vp)} + S_p\right]}_{=:C_2(p)}\\
-       & = 1+ T(\varepsilon^{-1},1,\vp) C_2 (p)\\
+       + \underbrace{\sum_{i=L(p)}^\infty \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}}_{\le S(p) <\infty\ \text{by \eqref{eq:strong_tractiff3}} }\right] \\
+       & \le 1+ T(\varepsilon^{-1},1,\vp) \underbrace{\left[\frac{(L(p)-1)}{T(\lambda_{\max}^{-1},1,\vp)} + S(p)\right]}_{=:C_1(p)}\\
+       & = 1+ T(\varepsilon^{-1},1,\vp) C_1 (p)\\
        &\le C_{\vp} T(\varepsilon^{-1},1,\vp),
@@
 for some suitably chosen $C_{\vp}>0$. This means that we have strong $T$-tractability, and verifies sufficiency of \eqref{eq:strong_tractiff3}.
-As for $\mathcal{P}_{\text{opt}}$, we immediately see from the above argument that $\mathcal{P}_{\text{opt}}=(p^*,0)$, where
-\[
- p^* \le \inf\{p>0\ \mbox{such that \eqref{eq:strong_tractiff3} holds}\}.
-\]
 
@@
 Suppose that we have strong
-$T$-tractability. That is, for some $p>0$ there exists a positive constant $C_{\vp}$ such that
+$T$-tractability. That is, for some $\vp \ge \vzero$ there exists a positive constant $C_{\vp}$ such that
 \[
 \comp(\varepsilon,d)\le C_{\vp}\, T(\varepsilon^{-1},1,\vp)
+\qquad \forall \varepsilon > 0, \ d \in \mathbb{N}.
 \]
-for all $\varepsilon\in (0,\infty)$.
-
-% This, in turn, means that
-% \begin{equation}\label{eq_strong_tract_p'3}
-% \comp(\varepsilon,d)\le C_{\vp} T(\varepsilon^{-1},1,p',0)
-% \end{equation}
-% for all $p'>p$.
-%
-% \noindent This means for (possibly small) $\delta_p>0$, there exists a constant $K$ such that \eqref{eq_strong_tract_p'3} holds for $p'=p+\delta_p$.
-
 Since the eigenvalues $\lambda_{j,d}$ are non-increasing, we have
@@
 \end{equation}
-Let
+
+Define
 \[
-j=j (\varepsilon):= \lfloor C_{\vp}\, T(\varepsilon^{-1},1,\vp)\rfloor +1.
+j (\varepsilon,\vp):= \lfloor C_{\vp}\, T(\varepsilon^{-1},1,\vp)\rfloor +1, \quad
+ L(\vp):= j (\infty,\vp).
 \]
-When we vary $\varepsilon\in (0,\infty)$, we have that $j\in \{j_d^*, j_d^*+1, j_d^*+2,\ldots\}$, where
-\[
-  j_d^*=\lfloor  T(0,1,\vp)\rfloor +1,
-\]
-by the monotonicity of $T$.
-
+Thus, it follows by \eqref{eq:lambda_K_strong3} that $\lambda_{j(\varepsilon,\vp),d} \le \varepsilon$.
 Note furthermore that we always have
 \[
-j=j(\varepsilon)\le C_{\vp}\, T(\varepsilon^{-1},1,\vp)+1.
+j(\varepsilon)\le C_{\vp}\, T(\varepsilon^{-1},1,\vp)+1 \le C_{\vp} T(\lambda_{j(\varepsilon,\vp),d}^{-1},1,\vp)+1, \qquad \forall \varepsilon > 0,
 \]
-Due to our assumptions, we know that
-$T(\cdot,1, \vp)$ is increasing in the first argument if
-we keep $p$ fixed.
+since
+$T(\cdot,1, \vp)$ is non-decreasing.
 
-Then, by \eqref{eq:lambda_K_strong3},
+For $\varepsilon$ taking on all positive values, $j(\varepsilon,\vp)$ takes on all values greater than or equal to $L(\vp)$, so
 \[
-j \le C_{\vp} T(\varepsilon^{-1},1,\vp)+1\le C_{\vp} T(\lambda_{j,d}^{-1},1,\vp)+1,
+j\le C_{\vp}\, T(\varepsilon^{-1},1,\vp)+1 \le C_{\vp} T(\lambda_{j,d}^{-1},1,\vp)+1, \qquad \forall j \ge L(\vp).
 \]
-and the latter chain of inequalities holds for all $j\ge j_d^*$.
+This implies via our technical assumption \eqref{eq:ptauassume} that
+\begin{equation*}
+ K_{\vp,\tau}\,T (\lambda_{j,d}^{-1},1,\tau \vp) \ge
+ [T(\lambda_{j,d}^{-1},1, \vp)]^\tau
+ \ge
+  \left[\frac{(j-1)}{C_{\vp}}\right]^\tau \qquad \forall j \ge L(\vp)
+\end{equation*}
+Summing both sides of the inequality yields and noting that $L(\vp) \le L(\tau\v)$, it follows that
+\begin{multline*}
+\sup_{d\in\naturals} \sum_{j=L(\tau\vp)}^\infty \frac{1}{T (\lambda_{j,d}^{-1},1, \tau \vp)} \le
+\sup_{d\in\naturals} \sum_{j=L(\vp)}^\infty \frac{1}{T (\lambda_{j,d}^{-1},1, \tau \vp)} \\
+\le K_{\vp,\tau}\, C_{\vp}^\tau
+\sum_{j=L(\vp)}^\infty \frac{1}{(j-1)^\tau} \le
+K_{\vp,\tau}\, C_{\vp}^\tau\, \zeta (\tau) < \infty,
+\end{multline*}
+where $\zeta$ denotes the Riemann zeta function.
+This yields \eqref{eq:strong_tractiff3} with $p$ replaced by $\tau p$, and so we see the necessity of $\eqref{eq:strong_tractiff3}$.
 
-This implies
-\[
- T(\lambda_{j,d}^{-1},1, \vp) \ge \frac{j-1}{C_{\vp}}.
-\]
-This, in turn, implies, for any $\tau>1$, that
-\[
- (T(\lambda_{j,d}^{-1},1, \vp))^\tau \ge \frac{(j-1)^\tau}{C_{\vp}^\tau },
-\]
-which yields, due to our assumption on $T$,
-\[
- K_{\vp,\tau}\,T (\lambda_{j,d}^{-1},1,\tau \vp) \ge \frac{(j-1)^\tau}{C_{\vp}^\tau},
-\]
-for some $K_{\vp,\tau}>0$.
-This gives
-\[
-\sum_{j=j_d^*}^\infty \frac{1}{T (\lambda_{j,d}^{-1},1, \tau \vp)} \le K_{\vp,\tau}\, C_{\vp}^\tau
-\sum_{j=j_d^*}^\infty \frac{1}{(j-1)^\tau} \le
-\peter{K_{\vp,\tau}\, C_{\vp}^\tau\, \zeta (\tau) }< \infty,
-\]
-\peter{where by $\zeta(\cdot)$ we denote the Riemann zeta function. Consequently,
-\[
-\sup_{d\in\naturals} \sum_{j=j_d^*}^\infty \frac{1}{T (\lambda_{j,d}^{-1},1, \tau \vp)} \le K_{\vp,\tau}\, C_{\vp}^\tau\, \zeta (\tau) < \infty.
-\]
-}
-
-Note, however, that, \peter{for any $d\in\naturals$,}
-\[
- j_d^* = \lfloor C_{\vp}\, T(0,1,\vp)\rfloor +1 \le \lfloor C_{\vp}\, T(0,1,\tau \vp)\rfloor +1
-\]
-Hence, we can find $L(\tau p)$, which is independent of $\varepsilon$ and $d$, such that
-\[
- \peter{\sup_{d\in\naturals}} \sum_{j=L(\tau p)}^\infty \frac{1}{T(\lambda_{j,d}^{-1},1, \tau \vp)}<\infty.
-\]
-This yields \eqref{eq:strong_tractiff3} with $p$ replaced by $\tau p$, and so we see necessity of $\eqref{eq:strong_tractiff3}$.
+\bigskip
+\noindent \textbf{Optimality:} \\
+To complete the proof, we must show that $\widetilde{\cp}_{\textup{opt}} = \cp_{\textup{opt}}$.
 
@@
 
+As for $\mathcal{P}_{\text{opt}}$, we immediately see from the above argument that $\mathcal{P}_{\text{opt}}=(p^*,0)$, where
+\[
+p^* \le \inf\{p>0\ \mbox{such that \eqref{eq:strong_tractiff3} holds}\}.
+\]
+
 \end{proof}
+
 \bigskip

### 2023-03-11 GeneralizedTractability_230310.tex
Fred M2 2023 Mac Updates

@@
 \newcommand{\kachi}[1]{\begingroup\color{ForestGreen}#1\endgroup}
+
+\newcommand{\vinfty}{\boldsymbol{\infty}}
 
@@
 $T$-tractable with parameter $\vp$ iff the complexity is independent of the dimension, that is, there exists a positive constant $C_{\vp}$ such that
-\begin{equation} \label{eq:tract_def}
+\begin{equation} \label{eq:strong_tract_def}
 	\comp(\varepsilon,d) \le C_{\vp}\, T(\varepsilon^{-1},1,\vp) \qquad \forall \varepsilon >0 , \ d \in \mathbb{N}.
@@
 
-If \eqref{eq:tract_def} holds for some $\vp$, it clearly holds for larger, $\vp$.  We are often interested in the optimal or smallest $\vp$ for which \eqref{eq:tract_def} holds.
+If \eqref{eq:tract_def} holds for some $\vp$, it clearly holds for larger, $\vp$.
+We are often interested in the optimal or smallest $\vp$ for which \eqref{eq:tract_def} holds.
+Let $\cp_{\textup{true}} : = \{\vp^* : \eqref{eq:tract_def} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty})\}$
 The  set of optimal parameters, $\mathcal{P}_{\text{opt}}$ is defined as
 \begin{equation}
-	\mathcal{P}_{\textup{opt}} : = \{\vp^* : \eqref{eq:tract_def} \text{ holds }\forall \vp \in [\vp,\boldsymbol{\infty}) \setminus \{\vp^*\} \text{ and }
-	\eqref{eq:tract_def} \text{ fails } \forall \vp \in [\vzero,\vp] \setminus \{\vp^*\} \}.
+	\mathcal{P}_{\textup{opt}} : = \{\vp^* \in \cp_{\textup{true}} :  \vp* \notin [\vp^\dagger,\boldsymbol{\infty}) \ \forall \vp^\dagger \in  \cp_{\textup{true}} \setminus \{\vp^*\} \}.
 \end{equation}
@@
 
-In the sections below we prove necessary and sufficient conditions on tractability as generally defined in \eqref{eq:tract_def}.
+In the sections below we prove necessary and sufficient conditions on tractability as generally defined in \eqref{eq:tract_def} and \eqref{eq:strong_tract_def}.
 These conditions  that involve the boundedness of sums defined in terms of $\{T(\lambda_{i,d}^{-1},\cdot, \cdot)\}_{i=1}^\infty$.
@@
 \end{equation}
-If \eqref{eq:strong_tractiff3} holds for some $\vp$, then
+If \eqref{eq:strong_tractiff3} holds for some $\vp$, let  $\widetilde{\cp}_{\textup{true}} : = \{\vp^* : \eqref{eq:strong_tractiff3} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty})\}$.
+Then the set of optimal strong tractability parameters is
 \[
-	\widetilde{\mathcal{P}}_{\textup{opt}} := \{\vp^* : \eqref{eq:strong_tractiff3} \text{ holds }\forall \vp \in [\vp,\boldsymbol{\infty}) \setminus \{\vp^*\} \text{ and }
-\eqref{eq:strong_tractiff3} \text{ fails } \forall \vp \in [\vzero,\vp] \setminus \{\vp^*\} \} = \mathcal{P}}_{\textup{opt}.
+	\cp_{\textup{opt}} = \widetilde{\mathcal{P}}_{\textup{opt}} :=
+	\{\vp^* \in \widetilde{\cp}_{\textup{true}} :  \vp* \notin [\vp^\dagger,\boldsymbol{\infty}) \ \forall \vp^\dagger \in  \widetilde{\cp}_{\textup{true}} \setminus \{\vp^*\} \}.
 \]
@@
 Given that $T$ is increasing in its arguments, we have the following equivalent expression for the complexity:
-    \begin{equation*}
-    \comp(\varepsilon, d) &= \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon\} = \min \biggl\{n \in \natzero : \frac{1}{T(\lambda_{n+1,d}^{-1},1,\vp)}\le \frac{1}{T(\varepsilon^{-1},1,\vp) }\biggr\}.
-\end{equation*}
+    \begin{equation} \label{eq:comp_equiv}
+    \comp(\varepsilon, d) &= \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon\} = \min \biggl\{n \in \natzero : \frac{1}{T(\lambda_{n+1,d}^{-1},d,\vp)}\le \frac{1}{T(\varepsilon^{-1},d,\vp) }\biggr\}.
+\end{equation}
+We use this expression for $d=1$ here and for arbitrary $d$ in the next subsection
+
 Also since the $\lambda_{i,d}$ are non-increasing, it follows that the $T(\lambda_{i,d}^{-1},1,\vp)$ are non-decreasing. In particular, for all $n\in \mathbb{N}$, we have
@@
 \begin{align*}
-    \MoveEqLeft{\lambda_{n+1,d} \le \lambda_{n,d} \le \cdots \le \lambda_{1,d}} \\
+    \lambda_{n+1,d} \le \lambda_{n,d} \le \cdots \le \lambda_{1,d}
     & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},1,\vp)} \le \frac{1}{T(\lambda_{n, d}^{-1},1,\vp)} \le \cdots \le \frac{1}{T(\lambda_{1, d}^{-1},1,\vp)} \\
@@
 \end{align*}
-Thus, we can conclude that
+Thus, we can conclude from the previous line that
 \begin{equation*}
@@
 
-This inequality implies an upper bound on the complexity of
+This last inequality implies an upper bound on the complexity of
 \begin{align*}
@@
 \end{align*}
-for some suitably chosen $C_{\vp}>0$. This means that we have strong $T$-tractability, and verifies sufficiency of \eqref{eq:strong_tractiff3}.
+for some suitably chosen $C_{\vp}>0$. This means that we have strong $T$-tractability via \eqref{eq:strong_tract_def}, and verifies sufficiency of \eqref{eq:strong_tractiff3}.
 
@@
 Suppose that we have strong
-$T$-tractability. That is, for some $\vp \ge \vzero$ there exists a positive constant $C_{\vp}$ such that
+$T$-tractability as defined in \eqref{eq:strong_tract_def}. That is, for some $\vp \ge \vzero$ there exists a positive constant $C_{\vp}$ such that
 \[
@@
 \end{equation*}
-Summing both sides of the inequality yields and noting that $L(\vp) \le L(\tau\v)$, it follows that
+Summing both sides of the inequality yields and noting that $L(\vp) \le L(\tau\vp)$, it follows that
 \begin{multline*}
@@
 \noindent \textbf{Optimality:} \\
-To complete the proof, we must show that $\widetilde{\cp}_{\textup{opt}} = \cp_{\textup{opt}}$.
+To complete the proof, we must show that $\cp_{\textup{opt}} = \widetilde{\cp}_{\textup{opt}}$.
+We do this by proving that $\cp_{\textup{true}} = \widetilde{\cp}_{\textup{true}}$.
+Then, since $\cp_{\textup{opt}}$ is defined in terms of $\cp_{\textup{opt}}$ in the same way as $\widetilde{\cp}_{\textup{opt}}$ is defined in terms of $\widetilde{\cp}_{\textup{opt}}$, it follows that $\cp_{\textup{opt}} = \widetilde{\cp}_{\textup{opt}}$.
 
-Assume that $\mathcal{P}_{\text{opt}}=(p^*,0)$. We already know from the first part of the proof that
-\[
- p^* \le \inf\{p>0\ \mbox{such that \eqref{eq:strong_tractiff3} holds}\}.
-\]
-Suppose that we would have
-\[
- p^* < \inf\{p>0\ \mbox{such that \eqref{eq:strong_tractiff3} holds}\}.
-\]
-\peter{Then, however, there exists a $p^\dag$ such that
-\[
-p^* < p^\dag < \inf\{p>0\ \mbox{such that \eqref{eq:strong_tractiff3} holds}\},
-\]
-and that the problem is $T$-tractable with parameters $q=0$ and $p^\dag$. }
-We can proceed as in the second part of the proof and show that
-\[
- \sup_{d\in\naturals} \sum_{j=L(\tau \peter{p^\dag})}^\infty \frac{1}{T(\lambda_{j,d}^{-1},1, \tau \peter{p^\dag},0)}<\infty.
-\]
-for any $\tau>1$, and a suitable $L(\tau \peter{p^\dag})$. By choosing $\tau$ sufficiently close to 1, we then would
-obtain
-\[
- \tau \peter{p^\dag} < \inf\{p>0\ \mbox{such that \eqref{eq:strong_tractiff3} holds}\},
-\]
-which is a contradiction. So, we must have
-\[
- p^* = \inf\{p>0\ \mbox{such that \eqref{eq:strong_tractiff3} holds}\}.
-\]
+If $\vp^* \in \cp_{\textup{true}}$, then \eqref{eq:strong_tract_def} holds for all $\vp \in (\vp^*,\vinfty)$.
+By the argument to prove the necessary condition, it follows that \eqref{eq:strong_tractiff3} must also hold for all $\vp \in (\vp^*,\vinfty)$, so $\vp^* \in \widetilde{\cp}_{\textup{true}}$.
+Conversely, if $\vp^* \in \widetilde{\cp}_{\textup{true}}$, then \eqref{eq:strong_tractiff3}  holds for all $\vp \in (\vp^*,\vinfty)$.
+By the argument to prove the sufficient condition, it follows that \eqref{eq:strong_tract_def} must also hold for all $\vp \in (\vp^*,\vinfty)$, so $\vp^* \in \cp}_{\textup{true}}$.
 
-This concludes the proof of the theorem.
+\bigskip
 
-As for $\mathcal{P}_{\text{opt}}$, we immediately see from the above argument that $\mathcal{P}_{\text{opt}}=(p^*,0)$, where
-\[
-p^* \le \inf\{p>0\ \mbox{such that \eqref{eq:strong_tractiff3} holds}\}.
-\]
+\noindent This concludes the proof of the theorem.
 

### 2023-03-11 GeneralizedTractability_230310.tex
Fred M2 2023 Mac Updates

@@
 \begin{proof}
-\textbf{Sufficient condition:}\\
+\textbf{Sufficient condition:}\newline
+We make the first part of the argument in some generality so that it can be reused in the proof of Theorem \ref{thm_main_tract2} for tractability.
 Given that $T$ is increasing in its arguments, we have the following equivalent expression for the complexity:
     \begin{equation} \label{eq:comp_equiv}
-    \comp(\varepsilon, d) &= \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon\} = \min \biggl\{n \in \natzero : \frac{1}{T(\lambda_{n+1,d}^{-1},d,\vp)}\le \frac{1}{T(\varepsilon^{-1},d,\vp) }\biggr\}.
+    \comp(\varepsilon, d) &= \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon\} = \min \biggl\{n \in \natzero : \frac{1}{T(\lambda_{n+1,d}^{-1},d',\vp)}\le \frac{1}{T(\varepsilon^{-1},d',\vp) }\biggr\},
 \end{equation}
-We use this expression for $d=1$ here and for arbitrary $d$ in the next subsection
+for any $d' \in \naturals$.
 
-Also since the $\lambda_{i,d}$ are non-increasing, it follows that the $T(\lambda_{i,d}^{-1},1,\vp)$ are non-decreasing. In particular, for all $n\in \mathbb{N}$, we have
-
+Also since the $\lambda_{i,d}$ are non-increasing in $i$, it follows that the $T(\lambda_{i,d}^{-1},d',\vp)$ are non-decreasing in $i$. In particular, for all $n\in \mathbb{N}$, we have
 \begin{align*}
     \lambda_{n+1,d} \le \lambda_{n,d} \le \cdots \le \lambda_{1,d}
-    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},1,\vp)} \le \frac{1}{T(\lambda_{n, d}^{-1},1,\vp)} \le \cdots \le \frac{1}{T(\lambda_{1, d}^{-1},1,\vp)} \\
-    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},1,\vp) }
-    \le \frac 1n \sum_{i=1}^n  \frac{1}{T(\lambda_{i, d}^{-1},1,\vp) }
-    \le \frac 1n \sum_{i=1}^\infty  \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}.
+    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d',\vp)} \le \frac{1}{T(\lambda_{n, d}^{-1},d',\vp)} \le \cdots \le \frac{1}{T(\lambda_{1, d}^{-1},d',\vp)} \\
+    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d',\vp) }
+    \le \frac 1n \sum_{i=1}^n  \frac{1}{T(\lambda_{i, d}^{-1},d',\vp) }
+    \le \frac 1n \sum_{i=1}^\infty  \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)}.
 \end{align*}
 Thus, we can conclude from the previous line that
-\begin{equation*}
-    n \ge T(\varepsilon^{-1},1,\vp) \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}
-   \implies   \frac{1}{T(\lambda_{n+1, d}^{-1},1,\vp)} \le
-   \frac 1n \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},1,\vp) } \le \frac{1}{T(\varepsilon^{-1},1,\vp)}.
-\end{equation*}
+\begin{multline*}
+    n \ge T(\varepsilon^{-1},d',\vp) \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} \\
+   \implies   \frac{1}{T(\lambda_{n+1, d}^{-1},d',\vp)} \le
+   \frac 1n \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d',\vp) } \le \frac{1}{T(\varepsilon^{-1},d',\vp)} \qquad \forall \varepsilon > 0, \ d,d' \in \naturals.
+\end{multline*}
+This last inequality together with \eqref{eq:comp_equiv} implies an upper bound on the complexity: of
+\begin{equation}
+	\comp(\varepsilon,d)
+	\le 1 + T(\varepsilon^{-1},d',\vp) \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} \qquad \forall \varepsilon > 0, \ d, d' \in \naturals
+\end{equation}
 
-This last inequality implies an upper bound on the complexity of
+Now we take this upper bound further, specializing to the case of $d'=1$:
 \begin{align*}
        \comp(\varepsilon,d)
-       &\le 1 + T(\varepsilon^{-1},1,\vp) \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)} \\
-       & = 1 + T(\varepsilon^{-1},1, \vp) \left [ \sum_{i=1}^{L(p)-1} \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}
+       & = 1 + T(\varepsilon^{-1},1, \vp) \left [ \sum_{i=1}^{L(\vp)-1} \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}
        + \underbrace{\sum_{i=L(p)}^\infty \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}}_{\le S(p) <\infty\ \text{by \eqref{eq:strong_tractiff3}} }\right] \\

### 2023-03-12 GeneralizedTractability_230310.tex
Fred M2 2023 Mac Updates

@@
 \end{equation}
+In this article we allow $\vp$ to be a scalar or vector as the situation requires.
 
@@
 
-If \eqref{eq:tract_def} holds for some $\vp$, it clearly holds for larger, $\vp$.
-We are often interested in the optimal or smallest $\vp$ for which \eqref{eq:tract_def} holds.
-Let $\cp_{\textup{true}} : = \{\vp^* : \eqref{eq:tract_def} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty})\}$
-The  set of optimal parameters, $\mathcal{P}_{\text{opt}}$ is defined as
-\begin{equation}
-	\mathcal{P}_{\textup{opt}} : = \{\vp^* \in \cp_{\textup{true}} :  \vp* \notin [\vp^\dagger,\boldsymbol{\infty}) \ \forall \vp^\dagger \in  \cp_{\textup{true}} \setminus \{\vp^*\} \}.
-\end{equation}
-In this article we allow $\vp$ to be a scalar or vector as the situation requires.
+If \eqref{eq:tract_def} holds for some $\vp$, it clearly holds for larger, $\vp$.  We are often interested in the optimal or smallest $\vp$ for which \eqref{eq:tract_def} holds.  Let
+\begin{equation*}
+	\cp_{\textup{trct}} : = \{\vp^* : \eqref{eq:tract_def} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty})\}, \qquad
+	\cp_{\textup{strct}} : = \{\vp^* : \eqref{eq:strong_tract_def} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty})\}.
+\end{equation*}
+The  set of optimal parameters is defined as all of those parameters satisfying the (strong) tractability conditions that are not greater than or equal to others:
+\begin{gather}
+	\label{eq:Poptdef}
+	\mathcal{P}_{\textup{opt}} : = \{\vp^* \in \cp_{\textup{trct}} :  \vp* \notin [\vp^\dagger,\boldsymbol{\infty}) \ \forall \vp^\dagger \in  \cp_{\textup{trct}} \setminus \{\vp^*\} \}, \\
+	\label{eq:Psoptdef}
+	\mathcal{P}_{\textup{sopt}} : = \{\vp^* \in \cp_{\textup{strct}} :  \vp* \notin [\vp^\dagger,\boldsymbol{\infty}) \ \forall \vp^\dagger \in  \cp_{\textup{strct}} \setminus \{\vp^*\} \}.
+\end{gather}
 
@@
 \begin{equation*}
-	\begin{array}{r@{\qquad}c@{\qquad}c}
-		& T(\varepsilon^{-1},d,\vp)\\
+	\begin{array}{r@{\qquad}c@{\qquad}cc}
+		& T(\varepsilon^{-1},d,\vp)
+		& T(0,d,\vp)\\
 		\toprule
-		\text{strong polynomial algebraic  tractability} & \max(1,\varepsilon^{-p})\\
-		\text{polynomial algebraic tractability} & \max(1,\varepsilon^{-p})d^{q}\\
-		\text{strong polynomial exponential tractability} &  [\max(1,\log(1 + \varepsilon^{-1})]^p\\
+		\text{strong polynomial algebraic  tractability} & \max(1,\varepsilon^{-p}) & 1\\
+		\text{polynomial algebraic tractability} & \max(1,\varepsilon^{-p})d^{q} & d^{q}\\
+		\text{strong polynomial exponential tractability} &  [\max(1,\log(1 + \varepsilon^{-1})]^p & 1\\
 		\text{polynomial exponential tractability} &
-		[\max(1,\log(1 + \varepsilon^{-1}))]^p  d^{q}
+		[\max(1,\log(1 + \varepsilon^{-1}))]^p  d^{q} & d^{q}
 	\end{array}
 \end{equation*}
-Here, $\vp = (p,q)$ in some cases.
+Here above, $\vp = (p,q)$ in some cases.
 
@@
 \begin{equation} \label{eq:strong_tractiff3}
-     S(p):=\sup_{d \in \naturals} \sum_{i = L(\vp)}^\infty \frac{1}{T(\lambda_{i,d}^{-1},1,\vp)} < \infty.
+     S(\vp):=\sup_{d \in \naturals} \sum_{i = L(\vp)}^\infty \frac{1}{T(\lambda_{i,d}^{-1},1,\vp)} < \infty.
 \end{equation}
-If \eqref{eq:strong_tractiff3} holds for some $\vp$, let  $\widetilde{\cp}_{\textup{true}} : = \{\vp^* : \eqref{eq:strong_tractiff3} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty})\}$.
-Then the set of optimal strong tractability parameters is
+If \eqref{eq:strong_tractiff3} holds for some $\vp$, let  $\widetilde{\cp}_{\textup{strct}} : = \{\vp^* : \eqref{eq:strong_tractiff3} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty})\}$.
+Then $\cp_{\textup{strct}} = \widetilde{\cp}_{\textup{strct}}$, and the set of optimal strong tractability parameters is
 \[
-	\cp_{\textup{opt}} = \widetilde{\mathcal{P}}_{\textup{opt}} :=
-	\{\vp^* \in \widetilde{\cp}_{\textup{true}} :  \vp* \notin [\vp^\dagger,\boldsymbol{\infty}) \ \forall \vp^\dagger \in  \widetilde{\cp}_{\textup{true}} \setminus \{\vp^*\} \}.
+	\cp_{\textup{sopt}} =
+	\{\vp^* \in \widetilde{\cp}_{\textup{strct}} :  \vp* \notin [\vp^\dagger,\boldsymbol{\infty}) \ \forall \vp^\dagger \in  \widetilde{\cp}_{\textup{strct}} \setminus \{\vp^*\} \}.
 \]
@@
 This last inequality together with \eqref{eq:comp_equiv} implies an upper bound on the complexity: of
-\begin{equation}
+\begin{equation} \label{eq:compUP}
 	\comp(\varepsilon,d)
@@
        + \underbrace{\sum_{i=L(p)}^\infty \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}}_{\le S(p) <\infty\ \text{by \eqref{eq:strong_tractiff3}} }\right] \\
-       & \le 1+ T(\varepsilon^{-1},1,\vp) \underbrace{\left[\frac{(L(p)-1)}{T(\lambda_{\max}^{-1},1,\vp)} + S(p)\right]}_{=:C_1(p)}\\
+       & \le 1+ T(\varepsilon^{-1},1,\vp) \underbrace{\left[\frac{(L(p)-1)}{T(\lambda_{\max}^{-1},1,\vp)} + S(\vp)\right]}_{=:C_1(\vp)}\\
        & = 1+ T(\varepsilon^{-1},1,\vp) C_1 (p)\\
@@
 \[
-j(\varepsilon)\le C_{\vp}\, T(\varepsilon^{-1},1,\vp)+1 \le C_{\vp} T(\lambda_{j(\varepsilon,\vp),d}^{-1},1,\vp)+1, \qquad \forall \varepsilon > 0,
+j(\varepsilon,\vp)\le C_{\vp}\, T(\varepsilon^{-1},1,\vp)+1 \le C_{\vp} T(\lambda_{j(\varepsilon,\vp),d}^{-1},1,\vp)+1, \qquad \forall \varepsilon > 0,
 \]
@@
 \noindent \textbf{Optimality:} \\
-To complete the proof, we must show that $\cp_{\textup{opt}} = \widetilde{\cp}_{\textup{opt}}$.
-We do this by proving that $\cp_{\textup{true}} = \widetilde{\cp}_{\textup{true}}$.
-Then, since $\cp_{\textup{opt}}$ is defined in terms of $\cp_{\textup{opt}}$ in the same way as $\widetilde{\cp}_{\textup{opt}}$ is defined in terms of $\widetilde{\cp}_{\textup{opt}}$, it follows that $\cp_{\textup{opt}} = \widetilde{\cp}_{\textup{opt}}$.
+To complete the proof, we must show that $\cp_{\textup{strct}} = \widetilde{\cp}_{\textup{strct}}$.
+Then, the expression for  $\cp_{\textup{sopt}}$ automatically follows from its definition in \eqref{eq:Psoptdef}.
 
-If $\vp^* \in \cp_{\textup{true}}$, then \eqref{eq:strong_tract_def} holds for all $\vp \in (\vp^*,\vinfty)$.
-By the argument to prove the necessary condition, it follows that \eqref{eq:strong_tractiff3} must also hold for all $\vp \in (\vp^*,\vinfty)$, so $\vp^* \in \widetilde{\cp}_{\textup{true}}$.
-Conversely, if $\vp^* \in \widetilde{\cp}_{\textup{true}}$, then \eqref{eq:strong_tractiff3}  holds for all $\vp \in (\vp^*,\vinfty)$.
-By the argument to prove the sufficient condition, it follows that \eqref{eq:strong_tract_def} must also hold for all $\vp \in (\vp^*,\vinfty)$, so $\vp^* \in \cp}_{\textup{true}}$.
+If $\vp^* \in \cp_{\textup{strct}}$, then \eqref{eq:strong_tract_def} holds for all $\vp \in (\vp^*,\vinfty)$.
+By the argument to prove the necessary condition, it follows that \eqref{eq:strong_tractiff3} must also hold for all $\vp \in (\vp^*,\vinfty)$, so $\vp^* \in \widetilde{\cp}_{\textup{strct}}$.
+Conversely, if $\vp^* \in \widetilde{\cp}_{\textup{strct}}$, then \eqref{eq:strong_tractiff3}  holds for all $\vp \in (\vp^*,\vinfty)$.
+By the argument to prove the sufficient condition, it follows that \eqref{eq:strong_tract_def} must also hold for all $\vp \in (\vp^*,\vinfty)$, so $\vp^* \in \cp}_{\textup{strct}}$.
 
@@
 \begin{theorem}\label{thm_main_tract2}
-A problem is $T$-tractable iff there exist $p,q>0$, and $q_1>0$ and a constant $L(p,q_1) > 0$ such that
+A problem is $T$-tractable iff there exist $\vp\ge \vzero$ and a constant $L(\vp) > 0$ such that
 \begin{equation} \label{eq:tractiff4}
-     S_{p,q,q_1}:=\sup_{d \in \naturals}
-     \sum_{i = \lceil L(p,q_1)\, T(0,d,p,q_1) \rceil}^\infty \frac{1}{T(\lambda^{-1}_{i,d},d,p,q)}< \infty.
+     S(\vp):=\sup_{d \in \naturals}
+     \sum_{i = \lceil L(\vp)\, T(0,d,\vp) \rceil}^\infty \frac{1}{T(\lambda^{-1}_{i,d},d,\vp)}< \infty.
 \end{equation}
-\end{theorem}
-
-\peter{(PETER: Do we also want to include a statement on the optimal parameters $p^*,q^*$?)}
+If \eqref{eq:tractiff4} holds for some $\vp$, let  $\widetilde{\cp}_{\textup{trct}} : = \{\vp^* : \eqref{eq:tractiff4} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty})\}$.
+Then $\cp_{\textup{trct}} = \widetilde{\cp}_{\textup{trct}}$, and the set of optimal strong tractability parameters is
+\[
+\cp_{\textup{opt}} =
+\{\vp^* \in \widetilde{\cp}_{\textup{trct}} :  \vp* \notin [\vp^\dagger,\boldsymbol{\infty}) \ \forall \vp^\dagger \in  \widetilde{\cp}_{\textup{trct}} \setminus \{\vp^*\} \}.
+\]\end{theorem}
 
 \begin{proof}
-    \textbf{Sufficient Condition:}\\ Suppose that \eqref{eq:tractiff4} holds for some $p,q>0$.
-Because $T$ is increasing in its arguments, it follows that the complexity may be equivalently expressed as
+    \textbf{Sufficient Condition:}\\
+Suppose that \eqref{eq:tractiff4} holds for some $\vp \ge 0$.
+By the argument in the proof of the sufficient condition for Theorem \ref{thm_main_strong_tract2}, it follows from \eqref{eq:compUP} with $d'=d$ that the complexity has an upper bound of
+\begin{equation*}
+	 \comp(\varepsilon,d)} \le 1 + T(\varepsilon^{-1},d,\vp) \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}
+\end{equation*}
+
+Let $J(\vp,d): = \lceil L(\vp)\, T(0,d,\vp)\rceil$.  Then this upper bound on the complexity can be further bounded above by
 \begin{align*}
-    \comp(\varepsilon, d) &= \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon\} \\
-    &= \min \biggl\{n \in \natzero : \frac{1}{T(\lambda_{n+1, d}^{-1},d,p,q)} \le \frac{1}{T(\varepsilon^{-1},d,p,q)} \biggr\}.
+       \comp(\varepsilon,d)
+       & = 1 + T(\varepsilon^{-1},d,\vp) \Biggl [ \sum_{i=1}^{J(\vp,d) -1} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}
+       + \underbrace{\sum_{i=J(\vp,d)}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}}_{\le S(\vp) \text{ by \eqref{eq:tractiff4}}} \Biggr ] \\
+       & \le 1+ T(\varepsilon^{-1},d,\vp)\left[ \frac{J(\vp,d)-1}{T(\lambda_{\max}^{-1},d,\vp)} + S(\vp)\right]
+        \\
+       & \le 1+ T(\varepsilon^{-1},d,\vp)\left[L(\vp)\, T(0,d,\vp) + S(\vp)\right] \qquad \text{since } T(\lambda_{\max}^{-1},d,\vp) \ge 1\\
+       & \le 1+L(\vp)\,T(\varepsilon^{-1},d,\vp) T(0,d,\vp) + S(\vp)\, T(\varepsilon^{-1},d,\vp)\\
+       & \le 1+L(\vp)\,T(\varepsilon^{-1},d,\vp) T(\varepsilon^{-1},d,\vp) + S(\vp)\, T(\varepsilon^{-1},d,\vp)\\
+       & \le 1+L(\vp)\,K_{\vp,2} T(\varepsilon^{-1},d,2\vp)  + S(\vp)\, T(\varepsilon^{-1},d,\vp)  \qquad \text{by \eqref{eq:ptauassume}}\\
+       & \le C_{2}(2\vp) \,T(\varepsilon^{-1},d,2\vp)
 \end{align*}
+for some suitably chosen $C_{2}(2\vp)>0$. It follows that we have $T$-tractability, which shows sufficiency of \eqref{eq:tractiff4}. \\
 
-Since the $\lambda_{i,d}$ are non-increasing it follows that the $\phi(\lambda_{i, d}^{-1},p)$ are non-decreasing.
-In particular, for all $n \in \naturals$,
-\begin{align*}
-    \MoveEqLeft{\lambda_{n+1,d} \le \lambda_{n,d} \le \cdots \le \lambda_{1,d}} \\
-    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d,p,q)} \le \frac{1}{T(\lambda_{n, d}^{-1},d,p,q))} \le \cdots \le \frac{1}{T(\lambda_{1, d}^{-1},d,p,q)} \\
-    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d,p.q)}
-    \le \frac 1n \sum_{i=1}^n  \frac{1}{T(\lambda_{i, d}^{-1},d,p,q)}
-    \le \frac 1n \sum_{i=1}^\infty  \frac{1}{T(\lambda_{i, d}^{-1},d,p,q)}.
-\end{align*}
-Thus, we can conclude that
-\begin{align*}
-    n \ge T(\varepsilon^{-1},d,p,q) \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d,p,q)}
-    & \implies
-  \frac 1n \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d,p,q)} \le  \frac{1}{T(\varepsilon^{-1},d,p,q)} \\
-   & \implies   \frac{1}{T(\lambda_{n+1, d}^{-1},d,p,q)} \le \frac{1}{T(\varepsilon^{-1},d,p,q)}.
-\end{align*}
-This implies an upper bound on the complexity of
-\begin{align*}
-       \MoveEqLeft{\comp(\varepsilon,d)} \\
-       &\le 1 + T(\varepsilon^{-1},d,p,q) \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d,p,q)} \\
-       & = 1 + T(\varepsilon^{-1},d,p,q) \left [ \sum_{i=1}^{\lceil L(p,q_1)\, T(0,d,p,q_1)\rceil -1} \frac{1}{T(\lambda_{i, d}^{-1},d,p,q)}
-       + \sum_{i=\lceil L(p,q_1)\, T(0,d,p,q_1) \rceil}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d,p,q)} \right ] \\
-       & \le 1+ T(\varepsilon^{-1},d,p,q)\left[ \frac{\lceil L(p,q_1)\, T(0,d,p,q_1)\rceil-1}{T(\lambda_{\max}^{-1},d,p,q)} + S_{p,q,q_1}\right]
-        \qquad \text{by \eqref{eq:tractiff4}} \\
-       & \le 1+ T(\varepsilon^{-1},d,p,q)\left[L(p,q_1)\, T(0,d,p,q_1) + S_{p,q,q_1}\right]\\
-       & \le 1+L(p,q_1)\,T(\varepsilon^{-1},d,p,q) T(0,d,p,q_1) + S_{p,q,q_1}\, T(\varepsilon^{-1},d,p,q)\\
-       & \le 1+L(p,q_1)\,T(\varepsilon^{-1},d,p,q) T(\varepsilon^{-1},d,p,q_1) + S_{p,q,q_1}\, T(\varepsilon^{-1},d,p,q)\\
-       & \le 1+L(p,q_1)\,T(\varepsilon^{-1},d,2p,2\max\{q,q_1\})  + S_{p,q}\, T(\varepsilon^{-1},d,p,q)  \\
-       & \le C_{2p,2\max\{q,q_1\}} \,T(\varepsilon^{-1},d,2p,2\max\{q,q_1\})
-\end{align*}
-for some suitably chosen $C_{2p,2\max\{q,q_1\}}>0$. It follows that we have $T$-tractability, which shows sufficiency of \eqref{eq:tractiff4}. \\
+\noindent \textbf{Necessary condition:}\\
+Suppose that we have
+$T$-tractability. That is, for some $\vp \ge \vzero$, there exists a positive constant $C_{\vp}$ such that
+\[
+\comp(\varepsilon,d)\le C_{\vp}\, (T(\varepsilon^{-1},d,\vp) \qquad \forall \varepsilon > 0,  \ d \in \naturals.
+\]
+Since the eigenvalues $\lambda_{j,d}$ are non-increasing, we have
+\begin{equation}\label{eq:lambda_K4}
+	\lambda_{\lfloor C_{\vp}\, T(\varepsilon^{-1},d,\vp)\rfloor +1,d}\le \varepsilon.
+\end{equation}
+Define
+\[
+j (\varepsilon,d,\vp):= \lfloor C_{\vp}\, T(\varepsilon^{-1},d,\vp)\rfloor +1, \quad
+j (\infty,d,\vp) = \lfloor C_{\vp}\, T(0,d,\vp)\rfloor +1.
+\]
+Thus, it follows by \eqref{eq:lambda_K4} that $\lambda_{j(\varepsilon,d,\vp),d} \le \varepsilon$.
+Note furthermore that we always have
+\[
+j(\varepsilon,d,\vp)\le C_{\vp}\, T(\varepsilon^{-1},1,\vp)+1 \le C_{\vp} T(\lambda_{j(\varepsilon,d,\vp),d}^{-1},1,\vp)+1, \qquad \forall \varepsilon > 0, \ d \in \naturals
+\]
+since
+$T(\cdot,d,\vp)$ is non-decreasing.
 
-\textbf{Necessary condition:}\\
-Suppose that we have
-$T$-tractability. That is, for some $p>0$ and $q>0$, there exists a positive constant $C_{p,q}$ such that
+For $\varepsilon$ taking on all positive values, $j(\varepsilon,d,\vp)$ takes on all values greater than or equal to $j(\infty,d,\vp)$, so
 \[
-\comp(\varepsilon,d)\le C_{p,q}\, (T(\varepsilon^{-1},d,p,q)
+j\le C_{\vp}\, T(\varepsilon^{-1},d,\vp)+1 \le C_{\vp} T(\lambda_{j,d}^{-1},d,\vp)+1, \qquad \forall j \ge j(\infty,d,\vp).
 \]
-for all $\varepsilon\in (0,\infty)$ and all $d\in\naturals$.
+This implies via our technical assumption \eqref{eq:ptauassume} that
+\begin{equation*}
+	K_{\vp,\tau}\,T (\lambda_{j,d}^{-1},1,\tau \vp) \ge
+	[T(\lambda_{j,d}^{-1},1, \vp)]^\tau
+	\ge
+	\left[\frac{(j-1)}{C_{\vp}}\right]^\tau \qquad \forall j \ge j(\infty,d,\vp)
+\end{equation*}
+Summing both sides of the inequality yields and noting that $L(\vp) \le L(\tau\vp)$, it follows that
+\begin{multline*}
+	\sup_{d\in\naturals} \sum_{j=L(\tau\vp)}^\infty \frac{1}{T (\lambda_{j,d}^{-1},1, \tau \vp)} \le
+	\sup_{d\in\naturals} \sum_{j=L(\vp)}^\infty \frac{1}{T (\lambda_{j,d}^{-1},1, \tau \vp)} \\
+	\le K_{\vp,\tau}\, C_{\vp}^\tau
+	\sum_{j=L(\vp)}^\infty \frac{1}{(j-1)^\tau} \le
+	K_{\vp,\tau}\, C_{\vp}^\tau\, \zeta (\tau) < \infty,
+\end{multline*}
+where $\zeta$ denotes the Riemann zeta function.
+This yields \eqref{eq:strong_tractiff3} with $p$ replaced by $\tau p$, and so we see the necessity of $\eqref{eq:strong_tractiff3}$.
 
@@
 \begin{equation}\label{eq:lambda_K4}
-\lambda_{\lfloor C_{p,q}\, T(\varepsilon^{-1},d,p,q)\rfloor +1,d}\le \varepsilon.
+\lambda_{\lfloor C_{\vp}\, T(\varepsilon^{-1},d,\vp)\rfloor +1,d}\le \varepsilon.
 \end{equation}
@@
 \[
-j=j (\varepsilon):= \lfloor C_{p,q}\, T(\varepsilon^{-1},d,p,q)\rfloor +1.
+j=j (\varepsilon):= \lfloor C_{\vp}\, T(\varepsilon^{-1},d,\vp)\rfloor +1.
 \]
@@
 \[
-  j_d^*=\lfloor C_{p,q}\, T(0,d,p,q)\rfloor +1
+  j_d^*=\lfloor C_{\vp}\, T(0,d,\vp)\rfloor +1
 \]
@@
 \[
-j\le C_{p,q}\, T(\varepsilon^{-1},d,p,q) +1.
+j\le C_{\vp}\, T(\varepsilon^{-1},d,\vp) +1.
 \]
 Due to our assumptions, we know that
-$T(\cdot,d,p,q)$ is increasing in the first argument if
+$T(\cdot,d,\vp)$ is increasing in the first argument if
 we keep $p$ and $q$ fixed.
@@
 \[
-j \le C_{p,q}\, T(\varepsilon^{-1},d,p,q) +1 \le C_{p,q}\, T(\lambda_{j,d}^{-1},d,p,q) +1,
+j \le C_{\vp}\, T(\varepsilon^{-1},d,\vp) +1 \le C_{\vp}\, T(\lambda_{j,d}^{-1},d,\vp) +1,
 \]
@@
 \[
-T(\lambda_{j,d}^{-1},d, p,q) \ge \frac{j-1}{C_{p,q}}.
+T(\lambda_{j,d}^{-1},d, \vp) \ge \frac{j-1}{C_{\vp}}.
 \]
@@
 \[
- (T(\lambda_{j,d}^{-1},d,p,q))^\tau \ge \frac{(j-1)^\tau}{C_{p,q}^\tau},
+ (T(\lambda_{j,d}^{-1},d,\vp))^\tau \ge \frac{(j-1)^\tau}{C_{\vp}^\tau},
 \]
@@
 \[
- K_{p,q,\tau}\, T (\lambda_{j,d}^{-1},d,\tau p,\tau q) \ge (T(\lambda_{j,d}^{-1},d, p,q))^\tau
- \ge \frac{(j-1)^\tau}{C_{p,q}^\tau}.
+ K_{\vp,\tau}\, T (\lambda_{j,d}^{-1},d,\tau p,\tau q) \ge (T(\lambda_{j,d}^{-1},d, \vp))^\tau
+ \ge \frac{(j-1)^\tau}{C_{\vp}^\tau}.
 \]
@@
 \sum_{j=j_d^*}^\infty \frac{1}{T(\lambda_{j,d}^{-1},d, \tau p,\tau q)}
-\le K_{p,q,\tau}\, C_{p,q}^\tau \sum_{j=j_d^*}^\infty \frac{1}{(j-1)^\tau}
-\peter{\le K_{p,q,\tau}\, C_{p,q}^\tau \, \zeta(\tau)}
+\le K_{\vp,\tau}\, C_{\vp}^\tau \sum_{j=j_d^*}^\infty \frac{1}{(j-1)^\tau}
+\peter{\le K_{\vp,\tau}\, C_{\vp}^\tau \, \zeta(\tau)}
 <\infty.
@@
 \[
-\sup_{d\in\naturals} \sum_{j=j_d^*}^\infty \frac{1}{T(\lambda_{j,d}^{-1},d, \tau p,\tau q)} \le K_{p,q,\tau}\, C_{p,q}^\tau \, \zeta(\tau) < \infty.
+\sup_{d\in\naturals} \sum_{j=j_d^*}^\infty \frac{1}{T(\lambda_{j,d}^{-1},d, \tau p,\tau q)} \le K_{\vp,\tau}\, C_{\vp}^\tau \, \zeta(\tau) < \infty.
 \]
@@
 \[
- j_d^* = \lfloor C_{p,q}\, T(0,d,p,q)\rfloor +1 \le \lfloor C_{p,q}^\tau\, T(0,d,\tau p,\tau q)\rfloor +1.
+ j_d^* = \lfloor C_{\vp}\, T(0,d,\vp)\rfloor +1 \le \lfloor C_{\vp}^\tau\, T(0,d,\tau p,\tau q)\rfloor +1.
 \]
@@
 \[
- T(\varepsilon^{-1},d,p,q)= (\max\{\varepsilon^{-1},1\})^p .
+ T(\varepsilon^{-1},d,\vp)= (\max\{\varepsilon^{-1},1\})^p .
 \]
@@
 \[
- T(\varepsilon^{-1},d,p,q)= (\max\{\varepsilon^{-1},1\})^p\, d^q.
+ T(\varepsilon^{-1},d,\vp)= (\max\{\varepsilon^{-1},1\})^p\, d^q.
 \]
@@
 \[
- \sup_{d\in\naturals} \sum_{i=L(p,q_1) d^{q_1}}^\infty (\min\{\lambda_{i,d},1\})^p d^{-q} < \infty.
+ \sup_{d\in\naturals} \sum_{i=L(\vp) d^{q_1}}^\infty (\min\{\lambda_{i,d},1\})^p d^{-q} < \infty.
 \]

### 2023-03-12 GeneralizedTractability_230310.tex
Updates from Overleaf
Fred M2 2023 Mac Updates

@@
     \begin{equation} \label{eq:comp_equiv}
-    \comp(\varepsilon, d) &= \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon\} = \min \biggl\{n \in \natzero : \frac{1}{T(\lambda_{n+1,d}^{-1},d',\vp)}\le \frac{1}{T(\varepsilon^{-1},d',\vp) }\biggr\},
+    \comp(\varepsilon, d) = \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon\} = \min \biggl\{n \in \natzero : \frac{1}{T(\lambda_{n+1,d}^{-1},d',\vp)}\le \frac{1}{T(\varepsilon^{-1},d',\vp) }\biggr\},
 \end{equation}
@@
 \begin{equation*}
-	K_{\vp,\tau}\,T (\lambda_{j,d}^{-1},1,\tau \vp) \ge
-	[T(\lambda_{j,d}^{-1},1, \vp)]^\tau
+	K_{\vp,\tau}\,T (\lambda_{j,d}^{-1},d,\tau \vp) \ge
+	[T(\lambda_{j,d}^{-1},d, \vp)]^\tau
 	\ge
@@
 \begin{multline*}
-	\sup_{d\in\naturals} \sum_{j=L(\tau\vp)}^\infty \frac{1}{T (\lambda_{j,d}^{-1},1, \tau \vp)} \le
-	\sup_{d\in\naturals} \sum_{j=L(\vp)}^\infty \frac{1}{T (\lambda_{j,d}^{-1},1, \tau \vp)} \\
+	\sup_{d\in\naturals} \sum_{j=j(\infty,d,\vp)}^\infty \frac{1}{T (\lambda_{j,d}^{-1},d, \tau \vp)} \le
+	\sup_{d\in\naturals} \sum_{j=j(\infty,d,\vp)}^\infty \frac{1}{T (\lambda_{j,d}^{-1},d, \tau \vp)} \\
 	\le K_{\vp,\tau}\, C_{\vp}^\tau
-	\sum_{j=L(\vp)}^\infty \frac{1}{(j-1)^\tau} \le
+	\sum_{j=j(\infty,d,\vp)}^\infty \frac{1}{(j-1)^\tau} \le
 	K_{\vp,\tau}\, C_{\vp}^\tau\, \zeta (\tau) < \infty,
@@
 
-We know that
-\[
-\lambda_{\comp(\varepsilon,d)+1,d}\le \varepsilon.
-\]
-Since the eigenvalues $\lambda_{j,d}$ are non-increasing, we have
-\begin{equation}\label{eq:lambda_K4}
-\lambda_{\lfloor C_{\vp}\, T(\varepsilon^{-1},d,\vp)\rfloor +1,d}\le \varepsilon.
-\end{equation}
-Let
-\[
-j=j (\varepsilon):= \lfloor C_{\vp}\, T(\varepsilon^{-1},d,\vp)\rfloor +1.
-\]
-If we vary $\varepsilon\in (0,\infty)$, we see that $j=j_d^*, j_d^*+1, j_d^*+2,\ldots$, where
-\[
-  j_d^*=\lfloor C_{\vp}\, T(0,d,\vp)\rfloor +1
-\]
-Note that
-\[
-j\le C_{\vp}\, T(\varepsilon^{-1},d,\vp) +1.
-\]
-Due to our assumptions, we know that
-$T(\cdot,d,\vp)$ is increasing in the first argument if
-we keep $p$ and $q$ fixed.
-
-Then, by \eqref{eq:lambda_K4},
-\[
-j \le C_{\vp}\, T(\varepsilon^{-1},d,\vp) +1 \le C_{\vp}\, T(\lambda_{j,d}^{-1},d,\vp) +1,
-\]
-and the latter chain of inequalities holds for all $j\ge j_d^*$.
-
-This implies
-\[
-T(\lambda_{j,d}^{-1},d, \vp) \ge \frac{j-1}{C_{\vp}}.
-\]
-This, in turn, implies, for any $\tau>1$, that
-\[
- (T(\lambda_{j,d}^{-1},d,\vp))^\tau \ge \frac{(j-1)^\tau}{C_{\vp}^\tau},
-\]
-which yields
-\[
- K_{\vp,\tau}\, T (\lambda_{j,d}^{-1},d,\tau p,\tau q) \ge (T(\lambda_{j,d}^{-1},d, \vp))^\tau
- \ge \frac{(j-1)^\tau}{C_{\vp}^\tau}.
-\]
-This then implies
-\[
-\sum_{j=j_d^*}^\infty \frac{1}{T(\lambda_{j,d}^{-1},d, \tau p,\tau q)}
-\le K_{\vp,\tau}\, C_{\vp}^\tau \sum_{j=j_d^*}^\infty \frac{1}{(j-1)^\tau}
-\peter{\le K_{\vp,\tau}\, C_{\vp}^\tau \, \zeta(\tau)}
-<\infty.
-\]
-\peter{
-Consequently,
-\[
-\sup_{d\in\naturals} \sum_{j=j_d^*}^\infty \frac{1}{T(\lambda_{j,d}^{-1},d, \tau p,\tau q)} \le K_{\vp,\tau}\, C_{\vp}^\tau \, \zeta(\tau) < \infty.
-\]
-}
 Note now that, \peter{for any $d\in\naturals$,}

### 2023-03-12 GeneralizedTractability_230310.tex
Fred M2 2023 Mac Updates

@@
 where $\zeta$ denotes the Riemann zeta function.
-This yields \eqref{eq:strong_tractiff3} with $p$ replaced by $\tau p$, and so we see the necessity of $\eqref{eq:strong_tractiff3}$.
 
@@
 \[
- j_d^* = \lfloor C_{\vp}\, T(0,d,\vp)\rfloor +1 \le \lfloor C_{\vp}^\tau\, T(0,d,\tau p,\tau q)\rfloor +1.
+ j(\infty,d,\vp) = \lfloor C_{\vp}\, T(0,d,\vp)\rfloor +1 \le \lfloor C_{\vp}^\tau\, T(0,d,\tau \vp)\rfloor +1.
 \]
-So, there exists $L(\tau p,\tau q)$ such that
+So, there exists $L(\tau \vp)$ such that
 \[
-\peter{\sup_{d\in\naturals}}\,\, \sum_{j=\lceil L(\tau p,\tau q) T(0,d,\tau p,\tau q)\rceil}^\infty \frac{1}{T(\lambda_{j,d}^{-1},d, \tau p,\tau q)}<\infty.
+\peter{\sup_{d\in\naturals}}\,\, \sum_{j=\lceil L(\tau \vp) T(0,d,\tau \vp)\rceil}^\infty \frac{1}{T(\lambda_{j,d}^{-1},d, \tau\vp)}<\infty.
 \]
+\fred{Fred:  Not sure how $C_{\vp}^\tau$ becomes $L(\tau \vp)$?}
 
-This yields \eqref{eq:tractiff4} with $p$ replaced by $\tau p$ and $q$ and $q_1$ replaced by $\tau q$, and so we see the necessity of $\eqref{eq:tractiff4}$.
+This yields \eqref{eq:tractiff4} with $\vp$ replaced by $\tau \vp$, and so we see the necessity of $\eqref{eq:tractiff4}$.
+
+\bigskp
+
+\noindent \textbf{Optimality:}
+\fred{Not sure how to make optimality works because for sufficiency $\vp$ turns into $2\vp$.}
 

### 2023-03-23 GeneralizedTractability_230310.tex
Updates from Overleaf

@@
 
-If \eqref{eq:tract_def} holds for some $\vp$, it clearly holds for larger, $\vp$.  We are often interested in the optimal or smallest $\vp$ for which \eqref{eq:tract_def} holds.  Let
+If \eqref{eq:tract_def} holds for some $\vp$, it clearly holds for larger, $\vp$.
+We are often interested in the optimal or smallest $\vp$ for which \eqref{eq:tract_def} holds.
+Define the closures of the sets of parameters for which our (strong) tractability conditions hold:
 \begin{equation*}
@@
 
-Certain common notions of tractability are covered by the general situation described above
+Certain common notions of tractability are covered by the general situation described above.
 \begin{equation*}
@@
        \comp(\varepsilon,d)
-       & = 1 + T(\varepsilon^{-1},1, \vp) \left [ \sum_{i=1}^{L(\vp)-1} \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}
-       + \underbrace{\sum_{i=L(p)}^\infty \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}}_{\le S(p) <\infty\ \text{by \eqref{eq:strong_tractiff3}} }\right] \\
+       & = 1 + T(\varepsilon^{-1},1, \vp) \Biggl [ \sum_{i=1}^{L(\vp)-1} \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}
+       + \underbrace{\sum_{i=L(p)}^\infty \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}}_{\le S(p) <\infty\ \text{by \eqref{eq:strong_tractiff3}} }\Biggr] \\
        & \le 1+ T(\varepsilon^{-1},1,\vp) \underbrace{\left[\frac{(L(p)-1)}{T(\lambda_{\max}^{-1},1,\vp)} + S(\vp)\right]}_{=:C_1(\vp)}\\
@@
 j (\varepsilon,\vp):= \lfloor C_{\vp}\, T(\varepsilon^{-1},1,\vp)\rfloor +1, \quad
- L(\vp):= j (\infty,\vp).
+j (\infty,\vp) = \lim_{\varepsilon \to \infty} j (\varepsilon,\vp) .
 \]
@@
 \end{equation*}
-Summing both sides of the inequality yields and noting that $L(\vp) \le L(\tau\vp)$, it follows that
-\begin{multline*}
-\sup_{d\in\naturals} \sum_{j=L(\tau\vp)}^\infty \frac{1}{T (\lambda_{j,d}^{-1},1, \tau \vp)} \le
-\sup_{d\in\naturals} \sum_{j=L(\vp)}^\infty \frac{1}{T (\lambda_{j,d}^{-1},1, \tau \vp)} \\
+Summing both sides of the inequality yields it follows that
+\begin{equation*}
+\sup_{d\in\naturals} \sum_{j=j (\infty,\vp)}^\infty \frac{1}{T (\lambda_{j,d}^{-1},1, \tau \vp)}
 \le K_{\vp,\tau}\, C_{\vp}^\tau
-\sum_{j=L(\vp)}^\infty \frac{1}{(j-1)^\tau} \le
+\sum_{j=j (\infty,\vp)}^\infty \frac{1}{(j-1)^\tau} \le
 K_{\vp,\tau}\, C_{\vp}^\tau\, \zeta (\tau) < \infty,
-\end{multline*}
+\end{equation*}
 where $\zeta$ denotes the Riemann zeta function.
-This yields \eqref{eq:strong_tractiff3} with $p$ replaced by $\tau p$, and so we see the necessity of $\eqref{eq:strong_tractiff3}$.
+This yields \eqref{eq:strong_tractiff3} with $\vp$ replaced by $\vp' = \tau \vp$ and $L(\vp') = j (\infty,\vp)$, and so we see the necessity of $\eqref{eq:strong_tractiff3}$.
 
@@
 \begin{equation*}
-	 \comp(\varepsilon,d)} \le 1 + T(\varepsilon^{-1},d,\vp) \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}
+	 \comp(\varepsilon,d) \le 1 + T(\varepsilon^{-1},d,\vp) \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}
 \end{equation*}
@@
 \[
-\comp(\varepsilon,d)\le C_{\vp}\, (T(\varepsilon^{-1},d,\vp) \qquad \forall \varepsilon > 0,  \ d \in \naturals.
+\comp(\varepsilon,d)\le C_{\vp}\, T(\varepsilon^{-1},d,\vp) \qquad \forall \varepsilon > 0,  \ d \in \naturals.
 \]
@@
 Summing both sides of the inequality yields and noting that $L(\vp) \le L(\tau\vp)$, it follows that
+\peter{(Peter: Why does $L(\cdot)$ ocur here?)} \fred{Because I got lost a bit.}
+
 \begin{multline*}
@@
 
+\peter{Peter: You are right. We could probably solve this by just saying above that 
+\[
+ j(\infty,d,\vp) = \lfloor C_{\vp}\, T(0,d,\vp)\rfloor +1 \le \lfloor C_{\vp}\, T(0,d,\tau \vp)\rfloor +1,
+\]
+and then introduce $L(\tau \vp)$ to bound $C_{\vp}$ and also incorporate the ``+1''?
+}
+
 This yields \eqref{eq:tractiff4} with $\vp$ replaced by $\tau \vp$, and so we see the necessity of $\eqref{eq:tractiff4}$.
 
-\bigskp
+\bigskip
 

### 2023-03-23 GeneralizedTractability_230310.tex
Updates from Overleaf

@@
 \begin{theorem}\label{thm_main_strong_tract2}
-A problem is strongly $T$-tractable iff there exists $\vp \in [\vzero, \boldsymbol{\infty})$ and an integer $L(\vp) > 0$ such that
+A problem is strongly $T$-tractable iff there exists $\vp \in [\vzero, \boldsymbol{\infty})$ and an integer $L_{\vp} > 0$ such that
 \begin{equation} \label{eq:strong_tractiff3}
-     S(\vp):=\sup_{d \in \naturals} \sum_{i = L(\vp)}^\infty \frac{1}{T(\lambda_{i,d}^{-1},1,\vp)} < \infty.
+     S(\vp):=\sup_{d \in \naturals} \sum_{i = L_{\vp}}^\infty \frac{1}{T(\lambda_{i,d}^{-1},1,\vp)} < \infty.
 \end{equation}
@@
        \comp(\varepsilon,d)
-       & = 1 + T(\varepsilon^{-1},1, \vp) \Biggl [ \sum_{i=1}^{L(\vp)-1} \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}
+       & = 1 + T(\varepsilon^{-1},1, \vp) \Biggl [ \sum_{i=1}^{L_{\vp}-1} \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}
        + \underbrace{\sum_{i=L(p)}^\infty \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}}_{\le S(p) <\infty\ \text{by \eqref{eq:strong_tractiff3}} }\Biggr] \\
@@
 \end{align*}
-for some suitably chosen $C_{\vp}>0$. This means that we have strong $T$-tractability via \eqref{eq:strong_tract_def}, and verifies sufficiency of \eqref{eq:strong_tractiff3}.
+for some suitably chosen $C_{\vp}>0$. This means that we have strong $T$-tractability via \eqref{eq:strong_tract_def}, and verifies the sufficiency of \eqref{eq:strong_tractiff3}.
 
@@
 where $\zeta$ denotes the Riemann zeta function.
-This yields \eqref{eq:strong_tractiff3} with $\vp$ replaced by $\vp' = \tau \vp$ and $L(\vp') = j (\infty,\vp)$, and so we see the necessity of $\eqref{eq:strong_tractiff3}$.
+This yields \eqref{eq:strong_tractiff3} with $\vp$ replaced by $\vp' = \tau \vp$ and $L_{\vp'} = j (\infty,\vp)$, and so we see the necessity of $\eqref{eq:strong_tractiff3}$.
 
@@
 
-If $\vp^* \in \cp_{\textup{strct}}$, then \eqref{eq:strong_tract_def} holds for all $\vp \in (\vp^*,\vinfty)$.
-By the argument to prove the necessary condition, it follows that \eqref{eq:strong_tractiff3} must also hold for all $\vp \in (\vp^*,\vinfty)$, so $\vp^* \in \widetilde{\cp}_{\textup{strct}}$.
-Conversely, if $\vp^* \in \widetilde{\cp}_{\textup{strct}}$, then \eqref{eq:strong_tractiff3}  holds for all $\vp \in (\vp^*,\vinfty)$.
-By the argument to prove the sufficient condition, it follows that \eqref{eq:strong_tract_def} must also hold for all $\vp \in (\vp^*,\vinfty)$, so $\vp^* \in \cp}_{\textup{strct}}$.
+First we show  that if $\vp^* \in \cp_{\textup{strct}}$, then $\vp^* \in \widetilde{\cp}_{\textup{strct}}$.
+If $\vp^* \in \cp_{\textup{strct}}$, then \eqref{eq:strong_tract_def} must hold for all $\vp' \in (\vp^*,\vinfty)$.
+For any $\vp' \in (\vp^*,\vinfty)$, we may choose $\vp$ and $\tau$ such that $\vp^* < \vp < \vp' = \tau \vp$.
+Since $\vp > \vp^*$, \eqref{eq:strong_tract_def} also holds for $\vp$, and it follows that \eqref{eq:strong_tractiff3} must hold for $\vp'$ by the proof of necessity above.
+Thus, $\vp^* \in \widetilde{\cp}_{\textup{strct}}$.
+
+Next we show that if $\vp^* \in \widetilde{\cp}_{\textup{strct}}$, then $\vp^* \in \cp_{\textup{strct}}$.
+If $\vp^* \in \widetilde{\cp}_{\textup{strct}}$, then \eqref{eq:strong_tractiff3}  holds for all $\vp \in (\vp^*,\vinfty)$.
+By the argument to prove the sufficient condition above, it follows that \eqref{eq:strong_tract_def} must also hold for all $\vp \in (\vp^*,\vinfty)$.
+Thus, $\vp^* \in \cp}_{\textup{strct}}$.
 

### 2023-03-30 GeneralizedTractability_230310.tex
Updates from Overleaf

@@
 \]
-A tractability function is a simple function that provides an upper bound on the computational complexity of a problem
-A problem is $T$-tractable with parameter $\vp$ iff there exists a positive constant $C_{\vp}$ such that
+A tractability function is a function of simple form that provides an upper bound on the computational complexity of a problem.
+A problem is defined as $T$-tractable with parameter $\vp$ iff there exists a positive constant $C_{\vp}$ such that
 \begin{equation} \label{eq:tract_def}
@@
 A problem is \emph{strongly}
-$T$-tractable with parameter $\vp$ iff the complexity is independent of the dimension, that is, there exists a positive constant $C_{\vp}$ such that
+$T$-tractable with parameter $\vp$ iff the complexity is independent of the dimension of the problem, that is, there exists a positive constant $C_{\vp}$ such that
 \begin{equation} \label{eq:strong_tract_def}
@@
 which implies that the problem does not become easier by decreasing the tolerance, $\varepsilon$, or increasing the dimension, $d$.
+Furthermore, increasing $\vp$ does not decrease $T(\cdot, \cdot, \vp)$.
 Since there are an infinite number of positive eigenvalues, it also make sense to assume that
@@
 \end{equation}
-There is a technical assumption required for our analysis.  There exists a $K_{\vp,\tau}$ depending on $\vp$ and $\tau$, but  independent of $\varepsilon$ and $d$, such that
+Finally, there is a technical assumption required for our analysis.  There exists a $K_{\vp,\tau}$ depending on $\vp$ and $\tau$, but  independent of $\varepsilon$ and $d$, such that
 \begin{equation} \label{eq:ptauassume}
@@
 	\label{eq:Poptdef}
-	\mathcal{P}_{\textup{opt}} : = \{\vp^* \in \cp_{\textup{trct}} :  \vp* \notin [\vp^\dagger,\boldsymbol{\infty}) \ \forall \vp^\dagger \in  \cp_{\textup{trct}} \setminus \{\vp^*\} \}, \\
+	\mathcal{P}_{\textup{opt}} : = \{\vp^* \in \cp_{\textup{trct}} :  \vp^* \notin [\vp^\dagger,\boldsymbol{\infty}) \ \forall \vp^\dagger \in  \cp_{\textup{trct}} \setminus \{\vp^*\} \}, \\
 	\label{eq:Psoptdef}
-	\mathcal{P}_{\textup{sopt}} : = \{\vp^* \in \cp_{\textup{strct}} :  \vp* \notin [\vp^\dagger,\boldsymbol{\infty}) \ \forall \vp^\dagger \in  \cp_{\textup{strct}} \setminus \{\vp^*\} \}.
+	\mathcal{P}_{\textup{sopt}} : = \{\vp^* \in \cp_{\textup{strct}} :  \vp^* \notin [\vp^\dagger,\boldsymbol{\infty}) \ \forall \vp^\dagger \in  \cp_{\textup{strct}} \setminus \{\vp^*\} \}.
 \end{gather}
@@
 In the sections below we prove necessary and sufficient conditions on tractability as generally defined in \eqref{eq:tract_def} and \eqref{eq:strong_tract_def}.
-These conditions  that involve the boundedness of sums defined in terms of $\{T(\lambda_{i,d}^{-1},\cdot, \cdot)\}_{i=1}^\infty$.
-In practice, it may be easier to verify whether or not these conditions hold than to deal with \eqref{eq:comp_def} directly.
+These conditions involve the boundedness of sums defined in terms of $\{T(\lambda_{i,d}^{-1},\cdot, \cdot)\}_{i=1}^\infty$.
+In practice, it may be easier to verify whether or not these conditions hold than to verify \eqref{eq:comp_def} directly.
 
@@
 \begin{equation} \label{eq:strong_tractiff3}
-     S(\vp):=\sup_{d \in \naturals} \sum_{i = L_{\vp}}^\infty \frac{1}{T(\lambda_{i,d}^{-1},1,\vp)} < \infty.
+     S_{\vp}:=\sup_{d \in \naturals} \sum_{i = L_{\vp}}^\infty \frac{1}{T(\lambda_{i,d}^{-1},1,\vp)} < \infty.
 \end{equation}
@@
 We make the first part of the argument in some generality so that it can be reused in the proof of Theorem \ref{thm_main_tract2} for tractability.
-Given that $T$ is increasing in its arguments, we have the following equivalent expression for the complexity:
-    \begin{equation} \label{eq:comp_equiv}
-    \comp(\varepsilon, d) = \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon\} = \min \biggl\{n \in \natzero : \frac{1}{T(\lambda_{n+1,d}^{-1},d',\vp)}\le \frac{1}{T(\varepsilon^{-1},d',\vp) }\biggr\},
-\end{equation}
-for any $d' \in \naturals$.
 
-Also since the $\lambda_{i,d}$ are non-increasing in $i$, it follows that the $T(\lambda_{i,d}^{-1},d',\vp)$ are non-decreasing in $i$. In particular, for all $n\in \mathbb{N}$, we have
+Since the $\lambda_{i,d}$ are non-increasing in $i$, it follows that the $T(\lambda_{i,d}^{-1},d',\vp)$ are non-decreasing in $i$. In particular, for all $n\in \mathbb{N}$, we have
 \begin{align*}
@@
 Thus, we can conclude from the previous line that
-\begin{multline*}
+\begin{multline} \label{eq:implicate_a}
     n \ge T(\varepsilon^{-1},d',\vp) \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} \\
@@
    \frac 1n \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d',\vp) } \le \frac{1}{T(\varepsilon^{-1},d',\vp)} \qquad \forall \varepsilon > 0, \ d,d' \in \naturals.
-\end{multline*}
-This last inequality together with \eqref{eq:comp_equiv} implies an upper bound on the complexity: of
+\end{multline}
+
+Moreover, given that $T$ is increasing in its arguments, we have the following equivalent expression for the complexity via \eqref{eq:comp_def}:
+    \begin{equation*} %\label{eq:comp_equiv}
+    \comp(\varepsilon, d) = \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon\} = \min \biggl\{n \in \natzero : \frac{1}{T(\lambda_{n+1,d}^{-1},d',\vp)}\le \frac{1}{T(\varepsilon^{-1},d',\vp) }\biggr\},
+\end{equation*}
+for any $d' \in \naturals$.  Combining this expression for the complexity with the implication in \eqref{eq:implicate_a}, we can conclude from the previous line that
 \begin{equation} \label{eq:compUP}
@@
        & = 1 + T(\varepsilon^{-1},1, \vp) \Biggl [ \sum_{i=1}^{L_{\vp}-1} \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}
-       + \underbrace{\sum_{i=L(p)}^\infty \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}}_{\le S(p) <\infty\ \text{by \eqref{eq:strong_tractiff3}} }\Biggr] \\
-       & \le 1+ T(\varepsilon^{-1},1,\vp) \underbrace{\left[\frac{(L(p)-1)}{T(\lambda_{\max}^{-1},1,\vp)} + S(\vp)\right]}_{=:C_1(\vp)}\\
-       & = 1+ T(\varepsilon^{-1},1,\vp) C_1 (p)\\
-       &\le C_{\vp} T(\varepsilon^{-1},1,\vp),
+       + \underbrace{\sum_{i=L_{\vp}}^\infty \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}}_{\le S_{\vp} <\infty\ \text{by \eqref{eq:strong_tractiff3}} }\Biggr] \\
+       & \le 1+ T(\varepsilon^{-1},1,\vp) \underbrace{\left[\frac{(L(p)-1)}{T(\lambda_{\max}^{-1},1,\vp)} + S_{\vp}\right]}_{=:C_{1,\vp}}\\
+       & = 1+ T(\varepsilon^{-1},1,\vp) C_{1,\vp}\\
+       & \le \underbrace{2 C_{1,\vp}}_{\text{since } T(\varepsilon^{-1},1,\vp) \ge 1} T(\varepsilon^{-1},1,\vp)
+       = \underbrace{C_{\vp}}_{:=2 C_{1,\vp}}T(\varepsilon^{-1},1,\vp).
 \end{align*}
-for some suitably chosen $C_{\vp}>0$. This means that we have strong $T$-tractability via \eqref{eq:strong_tract_def}, and verifies the sufficiency of \eqref{eq:strong_tractiff3}.
+This means that we have strong $T$-tractability via \eqref{eq:strong_tract_def}, and verifies the sufficiency of \eqref{eq:strong_tractiff3}.
 
@@
 
-For $\varepsilon$ taking on all positive values, $j(\varepsilon,\vp)$ takes on all values greater than or equal to $L(\vp)$, so
+For $\varepsilon$ taking on all positive values, $j(\varepsilon,\vp)$ takes on all values greater than or equal to $j(\infty,\vp)$, so
 \[
-j\le C_{\vp}\, T(\varepsilon^{-1},1,\vp)+1 \le C_{\vp} T(\lambda_{j,d}^{-1},1,\vp)+1, \qquad \forall j \ge L(\vp).
+j\le C_{\vp} T(\lambda_{j,d}^{-1},1,\vp)+1, \qquad \forall j \ge j(\infty,\vp).
 \]
@@
  \ge
-  \left[\frac{(j-1)}{C_{\vp}}\right]^\tau \qquad \forall j \ge L(\vp)
+  \left[\frac{(j-1)}{C_{\vp}}\right]^\tau \qquad \forall j \ge j(\infty,\vp)
 \end{equation*}
@@
 
+\subsection{Tractability} \label{sec:tractability}
+
 \bigskip
@@
 \begin{equation} \label{eq:tractiff4}
-     S(\vp):=\sup_{d \in \naturals}
+     S_{\vp}:=\sup_{d \in \naturals}
      \sum_{i = \lceil L(\vp)\, T(0,d,\vp) \rceil}^\infty \frac{1}{T(\lambda^{-1}_{i,d},d,\vp)}< \infty.
@@
        & = 1 + T(\varepsilon^{-1},d,\vp) \Biggl [ \sum_{i=1}^{J(\vp,d) -1} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}
-       + \underbrace{\sum_{i=J(\vp,d)}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}}_{\le S(\vp) \text{ by \eqref{eq:tractiff4}}} \Biggr ] \\
-       & \le 1+ T(\varepsilon^{-1},d,\vp)\left[ \frac{J(\vp,d)-1}{T(\lambda_{\max}^{-1},d,\vp)} + S(\vp)\right]
+       + \underbrace{\sum_{i=J(\vp,d)}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}}_{\le S_{\vp} \text{ by \eqref{eq:tractiff4}}} \Biggr ] \\
+       & \le 1+ T(\varepsilon^{-1},d,\vp)\left[ \frac{J(\vp,d)-1}{T(\lambda_{\max}^{-1},d,\vp)} + S_{\vp}\right]
         \\
-       & \le 1+ T(\varepsilon^{-1},d,\vp)\left[L(\vp)\, T(0,d,\vp) + S(\vp)\right] \qquad \text{since } T(\lambda_{\max}^{-1},d,\vp) \ge 1\\
-       & \le 1+L(\vp)\,T(\varepsilon^{-1},d,\vp) T(0,d,\vp) + S(\vp)\, T(\varepsilon^{-1},d,\vp)\\
-       & \le 1+L(\vp)\,T(\varepsilon^{-1},d,\vp) T(\varepsilon^{-1},d,\vp) + S(\vp)\, T(\varepsilon^{-1},d,\vp)\\
-       & \le 1+L(\vp)\,K_{\vp,2} T(\varepsilon^{-1},d,2\vp)  + S(\vp)\, T(\varepsilon^{-1},d,\vp)  \qquad \text{by \eqref{eq:ptauassume}}\\
+       & \le 1+ T(\varepsilon^{-1},d,\vp)\left[L(\vp)\, T(0,d,\vp) + S_{\vp}\right] \qquad \text{since } T(\lambda_{\max}^{-1},d,\vp) \ge 1\\
+       & \le 1+L(\vp)\,T(\varepsilon^{-1},d,\vp) T(0,d,\vp) + S_{\vp}\, T(\varepsilon^{-1},d,\vp)\\
+       & \le 1+L(\vp)\,T(\varepsilon^{-1},d,\vp) T(\varepsilon^{-1},d,\vp) + S_{\vp}\, T(\varepsilon^{-1},d,\vp)\\
+       & \le 1+L(\vp)\,K_{\vp,2} T(\varepsilon^{-1},d,2\vp)  + S_{\vp}\, T(\varepsilon^{-1},d,\vp)  \qquad \text{by \eqref{eq:ptauassume}}\\
        & \le C_{2}(2\vp) \,T(\varepsilon^{-1},d,2\vp)

### 2023-03-30 GeneralizedTractability_230310.tex
Fred Office computer updates

@@
 By the argument to prove the sufficient condition above, it follows that \eqref{eq:strong_tract_def} must also hold for all $\vp \in (\vp^*,\vinfty)$.
-Thus, $\vp^* \in \cp}_{\textup{strct}}$.
+Thus, $\vp^* \in \cp_{\textup{strct}}$.
 
@@
 
-\bigskip
+The argument proving equivalent conditions for tractability is similar to, but somewhat more involved than the proof of Theorem \ref{thm_main_strong_tract2}.
+Moreover, the specification of the set of optimal parameters is not as precise as in Theorem \ref{thm_main_strong_tract2}.
 
 \begin{theorem}\label{thm_main_tract2}
-A problem is $T$-tractable iff there exist $\vp\ge \vzero$ and a constant $L(\vp) > 0$ such that
+A problem is $T$-tractable iff there exist $\vp\ge \vzero$ and a constant $L_{\vp} > 0$ such that
 \begin{equation} \label{eq:tractiff4}
      S_{\vp}:=\sup_{d \in \naturals}
-     \sum_{i = \lceil L(\vp)\, T(0,d,\vp) \rceil}^\infty \frac{1}{T(\lambda^{-1}_{i,d},d,\vp)}< \infty.
+     \sum_{i = \lceil L_{\vp}\, T(0,d,\vp) \rceil}^\infty \frac{1}{T(\lambda^{-1}_{i,d},d,\vp)}< \infty.
 \end{equation}
-If \eqref{eq:tractiff4} holds for some $\vp$, let  $\widetilde{\cp}_{\textup{trct}} : = \{\vp^* : \eqref{eq:tractiff4} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty})\}$.
+If \eqref{eq:tractiff4} holds for some $\vp$, let  $\widetilde{\cp}_{\textup{trct}} : = \{\vp^* : \eqref{eq:tractiff4} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty})\}$, and   $\widehat{\cp}_{\textup{trct}} : = \{\vp^* : 2\vp \in \widetilde{\cp}_{\textup{trct}}\}$.
 Then $\cp_{\textup{trct}} = \widetilde{\cp}_{\textup{trct}}$, and the set of optimal strong tractability parameters is
@@
 \cp_{\textup{opt}} =
-\{\vp^* \in \widetilde{\cp}_{\textup{trct}} :  \vp* \notin [\vp^\dagger,\boldsymbol{\infty}) \ \forall \vp^\dagger \in  \widetilde{\cp}_{\textup{trct}} \setminus \{\vp^*\} \}.
+\{\vp^* \in \widetilde{\cp}_{\textup{trct}} :  \vp^* \notin [\vp^\dagger,\boldsymbol{\infty}) \ \forall \vp^\dagger \in  \widetilde{\cp}_{\textup{trct}} \setminus \{\vp^*\} \}.
 \]\end{theorem}
@@
 
-Let $J(\vp,d): = \lceil L(\vp)\, T(0,d,\vp)\rceil$.  Then this upper bound on the complexity can be further bounded above by
+Let $J(\vp,d): = \lceil L_{\vp}\, T(0,d,\vp)\rceil$.  Then this upper bound on the complexity can be further bounded above by
 \begin{align*}
@@
         \\
-       & \le 1+ T(\varepsilon^{-1},d,\vp)\left[L(\vp)\, T(0,d,\vp) + S_{\vp}\right] \qquad \text{since } T(\lambda_{\max}^{-1},d,\vp) \ge 1\\
-       & \le 1+L(\vp)\,T(\varepsilon^{-1},d,\vp) T(0,d,\vp) + S_{\vp}\, T(\varepsilon^{-1},d,\vp)\\
-       & \le 1+L(\vp)\,T(\varepsilon^{-1},d,\vp) T(\varepsilon^{-1},d,\vp) + S_{\vp}\, T(\varepsilon^{-1},d,\vp)\\
-       & \le 1+L(\vp)\,K_{\vp,2} T(\varepsilon^{-1},d,2\vp)  + S_{\vp}\, T(\varepsilon^{-1},d,\vp)  \qquad \text{by \eqref{eq:ptauassume}}\\
+       & \le 1+ T(\varepsilon^{-1},d,\vp)\left[L_{\vp}\, T(0,d,\vp) + S_{\vp}\right] \qquad \text{since } T(\lambda_{\max}^{-1},d,\vp) \ge 1\\
+       & \le 1+L_{\vp}\,T(\varepsilon^{-1},d,\vp) T(0,d,\vp) + S_{\vp}\, T(\varepsilon^{-1},d,\vp)\\
+       & \le 1+L_{\vp}\,T(\varepsilon^{-1},d,\vp) T(\varepsilon^{-1},d,\vp) + S_{\vp}\, T(\varepsilon^{-1},d,\vp)\\
+       & \le 1+L_{\vp}\,K_{\vp,2} T(\varepsilon^{-1},d,2\vp)  + S_{\vp}\, T(\varepsilon^{-1},d,\vp)  \qquad \text{by \eqref{eq:ptauassume}}\\
        & \le C_{2}(2\vp) \,T(\varepsilon^{-1},d,2\vp)
@@
 \end{equation*}
-Summing both sides of the inequality yields and noting that $L(\vp) \le L(\tau\vp)$, it follows that
+Summing both sides of the inequality yields and noting that $L_{\vp} \le L(\tau\vp)$, it follows that
 \peter{(Peter: Why does $L(\cdot)$ ocur here?)} \fred{Because I got lost a bit.}
@@
 \[
- \sup_{d\in\naturals} \sum_{i=L(\vp) d^{q_1}}^\infty (\min\{\lambda_{i,d},1\})^p d^{-q} < \infty.
+ \sup_{d\in\naturals} \sum_{i=L_{\vp} d^{q_1}}^\infty (\min\{\lambda_{i,d},1\})^p d^{-q} < \infty.
 \]

### 2023-04-01 GeneralizedTractability_230310.tex
Fred M2 2023 Mac Updates polishing

@@
 
-Let $\cf_d$ and $\cg_d$ Hilbert spaces, and $\SOL_d : \cf_d \to \cg_d$ be a linear solution operator with adjoint $\SOL_d^*$ such that $\SOL_d^*\SOL_d : \cf_d \to \cf_d$ has eigenvalues and orthonormal eigenvectors
+Let $\cf_d$ and $\cg_d$ be Hilbert spaces, and $\SOL_d : \cf_d \to \cg_d$ be a linear solution operator with adjoint $\SOL_d^*$ such that $\SOL_d^*\SOL_d : \cf_d \to \cf_d$ has eigenvalues and orthonormal eigenvectors
 \[
@@
 \end{equation}
+The question is,``How hard is this problem as $\varepsilon$ tends to zero or as $d$ tends to infinity?''  We want to identify equivalent conditions in terms of the singular values that are easier to verify than dealing with the definition in \eqref{eq:comp_def}.
 
@@
 A tractability function is a function of simple form that provides an upper bound on the computational complexity of a problem.
+Some examples of tractability functions considered previously are provided in Section \ref{sec:examples}.
+
 A problem is defined as $T$-tractable with parameter $\vp$ iff there exists a positive constant $C_{\vp}$ such that
@@
 \end{equation}
-In this article we allow $\vp$ to be a scalar or vector as the situation requires.
+In this article we allow $\vp$ to be a scalar or vector as the situation dictates.
 
@@
 
-\section{Examples}
+\section{Examples} \label{sec:examples}
 

### 2023-04-01 GeneralizedTractability_230310.tex
Fred M2 2023 Mac Updates
Fred's Home Computer tweaking lower bound on T and Thm 1

@@
 
-\newcommand{\fred}[1]{\begingroup\color{blue}#1\endgroup}
+\newcommand{\fred}[1]{\begingroup\color{blue}Fred: #1\endgroup}
 \newcommand{\peter}[1]{\begingroup\color{purple}#1\endgroup}
@@
 \[
-T :(0,\infty) \times \mathbb{N} \times [0,\infty)^s \rightarrow [1,\infty),
+T :(0,\infty) \times \mathbb{N} \times [0,\infty)^s \rightarrow (0,\infty),
 \]
+\fred{I think that we do not need to bound $T$ away from $0$.}
 A tractability function is a function of simple form that provides an upper bound on the computational complexity of a problem.
-Some examples of tractability functions considered previously are provided in Section \ref{sec:examples}.
+Some examples of tractability functions commonly considered are provided in Section \ref{sec:examples}.
 
@@
 \begin{equation} \label{eq:ptauassume}
-	[T(\varepsilon^{-1},d,\vp)]^\tau \le K_{\vp,\tau} T(\varepsilon^{-1},d,\tau \vp),   \quad \forall \varepsilon \in (0,\infty), \ d \in \naturals, \ \vp\in[0,\infty)^s, \ \tau\in (1,\infty).
+	[T(\varepsilon^{-1},d,\vp)]^\tau \le K_{\vp,\tau} T(\varepsilon^{-1},d,\tau \vp),   \quad \forall \varepsilon \in (0,\infty), \ d \in \naturals, \ \vp\in[0,\infty)^s, \ \tau\in [1,\infty). 
 \end{equation}
@@
 \end{equation*}
-for any $d' \in \naturals$.  Combining this expression for the complexity with the implication in \eqref{eq:implicate_a}, we can conclude from the previous line that
+for any $d' \in \naturals$.  Combining this expression for the complexity with the implication in \eqref{eq:implicate_a} implies an upper bound on the complexity: \fred{think $1+$ not needed}
 \begin{equation} \label{eq:compUP}
 	\comp(\varepsilon,d)
-	\le 1 + T(\varepsilon^{-1},d',\vp) \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} \qquad \forall \varepsilon > 0, \ d, d' \in \naturals
+	\le T(\varepsilon^{-1},d',\vp) \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} \qquad \forall \varepsilon > 0, \ d, d' \in \naturals.
 \end{equation}
@@
        \comp(\varepsilon,d)
-       & = 1 + T(\varepsilon^{-1},1, \vp) \Biggl [ \sum_{i=1}^{L_{\vp}-1} \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}
+       & = T(\varepsilon^{-1},1, \vp) \Biggl [ \sum_{i=1}^{L_{\vp}-1} \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}
        + \underbrace{\sum_{i=L_{\vp}}^\infty \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}}_{\le S_{\vp} <\infty\ \text{by \eqref{eq:strong_tractiff3}} }\Biggr] \\
-       & \le 1+ T(\varepsilon^{-1},1,\vp) \underbrace{\left[\frac{(L(p)-1)}{T(\lambda_{\max}^{-1},1,\vp)} + S_{\vp}\right]}_{=:C_{1,\vp}}\\
-       & = 1+ T(\varepsilon^{-1},1,\vp) C_{1,\vp}\\
-       & \le \underbrace{2 C_{1,\vp}}_{\text{since } T(\varepsilon^{-1},1,\vp) \ge 1} T(\varepsilon^{-1},1,\vp)
-       = \underbrace{C_{\vp}}_{:=2 C_{1,\vp}}T(\varepsilon^{-1},1,\vp).
+       & \le T(\varepsilon^{-1},1,\vp) \underbrace{\left[\frac{(L(p)-1)}{T(\lambda_{\max}^{-1},1,\vp)} + S_{\vp}\right]}_{=:C_{\vp}}\\
+       & =  C_{\vp}T(\varepsilon^{-1},1,\vp).
+%       & \le \underbrace{2 C_{1,\vp}}_{\text{since } T(\varepsilon^{-1},1,\vp) \ge 1} T(\varepsilon^{-1},1,\vp)
+%       = \underbrace{C_{\vp}}_{:=2 C_{1,\vp}}T(\varepsilon^{-1},1,\vp).
 \end{align*}
@@
 \]
-Since the eigenvalues $\lambda_{j,d}$ are non-increasing, we have
+Since the sequence of eigenvalues $\lambda_{1,d}, \lambda_{2,d}, \ldots $ is non-increasing, we have
 \begin{equation}\label{eq:lambda_K_strong3}
@@
 j (\varepsilon,\vp):= \lfloor C_{\vp}\, T(\varepsilon^{-1},1,\vp)\rfloor +1, \quad
-j (\infty,\vp) = \lim_{\varepsilon \to \infty} j (\varepsilon,\vp) .
+j (\infty,\vp) = \lim_{\varepsilon \to \infty} j (\varepsilon,\vp) \ge 1 .
 \]
@@
 This implies via our technical assumption \eqref{eq:ptauassume} that
-\begin{equation*}
+\begin{gather*}
  K_{\vp,\tau}\,T (\lambda_{j,d}^{-1},1,\tau \vp) \ge
@@
  \ge
-  \left[\frac{(j-1)}{C_{\vp}}\right]^\tau \qquad \forall j \ge j(\infty,\vp)
-\end{equation*}
-Summing both sides of the inequality yields it follows that
-\begin{equation*}
+  \left[\frac{(j-1)}{C_{\vp}}\right]^\tau \qquad \forall j \ge j(\infty,\vp) \\
+ \frac{1}{T (\lambda_{j,d}^{-1},1,\tau \vp)} \le
+\frac{K_{\vp,\tau}\, C_{\vp}^\tau}{(j-1)^\tau}\qquad \forall j \ge j(\infty,\vp)
+\end{gather*}
+Summing both sides of this last inequality for $j$ from $j(\infty,\vp) \ge 1$ to $\inft$ yields 
+\begin{align*}
 \sup_{d\in\naturals} \sum_{j=j (\infty,\vp)}^\infty \frac{1}{T (\lambda_{j,d}^{-1},1, \tau \vp)}
-\le K_{\vp,\tau}\, C_{\vp}^\tau
-\sum_{j=j (\infty,\vp)}^\infty \frac{1}{(j-1)^\tau} \le
-K_{\vp,\tau}\, C_{\vp}^\tau\, \zeta (\tau) < \infty,
-\end{equation*}
+& \le  \sup_{d\in\naturals} \frac{1}{T (\lambda_{1,d}^{-1},1, \tau \vp)} + K_{\vp,\tau}\, C_{\vp}^\tau
+\sum_{j=2}^\infty \frac{1}{(j-1)^\tau} \\
+& \le\frac{1}{T (\lambda_{\max}^{-1},1, \tau \vp)} +  K_{\vp,\tau}\, C_{\vp}^\tau
+\zeta (\tau)  < \infty,
+\end{align*}
 where $\zeta$ denotes the Riemann zeta function.

### 2023-04-01 GeneralizedTractability_230310.tex

@@
 \end{equation}
-The question is,``How hard is this problem as $\varepsilon$ tends to zero or as $d$ tends to infinity?''  We want to identify equivalent conditions in terms of the singular values that are easier to verify than dealing with the definition in \eqref{eq:comp_def}.
+
+By definition, the complexity is non-decreasing  as $\varepsilon$ tends to zero.
+We also expect it to be non-decreasing as $d$ tends to infinity.
+This assumes that the Hilbert spaces are defined in such a way that $\lambda_{j,\cdot}$ is non-decreasing, although this assumption is not needed for our results.
+
+The question is,``How hard is this problem as $\varepsilon$ tends to zero or as $d$ tends to infinity?''  We want to bound the complexity in terms of a simple function of $\varepsilon$ and $d$ and identify simple conditions on the singular values that are equivalent to this bound holding.
 

### 2023-04-01 GeneralizedTractability_230310.tex
Updates from Overleaf

--- 2023-04-01 GeneralizedTractability_230310.tex
@@
 A tractability function is a function of simple form that provides an upper bound on the computational complexity of a problem.
-Some examples of tractability functions considered previously are provided in Section \ref{sec:examples}.
+Some examples of tractability functions commonly considered are provided in Section \ref{sec:examples}.
 

### 2023-04-02 GeneralizedTractability_230310.tex
Updates from Overleaf
Fred's Home Computer

--- 2023-04-01 GeneralizedTractability_230310.tex
@@
 \end{gather*}
-Summing both sides of this last inequality for $j$ from $j(\infty,\vp) \ge 1$ to $\inft$ yields 
+Summing both sides of this last inequality for $j$ from $j(\infty,\vp) \ge 1$ to $\infty$ yields 
 \begin{align*}
@@
 \begin{equation*}
-	 \comp(\varepsilon,d) \le 1 + T(\varepsilon^{-1},d,\vp) \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}
+	 \comp(\varepsilon,d) \le  T(\varepsilon^{-1},d,\vp) \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}
 \end{equation*}
@@
        \comp(\varepsilon,d)
-       & = 1 + T(\varepsilon^{-1},d,\vp) \Biggl [ \sum_{i=1}^{J(\vp,d) -1} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}
+       & = T(\varepsilon^{-1},d,\vp) \Biggl [ \sum_{i=1}^{J(\vp,d) -1} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}
        + \underbrace{\sum_{i=J(\vp,d)}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}}_{\le S_{\vp} \text{ by \eqref{eq:tractiff4}}} \Biggr ] \\
-       & \le 1+ T(\varepsilon^{-1},d,\vp)\left[ \frac{J(\vp,d)-1}{T(\lambda_{\max}^{-1},d,\vp)} + S_{\vp}\right]
+       & \le T(\varepsilon^{-1},d,\vp)\left[ \frac{J(\vp,d)-1}{T(\lambda_{\max}^{-1},d,\vp)} + S_{\vp}\right]
         \\
-       & \le 1+ T(\varepsilon^{-1},d,\vp)\left[L_{\vp}\, T(0,d,\vp) + S_{\vp}\right] \qquad \text{since } T(\lambda_{\max}^{-1},d,\vp) \ge 1\\
-       & \le 1+L_{\vp}\,T(\varepsilon^{-1},d,\vp) T(0,d,\vp) + S_{\vp}\, T(\varepsilon^{-1},d,\vp)\\
-       & \le 1+L_{\vp}\,T(\varepsilon^{-1},d,\vp) T(\varepsilon^{-1},d,\vp) + S_{\vp}\, T(\varepsilon^{-1},d,\vp)\\
-       & \le 1+L_{\vp}\,K_{\vp,2} T(\varepsilon^{-1},d,2\vp)  + S_{\vp}\, T(\varepsilon^{-1},d,\vp)  \qquad \text{by \eqref{eq:ptauassume}}\\
-       & \le C_{2}(2\vp) \,T(\varepsilon^{-1},d,2\vp)
+       & \le T(\varepsilon^{-1},d,\vp)\left[\frac{L_{\vp}\, T(0,d,\vp)}{T(\lambda_{\max}^{-1},d,\vp)} + S_{\vp}\right] \\
+       & \le\frac{L_{\vp}}{T(\lambda_{\max}^{-1},d,\vp)} \,T(\varepsilon^{-1},d,\vp) T(0,d,\vp) + S_{\vp}\, T(\varepsilon^{-1},d,\vp)\\
+       & \le\frac{L_{\vp}}{T(\lambda_{\max}^{-1},d,\vp)} \,T(\varepsilon^{-1},d,\vp) T(\varepsilon^{-1},d,\vp) + S_{\vp}\, T(\varepsilon^{-1},d,\vp)\\
+       & \le \frac{L_{\vp}\,K_{\vp,2}}{T(\lambda_{\max}^{-1},d,\vp)}  T(\varepsilon^{-1},d,2\vp)  + S_{\vp}\, T(\varepsilon^{-1},d,\vp)  \qquad \text{by \eqref{eq:ptauassume}}\\
+       & \le \underbrace{\left[\frac{L_{\vp}\,K_{\vp,2}}{T(\lambda_{\max}^{-1},d,\vp)} + S_{\vp}\right]}_{=:C_{2\vp}} \,T(\varepsilon^{-1},d,2\vp)
 \end{align*}
-for some suitably chosen $C_{2}(2\vp)>0$. It follows that we have $T$-tractability, which shows sufficiency of \eqref{eq:tractiff4}. \\
+It follows that we have $T$-tractability, which shows sufficiency of \eqref{eq:tractiff4}. \\
 

### 2023-04-02 GeneralizedTractability_230310.tex
Updates from Overleaf
Fred's Home Computer

@@
 \end{gather*}
-Summing both sides of this last inequality for $j$ from $j(\infty,\vp) \ge 1$ to $\infty$ yields 
+Summing both sides of this last inequality for $j$ from $j(\infty,\vp) \ge 1$ to $\vinfty$ yields 
 \begin{align*}
@@
         \\
-       & \le T(\varepsilon^{-1},d,\vp)\left[\frac{L_{\vp}\, T(0,d,\vp)}{T(\lambda_{\max}^{-1},d,\vp)} + S_{\vp}\right] \\
-       & \le\frac{L_{\vp}}{T(\lambda_{\max}^{-1},d,\vp)} \,T(\varepsilon^{-1},d,\vp) T(0,d,\vp) + S_{\vp}\, T(\varepsilon^{-1},d,\vp)\\
-       & \le\frac{L_{\vp}}{T(\lambda_{\max}^{-1},d,\vp)} \,T(\varepsilon^{-1},d,\vp) T(\varepsilon^{-1},d,\vp) + S_{\vp}\, T(\varepsilon^{-1},d,\vp)\\
-       & \le \frac{L_{\vp}\,K_{\vp,2}}{T(\lambda_{\max}^{-1},d,\vp)}  T(\varepsilon^{-1},d,2\vp)  + S_{\vp}\, T(\varepsilon^{-1},d,\vp)  \qquad \text{by \eqref{eq:ptauassume}}\\
-       & \le \underbrace{\left[\frac{L_{\vp}\,K_{\vp,2}}{T(\lambda_{\max}^{-1},d,\vp)} + S_{\vp}\right]}_{=:C_{2\vp}} \,T(\varepsilon^{-1},d,2\vp)
+       & \le T(\varepsilon^{-1},d,\vp)\left[\frac{L_{\vp}\, T(0,d,\vp)}{T(\lambda_{\max}^{-1},1,\vp)} + S_{\vp}\right] \\
+       & \le\frac{L_{\vp}}{T(\lambda_{\max}^{-1},1,\vp)} \,T(\varepsilon^{-1},d,\vp) T(0,d,\vp) + S_{\vp}\, T(\varepsilon^{-1},d,\vp)\\
+       & \le\frac{L_{\vp}}{T(\lambda_{\max}^{-1},1,\vp)} \,T(\varepsilon^{-1},d,\vp) T(\varepsilon^{-1},d,\vp) + S_{\vp}\, T(\varepsilon^{-1},d,\vp)\\
+       & \le \frac{L_{\vp}\,K_{\vp,2}}{T(\lambda_{\max}^{-1},1,\vp)}  T(\varepsilon^{-1},d,2\vp)  + S_{\vp}\, T(\varepsilon^{-1},d,\vp)  \qquad \text{by \eqref{eq:ptauassume}}\\
+       & \le \underbrace{\left[\frac{L_{\vp}\,K_{\vp,2}}{T(\lambda_{\max}^{-1},1,\vp)} + S_{\vp}\right]}_{=:C_{2\vp}} \,T(\varepsilon^{-1},d,2\vp)
 \end{align*}
@@
 \end{definition}
+
+\peter{
+\section{Weak $T$-$(s,t)$-weak tractability (work in progress)} \label{sec:weak}
+
+\begin{definition}[$T$-$(s,t)$-weak tractability]
+Let $s,t>0$. We say that the problem is \emph{$T$-$(s,t)$ weakly tractable} if
+    \[\lim_{\varepsilon^{-1}+d\rightarrow \infty} \frac{\log n(\varepsilon,d)}{T(\varepsilon^{-s},1,\vp) + T(0,d^t,\vp)} = 0.\]
+\end{definition}
+
+We show a necessary and sufficient condition for $T$-$(s,t)$-weak tractability, working analogously to \cite{WW17}.
+\begin{theorem}\label{thm:weak}
+For $c>0$, define
+\[
+\sigma (c,d,s,\vp):= \sum_{i=1}^\infty \exp \left(-c\, T(\lambda_{i,d}^{-s},1,\vp)\right).
+\]
+Then the problem is $T$-$(s,t)$-weakly tractable if and only if
+\[
+\mu (c,s,t,\vp)=\sup_{d\in\naturals} \sigma (c,d,s,\vp) \exp\left(-c\, T(0,d^t,p,q)\right)<\infty
+\]
+holds for all $c>0$.
+\end{theorem}
+\begin{proof}
+ We first show the necessity of the condition in the theorem.
+Indeed, suppose that the problem is  $T$-$(s,t)$-weakly tractable.
+Then, for any $c>0$ there exists a positive integer $V=V(c)$ such that
+ \[
+ n(\varepsilon,d)\le 
+ \left\lfloor \exp\left(c\,
+ \left(T(\varepsilon^{-s},1,\vp) + T(0,d^t,\vp)\right)
+ \right) \right\rfloor
+ \]
+ whenever $\varepsilon^{-1} + d \ge V$. For $d\in\naturals$ 
+ choose $\varepsilon>0$ such that $\varepsilon^{-1}\ge \max\{1,V-d\}$. Since the eigenvalues $\lambda{i,d}$ are non-increasing in $i$, we know that
+ \[
+ \lambda_{\lfloor \exp(c\,
+ (T(\varepsilon^{-s},1,\vp) + T(0,d^t,\vp))) \rfloor+1}^2 \le \varepsilon^2
+ \]
+ for any $\varepsilon$ satisfying $\varepsilon^{-1}\ge \max\{1,V-d\}$.
+Let 
+\[
+n=n(\varepsilon):= \lfloor \exp(c\,
+ (T(\varepsilon^{-s},1,\vp) + T(0,d^t,\vp))) \rfloor+1
+\]
+and
+\[
+n^*:= \lfloor \exp(c\,
+ (T(\max\{1,(V-d)^s\},1,\vp) + T(0,d^t,\vp))) \rfloor+1.
+\]
+By varying $\varepsilon^{-1}$ ini the interval 
+$[\max\{1,V-d\},\infty)$ we can make $n(\varepsilon)$ attain 
+any integer value greater than or equal to $n^*$.
+
+[TO BE CONTINUED]
+
+\end{proof}
+}
+
 \begin{thebibliography}{99}
@@
 European Mathematical Society Publishing House, Zurich, 2008.
- ×
+ \bibitem{WW17} A.G.~Werschulz,H.~Wo\'zniakowski. A new characterization of $(s,t)$-weak tractability. J. Complexity 38, 68--79, 2017. 
 \end{thebibliography}

### 2023-04-02 GeneralizedTractability_230310.tex
Fred M2 2023 Mac Updates

--- 2023-04-02 GeneralizedTractability_230310.tex
@@
 \]
-\fred{I think that we do not need to bound $T$ away from $0$.}
+\fred{I think that we do not need to bound $T$ away from $0$, but doing so may help satisfy \eqref{eq:ptauassume}.}
 A tractability function is a function of simple form that provides an upper bound on the computational complexity of a problem.
@@
 \[
-j (\varepsilon,\vp):= \lfloor C_{\vp}\, T(\varepsilon^{-1},1,\vp)\rfloor +1, \quad
-j (\infty,\vp) = \lim_{\varepsilon \to \infty} j (\varepsilon,\vp) \ge 1 .
+i(\varepsilon,\vp):= \lfloor C_{\vp}\, T(\varepsilon^{-1},1,\vp)\rfloor +1, \quad
+i(\infty,\vp) = \lim_{\varepsilon \to \infty}  i(\varepsilon,\vp) \ge 1 .
 \]
-Thus, it follows by \eqref{eq:lambda_K_strong3} that $\lambda_{j(\varepsilon,\vp),d} \le \varepsilon$.
+Thus, it follows by \eqref{eq:lambda_K_strong3} that $\lambda_{i(\varepsilon,\vp),d} \le \varepsilon$.
 Note furthermore that we always have
 \[
-j(\varepsilon,\vp)\le C_{\vp}\, T(\varepsilon^{-1},1,\vp)+1 \le C_{\vp} T(\lambda_{j(\varepsilon,\vp),d}^{-1},1,\vp)+1, \qquad \forall \varepsilon > 0,
+i(\varepsilon,\vp)\le C_{\vp}\, T(\varepsilon^{-1},1,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,\vp),d}^{-1},1,\vp)+1, \qquad \forall \varepsilon > 0,
 \]
@@
 
-For $\varepsilon$ taking on all positive values, $j(\varepsilon,\vp)$ takes on all values greater than or equal to $j(\infty,\vp)$, so
+For $\varepsilon$ taking on all positive values, $i(\varepsilon,\vp)$ takes on all values greater than or equal to $i(\infty,\vp)$, so
 \[
-j\le C_{\vp} T(\lambda_{j,d}^{-1},1,\vp)+1, \qquad \forall j \ge j(\infty,\vp).
+i\le C_{\vp} T(\lambda_{i,d}^{-1},1,\vp)+1, \qquad \forall i \ge i(\infty,\vp).
 \]
@@
 \begin{gather*}
- K_{\vp,\tau}\,T (\lambda_{j,d}^{-1},1,\tau \vp) \ge
- [T(\lambda_{j,d}^{-1},1, \vp)]^\tau
+ K_{\vp,\tau}\,T (\lambda_{i,d}^{-1},1,\tau \vp) \ge
+ [T(\lambda_{i,d}^{-1},1, \vp)]^\tau
  \ge
-  \left[\frac{(j-1)}{C_{\vp}}\right]^\tau \qquad \forall j \ge j(\infty,\vp) \\
- \frac{1}{T (\lambda_{j,d}^{-1},1,\tau \vp)} \le
-\frac{K_{\vp,\tau}\, C_{\vp}^\tau}{(j-1)^\tau}\qquad \forall j \ge j(\infty,\vp)
+  \left[\frac{(i-1)}{C_{\vp}}\right]^\tau \qquad \forall i \ge i(\infty,\vp) \\
+ \frac{1}{T (\lambda_{i,d}^{-1},1,\tau \vp)} \le
+\frac{K_{\vp,\tau}\, C_{\vp}^\tau}{(i-1)^\tau}\qquad \forall i \ge i(\infty,\vp).
 \end{gather*}
-Summing both sides of this last inequality for $j$ from $j(\infty,\vp) \ge 1$ to $\infty$ yields 
-\begin{align*}
-\sup_{d\in\naturals} \sum_{j=j (\infty,\vp)}^\infty \frac{1}{T (\lambda_{j,d}^{-1},1, \tau \vp)}
-& \le  \sup_{d\in\naturals} \frac{1}{T (\lambda_{1,d}^{-1},1, \tau \vp)} + K_{\vp,\tau}\, C_{\vp}^\tau
-\sum_{j=2}^\infty \frac{1}{(j-1)^\tau} \\
-& \le\frac{1}{T (\lambda_{\max}^{-1},1, \tau \vp)} +  K_{\vp,\tau}\, C_{\vp}^\tau
+Summing both sides of this last inequality over $i$ from $i(\infty,\vp) +1 \ge 2$ to $\vinfty$ yields
+\begin{equation*}
+\sup_{d\in\naturals} \sum_{i=i(\infty,\vp) +1 }^\infty \frac{1}{T (\lambda_{i,d}^{-1},1, \tau \vp)}
+ \le  K_{\vp,\tau}\, C_{\vp}^\tau
+\sum_{i=2}^\infty \frac{1}{(i-1)^\tau} \\
+ \le K_{\vp,\tau}\, C_{\vp}^\tau
 \zeta (\tau)  < \infty,
-\end{align*}
+\end{equation*}
 where $\zeta$ denotes the Riemann zeta function.
-This yields \eqref{eq:strong_tractiff3} with $\vp$ replaced by $\vp' = \tau \vp$ and $L_{\vp'} = j (\infty,\vp)$, and so we see the necessity of $\eqref{eq:strong_tractiff3}$.
+This yields \eqref{eq:strong_tractiff3} with $\vp$ replaced by $\vp' = \tau \vp$ and $L_{\vp'} = i(\infty,\vp) +1$, and so we see the necessity of $\eqref{eq:strong_tractiff3}$.
 
@@
 \]
-Since the eigenvalues $\lambda_{j,d}$ are non-increasing, we have
+Since the sequence of eigenvalues $\lambda_{1,d}, \lambda_{2,d}, \ldots $ is non-increasing, we have
 \begin{equation}\label{eq:lambda_K4}
-	\lambda_{\lfloor C_{\vp}\, T(\varepsilon^{-1},d,\vp)\rfloor +1,d}\le \varepsilon.
+	\lambda_{\lfloor C_{\vp}\, T(\varepsilon^{-1},d,\vp)\rfloor +1,d}\le \varepsilon \qquad \forall \varepsilon > 0,  \ d \in \naturals..
 \end{equation}
-Define
+Define the integers
 \[
-j (\varepsilon,d,\vp):= \lfloor C_{\vp}\, T(\varepsilon^{-1},d,\vp)\rfloor +1, \quad
-j (\infty,d,\vp) = \lfloor C_{\vp}\, T(0,d,\vp)\rfloor +1.
+i (\varepsilon,d,\vp):= \lfloor C_{\vp}\, T(\varepsilon^{-1},d,\vp)\rfloor +1, \qquad
+i (\infty,d,\vp) = \lfloor C_{\vp}\, T(0,d,\vp)\rfloor +1 \ge 1.
 \]
-Thus, it follows by \eqref{eq:lambda_K4} that $\lambda_{j(\varepsilon,d,\vp),d} \le \varepsilon$.
+Thus, it follows by \eqref{eq:lambda_K4} that $\lambda_{i(\varepsilon,d,\vp),d} \le \varepsilon$.
 Note furthermore that we always have
 \[
-j(\varepsilon,d,\vp)\le C_{\vp}\, T(\varepsilon^{-1},1,\vp)+1 \le C_{\vp} T(\lambda_{j(\varepsilon,d,\vp),d}^{-1},1,\vp)+1, \qquad \forall \varepsilon > 0, \ d \in \naturals
+i(\varepsilon,d,\vp)\le C_{\vp}\, T(\varepsilon^{-1},d,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,d,\vp),d}^{-1},d,\vp)+1, \qquad \forall \varepsilon > 0, \ d \in \naturals,
 \]
@@
 
-For $\varepsilon$ taking on all positive values, $j(\varepsilon,d,\vp)$ takes on all values greater than or equal to $j(\infty,d,\vp)$, so
+For $\varepsilon$ taking on all positive values, $i(\varepsilon,d,\vp)$ takes on all values greater than or equal to $i(\infty,d,\vp)$, so
 \[
-j\le C_{\vp}\, T(\varepsilon^{-1},d,\vp)+1 \le C_{\vp} T(\lambda_{j,d}^{-1},d,\vp)+1, \qquad \forall j \ge j(\infty,d,\vp).
+i\le C_{\vp}\, T(\varepsilon^{-1},d,\vp)+1 \le C_{\vp} T(\lambda_{i,d}^{-1},d,\vp)+1, \qquad \forall i \ge i(\infty,d,\vp).
 \]
-This implies via our technical assumption \eqref{eq:ptauassume} that
+This implies via our technical assumption \eqref{eq:ptauassume} that for any $\tau > 1$,
+\begin{gather*}
+	K_{\vp,\tau}\,T (\lambda_{i,d}^{-1},d,\tau \vp) \ge
+	[T(\lambda_{i,d}^{-1},d, \vp)]^\tau
+	\ge
+	\left[\frac{(i-1)}{C_{\vp}}\right]^\tau \qquad \forall i \ge i(\infty,d,\vp), \\
+	 \frac{1}{T (\lambda_{i,d}^{-1},d,\tau \vp)} \le
+	\frac{K_{\vp,\tau}\, C_{\vp}^\tau}{(i-1)^\tau}\qquad \forall i \ge i(\infty,\vp).
+\end{gather*}
+
+Let $\vp' = \tau \vp$.
+Note that $i(\infty,d,\cdot)$ is nondecreasing.
+Summing both sides of the inequality over $i$ from $i(\infty,d,\vp') + 1 \ge i(\infty,d, \vp) + 1 \ge 2$ to $\infty$ it follows that
 \begin{equation*}
-	K_{\vp,\tau}\,T (\lambda_{j,d}^{-1},d,\tau \vp) \ge
-	[T(\lambda_{j,d}^{-1},d, \vp)]^\tau
-	\ge
-	\left[\frac{(j-1)}{C_{\vp}}\right]^\tau \qquad \forall j \ge j(\infty,d,\vp)
+	\sup_{d\in\naturals} \, \, \sum_{i=i (\infty,d,\vp')+1}^\infty \frac{1}{T (\lambda_{i,d}^{-1},d,\vp')}
+	 \le  K_{\vp,\tau}\, C_{\vp}^\tau
+	\sum_{i=2}^\infty \frac{1}{(i-1)^\tau} \\
+	 \le  K_{\vp,\tau}\, C_{\vp}^\tau
+	\zeta (\tau)  < \infty,
 \end{equation*}
-Summing both sides of the inequality yields and noting that $L_{\vp} \le L(\tau\vp)$, it follows that
-\peter{(Peter: Why does $L(\cdot)$ ocur here?)} \fred{Because I got lost a bit.}
-
-\begin{multline*}
-	\sup_{d\in\naturals} \sum_{j=j(\infty,d,\vp)}^\infty \frac{1}{T (\lambda_{j,d}^{-1},d, \tau \vp)} \le
-	\sup_{d\in\naturals} \sum_{j=j(\infty,d,\vp)}^\infty \frac{1}{T (\lambda_{j,d}^{-1},d, \tau \vp)} \\
-	\le K_{\vp,\tau}\, C_{\vp}^\tau
-	\sum_{j=j(\infty,d,\vp)}^\infty \frac{1}{(j-1)^\tau} \le
-	K_{\vp,\tau}\, C_{\vp}^\tau\, \zeta (\tau) < \infty,
-\end{multline*}
 where $\zeta$ denotes the Riemann zeta function.
 
-Note now that, \peter{for any $d\in\naturals$,}
+Note now that, for any $d\in\naturals$,
+\begin{align*}
+ i(\infty,d,\vp') & = \lfloor C_{\vp'}\, T(0,d,\vp')\rfloor +1 \le  \left[C_{\vp'} + \frac{1}{T(0,d,\vp')}   \right]\, T(0,d,\vp')\\
+ & \le  \underbrace{\left[C_{\vp'} + \frac{1}{T(0,d,\vp')}   \right]}_{=:L_{\vp'}}\, T(0,d,\vp')
+ \le \lceil L_{\vp'} T(0,d,\vp')\rceil .
+\end{align*}
+For this choice of $ L_{\vp'}$ we have
 \[
- j(\infty,d,\vp) = \lfloor C_{\vp}\, T(0,d,\vp)\rfloor +1 \le \lfloor C_{\vp}^\tau\, T(0,d,\tau \vp)\rfloor +1.
+\sup_{d\in\naturals}}\,\, \sum_{i=\lceil L(\vp') T(0,d,\vp')\rceil}^\infty \frac{1}{T(\lambda_{i,d}^{-1},d, \vp')}
+\le
+\sup_{d\in\naturals} \, \, \sum_{i=i (\infty,d,\vp')+1}^\infty \frac{1}{T (\lambda_{i,d}^{-1},d,\vp')} <
+\infty.
 \]
-So, there exists $L(\tau \vp)$ such that
-\[
-\peter{\sup_{d\in\naturals}}\,\, \sum_{j=\lceil L(\tau \vp) T(0,d,\tau \vp)\rceil}^\infty \frac{1}{T(\lambda_{j,d}^{-1},d, \tau\vp)}<\infty.
-\]
-\fred{Fred:  Not sure how $C_{\vp}^\tau$ becomes $L(\tau \vp)$?}
-
-\peter{Peter: You are right. We could probably solve this by just saying above that
-\[
- j(\infty,d,\vp) = \lfloor C_{\vp}\, T(0,d,\vp)\rfloor +1 \le \lfloor C_{\vp}\, T(0,d,\tau \vp)\rfloor +1,
-\]
-and then introduce $L(\tau \vp)$ to bound $C_{\vp}$ and also incorporate the ``+1''?
-}
-
-This yields \eqref{eq:tractiff4} with $\vp$ replaced by $\tau \vp$, and so we see the necessity of $\eqref{eq:tractiff4}$.
+This yields \eqref{eq:tractiff4} with $\vp$ replaced by $\vp'$, so we see the necessity of $\eqref{eq:tractiff4}$.
 

### 2023-04-03 GeneralizedTractability_230310.tex
Fred's Home Computer finished optimality for Theorem

@@
 	\label{eq:Poptdef}
-	\mathcal{P}_{\textup{opt}} : = \{\vp^* \in \cp_{\textup{trct}} :  \vp^* \notin [\vp^\dagger,\boldsymbol{\infty}) \ \forall \vp^\dagger \in  \cp_{\textup{trct}} \setminus \{\vp^*\} \}, \\
+	\mathcal{P}_{\textup{opt}} : = \{\vp^* \in \cp_{\textup{trct}} :  \vp^* \notin [\vp,\boldsymbol{\infty}) \ \forall \vp \in  \cp_{\textup{trct}} \setminus \{\vp^*\} \}, \\
 	\label{eq:Psoptdef}
-	\mathcal{P}_{\textup{sopt}} : = \{\vp^* \in \cp_{\textup{strct}} :  \vp^* \notin [\vp^\dagger,\boldsymbol{\infty}) \ \forall \vp^\dagger \in  \cp_{\textup{strct}} \setminus \{\vp^*\} \}.
+	\mathcal{P}_{\textup{sopt}} : = \{\vp^* \in \cp_{\textup{strct}} :  \vp^* \notin [\vp,\boldsymbol{\infty}) \ \forall \vp \in  \cp_{\textup{strct}} \setminus \{\vp^*\} \}.
 \end{gather}
@@
 	\cp_{\textup{sopt}} =
-	\{\vp^* \in \widetilde{\cp}_{\textup{strct}} :  \vp* \notin [\vp^\dagger,\boldsymbol{\infty}) \ \forall \vp^\dagger \in  \widetilde{\cp}_{\textup{strct}} \setminus \{\vp^*\} \}.
+	\{\vp^* \in \widetilde{\cp}_{\textup{strct}} :  \vp^* \notin [\vp^\dagger,\boldsymbol{\infty}) \ \forall \vp^\dagger \in  \widetilde{\cp}_{\textup{strct}} \setminus \{\vp^*\} \}.
 \]
@@
 
-\noindent This concludes the proof of the theorem.
+\noindent This concludes the proof of  Theorem \ref{thm_main_strong_tract2}.
 
@@
 \end{equation}
-If \eqref{eq:tractiff4} holds for some $\vp$, let  $\widetilde{\cp}_{\textup{trct}} : = \{\vp^* : \eqref{eq:tractiff4} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty})\}$, and   $\widehat{\cp}_{\textup{trct}} : = \{\vp^* : 2\vp \in \widetilde{\cp}_{\textup{trct}}\}$.
-Then $\cp_{\textup{trct}} = \widetilde{\cp}_{\textup{trct}}$, and the set of optimal strong tractability parameters is
+If \eqref{eq:tractiff4} holds for some $\vp$, let  
 \[
-\cp_{\textup{opt}} =
-\{\vp^* \in \widetilde{\cp}_{\textup{trct}} :  \vp^* \notin [\vp^\dagger,\boldsymbol{\infty}) \ \forall \vp^\dagger \in  \widetilde{\cp}_{\textup{trct}} \setminus \{\vp^*\} \}.
-\]\end{theorem}
+\widetilde{\cp}_{\textup{opt}} : = \{\vp^* : \eqref{eq:tractiff4} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty}) \text{ and }  \eqref{eq:tractiff4} \text{ does not hold } \forall \vp \in [\vzero,\vp^*/2)\}.
+\]
+Then $\cp_{\textup{opt}} \subseteq \widetilde{\cp}_{\textup{opt}}$.
+\
+\end{theorem}
 
@@
 \end{align*}
-It follows that we have $T$-tractability, which shows sufficiency of \eqref{eq:tractiff4}. \\
+It follows that we have $T$-tractability, which shows sufficiency of \eqref{eq:tractiff4}.
+
+\bigskip
 
@@
  i(\infty,d,\vp') & = \lfloor C_{\vp'}\, T(0,d,\vp')\rfloor +1 \le  \left[C_{\vp'} + \frac{1}{T(0,d,\vp')}   \right]\, T(0,d,\vp')\\
- & \le  \underbrace{\left[C_{\vp'} + \frac{1}{T(0,d,\vp')}   \right]}_{=:L_{\vp'}}\, T(0,d,\vp')
+ & \le  \underbrace{\left[C_{\vp'} + \frac{1}{T(0,1,\vp')}   \right]}_{=:L_{\vp'}}\, T(0,d,\vp')
  \le \lceil L_{\vp'} T(0,d,\vp')\rceil .
@@
 \noindent \textbf{Optimality:}
-\fred{Not sure how to make optimality works because for sufficiency $\vp$ turns into $2\vp$.}
+Finally we need to show that $\cp_{\textup{opt}} \subseteq \widetilde{\cp}_{\textup{opt}}$.
+Suppose that  $\vp^* \in \cp_{\textup{opt}}$.
+We show that $\vp^*$ satisfies the two conditions for membership in $\widetilde{\cp}_{\textup{opt}}$.
+
+By the definition of  $\cp_{\textup{opt}}$ \eqref{eq:tract_def}  holds for all $\vp \in (\vp^*,\boldsymbol{\infty})$, which implies by the argument for necessity that  \eqref{eq:tractiff4} holds for all $\vp \in (\vp^*,\boldsymbol{\infty})$.
+This is the first condition for membership in $\widetilde{\cp}_{\textup{opt}}$.
+
+Also, if  $\vp^* \in \cp_{\textup{opt}}$, then \eqref{eq:tract_def} must not hold for all $\vp \in [\vzero, \vp^*)$.
+By the sufficiency argument, this implies that \eqref{eq:tractiff4} cannot hold for all $\vp \in [\vp^*/2)$.
+This is the second condition for membership in $\widetilde{\cp}_{\textup{opt}}$.
+
+Thus,  $\cp_{\textup{opt}} \subseteq \widetilde{\cp}_{\textup{opt}}$.  This concludes the proof of Theorem \ref{thm_main_tract2}.
 

### 2023-04-03 GeneralizedTractability_230310.tex
Fred's Home Computer Thm 3 optimality
Updates from Overleaf

@@
 Also, if  $\vp^* \in \cp_{\textup{opt}}$, then \eqref{eq:tract_def} must not hold for all $\vp \in [\vzero, \vp^*)$.
-By the sufficiency argument, this implies that \eqref{eq:tractiff4} cannot hold for all $\vp \in [\vp^*/2)$.
+By the sufficiency argument, this implies that \eqref{eq:tractiff4} cannot hold for all $\vp \in [\vzero,\vp^*/2)$.
 This is the second condition for membership in $\widetilde{\cp}_{\textup{opt}}$.
@@
 \peter{
-\section{Weak $T$-$(s,t)$-weak tractability (work in progress)} \label{sec:weak}
+\section{Weak $T$-$(s,t)$-weak tractability} \label{sec:weak}
 
@@
 \[
-\mu (c,s,t,\vp)=\sup_{d\in\naturals} \sigma (c,d,s,\vp) \exp\left(-c\, T(0,d^t,p,q)\right)<\infty
+\mu (c,s,t,\vp)=\sup_{d\in\naturals} \sigma (c,d,s,\vp) \exp\left(-c\, T(0,d^t,\vp)\right)<\infty
 \]
@@
 
-[TO BE CONTINUED]
+Furthermore, we have, as $\lambda_{n,d}\le \varepsilon$ and as $T$ is monotonically increasing, 
+\begin{eqnarray*}
+n(\varepsilon)-1 & \le & \exp(c\, (T(\varepsilon^{-s},1,\vp) + T(0,d^t,\vp)))\\
+& \le & \exp(c\, (T(\lambda_{n(\varepsilon),d}^{-s},1,\vp) + T(0,d^t,\vp))),
+\end{eqnarray*}
+which is equivalent to 
+\[
+\exp(-2c\, (T(\lambda_{n(\varepsilon),d}^{-s},1,\vp) + T(0,d^t,\vp))) \le \frac{1}{(n(\varepsilon)-1)^2}.
+\]
+Therefore,
+\begin{eqnarray*}
+    \exp(-2c\, T(0,d^t,\vp)) \sum_{i=1}^\infty \exp(-2c\, T(\lambda_{i,d}^{-s},1,\vp))
+    &\le& \exp(-2c\, T(0,d^t,\vp))\, (n^*-1) + \sum_{i=n^*}^\infty \frac{1}{(i-1)^2}\\
+    &\le& \exp(-2c\, T(0,d^t,\vp))\, (n^*-1) + \frac{\pi^2}{6}.
+\end{eqnarray*}
+Moreover,
+\begin{eqnarray*}
+    \exp(-2c\, T(0,d^t,\vp))\, (n^*-1) &\le & \exp(-2c\, T(0,d^t,\vp))\, 
+    \exp (c\, T(V^s,1,\vp) + c\, T(0,d^t,\vp))\\
+    &\le & \exp (c\, T(V^s,1,\vp))\\
+    &<& \infty,
+\end{eqnarray*}
+independently of $d$. This implies that 
+\[
+\exp(-2c\, T(0,d^t,\vp)) \sum_{i=1}^\infty \exp(-2c\, T(\lambda_{i,d}^{-s},1,\vp))<\infty,
+\]
+also independently of $d$. As $c>0$ was chosen arbitrarily, we can replace $2c$ by $c$ and see
+necessity of the condition in the theorem.
+
+\medskip
+
+We now show sufficiency.
+
+Suppose that $\mu(c,s,t,\vp) <\infty$ for all $c>0$. It is no loss of generality to assume that 
+$\mu(c,s,t,\vp) \ge 1$. Since the terms of the series in the definition of $\mu(c,s,t,\vp) $ are non-increasing, we have 
+\[
+\exp (-c\, T(0,d^t,\vp))\, n\, \exp (-c\, T(\lambda_{n,d}^{-s},1,\vp)) \le \mu (c,s,t,\vp).
+\]
+Then we obtain 
+\[
+\exp (-c\, T(\lambda_{n,d}^{-s},1,\vp)) \le \frac{1}{n}\, \mu (c,s,t,\vp)\, 
+\exp (c\, T(0,d^t,\vp)),
+\]
+which is equivalent to 
+\[
+\exp (c\, T(\lambda_{n,d}^{-s},1,\vp)) \ge \frac{n}{\mu (c,s,t,\vp)\, 
+\exp (c\, T(0,d^t,\vp))},
+\]
+which in turn is equivalent to 
+\[
+T(\lambda_{n,d}^{-s},1,\vp) \ge \frac{1}{c}\log \left(\frac{n}{\mu (c,s,t,\vp)\, 
+\exp (c\, T(0,d^t,\vp))}\right)
+\]
+as long as 
+\[
+n> \mu (c,s,t,\vp)\, \exp (c\, T(0,d^t,\vp)).
+\]
+This implies that for the special choice 
+\[
+n= \left\lceil 
+   \mu (c,s,t,\vp)\, \exp \left(c\, (T(\varepsilon^{-s},1,\vp) + T(0,d^t,\vp))\right)
+   \right\rceil 
+\]
+we have
+\[
+T(\lambda_{n,d}^{-s},1,\vp) \ge T(\varepsilon^{-1},1,\vp),
+\]
+which implies that $\lambda_{n,d} \le \varepsilon$, and thus $n(\varepsilon,d)\le n$. Note that the 
+argument $x$ of the ceiling function in the definition of our special $n$ is at least one, which implies 
+$\lceil x \rceil \le 2x$.
+
+Consequently,
+\[
+n(\varepsilon, d) \le \exp\left(c\, \left(
+\frac{\log (2\mu (c,s,t,\vp) )}{c}
+T(\varepsilon^{-s},1,\vp) + T(0,d^t,\vp)
+\right)\right).
+\]
+Clearly, there must exist a positive $V=V(c,s,t,\vp)$ such that when $\varepsilon^{-1} +d \ge V$ it holds true that
+\[
+  T(\varepsilon^{-s},1,\vp) + T(0,d^t,\vp) \ge \frac{\log (2\mu (c,s,t,\vp) )}{c}.
+\]
+Hence we finally have 
+\[
+n(\varepsilon,d) \le \exp (2c\, (T(\varepsilon^{-s},1,\vp) + T(0,d^t,\vp))).
+\]
+Since the latter inequality holds for every $c>0$, we have $T$-$(s,t)$-weak tractability.
 

### 2023-04-08 GeneralizedTractability_230310.tex
Updates from Overleaf

@@
 
-\newcommand{\fred}[1]{\begingroup\color{blue}Fred: #1\endgroup}
+\newcommand{\fred}[1]{\begingroup\color{blue}#1\endgroup}
 \newcommand{\peter}[1]{\begingroup\color{purple}#1\endgroup}
@@
 
-Note that the tractability function is bounded below away from zero even as $\varepsilon \to \infty$, so that the information based complexity is not expected to vanish under arbitrarily loose error requirements.
+Note that the tractability function is bounded below away from zero even as $\varepsilon \to \infty$, so that the information-based complexity is not expected to vanish under arbitrarily loose error requirements.
 For this definition of tractability to make sense we assume that
@@
 \begin{align*}
- i(\infty,d,\vp') & = \lfloor C_{\vp'}\, T(0,d,\vp')\rfloor +1 \le  \left[C_{\vp'} + \frac{1}{T(0,d,\vp')}   \right]\, T(0,d,\vp')\\
- & \le  \underbrace{\left[C_{\vp'} + \frac{1}{T(0,1,\vp')}   \right]}_{=:L_{\vp'}}\, T(0,d,\vp')
+ i(\infty,d,\vp') +1  & = \lfloor C_{\vp'}\, T(0,d,\vp')\rfloor +2 \le  \left[C_{\vp'} + \frac{1}{T(0,d,\vp')}   \right]\, T(0,d,\vp')\\
+ & \le  \underbrace{\left[C_{\vp'} + \frac{2}{T(0,1,\vp')}   \right]}_{=:L_{\vp'}}\, T(0,d,\vp')
  \le \lceil L_{\vp'} T(0,d,\vp')\rceil .
 \end{align*}
-For this choice of $ L_{\vp'}$ we have
+For this choice of $L_{\vp'}$ we have
 \[
-\sup_{d\in\naturals}}\,\, \sum_{i=\lceil L(\vp') T(0,d,\vp')\rceil}^\infty \frac{1}{T(\lambda_{i,d}^{-1},d, \vp')}
+\sup_{d\in\naturals}\,\, \sum_{i=\lceil L(\vp') T(0,d,\vp')\rceil}^\infty \frac{1}{T(\lambda_{i,d}^{-1},d, \vp')}
 \le
@@
     \[
-    n(\varepsilon,d) \leq C\exp\{t(1+\ln(1/\varepsilon))(1+\ln(d))\}
+    n(\varepsilon,d) \leq C\exp\{t(1+\ln(\varepsilon^{-1}))(1+\ln(d))\}
     \] for all $\varepsilon \in (0,1)$ and $d\in\mathbb{N}$.
@@
 \]
-By varying $\varepsilon^{-1}$ ini the interval 
+By varying $\varepsilon^{-1}$ in the interval 
 $[\max\{1,V-d\},\infty)$ we can make $n(\varepsilon)$ attain 
@@
 }
+\paragraph{Example 3: EXP-strong polynomial tractability}
+
+Let $T: (0,\infty) \times \naturals \times [0,\infty) \times [0,\infty)\Rightarrow [1,\infty)$
+be defined by
+\[
+ T(\varepsilon^{-1},d,\vp)= (1+\log\max\{\varepsilon^{-1},1\})^p.
+\]
+Then Theorem \ref{thm_main_tract2} yields the iff-condition
+\[
+ \sup_{d\in\naturals} \sum_{i=L_{\vp} d^{q_1}}^\infty (\min\{\lambda_{i,d},1\})^p  < \infty.
+\]
+\paragraph{Example 4: EXP-polynomial tractability}
+
+Let $T: (0,\infty) \times \naturals \times [0,\infty) \times [0,\infty)\Rightarrow [1,\infty)$
+be defined by
+\[
+ T(\varepsilon^{-1},d,\vp)= (1+\log \max\{\varepsilon^{-1},1\})^p\, d^q.
+\]
+Then Theorem \ref{thm_main_tract2} yields the iff-condition
+\[
+ \sup_{d\in\naturals} \sum_{i=L_{\vp} d^{q_1}}^\infty (\min\{\lambda_{i,d},1\})^p d^{-q} < \infty.
+\]
+\paragraph{Example 5: $(t,s)$-Weak tractability}
+
+Let $T: (0,\infty) \times \naturals \times [0,\infty) \times [0,\infty)\Rightarrow [1,\infty)$. Suppose we have $T$-$(s,t)$- weak tractability, such that
+\[
+ \lim_{d+\varepsilon^{-1}\rightarrow\infty} \frac{\log \max(1,n(\varepsilon,d))}{d^t +(\max(1,\varepsilon^{-1}))^s} =0.
+\]
+Then Theorem \ref{thm:weak} yields the iff-condition
+\[
+\sup_{d\in\naturals} \sigma (c,d,s,\vp) \exp\left(-c\, T(0,d^t,\vp)\right)<\infty
+\]
+where $\sigma (c,d,s,\vp) = $
+
+\section{$T$-Quasi-polynomial tractability} \label{sec:qpt}
+
+\begin{definition}[$T$-Quasi-polynomial tractability]
+We say that the problem is \emph{$T$- quasi-polynomial tractable} if there exists positive $C_{\vp}$ such that
+   %\[ n(\varepsilon,d)\leq C_{\vp}\exp\{(T(0,d,\vp))(T(\varepsilon^{-1},1,\vp)\}\]
+   \[ n(\varepsilon,d)\leq C_{\vp}\exp\{(T(\varepsilon^{-1},d,\vp)\}\]
+\end{definition}
+
+\begin{theorem}\label{thm:qpt}
+A problem is $T$-quasi-polynomial tractable iff there exists $\vp \in [\vzero, \boldsymbol{\infty})$ such that
+\begin{equation}\label{thmqpt}
+M_{\vp} := \sup_{d\in\mathbb{N}}\sum_{i=1}^\infty \frac{1}{T(\lambda_{i,d}^{-1},d,\vp)}
+<\infty
+\end{equation}
+%where $\Bar{p} = -p(1+\log(T(0,d,\vp))$.
+If it holds then 
+\[n(\varepsilon,d)\leq 1+T(0,d^\tau,\vp)+ T(0,d^\tau,\vp)T(\varepsilon^{-1},1,\vp)\]
+\end{theorem}
+\begin{proof}
+\textbf{Necessity Condition:}\\
+Suppose that we have $T$-quasi-polynomial tractability, i.e., for some $\vp\geq 0$, there exists positive $C_{\vp}$ such that
+%\[\comp(\varepsilon,d)\le C_{\vp}\exp\{(T(0,d,\vp)(T(\varepsilon^{-1},1,\vp))\}\quad\quad \forall\varepsilon >0, d\in \mathbb{N}\] 
+\[
+\comp(\varepsilon,d)\le C_{\vp}\exp\{T(\varepsilon^{-1},d,\vp)\}
+\quad\quad \forall\varepsilon >0, d\in \mathbb{N}
+\] 
+Since $\lambda_{i,d}$ are non-increasing, we have
+\[
+\lambda_{\left\lfloor C_{\vp}\exp\{T(\varepsilon^{-1},d,\vp)\}\right\rfloor+1,d}\leq \varepsilon^2
+\]
+Given that the estimate holds for all $\varepsilon> 0$, we assume that $\varepsilon \in (0, 1]$.\\
+
+If we vary $\varepsilon\in (0,1]$, we have that
+\[
+j(\varepsilon,d,\vp) = \left\lfloor C_{\vp}\exp\{T(\varepsilon^{-1},d,\vp)\}\right\rfloor+1
+\] which attains the values $j = j_d,j_{d+1},\dots$, where
+\[
+j(\infty,d,\vp)=j_d = \lfloor C_{\vp}\exp\{ T(0,d,\vp)\}\rfloor + 1
+\]
+Furthermore, we have
+\[j \leq C_{\vp}\exp\{T(\varepsilon^{-1},d,\vp)\}+1 \leq C_{\vp}\exp\{T(\lambda^{-1}_{j,d},d,\vp)\}+1 \]
+This implies that
+\[
+\left(\log\frac{j-1}{C_{\vp}}\right)^\tau \leq \left(T(\varepsilon^{-1},d,\vp)\right)^\tau \leq K_{\vp,\tau}T(\lambda_{j,d},d,\tau\vp) 
+\]
+we have 
+%\[\frac{1}{T(\lambda_{i,d}^{-1},d,\vp)} \leq \frac{K_{\vp,\tau}}{\left(\log\frac{j-1}{C_{\vp}}\right)^\tau}\]
+\end{proof}
 

### 2023-04-10 GeneralizedTractability_230310.tex
Fred's Home Computer

@@
 
+\section{Fred's Attempt at sub-$h$ $T$-Tractability}
+May we frame weak tractability more generally?
+
+Let $h:[0,\infty) \to [1,\infty)]$ satisfy
+\begin{equation} \label{eq:h_cond}
+	h \text{ is non-decreasing}, \qquad 
+	h(0)=1, \qquad  [h(x)]^\tau \le h(\tau x) \quad \forall x \ge 0, \tau > 1.
+\end{equation}
+
+\begin{definition}
+	A problem is sub-$h \circ T$ tractable if
+	\begin{equation*}
+		\lim_{\varepsilon^{-1} + d \to \infty} \frac{\comp(\varepsilon,d)}{h(cT(\varepsilon^{-1},d,\vp))} = 0 \qquad \forall c>0
+	\end{equation*}
+\end{definition}
+
+\begin{theorem}\label{thm:subhT}
+	The problem is sub-$h \circ T$ tractable if and only if
+	\[
+	S_{c,\vp}=\sup_{d\in\naturals}  \, \sum_{i=1}^\infty \frac1{h(c\, T(\lambda_{i,d},d,\vp))} <\infty \qquad \forall c > 0.
+	\]
+\end{theorem}
+\begin{proof}
+We suppress the $\vp$ dependence, because it does not enter into the proof.
+
+\bigskip
+
+\noindent \textbf{Necessary Condition:}\\
+Suppose that the problem is  sub-$h \circ T$ tractable. Then, for any $c>0$ there exists a positive integer $V_c$ such that  
+\[
+	\comp(\varepsilon,d)\le 
+	\left\lfloor{h(cT(\varepsilon^{-1},d)) \right\rfloor \qquad \forall \varepsilon^{-1} + d \ge V_c.
+\]
+By the definition of complexity in \eqref{eq:comp_def}, it follows that 
+\[
+	\lambda_{n(\varepsilon,d,c),d} \le \varepsilon \quad \forall \varepsilon^{-1} + d \ge V_c, \qquad \text{where }
+	n(\varepsilon,d,c):=\left\lfloor{h(cT(\varepsilon^{-1},d)) \right\rfloor.
+\]
+Since $h(cT(\cdot,d))$ is non-decreasing, it follows that
+\begin{equation*}
+		n(\varepsilon,d,c)\le  h(cT(\varepsilon^{-1},d)) \le  h(cT(\lambda^{-1}_{n(\varepsilon,d,c),d},d)) \qquad  \quad \forall \varepsilon^{-1} + d \ge V_c.
+\end{equation*}
+
+For a fixed $d$, the largest the largest $\varepsilon$ can be and still satisfy $ \varepsilon^{-1} + d \ge V_c$ is $\max(V_c - d,1)$.   Let 
+\begin{equation} \label{eq:nstardef}
+	n^*(d,c) : = n(\max(V_c - d,1),d,c) \le h(cT(\max(V_c-d,1),d)
+\end{equation} 
+By varying $\varepsilon^{-1}$ in the interval $[\max\{1,V_c-d\},\infty)$,  the integer $	n(\varepsilon,d,c)$ attains all values greater than or equal to $n^*(d,c)$.  Thus, 
+\begin{align}
+		n &\le h(cT(\lambda^{-1}_{n,d},d)) \qquad  \forall n \ge n^*(d,c), \label{eq:subhTneq}\\
+		\nonumber
+		\frac{1}{h(2 cT(\lambda^{-1}_{n,d},d)) } & \le \frac{1}{[h(cT(\lambda^{-1}_{n,d},d))]^{2}}  \le \frac 1{n^2}   \qquad  \forall n \ge n^*(d,c) \qquad \text{by \eqref{eq:h_cond}}. \\
+		\intertext{Combining this inequality with ...}
+		\nonumber
+		S_{2c} = 	S_{2c,\vp} & =\sup_{d\in\naturals}  \, \sum_{i=1}^\infty \frac1{h(2c\, T(\lambda_{i,d},d))} \\
+		\nonumber
+		&  = \sup_{d\in\naturals} \left [
+		\sum_{i=1}^{n^*(d,c)-1} \frac1{h(2c\, T(\lambda_{i,d},d))}
+		+ \sum_{i=n^*(d,c)}^\infty \frac1{h(2c\, T(\lambda_{i,d},d))} 
+		\right]\\
+		 \nonumber
+		 & \le \sup_{d\in\naturals} \left [
+\frac{n^*(d,c)-1}{h(2c\, T(\lambda_{\max},d))}
++ \sum_{i=1}^\infty \frac1{n^2}
+\right] 
+ \qquad \text{by \eqref{eq:subhTneq}}\\ 
+		 & \le \sup_{d\in\naturals} \left [
+		 \frac{ h(cT(\max(V_c-d,1),d)}{h(2c\, T(\lambda_{\max},d))}
+		\right] + \frac{\pi^2}{6}
+		\qquad \text{by \eqref{eq:nstardef}.}
+\end{align}
+	which is equivalent to 
+	\[
+	\exp(-2c\, (T(\lambda_{n(\varepsilon),d}^{-s},1,\vp) + T(0,d^t,\vp))) \le \frac{1}{(n(\varepsilon)-1)^2}.
+	\]
+	Therefore,
+	\begin{eqnarray*}
+		\exp(-2c\, T(0,d^t,\vp)) \sum_{i=1}^\infty \exp(-2c\, T(\lambda_{i,d}^{-s},1,\vp))
+		&\le& \exp(-2c\, T(0,d^t,\vp))\, (n^*-1) + \sum_{i=n^*}^\infty \frac{1}{(i-1)^2}\\
+		&\le& \exp(-2c\, T(0,d^t,\vp))\, (n^*-1) + \frac{\pi^2}{6}.
+	\end{eqnarray*}
+	Moreover,
+	\begin{eqnarray*}
+		\exp(-2c\, T(0,d^t,\vp))\, (n^*-1) &\le & \exp(-2c\, T(0,d^t,\vp))\, 
+		\exp (c\, T(V^s,1,\vp) + c\, T(0,d^t,\vp))\\
+		&\le & \exp (c\, T(V^s,1,\vp))\\
+		&<& \infty,
+	\end{eqnarray*}
+	independently of $d$. This implies that 
+	\[
+	\exp(-2c\, T(0,d^t,\vp)) \sum_{i=1}^\infty \exp(-2c\, T(\lambda_{i,d}^{-s},1,\vp))<\infty,
+	\]
+	also independently of $d$. As $c>0$ was chosen arbitrarily, we can replace $2c$ by $c$ and see
+	necessity of the condition in the theorem.
+
+	\medskip
+
+  \textbf{Sufficient Condition:}\\
+	We now show sufficiency.
+
+	Suppose that $\mu(c,s,t,\vp) <\infty$ for all $c>0$. It is no loss of generality to assume that 
+	$\mu(c,s,t,\vp) \ge 1$. Since the terms of the series in the definition of $\mu(c,s,t,\vp) $ are non-increasing, we have 
+	\[
+	\exp (-c\, T(0,d^t,\vp))\, n\, \exp (-c\, T(\lambda_{n,d}^{-s},1,\vp)) \le \mu (c,s,t,\vp).
+	\]
+	Then we obtain 
+	\[
+	\exp (-c\, T(\lambda_{n,d}^{-s},1,\vp)) \le \frac{1}{n}\, \mu (c,s,t,\vp)\, 
+	\exp (c\, T(0,d^t,\vp)),
+	\]
+	which is equivalent to 
+	\[
+	\exp (c\, T(\lambda_{n,d}^{-s},1,\vp)) \ge \frac{n}{\mu (c,s,t,\vp)\, 
+		\exp (c\, T(0,d^t,\vp))},
+	\]
+	which in turn is equivalent to 
+	\[
+	T(\lambda_{n,d}^{-s},1,\vp) \ge \frac{1}{c}\log \left(\frac{n}{\mu (c,s,t,\vp)\, 
+		\exp (c\, T(0,d^t,\vp))}\right)
+	\]
+	as long as 
+	\[
+	n> \mu (c,s,t,\vp)\, \exp (c\, T(0,d^t,\vp)).
+	\]
+	This implies that for the special choice 
+	\[
+	n= \left\lceil 
+	\mu (c,s,t,\vp)\, \exp \left(c\, (T(\varepsilon^{-s},1,\vp) + T(0,d^t,\vp))\right)
+	\right\rceil 
+	\]
+	we have
+	\[
+	T(\lambda_{n,d}^{-s},1,\vp) \ge T(\varepsilon^{-1},1,\vp),
+	\]
+	which implies that $\lambda_{n,d} \le \varepsilon$, and thus $n(\varepsilon,d)\le n$. Note that the 
+	argument $x$ of the ceiling function in the definition of our special $n$ is at least one, which implies 
+	$\lceil x \rceil \le 2x$.
+
+	Consequently,
+	\[
+	n(\varepsilon, d) \le \exp\left(c\, \left(
+	\frac{\log (2\mu (c,s,t,\vp) )}{c}
+	T(\varepsilon^{-s},1,\vp) + T(0,d^t,\vp)
+	\right)\right).
+	\]
+	Clearly, there must exist a positive $V=V(c,s,t,\vp)$ such that when $\varepsilon^{-1} +d \ge V$ it holds true that
+	\[
+	T(\varepsilon^{-s},1,\vp) + T(0,d^t,\vp) \ge \frac{\log (2\mu (c,s,t,\vp) )}{c}.
+	\]
+	Hence we finally have 
+	\[
+	n(\varepsilon,d) \le \exp (2c\, (T(\varepsilon^{-s},1,\vp) + T(0,d^t,\vp))).
+	\]
+	Since the latter inequality holds for every $c>0$, we have $T$-$(s,t)$-weak tractability.
+
+\end{proof}
+
 \begin{thebibliography}{99}

### 2023-04-10 GeneralizedTractability_230310.tex
Fred's Home Computer

@@
 \begin{equation} \label{eq:h_cond}
-	h \text{ is non-decreasing}, \qquad 
+	h \text{ is strictly increasing}, \qquad 
 	h(0)=1, \qquad  [h(x)]^\tau \le h(\tau x) \quad \forall x \ge 0, \tau > 1.
@@
 	\[
-	S_{c,\vp}=\sup_{d\in\naturals}  \, \sum_{i=1}^\infty \frac1{h(c\, T(\lambda_{i,d},d,\vp))} <\infty \qquad \forall c > 0.
+	S_c = S_{c,\vp} :=\sup_{d\in\naturals}  \, \sum_{i=1}^\infty \frac1{h(c\, T(\lambda_{i,d},d,\vp))} <\infty \qquad \forall c > 0.
 	\]
@@
 		\nonumber
-		S_{2c} = 	S_{2c,\vp} & =\sup_{d\in\naturals}  \, \sum_{i=1}^\infty \frac1{h(2c\, T(\lambda_{i,d},d))} \\
+		S_{2c} & =\sup_{d\in\naturals}  \, \sum_{i=1}^\infty \frac1{h(2c\, T(\lambda_{i,d},d))} \\
 		\nonumber
@@
 \end{align}
-	which is equivalent to 
-	\[
-	\exp(-2c\, (T(\lambda_{n(\varepsilon),d}^{-s},1,\vp) + T(0,d^t,\vp))) \le \frac{1}{(n(\varepsilon)-1)^2}.
-	\]
-	Therefore,
-	\begin{eqnarray*}
-		\exp(-2c\, T(0,d^t,\vp)) \sum_{i=1}^\infty \exp(-2c\, T(\lambda_{i,d}^{-s},1,\vp))
-		&\le& \exp(-2c\, T(0,d^t,\vp))\, (n^*-1) + \sum_{i=n^*}^\infty \frac{1}{(i-1)^2}\\
-		&\le& \exp(-2c\, T(0,d^t,\vp))\, (n^*-1) + \frac{\pi^2}{6}.
-	\end{eqnarray*}
-	Moreover,
+\fred{Here maybe we need additivity of $T$ .  I will pause.}	Moreover,
 	\begin{eqnarray*}
@@
 
-	\medskip
+	\bigskip
 
-  \textbf{Sufficient Condition:}\\
-	We now show sufficiency.
-
-	Suppose that $\mu(c,s,t,\vp) <\infty$ for all $c>0$. It is no loss of generality to assume that 
-	$\mu(c,s,t,\vp) \ge 1$. Since the terms of the series in the definition of $\mu(c,s,t,\vp) $ are non-increasing, we have 
+\noindent \textbf{Sufficient Condition:}\\	
+Suppose that $S_c <\infty$ for all $c>0$.  Since the terms of the series in the definition of $S_c$ are non-increasing, we have 
 	\[
-	\exp (-c\, T(0,d^t,\vp))\, n\, \exp (-c\, T(\lambda_{n,d}^{-s},1,\vp)) \le \mu (c,s,t,\vp).
+		\frac{n}{h(cT(\lambda_{n,d}^{-1},d))}\le S_c \qquad \forall n,d \in \naturals.
 	\]
-	Then we obtain 
+or equivalently
 \[
-	\exp (-c\, T(\lambda_{n,d}^{-s},1,\vp)) \le \frac{1}{n}\, \mu (c,s,t,\vp)\, 
-	\exp (c\, T(0,d^t,\vp)),
-	\]
-	which is equivalent to 
-	\[
-	\exp (c\, T(\lambda_{n,d}^{-s},1,\vp)) \ge \frac{n}{\mu (c,s,t,\vp)\, 
-		\exp (c\, T(0,d^t,\vp))},
-	\]
-	which in turn is equivalent to 
-	\[
-	T(\lambda_{n,d}^{-s},1,\vp) \ge \frac{1}{c}\log \left(\frac{n}{\mu (c,s,t,\vp)\, 
-		\exp (c\, T(0,d^t,\vp))}\right)
-	\]
-	as long as 
-	\[
-	n> \mu (c,s,t,\vp)\, \exp (c\, T(0,d^t,\vp)).
+	n\le S_c \, h(cT(\lambda_{n,d}^{-1},d))   \qquad \forall n,d \in \naturals.
 \]
@@
 \[
-	n= \left\lceil 
-	\mu (c,s,t,\vp)\, \exp \left(c\, (T(\varepsilon^{-s},1,\vp) + T(0,d^t,\vp))\right)
-	\right\rceil 
+	n = \left\lceil 
+	S_c \, h(cT(\varepsilon^{-1},d))  
+	\right\rceil \ge 1
 \]
@@
 	\[
-	T(\lambda_{n,d}^{-s},1,\vp) \ge T(\varepsilon^{-1},1,\vp),
+	T(\lambda_{n,d}^{-s},d) \ge T(\varepsilon^{-1},d).
 	\]
-	which implies that $\lambda_{n,d} \le \varepsilon$, and thus $n(\varepsilon,d)\le n$. Note that the 
-	argument $x$ of the ceiling function in the definition of our special $n$ is at least one, which implies 
-	$\lceil x \rceil \le 2x$.
+Since $T(\cdot,d)$ is non-decreasing, it follows that $\lambda_{n,d} \le \varepsilon$, and thus 
+\[
+\comp(\varepsilon,d) \le  \left\lceil 
+S_c \, h(cT(\varepsilon^{-1},d))  
+\right\rceil.  
+\]
 
 Consequently,
-	\[
-	n(\varepsilon, d) \le \exp\left(c\, \left(
-	\frac{\log (2\mu (c,s,t,\vp) )}{c}
-	T(\varepsilon^{-s},1,\vp) + T(0,d^t,\vp)
-	\right)\right).
-	\]
-	Clearly, there must exist a positive $V=V(c,s,t,\vp)$ such that when $\varepsilon^{-1} +d \ge V$ it holds true that
-	\[
-	T(\varepsilon^{-s},1,\vp) + T(0,d^t,\vp) \ge \frac{\log (2\mu (c,s,t,\vp) )}{c}.
-	\]
-	Hence we finally have 
-	\[
-	n(\varepsilon,d) \le \exp (2c\, (T(\varepsilon^{-s},1,\vp) + T(0,d^t,\vp))).
-	\]
-	Since the latter inequality holds for every $c>0$, we have $T$-$(s,t)$-weak tractability.
+\begin{align*}
+\lim_{\varepsilon^{-1} + d \to \infty} \frac{\comp(\varepsilon,d)}{ h(2cT(\varepsilon^{-1},d))  }
+& \le \lim_{\varepsilon^{-1} + d \to \infty} \frac{ \left\lceil 
+	S_c \, h(cT(\varepsilon^{-1},d)) \right\rceil}{ [h(cT(\varepsilon^{-1},d))]^2  } \qquad \text{by \eqref{eq:h_cond}}
+\\
+& \le \lim_{\varepsilon^{-1} + d \to \infty} \frac{
+	S_c \, h(cT(\varepsilon^{-1},d))+1}{ [h(cT(\varepsilon^{-1},d))]^2  }  \\
+& = \lim_{\varepsilon^{-1} + d \to \infty} \left \{\frac{
+	S_c }{ h(cT(\varepsilon^{-1},d))  }  + \frac{
+	1}{ [h(cT(\varepsilon^{-1},d))]^2 } \right \} \\
+& = 0, \qquad \text{since } \lim_{\varepsilon^{-1} + d \to \infty} T(\varepsilon^{-1},d) = \infty.
+\end{align*}	
+\fred{Maybe this last assumption on $T$ tending to infinity also depends on the additivity or something similar.}
 
+This completes the proof.
 \end{proof}

### 2023-04-10 GeneralizedTractability_230310.tex
Updates from Overleaf

@@
 
-\begin{definition}
+\begin{definition} \label{def:subhT}
 	A problem is sub-$h \circ T$ tractable if
@@
 
+\noindent \textbf{Sufficient Condition:}\\	
+Suppose that $S_c <\infty$ for all $c>0$.  Since the terms of the series in the definition of $S_c$ are non-increasing, we have 
+	\[
+		\frac{n}{h(cT(\lambda_{n,d}^{-1},d))}\le S_c \qquad \forall n,d \in \naturals.
+	\]
+or equivalently
+\[
+	n\le S_c \, h(cT(\lambda_{n,d}^{-1},d))   \qquad \forall n,d \in \naturals.
+\]
+This implies that for the special choice 
+\[
+	n = \left\lceil 
+	S_c \, h(cT(\varepsilon^{-1},d))  
+	\right\rceil \ge 1
+\]
+	we have
+	\[
+	T(\lambda_{n,d}^{-s},d) \ge T(\varepsilon^{-1},d).
+	\]
+Since $T(\cdot,d)$ is non-decreasing, it follows that $\lambda_{n,d} \le \varepsilon$, and thus 
+\[
+\comp(\varepsilon,d) \le  \left\lceil 
+S_c \, h(cT(\varepsilon^{-1},d))  
+\right\rceil.  
+\]
+
+Consequently,
+\begin{align*}
+\lim_{\varepsilon^{-1} + d \to \infty} \frac{\comp(\varepsilon,d)}{ h(2cT(\varepsilon^{-1},d))  }
+& \le \lim_{\varepsilon^{-1} + d \to \infty} \frac{ \left\lceil 
+	S_c \, h(cT(\varepsilon^{-1},d)) \right\rceil}{ [h(cT(\varepsilon^{-1},d))]^2  } \qquad \text{by \eqref{eq:h_cond}}
+\\
+& \le \lim_{\varepsilon^{-1} + d \to \infty} \frac{
+	S_c \, h(cT(\varepsilon^{-1},d))+1}{ [h(cT(\varepsilon^{-1},d))]^2  }  \\
+& = \lim_{\varepsilon^{-1} + d \to \infty} \left \{\frac{
+	S_c }{ h(cT(\varepsilon^{-1},d))  }  + \frac{
+	1}{ [h(cT(\varepsilon^{-1},d))]^2 } \right \} \\
+& = 0, \qquad \text{since } \lim_{\varepsilon^{-1} + d \to \infty} T(\varepsilon^{-1},d) = \infty.
+\end{align*}	
+\fred{Maybe this last assumption on $T$ tending to infinity also depends on the additivity or something similar.}  Since $c$ is arbitrary, we have satisfied the condition of Definition \ref{def:subhT}.
+
+\bigskip
+
 \noindent \textbf{Necessary Condition:}\\
@@
 	\comp(\varepsilon,d)\le 
-	\left\lfloor{h(cT(\varepsilon^{-1},d)) \right\rfloor \qquad \forall \varepsilon^{-1} + d \ge V_c.
+	\left\lfloor h(cT(\varepsilon^{-1},d)) \right\rfloor \qquad \forall \varepsilon^{-1} + d \ge V_c.
 \]
@@
 	\lambda_{n(\varepsilon,d,c),d} \le \varepsilon \quad \forall \varepsilon^{-1} + d \ge V_c, \qquad \text{where }
-	n(\varepsilon,d,c):=\left\lfloor{h(cT(\varepsilon^{-1},d)) \right\rfloor.
+	n(\varepsilon,d,c):=\left\lfloor h(cT(\varepsilon^{-1},d)) \right\rfloor.
 \]
@@
 
-\noindent \textbf{Sufficient Condition:}\\	
-Suppose that $S_c <\infty$ for all $c>0$.  Since the terms of the series in the definition of $S_c$ are non-increasing, we have 
-	\[
-		\frac{n}{h(cT(\lambda_{n,d}^{-1},d))}\le S_c \qquad \forall n,d \in \naturals.
-	\]
-or equivalently
-\[
-	n\le S_c \, h(cT(\lambda_{n,d}^{-1},d))   \qquad \forall n,d \in \naturals.
-\]
-This implies that for the special choice 
-\[
-	n = \left\lceil 
-	S_c \, h(cT(\varepsilon^{-1},d))  
-	\right\rceil \ge 1
-\]
-	we have
-	\[
-	T(\lambda_{n,d}^{-s},d) \ge T(\varepsilon^{-1},d).
-	\]
-Since $T(\cdot,d)$ is non-decreasing, it follows that $\lambda_{n,d} \le \varepsilon$, and thus 
-\[
-\comp(\varepsilon,d) \le  \left\lceil 
-S_c \, h(cT(\varepsilon^{-1},d))  
-\right\rceil.  
-\]
-
-Consequently,
-\begin{align*}
-\lim_{\varepsilon^{-1} + d \to \infty} \frac{\comp(\varepsilon,d)}{ h(2cT(\varepsilon^{-1},d))  }
-& \le \lim_{\varepsilon^{-1} + d \to \infty} \frac{ \left\lceil 
-	S_c \, h(cT(\varepsilon^{-1},d)) \right\rceil}{ [h(cT(\varepsilon^{-1},d))]^2  } \qquad \text{by \eqref{eq:h_cond}}
-\\
-& \le \lim_{\varepsilon^{-1} + d \to \infty} \frac{
-	S_c \, h(cT(\varepsilon^{-1},d))+1}{ [h(cT(\varepsilon^{-1},d))]^2  }  \\
-& = \lim_{\varepsilon^{-1} + d \to \infty} \left \{\frac{
-	S_c }{ h(cT(\varepsilon^{-1},d))  }  + \frac{
-	1}{ [h(cT(\varepsilon^{-1},d))]^2 } \right \} \\
-& = 0, \qquad \text{since } \lim_{\varepsilon^{-1} + d \to \infty} T(\varepsilon^{-1},d) = \infty.
-\end{align*}	
-\fred{Maybe this last assumption on $T$ tending to infinity also depends on the additivity or something similar.}
-
 This completes the proof.

### 2023-04-11 GeneralizedTractability_230310.tex
Updates from Overleaf

@@
 \[
-\lambda_{\max}^2 \ge \lambda_{1,d}^2 \ge \lambda_{2,d}^2 \ge \cdots, \qquad u_{1,d}, u_{2,d}, \ldots,
+\lambda_{\max}^2 \ge \lambda_{1,d}^2 \ge \lambda_{2,d}^2 \ge \cdots, \qquad u_{1,d}, u_{2,d}, \ldots, \qquad d \in \naturals.
 \]
@@
 
-\section{Main Results}
+\section{(Strong) Tractability}
 
@@
 Let $T$ be a tractability function defined as follows,
-\[
+\begin{equation} \label{eq:Tspec}
     T :(0,\infty) \times \mathbb{N} \times [0,\infty)^s \rightarrow (0,\infty),
-\]
+\end{equation}
 \fred{I think that we do not need to bound $T$ away from $0$, but doing so may help satisfy \eqref{eq:ptauassume}.}
@@
 \end{equation}
+\end{subequations}
 Finally, there is a technical assumption required for our analysis.  There exists a $K_{\vp,\tau}$ depending on $\vp$ and $\tau$, but  independent of $\varepsilon$ and $d$, such that
@@
 \end{equation}
-\end{subequations}
 
@@
 \begin{theorem}\label{thm_main_strong_tract2}
+Let $T$ be a tractability function as specified in \eqref{eq:Tspec} and satisfying \eqref{eq:Tconditions} and \eqref{eq:ptauassume}.
 A problem is strongly $T$-tractable iff there exists $\vp \in [\vzero, \boldsymbol{\infty})$ and an integer $L_{\vp} > 0$ such that
@@
 \begin{theorem}\label{thm_main_tract2}
+Let $T$ be a tractability function as specified in \eqref{eq:Tspec} and satisfying \eqref{eq:Tconditions} and \eqref{eq:ptauassume}.
 A problem is $T$-tractable iff there exist $\vp\ge \vzero$ and a constant $L_{\vp} > 0$ such that
@@
 %where $\Bar{p} = -p(1+\log(T(0,d,\vp))$.
-If it holds then 
-\[n(\varepsilon,d)\leq 1+T(0,d^\tau,\vp)+ T(0,d^\tau,\vp)T(\varepsilon^{-1},1,\vp)\]
+%If it holds then 
+%\[n(\varepsilon,d)\leq 1+T(0,d^\tau,\vp)+ T(0,d^\tau,\vp)T(\varepsilon^{-1},1,\vp)\]
 \end{theorem}
@@
 \[j \leq C_{\vp}\exp\{T(\varepsilon^{-1},d,\vp)\}+1 \leq C_{\vp}\exp\{T(\lambda^{-1}_{j,d},d,\vp)\}+1 \]
-This implies that
-\[
-\left(\log\frac{j-1}{C_{\vp}}\right)^\tau \leq \left(T(\varepsilon^{-1},d,\vp)\right)^\tau \leq K_{\vp,\tau}T(\lambda_{j,d},d,\tau\vp) 
-\]
+This implies that for $\tau>1$, we have
+%\[\left(\log\frac{j-1}{C_{\vp}}\right)^\tau \leq \left(T(\varepsilon^{-1},d,\vp)\right)^\tau \leq K_{\vp,\tau}T(\lambda_{j,d},d,\tau\vp) \]
 we have 
@@
 \begin{theorem}\label{thm:subhT}
+	Let $T$ be a tractability function as specified in \eqref{eq:Tspec} and satisfying \eqref{eq:Tconditions}.
+Moreover, let $\lim_{d \to \infty} T(\varepsilon^{-1},d) = \infty$ for all $\varepsilon > 0$.
 The problem is sub-$h \circ T$ tractable if and only if
@@
 Consequently,
-\begin{align*}
+\begin{align}
+\nonumber
 \lim_{\varepsilon^{-1} + d \to \infty} \frac{\comp(\varepsilon,d)}{ h(2cT(\varepsilon^{-1},d))  }
@@
 \\
+\nonumber
 & \le \lim_{\varepsilon^{-1} + d \to \infty} \frac{
@@
 	S_c }{ h(cT(\varepsilon^{-1},d))  }  + \frac{
-	1}{ [h(cT(\varepsilon^{-1},d))]^2 } \right \} \\
-& = 0, \qquad \text{since } \lim_{\varepsilon^{-1} + d \to \infty} T(\varepsilon^{-1},d) = \infty.
-\end{align*}	
-\fred{Maybe this last assumption on $T$ tending to infinity also depends on the additivity or something similar.}  Since $c$ is arbitrary, we have satisfied the condition of Definition \ref{def:subhT}.
+	1}{ [h(cT(\varepsilon^{-1},d))]^2 } \right \} \label{eq:alastone}.
+\end{align}	
+The finiteness of $S_c$ implies that $\lim_{\varepsilon \to 0} T(\varepsilon^{-1},d) = \infty$ for all $d \in \naturals$.
+Together with the hypothesis on $\lim_{d \to \infty} T(\varepsilon^{-1},d)$, we can infer that $\lim_{\varepsilon^{-1} + d \to \infty} T(\varepsilon^{-1},d) = \infty$.
+This implies that the limit in \eqref{eq:alastone} vanishes.
+Since $c$ is arbitrary, we have satisfied the condition of Definition \ref{def:subhT}.
 
@@
 
-For a fixed $d$, the largest the largest $\varepsilon$ can be and still satisfy $ \varepsilon^{-1} + d \ge V_c$ is $\max(V_c - d,1)$.   Let 
+For a fixed $d$, define $\varepsilon^{-1}_{\max,d} = \max(V_c - d,\lambda_{\max}^{-1})$.
+the largest the largest $\varepsilon$ can be and still satisfy $ \varepsilon^{-1} + d \ge V_c$ is $\max(V_c - d,1)$.
+Let
 \begin{equation} \label{eq:nstardef}
-	n^*(d,c) : = n(\max(V_c - d,1),d,c) \le h(cT(\max(V_c-d,1),d)
+	\varepsilon^{-1}_{\max,d} := \max(V_c - d,\lambda_{\max}^{-1}), \qquad n^*(d,c) : = n(\varepsilon^{-1}_{\max,d},d,c) \le h(cT(\varepsilon^{-1}_{\max,d},d)).
 \end{equation} 
-By varying $\varepsilon^{-1}$ in the interval $[\max\{1,V_c-d\},\infty)$,  the integer $	n(\varepsilon,d,c)$ attains all values greater than or equal to $n^*(d,c)$.  Thus, 
+By varying $\varepsilon^{-1}$ in the interval $[\varepsilon^{-1}_{\max,d},\infty)$,  the integer $n(\varepsilon,d,c)$ attains all values greater than or equal to $n^*(d,c)$.  Thus, 
 \begin{align}
@@
 		\frac{1}{h(2 cT(\lambda^{-1}_{n,d},d)) } & \le \frac{1}{[h(cT(\lambda^{-1}_{n,d},d))]^{2}}  \le \frac 1{n^2}   \qquad  \forall n \ge n^*(d,c) \qquad \text{by \eqref{eq:h_cond}}. \\
-		\intertext{Combining this inequality with ...}
+		\intertext{Combining this inequality with the upper bound on $n^*(d,c)$ yields}
 		\nonumber
-		S_{2c} & =\sup_{d\in\naturals}  \, \sum_{i=1}^\infty \frac1{h(2c\, T(\lambda_{i,d},d))} \\
+		S_{2c} & =\sup_{d\in\naturals}  \, \sum_{i=1}^\infty \frac1{h(2cT(\lambda_{i,d}^{-1},d))} \\
 		\nonumber
 		&  = \sup_{d\in\naturals} \left [
-		\sum_{i=1}^{n^*(d,c)-1} \frac1{h(2c\, T(\lambda_{i,d},d))}
-		+ \sum_{i=n^*(d,c)}^\infty \frac1{h(2c\, T(\lambda_{i,d},d))} 
+		\sum_{i=1}^{n^*(d,c)-1} \frac1{h(2cT(\lambda_{i,d}^{-1},d))}
+		+ \sum_{i=n^*(d,c)}^\infty \frac1{h(2cT(\lambda_{i,d}^{-1},d))} 
 		\right]\\
@@
 		 & \le \sup_{d\in\naturals} \left [
-\frac{n^*(d,c)-1}{h(2c\, T(\lambda_{\max},d))}
+\frac{n^*(d,c)-1}{h(2cT(\lambda_{\max}^{-1},d))}
 + \sum_{i=1}^\infty \frac1{n^2}
@@
  \qquad \text{by \eqref{eq:subhTneq}}\\ 
+ \label{eq:lastone}
 		 & \le \sup_{d\in\naturals} \left [
-		 \frac{ h(cT(\max(V_c-d,1),d)}{h(2c\, T(\lambda_{\max},d))}
+		 \frac{ h(cT(\varepsilon^{-1}_{\max,d},d))}{h(2cT(\lambda_{\max}^{-1},d))}
 		\right] + \frac{\pi^2}{6}
@@
 \end{align}
-\fred{Here maybe we need additivity of $T$ .  I will pause.}	Moreover,
-	\begin{eqnarray*}
-		\exp(-2c\, T(0,d^t,\vp))\, (n^*-1) &\le & \exp(-2c\, T(0,d^t,\vp))\, 
-		\exp (c\, T(V^s,1,\vp) + c\, T(0,d^t,\vp))\\
-		&\le & \exp (c\, T(V^s,1,\vp))\\
-		&<& \infty,
-	\end{eqnarray*}
-	independently of $d$. This implies that 
+
+Note that 
 \[
-	\exp(-2c\, T(0,d^t,\vp)) \sum_{i=1}^\infty \exp(-2c\, T(\lambda_{i,d}^{-s},1,\vp))<\infty,
+\varepsilon^{-1}_{\max,d} = \max(V_c - d,\lambda_{\max}^{-1}) 
+= \begin{cases} V_c - d \le V_c, & d \in \{1, \ldots, d^* : = \lfloor V_c - \lambda_{\max}^{-1} \rfloor\} \\
+\lambda_{\max}^{-1}, & d \in \{d^*+1, \ldots\}
+\end{cases}
 \]
-	also independently of $d$. As $c>0$ was chosen arbitrarily, we can replace $2c$ by $c$ and see
-	necessity of the condition in the theorem.
+Recalling that $T$ is non-decreasing in it's arguments, this implies that 
+\begin{align*}
+    \sup_{d\in\naturals} \,
+		 \frac{ h(cT(\varepsilon^{-1}_{\max,d},d))}{h(2cT(\lambda_{\max}^{-1},d))}
+  &\le \max \left \{  
+  \sup_{d \in \{1, \ldots, d^*\}} \,
+		 \frac{ h(cT(\varepsilon^{-1}_{\max,d},d))}{h(2cT(\lambda_{\max}^{-1},d))}, 
+  \sup_{d\in \{d^*+1, \ldots \}} \,
+		 \frac{ h(cT(\varepsilon^{-1}_{\max,d},d))}{h(2cT(\lambda_{\max}^{-1},d))}
+  \right \} \\
+  & \le \max \left \{  
+  \sup_{d \in \{1, \ldots, d^*\}}  \,
+		 \frac{ h(cT(V_c,d))}{h(2cT(\lambda_{\max}^{-1},d))}
+  , 
+  \sup_{d\in \{d^*+1, \ldots \}}  \,
+		 \frac{ h(cT(\lambda_{\max}^{-1},d))}{h(2cT(\lambda_{\max}^{-1},d))}
+  \right \}
+  \\
+  & \le \max \left \{  
+		 \frac{ h(cT(V_c,d^*))}{h(2cT(\lambda_{\max}^{-1},1))}, 
+  \sup_{d\in \{d^*+1, \ldots \}}  \,
+		 \frac{ h(cT(\lambda_{\max}^{-1},d))}{[h(cT(\lambda_{\max}^{-1},d))]^2}
+  \right \} \\
+  & = \max \left \{  
+		 \frac{ h(cT(V_c,d^*))}{h(2cT(\lambda_{\max}^{-1},1))}, 
+  \sup_{d\in \{d^*+1, \ldots \}} \,
+		 \frac{1}{h(cT(\lambda_{\max}^{-1},d))}
+  \right \} \\
+  & < \infty \qquad \text{since }h \ge 1.
+\end{align*}
+Combining this bound with \eqref{eq:lastone} establishes the finiteness of $S_2c$ and completes the proof of the necessary condition.
 

### 2023-04-11 GeneralizedTractability_230411.tex
Updates from Overleaf

--- 2023-04-11 GeneralizedTractability_230310.tex
@@
 
-Let $\cf_d$ and $\cg_d$ be Hilbert spaces, and $\SOL_d : \cf_d \to \cg_d$ be a linear solution operator with adjoint $\SOL_d^*$ such that $\SOL_d^*\SOL_d : \cf_d \to \cf_d$ has eigenvalues and orthonormal eigenvectors
+Let $\cf_d$ and $\cg_d$ be Hilbert spaces, and $\SOL_d : \cf_d \to \cg_d$ be a linear solution operator \peter{(PETER: do we need to assume compactness of $\SOL_d$ to guarantee solvability of the problem?)} with adjoint $\SOL_d^*$ such that $\SOL_d^*\SOL_d : \cf_d \to \cf_d$ has eigenvalues and orthonormal eigenvectors
 \[
@@
 \]
-This means that the non-negative $\lambda_{i,d}$ are the singular values of the $\SOL_d$. To avoid trivial cases, we assume that there are an infinite number of positive eigenvalues.
+This means that the non-negative $\lambda_{i,d}$ are the singular values of the \peter{operator} $\SOL_d$.
+To avoid trivial cases, we assume that there are an infinite number of positive eigenvalues.
+\peter{We remark that in the literature on Information-Based Complexity the singular values of $\SOL_d$ are often denoted by $\sqrt{\lambda_{i,d}}$ instead of $\lambda_{i,d}$.
+However, since we assume non-negativity of the $\lambda_{i,d}$, the notation used here is equivalent.}
 
@@
 \]
-where $\cb_d$ is the unit ball in $\cf_d$ and $\APP_d(f,\varepsilon)$ is allowed to depend on arbitrary linear functionals.  In this case, the optimal solution is
+where $\cb_d$ is the unit ball in $\cf_d$ and $\APP_d(f,\varepsilon)$ is allowed to depend on arbitrary linear functionals \peter{(note that we also allow adaptive information, i.e., the linear functionals may sequentially depend on each other)}.
+In this case, the optimal solution is
 \[
@@
 \]
-and the complexity of our linear problem is
+and the \peter{information} complexity of our linear problem is
 \begin{equation}\label{eq:comp_def}
@@
 
-By definition, the complexity is non-decreasing  as $\varepsilon$ tends to zero.
-We also expect it to be non-decreasing as $d$ tends to infinity.
-This assumes that the Hilbert spaces are defined in such a way that $\lambda_{j,\cdot}$ is non-decreasing, although this assumption is not needed for our results.
+By definition, the complexity is non-decreasing  as $\varepsilon$ tends to zero.  We also expect it to be non-decreasing as $d$ tends to infinity.  \peter{This means that we are actually considering 
+a whole sequence of problems  $\SOL_d : \cf_d \to \cg_d$, for $d\in\naturals$, and we furthermore assume} that the Hilbert spaces are defined in such a way that $\lambda_{j,\cdot}$ is non-decreasing, although this assumption is not needed for our results.
 
 The question is,``How hard is this problem as $\varepsilon$ tends to zero or as $d$ tends to infinity?''  We want to bound the complexity in terms of a simple function of $\varepsilon$ and $d$ and identify simple conditions on the singular values that are equivalent to this bound holding.
+
+\peter{TODO: Maybe add a short paragraph on notation used in the paper and on its structure? In particular, we should introduce 
+an ordering of the parameters $\vp$.}
 
@@
 
-A problem is defined as $T$-tractable with parameter $\vp$ iff there exists a positive constant $C_{\vp}$ such that
+A problem is defined as $T$-tractable with parameter $\vp$ iff there exists a positive constant $C_{\vp}$, \peter{which is independent of $\varepsilon$ and $d$,} such that
 \begin{equation} \label{eq:tract_def}
@@
 A problem is \emph{strongly}
-$T$-tractable with parameter $\vp$ iff the complexity is independent of the dimension of the problem, that is, there exists a positive constant $C_{\vp}$ such that
+$T$-tractable with parameter $\vp$ iff the complexity is independent of the dimension of the problem, that is, there exists a positive constant $C_{\vp}$, \peter{again independent of $\varepsilon$ and $d$,} such that
 \begin{equation} \label{eq:strong_tract_def}
@@
 
-Note that the tractability function is bounded below away from zero even as $\varepsilon \to \infty$, so that the information-based complexity is not expected to vanish under arbitrarily loose error requirements.
+Note that the tractability function is bounded below away from zero even as $\varepsilon \to \infty$ \peter{[PETER: Is it?]}, so that the information complexity is not expected to vanish under arbitrarily loose error requirements.
 For this definition of tractability to make sense we assume that
@@
 \begin{equation}
-	T \text{ is non-decreasing in all variables}
+	T \text{ is non-decreasing in all variables,}
 \end{equation}
@@
 Furthermore, increasing $\vp$ does not decrease $T(\cdot, \cdot, \vp)$.
-Since there are an infinite number of positive eigenvalues, it also make sense to assume that
+Since there are an infinite number of positive eigenvalues, it also makes sense to assume that
 \begin{equation}
@@
 
-If \eqref{eq:tract_def} holds for some $\vp$, it clearly holds for larger, $\vp$.
+If \eqref{eq:tract_def} holds for some $\vp$, it clearly holds for larger $\vp$.
 We are often interested in the optimal or smallest $\vp$ for which \eqref{eq:tract_def} holds.
@@
 \end{equation*}
-Here above, $\vp = (p,q)$ in some cases.
+Here above, $\vp = (p,q)$ in some cases. \peter{A general reference 
+for results on algebraic tractability is \cite{NW08}, for exponential tractability we refer to \cite{HKW19} and \cite{KW19}.}
 
 In the sections below we prove necessary and sufficient conditions on tractability as generally defined in \eqref{eq:tract_def} and \eqref{eq:strong_tract_def}.
-These conditions involve the boundedness of sums defined in terms of $\{T(\lambda_{i,d}^{-1},\cdot, \cdot)\}_{i=1}^\infty$.
-In practice, it may be easier to verify whether or not these conditions hold than to verify \eqref{eq:comp_def} directly.
+These conditions involve the boundedness of sums defined in terms of \peter{$(T(\lambda_{i,d}^{-1},\cdot, \cdot))_{i=1}^\infty$}.
+In practice, it may be easier to verify whether or not these conditions hold than to verify \peter{\eqref{eq:tract_def} and \eqref{eq:strong_tract_def}} directly.
 
@@
 We first consider the simpler case when the complexity is essentially independent of the dimension, $d$.
-The proof also introduces the line of argument used for the case where there is $d$ dependence.
+The proof also introduces the line of argument used for the case where there is $d$-dependence.
 
@@
 \]
+\peter{[PETER: Maybe using $\widetilde{\vp}$ instead of $\vp^\dagger$ in the definition of $\cp_{\textup{sopt}}$ is more intuitive?]}
 \end{theorem}
@@
 
-Since the $\lambda_{i,d}$ are non-increasing in $i$, it follows that the $T(\lambda_{i,d}^{-1},d',\vp)$ are non-decreasing in $i$. In particular, for all $n\in \mathbb{N}$, we have
+Since the $\lambda_{i,d}$ are non-increasing in $i$, it follows that the $T(\lambda_{i,d}^{-1},d',\vp)$ are non-decreasing in $i$ \peter{for any $d'\in\naturals$}.
+In particular, for all $n\in \mathbb{N}$, we have
 \begin{align*}
@@
 for any $d' \in \naturals$.  Combining this expression for the complexity with the implication in \eqref{eq:implicate_a} implies an upper bound on the complexity: \fred{think $1+$ not needed} 
+\peter{[PETER: I think we do need $+1$, because from \eqref{eq:implicate_a} we obtain a lower bound on $n$, but we still need to take the ceiling function.]}
 \begin{equation} \label{eq:compUP}
@@
        \comp(\varepsilon,d)
-       & = T(\varepsilon^{-1},1, \vp) \Biggl [ \sum_{i=1}^{L_{\vp}-1} \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}
+       & \peter{\le} T(\varepsilon^{-1},1, \vp) \Biggl [ \sum_{i=1}^{L_{\vp}-1} \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}
        + \underbrace{\sum_{i=L_{\vp}}^\infty \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}}_{\le S_{\vp} <\infty\ \text{by \eqref{eq:strong_tractiff3}} }\Biggr] \\
-       & \le T(\varepsilon^{-1},1,\vp) \underbrace{\left[\frac{(L(p)-1)}{T(\lambda_{\max}^{-1},1,\vp)} + S_{\vp}\right]}_{=:C_{\vp}}\\
+       & \le T(\varepsilon^{-1},1,\vp) \underbrace{\left[\frac{(L_{\vp}-1)}{T(\lambda_{\max}^{-1},1,\vp)} + S_{\vp}\right]}_{=:C_{\vp}}\\
        & =  C_{\vp}T(\varepsilon^{-1},1,\vp).
@@
  \frac{1}{T (\lambda_{i,d}^{-1},1,\tau \vp)} \le
-\frac{K_{\vp,\tau}\, C_{\vp}^\tau}{(i-1)^\tau}\qquad \forall i \ge i(\infty,\vp).
+\frac{K_{\vp,\tau}\, C_{\vp}^\tau}{(i-1)^\tau}\qquad \forall i \ge \peter{\max\{i(\infty,\vp),2\}} .
 \end{gather*}
@@
 Suppose that \eqref{eq:tractiff4} holds for some $\vp \ge 0$.
-By the argument in the proof of the sufficient condition for Theorem \ref{thm_main_strong_tract2}, it follows from \eqref{eq:compUP} with $d'=d$ that the complexity has an upper bound of
+By the argument in the proof of the sufficient condition for Theorem \ref{thm_main_strong_tract2}, it follows from \eqref{eq:compUP} with $d'=d$ that the \peter{information} complexity has an upper bound of
 \begin{equation*}
@@
 \end{equation*}
+\peter{[PETER: Again, it seems to me we need +1.]}
 
@@
        \comp(\varepsilon,d)
-       & = T(\varepsilon^{-1},d,\vp) \Biggl [ \sum_{i=1}^{J(\vp,d) -1} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}
+       & \peter{\le} T(\varepsilon^{-1},d,\vp) \Biggl [ \sum_{i=1}^{J(\vp,d) -1} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}
        + \underbrace{\sum_{i=J(\vp,d)}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}}_{\le S_{\vp} \text{ by \eqref{eq:tractiff4}}} \Biggr ] \\
@@
        & \le T(\varepsilon^{-1},d,\vp)\left[\frac{L_{\vp}\, T(0,d,\vp)}{T(\lambda_{\max}^{-1},1,\vp)} + S_{\vp}\right] \\
-       & \le\frac{L_{\vp}}{T(\lambda_{\max}^{-1},1,\vp)} \,T(\varepsilon^{-1},d,\vp) T(0,d,\vp) + S_{\vp}\, T(\varepsilon^{-1},d,\vp)\\
+       & \peter{=}\frac{L_{\vp}}{T(\lambda_{\max}^{-1},1,\vp)} \,T(\varepsilon^{-1},d,\vp) T(0,d,\vp) + S_{\vp}\, T(\varepsilon^{-1},d,\vp)\\
        & \le\frac{L_{\vp}}{T(\lambda_{\max}^{-1},1,\vp)} \,T(\varepsilon^{-1},d,\vp) T(\varepsilon^{-1},d,\vp) + S_{\vp}\, T(\varepsilon^{-1},d,\vp)\\
        & \le \frac{L_{\vp}\,K_{\vp,2}}{T(\lambda_{\max}^{-1},1,\vp)}  T(\varepsilon^{-1},d,2\vp)  + S_{\vp}\, T(\varepsilon^{-1},d,\vp)  \qquad \text{by \eqref{eq:ptauassume}}\\
-       & \le \underbrace{\left[\frac{L_{\vp}\,K_{\vp,2}}{T(\lambda_{\max}^{-1},1,\vp)} + S_{\vp}\right]}_{=:C_{2\vp}} \,T(\varepsilon^{-1},d,2\vp)
+       & \le \underbrace{\left[\frac{L_{\vp}\,K_{\vp,2}}{T(\lambda_{\max}^{-1},1,\vp)} + S_{\vp}\right]}_{=:C_{2\vp}} \,T(\varepsilon^{-1},d,2\vp).
 \end{align*}
@@
 \begin{equation}\label{eq:lambda_K4}
-	\lambda_{\lfloor C_{\vp}\, T(\varepsilon^{-1},d,\vp)\rfloor +1,d}\le \varepsilon \qquad \forall \varepsilon > 0,  \ d \in \naturals..
+	\lambda_{\lfloor C_{\vp}\, T(\varepsilon^{-1},d,\vp)\rfloor +1,d}\le \varepsilon \qquad \forall \varepsilon > 0,  \ d \in \naturals.
 \end{equation}
@@
 i (\varepsilon,d,\vp):= \lfloor C_{\vp}\, T(\varepsilon^{-1},d,\vp)\rfloor +1, \qquad
-i (\infty,d,\vp) = \lfloor C_{\vp}\, T(0,d,\vp)\rfloor +1 \ge 1.
+i (\infty,d,\vp) \peter{:=} \lfloor C_{\vp}\, T(0,d,\vp)\rfloor +1 \ge 1.
 \]
@@
 	 \frac{1}{T (\lambda_{i,d}^{-1},d,\tau \vp)} \le
-	\frac{K_{\vp,\tau}\, C_{\vp}^\tau}{(i-1)^\tau}\qquad \forall i \ge i(\infty,\vp).
+	\frac{K_{\vp,\tau}\, C_{\vp}^\tau}{(i-1)^\tau}\qquad \forall i \ge \peter{\max\{i(\infty,\vp),2\}}.
 \end{gather*}
@@
 Let $\vp' = \tau \vp$.
-Note that $i(\infty,d,\cdot)$ is nondecreasing.
-Summing both sides of the inequality over $i$ from $i(\infty,d,\vp') + 1 \ge i(\infty,d, \vp) + 1 \ge 2$ to $\infty$ it follows that
+Note that $i(\infty,d,\cdot)$ is non-decreasing.
+Summing both sides of the \peter{latter} inequality over $i$ from $i(\infty,d,\vp') + 1 \ge i(\infty,d, \vp) + 1 \ge 2$ to $\infty$ it follows that
 \begin{equation*}
@@
 \begin{align*}
- i(\infty,d,\vp') +1  & = \lfloor C_{\vp'}\, T(0,d,\vp')\rfloor +2 \le  \left[C_{\vp'} + \frac{1}{T(0,d,\vp')}   \right]\, T(0,d,\vp')\\
+ i(\infty,d,\vp') +1  & = \lfloor C_{\vp'}\, T(0,d,\vp')\rfloor +2 \le  \left[C_{\vp'} + \frac{\peter{2}}{T(0,d,\vp')}   \right]\, T(0,d,\vp')\\
  & \le  \underbrace{\left[C_{\vp'} + \frac{2}{T(0,1,\vp')}   \right]}_{=:L_{\vp'}}\, T(0,d,\vp')
@@
 By the definition of  $\cp_{\textup{opt}}$ \eqref{eq:tract_def}  holds for all $\vp \in (\vp^*,\boldsymbol{\infty})$, which implies by the argument for necessity that  \eqref{eq:tractiff4} holds for all $\vp \in (\vp^*,\boldsymbol{\infty})$.
+\peter{Indeed, the latter is deduced similarly as in the proof of Theorem \ref{thm_main_strong_tract2}.}
 This is the first condition for membership in $\widetilde{\cp}_{\textup{opt}}$.
@@
 Since $h(cT(\cdot,d))$ is non-decreasing, it follows that
-\begin{equation*}
-		n(\varepsilon,d,c)\le  h(cT(\varepsilon^{-1},d)) \le  h(cT(\lambda^{-1}_{n(\varepsilon,d,c),d},d)) \qquad  \quad \forall \varepsilon^{-1} + d \ge V_c.
-\end{equation*}
+\begin{equation}
+		n(\varepsilon,d,c)\le  h(cT(\varepsilon^{-1},d)) \le  h(cT(\lambda^{-1}_{n(\varepsilon,d,c),d},d)) \qquad  \quad \forall \varepsilon^{-1} + d \ge V_c. \label{eq:nedcbound}
+\end{equation}
 
-For a fixed $d$, define $\varepsilon^{-1}_{\max,d} = \max(V_c - d,\lambda_{\max}^{-1})$.
-the largest the largest $\varepsilon$ can be and still satisfy $ \varepsilon^{-1} + d \ge V_c$ is $\max(V_c - d,1)$.
-Let
+For a fixed $c$ and $d$, define
 \begin{equation} \label{eq:nstardef}
-	\varepsilon^{-1}_{\max,d} := \max(V_c - d,\lambda_{\max}^{-1}), \qquad n^*(d,c) : = n(\varepsilon^{-1}_{\max,d},d,c) \le h(cT(\varepsilon^{-1}_{\max,d},d)).
+	\varepsilon^{-1}_{\max}(d,c) := \max(V_c - d,\lambda_{\max}^{-1}), \qquad n^*(d,c) : = n(\varepsilon^{-1}_{\max}(d,c),d,c) \le h(cT(\varepsilon^{-1}_{\max}(d,c),d)).
 \end{equation} 
-By varying $\varepsilon^{-1}$ in the interval $[\varepsilon^{-1}_{\max,d},\infty)$,  the integer $n(\varepsilon,d,c)$ attains all values greater than or equal to $n^*(d,c)$.  Thus, 
+By varying $\varepsilon^{-1}$ in the interval $[\varepsilon^{-1}_{\max}(d,c),\infty)$,  the integer $n(\varepsilon,d,c)$ attains all values greater than or equal to $n^*(d,c)$.
+Thus, by \eqref{eq:nedcbound},
 \begin{align}
@@
 		 & \le \sup_{d\in\naturals} \left [
-		 \frac{ h(cT(\varepsilon^{-1}_{\max,d},d))}{h(2cT(\lambda_{\max}^{-1},d))}
+		 \frac{ h(cT(\varepsilon^{-1}_{\max}(d,c),d))}{h(2cT(\lambda_{\max}^{-1},d))}
 		\right] + \frac{\pi^2}{6}
@@
 \[
-\varepsilon^{-1}_{\max,d} = \max(V_c - d,\lambda_{\max}^{-1}) 
-= \begin{cases} V_c - d \le V_c, & d \in \{1, \ldots, d^* : = \lfloor V_c - \lambda_{\max}^{-1} \rfloor\} \\
-\lambda_{\max}^{-1}, & d \in \{d^*+1, \ldots\}
+\varepsilon^{-1}_{\max}(d,c) = \max(V_c - d,\lambda_{\max}^{-1}) 
+= \begin{cases} V_c - d \le V_c, & d \in \{1, \ldots, d^*_c : = \lfloor V_c - \lambda_{\max}^{-1} \rfloor\} \\
+\lambda_{\max}^{-1}, & d \in \{d^*_c+1, \ldots\}
 \end{cases}
@@
 \begin{align*}
-    \sup_{d\in\naturals} \,
-		 \frac{ h(cT(\varepsilon^{-1}_{\max,d},d))}{h(2cT(\lambda_{\max}^{-1},d))}
+    \MoveEqLeft{\sup_{d\in\naturals} \,
+		 \frac{ h(cT(\varepsilon^{-1}_{\max}(d,c),d))}{h(2cT(\lambda_{\max}^{-1},d))}}\\
   &\le \max \left \{  
-  \sup_{d \in \{1, \ldots, d^*\}} \,
-		 \frac{ h(cT(\varepsilon^{-1}_{\max,d},d))}{h(2cT(\lambda_{\max}^{-1},d))}, 
-  \sup_{d\in \{d^*+1, \ldots \}} \,
-		 \frac{ h(cT(\varepsilon^{-1}_{\max,d},d))}{h(2cT(\lambda_{\max}^{-1},d))}
+  \sup_{d \in \{1, \ldots, d^*_c\}} \,
+		 \frac{ h(cT(\varepsilon^{-1}_{\max}(d,c),d))}{h(2cT(\lambda_{\max}^{-1},d))}, 
+  \sup_{d\in \{d^*_c+1, \ldots \}} \,
+		 \frac{ h(cT(\varepsilon^{-1}_{\max}(d,c),d))}{h(2cT(\lambda_{\max}^{-1},d))}
   \right \} \\
   & \le \max \left \{  
-  \sup_{d \in \{1, \ldots, d^*\}}  \,
+  \sup_{d \in \{1, \ldots, d^*_c\}}  \,
 		 \frac{ h(cT(V_c,d))}{h(2cT(\lambda_{\max}^{-1},d))}
   , 
-  \sup_{d\in \{d^*+1, \ldots \}}  \,
+  \sup_{d\in \{d^*_c+1, \ldots \}}  \,
 		 \frac{ h(cT(\lambda_{\max}^{-1},d))}{h(2cT(\lambda_{\max}^{-1},d))}
@@
   & \le \max \left \{  
-		 \frac{ h(cT(V_c,d^*))}{h(2cT(\lambda_{\max}^{-1},1))}, 
-  \sup_{d\in \{d^*+1, \ldots \}}  \,
+		 \frac{ h(cT(V_c,d^*_c))}{h(2cT(\lambda_{\max}^{-1},1))}, 
+  \sup_{d\in \{d^*_c+1, \ldots \}}  \,
 		 \frac{ h(cT(\lambda_{\max}^{-1},d))}{[h(cT(\lambda_{\max}^{-1},d))]^2}
@@
   & = \max \left \{  
-		 \frac{ h(cT(V_c,d^*))}{h(2cT(\lambda_{\max}^{-1},1))}, 
-  \sup_{d\in \{d^*+1, \ldots \}} \,
-		 \frac{1}{h(cT(\lambda_{\max}^{-1},d))}
+		 \frac{ h(cT(V_c,d^*_c))}{h(2cT(\lambda_{\max}^{-1},1))}, 
+		 \frac{1}{h(cT(\lambda_{\max}^{-1},d^*_c+1))}
   \right \} \\
-  & < \infty \qquad \text{since }h \ge 1.
+  & < \infty.
 \end{align*}
-Combining this bound with \eqref{eq:lastone} establishes the finiteness of $S_2c$ and completes the proof of the necessary condition.
+Combining this bound with \eqref{eq:lastone} establishes the finiteness of $S_{2c}$ and completes the proof of the necessary condition.
 
@@
 
-\bibitem{NW08} E.~Novak,H.~Wo\'zniakowski. \textit{Tractability of Multivariate Problems, Volume I: Linear Information}.
+\bibitem{HKW19} F.J.~Hickernell, P. Kritzer, H.~Wo\'zniakowski.  Exponential tractability of linear tensor product problems. In: 
+D.R.~Wood, J.~DeGier, C.~Praeger, T.~Tao (eds.), 2018 MATRIX Annals, 61--78, Springer, Cham, 2020. 
+\bibitem{KW19} P. Kritzer, H.~Wo\'zniakowski.
+Simple characterizations of exponential tractability for linear
+multivariate problems. J.~Complexity 51, 110--128, 2019.
+\bibitem{NW08} E.~Novak, H.~Wo\'zniakowski. \textit{Tractability of Multivariate Problems, Volume I: Linear Information}.
 European Mathematical Society Publishing House, Zurich, 2008.
- \bibitem{WW17} A.G.~Werschulz,H.~Wo\'zniakowski. A new characterization of $(s,t)$-weak tractability. J. Complexity 38, 68--79, 2017. 
+ \bibitem{WW17} A.G.~Werschulz, H.~Wo\'zniakowski. A new characterization of $(s,t)$-weak tractability. J. Complexity 38, 68--79, 2017. 
 \end{thebibliography}

### 2023-04-11 Older_versions/GeneralizedTractability_230310.tex
Updates from Overleaf

--- 2023-04-11 GeneralizedTractability_230310.tex
@@
 We say that the problem is \emph{$T$- quasi-polynomial tractable} if there exists positive $C_{\vp}$ such that
-   %\[ n(\varepsilon,d)\leq C_{\vp}\exp\{(T(0,d,\vp))(T(\varepsilon^{-1},1,\vp)\}\]
-   \[ n(\varepsilon,d)\leq C_{\vp}\exp\{(T(\varepsilon^{-1},d,\vp)\}\]
+   \[ n(\varepsilon,d)\leq C_{\vp}\exp\{(T(0,d,\vp))(T(\varepsilon^{-1},1,\vp)\}\]
+  % \[ n(\varepsilon,d)\leq C_{\vp}\exp\{(T(\varepsilon^{-1},d,\vp)\}\]
 \end{definition}
@@
 Suppose that we have $T$-quasi-polynomial tractability, i.e., for some $\vp\geq 0$, there exists positive $C_{\vp}$ such that
-%\[\comp(\varepsilon,d)\le C_{\vp}\exp\{(T(0,d,\vp)(T(\varepsilon^{-1},1,\vp))\}\quad\quad \forall\varepsilon >0, d\in \mathbb{N}\] 
-\[
-\comp(\varepsilon,d)\le C_{\vp}\exp\{T(\varepsilon^{-1},d,\vp)\}
-\quad\quad \forall\varepsilon >0, d\in \mathbb{N}
-\] 
+\[\comp(\varepsilon,d)\le C_{\vp}\exp\{(T(0,d,\vp)(T(\varepsilon^{-1},1,\vp))\}\quad\quad \forall\varepsilon >0, d\in \mathbb{N}\] 
+%\[\comp(\varepsilon,d)\le C_{\vp}\exp\{T(\varepsilon^{-1},d,\vp)\}\quad\quad \forall\varepsilon >0, d\in \mathbb{N}\] 
 Since $\lambda_{i,d}$ are non-increasing, we have
 \[
-\lambda_{\left\lfloor C_{\vp}\exp\{T(\varepsilon^{-1},d,\vp)\}\right\rfloor+1,d}\leq \varepsilon^2
+\lambda_{\left\lfloor C_{\vp}\exp\{(T(0,d,\vp)(T(\varepsilon^{-1},1,\vp))\}\right\rfloor+1,d}\leq \varepsilon^2
 \]
@@
 \[
-j(\varepsilon,d,\vp) = \left\lfloor C_{\vp}\exp\{T(\varepsilon^{-1},d,\vp)\}\right\rfloor+1
+j(\varepsilon,d,\vp) = \left\lfloor C_{\vp}\exp\{(T(0,d,\vp)(T(\varepsilon^{-1},1,\vp))\}\right\rfloor+1
 \] which attains the values $j = j_d,j_{d+1},\dots$, where
@@
 Furthermore, we have
-\[j \leq C_{\vp}\exp\{T(\varepsilon^{-1},d,\vp)\}+1 \leq C_{\vp}\exp\{T(\lambda^{-1}_{j,d},d,\vp)\}+1 \]
+\[j \leq C_{\vp}\exp\{(T(0,d,\vp)(T(\varepsilon^{-1},1,\vp))\}+1 \leq C_{\vp}\exp\{(T(0,d,\vp)(T(\lambda^{-1}_{j,d},1,\vp))\}+1 \quad \forall j \geq j_d \]
 This implies that for $\tau>1$, we have
-%\[\left(\log\frac{j-1}{C_{\vp}}\right)^\tau \leq \left(T(\varepsilon^{-1},d,\vp)\right)^\tau \leq K_{\vp,\tau}T(\lambda_{j,d},d,\tau\vp) \]
-we have 
+\[
+\left(\frac{j-1}{C_{\vp}}\right)^{\tau/T(0,d,\vp)} \leq \exp\{T(\lambda^{-1}_{j,d},1,\vp)\}
+\]
+\[
+\exp\{-\tau T(\lambda^{-1}_{j,d},1,\vp\} \leq \left(\frac{C_{\vp}}{j-1}\right)^{\tau/T(0,d,\vp)}\Rightarrow
+\exp\{-\tau T(\lambda^{-1}_{j,d},1,\vp)(T(0,d,\vp)\} \leq C_{\vp}^\tau (j-1)^{-\tau}
+\]
+
 %\[\frac{1}{T(\lambda_{i,d}^{-1},d,\vp)} \leq \frac{K_{\vp,\tau}}{\left(\log\frac{j-1}{C_{\vp}}\right)^\tau}\]
+
+\textbf{Sufficient condition:} Suppose that (\ref{}) holds for some $\vp \geq 0$. We need to show that for some $C_{\vp}>0$ we have 
+\[
+\text{comp}(\varepsilon,d) \leq C_{\vp}\exp\{T(0,d,\vp)T(\varepsilon^{-1},1,\vp)\} \quad \forall \varepsilon > , d \in \mathbb{N}
+\] Let
 \end{proof}

### 2023-04-11 GeneralizedTractability_230411.tex
Updates from Overleaf

@@
 Let $\cf_d$ and $\cg_d$ be Hilbert spaces, and $\SOL_d : \cf_d \to \cg_d$ be a linear solution operator \peter{(PETER: do we need to assume compactness of $\SOL_d$ to guarantee solvability of the problem?)} with adjoint $\SOL_d^*$ such that $\SOL_d^*\SOL_d : \cf_d \to \cf_d$ has eigenvalues and orthonormal eigenvectors
-\[
+\begin{equation} \label{eq:eigenvalues}
 \lambda_{\max}^2 \ge \lambda_{1,d}^2 \ge \lambda_{2,d}^2 \ge \cdots, \qquad u_{1,d}, u_{2,d}, \ldots, \qquad d \in \naturals.
-\]
+\end{equation}
 This means that the non-negative $\lambda_{i,d}$ are the singular values of the \peter{operator} $\SOL_d$.
@@
 By definition, the complexity is non-decreasing  as $\varepsilon$ tends to zero.  We also expect it to be non-decreasing as $d$ tends to infinity.  \peter{This means that we are actually considering 
-a whole sequence of problems  $\SOL_d : \cf_d \to \cg_d$, for $d\in\naturals$, and we furthermore assume} that the Hilbert spaces are defined in such a way that $\lambda_{j,\cdot}$ is non-decreasing, although this assumption is not needed for our results.
+a whole sequence of problems  $\SOL_d : \cf_d \to \cg_d$, for $d\in\naturals$, and we furthermore assume} that the Hilbert spaces are defined in such a way that $\lambda_{\cdot,d}$ is non-decreasing for every $d$, as spelled out in \eqref{eq:eigenvalues}, although this assumption is not needed for our results.
 
@@
 
-Note that the tractability function is bounded below away from zero even as $\varepsilon \to \infty$ \peter{[PETER: Is it?]}, so that the information complexity is not expected to vanish under arbitrarily loose error requirements.
+%Note that the tractability function is bounded below away from zero even as $\varepsilon \to \infty$ \peter{[PETER: Is it?]}, so that the information complexity is not expected to vanish under arbitrarily loose error requirements.
 For this definition of tractability to make sense we assume that
@@
 	\cp_{\textup{sopt}} =
-	\{\vp^* \in \widetilde{\cp}_{\textup{strct}} :  \vp^* \notin [\vp^\dagger,\boldsymbol{\infty}) \ \forall \vp^\dagger \in  \widetilde{\cp}_{\textup{strct}} \setminus \{\vp^*\} \}.
+	\{\vp^* \in \widetilde{\cp}_{\textup{strct}} :  \vp^* \notin [\widetilde{\vp},\boldsymbol{\infty}) \ \forall \widetilde{\vp}\in  \widetilde{\cp}_{\textup{strct}} \setminus \{\vp^*\} \}.
 \]
-\peter{[PETER: Maybe using $\widetilde{\vp}$ instead of $\vp^\dagger$ in the definition of $\cp_{\textup{sopt}}$ is more intuitive?]}
+%\peter{[PETER: Maybe using $\widetilde{\vp}$ instead of $\vp^\dagger$ in the definition of $\cp_{\textup{sopt}}$ is more intuitive?]}
 \end{theorem}

### 2023-04-13 GeneralizedTractability_230411.tex
Updates from Overleaf

@@
 \usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
-
+\usepackage[normalem]{ulem}
 \usepackage{algorithmic}
@@
 
-Let $\cf_d$ and $\cg_d$ be Hilbert spaces, and $\SOL_d : \cf_d \to \cg_d$ be a linear solution operator \peter{(PETER: do we need to assume compactness of $\SOL_d$ to guarantee solvability of the problem?)} with adjoint $\SOL_d^*$ such that $\SOL_d^*\SOL_d : \cf_d \to \cf_d$ has eigenvalues and orthonormal eigenvectors
+Let $\cf_d$ and $\cg_d$ be Hilbert spaces, and $\SOL_d : \cf_d \to \cg_d$ be a linear solution operator  with adjoint $\SOL_d^*$ such that $\SOL_d^*\SOL_d : \cf_d \to \cf_d$ has eigenvalues and orthonormal eigenvectors
 \begin{equation} \label{eq:eigenvalues}
@@
 This means that the non-negative $\lambda_{i,d}$ are the singular values of the \peter{operator} $\SOL_d$. 
+We make the technical assumption that $\SOL_d$ is a compact operator.
+This implies (see, e.g., \cite{NW08}) that the $\lambda_{i,d}$ converge to zero as $i$ tends to infinity, which in turn implies that the problem is solvable by suitable algorithms.
+
 To avoid trivial cases, we assume that there are an infinite number of positive eigenvalues.
@@
 \end{equation}
-\fred{I think that we do not need to bound $T$ away from $0$, but doing so may help satisfy \eqref{eq:ptauassume}.}
 A tractability function is a function of simple form that provides an upper bound on the computational complexity of a problem.
@@
 \begin{subequations} \label{eq:Tconditions}
-\begin{equation}
+\begin{equation} \label{eq:Tnondecreasing}
 	T \text{ is non-decreasing in all variables,}
@@
 \end{equation}
-Since $T(\cdot,d,\vp)$ is non-decreasing, we may define the following limit:
+Since $T(\cdot,d,\vp)$ is non-decreasing, we may define the following limit, which we assume will always be positive:
 \begin{equation}
-	T(0,d,\vp):=\lim_{\varepsilon\to\infty}T(\varepsilon^{-1},d,\vp).
+	T(0,d,\vp):=\lim_{\varepsilon\to\infty}T(\varepsilon^{-1},d,\vp) \ge T(0,1,\vzero) > 0.
 \end{equation}
@@
 Moreover, given that $T$ is increasing in its arguments, we have the following equivalent expression for the complexity via \eqref{eq:comp_def}:
-    \begin{equation*} %\label{eq:comp_equiv}
-    \comp(\varepsilon, d) = \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon\} = \min \biggl\{n \in \natzero : \frac{1}{T(\lambda_{n+1,d}^{-1},d',\vp)}\le \frac{1}{T(\varepsilon^{-1},d',\vp) }\biggr\},
-\end{equation*}
-for any $d' \in \naturals$.  Combining this expression for the complexity with the implication in \eqref{eq:implicate_a} implies an upper bound on the complexity: \fred{think $1+$ not needed} 
-\peter{[PETER: I think we do need $+1$, because from \eqref{eq:implicate_a} we obtain a lower bound on $n$, but we still need to take the ceiling function.]}
-\begin{equation} \label{eq:compUP}
-	\comp(\varepsilon,d)
-	\le T(\varepsilon^{-1},d',\vp) \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} \qquad \forall \varepsilon > 0, \ d, d' \in \naturals.
-\end{equation}
+    \begin{align} %\label{eq:comp_equiv}
+    \nonumber 
+    \comp(\varepsilon, d) & = \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon\} \\
+    \nonumber 
+    & = \min \biggl\{n \in \natzero : \frac{1}{T(\lambda_{n+1,d}^{-1},d',\vp)}\le \frac{1}{T(\varepsilon^{-1},d',\vp) }\biggr\} \qquad \forall d' \in \naturals\\
+    \nonumber 
+    & \le  \min \biggl\{n \in \natzero : n \ge T(\varepsilon^{-1},d',\vp) \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} \biggr\} \quad \forall d' \in \naturals \qquad \text{by \eqref{eq:implicate_a}} \\
+    & \le  T(\varepsilon^{-1},d',\vp) \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} + 1 \quad \forall d' \in \naturals. \label{eq:compUP}
+\end{align}
 
@@
        & \peter{\le} T(\varepsilon^{-1},1, \vp) \Biggl [ \sum_{i=1}^{L_{\vp}-1} \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}
-       + \underbrace{\sum_{i=L_{\vp}}^\infty \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}}_{\le S_{\vp} <\infty\ \text{by \eqref{eq:strong_tractiff3}} }\Biggr] \\
-       & \le T(\varepsilon^{-1},1,\vp) \underbrace{\left[\frac{(L_{\vp}-1)}{T(\lambda_{\max}^{-1},1,\vp)} + S_{\vp}\right]}_{=:C_{\vp}}\\
+       + \underbrace{\sum_{i=L_{\vp}}^\infty \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}}_{\le S_{\vp} <\infty\ \text{by \eqref{eq:strong_tractiff3}} }
+       + \frac{1}{T(\varepsilon^{-1},1, \vp)} \Biggr] \\
+       & \le T(\varepsilon^{-1},1,\vp) \underbrace{\left[\frac{(L_{\vp}-1)}{T(\lambda_{\max}^{-1},1,\vp)} + S_{\vp} + \frac{1}{T(0,1, \vp)}\right]}_{=:C_{\vp}}\\
        & =  C_{\vp}T(\varepsilon^{-1},1,\vp).
@@
 \begin{equation*}
-	 \comp(\varepsilon,d) \le  T(\varepsilon^{-1},d,\vp) \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}
+	 \comp(\varepsilon,d) \le  T(\varepsilon^{-1},d,\vp) \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)} + 1
 \end{equation*}
-\peter{[PETER: Again, it seems to me we need +1.]}
+%\peter{[PETER: Again, it seems to me we need +1.]}
 
@@
        & \peter{\le} T(\varepsilon^{-1},d,\vp) \Biggl [ \sum_{i=1}^{J(\vp,d) -1} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}
-       + \underbrace{\sum_{i=J(\vp,d)}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}}_{\le S_{\vp} \text{ by \eqref{eq:tractiff4}}} \Biggr ] \\
-       & \le T(\varepsilon^{-1},d,\vp)\left[ \frac{J(\vp,d)-1}{T(\lambda_{\max}^{-1},d,\vp)} + S_{\vp}\right]
-        \\
-       & \le T(\varepsilon^{-1},d,\vp)\left[\frac{L_{\vp}\, T(0,d,\vp)}{T(\lambda_{\max}^{-1},1,\vp)} + S_{\vp}\right] \\
-       & \peter{=}\frac{L_{\vp}}{T(\lambda_{\max}^{-1},1,\vp)} \,T(\varepsilon^{-1},d,\vp) T(0,d,\vp) + S_{\vp}\, T(\varepsilon^{-1},d,\vp)\\
-       & \le\frac{L_{\vp}}{T(\lambda_{\max}^{-1},1,\vp)} \,T(\varepsilon^{-1},d,\vp) T(\varepsilon^{-1},d,\vp) + S_{\vp}\, T(\varepsilon^{-1},d,\vp)\\
-       & \le \frac{L_{\vp}\,K_{\vp,2}}{T(\lambda_{\max}^{-1},1,\vp)}  T(\varepsilon^{-1},d,2\vp)  + S_{\vp}\, T(\varepsilon^{-1},d,\vp)  \qquad \text{by \eqref{eq:ptauassume}}\\
-       & \le \underbrace{\left[\frac{L_{\vp}\,K_{\vp,2}}{T(\lambda_{\max}^{-1},1,\vp)} + S_{\vp}\right]}_{=:C_{2\vp}} \,T(\varepsilon^{-1},d,2\vp).
+       + \underbrace{\sum_{i=J(\vp,d)}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}}_{\le S_{\vp} \text{ by \eqref{eq:tractiff4}}} 
+       + \frac{1}{T(\varepsilon^{-1},d, \vp)} \Biggr ] \\
+       & \le T(\varepsilon^{-1},d,\vp)\left[ \frac{J(\vp,d)-1}{T(\lambda_{\max}^{-1},d,\vp)} + S_{\vp} + \frac{1}{T(0,1, \vp)}\right]
+       \qquad \text{by \eqref{eq:Tnondecreasing}}  \\
+       & \le T(\varepsilon^{-1},d,\vp)\left[\frac{L_{\vp}\, T(0,d,\vp)}{T(\lambda_{\max}^{-1},1,\vp)} + S_{\vp} + \frac{1}{T(0,1, \vp)}\right] \\
+       & \peter{=}\frac{L_{\vp}}{T(\lambda_{\max}^{-1},1,\vp)} \,T(\varepsilon^{-1},d,\vp) T(0,d,\vp) + \left [  S_{\vp} + \frac{1}{T(0,1, \vp)}\right] T(\varepsilon^{-1},d,\vp)\\
+       & \le\frac{L_{\vp}}{T(\lambda_{\max}^{-1},1,\vp)} \,T(\varepsilon^{-1},d,\vp) T(\varepsilon^{-1},d,\vp) +\left [  S_{\vp} + \frac{1}{T(0,1, \vp)}\right] T(\varepsilon^{-1},d,\vp)\\
+       & \le \frac{L_{\vp}\,K_{\vp,2}}{T(\lambda_{\max}^{-1},1,\vp)}  T(\varepsilon^{-1},d,2\vp)  +\left [  S_{\vp} + \frac{1}{T(0,1, \vp)}\right] T(\varepsilon^{-1},d,\vp)  \qquad \text{by \eqref{eq:ptauassume}}\\
+       & \le \underbrace{\left[\frac{L_{\vp}\,K_{\vp,2}}{T(\lambda_{\max}^{-1},1,\vp)} + S_{\vp} + \frac{1}{T(0,1, \vp)}\right]}_{=:C_{2\vp}} \,T(\varepsilon^{-1},d,2\vp) \qquad \text{by \eqref{eq:Tnondecreasing}}.
 \end{align*}
@@
 	\begin{equation*}
-		\lim_{\varepsilon^{-1} + d \to \infty} \frac{\comp(\varepsilon,d)}{h(cT(\varepsilon^{-1},d,\vp))} = 0 \qquad \forall c>0
+		\lim_{\varepsilon^{-1} + d \to \infty} \frac{\comp(\varepsilon,d)}{h(cT(\varepsilon^{-1},d,\vp))} = 0 \qquad \text{\sout{$\forall c>0$}}
 	\end{equation*}
@@
 	\[
-	S_c = S_{c,\vp} :=\sup_{d\in\naturals}  \, \sum_{i=1}^\infty \frac1{h(c\, T(\lambda_{i,d},d,\vp))} <\infty \qquad \forall c > 0.
+	S_c = S_{c,\vp} :=\sup_{d\in\naturals}  \, \sum_{i=1}^\infty \frac1{h(c\, T(\lambda_{i,d}^{-1},d,\vp))} <\infty \qquad \forall c > 0.
 	\]
@@
 		 \frac{ h(cT(V_c,d^*_c))}{h(2cT(\lambda_{\max}^{-1},1))}, 
-		 \frac{1}{h(cT(\lambda_{\max}^{-1},d^*_c+1))}
+		 \frac{1}{h(cT(\lambda_{\max}^{-1},d_c^*+1))}
   \right \} \\
@@
 \end{proof}
+
+If $f(x)$ and $g(x)$ are both positive, and $\lim_{x \to \infty} g(x) = \infty$, is it true that
+\[
+\lim_{x \to \infty} \frac{f(x)}{g(x)} = 0 \iff 
+\lim_{x \to \infty} \frac{\log(f(x))}{\log(g(x))} = 0?
+\]
 

### 2023-04-13 Older_versions/GeneralizedTractability_230310.tex
Updates from Overleaf

@@
 \[
-\sup_{d\in\naturals} \sigma (c,d,s,\vp) \exp\left(-c\, T(0,d^t,\vp)\right)<\infty
+\sup_{d\in\naturals} \sigma (c,d,s,\vp) \exp\left(-cd^t\right)<\infty
 \]
-where $\sigma (c,d,s,\vp) = $
+where $\displaystyle\sigma (c,d,s,\vp) =\sum_{i=1}^\infty \exp\left(-c\left(\lambda^{-1}_{i,d}\right)^{s/2}\right) $
 
@@
 We say that the problem is \emph{$T$- quasi-polynomial tractable} if there exists positive $C_{\vp}$ such that
-   \[ n(\varepsilon,d)\leq C_{\vp}\exp\{(T(0,d,\vp))(T(\varepsilon^{-1},1,\vp)\}\]
-  % \[ n(\varepsilon,d)\leq C_{\vp}\exp\{(T(\varepsilon^{-1},d,\vp)\}\]
+ %  \[ n(\varepsilon,d)\leq C_{\vp}\exp\{(T(0,d,\vp))(T(\varepsilon^{-1},1,\vp)\}\]
+  \[ n(\varepsilon,d)\leq C_{\vp}\exp\{(T(\varepsilon^{-1},d,\vp)\}\]
 \end{definition}
@@
 \begin{equation}\label{thmqpt}
-M_{\vp} := \sup_{d\in\mathbb{N}}\sum_{i=1}^\infty \frac{1}{T(\lambda_{i,d}^{-1},d,\vp)}
+M_{\vp} := \sup_{d\in\mathbb{N}}\sum_{i=1}^\infty \left[\frac{1}{T(\lambda_{i,d}^{-1},d,\vp)}\right]^{T(0,d,\vp)}
 <\infty
@@
 Suppose that we have $T$-quasi-polynomial tractability, i.e., for some $\vp\geq 0$, there exists positive $C_{\vp}$ such that
-\[\comp(\varepsilon,d)\le C_{\vp}\exp\{(T(0,d,\vp)(T(\varepsilon^{-1},1,\vp))\}\quad\quad \forall\varepsilon >0, d\in \mathbb{N}\] 
-%\[\comp(\varepsilon,d)\le C_{\vp}\exp\{T(\varepsilon^{-1},d,\vp)\}\quad\quad \forall\varepsilon >0, d\in \mathbb{N}\] 
+%\[\comp(\varepsilon,d)\le C_{\vp}\exp\{(T(0,d,\vp)(T(\varepsilon^{-1},1,\vp))\}\quad\quad \forall\varepsilon >0, d\in \mathbb{N}\] 
+\[\comp(\varepsilon,d)\le C_{\vp}\exp\{(T(0,d,\vp))(T(\varepsilon^{-1},d,\vp))\}\quad\quad \forall\varepsilon >0, d\in \mathbb{N}\] 
 Since $\lambda_{i,d}$ are non-increasing, we have
+%\[\lambda_{\left\lfloor C_{\vp}\exp\{T(\varepsilon^{-1},d,\vp)\}\right\rfloor+1,d}\leq \varepsilon^2\]
 \[
-\lambda_{\left\lfloor C_{\vp}\exp\{(T(0,d,\vp)(T(\varepsilon^{-1},1,\vp))\}\right\rfloor+1,d}\leq \varepsilon^2
+\lambda_{\left\lfloor C_{\vp}\exp\{(T(0,d,\vp))(T(\varepsilon^{-1},d,\vp))\}\right\rfloor+1,d}\leq \varepsilon
 \]
@@
 \[
-j(\varepsilon,d,\vp) = \left\lfloor C_{\vp}\exp\{(T(0,d,\vp)(T(\varepsilon^{-1},1,\vp))\}\right\rfloor+1
+j(\varepsilon,d,\vp) = \left\lfloor C_{\vp}\exp\{(T(0,d,\vp))(T(\varepsilon^{-1},d,\vp))\}\}\right\rfloor+1
 \] which attains the values $j = j_d,j_{d+1},\dots$, where
 \[
-j(\infty,d,\vp)=j_d = \lfloor C_{\vp}\exp\{ T(0,d,\vp)\}\rfloor + 1
+j(\infty,d,\vp)=j_d = \lfloor C_{\vp}\exp\{(T(0,d,\vp))T(0,d,\vp)\}\rfloor + 1
 \]
 Furthermore, we have
-\[j \leq C_{\vp}\exp\{(T(0,d,\vp)(T(\varepsilon^{-1},1,\vp))\}+1 \leq C_{\vp}\exp\{(T(0,d,\vp)(T(\lambda^{-1}_{j,d},1,\vp))\}+1 \quad \forall j \geq j_d \]
+\[j \leq C_{\vp}\exp\{(T(0,d,\vp))(T(\varepsilon^{-1},d,\vp)\}+1 \leq C_{\vp}\exp\{(T(0,d,\vp))(T(\lambda_{j,d}^{-1},d,\vp)\}+1 \quad \forall j \geq j_d \]
 This implies that for $\tau>1$, we have
 \[
-\left(\frac{j-1}{C_{\vp}}\right)^{\tau/T(0,d,\vp)} \leq \exp\{T(\lambda^{-1}_{j,d},1,\vp)\}
+(j-1)^{\tau} \leq C_{\vp}\exp\{\tau(T(0,d,\vp)) (T(\lambda_{j,d}^{-1},d,\vp)\}
 \]
+This implies
 \[
-\exp\{-\tau T(\lambda^{-1}_{j,d},1,\vp\} \leq \left(\frac{C_{\vp}}{j-1}\right)^{\tau/T(0,d,\vp)}\Rightarrow
-\exp\{-\tau T(\lambda^{-1}_{j,d},1,\vp)(T(0,d,\vp)\} \leq C_{\vp}^\tau (j-1)^{-\tau}
+\exp\{-\tau(T(0,d,\vp))( T(\lambda_{j,d}^{-1},d,\vp) \leq \frac{C_{\vp}}{(j-1)^\tau}
 \]
-
+We can get
+\[
+T(\lambda_{i,d},d,\vp))^{-\tau T(0,d,\vp)}\leq C_{\tau,\vp}\frac{1}{(j-1)^\tau} 
+\]provided $T(\lambda_{i,d},d,\vp)\geq e$. Therefore, we get
+\[
+\sum_{i=1}^\infty T(\lambda_{i,d},d,\vp))^{-\tau T(0,d,\vp)} \leq C_{\tau,\vp}\sum_{i=1}^\infty \frac{1}{(j-1)^\tau}
+< \infty\]
 %\[\frac{1}{T(\lambda_{i,d}^{-1},d,\vp)} \leq \frac{K_{\vp,\tau}}{\left(\log\frac{j-1}{C_{\vp}}\right)^\tau}\]
-
-\textbf{Sufficient condition:} Suppose that (\ref{}) holds for some $\vp \geq 0$. We need to show that for some $C_{\vp}>0$ we have 
+This yields \eqref{thmqpt}.\\
+\textbf{Sufficient condition:} Suppose that (\ref{thmqpt}) holds for some $\vp \geq 0$. We need to show that for some $C_{\vp}>0$ we have 
 \[
-\text{comp}(\varepsilon,d) \leq C_{\vp}\exp\{T(0,d,\vp)T(\varepsilon^{-1},1,\vp)\} \quad \forall \varepsilon > , d \in \mathbb{N}
-\] Let
+\text{comp}(\varepsilon,d) \leq C_{\vp}\exp\{(T(0,d,\vp))(T(\varepsilon^{-1},d,\vp)\} \quad \forall \varepsilon > , d \in \mathbb{N}
+\] Given that $\lambda_{i,d}$ are non-increasing, it follows that $T$ is increasing in its arguments, hence we have the following arguments from previous theorems, i.e.,
+\[
+\text{comp}(\varepsilon,d) \leq \left(T(\varepsilon^{-1},d,\vp)\right)^{T(0,d,\vp)}\sum_{j=1}^\infty\left[\frac{1}{T(\lambda^{-1}_{j,d},d,\vp)}\right]^{T(0,d,\vp)}
+\]
+Now, we have the following upper bound on the complexity as follows
+\begin{align*}
+    \comp(\varepsilon,d) &\leq T(\varepsilon^{-1},d,\vp)^{T(0,d,\vp)}\sum_{j=1}^\infty\left[\frac{1}{T(\lambda^{-1}_{j,d},d,\vp)}\right]^{T(0,d,\vp)}\\
+    &\leq T(\varepsilon^{-1},d,\vp)^{T(0,d,\vp)}\left[\sum_{j=1}^{C_{\vp}-1}\left[\frac{1}{T(\lambda^{-1}_{j,d},d,\vp)}\right]^{T(0,d,\vp)} + \sum_{j=C_{\vp}}^\infty\left[ \frac{1}{T(\lambda_{j,d}^{-1},d,\vp)}\right]^{T(0,d,\vp)}\right]\\
+     & \le T(\varepsilon^{-1},d,\vp)^{T(0,d,\vp)}\left[ \left[\frac{C_{\vp}-1}{T(\lambda_{\max}^{-1},d,\vp)}\right]^{T(0,d,\vp)} + M_{\vp}\right]
+        \qquad \text{by \eqref{thmqpt}} \\
+       & \le T(\varepsilon^{-1},d,\vp)^{T(0,d,\vp)}\left[(C_{\vp})^{T(0,d,\vp)} + M_{\vp}\right]\\ 
+       & \le \left(C_{\vp}\,T(\varepsilon^{-1},d,\vp)\right)^{T(0,d,\vp)} + M_{\vp}\, T(\varepsilon^{-1},d,\vp)^{T(0,d,\vp)}\\
+       & \le C_{\vp}\,T(\varepsilon^{-1},d,\vp)^{T(0,d,\vp)}
+\end{align*}
+%It follows that we have $T$-quasi-polynomial tractability.
 \end{proof}
+\kachi{To do: Find an example for this case.}
 

### 2023-04-18 Older_versions/GeneralizedTractability_230411.tex
Fred M2 2023 Mac Updates

--- 2023-04-13 GeneralizedTractability_230411.tex
@@
 
-Let $h:[0,\infty) \to [1,\infty)]$ satisfy
+Let $h:[0,\infty) \to [1,\infty)$ satisfy
 \begin{equation} \label{eq:h_cond}
 	h \text{ is strictly increasing}, \qquad 
-	h(0)=1, \qquad  [h(x)]^\tau \le h(\tau x) \quad \forall x \ge 0, \tau > 1.
+	h(0)=1, \qquad  [h(x)]^c \le h(c x) \quad \forall x \ge 0, c > 0.
 \end{equation}
+\peter{Let us make the slightly stronger assumption on $h$ that
+\[
+h(x)\cdot h(y) \le h(x+y)\quad \forall x,y\in [0,\infty),
+\]
+and let us denote the inverse function of $h$ by $h^{-1}$. 
+Then, for arbitrary $z,w \in [1,\infty)$ we choose $x=h^{-1}(z)$ and $y=h^{-1}(w)$, to obtain
+\[
+z w \le h (h^{-1}(z)+h^{-1}(w)),
+\]
+which yields by the monotonicity of $h^{-1}$ that
+\begin{equation}\label{eq:submult_h_inverse}
+h^{-1}(z w) \le h^{-1}(z)+h^{-1}(w).
+\end{equation}
+}
+
+\fred{There is a problem here because I was assuming that 
+\[
+\lim_{x \to \infty} \frac{f(x)}{g(x)} = 0 \iff 
+\lim_{x \to \infty} \frac{\log(f(x))}{\log(g(x))} = 0.
+\]
+But this is NOT the case, e.g., $f(x) = x^2$ and $g(x) = x^4$.  So we may need 
+\begin{definition} \label{def:subhT}
+	A problem is sub-$h \circ T$ tractable if
+	\begin{equation*}
+		\lim_{\varepsilon^{-1} + d \to \infty} \frac{h^{-1}(\comp(\varepsilon,d))}{T(\varepsilon^{-1},d,\vp)} = 0.
+	\end{equation*}
+\end{definition}
+And NOT what I had below.}
 
@@
 	\begin{equation*}
-		\lim_{\varepsilon^{-1} + d \to \infty} \frac{\comp(\varepsilon,d)}{h(cT(\varepsilon^{-1},d,\vp))} = 0 \qquad \text{\sout{$\forall c>0$}}
+		\lim_{\varepsilon^{-1} + d \to \infty} \frac{\comp(\varepsilon,d)}{h(T(\varepsilon^{-1},d,\vp))} = 0.
 	\end{equation*}
@@
 S_c \, h(cT(\varepsilon^{-1},d))  
-\right\rceil.  
+\right\rceil \qquad \forall c > 0.  
 \]
 
-Consequently,
+\peter{
+We could go on like this:
+
+It is no loss of generality to assume that $S_c \ge 1$. From above we get 
+\[
+h^{-1}(\comp(\varepsilon,d)) \le h^{-1} \left( \left\lceil 
+S_c \, h(cT(\varepsilon^{-1},d))  
+\right\rceil \right) \le h^{-1} \left(  
+2 S_c \, h(cT(\varepsilon^{-1},d))  
+ \right) \qquad \forall c > 0,
+\]
+where we used that the argument of the ceiling function is at least one.
+
+From this we deduce, by \eqref{eq:submult_h_inverse},
+\[
+h^{-1}(\comp(\varepsilon,d)) \le
+ h^{-1} (2 S_c) + cT (\varepsilon^{-1},d).
+\]
+Now, for sufficiently large $\varepsilon^{-1}+d$, we must have
+\[
+c T (\varepsilon^{-1},d) \ge h^{-1} (2 S_c).
+\]
+This is because the finiteness of $S_c$ implies that $\lim_{\varepsilon \to 0} T(\varepsilon^{-1},d) = \infty$ for all $d \in \naturals$,  together with the hypothesis on $\lim_{d \to \infty} T(\varepsilon^{-1},d)$.
+So, 
+\[
+h^{-1}(\comp(\varepsilon,d)) \le 2 cT (\varepsilon^{-1},d).
+\]
+Since the latter holds for any $c>0$, we have sub-$h\circ T$-tractability.
+
+}
+
+Consequently, choosing $c=1/2$, it follows that 
 \begin{align}
 \nonumber
-\lim_{\varepsilon^{-1} + d \to \infty} \frac{\comp(\varepsilon,d)}{ h(2cT(\varepsilon^{-1},d))  }
+\lim_{\varepsilon^{-1} + d \to \infty} \frac{\comp(\varepsilon,d)}{ h(T(\varepsilon^{-1},d))  }
+& = \lim_{\varepsilon^{-1} + d \to \infty} \frac{\comp(\varepsilon,d)}{ h(2cT(\varepsilon^{-1},d))  } \\
 & \le \lim_{\varepsilon^{-1} + d \to \infty} \frac{ \left\lceil 
@@
 This implies that the limit in \eqref{eq:alastone} vanishes.
-Since $c$ is arbitrary, we have satisfied the condition of Definition \ref{def:subhT}.
 
@@
 \noindent \textbf{Necessary Condition:}\\
-Suppose that the problem is  sub-$h \circ T$ tractable. Then, for any $c>0$ there exists a positive integer $V_c$ such that  
+Suppose that the problem is  sub-$h \circ T$ tractable.
+Then, for any $c>0$ there exists a positive integer $V_c$ such that  \fred{having a little trouble removing the $c$ here.} \peter{Here we do not need to remove the $c$, and actually shouldn't.
+Just in the limit relation it was not necessary.}
 \[
@@
 \]
-By the definition of complexity in \eqref{eq:comp_def}, it follows that 
+By the definition of the information complexity in \eqref{eq:comp_def}, it follows that 
 \[
 	\lambda_{n(\varepsilon,d,c),d} \le \varepsilon \quad \forall \varepsilon^{-1} + d \ge V_c, \qquad \text{where }
-	n(\varepsilon,d,c):=\left\lfloor h(cT(\varepsilon^{-1},d)) \right\rfloor.
+	n(\varepsilon,d,c):=\left\lfloor h(cT(\varepsilon^{-1},d)) \right\rfloor \peter{+1}.
 \]
@@
 \begin{equation}
-		n(\varepsilon,d,c)\le  h(cT(\varepsilon^{-1},d)) \le  h(cT(\lambda^{-1}_{n(\varepsilon,d,c),d},d)) \qquad  \quad \forall \varepsilon^{-1} + d \ge V_c. \label{eq:nedcbound}
+		n(\varepsilon,d,c)\le  h(cT(\varepsilon^{-1},d)) \peter{+1}\le  h(cT(\lambda^{-1}_{n(\varepsilon,d,c),d},d)) \peter{+1}\qquad  \quad \forall \varepsilon^{-1} + d \ge V_c. \label{eq:nedcbound}
 \end{equation}
@@
 \begin{equation} \label{eq:nstardef}
-	\varepsilon^{-1}_{\max}(d,c) := \max(V_c - d,\lambda_{\max}^{-1}), \qquad n^*(d,c) : = n(\varepsilon^{-1}_{\max}(d,c),d,c) \le h(cT(\varepsilon^{-1}_{\max}(d,c),d)).
+	\varepsilon^{-1}_{\max}(d,c) := \max(V_c - d,\lambda_{\max}^{-1}), \qquad n^*(d,c) : = n(\varepsilon^{-1}_{\max}(d,c),d,c) \le h(cT(\varepsilon^{-1}_{\max}(d,c),d)) \peter{+1}.
 \end{equation} 
@@
 \]
-Recalling that $T$ is non-decreasing in it's arguments, this implies that 
+Recalling that $T$ is non-decreasing in its arguments, this implies that 
 \begin{align*}

### 2023-04-20 GeneralizedTractability_230418.tex
Updates from Overleaf

--- 2023-04-18 Older_versions/GeneralizedTractability_230411.tex
@@
 \newtheorem{definition}{Definition}
+\newtheorem{example}{Example}
 
@@
 The goal is to find an approximate solution, $\APP_d:\cb_d \times (0,\infty) \to \cg_d$ satisfying
-\[
-\norm[\cg_d]{\SOL_d(f) - \APP_d(f,\varepsilon)} \le \varepsilon,
-\]
+\begin{equation}
+    \label{eq:errcrit}
+    \norm[\cg_d]{\SOL_d(f) - \APP_d(f,\varepsilon)} \le \varepsilon \qquad \forall f \in \cb_d, \ \varepsilon \in (0,\infty)
+\end{equation}
 where $\cb_d$ is the unit ball in $\cf_d$ and $\APP_d(f,\varepsilon)$ is allowed to depend on arbitrary linear functionals \peter{(note that we also allow adaptive information, i.e., the linear functionals may sequentially depend on each other)}.
-In this case, the optimal solution is
+
+The information complexity of the problem $\SOL_d$ is denoted $\comp(\varepsilon,d)$ and defined as the minimum number of linear functionals required to satisfy the error criterion \eqref{eq:errcrit},
+\begin{equation*}
+\comp:(0,\infty) \times \naturals \to \natzero.
+\end{equation*}
+By definition, the complexity is non-decreasing  as $\varepsilon$ tends to zero.  We also expect it to be non-decreasing as $d$ tends to infinity.  \peter{This means that we are actually considering 
+a whole sequence of problems  $\SOL_d : \cf_d \to \cg_d$, for $d\in\naturals$, and we furthermore assume} that the Hilbert spaces are defined in such a way that $\lambda_{\cdot,d}$ is non-decreasing for every $d$, as spelled out in \eqref{eq:eigenvalues}, although this assumption is not needed for our results.
+
+For this case where arbitrary linear functionals are allowed, the optimal solution is
 \[
@@
 \begin{equation}\label{eq:comp_def}
-\comp(\varepsilon, d) = \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon\}.
+\comp(\varepsilon, d) = \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon\}, \qquad \comp:(0,\infty) \times \naturals \to \natzero.
 \end{equation}
-
-By definition, the complexity is non-decreasing  as $\varepsilon$ tends to zero.  We also expect it to be non-decreasing as $d$ tends to infinity.  \peter{This means that we are actually considering 
-a whole sequence of problems  $\SOL_d : \cf_d \to \cg_d$, for $d\in\naturals$, and we furthermore assume} that the Hilbert spaces are defined in such a way that $\lambda_{\cdot,d}$ is non-decreasing for every $d$, as spelled out in \eqref{eq:eigenvalues}, although this assumption is not needed for our results.
 
@@
 
-\peter{TODO: Maybe add a short paragraph on notation used in the paper and on its structure? In particular, we should introduce 
-an ordering of the parameters $\vp$.}
+\peter{TODO: Maybe add a short paragraph on the notation used in the paper and on its structure? In particular, we should introduce 
+an ordering of the parameters $\vp$.}\\
+\kachi{Throughout the article, we use the following notation.}\\
 
-\section{(Strong) Tractability}
+\kachi{In Section \ref{sec:spt}, we give the definitions of the considered tractability notions, in particular (strong) tractability.
+We then consider the strong tractability where the complexity is independent of the dimension, $d$.
+We then turn to tractability.
+In Section \ref{sec:examples} we provided examples of strong(traceability) functions for both the algebraic and exponential cases.
+}
+
+\section{(Strong) Tractability}\label{sec:spt}
 
@@
 
-\paragraph{Example 1: Strong polynomial tractability}
+\begin{example}[Strong polynomial tractability]
 
-Let $T: (0,\infty) \times \naturals \times [0,\infty) \times [0,\infty)\Rightarrow [1,\infty)$
+Let $ T :(0,\infty) \times \mathbb{N} \times [0,\infty)^s \rightarrow (0,\infty)$
 be defined by
@@
 This essentially recovers the result on strong polynomial tractability in \cite[Theorem 5.1]{NW08}
+\end{example}
 
-\paragraph{Example 2: Polynomial tractability}
-
-Let $T: (0,\infty) \times \naturals \times [0,\infty) \times [0,\infty)\Rightarrow [1,\infty)$
+\begin{example}[Polynomial traceability]
+Let $ T :(0,\infty) \times \mathbb{N} \times [0,\infty)^s \rightarrow (0,\infty)$
 be defined by
@@
 This essentially recovers the result on polynomial tractability in \cite[Theorem 5.1]{NW08}
+\end{example}
 
 \peter{(PETER: Add further examples (e.g., EXP- polynomial tractability, etc.)}
+\kachi{\begin{example}[EXP-strong polynomial tractability]
+Let $ T :(0,\infty) \times \mathbb{N} \times [0,\infty)^s \rightarrow (0,\infty)$
+be defined by
+\[
+ T(\varepsilon^{-1},d,\vp)= (1+\log\max\{\varepsilon^{-1},1\})^p.
+\]
+Then Theorem \ref{thm_main_tract2} yields the iff-condition
+\[
+ \sup_{d\in\naturals} \sum_{i=L_{\vp} d^{q_1}}^\infty (\min\{\lambda_{i,d},1\})^p  < \infty.
+\]
+\end{example}
+\begin{example}[EXP-polynomial traceability]
 
+Let $ T :(0,\infty) \times \mathbb{N} \times [0,\infty)^s \rightarrow (0,\infty)$
+be defined by
+\[
+ T(\varepsilon^{-1},d,\vp)= (1+\log \max\{\varepsilon^{-1},1\})^p\, d^q.
+\]
+Then Theorem \ref{thm_main_tract2} yields the iff-condition
+\[
+ \sup_{d\in\naturals} \sum_{i=L_{\vp} d^{q_1}}^\infty (\min\{\lambda_{i,d},1\})^p d^{-q} < \infty.
+\]
+\end{example}}
 \bigskip
@@
 \end{definition}
-\begin{definition}[Quasi-polynomial Tractability]
-    The problem is \emph{quasi-polynomially tractable}, if there exist two constants $C, t> 0$ such that
-    \[
-    n(\varepsilon,d) \leq C\exp\{t(1+\ln(\varepsilon^{-1}))(1+\ln(d))\}
-    \] for all $\varepsilon \in (0,1)$ and $d\in\mathbb{N}$.
-\end{definition}
+%\begin{definition}[Quasi-polynomial Tractability]
+ %   The problem is \emph{quasi-polynomially tractable}, if there exist two constants $C, t> 0$ such that
+  %  \[
+   % n(\varepsilon,d) \leq C\exp\{t(1+\ln(\varepsilon^{-1}))(1+\ln(d))\}
+    %\] for all $\varepsilon \in (0,1)$ and $d\in\mathbb{N}$.
+%\end{definition}
 
@@
 }
-\paragraph{Example 3: EXP-strong polynomial tractability}
 
-Let $T: (0,\infty) \times \naturals \times [0,\infty) \times [0,\infty)\Rightarrow [1,\infty)$
+%\paragraph{Example 5: $(t,s)$-Weak tractability}
+%Let $ T :(0,\infty) \times \mathbb{N} \times [0,\infty)^s \rightarrow (0,\infty)$. Suppose we have $T$-$(s,t)$- weak tractability, such that
+%\[ \lim_{d+\varepsilon^{-1}\rightarrow\infty} \frac{\log \max(1,n(\varepsilon,d))}{d^t +(\max(1,\varepsilon^{-1}))^s} =0.\]
+%Then Theorem \ref{thm:weak} yields the iff-condition
+%\[
+%\sup_{d\in\naturals} \sigma (c,d,s,\vp) \exp\left(-c\, T(0,d^t,\vp)\right)<\infty
+%\]
+%where $\displaystyle\sigma (c,d,s,\vp) =\sum_{i=1}^\infty \exp\left(-c\left(\lambda^{-1}_{i,d}\right)^{s/2}\right) $
+\kachi{
+\begin{example}[Quasi-$T$-polynomial tractability] 
+\begin{definition}
+    As defined in \cite{GW11}, we say that a problem is \emph{quasi-polynomially tractable} if there exist two constants $C$, $t > 0$, such that
+\[
+n(\varepsilon,d) \leq C\exp\{t(1+\ln(\varepsilon^{-1}))(1+\ln(d))\}\] 
+for all $\varepsilon \in (0,1)$ and $d\in\mathbb{N}$.\\
+\end{definition}
+Suppose $ T :(0,\infty) \times \mathbb{N} \times [0,\infty)^s \rightarrow (0,\infty)$
 be defined by
 \[
- T(\varepsilon^{-1},d,\vp)= (1+\log\max\{\varepsilon^{-1},1\})^p.
+ T(\varepsilon^{-1},d,\vp)= \exp\{\vp(1+\ln d)(1+\ln \max(\varepsilon^{-1},1))\}
 \]
-Then Theorem \ref{thm_main_tract2} yields the iff-condition
+\end{example}
+
+Then Theorem \ref{sec:tractability} yields the iff-condition as follows
+
 \[
- \sup_{d\in\naturals} \sum_{i=L_{\vp} d^{q_1}}^\infty (\min\{\lambda_{i,d},1\})^p  < \infty.
+\sup_{d\in\mathbb{N}}\sum_{i=Lpd^{q_1}} \left(\min\{\lambda_{i,d},1\} \right)^{p(1+\ln d)}d^{-q} < \infty
 \]
-\paragraph{Example 4: EXP-polynomial tractability}
+}
 
-Let $T: (0,\infty) \times \naturals \times [0,\infty) \times [0,\infty)\Rightarrow [1,\infty)$
-be defined by
-\[
- T(\varepsilon^{-1},d,\vp)= (1+\log \max\{\varepsilon^{-1},1\})^p\, d^q.
-\]
-Then Theorem \ref{thm_main_tract2} yields the iff-condition
-\[
- \sup_{d\in\naturals} \sum_{i=L_{\vp} d^{q_1}}^\infty (\min\{\lambda_{i,d},1\})^p d^{-q} < \infty.
-\]
-\paragraph{Example 5: $(t,s)$-Weak tractability}
-
-Let $T: (0,\infty) \times \naturals \times [0,\infty) \times [0,\infty)\Rightarrow [1,\infty)$. Suppose we have $T$-$(s,t)$- weak tractability, such that
-\[
- \lim_{d+\varepsilon^{-1}\rightarrow\infty} \frac{\log \max(1,n(\varepsilon,d))}{d^t +(\max(1,\varepsilon^{-1}))^s} =0.
-\]
-Then Theorem \ref{thm:weak} yields the iff-condition
-\[
-\sup_{d\in\naturals} \sigma (c,d,s,\vp) \exp\left(-c\, T(0,d^t,\vp)\right)<\infty
-\]
-where $\sigma (c,d,s,\vp) = $
-
-\section{$T$-Quasi-polynomial tractability} \label{sec:qpt}
-
-\begin{definition}[$T$-Quasi-polynomial tractability]
-We say that the problem is \emph{$T$- quasi-polynomial tractable} if there exists positive $C_{\vp}$ such that
-   %\[ n(\varepsilon,d)\leq C_{\vp}\exp\{(T(0,d,\vp))(T(\varepsilon^{-1},1,\vp)\}\]
-   \[ n(\varepsilon,d)\leq C_{\vp}\exp\{(T(\varepsilon^{-1},d,\vp)\}\]
-\end{definition}
-
-\begin{theorem}\label{thm:qpt}
-A problem is $T$-quasi-polynomial tractable iff there exists $\vp \in [\vzero, \boldsymbol{\infty})$ such that
-\begin{equation}\label{thmqpt}
-M_{\vp} := \sup_{d\in\mathbb{N}}\sum_{i=1}^\infty \frac{1}{T(\lambda_{i,d}^{-1},d,\vp)}
-<\infty
-\end{equation}
-%where $\Bar{p} = -p(1+\log(T(0,d,\vp))$.
-%If it holds then 
-%\[n(\varepsilon,d)\leq 1+T(0,d^\tau,\vp)+ T(0,d^\tau,\vp)T(\varepsilon^{-1},1,\vp)\]
-\end{theorem}
-\begin{proof}
-\textbf{Necessity Condition:}\\
-Suppose that we have $T$-quasi-polynomial tractability, i.e., for some $\vp\geq 0$, there exists positive $C_{\vp}$ such that
-%\[\comp(\varepsilon,d)\le C_{\vp}\exp\{(T(0,d,\vp)(T(\varepsilon^{-1},1,\vp))\}\quad\quad \forall\varepsilon >0, d\in \mathbb{N}\] 
-\[
-\comp(\varepsilon,d)\le C_{\vp}\exp\{T(\varepsilon^{-1},d,\vp)\}
-\quad\quad \forall\varepsilon >0, d\in \mathbb{N}
-\] 
-Since $\lambda_{i,d}$ are non-increasing, we have
-\[
-\lambda_{\left\lfloor C_{\vp}\exp\{T(\varepsilon^{-1},d,\vp)\}\right\rfloor+1,d}\leq \varepsilon^2
-\]
-Given that the estimate holds for all $\varepsilon> 0$, we assume that $\varepsilon \in (0, 1]$.\\
-
-If we vary $\varepsilon\in (0,1]$, we have that
-\[
-j(\varepsilon,d,\vp) = \left\lfloor C_{\vp}\exp\{T(\varepsilon^{-1},d,\vp)\}\right\rfloor+1
-\] which attains the values $j = j_d,j_{d+1},\dots$, where
-\[
-j(\infty,d,\vp)=j_d = \lfloor C_{\vp}\exp\{ T(0,d,\vp)\}\rfloor + 1
-\]
-Furthermore, we have
-\[j \leq C_{\vp}\exp\{T(\varepsilon^{-1},d,\vp)\}+1 \leq C_{\vp}\exp\{T(\lambda^{-1}_{j,d},d,\vp)\}+1 \]
-This implies that for $\tau>1$, we have
-%\[\left(\log\frac{j-1}{C_{\vp}}\right)^\tau \leq \left(T(\varepsilon^{-1},d,\vp)\right)^\tau \leq K_{\vp,\tau}T(\lambda_{j,d},d,\tau\vp) \]
-we have 
-%\[\frac{1}{T(\lambda_{i,d}^{-1},d,\vp)} \leq \frac{K_{\vp,\tau}}{\left(\log\frac{j-1}{C_{\vp}}\right)^\tau}\]
-\end{proof}
-
-\section{Fred's Attempt at sub-$h$ $T$-Tractability}
-May we frame weak tractability more generally?
-
-Let $h:[0,\infty) \to [1,\infty)$ satisfy
+\section{Sub-$h$ Tractability}
+In this section we generalize the concept of weak tractability \cite{}.  Let  $h:[0,\infty) \to [1,\infty)$ satisfy
 \begin{equation} \label{eq:h_cond}
 	h \text{ is strictly increasing}, \qquad 
-	h(0)=1, \qquad  [h(x)]^c \le h(c x) \quad \forall x \ge 0, c > 0.
+	h(0)=1, \qquad  
+ h(x+y) \ge  h(x)\cdot h(y)  \quad \forall x,y \ge 0.
 \end{equation}
-\peter{Let us make the slightly stronger assumption on $h$ that
-\[
-h(x)\cdot h(y) \le h(x+y)\quad \forall x,y\in [0,\infty),
-\]
-and let us denote the inverse function of $h$ by $h^{-1}$. 
+This means that $\log(h(\cdot))$ is a superadditive function.  The function $h$ here can be thought of as the exponential function for weak tractability.
+
+Furthermore, let us denote the inverse function of $h$ by $h^{-1}$. 
 Then, for arbitrary $z,w \in [1,\infty)$ we choose $x=h^{-1}(z)$ and $y=h^{-1}(w)$, to obtain
@@
 \end{equation}
-}
-
-\fred{There is a problem here because I was assuming that 
-\[
-\lim_{x \to \infty} \frac{f(x)}{g(x)} = 0 \iff 
-\lim_{x \to \infty} \frac{\log(f(x))}{\log(g(x))} = 0.
-\]
-But this is NOT the case, e.g., $f(x) = x^2$ and $g(x) = x^4$.  So we may need 
+Now we define a generalized notion of weak tractability.
 \begin{definition} \label{def:subhT}
@@
 	\begin{equation*}
-		\lim_{\varepsilon^{-1} + d \to \infty} \frac{h^{-1}(\comp(\varepsilon,d))}{T(\varepsilon^{-1},d,\vp)} = 0.
+		\lim_{\varepsilon^{-1} + d \to \infty} \frac{h^{-1}(\max(1,\comp(\varepsilon,d)))}{T(\varepsilon^{-1},d,\vp)} = 0.
 	\end{equation*}
 \end{definition}
-And NOT what I had below.}
 
-\begin{definition} \label{def:subhT}
-	A problem is sub-$h \circ T$ tractable if
-	\begin{equation*}
-		\lim_{\varepsilon^{-1} + d \to \infty} \frac{\comp(\varepsilon,d)}{h(T(\varepsilon^{-1},d,\vp))} = 0.
-	\end{equation*}
-\end{definition}
+\fred{Can we say that this notion of tractabilty is stronger or weaker than $\comp(\varepsilon,d)/h(T(\varepsilon^{-1},d,\vp)) \to 0$ as $\varepsilon^{-1} + d \to \infty$?}
 
@@
 \begin{thebibliography}{99}
-
+\bibitem{GW11} M. Gnewuch, H.~~Wo\'zniakowski. Quasi-polynomial tractability, J.~Complexity, 27, 312--330 2011.
 \bibitem{HKW19} F.J.~Hickernell, P. Kritzer, H.~Wo\'zniakowski.  Exponential tractability of linear tensor product problems. In: 
@@
  \bibitem{WW17} A.G.~Werschulz, H.~Wo\'zniakowski. A new characterization of $(s,t)$-weak tractability. J. Complexity 38, 68--79, 2017.
+
 \end{thebibliography}

### 2023-04-20 GeneralizedTractability_230418.tex
Updates from Overleaf

@@
 an ordering of the parameters $\vp$.}\\
-\kachi{Throughout the article, we use the following notation.}\\
+%\kachi{Throughout the article, we use the following notation.}\\
 
 \kachi{In Section \ref{sec:spt}, we give the definitions of the considered tractability notions, in particular (strong) tractability.
-We then consider the strong tractability where the complexity is independent of the dimension, $d$.
-We then turn to tractability.
-In Section \ref{sec:examples} we provided examples of strong(traceability) functions for both the algebraic and exponential cases.
+We consider the strong tractability when the information complexity is independent of the dimension, $d$.
+We then turn to tractability  when the information complexity is polynomial in $d$ and $\varepsilon^{-1}$.
+In Section \ref{sec:examples} we provide examples of strong(tractability) functions for both the algebraic and exponential cases.
+We also consider other notions of tractability such as quasi-polynomial tractability, and a generalized notion of weak tractability.
+In the case of the generalized weak tractability, we give the necessary and sufficient conditions on the notion of exponential tractability in Section \ref{sec:subh}.
 }
@@
 
-\begin{example}[Polynomial traceability]
+\begin{example}[Polynomial tractability]
 Let $ T :(0,\infty) \times \mathbb{N} \times [0,\infty)^s \rightarrow (0,\infty)$
@@
 \end{example}
-\begin{example}[EXP-polynomial traceability]
+\begin{example}[EXP-polynomial tractability]
 
@@
 \begin{definition}
-    As defined in \cite{GW11}, we say that a problem is \emph{quasi-polynomially tractable} if there exist two constants $C$, $t > 0$, such that
-\[
-n(\varepsilon,d) \leq C\exp\{t(1+\ln(\varepsilon^{-1}))(1+\ln(d))\}\] 
-for all $\varepsilon \in (0,1)$ and $d\in\mathbb{N}$.\\
+    As defined in \cite{GW11}, we say that a problem is \emph{ quasi-polynomially tractable (QPT)} if there exist two constants $C$, $t > 0$, such that
+\begin{equation}\label{expqpt}
+    n(\varepsilon,d) \leq C\exp\{t(1+\log(\varepsilon^{-1}))(1+\log(d))\}
+\end{equation}
+for all $\varepsilon \in (0,1]$ and $d\in\mathbb{N}$.\\
 \end{definition}
@@
 \[
- T(\varepsilon^{-1},d,\vp)= \exp\{\vp(1+\ln d)(1+\ln \max(\varepsilon^{-1},1))\}
+ T(\varepsilon^{-1},d,\vp)= \exp\{\vp(1+\log d)(1+\log\max\{\varepsilon^{-1},1\})\}
 \]
-\end{example}
+Observe that this is a special case of the $T$-tractability function, where the function is polynomial in exponent $1+\log d$ and $1+\log\max\{\varepsilon^{-1},1\}$.
 
@@
 \]
+\end{example}
 }
 
-\section{Sub-$h$ Tractability}
+\section{Sub-$h$ Tractability}\label{sec:subh}
 In this section we generalize the concept of weak tractability \cite{}.  Let  $h:[0,\infty) \to [1,\infty)$ satisfy
@@
 \begin{definition} \label{def:subhT}
-	A problem is sub-$h \circ T$ tractable if
+	A problem is sub-$h$-$T$ tractable for parameter $\vp > \vzero$ if
 	\begin{equation*}
@@
 	Let $T$ be a tractability function as specified in \eqref{eq:Tspec} and satisfying \eqref{eq:Tconditions}.
-Moreover, let $\lim_{d \to \infty} T(\varepsilon^{-1},d) = \infty$ for all $\varepsilon > 0$.
-The problem is sub-$h \circ T$ tractable if and only if
+Moreover, let $\lim_{d \to \infty} T(\varepsilon^{-1},d,\vp) = \infty$ for all $\varepsilon > 0$, $\vp > \vzero$.
+The problem is sub-$h$-$T$ tractable if and only if
 	\[

### 2023-04-21 GeneralizedTractability_230418.tex
Updates from Overleaf

@@
 
-Let $\cf_d$ and $\cg_d$ be Hilbert spaces, and $\SOL_d : \cf_d \to \cg_d$ be a linear solution operator  with adjoint $\SOL_d^*$ such that $\SOL_d^*\SOL_d : \cf_d \to \cf_d$ has eigenvalues and orthonormal eigenvectors
+Let $\{\cf_d\}_{d \in \naturals}$ and $\{\cg_d\}_{d \in \naturals}$ be sequences of Hilbert spaces, and $\{\SOL_d : \cf_d \to \cg_d\}_{d \in \naturals}$ be a sequence of linear solution operators  with adjoints $\SOL_d^*$ such that $\SOL_d^*\SOL_d : \cf_d \to \cf_d$ has eigenvalues and orthonormal eigenvectors
 \begin{equation} \label{eq:eigenvalues}
@@
 \end{equation}
-This means that the non-negative $\lambda_{i,d}$ are the singular values of the \peter{operator} $\SOL_d$. 
+This means that the non-negative $\lambda_{i,d}$ are the singular values of the operator $\SOL_d$.
+We remark that in the literature on Information-Based Complexity the singular values of $\SOL_d$ are often denoted by $\sqrt{\lambda_{i,d}}$ instead of $\lambda_{i,d}$.
+However, since we assume non-negativity of the $\lambda_{i,d}$, the notation used here is equivalent.
+The non-decreasing ordering of the eigenvalues for each $d$ facilitates the proof of conditions for tractability, but our conditions do not depend on the ordering.
+
 We make the technical assumption that $\SOL_d$ is a compact operator.
-This implies (see, e.g., \cite{NW08}) that the $\lambda_{i,d}$ converge to zero as $i$ tends to infinity, which in turn implies that the problem is solvable by suitable algorithms.
+This implies (see, e.g., \cite{NW08}) that $\lambda_{i,d}$ converges to zero as $i$ tends to infinity for every $d$, which in turn implies that the problem is solvable by suitable algorithms.
+To avoid trivial cases, we assume that there are an infinite number of positive eigenvalues.
 
-To avoid trivial cases, we assume that there are an infinite number of positive eigenvalues.
-\peter{We remark that in the literature on Information-Based Complexity the singular values of $\SOL_d$ are often denoted by $\sqrt{\lambda_{i,d}}$ instead of $\lambda_{i,d}$.
-However, since we assume non-negativity of the $\lambda_{i,d}$, the notation used here is equivalent.}
-
-The goal is to find an approximate solution, $\APP_d:\cb_d \times (0,\infty) \to \cg_d$ satisfying
+The goal is to find a sequence of approximate solution operators, $\{\APP_d:\cb_d \times (0,\infty) \to \cg_d\}_{d \in \naturals}$ satisfying
 \begin{equation}
@@
 \end{equation}
-where $\cb_d$ is the unit ball in $\cf_d$ and $\APP_d(f,\varepsilon)$ is allowed to depend on arbitrary linear functionals \peter{(note that we also allow adaptive information, i.e., the linear functionals may sequentially depend on each other)}.
+where $\cb_d$ is the unit ball in $\cf_d$ and $\APP_d(f,\varepsilon)$ is allowed to depend on arbitrary linear functionals.
+Note that we also allow adaptive information, i.e., the linear functionals may sequentially depend on each other.
 
-The information complexity of the problem $\SOL_d$ is denoted $\comp(\varepsilon,d)$ and defined as the minimum number of linear functionals required to satisfy the error criterion \eqref{eq:errcrit},
-\begin{equation*}
-\comp:(0,\infty) \times \naturals \to \natzero.
-\end{equation*}
-By definition, the complexity is non-decreasing  as $\varepsilon$ tends to zero.  We also expect it to be non-decreasing as $d$ tends to infinity.  \peter{This means that we are actually considering 
-a whole sequence of problems  $\SOL_d : \cf_d \to \cg_d$, for $d\in\naturals$, and we furthermore assume} that the Hilbert spaces are defined in such a way that $\lambda_{\cdot,d}$ is non-decreasing for every $d$, as spelled out in \eqref{eq:eigenvalues}, although this assumption is not needed for our results.
+The information complexity of the problem $\SOL_d$ is given by the function $\comp:(0,\infty) \times \naturals \to \natzero$, where $\comp(\varepsilon,d)$ is the minimum number of linear functionals required to satisfy the error criterion \eqref{eq:errcrit}.
+By definition, the complexity is non-decreasing  as $\varepsilon$ tends to zero.
+We also expect it to be non-decreasing as $d$ tends to infinity, since $d$ is typically the number of variables for the functions in $\cf_d$.
 
@@
 
-The question is,``How hard is this problem as $\varepsilon$ tends to zero or as $d$ tends to infinity?''  We want to bound the complexity in terms of a simple function of $\varepsilon$ and $d$ and identify simple conditions on the singular values that are equivalent to this bound holding.
+The question of tractability is one of determining how fast the complexity increases as $\varepsilon$ tends to zero and/or as $d$ tends to infinity.
+We want to bound the complexity in terms of a simple function of $\varepsilon^{-1}$ and $d$ and identify simple conditions on the singular values that are equivalent to this bound holding.
 

### 2023-04-21 GeneralizedTractability_230418.tex
Fred's Home Computer

@@
 \]
-and the \peter{information} complexity of our linear problem is
+and the information complexity of our linear problem is
 \begin{equation}\label{eq:comp_def}
@@
 
-A problem is defined as $T$-tractable with parameter $\vp$ iff there exists a positive constant $C_{\vp}$, \peter{which is independent of $\varepsilon$ and $d$,} such that
+A problem is defined as $T$-tractable with parameter $\vp$ iff there exists a positive constant $C_{\vp}$, which is independent of $\varepsilon$ and $d$, such that
 \begin{equation} \label{eq:tract_def}
@@
 A problem is \emph{strongly}
-$T$-tractable with parameter $\vp$ iff the complexity is independent of the dimension of the problem, that is, there exists a positive constant $C_{\vp}$, \peter{again independent of $\varepsilon$ and $d$,} such that
+$T$-tractable with parameter $\vp$ iff the complexity is independent of the dimension of the problem, that is, there exists a positive constant $C_{\vp}$, again independent of $\varepsilon$ and $d$, such that
 \begin{equation} \label{eq:strong_tract_def}
@@
 
-%Note that the tractability function is bounded below away from zero even as $\varepsilon \to \infty$ \peter{[PETER: Is it?]}, so that the information complexity is not expected to vanish under arbitrarily loose error requirements.
 For this definition of tractability to make sense we assume that
@@
 In the sections below we prove necessary and sufficient conditions on tractability as generally defined in \eqref{eq:tract_def} and \eqref{eq:strong_tract_def}.
-These conditions involve the boundedness of sums defined in terms of \peter{$(T(\lambda_{i,d}^{-1},\cdot, \cdot))_{i=1}^\infty$}.
-In practice, it may be easier to verify whether or not these conditions hold than to verify \peter{\eqref{eq:tract_def} and \eqref{eq:strong_tract_def}} directly.
+These conditions involve the boundedness of sums defined in terms of $(T(\lambda_{i,d}^{-1},\cdot, \cdot))_{i=1}^\infty$.
+In practice, it may be easier to verify whether or not these conditions hold than to verify \eqref{eq:tract_def and \eqref{eq:strong_tract_def}} directly.
 
@@
 \]
-%\peter{[PETER: Maybe using $\widetilde{\vp}$ instead of $\vp^\dagger$ in the definition of $\cp_{\textup{sopt}}$ is more intuitive?]}
 \end{theorem}
@@
 
-Since the $\lambda_{i,d}$ are non-increasing in $i$, it follows that the $T(\lambda_{i,d}^{-1},d',\vp)$ are non-decreasing in $i$ \peter{for any $d'\in\naturals$}.
+Since the $\lambda_{i,d}$ are non-increasing in $i$, it follows that the $T(\lambda_{i,d}^{-1},d',\vp)$ are non-decreasing in $i$ for any $d'\in\naturals$.
 In particular, for all $n\in \mathbb{N}$, we have
@@
        \comp(\varepsilon,d)
-       & \peter{\le} T(\varepsilon^{-1},1, \vp) \Biggl [ \sum_{i=1}^{L_{\vp}-1} \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}
+       & \le T(\varepsilon^{-1},1, \vp) \Biggl [ \sum_{i=1}^{L_{\vp}-1} \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}
        + \underbrace{\sum_{i=L_{\vp}}^\infty \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}}_{\le S_{\vp} <\infty\ \text{by \eqref{eq:strong_tractiff3}} }
@@
  \frac{1}{T (\lambda_{i,d}^{-1},1,\tau \vp)} \le
-\frac{K_{\vp,\tau}\, C_{\vp}^\tau}{(i-1)^\tau}\qquad \forall i \ge \peter{\max\{i(\infty,\vp),2\}} .
+\frac{K_{\vp,\tau}\, C_{\vp}^\tau}{(i-1)^\tau}\qquad \forall i \ge \max\{i(\infty,\vp),2\} .
 \end{gather*}
@@
 Suppose that \eqref{eq:tractiff4} holds for some $\vp \ge 0$.
-By the argument in the proof of the sufficient condition for Theorem \ref{thm_main_strong_tract2}, it follows from \eqref{eq:compUP} with $d'=d$ that the \peter{information} complexity has an upper bound of
+By the argument in the proof of the sufficient condition for Theorem \ref{thm_main_strong_tract2}, it follows from \eqref{eq:compUP} with $d'=d$ that the information complexity has an upper bound of
 \begin{equation*}
@@
 \end{equation*}
-%\peter{[PETER: Again, it seems to me we need +1.]}
 
@@
        \comp(\varepsilon,d)
-       & \peter{\le} T(\varepsilon^{-1},d,\vp) \Biggl [ \sum_{i=1}^{J(\vp,d) -1} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}
+       & \le T(\varepsilon^{-1},d,\vp) \Biggl [ \sum_{i=1}^{J(\vp,d) -1} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}
        + \underbrace{\sum_{i=J(\vp,d)}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}}_{\le S_{\vp} \text{ by \eqref{eq:tractiff4}}} 
@@
        & \le T(\varepsilon^{-1},d,\vp)\left[\frac{L_{\vp}\, T(0,d,\vp)}{T(\lambda_{\max}^{-1},1,\vp)} + S_{\vp} + \frac{1}{T(0,1, \vp)}\right] \\
-       & \peter{=}\frac{L_{\vp}}{T(\lambda_{\max}^{-1},1,\vp)} \,T(\varepsilon^{-1},d,\vp) T(0,d,\vp) + \left [  S_{\vp} + \frac{1}{T(0,1, \vp)}\right] T(\varepsilon^{-1},d,\vp)\\
+       & =\frac{L_{\vp}}{T(\lambda_{\max}^{-1},1,\vp)} \,T(\varepsilon^{-1},d,\vp) T(0,d,\vp) + \left [  S_{\vp} + \frac{1}{T(0,1, \vp)}\right] T(\varepsilon^{-1},d,\vp)\\
        & \le\frac{L_{\vp}}{T(\lambda_{\max}^{-1},1,\vp)} \,T(\varepsilon^{-1},d,\vp) T(\varepsilon^{-1},d,\vp) +\left [  S_{\vp} + \frac{1}{T(0,1, \vp)}\right] T(\varepsilon^{-1},d,\vp)\\
@@
 i (\varepsilon,d,\vp):= \lfloor C_{\vp}\, T(\varepsilon^{-1},d,\vp)\rfloor +1, \qquad
-i (\infty,d,\vp) \peter{:=} \lfloor C_{\vp}\, T(0,d,\vp)\rfloor +1 \ge 1.
+i (\infty,d,\vp) := \lfloor C_{\vp}\, T(0,d,\vp)\rfloor +1 \ge 1.
 \]
@@
 	 \frac{1}{T (\lambda_{i,d}^{-1},d,\tau \vp)} \le
-	\frac{K_{\vp,\tau}\, C_{\vp}^\tau}{(i-1)^\tau}\qquad \forall i \ge \peter{\max\{i(\infty,\vp),2\}}.
+	\frac{K_{\vp,\tau}\, C_{\vp}^\tau}{(i-1)^\tau}\qquad \forall i \ge \max\{i(\infty,\vp),2\}.
 \end{gather*}
@@
 Note that $i(\infty,d,\cdot)$ is non-decreasing.
-Summing both sides of the \peter{latter} inequality over $i$ from $i(\infty,d,\vp') + 1 \ge i(\infty,d, \vp) + 1 \ge 2$ to $\infty$ it follows that
+Summing both sides of the latter inequality over $i$ from $i(\infty,d,\vp') + 1 \ge i(\infty,d, \vp) + 1 \ge 2$ to $\infty$ it follows that
 \begin{equation*}
@@
 \begin{align*}
- i(\infty,d,\vp') +1  & = \lfloor C_{\vp'}\, T(0,d,\vp')\rfloor +2 \le  \left[C_{\vp'} + \frac{\peter{2}}{T(0,d,\vp')}   \right]\, T(0,d,\vp')\\
+ i(\infty,d,\vp') +1  & = \lfloor C_{\vp'}\, T(0,d,\vp')\rfloor +2 \le  \left[C_{\vp'} + \frac{2}{T(0,d,\vp')}   \right]\, T(0,d,\vp')\\
  & \le  \underbrace{\left[C_{\vp'} + \frac{2}{T(0,1,\vp')}   \right]}_{=:L_{\vp'}}\, T(0,d,\vp')
@@
 By the definition of  $\cp_{\textup{opt}}$ \eqref{eq:tract_def}  holds for all $\vp \in (\vp^*,\boldsymbol{\infty})$, which implies by the argument for necessity that  \eqref{eq:tractiff4} holds for all $\vp \in (\vp^*,\boldsymbol{\infty})$.
-\peter{Indeed, the latter is deduced similarly as in the proof of Theorem \ref{thm_main_strong_tract2}.}
+Indeed, the latter is deduced similarly as in the proof of Theorem \ref{thm_main_strong_tract2.}
 This is the first condition for membership in $\widetilde{\cp}_{\textup{opt}}$.
@@
 	\lambda_{n(\varepsilon,d,c),d} \le \varepsilon \quad \forall \varepsilon^{-1} + d \ge V_c, \qquad \text{where }
-	n(\varepsilon,d,c):=\left\lfloor h(cT(\varepsilon^{-1},d)) \right\rfloor \peter{+1}.
+	n(\varepsilon,d,c):=\left\lfloor h(cT(\varepsilon^{-1},d)) \right\rfloor +1.
 \]
@@
 \begin{equation}
-		n(\varepsilon,d,c)\le  h(cT(\varepsilon^{-1},d)) \peter{+1}\le  h(cT(\lambda^{-1}_{n(\varepsilon,d,c),d},d)) \peter{+1}\qquad  \quad \forall \varepsilon^{-1} + d \ge V_c. \label{eq:nedcbound}
+		n(\varepsilon,d,c)\le  h(cT(\varepsilon^{-1},d)) +1\le  h(cT(\lambda^{-1}_{n(\varepsilon,d,c),d},d)) +1\qquad  \quad \forall \varepsilon^{-1} + d \ge V_c. \label{eq:nedcbound}
 \end{equation}
@@
 \begin{equation} \label{eq:nstardef}
-	\varepsilon^{-1}_{\max}(d,c) := \max(V_c - d,\lambda_{\max}^{-1}), \qquad n^*(d,c) : = n(\varepsilon^{-1}_{\max}(d,c),d,c) \le h(cT(\varepsilon^{-1}_{\max}(d,c),d)) \peter{+1}.
+	\varepsilon^{-1}_{\max}(d,c) := \max(V_c - d,\lambda_{\max}^{-1}), \qquad n^*(d,c) : = n(\varepsilon^{-1}_{\max}(d,c),d,c) \le h(cT(\varepsilon^{-1}_{\max}(d,c),d)) +1.
 \end{equation} 

### 2023-04-21 GeneralizedTractability_230418.tex
Updates from Overleaf

@@
 \end{equation*}
-Here above, $\vp = (p,q)$ in some cases. \peter{A general reference 
-for results on algebraic tractability is \cite{NW08}, for exponential tractability we refer to \cite{HKW19} and \cite{KW19}.}
+Here above, $\vp = (p,q)$ in some cases. A general reference 
+for results on algebraic tractability is \cite{NW08}, for exponential tractability we refer to \cite{HKW19} and \cite{KW19}.
 
@@
 These conditions involve the boundedness of sums defined in terms of $(T(\lambda_{i,d}^{-1},\cdot, \cdot))_{i=1}^\infty$.
-In practice, it may be easier to verify whether or not these conditions hold than to verify \eqref{eq:tract_def and \eqref{eq:strong_tract_def}} directly.
+In practice, it may be easier to verify whether or not these conditions hold than to verify \eqref{eq:tract_def} and \eqref{eq:strong_tract_def} directly.
 

### 2023-04-21 GeneralizedTractability_230418.tex
Updates from Overleaf

@@
 \end{equation}
-This means that $\log(h(\cdot))$ is a superadditive function.  The function $h$ here can be thought of as the exponential function for weak tractability.
+This means that $\log(h)$ is a superadditive function.  An example of the function $h$ is the exponential function, from which we can recover weak tractability.
 

### 2023-04-21 GeneralizedTractability_230418.tex
Fred's Home Computer

@@
 
-\fred{We need to check the proof for
-\begin{itemize}
-\item correctness
-\item exponents
-\item whether the additional assumptions are too restrictive and can be generalized
-\item whether we need $\tau$ in the assumption
-\item Do we need non-decreasing or strictly increasing?
-\end{itemize}}
-\begin{definition}[Weak Tractability]
-If $n(\varepsilon,d)$ denotes the minimal number of function values needed to approximate all functions. We say that the problem is \emph{weakly tractable} if
-    \[\lim_{\varepsilon^{-1}+d\rightarrow \infty} \frac{\ln n(\varepsilon,d)}{\varepsilon^{-1}+d} = 0\]
-\end{definition}
 %\begin{definition}[Quasi-polynomial Tractability]
@@
 %\end{definition}
-
-\peter{
-\section{Weak $T$-$(s,t)$-weak tractability} \label{sec:weak}
-
-\begin{definition}[$T$-$(s,t)$-weak tractability]
-Let $s,t>0$. We say that the problem is \emph{$T$-$(s,t)$ weakly tractable} if
-    \[\lim_{\varepsilon^{-1}+d\rightarrow \infty} \frac{\log n(\varepsilon,d)}{T(\varepsilon^{-s},1,\vp) + T(0,d^t,\vp)} = 0.\]
-\end{definition}
-
-We show a necessary and sufficient condition for $T$-$(s,t)$-weak tractability, working analogously to \cite{WW17}.
-\begin{theorem}\label{thm:weak}
-For $c>0$, define
-\[
-\sigma (c,d,s,\vp):= \sum_{i=1}^\infty \exp \left(-c\, T(\lambda_{i,d}^{-s},1,\vp)\right).
-\]
-Then the problem is $T$-$(s,t)$-weakly tractable if and only if
-\[
-\mu (c,s,t,\vp)=\sup_{d\in\naturals} \sigma (c,d,s,\vp) \exp\left(-c\, T(0,d^t,\vp)\right)<\infty
-\]
-holds for all $c>0$.
-\end{theorem}
-\begin{proof}
- We first show the necessity of the condition in the theorem.
-Indeed, suppose that the problem is  $T$-$(s,t)$-weakly tractable.
-Then, for any $c>0$ there exists a positive integer $V=V(c)$ such that
- \[
- n(\varepsilon,d)\le 
- \left\lfloor \exp\left(c\,
- \left(T(\varepsilon^{-s},1,\vp) + T(0,d^t,\vp)\right)
- \right) \right\rfloor
- \]
- whenever $\varepsilon^{-1} + d \ge V$. For $d\in\naturals$ 
- choose $\varepsilon>0$ such that $\varepsilon^{-1}\ge \max\{1,V-d\}$. Since the eigenvalues $\lambda{i,d}$ are non-increasing in $i$, we know that
- \[
- \lambda_{\lfloor \exp(c\,
- (T(\varepsilon^{-s},1,\vp) + T(0,d^t,\vp))) \rfloor+1}^2 \le \varepsilon^2
- \]
- for any $\varepsilon$ satisfying $\varepsilon^{-1}\ge \max\{1,V-d\}$.
-Let 
-\[
-n=n(\varepsilon):= \lfloor \exp(c\,
- (T(\varepsilon^{-s},1,\vp) + T(0,d^t,\vp))) \rfloor+1
-\]
-and
-\[
-n^*:= \lfloor \exp(c\,
- (T(\max\{1,(V-d)^s\},1,\vp) + T(0,d^t,\vp))) \rfloor+1.
-\]
-By varying $\varepsilon^{-1}$ in the interval 
-$[\max\{1,V-d\},\infty)$ we can make $n(\varepsilon)$ attain 
-any integer value greater than or equal to $n^*$.
-
-Furthermore, we have, as $\lambda_{n,d}\le \varepsilon$ and as $T$ is monotonically increasing, 
-\begin{eqnarray*}
-n(\varepsilon)-1 & \le & \exp(c\, (T(\varepsilon^{-s},1,\vp) + T(0,d^t,\vp)))\\
-& \le & \exp(c\, (T(\lambda_{n(\varepsilon),d}^{-s},1,\vp) + T(0,d^t,\vp))),
-\end{eqnarray*}
-which is equivalent to 
-\[
-\exp(-2c\, (T(\lambda_{n(\varepsilon),d}^{-s},1,\vp) + T(0,d^t,\vp))) \le \frac{1}{(n(\varepsilon)-1)^2}.
-\]
-Therefore,
-\begin{eqnarray*}
-    \exp(-2c\, T(0,d^t,\vp)) \sum_{i=1}^\infty \exp(-2c\, T(\lambda_{i,d}^{-s},1,\vp))
-    &\le& \exp(-2c\, T(0,d^t,\vp))\, (n^*-1) + \sum_{i=n^*}^\infty \frac{1}{(i-1)^2}\\
-    &\le& \exp(-2c\, T(0,d^t,\vp))\, (n^*-1) + \frac{\pi^2}{6}.
-\end{eqnarray*}
-Moreover,
-\begin{eqnarray*}
-    \exp(-2c\, T(0,d^t,\vp))\, (n^*-1) &\le & \exp(-2c\, T(0,d^t,\vp))\, 
-    \exp (c\, T(V^s,1,\vp) + c\, T(0,d^t,\vp))\\
-    &\le & \exp (c\, T(V^s,1,\vp))\\
-    &<& \infty,
-\end{eqnarray*}
-independently of $d$. This implies that 
-\[
-\exp(-2c\, T(0,d^t,\vp)) \sum_{i=1}^\infty \exp(-2c\, T(\lambda_{i,d}^{-s},1,\vp))<\infty,
-\]
-also independently of $d$. As $c>0$ was chosen arbitrarily, we can replace $2c$ by $c$ and see
-necessity of the condition in the theorem.
-
-\medskip
-
-We now show sufficiency.
-
-Suppose that $\mu(c,s,t,\vp) <\infty$ for all $c>0$. It is no loss of generality to assume that 
-$\mu(c,s,t,\vp) \ge 1$. Since the terms of the series in the definition of $\mu(c,s,t,\vp) $ are non-increasing, we have 
-\[
-\exp (-c\, T(0,d^t,\vp))\, n\, \exp (-c\, T(\lambda_{n,d}^{-s},1,\vp)) \le \mu (c,s,t,\vp).
-\]
-Then we obtain 
-\[
-\exp (-c\, T(\lambda_{n,d}^{-s},1,\vp)) \le \frac{1}{n}\, \mu (c,s,t,\vp)\, 
-\exp (c\, T(0,d^t,\vp)),
-\]
-which is equivalent to 
-\[
-\exp (c\, T(\lambda_{n,d}^{-s},1,\vp)) \ge \frac{n}{\mu (c,s,t,\vp)\, 
-\exp (c\, T(0,d^t,\vp))},
-\]
-which in turn is equivalent to 
-\[
-T(\lambda_{n,d}^{-s},1,\vp) \ge \frac{1}{c}\log \left(\frac{n}{\mu (c,s,t,\vp)\, 
-\exp (c\, T(0,d^t,\vp))}\right)
-\]
-as long as 
-\[
-n> \mu (c,s,t,\vp)\, \exp (c\, T(0,d^t,\vp)).
-\]
-This implies that for the special choice 
-\[
-n= \left\lceil 
-   \mu (c,s,t,\vp)\, \exp \left(c\, (T(\varepsilon^{-s},1,\vp) + T(0,d^t,\vp))\right)
-   \right\rceil 
-\]
-we have
-\[
-T(\lambda_{n,d}^{-s},1,\vp) \ge T(\varepsilon^{-1},1,\vp),
-\]
-which implies that $\lambda_{n,d} \le \varepsilon$, and thus $n(\varepsilon,d)\le n$. Note that the 
-argument $x$ of the ceiling function in the definition of our special $n$ is at least one, which implies 
-$\lceil x \rceil \le 2x$.
-
-Consequently,
-\[
-n(\varepsilon, d) \le \exp\left(c\, \left(
-\frac{\log (2\mu (c,s,t,\vp) )}{c}
-T(\varepsilon^{-s},1,\vp) + T(0,d^t,\vp)
-\right)\right).
-\]
-Clearly, there must exist a positive $V=V(c,s,t,\vp)$ such that when $\varepsilon^{-1} +d \ge V$ it holds true that
-\[
-  T(\varepsilon^{-s},1,\vp) + T(0,d^t,\vp) \ge \frac{\log (2\mu (c,s,t,\vp) )}{c}.
-\]
-Hence we finally have 
-\[
-n(\varepsilon,d) \le \exp (2c\, (T(\varepsilon^{-s},1,\vp) + T(0,d^t,\vp))).
-\]
-Since the latter inequality holds for every $c>0$, we have $T$-$(s,t)$-weak tractability.
-
-\end{proof}
-}
 
@@
 	\[
-	T(\lambda_{n,d}^{-s},d) \ge T(\varepsilon^{-1},d).
+	T(\lambda_{n,d}^{-s},d) \ge T(\varepsilon^{-1},d) \qquad \forall \varepsilon > 0, \, d \in \naturals.
 	\]
@@
 S_c \, h(cT(\varepsilon^{-1},d))  
-\right\rceil \qquad \forall c > 0.  
+\right\rceil \le   \lceil \underbrace{
+S_c \, h(cT(0,1))}_{=: \widetilde{S}_c/2} \, h(cT(\varepsilon^{-1},d))  
+\rceil\qquad \forall c, \varepsilon > 0, \, d \in \naturals.
 \]
 
-\peter{
-We could go on like this:
+Since $S_c \ge 1/h(cT(0,1))$ by definition, it follows that $S_c \, h(cT(0,1)) \, h(cT(\varepsilon^{-1},d))  \ge 1$ and so 
+\begin{align*}
+\max(1,\comp(\varepsilon,d)) 
+& \le  \lceil  S_c \, h(cT(0,1)) \, h(cT(\varepsilon^{-1},d))   \rceil 
+ =  \lceil 
+(\widetilde{S}_c/2) \, h(cT(\varepsilon^{-1},d))  
+\rceil \\
+& \le   \widetilde{S}_c \, h(cT(\varepsilon^{-1},d))  
+\qquad\forall c, \varepsilon > 0, \, d \in \naturals.
+\end{align*}
+Since $h$ is strictly increasing, so is $h^{-1}$, and thus
+\begin{align*}
+h^{-1}(\max(1,\comp(\varepsilon,d)) ) & \le  h^{-1} \left(  
+\widetilde{S}_c \, h(cT(\varepsilon^{-1},d))  \right) 
+\\
+&  \le  h^{-1} (2 S_c) + cT (\varepsilon^{-1},d).
+\quad \forall c, \varepsilon > 0, \, d \in \naturals \qquad \text{by \eqref{eq:submult_h_inverse}.}
+\end{align*}
 
-It is no loss of generality to assume that $S_c \ge 1$. From above we get 
-\[
-h^{-1}(\comp(\varepsilon,d)) \le h^{-1} \left( \left\lceil 
-S_c \, h(cT(\varepsilon^{-1},d))  
-\right\rceil \right) \le h^{-1} \left(  
-2 S_c \, h(cT(\varepsilon^{-1},d))  
- \right) \qquad \forall c > 0,
-\]
-where we used that the argument of the ceiling function is at least one.
-
-From this we deduce, by \eqref{eq:submult_h_inverse},
-\[
-h^{-1}(\comp(\varepsilon,d)) \le
- h^{-1} (2 S_c) + cT (\varepsilon^{-1},d).
-\]
-Now, for sufficiently large $\varepsilon^{-1}+d$, we must have
-\[
-c T (\varepsilon^{-1},d) \ge h^{-1} (2 S_c).
-\]
-This is because the finiteness of $S_c$ implies that $\lim_{\varepsilon \to 0} T(\varepsilon^{-1},d) = \infty$ for all $d \in \naturals$,  together with the hypothesis on $\lim_{d \to \infty} T(\varepsilon^{-1},d)$.
-So, 
-\[
-h^{-1}(\comp(\varepsilon,d)) \le 2 cT (\varepsilon^{-1},d).
-\]
-Since the latter holds for any $c>0$, we have sub-$h\circ T$-tractability.
-
-}
-
-Consequently, choosing $c=1/2$, it follows that 
-\begin{align}
-\nonumber
-\lim_{\varepsilon^{-1} + d \to \infty} \frac{\comp(\varepsilon,d)}{ h(T(\varepsilon^{-1},d))  }
-& = \lim_{\varepsilon^{-1} + d \to \infty} \frac{\comp(\varepsilon,d)}{ h(2cT(\varepsilon^{-1},d))  } \\
-& \le \lim_{\varepsilon^{-1} + d \to \infty} \frac{ \left\lceil 
-	S_c \, h(cT(\varepsilon^{-1},d)) \right\rceil}{ [h(cT(\varepsilon^{-1},d))]^2  } \qquad \text{by \eqref{eq:h_cond}}
-\\
-\nonumber
-& \le \lim_{\varepsilon^{-1} + d \to \infty} \frac{
-	S_c \, h(cT(\varepsilon^{-1},d))+1}{ [h(cT(\varepsilon^{-1},d))]^2  }  \\
-& = \lim_{\varepsilon^{-1} + d \to \infty} \left \{\frac{
-	S_c }{ h(cT(\varepsilon^{-1},d))  }  + \frac{
-	1}{ [h(cT(\varepsilon^{-1},d))]^2 } \right \} \label{eq:alastone}.
-\end{align}	
 The finiteness of $S_c$ implies that $\lim_{\varepsilon \to 0} T(\varepsilon^{-1},d) = \infty$ for all $d \in \naturals$.
-Together with the hypothesis on $\lim_{d \to \infty} T(\varepsilon^{-1},d)$, we can infer that $\lim_{\varepsilon^{-1} + d \to \infty} T(\varepsilon^{-1},d) = \infty$.
-This implies that the limit in \eqref{eq:alastone} vanishes.
+Together with  the hypothesis on $\lim_{d \to \infty} T(\varepsilon^{-1},d)$ in \eqref{eq:h_cond}, it follows that $\lim_{\varepsilon^{-1} + d \to \infty} T(\varepsilon^{-1},d) = \infty$.
+Therefore
+\begin{equation*}
+	\lim_{\varepsilon^{-1} + d \to \infty} \frac{h^{-1}(\max(1,\comp(\varepsilon,d)))}{T(\varepsilon^{-1},d)} 
+	\le \lim_{\varepsilon^{-1} + d \to \infty} \frac{h^{-1} (2 S_c)}{T(\varepsilon^{-1},d)}  + c = c \qquad\forall c >  0.
+\end{equation*}
+Since this limit is bounded above by all positive $c$, it must be zero, and the problem is sub-$h$-$T$ tractable.
 
@@
 \noindent \textbf{Necessary Condition:}\\
-Suppose that the problem is  sub-$h \circ T$ tractable.
-Then, for any $c>0$ there exists a positive integer $V_c$ such that  \fred{having a little trouble removing the $c$ here.} \peter{Here we do not need to remove the $c$, and actually shouldn't.
-Just in the limit relation it was not necessary.}
-\[
-	\comp(\varepsilon,d)\le 
-	\left\lfloor h(cT(\varepsilon^{-1},d)) \right\rfloor \qquad \forall \varepsilon^{-1} + d \ge V_c.
-\]
+Suppose that the problem is  sub-$h \circ T$ tractable. Then, for any $c>0$ there exists a positive integer $V_c$ such that  
+\begin{gather*}
+	h^{-1}(\comp(\varepsilon,d))\le h^{-1}(\max(1,\comp(\varepsilon,d))) \le cT(\varepsilon^{-1},d)  \qquad \forall \varepsilon^{-1} + d \ge V_c, \\
+	\comp(\varepsilon,d) \le \left\lfloor h(cT(\varepsilon^{-1},d)) \right\rfloor \qquad \forall \varepsilon^{-1} + d \ge V_c.
+\end{gather*}
 By the definition of the information complexity in \eqref{eq:comp_def}, it follows that 
@@
 
-If $f(x)$ and $g(x)$ are both positive, and $\lim_{x \to \infty} g(x) = \infty$, is it true that
+\begin{example}[Weak Tractability]
+	Suppose that 
 	\[
-\lim_{x \to \infty} \frac{f(x)}{g(x)} = 0 \iff 
-\lim_{x \to \infty} \frac{\log(f(x))}{\log(g(x))} = 0?
+	T(\varepsilon^{-1},d,\vp) = \varepsilon^{-s} + d^t, \quad \forall \varepsilon > 0, \ d \in \naturals, \quad \text{where } \vp = (s,t), \qquad h(x) = \exp(x) \quad \forall x \ge 0.
 	\]
+	Then Theorem \ref{thm:subhT} implies that 
+	\[\lim_{\varepsilon^{-1}+d\rightarrow \infty} \frac{\log( \max(1,\comp(\varepsilon,d)))}{\varepsilon^{-s}+d^t} = 0 
+	\iff 
+	 \sup_{d\in\naturals}  \, \sum_{i=1}^\infty \exp(-c\, (\lambda_{i,d}^{-s} + d^t )) <\infty \qquad \forall c > 0.
+	\]
+	The expression on the left is the notion of $(s,t)$-weak tractability \cite{??}, and the condition on the right was derived in \cite{??}.
+Weak tractability corresponds to $(s,t)=(1,1)$, and uniform weak tractability corresponds to the case when a problem is weakly tractable for all positive $s$ and $t$.
+\end{example}
 

### 2023-04-21 GeneralizedTractability_230418.tex
Updates from Overleaf

@@
 
-\subsection{Notation and fundamental definitions}
+\subsection{Notation and fundamental definitions} \label{sec:not}
 Let $T$ be a tractability function defined as follows,
@@
 
+Certain common notions of tractability are covered by the general situation described above.
+{\small 
+\begin{equation*}
+	\begin{array}{r@{\qquad}c@{\qquad}cc}
+		\text{Tractability type} & T(\varepsilon^{-1},d,\vp)
+		& T(0,d,\vp)\\
+		\toprule
+		\text{strong polynomial algebraic} & \max(1,\varepsilon^{-p}) & 1\\
+		\text{polynomial algebraic} & \max(1,\varepsilon^{-p})d^{q} & d^{q}\\
+		\text{strong polynomial exponential} &  [\max(1,\log(1 + \varepsilon^{-1})]^p & 1\\
+		\text{polynomial exponential } &
+		[\max(1,\log(1 + \varepsilon^{-1}))]^p  d^{q} & d^{q} \\
+        \text{quasi-polynomial} & 
+        \exp\{p(1+\log(\max(1,\varepsilon^{-p}))(1+\log(d))\} &
+        \exp\{p(1+\log(d))\}
+	\end{array}
+\end{equation*}}
+Here above, $\vp = (p,q)$ in some cases and $\vp$ is a scalar in other cases. A general reference 
+for results on algebraic tractability is \cite{NW08}, for exponential tractability we refer to \cite{HKW19} and \cite{KW19}.
+
 If \eqref{eq:tract_def} holds for some $\vp$, it clearly holds for larger $\vp$.
@@
 \end{gather}
-
-Certain common notions of tractability are covered by the general situation described above.
-\begin{equation*}
-	\begin{array}{r@{\qquad}c@{\qquad}cc}
-		& T(\varepsilon^{-1},d,\vp)
-		& T(0,d,\vp)\\
-		\toprule
-		\text{strong polynomial algebraic  tractability} & \max(1,\varepsilon^{-p}) & 1\\
-		\text{polynomial algebraic tractability} & \max(1,\varepsilon^{-p})d^{q} & d^{q}\\
-		\text{strong polynomial exponential tractability} &  [\max(1,\log(1 + \varepsilon^{-1})]^p & 1\\
-		\text{polynomial exponential tractability} &
-		[\max(1,\log(1 + \varepsilon^{-1}))]^p  d^{q} & d^{q}
-	\end{array}
-\end{equation*}
-Here above, $\vp = (p,q)$ in some cases. A general reference 
-for results on algebraic tractability is \cite{NW08}, for exponential tractability we refer to \cite{HKW19} and \cite{KW19}.
 
@@
 Let $T$ be a tractability function as specified in \eqref{eq:Tspec} and satisfying \eqref{eq:Tconditions} and \eqref{eq:ptauassume}.
-A problem is $T$-tractable iff there exist $\vp\ge \vzero$ and a constant $L_{\vp} > 0$ such that
+A problem is $T$-tractable iff there exists $\vp\ge \vzero$ and a positive integer $L_{\vp}$ such that
 \begin{equation} \label{eq:tractiff4}
@@
 
-\begin{example}[Strong polynomial tractability]
+In this section, we illustrate Theorems \ref{thm_main_strong_tract2} and \ref{thm_main_tract2} for the types of tractability given in the table in Section \ref{sec:not}.
 
-Let $ T :(0,\infty) \times \mathbb{N} \times [0,\infty)^s \rightarrow (0,\infty)$
+\begin{example}[Strong algebraic polynomial tractability]
+
+Let the tractability function, $T$,
 be defined by
 \[
- T(\varepsilon^{-1},d,\vp)= (\max\{\varepsilon^{-1},1\})^p .
+ T(\varepsilon^{-1},d,p)= (\max\{\varepsilon^{-1},1\})^p 
+ \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, p \ge 0.
 \]
-Then Theorem \ref{thm_main_strong_tract2} yields the iff-condition
+Then Theorem \ref{thm_main_strong_tract2} yields the  equivalent condition for strong algebraic polynomial tractability: 
 \[
- \sup_{d\in\naturals} \sum_{i=L(p)}^\infty (\min\{\lambda_{i,d},1\})^p < \infty.
+ \sup_{d\in\naturals} \sum_{i=L_p}^\infty (\min\{\lambda_{i,d},1\})^p < \infty \text{ for some } p \ge 0, L_p \in \naturals.
 \]
-This essentially recovers the result on strong polynomial tractability in \cite[Theorem 5.1]{NW08}
+Furthermore, the optimal $p$ is the infimum of all $p$ for which the above condition holds.
+This essentially recovers the result in \cite[Theorem 5.1]{NW08}.
 \end{example}
 
-\begin{example}[Polynomial tractability]
-Let $ T :(0,\infty) \times \mathbb{N} \times [0,\infty)^s \rightarrow (0,\infty)$
+\begin{example}[Algebraic polynomial tractability]
+Let the tractability function, $T$,
 be defined by
 \[
- T(\varepsilon^{-1},d,\vp)= (\max\{\varepsilon^{-1},1\})^p\, d^q.
+ T(\varepsilon^{-1},d,p,q)= (\max\{\varepsilon^{-1},1\})^p\, d^q
+ \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, p,q \ge 0.
 \]
-Then Theorem \ref{thm_main_tract2} yields the iff-condition
+Then Theorem \ref{thm_main_tract2} yields the  equivalent condition for algebraic polynomial tractability: 
 \[
- \sup_{d\in\naturals} \sum_{i=L_{\vp} d^{q_1}}^\infty (\min\{\lambda_{i,d},1\})^p d^{-q} < \infty.
+ \sup_{d\in\naturals} \sum_{i=L_{p,q} d^{q}}^\infty (\min\{\lambda_{i,d},1\})^p d^{-q} < \infty \text{ for some } p,q \ge 0, L_{p,q} \in \naturals.
 \]
-This essentially recovers the result on polynomial tractability in \cite[Theorem 5.1]{NW08}
+Furthermore, the set of optimal $(p,q)$ is a subset of 
+\begin{multline*}
+\{(p^*,q^*) : \text{the above condition holds for all }(p,q) \in (p^*,\infty) \times (q^*,\infty) \\
+\text{but not for any }(p,q) \in [0,p^*/2) \times [0,q^*/2)\}.
+\end{multline*}
+This essentially recovers the result on polynomial tractability in \cite[Theorem 5.1]{NW08} \fred{same theorem as above??, what about optimality in \cite[Theorem 5.1]{NW08}}.
 \end{example}
 
-\peter{(PETER: Add further examples (e.g., EXP- polynomial tractability, etc.)}
 \kachi{\begin{example}[EXP-strong polynomial tractability]

### 2023-04-21 GeneralizedTractability_230418.tex
Updates from Overleaf

@@
 
-\fred{Can we say that this notion of tractabilty is stronger or weaker than $\comp(\varepsilon,d)/h(T(\varepsilon^{-1},d,\vp)) \to 0$ as $\varepsilon^{-1} + d \to \infty$?}
+Note that this definition of sub-$h$-$T$ tractability implies that
+\begin{equation} \label{eq:comp_slow_hcT}
+		\lim_{\varepsilon^{-1} + d \to \infty} \frac{\comp(\varepsilon,d)}{h(cT(\varepsilon^{-1},d,\vp))} = 0 \qquad \forall c > 0,
+\end{equation}
+which means that for $\varepsilon \to 0$ or $d \to \infty$  $\comp(\varepsilon,d))$ must increase slower than $h(cT(\varepsilon^{-1},d,\vp))$, no matter how small $c$ is.
 
@@
 \noindent \textbf{Necessary Condition:}\\
-Suppose that the problem is  sub-$h \circ T$ tractable. Then, for any $c>0$ there exists a positive integer $V_c$ such that  
-\begin{gather*}
-	h^{-1}(\comp(\varepsilon,d))\le h^{-1}(\max(1,\comp(\varepsilon,d))) \le cT(\varepsilon^{-1},d)  \qquad \forall \varepsilon^{-1} + d \ge V_c, \\
+Suppose that the problem is  sub-$h \circ T$ tractable. Then by \eqref{eq:comp_slow_hcT}, for any $c>0$ there exists a positive integer $V_c$ such that  
+\begin{equation*}
 	\comp(\varepsilon,d) \le \left\lfloor h(cT(\varepsilon^{-1},d)) \right\rfloor \qquad \forall \varepsilon^{-1} + d \ge V_c.
-\end{gather*}
+\end{equation*}
 By the definition of the information complexity in \eqref{eq:comp_def}, it follows that 

### 2023-04-21 GeneralizedTractability_230418.tex
Updates from Overleaf

@@
         \text{quasi-polynomial} & 
-        \exp\{p(1+\log(\max(1,\varepsilon^{-p}))(1+\log(d))\} &
+        \exp\{p(1+\log(\max(1,\varepsilon^{-1}))(1+\log(d))\} &
         \exp\{p(1+\log(d))\}
@@
 \]
-Then Theorem \ref{thm_main_strong_tract2} yields the  equivalent condition for strong algebraic polynomial tractability: 
+\fred{May we pull the exponent $p$ inside the $\max$?} Then Theorem \ref{thm_main_strong_tract2} yields the  equivalent condition for strong algebraic polynomial tractability: 
 \[
@@
 \begin{proof}
-We suppress the $\vp$ dependence, because it does not enter into the proof.
+The idea of this proof follows \cite{WW17}.
+We suppress the $\vp$ dependence in the proof, because it insignificant.
 
@@
 \end{align*}
-Since $h$ is strictly increasing, so is $h^{-1}$, and thus
+Since $h$ is strictly increasing, so is $h^{-1}$, and thus by \eqref{eq:submult_h_inverse}, 
 \begin{align*}
@@
 &  \le  h^{-1} (2 S_c) + cT (\varepsilon^{-1},d).
-\quad \forall c, \varepsilon > 0, \, d \in \naturals \qquad \text{by \eqref{eq:submult_h_inverse}.}
+\quad \forall c, \varepsilon > 0, \, d \in \naturals.
 \end{align*}
@@
 \end{align*}
-Combining this bound with \eqref{eq:lastone} establishes the finiteness of $S_{2c}$ and completes the proof of the necessary condition.
-
-	\bigskip
-
-This completes the proof.
+Combining this bound with the upper bound on $S_c$ in \eqref{eq:lastone} establishes the finiteness of $S_{2c}$ and completes the proof of the necessary condition.
+This concludes the proof of Theorem \ref{thm:subhT}.
 \end{proof}
@@
 	\[
-	T(\varepsilon^{-1},d,\vp) = \varepsilon^{-s} + d^t, \quad \forall \varepsilon > 0, \ d \in \naturals, \quad \text{where } \vp = (s,t), \qquad h(x) = \exp(x) \quad \forall x \ge 0.
+	T(\varepsilon^{-1},d,s,t) = \max(1,\varepsilon^{-1})^s + d^t, \quad \forall \varepsilon,s,t > 0, \, d \in \naturals, \qquad h(x) = \exp(x) \quad \forall x \ge 0.
 	\]
 	Then Theorem \ref{thm:subhT} implies that 
-	\[\lim_{\varepsilon^{-1}+d\rightarrow \infty} \frac{\log( \max(1,\comp(\varepsilon,d)))}{\varepsilon^{-s}+d^t} = 0 
+	\[\lim_{\varepsilon^{-1}+d\rightarrow \infty} \frac{\log( \comp(\varepsilon,d))}{\varepsilon^{-s}+d^t} = 0 
 	\iff 
-	 \sup_{d\in\naturals}  \, \sum_{i=1}^\infty \exp(-c\, (\lambda_{i,d}^{-s} + d^t )) <\infty \qquad \forall c > 0.
+	 \sup_{d\in\naturals}  \, \sum_{i=1}^\infty \exp(-c\, (\min(1,\lambda_{i,d})^{s} + d^t )) <\infty \qquad \forall c > 0.
 	\]
@@
 \end{example}
+
+\section{Summary}
+
+\fred{Do we consider the case of normalized error?}
 

### 2023-04-21 GeneralizedTractability_230418.tex
Fred M2 2023 Mac Updates

@@
 This implies (see, e.g., \cite{NW08}) that $\lambda_{i,d}$ converges to zero as $i$ tends to infinity for every $d$, which in turn implies that the problem is solvable by suitable algorithms.
-To avoid trivial cases, we assume that there are an infinite number of positive eigenvalues.
+To avoid trivial cases, we assume that there are an infinite number of positive eigenvalues for every $d$.
 
@@
 
-The information complexity of the problem $\SOL_d$ is given by the function $\comp:(0,\infty) \times \naturals \to \natzero$, where $\comp(\varepsilon,d)$ is the minimum number of linear functionals required to satisfy the error criterion \eqref{eq:errcrit}.
+The information complexity of the problem $\SOL_d$ is given by the function $\comp:(0,\infty) \times \naturals \to \natzero$, where $\comp(\varepsilon,d)$ is the number of linear functionals required by the best algorithm to satisfy the error criterion \eqref{eq:errcrit}.
 By definition, the complexity is non-decreasing  as $\varepsilon$ tends to zero.

### 2023-04-23 GeneralizedTractability_230418.tex
Updates from Overleaf

@@
 \end{equation}
+\fred{Are we restricting ourselves by not allowing $\lambda_{1,d} \to \infty$ as $d \to \infty$}
 This means that the non-negative $\lambda_{i,d}$ are the singular values of the operator $\SOL_d$.
@@
 %\kachi{Throughout the article, we use the following notation.}\\
+
+\fred{Point out that $T$ could increase quite rapidly, but this does not affect our theorems.}
 
@@
 \end{equation}
-which means that for $\varepsilon \to 0$ or $d \to \infty$  $\comp(\varepsilon,d))$ must increase slower than $h(cT(\varepsilon^{-1},d,\vp))$, no matter how small $c$ is.
+which means that for $\varepsilon \to 0$ or $d \to \infty$  $\comp(\varepsilon,d)$ must increase slower than $h(cT(\varepsilon^{-1},d,\vp))$, no matter how small $c$ is.
 
@@
 
-\section{Summary}
+\section{Discussion and Summary}
 
-\fred{Do we consider the case of normalized error?}
+\fred{
+\begin{itemize}
+\item Do we consider the case of normalized error? (Peter) 
+\item Are there cases of $T$ that do not correspond to known tractability measures? (Kachi)
+\item Restricted domain? (Fred)
+\end{itemize}}
 

### 2023-04-25 GeneralizedTractability_230418.tex
Updates from Overleaf

@@
 \end{equation}
-\fred{Are we restricting ourselves by not allowing $\lambda_{1,d} \to \infty$ as $d \to \infty$}
+\fred{Are we restricting ourselves by not allowing $\lambda_{1,d} \to \infty$ as $d \to \infty$?}
+\peter{Yes, indeed, I think we do (e.g., think of tensor product spaces where the first eigenvalue is bigger than one).
+But I am wondering whether we could do without $\lambda_{\max}$ by the assumption that $T$ is bounded away from zero by some absolute value $t$.
+Then, in all cases we could bound $1/T(\cdot,\cdot,\cdot)$ by $1/t$.
+Actually, is $T(0,1,\boldsymbol{0})$ our $t$?}
+
 This means that the non-negative $\lambda_{i,d}$ are the singular values of the operator $\SOL_d$.
@@
 
+\section{Try Restricted Region}
+
+Suppose that the domain of interesting $(\varepsilon^{-1},d)$ is given by 
+\begin{equation}
+    \Omega  = \{(\varepsilon^{-1},d) : \varepsilon > E(d) \ge 0, \ d \in \naturals \},
+\end{equation}
+where $E$ is a non-increasing function.  Furthermore, for all $d \in \naturals$, let $N(d) = \min \{n : \lambda_{n+1,d} \le E(d) \}$.  This means that 
+\[
+\lambda_{1,d}^{-1} \le \cdots \le \lambda_{N(d),d}^{-1} < E(d) \le \lambda_{N(d)+1,d}^{-1}, \qquad (\lambda_{1,d}^{-1},d), \ldots, (\lambda_{N(d),d}^{-1},d) \in \Omega.
+\]
+
+\subsection{Strong tractability}
+
+We first consider the simpler case when the complexity is essentially independent of the dimension, $d$.
+The proof also introduces the line of argument used for the case where there is $d$-dependence.
+
+\begin{theorem}\label{thm_main_strong_tract2}
+Let $T$ be a tractability function as specified in \eqref{eq:Tspec} and satisfying \eqref{eq:Tconditions} and \eqref{eq:ptauassume}.
+A problem is strongly $T$-tractable iff there exists $\vp \in [\vzero, \boldsymbol{\infty})$ and an integer $L_{\vp} > 0$ such that
+\begin{equation} \label{eq:strong_tractiff3}
+     S_{\vp}:=\sup_{d \in \naturals} \sum_{i = L_{\vp}}^{N(d)} \frac{1}{T(\lambda_{i,d}^{-1},1,\vp)} < \infty.
+\end{equation}
+If \eqref{eq:strong_tractiff3} holds for some $\vp$, let  $\widetilde{\cp}_{\textup{strct}} : = \{\vp^* : \eqref{eq:strong_tractiff3} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty})\}$.
+Then $\cp_{\textup{strct}} = \widetilde{\cp}_{\textup{strct}}$, and the set of optimal strong tractability parameters is
+\[
+	\cp_{\textup{sopt}} =
+	\{\vp^* \in \widetilde{\cp}_{\textup{strct}} :  \vp^* \notin [\widetilde{\vp},\boldsymbol{\infty}) \ \forall \widetilde{\vp}\in  \widetilde{\cp}_{\textup{strct}} \setminus \{\vp^*\} \}.
+\]
+\end{theorem}
+
+\begin{proof}
+\textbf{Sufficient condition:}\newline
+We make the first part of the argument in some generality so that it can be reused in the proof of Theorem \ref{thm_main_tract2} for tractability.
+
+Since the $\lambda_{i,d}$ are non-increasing in $i$, it follows that the $T(\lambda_{i,d}^{-1},d',\vp)$ are non-decreasing in $i$ for any $d'\in\{1, \ldots, d\}$.
+In particular, for all $n\in \{1, \ldots, N(d')\}$, we have
+\begin{align*}
+    \lambda_{n+1,d} \le \lambda_{n,d} \le \cdots \le \lambda_{1,d}
+    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d',\vp)} \le \frac{1}{T(\lambda_{n, d}^{-1},d',\vp)} \le \cdots \le \frac{1}{T(\lambda_{1, d}^{-1},d',\vp)} \\
+    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d',\vp) }
+    \le \frac 1n \sum_{i=1}^n  \frac{1}{T(\lambda_{i, d}^{-1},d',\vp) }
+    \le \frac 1n \sum_{i=1}^{N(d')}  \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)}.
+\end{align*}
+Thus, we can conclude from the previous line that
+\begin{multline} \label{eq:implicate_a}
+    n \ge T(\varepsilon^{-1},d',\vp) \sum_{i=1}^{N(d')} \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} \\
+   \implies   \frac{1}{T(\lambda_{n+1, d}^{-1},d',\vp)} \le
+   \frac 1n \sum_{i=1}^{N(d')} \frac{1}{T(\lambda_{i, d}^{-1},d',\vp) } \le \frac{1}{T(\varepsilon^{-1},d',\vp)} \qquad \forall \varepsilon > 0, \ d,d' \in \naturals.
+\end{multline}
+
+Moreover, given that $T$ is increasing in its arguments, we have the following equivalent expression for the complexity via \eqref{eq:comp_def}:
+    \begin{align} %\label{eq:comp_equiv}
+    \nonumber
+    \comp(\varepsilon, d) & = \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon\} \\
+    \nonumber
+    & = \min \biggl\{n \in \natzero : \frac{1}{T(\lambda_{n+1,d}^{-1},d',\vp)}\le \frac{1}{T(\varepsilon^{-1},d',\vp) }\biggr\} \qquad \forall d' \in \naturals\\
+    \nonumber
+    & \le  \min \biggl\{n \in \natzero : n \ge T(\varepsilon^{-1},d',\vp) \sum_{i=1}^{N(d')} \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} \biggr\} \quad \forall d' \in \naturals \qquad \text{by \eqref{eq:implicate_a}} \\
+    & \le  T(\varepsilon^{-1},d',\vp) \sum_{i=1}^{N(d')} \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} + 1 \quad \forall d' \in \naturals. \label{eq:compUP}
+\end{align}
+
+Now we take this upper bound further, specializing to the case of $d'=1$:
+\begin{align*}
+       \comp(\varepsilon,d)
+       & \le T(\varepsilon^{-1},1, \vp) \Biggl [ \sum_{i=1}^{L_{\vp}-1} \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}
+       + \underbrace{\sum_{i=L_{\vp}}^\infty \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}}_{\le S_{\vp} <\infty\ \text{by \eqref{eq:strong_tractiff3}} }
+       + \frac{1}{T(\varepsilon^{-1},1, \vp)} \Biggr] \\
+       & \le T(\varepsilon^{-1},1,\vp) \underbrace{\left[\frac{(L_{\vp}-1)}{T(\lambda_{\max}^{-1},1,\vp)} + S_{\vp} + \frac{1}{T(0,1, \vp)}\right]}_{=:C_{\vp}}\\
+       & =  C_{\vp}T(\varepsilon^{-1},1,\vp).
+%       & \le \underbrace{2 C_{1,\vp}}_{\text{since } T(\varepsilon^{-1},1,\vp) \ge 1} T(\varepsilon^{-1},1,\vp)
+%       = \underbrace{C_{\vp}}_{:=2 C_{1,\vp}}T(\varepsilon^{-1},1,\vp).
+\end{align*}
+This means that we have strong $T$-tractability via \eqref{eq:strong_tract_def}, and verifies the sufficiency of \eqref{eq:strong_tractiff3}.
+
+\bigskip
+\noindent \textbf{Necessary condition:} \\
+Suppose that we have strong
+$T$-tractability as defined in \eqref{eq:strong_tract_def}. That is, for some $\vp \ge \vzero$ there exists a positive constant $C_{\vp}$ such that
+\[
+\comp(\varepsilon,d)\le C_{\vp}\, T(\varepsilon^{-1},1,\vp)
+\qquad \forall \varepsilon > 0, \ d \in \mathbb{N}.
+\]
+Since the sequence of eigenvalues $\lambda_{1,d}, \lambda_{2,d}, \ldots $ is non-increasing, we have
+\begin{equation}\label{eq:lambda_K_strong3}
+\lambda_{\lfloor C_{\vp}\, T(\varepsilon^{-1},1,\vp)\rfloor +1,d}\le \varepsilon.
+\end{equation}
+
+Define
+\[
+i(\varepsilon,\vp):= \lfloor C_{\vp}\, T(\varepsilon^{-1},1,\vp)\rfloor +1, \quad
+i(\infty,\vp) = \lim_{\varepsilon \to \infty}  i(\varepsilon,\vp) \ge 1 .
+\]
+Thus, it follows by \eqref{eq:lambda_K_strong3} that $\lambda_{i(\varepsilon,\vp),d} \le \varepsilon$.
+Note furthermore that we always have
+\[
+i(\varepsilon,\vp)\le C_{\vp}\, T(\varepsilon^{-1},1,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,\vp),d}^{-1},1,\vp)+1, \qquad \forall \varepsilon > 0,
+\]
+since
+$T(\cdot,1, \vp)$ is non-decreasing.
+
+For $\varepsilon$ taking on all positive values, $i(\varepsilon,\vp)$ takes on all values greater than or equal to $i(\infty,\vp)$, so
+\[
+i\le C_{\vp} T(\lambda_{i,d}^{-1},1,\vp)+1, \qquad \forall i \ge i(\infty,\vp).
+\]
+This implies via our technical assumption \eqref{eq:ptauassume} that
+\begin{gather*}
+ K_{\vp,\tau}\,T (\lambda_{i,d}^{-1},1,\tau \vp) \ge
+ [T(\lambda_{i,d}^{-1},1, \vp)]^\tau
+ \ge
+  \left[\frac{(i-1)}{C_{\vp}}\right]^\tau \qquad \forall i \ge i(\infty,\vp) \\
+ \frac{1}{T (\lambda_{i,d}^{-1},1,\tau \vp)} \le
+\frac{K_{\vp,\tau}\, C_{\vp}^\tau}{(i-1)^\tau}\qquad \forall i \ge \max\{i(\infty,\vp),2\} .
+\end{gather*}
+Summing both sides of this last inequality over $i$ from $i(\infty,\vp) +1 \ge 2$ to $\vinfty$ yields
+\begin{equation*}
+\sup_{d\in\naturals} \sum_{i=i(\infty,\vp) +1 }^\infty \frac{1}{T (\lambda_{i,d}^{-1},1, \tau \vp)}
+ \le  K_{\vp,\tau}\, C_{\vp}^\tau
+\sum_{i=2}^\infty \frac{1}{(i-1)^\tau} \\
+ \le K_{\vp,\tau}\, C_{\vp}^\tau
+\zeta (\tau)  < \infty,
+\end{equation*}
+where $\zeta$ denotes the Riemann zeta function.
+This yields \eqref{eq:strong_tractiff3} with $\vp$ replaced by $\vp' = \tau \vp$ and $L_{\vp'} = i(\infty,\vp) +1$, and so we see the necessity of $\eqref{eq:strong_tractiff3}$.
+
+\bigskip
+\noindent \textbf{Optimality:} \\
+To complete the proof, we must show that $\cp_{\textup{strct}} = \widetilde{\cp}_{\textup{strct}}$.
+Then, the expression for  $\cp_{\textup{sopt}}$ automatically follows from its definition in \eqref{eq:Psoptdef}.
+
+First we show  that if $\vp^* \in \cp_{\textup{strct}}$, then $\vp^* \in \widetilde{\cp}_{\textup{strct}}$.
+If $\vp^* \in \cp_{\textup{strct}}$, then \eqref{eq:strong_tract_def} must hold for all $\vp' \in (\vp^*,\vinfty)$.
+For any $\vp' \in (\vp^*,\vinfty)$, we may choose $\vp$ and $\tau$ such that $\vp^* < \vp < \vp' = \tau \vp$.
+Since $\vp > \vp^*$, \eqref{eq:strong_tract_def} also holds for $\vp$, and it follows that \eqref{eq:strong_tractiff3} must hold for $\vp'$ by the proof of necessity above.
+Thus, $\vp^* \in \widetilde{\cp}_{\textup{strct}}$.
+
+Next we show that if $\vp^* \in \widetilde{\cp}_{\textup{strct}}$, then $\vp^* \in \cp_{\textup{strct}}$.
+If $\vp^* \in \widetilde{\cp}_{\textup{strct}}$, then \eqref{eq:strong_tractiff3}  holds for all $\vp \in (\vp^*,\vinfty)$.
+By the argument to prove the sufficient condition above, it follows that \eqref{eq:strong_tract_def} must also hold for all $\vp \in (\vp^*,\vinfty)$.
+Thus, $\vp^* \in \cp_{\textup{strct}}$.
+
+\bigskip
+
+\noindent This concludes the proof of  Theorem \ref{thm_main_strong_tract2}.
+
+\end{proof}
+
 \section{Discussion and Summary}
@@
 \begin{itemize}
-\item Do we consider the case of normalized error? (Peter) 
+\item Do we consider the case of normalized error?
+\peter{What would most likely change then, is: we would normalize all eigenvalues by dividing by the values of the $\lambda_{1,d}$, and all summations in the conditions could start with the index 1.
+It might be a bit more tricky for sub-$h$ tractability, where we would maybe make sure that all functions are still suitably defined.
+However, I would not expect new proof ideas.
+Maybe a remark along the lines of ``presumably everything works analogously'' is sufficient?}
 \item Are there cases of $T$ that do not correspond to known tractability measures? (Kachi)

### 2023-04-28 GeneralizedTractability_230418.tex
Updates from Overleaf

@@
 However, since we assume non-negativity of the $\lambda_{i,d}$, the notation used here is equivalent.
+\peter{[PETER: I am wondering whether we should go back to the more common notation once the manuscript is finalized (not right away). It would make the paper easier to read for the IBC community.]}
+
 The non-decreasing ordering of the eigenvalues for each $d$ facilitates the proof of conditions for tractability, but our conditions do not depend on the ordering.
@@
 \end{align*}
+
+\peter{
+[PETER: This is an alternative part of the proof. If it is correct we could use it instead of the black text.
+
+\bigskip
+
+Let $\widetilde{J}\in\naturals$.
+Since the $\lambda_{i,d}$ are non-increasing in $i$, it follows that the $T(\lambda_{i,d}^{-1},d',\vp)$ are non-decreasing in $i$ for any $d'\in\naturals$.
+In particular, for all $n\ge \widetilde{J}$, we have
+\begin{align*}
+    \lambda_{n+1,d} \le \lambda_{n,d} \le \cdots \le \lambda_{\widetilde{J},d}
+    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d',\vp)} \le \frac{1}{T(\lambda_{n, d}^{-1},d',\vp)} \le \cdots \le \frac{1}{T(\lambda_{\widetilde{J}, d}^{-1},d',\vp)} \\
+     \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d',\vp) }
+    \le &\frac{1}{n-\widetilde{J}+1} \sum_{i=\widetilde{J}}^n  \frac{1}{T(\lambda_{i, d}^{-1},d',\vp) }
+    \le \frac{1}{n-\widetilde{J}+1} \sum_{i=\widetilde{J}}^\infty  \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)}.
+\end{align*}
+
+Thus, we can conclude from the previous line that
+\begin{multline} \label{eq:implicate_a}
+    n - \widetilde{J} +1 \ge T(\varepsilon^{-1},d',\vp) \sum_{i=\widetilde{J}}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} \\
+   \implies   \frac{1}{T(\lambda_{n+1, d}^{-1},d',\vp)} \le
+   \frac{1}{n-\widetilde{J}+1} \sum_{i=\widetilde{J}}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d',\vp) } \le \frac{1}{T(\varepsilon^{-1},d',\vp)} \qquad \forall \varepsilon > 0, \ d,d' \in \naturals.
+\end{multline}
+
+Now we take this upper bound further, specializing to the case of $d'=1$ and $\widetilde{J}=L_{\vp}$:
+\begin{align*}
+       \comp(\varepsilon,d)
+       & \le T(\varepsilon^{-1},1, \vp) \Biggl [ \underbrace{\sum_{i=L_{\vp}}^\infty \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}}_{\le S_{\vp} <\infty\ \text{by \eqref{eq:strong_tractiff3}} }
+       + \frac{L_{\vp}}{T(\varepsilon^{-1},1, \vp)} \Biggr] \\
+       & \le T(\varepsilon^{-1},1,\vp) \underbrace{\left[S_{\vp} + \frac{L_{\vp}}{T(0,1, \vp)}\right]}_{=:C_{\vp}}\\
+       & =  C_{\vp}T(\varepsilon^{-1},1,\vp).
+%       & \le \underbrace{2 C_{1,\vp}}_{\text{since } T(\varepsilon^{-1},1,\vp) \ge 1} T(\varepsilon^{-1},1,\vp)
+%       = \underbrace{C_{\vp}}_{:=2 C_{1,\vp}}T(\varepsilon^{-1},1,\vp).
+\end{align*}
+
+\bigskip
+
+END OF THE ALTERNATIVE PROOF.]
+
+}
+
 This means that we have strong $T$-tractability via \eqref{eq:strong_tract_def}, and verifies the sufficiency of \eqref{eq:strong_tractiff3}.
@@
 Then $\cp_{\textup{opt}} \subseteq \widetilde{\cp}_{\textup{opt}}$.
-\
+
 \end{theorem}
@@
 \end{align*}
+
+\peter{
+[PETER: This is an alternative part of the proof. If it is correct we could use it instead of the black text.
+
+\bigskip
+
+Let $J(\vp,d): = \lceil L_{\vp}\, T(0,d,\vp)\rceil$.
+By the argument in the proof of the sufficient condition for Theorem \ref{thm_main_strong_tract2}, it follows from \eqref{eq:compUP} with $d'=d$ that the information complexity has an upper bound of
+\begin{equation*}
+	 \comp(\varepsilon,d) \le  T(\varepsilon^{-1},d,\vp) \sum_{i=J(\vp,d)}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)} + J(\vp,d)
+\end{equation*}
+ Then this upper bound on the complexity can be further bounded above by
+\begin{align*}
+       \comp(\varepsilon,d)
+       & \le T(\varepsilon^{-1},d,\vp) \Biggl [ 
+       \underbrace{\sum_{i=J(\vp,d)}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}}_{\le S_{\vp} \text{ by \eqref{eq:tractiff4}}}
+       + \frac{J(\vp,d)}{T(\varepsilon^{-1},d, \vp)} \Biggr ] \\
+       & \le T(\varepsilon^{-1},d,\vp)\left[ S_{\vp} + \frac{L_{\vp} T(0,d,\vp)+1}{T(\varepsilon^{-1},d, \vp)}\right]\\
+       & \le T(\varepsilon^{-1},d,\vp)\left[S_{\vp} +\frac{L_{\vp} T(0,d,\vp)}{T(\varepsilon^{-1},d, \vp)}
+       + \frac{1}{T(0,1, \vp)}\right]
+       \qquad \text{by \eqref{eq:Tnondecreasing}}   \\
+       & \le T(\varepsilon^{-1},d,\vp) 
+       \underbrace{\left [  S_{\vp} + L_{\vp} + \frac{1}{T(0,1, \vp)}\right]}_{=:C_{\vp}}
+       \qquad \text{by \eqref{eq:Tnondecreasing}}  
+\end{align*}
+
+\bigskip
+
+END OF THE ALTERNATIVE PROOF.]
+}
+
 It follows that we have $T$-tractability, which shows sufficiency of \eqref{eq:tractiff4}.

### 2023-05-06 GeneralizedTractability_230501.tex
Updates from Overleaf

--- 2023-04-28 GeneralizedTractability_230418.tex
@@
 
-For this case where arbitrary linear functionals are allowed, the optimal solution is
+For this case where arbitrary linear functionals are allowed, the optimal solution operator is
 \[
@@
 		[\max(1,\log(1 + \varepsilon^{-1}))]^p  d^{q} & d^{q} \\
-        \text{quasi-polynomial} & 
+        \text{quasi-polynomial algebraic} & 
         \exp\{p(1+\log(\max(1,\varepsilon^{-1}))(1+\log(d))\} &
+        \exp\{p(1+\log(d))\}\\
+        \text{quasi-polynomial exponential} & 
+        \exp\{p(1+\log(1+\log(\max(1,\varepsilon^{-1})))(1+\log(d))\} &
         \exp\{p(1+\log(d))\}
@@
 \end{equation*}}
+
 Here above, $\vp = (p,q)$ in some cases and $\vp$ is a scalar in other cases. A general reference
@@
 
-END OF THE ALTERNATIVE PROOF.]
+END OF THE ALTERNATIVE PROOF.
+
+TODO: Explain that $n\ge \widetilde{J}$ is no restriction due to the upper bound on the complexity.
+]
 
@@
 
+\fred{Compare the lower summation indices for Theorems 1 and 2}
 \begin{proof}
@@
 
-Let $J(\vp,d): = \lceil L_{\vp}\, T(0,d,\vp)\rceil$.
+Let $\widetilde{J}:=J(\vp,d): = \lceil L_{\vp}\, T(0,d,\vp)\rceil$.
 By the argument in the proof of the sufficient condition for Theorem \ref{thm_main_strong_tract2}, it follows from \eqref{eq:compUP} with $d'=d$ that the information complexity has an upper bound of
@@
 \[
- T(\varepsilon^{-1},d,p)= (\max\{\varepsilon^{-1},1\})^p
+ T(\varepsilon^{-1},d,p)= \max\{1,\varepsilon^{-p}\}
  \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, p \ge 0.
@@
 \[
- \sup_{d\in\naturals} \sum_{i=L_p}^\infty (\min\{\lambda_{i,d},1\})^p < \infty \text{ for some } p \ge 0, L_p \in \naturals.
+ \sup_{d\in\naturals} \sum_{i=L_p}^\infty (1,\min\{\lambda_{i,d}^p\}) < \infty \text{ for some } p \ge 0, L_p \in \naturals.
 \]
@@
 \[
- T(\varepsilon^{-1},d,p,q)= (\max\{\varepsilon^{-1},1\})^p\, d^q
+ T(\varepsilon^{-1},d,(p,q))= (\max\{1,\varepsilon^{-p}\})\, d^q
  \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, p,q \ge 0.
@@
 \[
- \sup_{d\in\naturals} \sum_{i=L_{p,q} d^{q}}^\infty (\min\{\lambda_{i,d},1\})^p d^{-q} < \infty \text{ for some } p,q \ge 0, L_{p,q} \in \naturals.
+ \sup_{d\in\naturals} \sum_{i=L_{p,q} d^{q}}^\infty (\min\{1,\lambda_{i,d}^p\}) d^{-q} < \infty \text{ for some } p,q \ge 0, L_{p,q} \in \naturals.
 \]
@@
 
-\kachi{\begin{example}[EXP-strong polynomial tractability]
-Let $ T :(0,\infty) \times \mathbb{N} \times [0,\infty)^s \rightarrow (0,\infty)$
+\begin{example}[Strong exponential polynomial tractability]
+Let the tractability function, $T$,
 be defined by
 \[
- T(\varepsilon^{-1},d,\vp)= (1+\log\max\{\varepsilon^{-1},1\})^p.
+ T(\varepsilon^{-1},d,p)= \left[\max\{1,\log(1+\varepsilon^{-1}\})\right]^p.
 \]
@@
 \end{example}
-\begin{example}[EXP-polynomial tractability]
-
-Let $ T :(0,\infty) \times \mathbb{N} \times [0,\infty)^s \rightarrow (0,\infty)$
+\begin{example}[Exponential polynomial tractability]
+
+Let the tractability function, $T$,
 be defined by
 \[
- T(\varepsilon^{-1},d,\vp)= (1+\log \max\{\varepsilon^{-1},1\})^p\, d^q.
+ T(\varepsilon^{-1},d,(p,q))=\left[\max\{1,\log(1+\varepsilon^{-1}\})\right]^p\, d^q.
 \]
@@
 \]
-\end{example}}
-\bigskip
-
-%\begin{definition}[Quasi-polynomial Tractability]
- %   The problem is \emph{quasi-polynomially tractable}, if there exist two constants $C, t> 0$ such that
-  %  \[
-   % n(\varepsilon,d) \leq C\exp\{t(1+\ln(\varepsilon^{-1}))(1+\ln(d))\}
-    %\] for all $\varepsilon \in (0,1)$ and $d\in\mathbb{N}$.
-%\end{definition}
-
-%\paragraph{Example 5: $(t,s)$-Weak tractability}
-%Let $ T :(0,\infty) \times \mathbb{N} \times [0,\infty)^s \rightarrow (0,\infty)$. Suppose we have $T$-$(s,t)$- weak tractability, such that
-%\[ \lim_{d+\varepsilon^{-1}\rightarrow\infty} \frac{\log \max(1,n(\varepsilon,d))}{d^t +(\max(1,\varepsilon^{-1}))^s} =0.\]
-%Then Theorem \ref{thm:weak} yields the iff-condition
-%\[
-%\sup_{d\in\naturals} \sigma (c,d,s,\vp) \exp\left(-c\, T(0,d^t,\vp)\right)<\infty
-%\]
-%where $\displaystyle\sigma (c,d,s,\vp) =\sum_{i=1}^\infty \exp\left(-c\left(\lambda^{-1}_{i,d}\right)^{s/2}\right) $
-\kachi{
-\begin{example}[Quasi-$T$-polynomial tractability]
+\end{example}
+\bigskip
+
+\begin{example}[Algebraic quasi-polynomial tractability]
 \begin{definition}
@@
 \end{definition}
-Suppose $ T :(0,\infty) \times \mathbb{N} \times [0,\infty)^s \rightarrow (0,\infty)$
+Let the tractability function, $T$,
 be defined by
 \[
- T(\varepsilon^{-1},d,\vp)= \exp\{\vp(1+\log d)(1+\log\max\{\varepsilon^{-1},1\})\}
-\]
-Observe that this is a special case of the $T$-tractability function, where the function is polynomial in exponent $1+\log d$ and $1+\log\max\{\varepsilon^{-1},1\}$.
+ T(\varepsilon^{-1},d,p)= \exp\{p(1+\log(\max\{1,\varepsilon^{-1}\})(1+\log d)\}
+\]
+Observe that this is a special case of the $T$-tractability function, where the function is polynomial of exponent $1+\log d$ and $1+\log\max\{\varepsilon^{-1},1\}$.
 
@@
 \]
+\end{example}
+\kachi{
+\begin{example}[Separable tractability]
+Let the tractability function, $T$,
+be defined by
+\[
+ T(\varepsilon^{-1},d,(p,q))= \phi(\varepsilon^{-1},p)\, \psi(d,q)
+ \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, p,q \ge 0.
+\]
+with non-decreasing functions $\phi : (0,\infty) \times (0,\infty) \to (0,\infty)$ and $\psi : \naturals  \times (0,\infty) \to (0,\infty)$.
+In addition, satisfying the following conditions as in (\ref{eq:ptauassume})
+\begin{align*}
+ (\phi(\varepsilon^{-1},p))^{\tau_1} &\le K_{p,\tau_1} \phi (\varepsilon^{-1},\tau_1 p)\\
+  (\psi(d,q))^{\tau_2} &\le K_{q,\tau_2} \psi (d,\tau_2 q)\\
+\end{align*}
+where $\tau_1, \tau_2>0$. %As the name implies, the roles of $\varepsilon^{-1}$ and $d$ are separated. 
+\end{example}
+\begin{example}[Non-separable symmetric tractability]
+    Let the tractability function, $T$, be defined by
+\[
+ T(\varepsilon^{-1},d,(p,q))= \exp\{\phi(\varepsilon^{-1},p)\, \psi(d,q)\}
+ \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, p,q \ge 0.
+\]  with non-decreasing functions $f_1$, $f_2 : [1,\infty)\rightarrow[1,\infty)$.
 \end{example}
@@
 
+\section{Acknowledgments}
+Thank Henryk and Erich.
+
 \begin{thebibliography}{99}

### 2023-05-06 GeneralizedTractability_230501.tex
revising section 2

@@
 \begin{equation} \label{eq:eigenvalues}
-\lambda_{\max}^2 \ge \lambda_{1,d}^2 \ge \lambda_{2,d}^2 \ge \cdots, \qquad u_{1,d}, u_{2,d}, \ldots, \qquad d \in \naturals.
+ \lambda_{1,d}^2 \ge \lambda_{2,d}^2 \ge \cdots, \qquad u_{1,d}, u_{2,d}, \ldots, \qquad d \in \naturals.
 \end{equation}
-\fred{Are we restricting ourselves by not allowing $\lambda_{1,d} \to \infty$ as $d \to \infty$?}
-\peter{Yes, indeed, I think we do (e.g., think of tensor product spaces where the first eigenvalue is bigger than one).
-But I am wondering whether we could do without $\lambda_{\max}$ by the assumption that $T$ is bounded away from zero by some absolute value $t$.
-Then, in all cases we could bound $1/T(\cdot,\cdot,\cdot)$ by $1/t$.
-Actually, is $T(0,1,\boldsymbol{0})$ our $t$?}
-
 This means that the non-negative $\lambda_{i,d}$ are the singular values of the operator $\SOL_d$.
@@
 However, since we assume non-negativity of the $\lambda_{i,d}$, the notation used here is equivalent.
-\peter{[PETER: I am wondering whether we should go back to the more common notation once the manuscript is finalized (not right away). It would make the paper easier to read for the IBC community.]}
-
+\peter{[PETER: I am wondering whether we should go back to the more common notation once the manuscript is finalized (not right away).
+It would make the paper easier to read for the IBC community.]}\fred{Fred: If we do, we introduce a lot of $\sqrt{\lambda}$ or $\varepsilon^{-2}$, which I find harder to translate in my brain.
+But I  will submit to the will of the majority.}
 The non-decreasing ordering of the eigenvalues for each $d$ facilitates the proof of conditions for tractability, but our conditions do not depend on the ordering.
@@
     \label{eq:errcrit}
-    \norm[\cg_d]{\SOL_d(f) - \APP_d(f,\varepsilon)} \le \varepsilon \qquad \forall f \in \cb_d, \ \varepsilon \in (0,\infty)
+    \norm[\cg_d]{\SOL_d(f) - \APP_d(f,\varepsilon)} \le \varepsilon \qquad \forall f \in \cb_d, \ \varepsilon \in (0,\infty),
 \end{equation}
@@
 \begin{equation*}
-	\begin{array}{r@{\qquad}c@{\qquad}cc}
+	\begin{array}{r@{\quad}c@{\quad}cc}
 		\text{Tractability type} & T(\varepsilon^{-1},d,\vp)
@@
 \textbf{Sufficient condition:}\newline
-We make the first part of the argument in some generality so that it can be reused in the proof of Theorem \ref{thm_main_tract2} for tractability.
+We make the first part of the argument in some generality so that it can be reused in the proof of Theorem \ref{thm_main_tract2} for tractability.  Fix any $\varepsilon > 0$ and any $d \in \naturals$.
 
 Since the $\lambda_{i,d}$ are non-increasing in $i$, it follows that the $T(\lambda_{i,d}^{-1},d',\vp)$ are non-decreasing in $i$ for any $d'\in\naturals$.
-In particular, for all $n\in \mathbb{N}$, we have
+In particular, for  any $N\in\naturals$ with $n\ge N$, we have
 \begin{align*}
-    \lambda_{n+1,d} \le \lambda_{n,d} \le \cdots \le \lambda_{1,d}
-    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d',\vp)} \le \frac{1}{T(\lambda_{n, d}^{-1},d',\vp)} \le \cdots \le \frac{1}{T(\lambda_{1, d}^{-1},d',\vp)} \\
-    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d',\vp) }
-    \le \frac 1n \sum_{i=1}^n  \frac{1}{T(\lambda_{i, d}^{-1},d',\vp) }
-    \le \frac 1n \sum_{i=1}^\infty  \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)}.
+    \lambda_{n+1,d} \le \lambda_{n,d} \le \cdots \le \lambda_{N,d}
+    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d',\vp)} \le \frac{1}{T(\lambda_{n, d}^{-1},d',\vp)} \le \cdots \le \frac{1}{T(\lambda_{N, d}^{-1},d',\vp)} \\
+     \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d',\vp) }
+    \le &\frac{1}{n-N+1} \sum_{i=N}^n  \frac{1}{T(\lambda_{i, d}^{-1},d',\vp) }
+    \le \frac{1}{n-N+1} \sum_{i=N}^\infty  \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)}.
 \end{align*}
@@
 \begin{multline} \label{eq:implicate_a}
-    n \ge T(\varepsilon^{-1},d',\vp) \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} \\
+    n - N +1 \ge T(\varepsilon^{-1},d',\vp) \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} \\
    \implies   \frac{1}{T(\lambda_{n+1, d}^{-1},d',\vp)} \le
-   \frac 1n \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d',\vp) } \le \frac{1}{T(\varepsilon^{-1},d',\vp)} \qquad \forall \varepsilon > 0, \ d,d' \in \naturals.
+   \frac{1}{n-N+1} \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d',\vp) } \le \frac{1}{T(\varepsilon^{-1},d',\vp)} \\ \forall d', n, N \in \naturals, \ N \le n.
 \end{multline}
@@
 	\nonumber
-    & = \min \biggl\{n \in \natzero : \frac{1}{T(\lambda_{n+1,d}^{-1},d',\vp)}\le \frac{1}{T(\varepsilon^{-1},d',\vp) }\biggr\} \qquad \forall d' \in \naturals\\
+	& = \min \biggl\{n \in \natzero : \frac{1}{T(\lambda_{n+1,d}^{-1},d',\vp)}\le \frac{1}{T(\varepsilon^{-1},d',\vp) }\biggr\} \qquad  \forall d'\in \naturals\\
 	\nonumber
-    & \le  \min \biggl\{n \in \natzero : n \ge T(\varepsilon^{-1},d',\vp) \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} \biggr\} \quad \forall d' \in \naturals \qquad \text{by \eqref{eq:implicate_a}} \\
-    & \le  T(\varepsilon^{-1},d',\vp) \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} + 1 \quad \forall d' \in \naturals. \label{eq:compUP}
+	& \le  \min \biggl\{n \in \natzero : n \ge N - 1 + T(\varepsilon^{-1},d',\vp) \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} \biggr\} \;  \forall  d', N \in \naturals, \quad \text{by \eqref{eq:implicate_a}}.
+	\intertext{Note that in this last expression, $n \ge N$ is enforced since $n$ is an integer strictly greater than  $N-1$ by definition.  This then implies that}
+	\comp(\varepsilon, d) 
+	& \le  T(\varepsilon^{-1},d',\vp) \Biggl [\frac{N}{T(\varepsilon^{-1},d',\vp)}  +  \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} \Biggr] \quad \forall  d', N \in \naturals.
+\label{eq:compUP}
 \end{align}
 
-Now we take this upper bound further, specializing to the case of $d'=1$:
+Now we take this upper bound further, specializing to the case of $d'=1$ and $N=L_{\vp}$:
 \begin{align*}
        \comp(\varepsilon,d)
-       & \le T(\varepsilon^{-1},1, \vp) \Biggl [ \sum_{i=1}^{L_{\vp}-1} \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}
-       + \underbrace{\sum_{i=L_{\vp}}^\infty \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}}_{\le S_{\vp} <\infty\ \text{by \eqref{eq:strong_tractiff3}} }
-       + \frac{1}{T(\varepsilon^{-1},1, \vp)} \Biggr] \\
-       & \le T(\varepsilon^{-1},1,\vp) \underbrace{\left[\frac{(L_{\vp}-1)}{T(\lambda_{\max}^{-1},1,\vp)} + S_{\vp} + \frac{1}{T(0,1, \vp)}\right]}_{=:C_{\vp}}\\
+       & \le T(\varepsilon^{-1},1, \vp) \Biggl [ \frac{L_{\vp}}{T(\varepsilon^{-1},1, \vp)}  + \underbrace{\sum_{i=L_{\vp}}^\infty \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}}_{\le S_{\vp} <\infty\ \text{by \eqref{eq:strong_tractiff3}} }
+        \Biggr] \\
+       & \le T(\varepsilon^{-1},1,\vp) \underbrace{\left[\frac{L_{\vp}}{T(0,1, \vp)} + S_{\vp} \right]}_{=:C_{\vp}}
+       \qquad \text{by \eqref{eq:Tnondecreasing}}\\
        & =  C_{\vp}T(\varepsilon^{-1},1,\vp).
@@
 \end{align*}
-
-\peter{
-[PETER: This is an alternative part of the proof. If it is correct we could use it instead of the black text.
-
-\bigskip
-
-Let $\widetilde{J}\in\naturals$.
-Since the $\lambda_{i,d}$ are non-increasing in $i$, it follows that the $T(\lambda_{i,d}^{-1},d',\vp)$ are non-decreasing in $i$ for any $d'\in\naturals$.
-In particular, for all $n\ge \widetilde{J}$, we have
-\begin{align*}
-    \lambda_{n+1,d} \le \lambda_{n,d} \le \cdots \le \lambda_{\widetilde{J},d}
-    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d',\vp)} \le \frac{1}{T(\lambda_{n, d}^{-1},d',\vp)} \le \cdots \le \frac{1}{T(\lambda_{\widetilde{J}, d}^{-1},d',\vp)} \\
-     \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d',\vp) }
-    \le &\frac{1}{n-\widetilde{J}+1} \sum_{i=\widetilde{J}}^n  \frac{1}{T(\lambda_{i, d}^{-1},d',\vp) }
-    \le \frac{1}{n-\widetilde{J}+1} \sum_{i=\widetilde{J}}^\infty  \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)}.
-\end{align*}
-
-Thus, we can conclude from the previous line that
-\begin{multline} \label{eq:implicate_a}
-    n - \widetilde{J} +1 \ge T(\varepsilon^{-1},d',\vp) \sum_{i=\widetilde{J}}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} \\
-   \implies   \frac{1}{T(\lambda_{n+1, d}^{-1},d',\vp)} \le
-   \frac{1}{n-\widetilde{J}+1} \sum_{i=\widetilde{J}}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d',\vp) } \le \frac{1}{T(\varepsilon^{-1},d',\vp)} \qquad \forall \varepsilon > 0, \ d,d' \in \naturals.
-\end{multline}
-
-Now we take this upper bound further, specializing to the case of $d'=1$ and $\widetilde{J}=L_{\vp}$:
-\begin{align*}
-       \comp(\varepsilon,d)
-       & \le T(\varepsilon^{-1},1, \vp) \Biggl [ \underbrace{\sum_{i=L_{\vp}}^\infty \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}}_{\le S_{\vp} <\infty\ \text{by \eqref{eq:strong_tractiff3}} }
-       + \frac{L_{\vp}}{T(\varepsilon^{-1},1, \vp)} \Biggr] \\
-       & \le T(\varepsilon^{-1},1,\vp) \underbrace{\left[S_{\vp} + \frac{L_{\vp}}{T(0,1, \vp)}\right]}_{=:C_{\vp}}\\
-       & =  C_{\vp}T(\varepsilon^{-1},1,\vp).
-%       & \le \underbrace{2 C_{1,\vp}}_{\text{since } T(\varepsilon^{-1},1,\vp) \ge 1} T(\varepsilon^{-1},1,\vp)
-%       = \underbrace{C_{\vp}}_{:=2 C_{1,\vp}}T(\varepsilon^{-1},1,\vp).
-\end{align*}
-
-\bigskip
-
-END OF THE ALTERNATIVE PROOF.
-
-TODO: Explain that $n\ge \widetilde{J}$ is no restriction due to the upper bound on the complexity.
-]
-
-}
-
 This means that we have strong $T$-tractability via \eqref{eq:strong_tract_def}, and verifies the sufficiency of \eqref{eq:strong_tractiff3}.
@@
 \begin{equation}\label{eq:lambda_K_strong3}
-\lambda_{\lfloor C_{\vp}\, T(\varepsilon^{-1},1,\vp)\rfloor +1,d}\le \varepsilon.
+\lambda_{\lfloor C_{\vp}\, T(\varepsilon^{-1},1,\vp)\rfloor +1,d}\le \varepsilon \qquad \forall \varepsilon > 0, \ d \in \mathbb{N}.
 \end{equation}
@@
 \[
-i(\varepsilon,\vp)\le C_{\vp}\, T(\varepsilon^{-1},1,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,\vp),d}^{-1},1,\vp)+1, \qquad \forall \varepsilon > 0,
+i(\varepsilon,\vp)\le C_{\vp}\, T(\varepsilon^{-1},1,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,\vp),d}^{-1},1,\vp)+1, \qquad \forall \varepsilon > 0, \ d \in \mathbb{N},
 \]
@@
 \[
-i\le C_{\vp} T(\lambda_{i,d}^{-1},1,\vp)+1, \qquad \forall i \ge i(\infty,\vp).
+i\le C_{\vp} T(\lambda_{i,d}^{-1},1,\vp)+1, \qquad \forall i \ge i(\infty,\vp), \ d \in \naturals.
 \]
@@
  \ge
-  \left[\frac{(i-1)}{C_{\vp}}\right]^\tau \qquad \forall i \ge i(\infty,\vp) \\
+  \left[\frac{(i-1)}{C_{\vp}}\right]^\tau \qquad \forall i \ge i(\infty,\vp)), \ d \in \naturals, \\
  \frac{1}{T (\lambda_{i,d}^{-1},1,\tau \vp)} \le
-\frac{K_{\vp,\tau}\, C_{\vp}^\tau}{(i-1)^\tau}\qquad \forall i \ge \max\{i(\infty,\vp),2\} .
+\frac{K_{\vp,\tau}\, C_{\vp}^\tau}{(i-1)^\tau}\qquad \forall i \ge \max\{i(\infty,\vp),2\}), \ d \in \naturals .
 \end{gather*}
@@
 \end{equation}
-If \eqref{eq:tractiff4} holds for some $\vp$, let
+
+If \eqref{eq:tractiff4} holds for some $\vp$, let $\widetilde{\cp}_{\textup{trct}} : = \{\vp^* : \eqref{eq:tractiff4} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty}) \}$.
+Then $\cp_{\textup{trct}} = \widetilde{\cp}_{\textup{trct}}$, and the set of optimal  tractability parameters is
 \[
-\widetilde{\cp}_{\textup{opt}} : = \{\vp^* : \eqref{eq:tractiff4} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty}) \text{ and }  \eqref{eq:tractiff4} \text{ does not hold } \forall \vp \in [\vzero,\vp^*/2)\}.
+\cp_{\textup{opt}} =
+\{\vp^* \in \widetilde{\cp}_{\textup{trct}} :  \vp^* \notin [\widetilde{\vp},\boldsymbol{\infty}) \ \forall \widetilde{\vp}\in  \widetilde{\cp}_{\textup{trct}} \setminus \{\vp^*\} \}.
 \]
-Then $\cp_{\textup{opt}} \subseteq \widetilde{\cp}_{\textup{opt}}$.
 
@@
 
-\fred{Compare the lower summation indices for Theorems 1 and 2}
+Comparing the equivalent conditions for strong tractability in \eqref{eq:strong_tractiff3} and tractability in \eref{eq:tractiff4}, they are seen to be nearly the same.
+The difference lies in the lower summation index, which is allowed to depend on $d$ for tractability, and the second argument of $T$ in the sum, which is $1$ for strong tractability, and $d$ in general.
+Both of these can allow $S_{\vp}$ to be finite in Theorem \ref{thm_main_tract2}, when it may be infinite in Theorem \ref{thm_main_strong_tract2}.
+
 \begin{proof}
@@
 Suppose that \eqref{eq:tractiff4} holds for some $\vp \ge 0$. 
-By the argument in the proof of the sufficient condition for Theorem \ref{thm_main_strong_tract2}, it follows from \eqref{eq:compUP} with $d'=d$ that the information complexity has an upper bound of
-\begin{equation*}
-	 \comp(\varepsilon,d) \le  T(\varepsilon^{-1},d,\vp) \sum_{i=1}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)} + 1
-\end{equation*}
-
-Let $J(\vp,d): = \lceil L_{\vp}\, T(0,d,\vp)\rceil$.  Then this upper bound on the complexity can be further bounded above by
-\begin{align*}
-       \comp(\varepsilon,d)
-       & \le T(\varepsilon^{-1},d,\vp) \Biggl [ \sum_{i=1}^{J(\vp,d) -1} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}
-       + \underbrace{\sum_{i=J(\vp,d)}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}}_{\le S_{\vp} \text{ by \eqref{eq:tractiff4}}}
-       + \frac{1}{T(\varepsilon^{-1},d, \vp)} \Biggr ] \\
-       & \le T(\varepsilon^{-1},d,\vp)\left[ \frac{J(\vp,d)-1}{T(\lambda_{\max}^{-1},d,\vp)} + S_{\vp} + \frac{1}{T(0,1, \vp)}\right]
-       \qquad \text{by \eqref{eq:Tnondecreasing}}  \\
-       & \le T(\varepsilon^{-1},d,\vp)\left[\frac{L_{\vp}\, T(0,d,\vp)}{T(\lambda_{\max}^{-1},1,\vp)} + S_{\vp} + \frac{1}{T(0,1, \vp)}\right] \\
-       & =\frac{L_{\vp}}{T(\lambda_{\max}^{-1},1,\vp)} \,T(\varepsilon^{-1},d,\vp) T(0,d,\vp) + \left [  S_{\vp} + \frac{1}{T(0,1, \vp)}\right] T(\varepsilon^{-1},d,\vp)\\
-       & \le\frac{L_{\vp}}{T(\lambda_{\max}^{-1},1,\vp)} \,T(\varepsilon^{-1},d,\vp) T(\varepsilon^{-1},d,\vp) +\left [  S_{\vp} + \frac{1}{T(0,1, \vp)}\right] T(\varepsilon^{-1},d,\vp)\\
-       & \le \frac{L_{\vp}\,K_{\vp,2}}{T(\lambda_{\max}^{-1},1,\vp)}  T(\varepsilon^{-1},d,2\vp)  +\left [  S_{\vp} + \frac{1}{T(0,1, \vp)}\right] T(\varepsilon^{-1},d,\vp)  \qquad \text{by \eqref{eq:ptauassume}}\\
-       & \le \underbrace{\left[\frac{L_{\vp}\,K_{\vp,2}}{T(\lambda_{\max}^{-1},1,\vp)} + S_{\vp} + \frac{1}{T(0,1, \vp)}\right]}_{=:C_{2\vp}} \,T(\varepsilon^{-1},d,2\vp) \qquad \text{by \eqref{eq:Tnondecreasing}}.
-\end{align*}
-
-\peter{
-[PETER: This is an alternative part of the proof. If it is correct we could use it instead of the black text.
-
-\bigskip
-
-Let $\widetilde{J}:=J(\vp,d): = \lceil L_{\vp}\, T(0,d,\vp)\rceil$.
-By the argument in the proof of the sufficient condition for Theorem \ref{thm_main_strong_tract2}, it follows from \eqref{eq:compUP} with $d'=d$ that the information complexity has an upper bound of
-\begin{equation*}
-	 \comp(\varepsilon,d) \le  T(\varepsilon^{-1},d,\vp) \sum_{i=J(\vp,d)}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)} + J(\vp,d)
-\end{equation*}
- Then this upper bound on the complexity can be further bounded above by
+By the argument in the proof of the sufficient condition for Theorem \ref{thm_main_strong_tract2}, it follows from \eqref{eq:compUP} with $d'=d$ and $N = \lceil L_{\vp}\, T(0,d,\vp)\rceil$ that 
 \begin{align*}
@@
        & \le T(\varepsilon^{-1},d,\vp) \Biggl [ 
-       \underbrace{\sum_{i=J(\vp,d)}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}}_{\le S_{\vp} \text{ by \eqref{eq:tractiff4}}}
-       + \frac{J(\vp,d)}{T(\varepsilon^{-1},d, \vp)} \Biggr ] \\
-       & \le T(\varepsilon^{-1},d,\vp)\left[ S_{\vp} + \frac{L_{\vp} T(0,d,\vp)+1}{T(\varepsilon^{-1},d, \vp)}\right]\\
-       & \le T(\varepsilon^{-1},d,\vp)\left[S_{\vp} +\frac{L_{\vp} T(0,d,\vp)}{T(\varepsilon^{-1},d, \vp)}
-       + \frac{1}{T(0,1, \vp)}\right]
+       \frac{\lceil L_{\vp}\, T(0,d,\vp)\rceil}{T(\varepsilon^{-1},d,\vp)}  + 
+       \underbrace{\sum_{i=\lceil L_{\vp}\, T(0,d,\vp)\rceil}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}}_{\le S_{\vp} \text{ by \eqref{eq:tractiff4}}}
+       \Biggr ] 
+        \quad \forall \varepsilon > 0, \ d  \in \naturals\\
+       & \le T(\varepsilon^{-1},d,\vp)\left[\frac{L_{\vp} T(0,d,\vp)+1}{T(\varepsilon^{-1},d, \vp)} +  S_{\vp} \right]
+        \qquad \forall \varepsilon > 0, \ d  \in \naturals\\
+       & \le T(\varepsilon^{-1},d,\vp)\left[\frac{L_{\vp} T(0,d,\vp)}{T(\varepsilon^{-1},d, \vp)}
+       + \frac{1}{T(0,1, \vp)} + S_{\vp}\right]
        \qquad \text{by \eqref{eq:Tnondecreasing}}   \\
        & \le T(\varepsilon^{-1},d,\vp) 
-       \underbrace{\left [  S_{\vp} + L_{\vp} + \frac{1}{T(0,1, \vp)}\right]}_{=:C_{\vp}}
+       \underbrace{\left [  L_{\vp} + \frac{1}{T(0,1, \vp)} + S_{\vp} \right]}_{=:C_{\vp}}
        \qquad \text{by \eqref{eq:Tnondecreasing}}  
 \end{align*}
-
-\bigskip
-
-END OF THE ALTERNATIVE PROOF.]
-}
-
 It follows that we have $T$-tractability, which shows sufficiency of \eqref{eq:tractiff4}.
@@
 \[
-i\le C_{\vp}\, T(\varepsilon^{-1},d,\vp)+1 \le C_{\vp} T(\lambda_{i,d}^{-1},d,\vp)+1, \qquad \forall i \ge i(\infty,d,\vp).
+i\le C_{\vp}\, T(\varepsilon^{-1},d,\vp)+1 \le C_{\vp} T(\lambda_{i,d}^{-1},d,\vp)+1, \qquad \forall i \ge i(\infty,d,\vp),  \ d \in \naturals.
 \]
@@
 	\ge
-	\left[\frac{(i-1)}{C_{\vp}}\right]^\tau \qquad \forall i \ge i(\infty,d,\vp), \\
+	\left[\frac{(i-1)}{C_{\vp}}\right]^\tau \qquad \forall i \ge i(\infty,d,\vp),  \ d \in \naturals, \\
 	 \frac{1}{T (\lambda_{i,d}^{-1},d,\tau \vp)} \le
-	\frac{K_{\vp,\tau}\, C_{\vp}^\tau}{(i-1)^\tau}\qquad \forall i \ge \max\{i(\infty,\vp),2\}.
+	\frac{K_{\vp,\tau}\, C_{\vp}^\tau}{(i-1)^\tau}\qquad \forall i \ge \max\{i(\infty,\vp),2\},  \ d \in \naturals.
 \end{gather*}
@@
 \noindent \textbf{Optimality:}
-Finally we need to show that $\cp_{\textup{opt}} \subseteq \widetilde{\cp}_{\textup{opt}}$.
-Suppose that  $\vp^* \in \cp_{\textup{opt}}$.
-We show that $\vp^*$ satisfies the two conditions for membership in $\widetilde{\cp}_{\textup{opt}}$.
+This proof is similar to the proof for the optimality condition for strong tractability in Theorem \ref{thm_main_strong_tract2}.
+We must show that $\cp_{\textup{trct}} = \widetilde{\cp}_{\textup{trct}}$.
+Then, the expression for  $\cp_{\textup{opt}}$ in this theorem automatically follows from its definition in \eqref{eq:Poptdef}.
 
-By the definition of  $\cp_{\textup{opt}}$ \eqref{eq:tract_def}  holds for all $\vp \in (\vp^*,\boldsymbol{\infty})$, which implies by the argument for necessity that  \eqref{eq:tractiff4} holds for all $\vp \in (\vp^*,\boldsymbol{\infty})$.
-Indeed, the latter is deduced similarly as in the proof of Theorem \ref{thm_main_strong_tract2.}
-This is the first condition for membership in $\widetilde{\cp}_{\textup{opt}}$.
+First we show  that if $\vp^* \in \cp_{\textup{trct}}$, then $\vp^* \in \widetilde{\cp}_{\textup{trct}}$.
+If $\vp^* \in \cp_{\textup{trct}}$, then \eqref{eq:tract_def} must hold for all $\vp' \in (\vp^*,\vinfty)$.
+For any $\vp' \in (\vp^*,\vinfty)$, we may choose $\vp$ and $\tau$ such that $\vp^* < \vp < \vp' = \tau \vp$.
+Since $\vp > \vp^*$, \eqref{eq:tract_def} also holds for $\vp$, and it follows that \eqref{eq:tractiff4} must hold for $\vp'$ by the proof of necessity above.
+Thus, $\vp^* \in \widetilde{\cp}_{\textup{trct}}$.
 
-Also, if  $\vp^* \in \cp_{\textup{opt}}$, then \eqref{eq:tract_def} must not hold for all $\vp \in [\vzero, \vp^*)$.
-By the sufficiency argument, this implies that \eqref{eq:tractiff4} cannot hold for all $\vp \in [\vzero,\vp^*/2)$.
-This is the second condition for membership in $\widetilde{\cp}_{\textup{opt}}$.
+Next we show that if $\vp^* \in \widetilde{\cp}_{\textup{trct}}$, then $\vp^* \in \cp_{\textup{trct}}$.
+If $\vp^* \in \widetilde{\cp}_{\textup{strct}}$, then \eqref{eq:tractiff4}  holds for all $\vp \in (\vp^*,\vinfty)$.
+By the argument to prove the sufficient condition above, it follows that \eqref{eq:strong_tract_def} must also hold for all $\vp \in (\vp^*,\vinfty)$.
+Thus, $\vp^* \in \cp_{\textup{trct}}$.
 
-Thus,  $\cp_{\textup{opt}} \subseteq \widetilde{\cp}_{\textup{opt}}$.  This concludes the proof of Theorem \ref{thm_main_tract2}.
-
+Thus,  $\cp_{\textup{opt}}= \widetilde{\cp}_{\textup{opt}}$.  This concludes the proof of Theorem \ref{thm_main_tract2}.
 \end{proof}

### 2023-05-10 GeneralizedTractability_230501.tex
Updates from Overleaf

@@
    \implies   \frac{1}{T(\lambda_{n+1, d}^{-1},d',\vp)} \le
-   \frac{1}{n-N+1} \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d',\vp) } \le \frac{1}{T(\varepsilon^{-1},d',\vp)} \\ \forall d', n, N \in \naturals, \ N \le n.
+   \frac{1}{n-N+1} \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d',\vp) } \le \frac{1}{T(\varepsilon^{-1},d',\vp)} \\ \forall d', n, N \in \naturals.
 \end{multline}
+We note that the left side of the implication implies $n \ge N$ automatically since $n$ is an integer  $n - N +1$ is assumed to be positive.
 
@@
 	\nonumber
-	& \le  \min \biggl\{n \in \natzero : n \ge N - 1 + T(\varepsilon^{-1},d',\vp) \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} \biggr\} \;  \forall  d', N \in \naturals, \quad \text{by \eqref{eq:implicate_a}}.
-	\intertext{Note that in this last expression, $n \ge N$ is enforced since $n$ is an integer strictly greater than  $N-1$ by definition.  This then implies that}
-	\comp(\varepsilon, d) 
+	& \le  \min \biggl\{n \in \natzero : n \ge N - 1 + T(\varepsilon^{-1},d',\vp) \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} \biggr\} \;  \forall  d', N \in \naturals, \quad \text{by \eqref{eq:implicate_a}} \\
 	& \le  T(\varepsilon^{-1},d',\vp) \Biggl [\frac{N}{T(\varepsilon^{-1},d',\vp)}  +  \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} \Biggr] \quad \forall  d', N \in \naturals.
@@
 
-Comparing the equivalent conditions for strong tractability in \eqref{eq:strong_tractiff3} and tractability in \eref{eq:tractiff4}, they are seen to be nearly the same.
+Comparing the equivalent conditions for strong tractability in \eqref{eq:strong_tractiff3} and tractability in \eqref{eq:tractiff4}, they are seen to be nearly the same.
 The difference lies in the lower summation index, which is allowed to depend on $d$ for tractability, and the second argument of $T$ in the sum, which is $1$ for strong tractability, and $d$ in general.
@@
 \]
-\fred{May we pull the exponent $p$ inside the $\max$?} Then Theorem \ref{thm_main_strong_tract2} yields the  equivalent condition for strong algebraic polynomial tractability:
+Then Theorem \ref{thm_main_strong_tract2} yields the  equivalent condition for strong algebraic polynomial tractability:
 \[
@@
 \end{example}
-\kachi{
-\begin{example}[Separable tractability]
-Let the tractability function, $T$,
+
+\kachi{In the following we introduce two specific cases of tractability which depend on the form of the function $T$.
+\begin{example}[(Strong) Separable tractability]
+Let the tractability function $T$,
 be defined by
@@
 with non-decreasing functions $\phi : (0,\infty) \times (0,\infty) \to (0,\infty)$ and $\psi : \naturals  \times (0,\infty) \to (0,\infty)$.
-In addition, satisfying the following conditions as in (\ref{eq:ptauassume})
+In addition, we assume the following conditions as in (\ref{eq:ptauassume})
+%\begin{align*}
+ %(\phi(\varepsilon^{-1},p))^{\tau_1} &\le K_{p,\tau_1} \phi (\varepsilon^{-1},\tau_1 p)\\ (\psi(d,q))^{\tau_2} &\le K_{q,\tau_2} \psi (d,\tau_2 q)\\\end{align*}
  \begin{align*}
- (\phi(\varepsilon^{-1},p))^{\tau_1} &\le K_{p,\tau_1} \phi (\varepsilon^{-1},\tau_1 p)\\
-  (\psi(d,q))^{\tau_2} &\le K_{q,\tau_2} \psi (d,\tau_2 q)\\
+     [T(\varepsilon^{-1},d,(p,q))]^\tau \leq K_{(p,q),\tau}T(\varepsilon^{-1},d,(\tau p,\tau q))
  \end{align*}
-where $\tau_1, \tau_2>0$. %As the name implies, the roles of $\varepsilon^{-1}$ and $d$ are separated. 
+where $\tau>0$.
+Observe that for this $T$, we have strong tractability if the following condition is satisfied
+\[
+ T(\varepsilon^{-1},1,p)= \phi(\varepsilon^{-1},p)\, \psi(1,0) = \phi(\varepsilon^{-1},p)
+ \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, p \ge 0.
+\]
+Thus, Theorem \ref{thm_main_strong_tract2} yields the following equivalent. We say that a problem is strongly separable tractable iff there exists $p>0$ and an integer $C(p)\ge 0$ such that
+\begin{equation} \label{eq:strong_tractiff}
+     \sup_{d \in \naturals} \sum_{i = L(p,1)}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)} < \infty.
+\end{equation}
+
+%As the name implies, the roles of $\varepsilon^{-1}$ and $d$ are separated. 
 \end{example}
 \begin{example}[Non-separable symmetric tractability]
-    Let the tractability function, $T$, be defined by
+    Let the tractability function $T$, be defined by
 \[
  T(\varepsilon^{-1},d,(p,q))= \exp\{\phi(\varepsilon^{-1},p)\, \psi(d,q)\}
- \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, p,q \ge 0.
-\]  with non-decreasing functions $f_1$, $f_2 : [1,\infty)\rightarrow[1,\infty)$.
+ \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, p\ge 0.
+\]  with non-decreasing functions $\phi : (0,\infty) \times (0,\infty) \to (0,\infty)$ and $\psi : \naturals  \times (0,\infty) \to (0,\infty)$.
 \end{example}
@@
 
-\begin{theorem}\label{thm_main_strong_tract2}
+\begin{theorem}\label{thm_main_strong_tract3}
 Let $T$ be a tractability function as specified in \eqref{eq:Tspec} and satisfying \eqref{eq:Tconditions} and \eqref{eq:ptauassume}.

### 2023-05-12 GeneralizedTractability_230501.tex
Updates from Overleaf

@@
 We want to bound the complexity in terms of a simple function of $\varepsilon^{-1}$ and $d$ and identify simple conditions on the singular values that are equivalent to this bound holding.
+\kachi{In this paper, we investigate such a function that we refer to as the generalized tractability function, denoted by $T$.
+A proper definition is given in Section \ref{sec:spt}.
+However, we define a tractability function
+\[
+ T :(0,\infty) \times \mathbb{N} \times [0,\infty)^s \rightarrow (0,\infty).
+\]
+which depends on $\varepsilon^{-1}$, $d$ and the parameter $\vp$ respectively.
+}
 
@@
 \[
- T(\varepsilon^{-1},d,p)= \max\{1,\varepsilon^{-p}\}
- \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, p \ge 0.
-\]
+ T(\varepsilon^{-1},d,\vp)= \max\{1,\varepsilon^{-p}\}
+ \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty),
+\]  where in this case $\vp$ is a scalar.
 Then Theorem \ref{thm_main_strong_tract2} yields the  equivalent condition for strong algebraic polynomial tractability:
 \[
- \sup_{d\in\naturals} \sum_{i=L_p}^\infty (1,\min\{\lambda_{i,d}^p\}) < \infty \text{ for some } p \ge 0, L_p \in \naturals.
+ \sup_{d\in\naturals} \sum_{i=L_p}^\infty (\min\{1,\lambda_{i,d}^p\}) < \infty \text{ for some } p \ge 0, L_p \in \naturals.
 \]
@@
 \[
- T(\varepsilon^{-1},d,(p,q))= (\max\{1,\varepsilon^{-p}\})\, d^q
- \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, p,q \ge 0.
-\]
+ T(\varepsilon^{-1},d,\vp)= \max\{1,\varepsilon^{-p}\}\, d^q
+ \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty)^2, 
+\] where in this case $\vp = (p,q)$.
 Then Theorem \ref{thm_main_tract2} yields the  equivalent condition for algebraic polynomial tractability:
 \[
- \sup_{d\in\naturals} \sum_{i=L_{p,q} d^{q}}^\infty (\min\{1,\lambda_{i,d}^p\}) d^{-q} < \infty \text{ for some } p,q \ge 0, L_{p,q} \in \naturals.
+ \sup_{d\in\naturals} \sum_{i=L_{(p,q)} d^{q}}^\infty (\min\{1,\lambda_{i,d}^p\}) d^{-q} < \infty \text{ for some } p,q \ge 0, L_{p,q} \in \naturals.
 \]
@@
 \[
- T(\varepsilon^{-1},d,p)= \left[\max\{1,\log(1+\varepsilon^{-1}\})\right]^p.
-\]
-Then Theorem \ref{thm_main_tract2} yields the iff-condition
-\[
- \sup_{d\in\naturals} \sum_{i=L_{\vp} d^{q_1}}^\infty (\min\{\lambda_{i,d},1\})^p  < \infty.
-\]
+ T(\varepsilon^{-1},d,\vp)= \left[\max\{1,\log(1+\varepsilon^{-1})\}\right]^p, \quad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty),
+\]
+where $\vp$ is a scalar. Then Theorem \ref{thm_main_strong_tract2} yields the equivalent condition for strong exponential polynomial tractability \[
+ \sup_{d\in\naturals} \sum_{i=L_{p} }^\infty (\min\{1,\log(1+\lambda_{i,d}\})^{p}  < \infty.
+\] In this case the optimal $p$ is the infimum of all $p$ for which the above condition holds.
 \end{example}
 \begin{example}[Exponential polynomial tractability]
-
 Let the tractability function, $T$,
@@
 \[
- T(\varepsilon^{-1},d,(p,q))=\left[\max\{1,\log(1+\varepsilon^{-1}\})\right]^p\, d^q.
-\]
-Then Theorem \ref{thm_main_tract2} yields the iff-condition
-\[
- \sup_{d\in\naturals} \sum_{i=L_{\vp} d^{q_1}}^\infty (\min\{\lambda_{i,d},1\})^p d^{-q} < \infty.
+ T(\varepsilon^{-1},d,\vp)=\left[\max\{1,\log(1+\varepsilon^{-1}\})\right]^p\, d^q, \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty)^2, 
+\] where $\vp = (p,q)$. Then Theorem \ref{thm_main_tract2} yields  the equivalent condition for exponential polynomial tractability
+\[
+ \sup_{d\in\naturals} \sum_{i=L_{(p,q)} d^{q}}^\infty [\min\{1,\log(1+\lambda_{i,d}\})]^p d^{-q} < \infty  \text{ for some } p,q \ge 0, L_{(p,q)} \in \naturals.
 \]
 \end{example}
-\bigskip
-
-\begin{example}[Algebraic quasi-polynomial tractability]
-\begin{definition}
-    As defined in \cite{GW11}, we say that a problem is \emph{ quasi-polynomially tractable (QPT)} if there exist two constants $C$, $t > 0$, such that
+
+\begin{example}[Algebraic quasi-polynomial tractability] Here we consider another common notions of tractability.
+
+As defined in \cite{GW11}, we say that a problem is \emph{quasi-polynomially tractable (QPT)} if there exist two constants $C$, $t > 0$, such that
 \begin{equation}\label{expqpt}
-    n(\varepsilon,d) \leq C\exp\{t(1+\log(\varepsilon^{-1}))(1+\log(d))\}
+    \comp(\varepsilon,d) \leq C\exp\{t(1+\log(\varepsilon^{-1}))(1+\log(d))\}
 \end{equation}
 for all $\varepsilon \in (0,1]$ and $d\in\mathbb{N}$.\\
-\end{definition}
-Let the tractability function, $T$,
+
+\noindent Let the tractability function, $T$,
 be defined by
 \[
- T(\varepsilon^{-1},d,p)= \exp\{p(1+\log(\max\{1,\varepsilon^{-1}\})(1+\log d)\}
-\]
-Observe that this is a special case of the $T$-tractability function, where the function is polynomial of exponent $1+\log d$ and $1+\log\max\{\varepsilon^{-1},1\}$.
-
-Then Theorem \ref{sec:tractability} yields the iff-condition as follows
-
-\[
-\sup_{d\in\mathbb{N}}\sum_{i=Lpd^{q_1}} \left(\min\{\lambda_{i,d},1\} \right)^{p(1+\ln d)}d^{-q} < \infty
+ T(\varepsilon^{-1},d,\vp)= \exp\{p(1+\log(\max\{1,\varepsilon^{-1}\}))(1+\log d)\}  \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty),
+\] where in this case $\vp = p$. This can be rewritten as 
+\[
+T(\varepsilon^{-1},d,\vp) = e^p[\max\{1,\varepsilon^{-1}\}]^{p(1+\log d)}d^p
+\]
+Observe that the function $T$ is a function of $\max\{1,\varepsilon^{-1}\}$ and $d$ which are, polynomial or not exponential in powers of $\max\{1,\varepsilon^{-1}\}$ and $d$.
+Hence we can apply Theorem \ref{thm_main_tract2} as follows.
+We have the following equivalent condition for quasi-polynomial tractability in the algebraic case
+\[
+\sup_{d\in\mathbb{N}}\sum_{i=Lp\,e^pd^{p}} \left(\min\{1,\lambda_{i,d}\} \right)^{p(1+\ln d)}e^{-p}d^{-p} < \infty \qquad \text{for some} p \geq 0, L_p \in \naturals.
+\]
+\end{example}
+\begin{example}[Exponential quasi-polynomial tractability]
+
+\noindent Suppose that the tractability function, $T$, is defined by
+\[
+ T(\varepsilon^{-1},d,\vp)= \exp\{p(1+\log(\max\{1,\log(1+\varepsilon^{-1})\}))(1+\log d)\}  \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty),
+\] where in this case $\vp = p$. This can be rewritten as 
+\[
+T(\varepsilon^{-1},d,\vp) = e^p[\max\{1,\log(1+\varepsilon^{-1}\})]^{p(1+\log d)}d^p
+\]
+Observe that the function $T$ is a function of $\max\{1,\log(1+\varepsilon^{-1})\}$ and $d$.
+Hence we can apply Theorem \ref{thm_main_tract2} as follows.
+We have the following equivalent condition for quasi-polynomial tractability in the exponential case
+\[
+\sup_{d\in\mathbb{N}}\sum_{i=Lp\,e^pd^{p}} \left(\min\{1,\log(1+\lambda_{i,d})\} \right)^{p(1+\ln d)}e^{-p}d^{-p} < \infty
 \]
@@
 \begin{example}[(Strong) Separable tractability]
-Let the tractability function $T$,
-be defined by
-\[
- T(\varepsilon^{-1},d,(p,q))= \phi(\varepsilon^{-1},p)\, \psi(d,q)
- \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, p,q \ge 0.
-\]
-with non-decreasing functions $\phi : (0,\infty) \times (0,\infty) \to (0,\infty)$ and $\psi : \naturals  \times (0,\infty) \to (0,\infty)$.
-In addition, we assume the following conditions as in (\ref{eq:ptauassume})
+Suppose that
+\[
+ T(\varepsilon^{-1},d,\vp)= \phi(\varepsilon^{-1},p)\, \psi(d,q)
+ \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty).
+\]
+with non-decreasing functions $\phi : (0,\infty) \times (0,\infty) \to (0,\infty)$ and $\psi : \naturals  \times (0,\infty) \to (0,\infty)$ and where $\vp = (p,q)$.
+
+%In addition, we assume the following conditions as in (\ref{eq:ptauassume}).
+That is, there exists a $K_{(p,q),\tau}$ depending on $p,q$ and $\tau$, but independent of $\varepsilon$ and $d$, such that
+%\begin{equation} \label{eq:tractiff}    \sup_{d \in \naturals} \frac{1}{\psi(d,q)} \sum_{i = C(p,q)}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p))} < \infty.\end{equation}
+
  %\begin{align*}
- %(\phi(\varepsilon^{-1},p))^{\tau_1} &\le K_{p,\tau_1} \phi (\varepsilon^{-1},\tau_1 p)\\ (\psi(d,q))^{\tau_2} &\le K_{q,\tau_2} \psi (d,\tau_2 q)\\\end{align*}
- \begin{align*}
-     [T(\varepsilon^{-1},d,(p,q))]^\tau \leq K_{(p,q),\tau}T(\varepsilon^{-1},d,(\tau p,\tau q))
- \end{align*}
-where $\tau>0$.
-Observe that for this $T$, we have strong tractability if the following condition is satisfied
-\[
- T(\varepsilon^{-1},1,p)= \phi(\varepsilon^{-1},p)\, \psi(1,0) = \phi(\varepsilon^{-1},p)
- \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, p \ge 0.
-\]
-Thus, Theorem \ref{thm_main_strong_tract2} yields the following equivalent. We say that a problem is strongly separable tractable iff there exists $p>0$ and an integer $C(p)\ge 0$ such that
-\begin{equation} \label{eq:strong_tractiff}
-     \sup_{d \in \naturals} \sum_{i = L(p,1)}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)} < \infty.
-\end{equation}
-
+  %   [T(\varepsilon^{-1},d,\vp]^\tau \leq K_{\vp,\tau}T(\varepsilon^{-1},d,\tau\vp) \quad \forall \varepsilon \in (0,\infty),\, d\in \mathbb{N},\, \vp\in[0,\infty)^2, \tau >0\end{align*}
+
+Observe that for this tractability function $T$, we have strong tractability if the following condition is satisfied
+\[
+ T(\varepsilon^{-1},1,\vp)= \phi(\varepsilon^{-1},p)\, \psi(1,0) = \phi(\varepsilon^{-1},p)
+ \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, p \ge 0,
+\] where in this case $\vp$ is a scalar.
+Furthermore, we assume the following technical conditions.
+There exists a $K_{(p,q),\tau}$ depending on $p,q$ and $\tau$, but independent of $\varepsilon$ and $d$, such that
+\begin{align*}
+     [\phi(\varepsilon^{-1},p)]^{\tau} &\le K_{(p,1),\tau} \phi (\varepsilon^{-1},\tau p)\\
+      [\psi(d,q)]^{\tau} &\le K_{(1,q),\tau} \psi (d,\tau q) \qquad \forall \, \varepsilon \in (0,\infty),\, d\in \naturals,\, p,q\geq 0,\, \tau >0.
+\end{align*}
+Thus, Theorem \ref{thm_main_strong_tract2} yields the following equivalent condition for strongly separable tractability
+\begin{equation*} \label{eq:strong_tractiff}
+     \sup_{d \in \naturals} \sum_{i = L_p}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)} < \infty.
+\end{equation*}
+Theorem \ref{thm_main_tract2} yields the following equivalent condition for 
+separable tractability
+\[
+ \sup_{d \in \naturals} \frac{1}{\psi(d,q)} \sum_{i = L_{(p,q)\psi(d,q)}}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)} < \infty.
+\]
 %As the name implies, the roles of $\varepsilon^{-1}$ and $d$ are separated. 
@@
 \]  with non-decreasing functions $\phi : (0,\infty) \times (0,\infty) \to (0,\infty)$ and $\psi : \naturals  \times (0,\infty) \to (0,\infty)$.
+Furthermore, we assume the following technical conditions.
+There exists a $K_{(p,q),\tau}$ depending on $p,q$ and $\tau$, but independent of $\varepsilon$ and $d$, such that
+\begin{align*}
+     [\phi(\varepsilon^{-1},p)]^{\tau} &\le K_{(p,1),\tau} \phi (\varepsilon^{-1},\tau p)\\
+      [\psi(d,q)]^{\tau} &\le K_{(1,q),\tau} \psi (d,\tau q) \qquad \forall \, \varepsilon \in (0,\infty),\, d\in \naturals,\, p,q\geq 0,\, \tau >0.
+\end{align*}
 \end{example}
@@
 
-\section{Try Restricted Region}
-
-Suppose that the domain of interesting $(\varepsilon^{-1},d)$ is given by 
+\section{Tractability on a Restricted Domain}
+
+Suppose that the domain of interesting $(\varepsilon^{-1},d)$ is not all of $(0,\infty \times \naturals$ but given by 
 \begin{equation}
@@
 \end{equation}
-where $E$ is a non-increasing function.  Furthermore, for all $d \in \naturals$, let $N(d) = \min \{n : \lambda_{n+1,d} \le E(d) \}$.  This means that 
-\[
-\lambda_{1,d}^{-1} \le \cdots \le \lambda_{N(d),d}^{-1} < E(d) \le \lambda_{N(d)+1,d}^{-1}, \qquad (\lambda_{1,d}^{-1},d), \ldots, (\lambda_{N(d),d}^{-1},d) \in \Omega.
-\]
-
-\subsection{Strong tractability}
-
-We first consider the simpler case when the complexity is essentially independent of the dimension, $d$.
-The proof also introduces the line of argument used for the case where there is $d$-dependence.
-
-\begin{theorem}\label{thm_main_strong_tract3}
+where $E$ is a non-increasing function.  A problem is
+$T$-tractable with parameter $\vp$ \emph{on the restricted domain $\Omega$} iff the complexity is independent of the dimension of the problem, that is, there exists a positive constant $C_{\vp}$, again independent of $\varepsilon$ and $d$, such that
+\begin{equation} \label{eq:rest_strong_tract_def}
+	\comp(\varepsilon,d) \le C_{\vp}\, T(\varepsilon^{-1},1,\vp) \qquad \forall(\varepsilon^{-1},d) \in \Omega.
+\end{equation}
+Define $M(d) = \max\{n : \lambda_{n+1,d} \ge E(d)\}$, i.e., 
+\[
+\lambda_{1,d}\ge  \cdots \ge \lambda_{M(d)+1,d} \ge E(d) > \lambda_{M(d)+2,d}, \qquad
+(\lambda_{1,d}^{-1},d), \cdots, (\lambda^{-1}_{M(d)+1,d},d) \} \in \Omega.
+\]
+
+\begin{theorem}\label{thm_main_rest_tract2}
 Let $T$ be a tractability function as specified in \eqref{eq:Tspec} and satisfying \eqref{eq:Tconditions} and \eqref{eq:ptauassume}.
-A problem is strongly $T$-tractable iff there exists $\vp \in [\vzero, \boldsymbol{\infty})$ and an integer $L_{\vp} > 0$ such that
-\begin{equation} \label{eq:strong_tractiff3}
-     S_{\vp}:=\sup_{d \in \naturals} \sum_{i = L_{\vp}}^{N(d)} \frac{1}{T(\lambda_{i,d}^{-1},1,\vp)} < \infty.
-\end{equation}
-If \eqref{eq:strong_tractiff3} holds for some $\vp$, let  $\widetilde{\cp}_{\textup{strct}} : = \{\vp^* : \eqref{eq:strong_tractiff3} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty})\}$.
-Then $\cp_{\textup{strct}} = \widetilde{\cp}_{\textup{strct}}$, and the set of optimal strong tractability parameters is
-\[
-	\cp_{\textup{sopt}} =
-	\{\vp^* \in \widetilde{\cp}_{\textup{strct}} :  \vp^* \notin [\widetilde{\vp},\boldsymbol{\infty}) \ \forall \widetilde{\vp}\in  \widetilde{\cp}_{\textup{strct}} \setminus \{\vp^*\} \}.
+A problem is $T$-tractable on $\Omega$ iff there exists $\vp\ge \vzero$ and a positive integer $L_{\vp}$ such that
+\begin{equation} \label{eq:rest_tractiff4}
+     S_{\vp}:=\sup_{d \in \naturals}
+     \sum_{i = \lceil L_{\vp}\, T(0,d,\vp) \rceil}^{M(d)} \frac{1}{T(\lambda^{-1}_{i,d},d,\vp)}< \infty.
+\end{equation}
+If \eqref{eq:rest_tractiff4} holds for some $\vp$, let $\widetilde{\cp}_{\textup{trct}} : = \{\vp^* : \eqref{eq:tractiff4} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty}) \}$.
+Then $\cp_{\textup{trct}} = \widetilde{\cp}_{\textup{trct}}$, and the set of optimal  tractability parameters is
+\[
+\cp_{\textup{opt}} =
+\{\vp^* \in \widetilde{\cp}_{\textup{trct}} :  \vp^* \notin [\widetilde{\vp},\boldsymbol{\infty}) \ \forall \widetilde{\vp}\in  \widetilde{\cp}_{\textup{trct}} \setminus \{\vp^*\} \}.
 \]
@@
 \begin{proof}
-\textbf{Sufficient condition:}\newline
-We make the first part of the argument in some generality so that it can be reused in the proof of Theorem \ref{thm_main_tract2} for tractability.
-
-Since the $\lambda_{i,d}$ are non-increasing in $i$, it follows that the $T(\lambda_{i,d}^{-1},d',\vp)$ are non-decreasing in $i$ for any $d'\in\{1, \ldots, d\}$.
-In particular, for all $n\in \{1, \ldots, N(d')\}$, we have
-\begin{align*}
-    \lambda_{n+1,d} \le \lambda_{n,d} \le \cdots \le \lambda_{1,d}
-    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d',\vp)} \le \frac{1}{T(\lambda_{n, d}^{-1},d',\vp)} \le \cdots \le \frac{1}{T(\lambda_{1, d}^{-1},d',\vp)} \\
-    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d',\vp) }
-    \le \frac 1n \sum_{i=1}^n  \frac{1}{T(\lambda_{i, d}^{-1},d',\vp) }
-    \le \frac 1n \sum_{i=1}^{N(d')}  \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)}.
+    \textbf{Sufficient Condition:}\\
+We adapt the argument in the proof of the sufficient condition for Theorems \ref{thm_main_strong_tract2} and \ref{thm_main_tract2}.
+Suppose that \eqref{eq:rest_tractiff4} holds for some $\vp \ge 0$.
+Fix any $(\varepsilon^{-1},d) \in \Omega$.
+Then
+
+Since the $\lambda_{i,d}$ are non-increasing in $i$, it follows that the $T(\lambda_{i,d}^{-1},d,\vp)$ are non-decreasing in $i$ for $i \in \{1, \ldots, M(d)+1\}$.
+In particular, for  any $n \in \{N, \ldots, M(d)\}$
+\begin{align*}
+    \lambda_{n+1,d} \le \lambda_{n,d} \le \cdots \le \lambda_{N,d}
+    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d,\vp)} \le \frac{1}{T(\lambda_{n, d}^{-1},d,\vp)} \le \cdots \le \frac{1}{T(\lambda_{N, d}^{-1},d,\vp)} \\
+     \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d,\vp) }
+    \le &\frac{1}{n-N+1} \sum_{i=N}^n  \frac{1}{T(\lambda_{i, d}^{-1},d,\vp) }
+    \le \frac{1}{n-N+1} \sum_{i=N}^{M(d)}  \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}.
 \end{align*}
 Thus, we can conclude from the previous line that
-\begin{multline} \label{eq:implicate_a}
-    n \ge T(\varepsilon^{-1},d',\vp) \sum_{i=1}^{N(d')} \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} \\
-   \implies   \frac{1}{T(\lambda_{n+1, d}^{-1},d',\vp)} \le
-   \frac 1n \sum_{i=1}^{N(d')} \frac{1}{T(\lambda_{i, d}^{-1},d',\vp) } \le \frac{1}{T(\varepsilon^{-1},d',\vp)} \qquad \forall \varepsilon > 0, \ d,d' \in \naturals.
+\begin{multline} \label{eq:implicate_a_rest}
+    n - N +1 \ge T(\varepsilon^{-1},d,\vp) \sum_{i=N}^{M(d)} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)} \\
+   \implies   \frac{1}{T(\lambda_{n+1, d}^{-1},d,\vp)} \le
+   \frac{1}{n-N+1} \sum_{i=N}^{M(d)} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp) } \le \frac{1}{T(\varepsilon^{-1},d,\vp)} \\ \forall d, n, N \in \naturals.
 \end{multline}
+We note that the left side of the implication implies $n \ge N$ automatically since $n$ is an integer  $n - N +1$ is assumed to be positive.
 
@@
 	\nonumber
-    & = \min \biggl\{n \in \natzero : \frac{1}{T(\lambda_{n+1,d}^{-1},d',\vp)}\le \frac{1}{T(\varepsilon^{-1},d',\vp) }\biggr\} \qquad \forall d' \in \naturals\\
+	& = \min \biggl\{n \in \natzero : \frac{1}{T(\lambda_{n+1,d}^{-1},d,\vp)}\le \frac{1}{T(\varepsilon^{-1},d,\vp) }\biggr\}\\
 	\nonumber
-    & \le  \min \biggl\{n \in \natzero : n \ge T(\varepsilon^{-1},d',\vp) \sum_{i=1}^{N(d')} \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} \biggr\} \quad \forall d' \in \naturals \qquad \text{by \eqref{eq:implicate_a}} \\
-    & \le  T(\varepsilon^{-1},d',\vp) \sum_{i=1}^{N(d')} \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} + 1 \quad \forall d' \in \naturals. \label{eq:compUP}
+	& \le  \min \biggl\{n \in \natzero : n \ge N - 1 + T(\varepsilon^{-1},d,\vp) \sum_{i=N}^{M(d)} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)} \biggr\} \;  \forall N \in \naturals, \quad \text{by \eqref{eq:implicate_a_rest}} \\
+	& \le  T(\varepsilon^{-1},d,\vp) \Biggl [\frac{N}{T(\varepsilon^{-1},d,\vp)}  +  \sum_{i=N}^{M(d)} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)} \Biggr] \quad \forall N \in \naturals. \label{eq:compUP_rest}
 \end{align}
 
-Now we take this upper bound further, specializing to the case of $d'=1$:
+it follows from \eqref{eq:compUP} with $N = \lceil L_{\vp}\, T(0,d,\vp)\rceil$ that 
 \begin{align*}
        \comp(\varepsilon,d)
-       & \le T(\varepsilon^{-1},1, \vp) \Biggl [ \sum_{i=1}^{L_{\vp}-1} \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}
-       + \underbrace{\sum_{i=L_{\vp}}^\infty \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}}_{\le S_{\vp} <\infty\ \text{by \eqref{eq:strong_tractiff3}} }
-       + \frac{1}{T(\varepsilon^{-1},1, \vp)} \Biggr] \\
-       & \le T(\varepsilon^{-1},1,\vp) \underbrace{\left[\frac{(L_{\vp}-1)}{T(\lambda_{\max}^{-1},1,\vp)} + S_{\vp} + \frac{1}{T(0,1, \vp)}\right]}_{=:C_{\vp}}\\
-       & =  C_{\vp}T(\varepsilon^{-1},1,\vp).
-%       & \le \underbrace{2 C_{1,\vp}}_{\text{since } T(\varepsilon^{-1},1,\vp) \ge 1} T(\varepsilon^{-1},1,\vp)
-%       = \underbrace{C_{\vp}}_{:=2 C_{1,\vp}}T(\varepsilon^{-1},1,\vp).
-\end{align*}
-This means that we have strong $T$-tractability via \eqref{eq:strong_tract_def}, and verifies the sufficiency of \eqref{eq:strong_tractiff3}.
+       & \le T(\varepsilon^{-1},d,\vp) \Biggl [ 
+       \frac{\lceil L_{\vp}\, T(0,d,\vp)\rceil}{T(\varepsilon^{-1},d,\vp)}  + 
+       \underbrace{\sum_{i=\lceil L_{\vp}\, T(0,d,\vp)\rceil}^{M(d)} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}}_{\le S_{\vp} \text{ by \eqref{eq:rest_tractiff4}}}
+       \Biggr ] 
+        \quad \forall \varepsilon > 0, \ d  \in \naturals\\
+       & \le T(\varepsilon^{-1},d,\vp)\left[\frac{L_{\vp} T(0,d,\vp)+1}{T(\varepsilon^{-1},d, \vp)} +  S_{\vp} \right]
+        \qquad \forall \varepsilon > 0, \ d  \in \naturals\\
+       & \le T(\varepsilon^{-1},d,\vp)\left[\frac{L_{\vp} T(0,d,\vp)}{T(\varepsilon^{-1},d, \vp)}
+       + \frac{1}{T(0,1, \vp)} + S_{\vp}\right]
+       \qquad \text{by \eqref{eq:Tnondecreasing}}   \\
+       & \le T(\varepsilon^{-1},d,\vp) 
+       \underbrace{\left [  L_{\vp} + \frac{1}{T(0,1, \vp)} + S_{\vp} \right]}_{=:C_{\vp}}
+       \qquad \text{by \eqref{eq:Tnondecreasing}}  
+\end{align*}
+It follows that we have $T$-tractability, which shows sufficiency of \eqref{eq:rest_tractiff4}.
 
 \bigskip
-\noindent \textbf{Necessary condition:} \\
-Suppose that we have strong
-$T$-tractability as defined in \eqref{eq:strong_tract_def}. That is, for some $\vp \ge \vzero$ there exists a positive constant $C_{\vp}$ such that
-\[
-\comp(\varepsilon,d)\le C_{\vp}\, T(\varepsilon^{-1},1,\vp)
-\qquad \forall \varepsilon > 0, \ d \in \mathbb{N}.
+
+\noindent \textbf{Necessary condition:}\\
+Suppose that we have
+$T$-tractability. That is, for some $\vp \ge \vzero$, there exists a positive constant $C_{\vp}$ such that
+\[
+\comp(\varepsilon,d)\le C_{\vp}\, T(\varepsilon^{-1},d,\vp) \qquad \forall (\varepsilon^{-1}, d) \in \Omega.
 \]
 Since the sequence of eigenvalues $\lambda_{1,d}, \lambda_{2,d}, \ldots $ is non-increasing, we have
-\begin{equation}\label{eq:lambda_K_strong3}
-\lambda_{\lfloor C_{\vp}\, T(\varepsilon^{-1},1,\vp)\rfloor +1,d}\le \varepsilon.
-\end{equation}
-
-Define
-\[
-i(\varepsilon,\vp):= \lfloor C_{\vp}\, T(\varepsilon^{-1},1,\vp)\rfloor +1, \quad
-i(\infty,\vp) = \lim_{\varepsilon \to \infty}  i(\varepsilon,\vp) \ge 1 .
-\]
-Thus, it follows by \eqref{eq:lambda_K_strong3} that $\lambda_{i(\varepsilon,\vp),d} \le \varepsilon$.
+\begin{equation}\label{eq:lambda_K4}
+	\lambda_{\lfloor C_{\vp}\, T(\varepsilon^{-1},d,\vp)\rfloor +1,d}\le \varepsilon \qquad 
+ \forall (\varepsilon^{-1}, d) \in \Omega.
+\end{equation}
+Define the integers \fred{Only got here because we have to be careful with the domain of stuff}
+\[
+i (\varepsilon,d,\vp):= \lfloor C_{\vp}\, T(\varepsilon^{-1},d,\vp)\rfloor +1, \qquad
+i (\infty,d,\vp) := \lfloor C_{\vp}\, T(0,d,\vp)\rfloor +1 \ge 1.
+\]
+Thus, it follows by \eqref{eq:lambda_K4} that $\lambda_{i(\varepsilon,d,\vp),d} \le \varepsilon$.
 Note furthermore that we always have
 \[
-i(\varepsilon,\vp)\le C_{\vp}\, T(\varepsilon^{-1},1,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,\vp),d}^{-1},1,\vp)+1, \qquad \forall \varepsilon > 0,
+i(\varepsilon,d,\vp)\le C_{\vp}\, T(\varepsilon^{-1},d,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,d,\vp),d}^{-1},d,\vp)+1, \qquad \forall \varepsilon > 0, \ d \in \naturals,
 \]
 since
-$T(\cdot,1, \vp)$ is non-decreasing.
-
-For $\varepsilon$ taking on all positive values, $i(\varepsilon,\vp)$ takes on all values greater than or equal to $i(\infty,\vp)$, so
-\[
-i\le C_{\vp} T(\lambda_{i,d}^{-1},1,\vp)+1, \qquad \forall i \ge i(\infty,\vp).
-\]
-This implies via our technical assumption \eqref{eq:ptauassume} that
+$T(\cdot,d,\vp)$ is non-decreasing.
+
+For $\varepsilon$ taking on all positive values, $i(\varepsilon,d,\vp)$ takes on all values greater than or equal to $i(\infty,d,\vp)$, so
+\[
+i\le C_{\vp}\, T(\varepsilon^{-1},d,\vp)+1 \le C_{\vp} T(\lambda_{i,d}^{-1},d,\vp)+1, \qquad \forall i \ge i(\infty,d,\vp),  \ d \in \naturals.
+\]
+This implies via our technical assumption \eqref{eq:ptauassume} that for any $\tau > 1$,
 \begin{gather*}
- K_{\vp,\tau}\,T (\lambda_{i,d}^{-1},1,\tau \vp) \ge
- [T(\lambda_{i,d}^{-1},1, \vp)]^\tau
+	K_{\vp,\tau}\,T (\lambda_{i,d}^{-1},d,\tau \vp) \ge
+	[T(\lambda_{i,d}^{-1},d, \vp)]^\tau
 	\ge
-  \left[\frac{(i-1)}{C_{\vp}}\right]^\tau \qquad \forall i \ge i(\infty,\vp) \\
- \frac{1}{T (\lambda_{i,d}^{-1},1,\tau \vp)} \le
-\frac{K_{\vp,\tau}\, C_{\vp}^\tau}{(i-1)^\tau}\qquad \forall i \ge \max\{i(\infty,\vp),2\} .
+	\left[\frac{(i-1)}{C_{\vp}}\right]^\tau \qquad \forall i \ge i(\infty,d,\vp),  \ d \in \naturals, \\
+	 \frac{1}{T (\lambda_{i,d}^{-1},d,\tau \vp)} \le
+	\frac{K_{\vp,\tau}\, C_{\vp}^\tau}{(i-1)^\tau}\qquad \forall i \ge \max\{i(\infty,\vp),2\},  \ d \in \naturals.
 \end{gather*}
-Summing both sides of this last inequality over $i$ from $i(\infty,\vp) +1 \ge 2$ to $\vinfty$ yields
+
+Let $\vp' = \tau \vp$.
+Note that $i(\infty,d,\cdot)$ is non-decreasing.
+Summing both sides of the latter inequality over $i$ from $i(\infty,d,\vp') + 1 \ge i(\infty,d, \vp) + 1 \ge 2$ to $\infty$ it follows that
 \begin{equation*}
-\sup_{d\in\naturals} \sum_{i=i(\infty,\vp) +1 }^\infty \frac{1}{T (\lambda_{i,d}^{-1},1, \tau \vp)}
+	\sup_{d\in\naturals} \, \, \sum_{i=i (\infty,d,\vp')+1}^\infty \frac{1}{T (\lambda_{i,d}^{-1},d,\vp')}
 	 \le  K_{\vp,\tau}\, C_{\vp}^\tau
@@
 where $\zeta$ denotes the Riemann zeta function.
-This yields \eqref{eq:strong_tractiff3} with $\vp$ replaced by $\vp' = \tau \vp$ and $L_{\vp'} = i(\infty,\vp) +1$, and so we see the necessity of $\eqref{eq:strong_tractiff3}$.
+
+Note now that, for any $d\in\naturals$,
+\begin{align*}
+ i(\infty,d,\vp') +1  & = \lfloor C_{\vp'}\, T(0,d,\vp')\rfloor +2 \le  \left[C_{\vp'} + \frac{2}{T(0,d,\vp')}   \right]\, T(0,d,\vp')\\
+ & \le  \underbrace{\left[C_{\vp'} + \frac{2}{T(0,1,\vp')}   \right]}_{=:L_{\vp'}}\, T(0,d,\vp')
+ \le \lceil L_{\vp'} T(0,d,\vp')\rceil .
+\end{align*}
+For this choice of $L_{\vp'}$ we have
+\[
+\sup_{d\in\naturals}\,\, \sum_{i=\lceil L(\vp') T(0,d,\vp')\rceil}^\infty \frac{1}{T(\lambda_{i,d}^{-1},d, \vp')}
+\le
+\sup_{d\in\naturals} \, \, \sum_{i=i (\infty,d,\vp')+1}^\infty \frac{1}{T (\lambda_{i,d}^{-1},d,\vp')} <
+\infty.
+\]
+This yields \eqref{eq:tractiff4} with $\vp$ replaced by $\vp'$, so we see the necessity of $\eqref{eq:tractiff4}$.
 
 \bigskip
-\noindent \textbf{Optimality:} \\
-To complete the proof, we must show that $\cp_{\textup{strct}} = \widetilde{\cp}_{\textup{strct}}$.
-Then, the expression for  $\cp_{\textup{sopt}}$ automatically follows from its definition in \eqref{eq:Psoptdef}.
-
-First we show  that if $\vp^* \in \cp_{\textup{strct}}$, then $\vp^* \in \widetilde{\cp}_{\textup{strct}}$.
-If $\vp^* \in \cp_{\textup{strct}}$, then \eqref{eq:strong_tract_def} must hold for all $\vp' \in (\vp^*,\vinfty)$.
+
+\noindent \textbf{Optimality:}
+This proof is similar to the proof for the optimality condition for strong tractability in Theorem \ref{thm_main_strong_tract2}.
+We must show that $\cp_{\textup{trct}} = \widetilde{\cp}_{\textup{trct}}$.
+Then, the expression for  $\cp_{\textup{opt}}$ in this theorem automatically follows from its definition in \eqref{eq:Poptdef}.
+
+First we show  that if $\vp^* \in \cp_{\textup{trct}}$, then $\vp^* \in \widetilde{\cp}_{\textup{trct}}$.
+If $\vp^* \in \cp_{\textup{trct}}$, then \eqref{eq:tract_def} must hold for all $\vp' \in (\vp^*,\vinfty)$.
 For any $\vp' \in (\vp^*,\vinfty)$, we may choose $\vp$ and $\tau$ such that $\vp^* < \vp < \vp' = \tau \vp$.
-Since $\vp > \vp^*$, \eqref{eq:strong_tract_def} also holds for $\vp$, and it follows that \eqref{eq:strong_tractiff3} must hold for $\vp'$ by the proof of necessity above.
-Thus, $\vp^* \in \widetilde{\cp}_{\textup{strct}}$.
-
-Next we show that if $\vp^* \in \widetilde{\cp}_{\textup{strct}}$, then $\vp^* \in \cp_{\textup{strct}}$.
-If $\vp^* \in \widetilde{\cp}_{\textup{strct}}$, then \eqref{eq:strong_tractiff3}  holds for all $\vp \in (\vp^*,\vinfty)$.
+Since $\vp > \vp^*$, \eqref{eq:tract_def} also holds for $\vp$, and it follows that \eqref{eq:tractiff4} must hold for $\vp'$ by the proof of necessity above.
+Thus, $\vp^* \in \widetilde{\cp}_{\textup{trct}}$.
+
+Next we show that if $\vp^* \in \widetilde{\cp}_{\textup{trct}}$, then $\vp^* \in \cp_{\textup{trct}}$.
+If $\vp^* \in \widetilde{\cp}_{\textup{strct}}$, then \eqref{eq:tractiff4}  holds for all $\vp \in (\vp^*,\vinfty)$.
 By the argument to prove the sufficient condition above, it follows that \eqref{eq:strong_tract_def} must also hold for all $\vp \in (\vp^*,\vinfty)$.
-Thus, $\vp^* \in \cp_{\textup{strct}}$.
-
-\bigskip
-
-\noindent This concludes the proof of  Theorem \ref{thm_main_strong_tract2}.
-
+Thus, $\vp^* \in \cp_{\textup{trct}}$.
+
+Thus,  $\cp_{\textup{opt}}= \widetilde{\cp}_{\textup{opt}}$.  This concludes the proof of Theorem \ref{thm_main_tract2}.
 \end{proof}
+
+Furthermore, for all $d \in \naturals$, let $M(d) = \min \{n : \lambda_{n+1,d} \le E(d) \}$.  This means that 
+\[
+\lambda_{1,d}^{-1} \le \cdots \le \lambda_{M(d),d}^{-1} < E^{-1}(d) \le \lambda_{M(d)+1,d}^{-1}, \qquad (\lambda_{1,d}^{-1},d), \ldots, (\lambda_{M(d),d}^{-1},d) \in \Omega.
+\]
 

### 2023-05-13 GeneralizedTractability_230501.tex
Updates from Overleaf

@@
         \text{quasi-polynomial exponential} & 
-        \exp\{p(1+\log(1+\log(\max(1,\varepsilon^{-1})))(1+\log(d))\} &
+        \exp\{p(1+\log(\max\{1,\log(1+\varepsilon^{-1})\}))(1+\log(d))\} &
         \exp\{p(1+\log(d))\}
@@
 \[
- \sup_{d\in\naturals} \sum_{i=L_{(p,q)} d^{q}}^\infty (\min\{1,\lambda_{i,d}^p\}) d^{-q} < \infty \text{ for some } p,q \ge 0, L_{p,q} \in \naturals.
+ \sup_{d\in\naturals} \sum_{i=L_{(p,q)} d^{q}}^\infty (\min\{1,\lambda_{i,d}^p\}) d^{-q} < \infty \text{ for some } p,q \ge 0, L_{(p,q)} \in \naturals.
 \]
@@
 where $\vp$ is a scalar. Then Theorem \ref{thm_main_strong_tract2} yields the equivalent condition for strong exponential polynomial tractability \[
- \sup_{d\in\naturals} \sum_{i=L_{p} }^\infty (\min\{1,\log(1+\lambda_{i,d}\})^{p}  < \infty.
+ \sup_{d\in\naturals} \sum_{i=L_{p} }^\infty (\min\{1,\log(1+\lambda_{i,d}\})^{p}  < \infty,\quad  \text{ for some } p \ge 0, L_{p} \in \naturals
 \] In this case the optimal $p$ is the infimum of all $p$ for which the above condition holds.
@@
 \[
- T(\varepsilon^{-1},d,\vp)= \exp\{p(1+\log(\max\{1,\varepsilon^{-1}\}))(1+\log d)\}  \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty),
+ T(\varepsilon^{-1},d,\vp)= \exp\{p(1+\log(\max\{1,\varepsilon^{-1}\}))(1+\log (d))\}  \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty),
 \] where in this case $\vp = p$. This can be rewritten as 
@@
 \[
- T(\varepsilon^{-1},d,\vp)= \exp\{p(1+\log(\max\{1,\log(1+\varepsilon^{-1})\}))(1+\log d)\}  \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty),
+ T(\varepsilon^{-1},d,\vp)= \exp\{p(1+\log(\max\{1,\log(1+\varepsilon^{-1})\}))(1+\log (d))\}  \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty),
 \] where in this case $\vp = p$. This can be rewritten as 
@@
  T(\varepsilon^{-1},d,\vp)= \phi(\varepsilon^{-1},p)\, \psi(d,q)
- \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty).
+ \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty)^2.
 \]
@@
 
+We say that a problem is defined as $T$-separable tractable with parameter $\vp$ iff there exists a positive constant $C_{\vp}$ which does not depend on $\varepsilon$ and $d$ such that
+\[
+\comp(\varepsilon,d) \leq  C_{\vp}\,T(\varepsilon^{-1},d,\vp)\qquad \forall \varepsilon >0, \, d\in\naturals,
+\]
+that is
+\[
+\comp(\varepsilon,d) \leq \phi(\varepsilon^{-1},p)\, \psi(d,q) \qquad \forall \varepsilon >0, \, d\in\naturals.
+\]
+A problem is strongly $T$-separable tractable with parameter $\vp$ iff the complexity is independent of $d$, that is, there exists a positive constant $C_{\vp}$ which again does not depend on $\varepsilon$ and $d$ such that
+\[
+\comp(\varepsilon,d) \leq C_{\vp}T(\varepsilon^{-1}, 1,\vp) \qquad \forall \varepsilon >0, \, d\in\naturals,
+\] where $\vp = p$. We have
+\[
+\comp(\varepsilon,d) \leq \phi(\varepsilon^{-1},p)\qquad \forall \varepsilon >0, \, d\in\naturals.
+\]
 %In addition, we assume the following conditions as in (\ref{eq:ptauassume}).
@@
 %\begin{equation} \label{eq:tractiff}    \sup_{d \in \naturals} \frac{1}{\psi(d,q)} \sum_{i = C(p,q)}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p))} < \infty.\end{equation}
-
+Furthermore, we assume that
+\[
+\lim_{\varepsilon\rightarrow0}T(\varepsilon^{-1},d,\vp) = \infty \qquad \forall d\in\naturals, \vp \in[0,\infty)^2.
+\]
+Also since $T(\cdot,d,\vp)$ is non-decreasing, we may define the following limit
+\[
+T(0,d,\vp):= \lim_{\varepsilon \rightarrow \infty}T(\varepsilon^{-1},d,\vp)\geq T(0,1,\textbf{0})>0
+\] 
+%Furthermore, we assume the following technical conditions. There exists a $K_{(p,q),\tau}$ depending on $p,q$ and $\tau$, but independent of $\varepsilon$ and $d$, such that
+\begin{align*}
+     [\phi(\varepsilon^{-1},p)]^{\tau} &\le K_{(p,1),\tau} \phi (\varepsilon^{-1},\tau p)\\
+      [\psi(d,q)]^{\tau} &\le K_{(1,q),\tau} \psi (d,\tau q) \qquad \forall \, \varepsilon \in (0,\infty),\, d\in \naturals,\, p,q\geq 0,\, \tau >0.
+\end{align*}
 %\begin{align*}
  %  [T(\varepsilon^{-1},d,\vp]^\tau \leq K_{\vp,\tau}T(\varepsilon^{-1},d,\tau\vp) \quad \forall \varepsilon \in (0,\infty),\, d\in \mathbb{N},\, \vp\in[0,\infty)^2, \tau >0\end{align*}
-
-Observe that for this tractability function $T$, we have strong tractability if the following condition is satisfied
-\[
- T(\varepsilon^{-1},1,\vp)= \phi(\varepsilon^{-1},p)\, \psi(1,0) = \phi(\varepsilon^{-1},p)
- \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, p \ge 0,
-\] where in this case $\vp$ is a scalar.
-Furthermore, we assume the following technical conditions.
-There exists a $K_{(p,q),\tau}$ depending on $p,q$ and $\tau$, but independent of $\varepsilon$ and $d$, such that
-\begin{align*}
-     [\phi(\varepsilon^{-1},p)]^{\tau} &\le K_{(p,1),\tau} \phi (\varepsilon^{-1},\tau p)\\
-      [\psi(d,q)]^{\tau} &\le K_{(1,q),\tau} \psi (d,\tau q) \qquad \forall \, \varepsilon \in (0,\infty),\, d\in \naturals,\, p,q\geq 0,\, \tau >0.
-\end{align*}
 Thus, Theorem \ref{thm_main_strong_tract2} yields the following equivalent condition for strongly separable tractability
@@
 \end{example}
-\begin{example}[Non-separable symmetric tractability]
+\begin{example}[Non-separable tractability]
     Let the tractability function $T$, be defined by
 \[
- T(\varepsilon^{-1},d,(p,q))= \exp\{\phi(\varepsilon^{-1},p)\, \psi(d,q)\}
- \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, p\ge 0.
-\]  with non-decreasing functions $\phi : (0,\infty) \times (0,\infty) \to (0,\infty)$ and $\psi : \naturals  \times (0,\infty) \to (0,\infty)$.
+ T(\varepsilon^{-1},d,\vp)= \exp\{p(\phi(\varepsilon^{-1})\, \psi(d))\}
+ \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp\in [0,\infty).
+\]  with non-decreasing functions $\phi : (0,\infty) \to (0,\infty)$ and $\psi : \naturals \to (0,\infty)$ and $\vp = p$.
 Furthermore, we assume the following technical conditions.
@@
 \lambda_{1,d}\ge  \cdots \ge \lambda_{M(d)+1,d} \ge E(d) > \lambda_{M(d)+2,d}, \qquad
-(\lambda_{1,d}^{-1},d), \cdots, (\lambda^{-1}_{M(d)+1,d},d) \} \in \Omega.
+(\lambda_{1,d}^{-1},d), \ldots, (\lambda^{-1}_{M(d)+1,d},d)  \in \Omega.
 \]

### 2023-06-04 GeneralizedTractability_230529.tex
Updates from Overleaf

--- 2023-05-13 GeneralizedTractability_230501.tex
@@
 \newcommand{\tpmod}[1]{{\;(\operatorname{mod}\;#1)}}
+\newcommand{\tI}{\widetilde{I}}
 
@@
 We want to bound the complexity in terms of a simple function of $\varepsilon^{-1}$ and $d$ and identify simple conditions on the singular values that are equivalent to this bound holding.
-\kachi{In this paper, we investigate such a function that we refer to as the generalized tractability function, denoted by $T$.
-A proper definition is given in Section \ref{sec:spt}.
-However, we define a tractability function
-\[
- T :(0,\infty) \times \mathbb{N} \times [0,\infty)^s \rightarrow (0,\infty).
-\]
-which depends on $\varepsilon^{-1}$, $d$ and the parameter $\vp$ respectively.
-}
+
+In this article, we investigate such a function that we refer to as the generalized tractability function, denoted by $T$:
+\begin{equation} \label{eq:Tspec}
+    T :(0,\infty) \times \mathbb{N} \times [0,\infty)^s \rightarrow (0,\infty),
+\end{equation}
+The conditions we require $T$ to satisfy are described in  Section \ref{sec:not}, however, the basic idea is that we we define our approximation problem to be tractable if 
+$\comp(\varepsilon, d) \le  C_{\vp}\, T(\varepsilon^{-1},d,\vp)$ for some constant, $C_{\vp}$, depending only on the parameter $\vp$.
+In practice, we expect $T(\varepsilon^{-1},d,\vp)$ to increase mildly with increasing $\varepsilon^{-1}$ and/or $d$, however most of our theorems do not require such an assumption.
 
@@
 
-\fred{Point out that $T$ could increase quite rapidly, but this does not affect our theorems.}
-
-\kachi{In Section \ref{sec:spt}, we give the definitions of the considered tractability notions, in particular (strong) tractability.
+In Section \ref{sec:spt}, we give the definitions of the considered tractability notions, in particular (strong) tractability.
 We consider the strong tractability when the information complexity is independent of the dimension, $d$.
@@
 In the case of the generalized weak tractability, we give the necessary and sufficient conditions on the notion of exponential tractability in Section \ref{sec:subh}.
-}
 
@@
 \subsection{Notation and fundamental definitions} \label{sec:not}
-Let $T$ be a tractability function defined as follows,
-\begin{equation} \label{eq:Tspec}
-    T :(0,\infty) \times \mathbb{N} \times [0,\infty)^s \rightarrow (0,\infty),
-\end{equation}
-A tractability function is a function of simple form that provides an upper bound on the computational complexity of a problem.
-Some examples of tractability functions commonly considered are provided in Section \ref{sec:examples}.
-
-A problem is defined as $T$-tractable with parameter $\vp$ iff there exists a positive constant $C_{\vp}$, which is independent of $\varepsilon$ and $d$, such that
-\begin{equation} \label{eq:tract_def}
-	\comp(\varepsilon,d) \le C_{\vp}\, T(\varepsilon^{-1},d,\vp) \qquad \forall \varepsilon >0, \ d \in \mathbb{N}.
-\end{equation}
-A problem is \emph{strongly}
-$T$-tractable with parameter $\vp$ iff the complexity is independent of the dimension of the problem, that is, there exists a positive constant $C_{\vp}$, again independent of $\varepsilon$ and $d$, such that
-\begin{equation} \label{eq:strong_tract_def}
-	\comp(\varepsilon,d) \le C_{\vp}\, T(\varepsilon^{-1},1,\vp) \qquad \forall \varepsilon >0 , \ d \in \mathbb{N}.
-\end{equation}
-In this article we allow $\vp$ to be a scalar or vector as the situation dictates.
-
-For this definition of tractability to make sense we assume that
-\begin{subequations} \label{eq:Tconditions}
-\begin{equation} \label{eq:Tnondecreasing}
-	T \text{ is non-decreasing in all variables,}
-\end{equation}
-which implies that the problem does not become easier by decreasing the tolerance, $\varepsilon$, or increasing the dimension, $d$.
-Furthermore, increasing $\vp$ does not decrease $T(\cdot, \cdot, \vp)$.
-Since there are an infinite number of positive eigenvalues, it also makes sense to assume that
-\begin{equation}
-	\lim_{\varepsilon \to 0} T(\varepsilon^{-1},d,\vp) = \infty \qquad \forall d \in \naturals, \ \vp \in [0,\infty)^s.
-\end{equation}
-Since $T(\cdot,d,\vp)$ is non-decreasing, we may define the following limit, which we assume will always be positive:
-\begin{equation}
-	T(0,d,\vp):=\lim_{\varepsilon\to\infty}T(\varepsilon^{-1},d,\vp) \ge T(0,1,\vzero) > 0.
-\end{equation}
-\end{subequations}
-Finally, there is a technical assumption required for our analysis.  There exists a $K_{\vp,\tau}$ depending on $\vp$ and $\tau$, but  independent of $\varepsilon$ and $d$, such that
-\begin{equation} \label{eq:ptauassume}
-	[T(\varepsilon^{-1},d,\vp)]^\tau \le K_{\vp,\tau} T(\varepsilon^{-1},d,\tau \vp),   \quad \forall \varepsilon \in (0,\infty), \ d \in \naturals, \ \vp\in[0,\infty)^s, \ \tau\in [1,\infty).
-\end{equation}
-
-Certain common notions of tractability are covered by the general situation described above.
+Let $T$ be a function given in \eqref{eq:Tspec}.
+A tractability function, $T$ is a function of simple form that provides an upper bound on the computational complexity of a problem.
+Some examples of tractability functions commonly considered are provided in Table \ref{tab:commonT}.
+
+\begin{table} 
+    \caption{Common forms of the tractability function, $T$}
 {\small
@@
 \end{equation*}}
-
-Here above, $\vp = (p,q)$ in some cases and $\vp$ is a scalar in other cases. A general reference
+\label{tab:commonT}
+\end{table}
+
+A problem is defined as $T$-tractable with parameter $\vp$ iff there exists a positive constant $C_{\vp}$, which is independent of $\varepsilon$ and $d$, such that
+\begin{equation} \label{eq:tract_def}
+	\comp(\varepsilon,d) \le C_{\vp}\, T(\varepsilon^{-1},d,\vp) \qquad \forall \varepsilon >0, \ d \in \mathbb{N}.
+\end{equation}
+A problem is \emph{strongly}
+$T$-tractable with parameter $\vp$ iff the complexity is independent of the dimension of the problem, that is, there exists a positive constant $C_{\vp}$, again independent of $\varepsilon$ and $d$, such that
+\begin{equation} \label{eq:strong_tract_def}
+	\comp(\varepsilon,d) \le C_{\vp}\, T(\varepsilon^{-1},1,\vp) \qquad \forall \varepsilon >0 , \ d \in \mathbb{N}.
+\end{equation}
+In this article we allow $\vp$ to be a scalar or vector as the situation dictates.
+
+For this definition of tractability to make sense we assume that
+\begin{subequations} \label{eq:Tconditions}
+\begin{equation} \label{eq:Tnondecreasing}
+	T \text{ is non-decreasing in all variables,}
+\end{equation}
+which implies that the problem is expected to be no easier by decreasing the tolerance, $\varepsilon$, or increasing the dimension, $d$.
+Furthermore, increasing $\vp$ does not decrease $T(\cdot, \cdot, \vp)$.
+Since there are an infinite number of positive eigenvalues, it also makes sense to assume that
+\begin{equation}
+	\lim_{\varepsilon \to 0} T(\varepsilon^{-1},d,\vp) = \infty \qquad \forall d \in \naturals, \ \vp \in [0,\infty)^s.
+\end{equation}
+Since $T(\cdot,d,\vp)$ is non-decreasing, we may define the following limit, which we assume will always be positive:
+\begin{equation}\label{eq:T0}	T(0,d,\vp):=\lim_{\varepsilon\to\infty}T(\varepsilon^{-1},d,\vp) \ge T(0,1,\vzero) > 0.
+\end{equation}
+\end{subequations}
+Finally, there is a technical assumption required for our analysis.  There exists a $K_{\vp,\tau}$ depending on $\vp$ and $\tau$, but  independent of $\varepsilon$ and $d$, such that
+\begin{equation} \label{eq:ptauassume}
+	[T(\varepsilon^{-1},d,\vp)]^\tau \le K_{\vp,\tau} T(\varepsilon^{-1},d,\tau \vp),   \quad \forall \varepsilon \in (0,\infty), \ d \in \naturals, \ \vp\in[0,\infty)^s, \ \tau\in [1,\infty).
+\end{equation}
+
+Certain common notions of tractability  covered by the general situation described above are provided in Table \ref{tab:commonT}.
+Here, $\vp = (p,q)$ in some cases and $\vp$ is a scalar in other cases.
+A general reference
 for results on algebraic tractability is \cite{NW08}, for exponential tractability we refer to \cite{HKW19} and \cite{KW19}.
@@
 	 \frac{1}{T (\lambda_{i,d}^{-1},d,\tau \vp)} \le
-	\frac{K_{\vp,\tau}\, C_{\vp}^\tau}{(i-1)^\tau}\qquad \forall i \ge \max\{i(\infty,\vp),2\},  \ d \in \naturals.
+	\frac{K_{\vp,\tau}\, C_{\vp}^\tau}{(i-1)^\tau}\qquad \forall i \ge \max\{i(\infty,d,\vp),2\},  \ d \in \naturals.
 \end{gather*}
@@
 \[
- \sup_{d\in\naturals} \sum_{i=L_{(p,q)} d^{q}}^\infty (\min\{1,\lambda_{i,d}^p\}) d^{-q} < \infty \text{ for some } p,q \ge 0, L_{(p,q)} \in \naturals.
+ \sup_{d\in\naturals}\, d^{-q} \sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty (\min\{1,\lambda_{i,d}^p\})  < \infty \text{ for some } p,q \ge 0, L_{(p,q)} \in \naturals.
 \]
@@
 \[
- \sup_{d\in\naturals} \sum_{i=L_{(p,q)} d^{q}}^\infty [\min\{1,\log(1+\lambda_{i,d}\})]^p d^{-q} < \infty  \text{ for some } p,q \ge 0, L_{(p,q)} \in \naturals.
+ \sup_{d\in\naturals}\, d^{-q} \sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty [\min\{1,\log(1+\lambda_{i,d}\})]^p < \infty  \text{ for some } p,q \ge 0, L_{(p,q)} \in \naturals.
 \]
@@
 
-\begin{example}[Algebraic quasi-polynomial tractability] Here we consider another common notions of tractability.
-
-As defined in \cite{GW11}, we say that a problem is \emph{quasi-polynomially tractable (QPT)} if there exist two constants $C$, $t > 0$, such that
-\begin{equation}\label{expqpt}
-    \comp(\varepsilon,d) \leq C\exp\{t(1+\log(\varepsilon^{-1}))(1+\log(d))\}
-\end{equation}
-for all $\varepsilon \in (0,1]$ and $d\in\mathbb{N}$.\\
-
-\noindent Let the tractability function, $T$,
-be defined by
-\[
- T(\varepsilon^{-1},d,\vp)= \exp\{p(1+\log(\max\{1,\varepsilon^{-1}\}))(1+\log (d))\}  \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty),
-\] where in this case $\vp = p$. This can be rewritten as 
-\[
-T(\varepsilon^{-1},d,\vp) = e^p[\max\{1,\varepsilon^{-1}\}]^{p(1+\log d)}d^p
-\]
-Observe that the function $T$ is a function of $\max\{1,\varepsilon^{-1}\}$ and $d$ which are, polynomial or not exponential in powers of $\max\{1,\varepsilon^{-1}\}$ and $d$.
-Hence we can apply Theorem \ref{thm_main_tract2} as follows.
-We have the following equivalent condition for quasi-polynomial tractability in the algebraic case
-\[
-\sup_{d\in\mathbb{N}}\sum_{i=Lp\,e^pd^{p}} \left(\min\{1,\lambda_{i,d}\} \right)^{p(1+\ln d)}e^{-p}d^{-p} < \infty \qquad \text{for some} p \geq 0, L_p \in \naturals.
-\]
-\end{example}
-\begin{example}[Exponential quasi-polynomial tractability]
-
-\noindent Suppose that the tractability function, $T$, is defined by
-\[
- T(\varepsilon^{-1},d,\vp)= \exp\{p(1+\log(\max\{1,\log(1+\varepsilon^{-1})\}))(1+\log (d))\}  \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty),
-\] where in this case $\vp = p$. This can be rewritten as 
-\[
-T(\varepsilon^{-1},d,\vp) = e^p[\max\{1,\log(1+\varepsilon^{-1}\})]^{p(1+\log d)}d^p
-\]
-Observe that the function $T$ is a function of $\max\{1,\log(1+\varepsilon^{-1})\}$ and $d$.
-Hence we can apply Theorem \ref{thm_main_tract2} as follows.
-We have the following equivalent condition for quasi-polynomial tractability in the exponential case
-\[
-\sup_{d\in\mathbb{N}}\sum_{i=Lp\,e^pd^{p}} \left(\min\{1,\log(1+\lambda_{i,d})\} \right)^{p(1+\ln d)}e^{-p}d^{-p} < \infty
-\]
-\end{example}
-
-\kachi{In the following we introduce two specific cases of tractability which depend on the form of the function $T$.
 \begin{example}[(Strong) Separable tractability]
-Suppose that
+Suppose that the tractability function is defined by
 \[
@@
 \]
-with non-decreasing functions $\phi : (0,\infty) \times (0,\infty) \to (0,\infty)$ and $\psi : \naturals  \times (0,\infty) \to (0,\infty)$ and where $\vp = (p,q)$.
+with non-decreasing functions $\phi : (0,\infty) \times (0,\infty) \to (0,\infty)$ and $\psi : \naturals  \times (0,\infty) \to (0,\infty)$ and where $\vp = (p,q)$, hence $T$ is non-decreasing in all variables.
 
@@
 \[
-\comp(\varepsilon,d) \leq  C_{\vp}\,T(\varepsilon^{-1},d,\vp)\qquad \forall \varepsilon >0, \, d\in\naturals,
-\]
-that is
-\[
-\comp(\varepsilon,d) \leq \phi(\varepsilon^{-1},p)\, \psi(d,q) \qquad \forall \varepsilon >0, \, d\in\naturals.
-\]
+\comp(\varepsilon,d) \leq  C_{\vp}\,\phi(\varepsilon^{-1},p)\, \psi(d,q)\qquad \forall \varepsilon >0, \, d\in\naturals,
+\] where $\vp = (p,q)$.
 A problem is strongly $T$-separable tractable with parameter $\vp$ iff the complexity is independent of $d$, that is, there exists a positive constant $C_{\vp}$ which again does not depend on $\varepsilon$ and $d$ such that
 \[
-\comp(\varepsilon,d) \leq C_{\vp}T(\varepsilon^{-1}, 1,\vp) \qquad \forall \varepsilon >0, \, d\in\naturals,
-\] where $\vp = p$. We have
-\[
-\comp(\varepsilon,d) \leq \phi(\varepsilon^{-1},p)\qquad \forall \varepsilon >0, \, d\in\naturals.
-\]
-%In addition, we assume the following conditions as in (\ref{eq:ptauassume}).
-That is, there exists a $K_{(p,q),\tau}$ depending on $p,q$ and $\tau$, but independent of $\varepsilon$ and $d$, such that
-%\begin{equation} \label{eq:tractiff}    \sup_{d \in \naturals} \frac{1}{\psi(d,q)} \sum_{i = C(p,q)}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p))} < \infty.\end{equation}
-Furthermore, we assume that
-\[
-\lim_{\varepsilon\rightarrow0}T(\varepsilon^{-1},d,\vp) = \infty \qquad \forall d\in\naturals, \vp \in[0,\infty)^2.
-\]
-Also since $T(\cdot,d,\vp)$ is non-decreasing, we may define the following limit
-\[
-T(0,d,\vp):= \lim_{\varepsilon \rightarrow \infty}T(\varepsilon^{-1},d,\vp)\geq T(0,1,\textbf{0})>0
-\] 
-%Furthermore, we assume the following technical conditions. There exists a $K_{(p,q),\tau}$ depending on $p,q$ and $\tau$, but independent of $\varepsilon$ and $d$, such that
+\comp(\varepsilon,d) \leq C_{\vp}\phi(\varepsilon^{-1},p)\qquad \forall \varepsilon >0, \, d\in\naturals,
+\] where $\vp = p$ is a scalar. 
+Furthermore, we assume the following as in \eqref{eq:Tconditions} and \eqref{eq:ptauassume}. We assume that
+\[
+\lim_{\varepsilon\rightarrow0}\phi(\varepsilon^{-1},p) = \infty \qquad \forall d\in\naturals, p >0.
+\] since there are an infinite number of positive eigenvalues. Furthermore, we have that $\phi(\cdot,p)$ is non-decreasing hence we define the following limit
+\[ \lim_{\varepsilon \rightarrow \infty}\phi(\varepsilon^{-1},p)\geq 1.
+\] 
+Additionally, we have the following technical assumptions.
+Suppose that, for any real $\tau_1, \tau_2>0$ and any $p,q>0$, we have that there exists $\hat{K}_{p,\tau_1}$ and $\hat{K}_{q\tau_2}$ such that
 \begin{align*}
-     [\phi(\varepsilon^{-1},p)]^{\tau} &\le K_{(p,1),\tau} \phi (\varepsilon^{-1},\tau p)\\
-      [\psi(d,q)]^{\tau} &\le K_{(1,q),\tau} \psi (d,\tau q) \qquad \forall \, \varepsilon \in (0,\infty),\, d\in \naturals,\, p,q\geq 0,\, \tau >0.
-\end{align*}
-%\begin{align*}
- %  [T(\varepsilon^{-1},d,\vp]^\tau \leq K_{\vp,\tau}T(\varepsilon^{-1},d,\tau\vp) \quad \forall \varepsilon \in (0,\infty),\, d\in \mathbb{N},\, \vp\in[0,\infty)^2, \tau >0\end{align*}
-Thus, Theorem \ref{thm_main_strong_tract2} yields the following equivalent condition for strongly separable tractability
+     [\phi(\varepsilon^{-1},p)]^{\tau_1} &\le \hat{K}_{p,\tau_1} \phi (\varepsilon^{-1},\tau_1 p)\\
+      [\psi(d,q)]^{\tau_2} &\le \hat{K}_{q,\tau_2} \psi (d,\tau_2 q) \qquad \forall \, \varepsilon \in (0,\infty),\, d\in \naturals.
+\end{align*} where $\hat{K}_{p,\tau_1}>0$ is a constant that may depend on $p$ and $\tau_1$, but is independent of $\varepsilon$, and where $\hat{K}_{q,\tau_2}>0$ is a constant that may depend on $q$ and $\tau_2$, but is independent of $d$.
+
+Thus, Theorem \ref{thm_main_strong_tract2} yields the following equivalent condition for strongly $T$-separable tractability
 \begin{equation*} \label{eq:strong_tractiff}
@@
 \[
- \sup_{d \in \naturals} \frac{1}{\psi(d,q)} \sum_{i = L_{(p,q)\psi(d,q)}}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)} < \infty.
-\]
-%As the name implies, the roles of $\varepsilon^{-1}$ and $d$ are separated. 
+ \sup_{d \in \naturals} \frac{1}{\psi(d,q)} \sum_{i = \lceil L_{(p,q)\psi(d,q)}\rceil}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)} < \infty,
+\] for some $p,q >0$ and $L_{(p,q)}\in\naturals$.
 \end{example}
+
 \begin{example}[Non-separable tractability]
-    Let the tractability function $T$, be defined by
+    Suppose we define the tractability function $T$ by
 \[
@@
 \]  with non-decreasing functions $\phi : (0,\infty) \to (0,\infty)$ and $\psi : \naturals \to (0,\infty)$ and $\vp = p$. 
-Furthermore, we assume the following technical conditions.
-There exists a $K_{(p,q),\tau}$ depending on $p,q$ and $\tau$, but independent of $\varepsilon$ and $d$, such that
-\begin{align*}
-     [\phi(\varepsilon^{-1},p)]^{\tau} &\le K_{(p,1),\tau} \phi (\varepsilon^{-1},\tau p)\\
-      [\psi(d,q)]^{\tau} &\le K_{(1,q),\tau} \psi (d,\tau q) \qquad \forall \, \varepsilon \in (0,\infty),\, d\in \naturals,\, p,q\geq 0,\, \tau >0.
-\end{align*}
+We say that a problem is non-separable tractable with parameter $\vp$ iff there exists a positive $C_{\vp}$ such that
+
+\[\comp(\varepsilon,d) \leq  C_{\vp}\exp\{p(\phi(\varepsilon^{-1})\psi(d))\}.\]
+
+Hence we can apply Theorem \ref{thm_main_tract2} as follows. We have the following equivalent condition for non-separable tractability
+\[
+\sup_{d\in\mathbb{N}}\frac{1}{\psi(d)}\sum_{i=Lp\,\psi(d)} \phi(\lambda_{i,d})\quad \text{for some } p \geq 0, L_p \in \naturals.
+\]
+We have the following special cases of non-separable tractability. \end{example}
+\begin{example}[Algebraic quasi-polynomial tractability]
+
+As defined in \cite{GW11}, we say that a problem is \emph{quasi-polynomially tractable (QPT)} if there exist two constants $C$, $t > 0$, such that
+\begin{equation}\label{expqpt}
+    \comp(\varepsilon,d) \leq C\exp\{t(1+\log(\varepsilon^{-1}))(1+\log(d))\}
+\end{equation}
+for all $\varepsilon \in (0,1]$ and $d\in\mathbb{N}$.\\
+
+\noindent Let the tractability function, $T$,
+be defined by
+\[
+ T(\varepsilon^{-1},d,\vp)= \exp\{p(1+\log(\max\{1,\varepsilon^{-1}\}))(1+\log (d))\}  \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty),
+\] where in this case $\vp = p$. This can be rewritten as 
+\[
+T(\varepsilon^{-1},d,\vp) = e^p[\max\{1,\varepsilon^{-1}\}]^{p(1+\log d)}d^p
+\]
+Observe that the function $T$ is a function of $\max\{1,\varepsilon^{-1}\}$ and $d$ which are, polynomial or not exponential in powers of $\max\{1,\varepsilon^{-1}\}$ and $d$.
+Hence we can apply Theorem \ref{thm_main_tract2} as follows.
+We have the following equivalent condition for quasi-polynomial tractability in the algebraic case
+\[
+\sup_{d\in\mathbb{N}}\,d^{-p}\sum_{i=Lp\,d^{p}} \left(\min\{1,\lambda_{i,d}\} \right)^{p(1+\ln d)} < \infty \qquad \text{for some } p \geq 0, L_p \in \naturals.\]
 \end{example}
-}
+\begin{example}[Exponential quasi-polynomial tractability]
+
+\noindent Suppose that the tractability function, $T$, is defined by
+\[
+ T(\varepsilon^{-1},d,\vp)= \exp\{p(1+\log(\max\{1,\log(1+\varepsilon^{-1})\}))(1+\log (d))\}  \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty),
+\] where in this case $\vp = p$. This can be rewritten as 
+\[
+T(\varepsilon^{-1},d,\vp) = e^p[\max\{1,\log(1+\varepsilon^{-1}\})]^{p(1+\log d)}d^p.
+\]
+Observe that the function $T$ is a function of $\max\{1,\log(1+\varepsilon^{-1})\}$ and $d$.
+Hence we can apply Theorem \ref{thm_main_tract2} as follows.
+We have the following equivalent condition for quasi-polynomial tractability in the exponential case
+\[
+\sup_{d\in\mathbb{N}}\,d^{-p}\sum_{i=Lp\,d^{p}} \left(\min\{1,\log(1+\lambda_{i,d})\} \right)^{p(1+\ln d)}e^{-p} < \infty \quad \text{for some } p \geq 0, L_p \in \naturals.
+\]
+\end{example}
+
+%In the following we introduce two specific cases of tractability which depend on the form of the function $T$ (see \cite{}).
 
@@
 
-Suppose that the domain of interesting $(\varepsilon^{-1},d)$ is not all of $(0,\infty \times \naturals$ but given by 
+Suppose that the domain of interest $(\varepsilon^{-1},d)$ is not all of $(0,\infty) \times \naturals$ but given by 
 \begin{equation}
-    \Omega  = \{(\varepsilon^{-1},d) : \varepsilon > E(d) \ge 0, \ d \in \naturals \},
-\end{equation}
-where $E$ is a non-increasing function.  A problem is
+    \Omega  = \{(\varepsilon^{-1},d) : \varepsilon \peter{> E(d) \ge 0}, \ d \in \naturals \},
+\end{equation}
+%where $E$ is a non-increasing \peter{[{is this a necessary assumption?}]} function.  
+A problem is \peter{strongly}
 $T$-tractable with parameter $\vp$ \emph{on the restricted domain $\Omega$} iff the complexity is independent of the dimension of the problem, that is, there exists a positive constant $C_{\vp}$, again independent of $\varepsilon$ and $d$, such that
@@
 \end{equation}
-Define $M(d) = \max\{n : \lambda_{n+1,d} \ge E(d)\}$, i.e., 
-\[
-\lambda_{1,d}\ge  \cdots \ge \lambda_{M(d)+1,d} \ge E(d) > \lambda_{M(d)+2,d}, \qquad
-(\lambda_{1,d}^{-1},d), \ldots, (\lambda^{-1}_{M(d)+1,d},d)  \in \Omega.
+\peter{[I am wondering whether this makes sense if $E$ depends on $d$? Do Gnewuch and Wo\'{z}niakowski allow dependence of $E$ on $d$?]}
+
+\peter{
+A problem is 
+$T$-tractable with parameter $\vp$ \emph{on the restricted domain $\Omega$} iff the complexity is independent of the dimension of the problem, that is, there exists a positive constant $C_{\vp}$, again independent of $\varepsilon$ and $d$, such that
+\begin{equation} \label{eq:rest_tract_def}
+	\comp(\varepsilon,d) \le C_{\vp}\, T(\varepsilon^{-1},d,\vp) \qquad \forall(\varepsilon^{-1},d) \in \Omega.
+\end{equation}
+}
+
+Define 
+\begin{equation} \label{eq:Mddef}
+    M(d) := \begin{cases}
+        \max\{n : \lambda_{n+1,d} > E(d)\}, & E(d) > 0, \\
+        \infty, & E(d) = 0.
+    \end{cases}
+\end{equation}
+This means that 
+\[
+\begin{cases}
+\lambda_{1,d}\ge  \cdots \ge \lambda_{M(d)+1,d} > E(d) \ge\lambda_{M(d)+2,d}, \quad
+(\lambda_{1,d}^{-1},d), \ldots, (\lambda^{-1}_{M(d)+1,d},d)  \in \Omega, & E(d) > 0, \\
+\lambda_{1,d}\ge \lambda_{2,d}\ge \cdots  > 0, \quad
+(\lambda_{1,d}^{-1},d), (\lambda_{2,d}^{-1},d), \ldots \in \Omega, & E(d) = 0.
+\end{cases}
 \]
@@
 Fix any $(\varepsilon^{-1},d) \in \Omega$.
-Then
 
 Since the $\lambda_{i,d}$ are non-increasing in $i$, it follows that the $T(\lambda_{i,d}^{-1},d,\vp)$ are non-decreasing in $i$ for $i \in \{1, \ldots, M(d)+1\}$.
-In particular, for  any $n \in \{N, \ldots, M(d)\}$
+In particular, for any \peter{$N\in\{1,\ldots,M(d)\}$ and any} $n \in \{N, \ldots, M(d)\}$
 \begin{align*}
@@
 \end{multline}
-We note that the left side of the implication implies $n \ge N$ automatically since $n$ is an integer  $n - N +1$ is assumed to be positive.
+We note that the left side of the implication implies $n \ge N$ automatically since $n$ is an integer and $n - N +1$ is assumed to be positive.
 
@@
 
-it follows from \eqref{eq:compUP} with $N = \lceil L_{\vp}\, T(0,d,\vp)\rceil$ that 
+it follows from \eqref{eq:compUP_rest} with $N = \lceil L_{\vp}\, T(0,d,\vp)\rceil$ that 
 \begin{align*}
@@
 \end{equation}
-Define the integers \fred{Only got here because we have to be careful with the domain of stuff}
+
+For $(\varepsilon^{-1}, d) \in \Omega$, define the integers 
 \[
@@
 \]
-Thus, it follows by \eqref{eq:lambda_K4} that $\lambda_{i(\varepsilon,d,\vp),d} \le \varepsilon$.
-Note furthermore that we always have
-\[
-i(\varepsilon,d,\vp)\le C_{\vp}\, T(\varepsilon^{-1},d,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,d,\vp),d}^{-1},d,\vp)+1, \qquad \forall \varepsilon > 0, \ d \in \naturals,
-\]
-since
-$T(\cdot,d,\vp)$ is non-decreasing.
-
-For $\varepsilon$ taking on all positive values, $i(\varepsilon,d,\vp)$ takes on all values greater than or equal to $i(\infty,d,\vp)$, so
-\[
-i\le C_{\vp}\, T(\varepsilon^{-1},d,\vp)+1 \le C_{\vp} T(\lambda_{i,d}^{-1},d,\vp)+1, \qquad \forall i \ge i(\infty,d,\vp),  \ d \in \naturals.
-\]
-This implies via our technical assumption \eqref{eq:ptauassume} that for any $\tau > 1$,
-\begin{gather*}
+It follows by \eqref{eq:lambda_K4} that $\lambda_{i(\varepsilon,d,\vp),d} \le \varepsilon$
+for any  $(\varepsilon^{-1}, d) \in \Omega$.
+Note furthermore that since $T(\cdot,d,\vp)$ is non-decreasing, we have
+\[
+i(\varepsilon,d,\vp)\le C_{\vp}\, T(\varepsilon^{-1},d,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,d,\vp),d}^{-1},d,\vp)+1, \qquad \forall (\varepsilon^{-1},d)\in\Omega.
+\]
+For $\varepsilon$ taking on all values in $(E(d),\infty)$, $i(\varepsilon,d,\vp)$ takes on (at least) all values 
+\[
+I_{d}:=\begin{cases} 
+\{i(\infty,d,\vp),\ldots, i(E(d),d,\vp)-1\}, & E(d) > 0, \\
+\{i(\infty,d,\vp), i(\infty,d,\vp) + 1, \ldots\}, & E(d) = 0.
+\end{cases}
+\]
+So,
+\[
+i\le  C_{\vp} T(\lambda_{i,d}^{-1},d,\vp)+1, \qquad \forall i\in I_{d},  \ d \in \naturals.
+\]
+
+This upper bound on $i$ in terms of $T(\lambda_{i,d}^{-1},d,\vp)$ implies via our technical assumption \eqref{eq:ptauassume} that for any $\tau > 1$,
+\[
 	K_{\vp,\tau}\,T (\lambda_{i,d}^{-1},d,\tau \vp) \ge
@@
 	\ge
-	\left[\frac{(i-1)}{C_{\vp}}\right]^\tau \qquad \forall i \ge i(\infty,d,\vp),  \ d \in \naturals, \\
+	\left[\frac{(i-1)}{C_{\vp}}\right]^\tau \qquad  \forall i\in I_{d},  \ d \in \naturals.
+ \]
+To carry the argument further, we need to show that the interval $I_d$ contains the interval
+\[
+\tI_{d}:=\begin{cases} 
+\{i(\infty,d,\vp),\ldots, M(d)\}, & E(d) > 0, \\
+\{i(\infty,d,\vp), i(\infty,d,\vp) + 1, \ldots\}, & E(d) = 0.
+\end{cases}
+\]
+
+Since $I_d = \tI_d$ when $E(d) =0$, we need only consider the case where $E(d) > 0$.  In this case \eqref{eq:Mddef} and \eqref{eq:lambda_K4} imply that
+\[
+\lambda_{i(E(d),d,\vp),d} \le \lambda_{M(d)+2} \le E(d) < \lambda_{M(d)+1,d}.
+\]
+This means that $i(E(d),d,\vp)-1 \ge M(d)+1$, and so $I_d \ge \tI_d$
+
+\[
+\lambda_{i(E(d),d,\vp),d} \le \lambda_{M(d)+2} \le E(d) < \lambda_{M(d)+1,d} 
+\]
+
+Choose an $\varepsilon \in (E(d),\infty)$ such that $i(\varepsilon,d,\vp) = i(E(d),d,\vp) - 1$.  It follows from \eqref{eq:lambda_K4} that
+\[
+\lambda_{i(\varepsilon,d,\vp)} \le \varepsilon < E(d) \le \lambda_{i(\varepsilon,d,\vp)} + 1
+\]
+
+Note that, for any $\delta>0$,
+\[
+\lambda_{\lfloor C_{\vp}\, T((E(d) + \delta)^{-1},d,\vp)\rfloor +1} \le E(d) + \delta, 
+\]
+\peter{Furthermore, define
+\[
+i (E(d),d,\vp):=\lim_{\delta\to 0}\, i (E(d)+\delta,d,\vp)
+= \lim_{\delta\to 0}\, \lfloor C_{\vp}\, T((E(d) + \delta)^{-1},d,\vp)\rfloor +1. 
+\]
+Note that, for any $\delta>0$,
+\[
+\lambda_{\lfloor C_{\vp}\, T((E(d) + \delta)^{-1},d,\vp)\rfloor +1} \le E(d) + \delta, 
+\]
+and therefore, for $\delta\to 0$, we obtain
+\[
+\lambda_{i (E(d),d,\vp)} \le E(d). 
+\]
+On the other hand, by definition of $M(d)$, $M(d)$ is minimal such that 
+\[
+\lambda_{M(d)+2}\le E(d).
+\]
+This implies that 
+\[
+M(d) < M(d) +2 \le i (E(d),d,\vp).
+\]
+
+}
+
+For $\varepsilon$ taking on all \peter{values in $(E(d),\infty)$}, $i(\varepsilon,d,\vp)$ takes on all values 
+\peter{in 
+\[
+I_{E(d),d}:=\{i(\infty,d,\vp),\ldots, i(E(d),d,\vp)\}
+\]
+} 
+so
+\[
+i\le C_{\vp}\, T(\varepsilon^{-1},d,\vp)+1 \le C_{\vp} T(\lambda_{i,d}^{-1},d,\vp)+1, \qquad \peter{\forall i\in I_{E(d),d}},  \ d \in \naturals.
+\]
+
+This implies via our technical assumption \eqref{eq:ptauassume} that for any $\tau > 1$,
+\[
+	K_{\vp,\tau}\,T (\lambda_{i,d}^{-1},d,\tau \vp) \ge
+	[T(\lambda_{i,d}^{-1},d, \vp)]^\tau
+	\ge
+	\left[\frac{(i-1)}{C_{\vp}}\right]^\tau \qquad  \peter{\forall i\in I_{E(d),d}},  \ d \in \naturals,
+ \]
+ and this implies
+ \[
 	 \frac{1}{T (\lambda_{i,d}^{-1},d,\tau \vp)} \le
-	\frac{K_{\vp,\tau}\, C_{\vp}^\tau}{(i-1)^\tau}\qquad \forall i \ge \max\{i(\infty,\vp),2\},  \ d \in \naturals.
-\end{gather*}
-
-Let $\vp' = \tau \vp$.
-Note that $i(\infty,d,\cdot)$ is non-decreasing.
-Summing both sides of the latter inequality over $i$ from $i(\infty,d,\vp') + 1 \ge i(\infty,d, \vp) + 1 \ge 2$ to $\infty$ it follows that
+	\frac{K_{\vp,\tau}\, C_{\vp}^\tau}{(i-1)^\tau}\qquad  \peter{\forall i\in 
+ \{i(\infty,d,\vp)+1,\ldots, M(d)\}},  \ d \in \naturals.
+\]
+
+Let $\vp' = \tau \vp$. \peter{Like in the proof of Theorem \ref{thm_main_tract2}, we note that $i(\infty,d,\vp) 
+\ge i(\infty,d,\vp')$. Furthermore, we also have 
+$M(d)\le i(E(d),d,\vp)\le i(E(d),d,\vp')$. Thus,}
+summing both sides of the latter inequality over \peter{$\{i(\infty,d,\vp')+1,\ldots, M(d)\} $} it follows that
 \begin{equation*}
-	\sup_{d\in\naturals} \, \, \sum_{i=i (\infty,d,\vp')+1}^\infty \frac{1}{T (\lambda_{i,d}^{-1},d,\vp')}
+	\sup_{d\in\naturals} \, \, \sum_{\peter{i=i(\infty,d,\vp')+1}}^{\peter{M(d)}} \frac{1}{T (\lambda_{i,d}^{-1},d,\vp')}
 	 \le  K_{\vp,\tau}\, C_{\vp}^\tau
-	\sum_{i=2}^\infty \frac{1}{(i-1)^\tau} \\
+	\sum_{i=2}^{\infty} \frac{1}{(i-1)^\tau} \\
 	 \le  K_{\vp,\tau}\, C_{\vp}^\tau
@@
 where $\zeta$ denotes the Riemann zeta function.
+
+\peter{[WHAT REMAINS TO BE DONE (HOPEFULLY NOT HARD): check that the summation range above is not empty.]}
 
@@
 \[
-\sup_{d\in\naturals}\,\, \sum_{i=\lceil L(\vp') T(0,d,\vp')\rceil}^\infty \frac{1}{T(\lambda_{i,d}^{-1},d, \vp')}
+\sup_{d\in\naturals}\,\, \sum_{i=\lceil L(\vp') T(0,d,\vp')\rceil}^{\peter{M(d)}} \frac{1}{T(\lambda_{i,d}^{-1},d, \vp')}
 \le

### 2023-06-04 Older_versions/GeneralizedTractability_230501.tex
Updates from Overleaf

--- 2023-05-13 GeneralizedTractability_230501.tex
@@
 \[
- \sup_{d\in\naturals} \sum_{i=L_{(p,q)} d^{q}}^\infty (\min\{1,\lambda_{i,d}^p\}) d^{-q} < \infty \text{ for some } p,q \ge 0, L_{(p,q)} \in \naturals.
+ \sup_{d\in\naturals}\, d^{-q} \sum_{i=L_{(p,q)} d^{q}}^\infty (\min\{1,\lambda_{i,d}^p\})  < \infty \text{ for some } p,q \ge 0, L_{(p,q)} \in \naturals.
 \]
@@
 \[
- \sup_{d\in\naturals} \sum_{i=L_{(p,q)} d^{q}}^\infty [\min\{1,\log(1+\lambda_{i,d}\})]^p d^{-q} < \infty  \text{ for some } p,q \ge 0, L_{(p,q)} \in \naturals.
+ \sup_{d\in\naturals}\, d^{-q} \sum_{i=L_{(p,q)} d^{q}}^\infty [\min\{1,\log(1+\lambda_{i,d}\})]^p < \infty  \text{ for some } p,q \ge 0, L_{(p,q)} \in \naturals.
 \]
@@
 \[
-\comp(\varepsilon,d) \leq  C_{\vp}\,T(\varepsilon^{-1},d,\vp)\qquad \forall \varepsilon >0, \, d\in\naturals,
-\]
-that is
-\[
-\comp(\varepsilon,d) \leq \phi(\varepsilon^{-1},p)\, \psi(d,q) \qquad \forall \varepsilon >0, \, d\in\naturals.
+\comp(\varepsilon,d) \leq  C_{\vp}\,\phi(\varepsilon^{-1},p)\, \psi(d,q)\qquad \forall \varepsilon >0, \, d\in\naturals.
 \]
@@
 \[
-\comp(\varepsilon,d) \leq C_{\vp}T(\varepsilon^{-1}, 1,\vp) \qquad \forall \varepsilon >0, \, d\in\naturals,
-\] where $\vp = p$. We have
-\[
-\comp(\varepsilon,d) \leq \phi(\varepsilon^{-1},p)\qquad \forall \varepsilon >0, \, d\in\naturals.
-\]
-%In addition, we assume the following conditions as in (\ref{eq:ptauassume}).
-That is, there exists a $K_{(p,q),\tau}$ depending on $p,q$ and $\tau$, but independent of $\varepsilon$ and $d$, such that
-%\begin{equation} \label{eq:tractiff}    \sup_{d \in \naturals} \frac{1}{\psi(d,q)} \sum_{i = C(p,q)}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p))} < \infty.\end{equation}
-Furthermore, we assume that
-\[
-\lim_{\varepsilon\rightarrow0}T(\varepsilon^{-1},d,\vp) = \infty \qquad \forall d\in\naturals, \vp \in[0,\infty)^2.
-\]
-Also since $T(\cdot,d,\vp)$ is non-decreasing, we may define the following limit
+\comp(\varepsilon,d) \leq C_{\vp}\phi(\varepsilon^{-1},p)\psi(1,q) \qquad \forall \varepsilon >0, \, d\in\naturals,
+\] where $\vp = (p,q)$. 
+Furthermore, we assume the following as in \eqref{eq:Tconditions} and \eqref{eq:ptauassume}.
+\[
+\lim_{\varepsilon\rightarrow0}\phi(\varepsilon^{-1},p) = \infty \qquad \forall d\in\naturals, p >0.
+\]
+Also since $T(\cdot,d,\vp)$ is non-decreasing, we define the following limit
 \[
@@
 \] 
-%Furthermore, we assume the following technical conditions. There exists a $K_{(p,q),\tau}$ depending on $p,q$ and $\tau$, but independent of $\varepsilon$ and $d$, such that
-\begin{align*}
-     [\phi(\varepsilon^{-1},p)]^{\tau} &\le K_{(p,1),\tau} \phi (\varepsilon^{-1},\tau p)\\
-      [\psi(d,q)]^{\tau} &\le K_{(1,q),\tau} \psi (d,\tau q) \qquad \forall \, \varepsilon \in (0,\infty),\, d\in \naturals,\, p,q\geq 0,\, \tau >0.
-\end{align*}
-%\begin{align*}
- %  [T(\varepsilon^{-1},d,\vp]^\tau \leq K_{\vp,\tau}T(\varepsilon^{-1},d,\tau\vp) \quad \forall \varepsilon \in (0,\infty),\, d\in \mathbb{N},\, \vp\in[0,\infty)^2, \tau >0\end{align*}
+Additionally, we have the following technical assumptions. Suppose that, for any real $\tau_1, \tau_2>0$ and any $p,q>0$, we have that 
+\begin{align*}
+     [\phi(\varepsilon^{-1},p)]^{\tau_1} &\le \hat{K}_{p,\tau_1} \phi (\varepsilon^{-1},\tau_1 p)\\
+      [\psi(d,q)]^{\tau_2} &\le \hat{K}_{q,\tau_2} \psi (d,\tau_2 q) \qquad \forall \, \varepsilon \in (0,\infty),\, d\in \naturals.
+\end{align*} where $L_{p,\tau_1}>0$ is a constant that may depend on $p$ and $\tau_1$, but is independent of $\varepsilon$, and where $L_{q,\tau_2}>0$ is a constant that may depend on $q$ and $\tau_2$, but is independent of $d$.
+\begin{align*}
+  [T(\varepsilon^{-1},d,\vp]^\tau \leq K_{\vp,\tau}T(\varepsilon^{-1},d,\tau\vp) \quad \forall \varepsilon \in (0,\infty),\, d\in \mathbb{N},\, \vp\in[0,\infty)^2, \tau >0\end{align*}
+
 Thus, Theorem \ref{thm_main_strong_tract2} yields the following equivalent condition for strongly separable tractability
@@
 %As the name implies, the roles of $\varepsilon^{-1}$ and $d$ are separated.
+
 \end{example}
+
 \begin{example}[Non-separable tractability]
@@
 \]  with non-decreasing functions $\phi : (0,\infty) \to (0,\infty)$ and $\psi : \naturals \to (0,\infty)$ and $\vp = p$. 
-Furthermore, we assume the following technical conditions.
-There exists a $K_{(p,q),\tau}$ depending on $p,q$ and $\tau$, but independent of $\varepsilon$ and $d$, such that
-\begin{align*}
-     [\phi(\varepsilon^{-1},p)]^{\tau} &\le K_{(p,1),\tau} \phi (\varepsilon^{-1},\tau p)\\
-      [\psi(d,q)]^{\tau} &\le K_{(1,q),\tau} \psi (d,\tau q) \qquad \forall \, \varepsilon \in (0,\infty),\, d\in \naturals,\, p,q\geq 0,\, \tau >0.
-\end{align*}
+We say that a problem is non-separable tractable with parameter $\vp$ iff there exists a positive $C_{\vp}$ such that
+\[
+\comp(\varepsilon,d) \leq C_{\vp} T(\varepsilon^{-1},d,\vp),
+\]
+for all $\varepsilon\in (0,1]$ and $d\in \naturals$, that is
+\[\comp(\varepsilon,d) \leq  \exp\{p(\phi(\varepsilon^{-1})\psi(d))\}.\]
+
+Hence we can apply Theorem \ref{thm_main_tract2} as follows. We have the following equivalent condition for non-separable tractability
+\[
+\sup_{d\in\mathbb{N}}\sum_{i=Lp\,\psi(d)} \phi(\lambda_{i,d})\psi(d) < \infty \qquad \text{for some} p \geq 0, L_p \in \naturals.
+\]
+We have the following special cases. \end{example}
+\begin{example}[Algebraic quasi-polynomial tractability] Here we consider another common notions of tractability.
+
+As defined in \cite{GW11}, we say that a problem is \emph{quasi-polynomially tractable (QPT)} if there exist two constants $C$, $t > 0$, such that
+\begin{equation}\label{expqpt}
+    \comp(\varepsilon,d) \leq C\exp\{t(1+\log(\varepsilon^{-1}))(1+\log(d))\}
+\end{equation}
+for all $\varepsilon \in (0,1]$ and $d\in\mathbb{N}$.\\
+
+\noindent Let the tractability function, $T$,
+be defined by
+\[
+ T(\varepsilon^{-1},d,\vp)= \exp\{p(1+\log(\max\{1,\varepsilon^{-1}\}))(1+\log (d))\}  \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty),
+\] where in this case $\vp = p$. This can be rewritten as 
+\[
+T(\varepsilon^{-1},d,\vp) = e^p[\max\{1,\varepsilon^{-1}\}]^{p(1+\log d)}d^p
+\]
+Observe that the function $T$ is a function of $\max\{1,\varepsilon^{-1}\}$ and $d$ which are, polynomial or not exponential in powers of $\max\{1,\varepsilon^{-1}\}$ and $d$.
+Hence we can apply Theorem \ref{thm_main_tract2} as follows.
+We have the following equivalent condition for quasi-polynomial tractability in the algebraic case
+\[
+\sup_{d\in\mathbb{N}}\frac{1}{d^p}\sum_{i=Lp\,d^{p}} \left(\min\{1,\lambda_{i,d}\} \right)^{p(1+\ln d)} < \infty \qquad \text{for some } p \geq 0, L_p \in \naturals.\]
 \end{example}
-}
+\begin{example}[Exponential quasi-polynomial tractability]
+
+\noindent Suppose that the tractability function, $T$, is defined by
+\[
+ T(\varepsilon^{-1},d,\vp)= \exp\{p(1+\log(\max\{1,\log(1+\varepsilon^{-1})\}))(1+\log (d))\}  \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty),
+\] where in this case $\vp = p$. This can be rewritten as 
+\[
+T(\varepsilon^{-1},d,\vp) = e^p[\max\{1,\log(1+\varepsilon^{-1}\})]^{p(1+\log d)}d^p
+\]
+Observe that the function $T$ is a function of $\max\{1,\log(1+\varepsilon^{-1})\}$ and $d$.
+Hence we can apply Theorem \ref{thm_main_tract2} as follows.
+We have the following equivalent condition for quasi-polynomial tractability in the exponential case
+\[
+\sup_{d\in\mathbb{N}}\sum_{i=Lp\,e^pd^{p}} \left(\min\{1,\log(1+\lambda_{i,d})\} \right)^{p(1+\ln d)}e^{-p}d^{-p} < \infty
+\]
+\end{example}
+
+%In the following we introduce two specific cases of tractability which depend on the form of the function $T$ (see \cite{}).
 
@@
 
-Suppose that the domain of interesting $(\varepsilon^{-1},d)$ is not all of $(0,\infty \times \naturals$ but given by 
+Suppose that the domain of interest $(\varepsilon^{-1},d)$ is not all of $(0,\infty) \times \naturals$ but given by 
 \begin{equation}
-    \Omega  = \{(\varepsilon^{-1},d) : \varepsilon > E(d) \ge 0, \ d \in \naturals \},
-\end{equation}
-where $E$ is a non-increasing function.  A problem is
+    \Omega  = \{(\varepsilon^{-1},d) : \varepsilon \peter{\ge E(d) > 0}, \ d \in \naturals \},
+\end{equation}
+where $E$ is a non-increasing \peter{[{is this a necessary assumption?}]} function.  A problem is \peter{strongly}
 $T$-tractable with parameter $\vp$ \emph{on the restricted domain $\Omega$} iff the complexity is independent of the dimension of the problem, that is, there exists a positive constant $C_{\vp}$, again independent of $\varepsilon$ and $d$, such that
@@
 \end{equation}
+\peter{[I am wondering whether this makes sense if $E$ depends on $d$? Do Gnewuch and Wo\'{z}niakowski allow dependence of $E$ on $d$?]}
+
+\peter{
+A problem is 
+$T$-tractable with parameter $\vp$ \emph{on the restricted domain $\Omega$} iff the complexity is independent of the dimension of the problem, that is, there exists a positive constant $C_{\vp}$, again independent of $\varepsilon$ and $d$, such that
+\begin{equation} \label{eq:rest_tract_def}
+	\comp(\varepsilon,d) \le C_{\vp}\, T(\varepsilon^{-1},d,\vp) \qquad \forall(\varepsilon^{-1},d) \in \Omega.
+\end{equation}
+}
+
 Define $M(d) = \max\{n : \lambda_{n+1,d} \ge E(d)\}$, i.e., 
@@
 Since the $\lambda_{i,d}$ are non-increasing in $i$, it follows that the $T(\lambda_{i,d}^{-1},d,\vp)$ are non-decreasing in $i$ for $i \in \{1, \ldots, M(d)+1\}$.
-In particular, for  any $n \in \{N, \ldots, M(d)\}$
+In particular, for any \peter{$N\in\{1,\ldots,M(d)\}$ and any} $n \in \{N, \ldots, M(d)\}$
 \begin{align*}
@@
 \end{equation}
-Define the integers \fred{Only got here because we have to be careful with the domain of stuff}
+Define the integers \fred{Only got here because we have to be careful with the domain of stuff.} 
+\peter{[PETER: Adding something we might use in color, but not deleting any of the things we already have.]}
 \[
@@
 \]
-Thus, it follows by \eqref{eq:lambda_K4} that $\lambda_{i(\varepsilon,d,\vp),d} \le \varepsilon$.
+
+It follows by \eqref{eq:lambda_K4} that $\lambda_{i(\varepsilon,d,\vp),d} \le \varepsilon$.
 Note furthermore that we always have
@@
 since
-$T(\cdot,d,\vp)$ is non-decreasing.
-
-For $\varepsilon$ taking on all positive values, $i(\varepsilon,d,\vp)$ takes on all values greater than or equal to $i(\infty,d,\vp)$, so
+$T(\cdot,d,\vp)$ is non-decreasing
+\peter{{[Actually, the }same should hold $\forall (\varepsilon^{-1},d)\in\Omega$, right? ]} .
+
+For $\varepsilon$ taking on all positive values \peter{(values in $[E(d),\infty)$)}, $i(\varepsilon,d,\vp)$ takes on all values greater than or equal to $i(\infty,d,\vp)$
+\peter{(in $\{i(\infty,d,\vp),\ldots, i(E(d),d,\vp)\}$)}, so
 \[
@@
 \]
+\peter{[Could we not go through the same argument as below with $i$ being in the set $\{i(\infty,d,\vp),\ldots, i(E(d),d,\vp)\}$?]}
+
 This implies via our technical assumption \eqref{eq:ptauassume} that for any $\tau > 1$,

### 2023-06-04 alternative.tex
Updates from Overleaf

--- 2023-06-04 Older_versions/GeneralizedTractability_230501.tex
@@
 \[
- \sup_{d\in\naturals}\, d^{-q} \sum_{i=L_{(p,q)} d^{q}}^\infty (\min\{1,\lambda_{i,d}^p\})  < \infty \text{ for some } p,q \ge 0, L_{(p,q)} \in \naturals.
+ \sup_{d\in\naturals} \sum_{i=L_{(p,q)} d^{q}}^\infty (\min\{1,\lambda_{i,d}^p\}) d^{-q} < \infty \text{ for some } p,q \ge 0, L_{(p,q)} \in \naturals.
 \]
@@
 \[
- \sup_{d\in\naturals}\, d^{-q} \sum_{i=L_{(p,q)} d^{q}}^\infty [\min\{1,\log(1+\lambda_{i,d}\})]^p < \infty  \text{ for some } p,q \ge 0, L_{(p,q)} \in \naturals.
+ \sup_{d\in\naturals} \sum_{i=L_{(p,q)} d^{q}}^\infty [\min\{1,\log(1+\lambda_{i,d}\})]^p d^{-q} < \infty  \text{ for some } p,q \ge 0, L_{(p,q)} \in \naturals.
 \]
@@
 
+\begin{example}[Algebraic quasi-polynomial tractability] Here we consider another common notions of tractability.
+
+As defined in \cite{GW11}, we say that a problem is \emph{quasi-polynomially tractable (QPT)} if there exist two constants $C$, $t > 0$, such that
+\begin{equation}\label{expqpt}
+    \comp(\varepsilon,d) \leq C\exp\{t(1+\log(\varepsilon^{-1}))(1+\log(d))\}
+\end{equation}
+for all $\varepsilon \in (0,1]$ and $d\in\mathbb{N}$.\\
+
+\noindent Let the tractability function, $T$,
+be defined by
+\[
+ T(\varepsilon^{-1},d,\vp)= \exp\{p(1+\log(\max\{1,\varepsilon^{-1}\}))(1+\log (d))\}  \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty),
+\] where in this case $\vp = p$. This can be rewritten as 
+\[
+T(\varepsilon^{-1},d,\vp) = e^p[\max\{1,\varepsilon^{-1}\}]^{p(1+\log d)}d^p
+\]
+Observe that the function $T$ is a function of $\max\{1,\varepsilon^{-1}\}$ and $d$ which are, polynomial or not exponential in powers of $\max\{1,\varepsilon^{-1}\}$ and $d$.
+Hence we can apply Theorem \ref{thm_main_tract2} as follows.
+We have the following equivalent condition for quasi-polynomial tractability in the algebraic case
+\[
+\sup_{d\in\mathbb{N}}\sum_{i=Lp\,e^pd^{p}} \left(\min\{1,\lambda_{i,d}\} \right)^{p(1+\ln d)}e^{-p}d^{-p} < \infty \qquad \text{for some} p \geq 0, L_p \in \naturals.
+\]
+\end{example}
+\begin{example}[Exponential quasi-polynomial tractability]
+
+\noindent Suppose that the tractability function, $T$, is defined by
+\[
+ T(\varepsilon^{-1},d,\vp)= \exp\{p(1+\log(\max\{1,\log(1+\varepsilon^{-1})\}))(1+\log (d))\}  \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty),
+\] where in this case $\vp = p$. This can be rewritten as 
+\[
+T(\varepsilon^{-1},d,\vp) = e^p[\max\{1,\log(1+\varepsilon^{-1}\})]^{p(1+\log d)}d^p
+\]
+Observe that the function $T$ is a function of $\max\{1,\log(1+\varepsilon^{-1})\}$ and $d$.
+Hence we can apply Theorem \ref{thm_main_tract2} as follows.
+We have the following equivalent condition for quasi-polynomial tractability in the exponential case
+\[
+\sup_{d\in\mathbb{N}}\sum_{i=Lp\,e^pd^{p}} \left(\min\{1,\log(1+\lambda_{i,d})\} \right)^{p(1+\ln d)}e^{-p}d^{-p} < \infty
+\]
+\end{example}
+
+In the following we introduce two specific cases of tractability which depend on the form of the function $T$ (see \cite{}).
 \begin{example}[(Strong) Separable tractability]
@@
 \[
-\comp(\varepsilon,d) \leq  C_{\vp}\,\phi(\varepsilon^{-1},p)\, \psi(d,q)\qquad \forall \varepsilon >0, \, d\in\naturals.
+\comp(\varepsilon,d) \leq  C_{\vp}\,T(\varepsilon^{-1},d,\vp)\qquad \forall \varepsilon >0, \, d\in\naturals,
+\]
+that is
+\[
+\comp(\varepsilon,d) \leq \phi(\varepsilon^{-1},p)\, \psi(d,q) \qquad \forall \varepsilon >0, \, d\in\naturals.
 \]
@@
 \[
-\comp(\varepsilon,d) \leq C_{\vp}\phi(\varepsilon^{-1},p)\psi(1,q) \qquad \forall \varepsilon >0, \, d\in\naturals,
-\] where $\vp = (p,q)$. 
+\comp(\varepsilon,d) \leq C_{\vp}T(\varepsilon^{-1}, 1,\vp) \qquad \forall \varepsilon >0, \, d\in\naturals,
+\] where $\vp = p$. That is, we have
+\[
+\comp(\varepsilon,d) \leq \phi(\varepsilon^{-1},p)\qquad \forall \varepsilon >0, \, d\in\naturals.
+\]
 Furthermore, we assume the following as in \eqref{eq:Tconditions} and \eqref{eq:ptauassume}.
 \[
-\lim_{\varepsilon\rightarrow0}\phi(\varepsilon^{-1},p) = \infty \qquad \forall d\in\naturals, p >0.
+\lim_{\varepsilon\rightarrow0}T(\varepsilon^{-1},d,\vp) = \infty \qquad \forall d\in\naturals, \vp \in[0,\infty)^2.
 \]
@@
 \] 
-Additionally, we have the following technical assumptions. Suppose that, for any real $\tau_1, \tau_2>0$ and any $p,q>0$, we have that 
+{\color{red} Additionally, we have the following technical assumptions. Suppose that, for any real $\tau>0$ we have
 \begin{align*}
-     [\phi(\varepsilon^{-1},p)]^{\tau_1} &\le \hat{K}_{p,\tau_1} \phi (\varepsilon^{-1},\tau_1 p)\\
-      [\psi(d,q)]^{\tau_2} &\le \hat{K}_{q,\tau_2} \psi (d,\tau_2 q) \qquad \forall \, \varepsilon \in (0,\infty),\, d\in \naturals.
-\end{align*} where $L_{p,\tau_1}>0$ is a constant that may depend on $p$ and $\tau_1$, but is independent of $\varepsilon$, and where $L_{q,\tau_2}>0$ is a constant that may depend on $q$ and $\tau_2$, but is independent of $d$.
-\begin{align*}
-  [T(\varepsilon^{-1},d,\vp]^\tau \leq K_{\vp,\tau}T(\varepsilon^{-1},d,\tau\vp) \quad \forall \varepsilon \in (0,\infty),\, d\in \mathbb{N},\, \vp\in[0,\infty)^2, \tau >0\end{align*}
-
-Thus, Theorem \ref{thm_main_strong_tract2} yields the following equivalent condition for strongly separable tractability
-\begin{equation*} \label{eq:strong_tractiff}
-     \sup_{d \in \naturals} \sum_{i = L_p}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)} < \infty.
-\end{equation*}
+  [T(\varepsilon^{-1},d,\vp)]^\tau \leq K_{\vp,\tau}T(\varepsilon^{-1},d,\tau\vp) \quad \forall \varepsilon \in (0,\infty),\, d\in \mathbb{N},\, \vp\in[0,\infty)^2, \tau >0,\end{align*} that is for positive $K_{\vp,\tau}$ we have by definition
+  \[
+  [\phi(\varepsilon^{-1},p)\, \psi(d,q) ]^\tau \leq K_{\vp,\tau} \phi(\varepsilon^{-1},\tau p)\, \psi(d,\tau q) \]
+%Thus, Theorem \ref{thm_main_strong_tract2} yields the following equivalent condition for strongly separable tractability
+%\begin{equation*} \label{eq:strong_tractiff}    \sup_{d \in \naturals} \sum_{i = L_p}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)} < \infty.\end{equation*}
 Theorem \ref{thm_main_tract2} yields the following equivalent condition for 
@@
 \[
- \sup_{d \in \naturals} \frac{1}{\psi(d,q)} \sum_{i = L_{(p,q)\psi(d,q)}}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)} < \infty.
-\]
+ \sup_{d \in \naturals} \frac{1}{\psi(d,q)} \sum_{i = L_{\vp\psi(d,q)}}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)} < \infty.
+\]
+Observe that the only place where assumption (\ref{eq:ptauassume}) is used is in the necessary condition as follows.
+Suppose that we have
+$T$-separable tractability. That is, for some $\vp \ge \vzero$, there exists a positive constant $C_{\vp}$ such that
+\[
+\comp(\varepsilon,d)\le C_{\vp}\, T(\varepsilon^{-1},d,\vp) \qquad \forall \varepsilon > 0,  \ d \in \naturals.
+\]
+Since the sequence of eigenvalues $\lambda_{1,d}, \lambda_{2,d}, \ldots $ is non-increasing, we have
+\begin{equation}\label{eq:lambda_K4}
+	\lambda_{\lfloor C_{\vp}\, T(\varepsilon^{-1},d,\vp)\rfloor +1,d}\le \varepsilon \qquad \forall \varepsilon > 0,  \ d \in \naturals.
+\end{equation}
+Define the integers
+\[
+i (\varepsilon,d,\vp):= \lfloor C_{\vp}\, T(\varepsilon^{-1},d,\vp)\rfloor +1, \qquad
+i (\infty,d,\vp) := \lfloor C_{\vp}\, T(0,d,\vp)\rfloor +1 \ge 1.
+\]
+Thus, it follows by \eqref{eq:lambda_K4} that $\lambda_{i(\varepsilon,d,\vp),d} \le \varepsilon$.
+Note furthermore that we always have
+\[
+i(\varepsilon,d,\vp)\le C_{\vp}\, T(\varepsilon^{-1},d,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,d,\vp),d}^{-1},d,\vp)+1, \qquad \forall \varepsilon > 0, \ d \in \naturals,
+\]
+since
+$T(\cdot,d,\vp)$ is non-decreasing.
+
+For $\varepsilon$ taking on all positive values, $i(\varepsilon,d,\vp)$ takes on all values greater than or equal to $i(\infty,d,\vp)$, so
+\[
+i\le C_{\vp}\, T(\varepsilon^{-1},d,\vp)+1 \le C_{\vp} T(\lambda_{i,d}^{-1},d,\vp)+1, \qquad \forall i \ge i(\infty,d,\vp),  \ d \in \naturals.
+\] That is
+\[
+i \leq C_{\vp}\phi(\varepsilon^{-1},p)\psi(d,q)+1\leq C_{\vp}\phi(\lambda^{-1}_{i,d},p)\psi(d,q)+1
+\]
+This implies via our technical assumption \eqref{eq:ptauassume} that for any $\tau > 1$,
+\begin{gather*}
+	K_{\vp,\tau}\,\phi (\lambda_{i,d}^{-1},\tau p)\psi(d,\tau q) \ge
+	[\phi(\lambda_{i,d}^{-1}, p)\psi(d,q)]^\tau
+	\ge
+	\left[\frac{(i-1)}{C_{\vp}}\right]^\tau \qquad \forall i \ge i(\infty,d,\vp),  \ d \in \naturals, \\
+	 \frac{1}{\phi (\lambda_{i,d}^{-1},\tau p)\psi(d,\tau q) } \le
+	\frac{K_{\vp,\tau}\, C_{\vp}^\tau}{(i-1)^\tau}\qquad \forall i \ge \max\{i(\infty,\vp),2\},  \ d \in \naturals.
+\end{gather*}
+
+Let $\vp' = (\tau p,\tau q)$.
+Note that $i(\infty,d,\cdot)$ is non-decreasing.
+Summing both sides of the latter inequality over $i$ from $i(\infty,d,\vp') + 1 \ge i(\infty,d, \vp) + 1 \ge 2$ to $\infty$ it follows that
+\begin{equation*}
+	\sup_{d\in\naturals} \, \, \sum_{i=i (\infty,d,\vp')+1}^\infty \frac{1}{T (\lambda_{i,d}^{-1},d,\vp')}
+	 \le  K_{\vp,\tau}\, C_{\vp}^\tau
+	\sum_{i=2}^\infty \frac{1}{(i-1)^\tau} \\
+	 \le  K_{\vp,\tau}\, C_{\vp}^\tau
+	\zeta (\tau)  < \infty,
+\end{equation*}
+where $\zeta$ denotes the Riemann zeta function.
+
+Note now that, for any $d\in\naturals$,
+\begin{align*}
+ i(\infty,d,\vp') +1  & = \lfloor C_{\vp'}\, T(0,d,\vp')\rfloor +2 \le  \left[C_{\vp'} + \frac{2}{T(0,d,\vp')}   \right]\, T(0,d,\vp')\\
+ & \le  \underbrace{\left[C_{\vp'} + \frac{2}{T(0,1,\vp')}   \right]}_{=:L_{\vp'}}\, T(0,d,\vp')
+ \le \lceil L_{\vp'} T(0,d,\vp')\rceil .
+\end{align*}
+For this choice of $L_{\vp'}$ we have
+\[
+\sup_{d\in\naturals}\,\, \sum_{i=\lceil L(\vp') T(0,d,\vp')\rceil}^\infty \frac{1}{T(\lambda_{i,d}^{-1},d, \vp')}
+\le
+\sup_{d\in\naturals} \, \, \sum_{i=i (\infty,d,\vp')+1}^\infty \frac{1}{T (\lambda_{i,d}^{-1},d,\vp')} <
+\infty.
+\]
+This yields \eqref{eq:tractiff4} with $\vp$ replaced by $\vp'$, so we see the necessity of $\eqref{eq:tractiff4}$.
+
 %As the name implies, the roles of $\varepsilon^{-1}$ and $d$ are separated. 
-
+}
 \end{example}
-
 \begin{example}[Non-separable tractability]
@@
 \[
-\sup_{d\in\mathbb{N}}\sum_{i=Lp\,\psi(d)} \phi(\lambda_{i,d})\psi(d) < \infty \qquad \text{for some} p \geq 0, L_p \in \naturals.
-\]
-We have the following special cases. \end{example}
-\begin{example}[Algebraic quasi-polynomial tractability] Here we consider another common notions of tractability.
-
-As defined in \cite{GW11}, we say that a problem is \emph{quasi-polynomially tractable (QPT)} if there exist two constants $C$, $t > 0$, such that
-\begin{equation}\label{expqpt}
-    \comp(\varepsilon,d) \leq C\exp\{t(1+\log(\varepsilon^{-1}))(1+\log(d))\}
-\end{equation}
-for all $\varepsilon \in (0,1]$ and $d\in\mathbb{N}$.\\
-
-\noindent Let the tractability function, $T$,
-be defined by
-\[
- T(\varepsilon^{-1},d,\vp)= \exp\{p(1+\log(\max\{1,\varepsilon^{-1}\}))(1+\log (d))\}  \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty),
-\] where in this case $\vp = p$. This can be rewritten as 
-\[
-T(\varepsilon^{-1},d,\vp) = e^p[\max\{1,\varepsilon^{-1}\}]^{p(1+\log d)}d^p
-\]
-Observe that the function $T$ is a function of $\max\{1,\varepsilon^{-1}\}$ and $d$ which are, polynomial or not exponential in powers of $\max\{1,\varepsilon^{-1}\}$ and $d$.
-Hence we can apply Theorem \ref{thm_main_tract2} as follows.
-We have the following equivalent condition for quasi-polynomial tractability in the algebraic case
-\[
-\sup_{d\in\mathbb{N}}\frac{1}{d^p}\sum_{i=Lp\,d^{p}} \left(\min\{1,\lambda_{i,d}\} \right)^{p(1+\ln d)} < \infty \qquad \text{for some } p \geq 0, L_p \in \naturals.\]
+\sup_{d\in\mathbb{N}}\sum_{i=Lp\,e^pd^{p}} \left(\min\{1,\lambda_{i,d}\} \right)^{p(1+\ln d)}e^{-p}d^{-p} < \infty \qquad \text{for some} p \geq 0, L_p \in \naturals.
+\]
+We observe that Example 5 is a special case  where in this case the function $\phi(\varepsilon^{-1})= 1+\log(\max\{1,\varepsilon^{-1}\})$ and $\psi(d) = 1+\log(d)$.
 \end{example}
-\begin{example}[Exponential quasi-polynomial tractability]
-
-\noindent Suppose that the tractability function, $T$, is defined by
-\[
- T(\varepsilon^{-1},d,\vp)= \exp\{p(1+\log(\max\{1,\log(1+\varepsilon^{-1})\}))(1+\log (d))\}  \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty),
-\] where in this case $\vp = p$. This can be rewritten as 
-\[
-T(\varepsilon^{-1},d,\vp) = e^p[\max\{1,\log(1+\varepsilon^{-1}\})]^{p(1+\log d)}d^p
-\]
-Observe that the function $T$ is a function of $\max\{1,\log(1+\varepsilon^{-1})\}$ and $d$.
-Hence we can apply Theorem \ref{thm_main_tract2} as follows.
-We have the following equivalent condition for quasi-polynomial tractability in the exponential case
-\[
-\sup_{d\in\mathbb{N}}\sum_{i=Lp\,e^pd^{p}} \left(\min\{1,\log(1+\lambda_{i,d})\} \right)^{p(1+\ln d)}e^{-p}d^{-p} < \infty
-\]
-\end{example}
-
-%In the following we introduce two specific cases of tractability which depend on the form of the function $T$ (see \cite{}).
 

### 2023-06-04 GeneralizedTractability_230529.tex
Updates from Overleaf

@@
 
-Since the $\lambda_{i,d}$ are non-increasing in $i$, it follows that the $T(\lambda_{i,d}^{-1},d,\vp)$ are non-decreasing in $i$ for $i \in \{1, \ldots, M(d)+1\}$.
-In particular, for any \peter{$N\in\{1,\ldots,M(d)\}$ and any} $n \in \{N, \ldots, M(d)\}$
+Define the interval
+\begin{equation} \label{eq:hIdef}
+\hI_{d}:=\begin{cases} 
+\{1,\ldots, M(d)\}, & M(d) < \infty, \\
+\naturals, & M(d) = \infty.
+\end{cases}
+\end{equation}
+Since the $\lambda_{i,d}$ are non-increasing in $i$, it follows that the $T(\lambda_{\cdot,d}^{-1},d,\vp)$ is non-decreasing. For any $N\in \hI_d$ and any $n \in \hI_d \setminus \{1, \ldots, N-1\}$,
 \begin{align*}
@@
    \implies   \frac{1}{T(\lambda_{n+1, d}^{-1},d,\vp)} \le
-   \frac{1}{n-N+1} \sum_{i=N}^{M(d)} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp) } \le \frac{1}{T(\varepsilon^{-1},d,\vp)} \\ \forall d, n, N \in \naturals.
+   \frac{1}{n-N+1} \sum_{i=N}^{M(d)} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp) } \le \frac{1}{T(\varepsilon^{-1},d,\vp)} \\ \forall d \in \naturals, \ N \in \hI_d, \ n \in \hI_d \setminus \{1, \ldots, N-1\}.
 \end{multline}
@@
 This upper bound on $i$ in terms of $T(\lambda_{i,d}^{-1},d,\vp)$ implies via our technical assumption \eqref{eq:ptauassume} that for any $\tau > 1$,
-\[
+\begin{equation}\label{eq:restrictKfive}
 	K_{\vp,\tau}\,T (\lambda_{i,d}^{-1},d,\tau \vp) \ge
@@
 	\left[\frac{(i-1)}{C_{\vp}}\right]^\tau \qquad  \forall i\in I_{d},  \ d \in \naturals.
- \]
+ \end{equation}
 To carry the argument further, we need to show that the interval $I_d$ contains the interval
@@
 \]
-This means that $i(E(d),d,\vp)-1 \ge M(d)+1$, and so $I_d \ge \tI_d$
-
-\[
-\lambda_{i(E(d),d,\vp),d} \le \lambda_{M(d)+2} \le E(d) < \lambda_{M(d)+1,d} 
-\]
-
-Choose an $\varepsilon \in (E(d),\infty)$ such that $i(\varepsilon,d,\vp) = i(E(d),d,\vp) - 1$.  It follows from \eqref{eq:lambda_K4} that
-\[
-\lambda_{i(\varepsilon,d,\vp)} \le \varepsilon < E(d) \le \lambda_{i(\varepsilon,d,\vp)} + 1
-\]
-
-Note that, for any $\delta>0$,
-\[
-\lambda_{\lfloor C_{\vp}\, T((E(d) + \delta)^{-1},d,\vp)\rfloor +1} \le E(d) + \delta, 
-\]
-\peter{Furthermore, define
-\[
-i (E(d),d,\vp):=\lim_{\delta\to 0}\, i (E(d)+\delta,d,\vp)
-= \lim_{\delta\to 0}\, \lfloor C_{\vp}\, T((E(d) + \delta)^{-1},d,\vp)\rfloor +1. 
-\]
-Note that, for any $\delta>0$,
-\[
-\lambda_{\lfloor C_{\vp}\, T((E(d) + \delta)^{-1},d,\vp)\rfloor +1} \le E(d) + \delta, 
-\]
-and therefore, for $\delta\to 0$, we obtain
-\[
-\lambda_{i (E(d),d,\vp)} \le E(d). 
-\]
-On the other hand, by definition of $M(d)$, $M(d)$ is minimal such that 
-\[
-\lambda_{M(d)+2}\le E(d).
-\]
-This implies that 
-\[
-M(d) < M(d) +2 \le i (E(d),d,\vp).
-\]
-
-}
-
-For $\varepsilon$ taking on all \peter{values in $(E(d),\infty)$}, $i(\varepsilon,d,\vp)$ takes on all values 
-\peter{in 
-\[
-I_{E(d),d}:=\{i(\infty,d,\vp),\ldots, i(E(d),d,\vp)\}
-\]
-} 
-so
-\[
-i\le C_{\vp}\, T(\varepsilon^{-1},d,\vp)+1 \le C_{\vp} T(\lambda_{i,d}^{-1},d,\vp)+1, \qquad \peter{\forall i\in I_{E(d),d}},  \ d \in \naturals.
-\]
-
-This implies via our technical assumption \eqref{eq:ptauassume} that for any $\tau > 1$,
-\[
-	K_{\vp,\tau}\,T (\lambda_{i,d}^{-1},d,\tau \vp) \ge
-	[T(\lambda_{i,d}^{-1},d, \vp)]^\tau
-	\ge
-	\left[\frac{(i-1)}{C_{\vp}}\right]^\tau \qquad  \peter{\forall i\in I_{E(d),d}},  \ d \in \naturals,
- \]
+This means that $i(E(d),d,\vp)-1 \ge M(d)+1$, and so $I_d \supseteq \tI_d$.
+
  and this implies

### 2023-06-05 GeneralizedTractability_230529.tex
Updates from Overleaf

@@
 \DeclareMathOperator{\APP}{APP}
+\renewcommand{\hI}{\ci}
 
@@
 
-Suppose that the domain of interest $(\varepsilon^{-1},d)$ is not all of $(0,\infty) \times \naturals$ but given by 
+Suppose that the domain of interest $(\varepsilon^{-1},d)$ is not all of $(0,\infty) \times \naturals$ but some subset
 \begin{equation}
-    \Omega  = \{(\varepsilon^{-1},d) : \varepsilon \peter{> E(d) \ge 0}, \ d \in \naturals \},
-\end{equation}
-%where $E$ is a non-increasing \peter{[{is this a necessary assumption?}]} function.  
+    \Omega  := \{(\varepsilon^{-1},d) : \varepsilon > E(d) \ge 0, \ d \in \naturals \}, \qquad E : \naturals \to [0,\infty).
+\end{equation}
+We then expect that the equivalent condition for (strong) tractability will be similar in form, but weaker than, the conditions in Theorems  \ref{thm_main_strong_tract2} and \ref{thm_main_tract2}.
 A problem is \peter{strongly}
@@
 \end{equation}
-\peter{[I am wondering whether this makes sense if $E$ depends on $d$? Do Gnewuch and Wo\'{z}niakowski allow dependence of $E$ on $d$?]}
-
-\peter{
+%\peter{[I am wondering whether this makes sense if $E$ depends on $d$? Do Gnewuch and Wo\'{z}niakowski allow dependence of $E$ on $d$?]}
 A problem is 
@@
 \end{equation}
-}
 
@@
     M(d) := \begin{cases}
-        \max\{n : \lambda_{n+1,d} > E(d)\}, & E(d) > 0, \\
+        \max\{n : \lambda_{n,d} > E(d)\}, & E(d) > 0, \\
         \infty, & E(d) = 0.
@@
 \begin{cases}
-\lambda_{1,d}\ge  \cdots \ge \lambda_{M(d)+1,d} > E(d) \ge\lambda_{M(d)+2,d}, \quad
-(\lambda_{1,d}^{-1},d), \ldots, (\lambda^{-1}_{M(d)+1,d},d)  \in \Omega, & E(d) > 0, \\
+\lambda_{1,d}\ge  \cdots \ge \lambda_{M(d),d} > E(d) \ge\lambda_{M(d)+1,d}, \quad
+(\lambda_{1,d}^{-1},d), \ldots, (\lambda^{-1}_{M(d),d},d)  \in \Omega, & E(d) > 0, \\
 \lambda_{1,d}\ge \lambda_{2,d}\ge \cdots  > 0, \quad
@@
 \]
+Also, for each $d \in \naturals$ define the interval 
+\begin{equation} \label{eq:hIdef}
+\hI_{d}:=\begin{cases} 
+\{1,\ldots, M(d)\}, & M(d) < \infty, \\
+\naturals, & M(d) = \infty.
+\end{cases}
+\end{equation}
+From the definition of $M(d)$ it follows that 
+\[
+\comp(\varepsilon,d) \in \hI_d \qquad \forall (\varepsilon^{-1},d) \in \Omega.
+\]
+
+\begin{theorem}\label{thm_main_rest_strong_tract}
+Let $T$ be a tractability function as specified in \eqref{eq:Tspec} and satisfying \eqref{eq:Tconditions} and \eqref{eq:ptauassume}.
+A problem is strongly $T$-tractable \emph{on the restricted domain $\Omega$} iff there exists $\vp \in [\vzero, \boldsymbol{\infty})$ and an integer $L_{\vp} > 0$ such that
+\begin{equation} \label{eq:strong_rest_tractiff}
+     S_{\vp}:=\sup_{d \in \naturals} \sum_{i = L_{\vp}}^{M(d)} \frac{1}{T(\lambda_{i,d}^{-1},1,\vp)} < \infty.
+\end{equation}
+If \eqref{eq:strong_rest_tractiff} holds for some $\vp$, let  $\widetilde{\cp}_{\textup{rstrct}} : = \{\vp^* : \eqref{eq:strong_rest_tractiff} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty})\}$.
+Then $\cp_{\textup{rstrct}} = \widetilde{\cp}_{\textup{rstrct}}$, and the set of optimal strong tractability parameters on the restricted domain is
+\[
+	\cp_{\textup{rsopt}} =
+	\{\vp^* \in \widetilde{\cp}_{\textup{rstrct}} :  \vp^* \notin [\widetilde{\vp},\boldsymbol{\infty}) \ \forall \widetilde{\vp}\in  \widetilde{\cp}_{\textup{rstrct}} \setminus \{\vp^*\} \}.
+\]
+\end{theorem}
+
+\begin{proof}
+\textbf{Sufficient condition:}\newline
+We make the first part of the argument in some generality so that it can be reused in the proof of Theorem \ref{thm_main_tract2} for tractability.  Fix any $\varepsilon > 0$ and any $d \in \naturals$.
+
+Since the $\lambda_{i,d}$ are non-increasing in $i$, it follows that the $T(\lambda_{i,d}^{-1},d',\vp)$ are non-decreasing in $i$ for any $d'\in\naturals$.
+In particular, for  any $N\in\naturals$ with $n\ge N$, we have
+\begin{align*}
+    \lambda_{n+1,d} \le \lambda_{n,d} \le \cdots \le \lambda_{N,d}
+    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d',\vp)} \le \frac{1}{T(\lambda_{n, d}^{-1},d',\vp)} \le \cdots \le \frac{1}{T(\lambda_{N, d}^{-1},d',\vp)} \\
+     \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d',\vp) }
+    \le &\frac{1}{n-N+1} \sum_{i=N}^n  \frac{1}{T(\lambda_{i, d}^{-1},d',\vp) }
+    \le \frac{1}{n-N+1} \sum_{i=N}^\infty  \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)}.
+\end{align*}
+Thus, we can conclude from the previous line that
+\begin{multline} \label{eq:implicate_a}
+    n - N +1 \ge T(\varepsilon^{-1},d',\vp) \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} \\
+   \implies   \frac{1}{T(\lambda_{n+1, d}^{-1},d',\vp)} \le
+   \frac{1}{n-N+1} \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d',\vp) } \le \frac{1}{T(\varepsilon^{-1},d',\vp)} \\ \forall d', n, N \in \naturals.
+\end{multline}
+We note that the left side of the implication implies $n \ge N$ automatically since $n$ is an integer  $n - N +1$ is assumed to be positive.
+
+Moreover, given that $T$ is increasing in its arguments, we have the following equivalent expression for the complexity via \eqref{eq:comp_def}:
+\begin{align} %\label{eq:comp_equiv}
+	\nonumber
+	\comp(\varepsilon, d) & = \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon\} \\
+	\nonumber
+	& = \min \biggl\{n \in \natzero : \frac{1}{T(\lambda_{n+1,d}^{-1},d',\vp)}\le \frac{1}{T(\varepsilon^{-1},d',\vp) }\biggr\} \qquad  \forall d'\in \naturals\\
+	\nonumber
+	& \le  \min \biggl\{n \in \natzero : n \ge N - 1 + T(\varepsilon^{-1},d',\vp) \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} \biggr\} \;  \forall  d', N \in \naturals, \quad \text{by \eqref{eq:implicate_a}} \\
+	& \le  T(\varepsilon^{-1},d',\vp) \Biggl [\frac{N}{T(\varepsilon^{-1},d',\vp)}  +  \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} \Biggr] \quad \forall  d', N \in \naturals.
+\label{eq:compUP}
+\end{align}
+
+Now we take this upper bound further, specializing to the case of $d'=1$ and $N=L_{\vp}$:
+\begin{align*}
+       \comp(\varepsilon,d)
+       & \le T(\varepsilon^{-1},1, \vp) \Biggl [ \frac{L_{\vp}}{T(\varepsilon^{-1},1, \vp)}  + \underbrace{\sum_{i=L_{\vp}}^\infty \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}}_{\le S_{\vp} <\infty\ \text{by \eqref{eq:strong_tractiff3}} }
+        \Biggr] \\
+       & \le T(\varepsilon^{-1},1,\vp) \underbrace{\left[\frac{L_{\vp}}{T(0,1, \vp)} + S_{\vp} \right]}_{=:C_{\vp}}
+       \qquad \text{by \eqref{eq:Tnondecreasing}}\\
+       & =  C_{\vp}T(\varepsilon^{-1},1,\vp).
+%       & \le \underbrace{2 C_{1,\vp}}_{\text{since } T(\varepsilon^{-1},1,\vp) \ge 1} T(\varepsilon^{-1},1,\vp)
+%       = \underbrace{C_{\vp}}_{:=2 C_{1,\vp}}T(\varepsilon^{-1},1,\vp).
+\end{align*}
+This means that we have strong $T$-tractability via \eqref{eq:strong_tract_def}, and verifies the sufficiency of \eqref{eq:strong_tractiff3}.
+
+\bigskip
+\noindent \textbf{Necessary condition:} \\
+Suppose that we have strong
+$T$-tractability as defined in \eqref{eq:strong_tract_def}. That is, for some $\vp \ge \vzero$ there exists a positive constant $C_{\vp}$ such that
+\[
+\comp(\varepsilon,d)\le C_{\vp}\, T(\varepsilon^{-1},1,\vp)
+\qquad \forall \varepsilon > 0, \ d \in \mathbb{N}.
+\]
+Since the sequence of eigenvalues $\lambda_{1,d}, \lambda_{2,d}, \ldots $ is non-increasing, we have
+\begin{equation}\label{eq:lambda_K_strong3}
+\lambda_{\lfloor C_{\vp}\, T(\varepsilon^{-1},1,\vp)\rfloor +1,d}\le \varepsilon \qquad \forall \varepsilon > 0, \ d \in \mathbb{N}.
+\end{equation}
+
+Define
+\[
+i(\varepsilon,\vp):= \lfloor C_{\vp}\, T(\varepsilon^{-1},1,\vp)\rfloor +1, \quad
+i(\infty,\vp) = \lim_{\varepsilon \to \infty}  i(\varepsilon,\vp) \ge 1 .
+\]
+Thus, it follows by \eqref{eq:lambda_K_strong3} that $\lambda_{i(\varepsilon,\vp),d} \le \varepsilon$.
+Note furthermore that we always have
+\[
+i(\varepsilon,\vp)\le C_{\vp}\, T(\varepsilon^{-1},1,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,\vp),d}^{-1},1,\vp)+1, \qquad \forall \varepsilon > 0, \ d \in \mathbb{N},
+\]
+since
+$T(\cdot,1, \vp)$ is non-decreasing.
+
+For $\varepsilon$ taking on all positive values, $i(\varepsilon,\vp)$ takes on all values greater than or equal to $i(\infty,\vp)$, so
+\[
+i\le C_{\vp} T(\lambda_{i,d}^{-1},1,\vp)+1, \qquad \forall i \ge i(\infty,\vp), \ d \in \naturals.
+\]
+This implies via our technical assumption \eqref{eq:ptauassume} that
+\begin{gather*}
+ K_{\vp,\tau}\,T (\lambda_{i,d}^{-1},1,\tau \vp) \ge
+ [T(\lambda_{i,d}^{-1},1, \vp)]^\tau
+ \ge
+  \left[\frac{(i-1)}{C_{\vp}}\right]^\tau \qquad \forall i \ge i(\infty,\vp)), \ d \in \naturals, \\
+ \frac{1}{T (\lambda_{i,d}^{-1},1,\tau \vp)} \le
+\frac{K_{\vp,\tau}\, C_{\vp}^\tau}{(i-1)^\tau}\qquad \forall i \ge \max\{i(\infty,\vp),2\}), \ d \in \naturals .
+\end{gather*}
+Summing both sides of this last inequality over $i$ from $i(\infty,\vp) +1 \ge 2$ to $\vinfty$ yields
+\begin{equation*}
+\sup_{d\in\naturals} \sum_{i=i(\infty,\vp) +1 }^\infty \frac{1}{T (\lambda_{i,d}^{-1},1, \tau \vp)}
+ \le  K_{\vp,\tau}\, C_{\vp}^\tau
+\sum_{i=2}^\infty \frac{1}{(i-1)^\tau} \\
+ \le K_{\vp,\tau}\, C_{\vp}^\tau
+\zeta (\tau)  < \infty,
+\end{equation*}
+where $\zeta$ denotes the Riemann zeta function.
+This yields \eqref{eq:strong_tractiff3} with $\vp$ replaced by $\vp' = \tau \vp$ and $L_{\vp'} = i(\infty,\vp) +1$, and so we see the necessity of $\eqref{eq:strong_tractiff3}$.
+
+\bigskip
+\noindent \textbf{Optimality:} \\
+To complete the proof, we must show that $\cp_{\textup{strct}} = \widetilde{\cp}_{\textup{strct}}$.
+Then, the expression for  $\cp_{\textup{sopt}}$ automatically follows from its definition in \eqref{eq:Psoptdef}.
+
+First we show  that if $\vp^* \in \cp_{\textup{strct}}$, then $\vp^* \in \widetilde{\cp}_{\textup{strct}}$.
+If $\vp^* \in \cp_{\textup{strct}}$, then \eqref{eq:strong_tract_def} must hold for all $\vp' \in (\vp^*,\vinfty)$.
+For any $\vp' \in (\vp^*,\vinfty)$, we may choose $\vp$ and $\tau$ such that $\vp^* < \vp < \vp' = \tau \vp$.
+Since $\vp > \vp^*$, \eqref{eq:strong_tract_def} also holds for $\vp$, and it follows that \eqref{eq:strong_tractiff3} must hold for $\vp'$ by the proof of necessity above.
+Thus, $\vp^* \in \widetilde{\cp}_{\textup{strct}}$.
+
+Next we show that if $\vp^* \in \widetilde{\cp}_{\textup{strct}}$, then $\vp^* \in \cp_{\textup{strct}}$.
+If $\vp^* \in \widetilde{\cp}_{\textup{strct}}$, then \eqref{eq:strong_tractiff3}  holds for all $\vp \in (\vp^*,\vinfty)$.
+By the argument to prove the sufficient condition above, it follows that \eqref{eq:strong_tract_def} must also hold for all $\vp \in (\vp^*,\vinfty)$.
+Thus, $\vp^* \in \cp_{\textup{strct}}$.
+
+\bigskip
+
+\noindent This concludes the proof of  Theorem \ref{thm_main_strong_tract2}.
+
+\end{proof}
 
@@
 
-Moreover, given that $T$ is increasing in its arguments, we have the following equivalent expression for the complexity via \eqref{eq:comp_def}:
+Moreover, given that $T$ is increasing in its arguments, we have the following equivalent expression for the information complexity via \eqref{eq:comp_def} for all $(\varepsilon^{-1},d) \in \Omega$:
 \begin{align} %\label{eq:comp_equiv}
 	\nonumber
-	\comp(\varepsilon, d) & = \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon\} \\
+	\comp(\varepsilon, d) & = \min \{n \in \hI_d : \lambda_{n+1, d} \le \varepsilon\} \\
 	\nonumber

### 2023-06-05 GeneralizedTractability_230529.tex
Updates from Overleaf

@@
 
+\begin{definition}
     A problem is defined as $T$-tractable with parameter $\vp$ iff there exists a positive constant $C_{\vp}$, which is independent of $\varepsilon$ and $d$, such that
@@
 \end{equation}
-In this article we allow $\vp$ to be a scalar or vector as the situation dictates.
+We allow $\vp$ to be a scalar or vector as the situation dictates.
+\end{definition}
 
@@
 \end{equation*}
+
+\begin{definition}
     The  set of optimal parameters is defined as all of those parameters satisfying the (strong) tractability conditions that are not greater than or equal to others:
@@
 \end{gather}
+\end{definition}
 
@@
 \begin{equation}
-    \Omega  := \{(\varepsilon^{-1},d) : \varepsilon > E(d) \ge 0, \ d \in \naturals \}, \qquad E : \naturals \to [0,\infty).
-\end{equation}
-We then expect that the equivalent condition for (strong) tractability will be similar in form, but weaker than, the conditions in Theorems  \ref{thm_main_strong_tract2} and \ref{thm_main_tract2}.
-A problem is \peter{strongly}
+    \Omega  := \{(\varepsilon^{-1},d) : \varepsilon > E(d), \ d \in \naturals \}, \qquad \text{where }E : \naturals \to [0,\infty).
+\end{equation}
+We then expect that the equivalent conditions for (strong) tractability will be similar in form, but weaker than, the conditions in Theorems  \ref{thm_main_strong_tract2} and \ref{thm_main_tract2}.
+
+\begin{definition}
+    A problem is strongly
 $T$-tractable with parameter $\vp$ \emph{on the restricted domain $\Omega$} iff the complexity is independent of the dimension of the problem, that is, there exists a positive constant $C_{\vp}$, again independent of $\varepsilon$ and $d$, such that
@@
 \end{equation}
-
-Define 
+ Define the closures of the sets of parameters for which our (strong) tractability conditions hold:
+\begin{equation*}
+	\cp_{\textup{rtrct}} : = \{\vp^* : \eqref{eq:rest_tract_def} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty})\}, \qquad
+	\cp_{\textup{rstrct}} : = \{\vp^* : \eqref{eq:rest_strong_tract_def} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty})\}.
+\end{equation*}
+    The  set of optimal parameters is defined as all of those parameters satisfying the (strong) tractability conditions that are not greater than or equal to others:
+\begin{gather}
+	\label{eq:Poptdef}
+	\mathcal{P}_{\textup{ropt}} : = \{\vp^* \in \cp_{\textup{rtrct}} :  \vp^* \notin [\vp,\boldsymbol{\infty}) \ \forall \vp \in  \cp_{\textup{rtrct}} \setminus \{\vp^*\} \}, \\
+	\label{eq:Psoptdef}
+	\mathcal{P}_{\textup{rsopt}} : = \{\vp^* \in \cp_{\textup{rstrct}} :  \vp^* \notin [\vp,\boldsymbol{\infty}) \ \forall \vp \in  \cp_{\textup{rstrct}} \setminus \{\vp^*\} \}.
+\end{gather}
+\end{definition}
+
+Define $M: \naturals \to \natzero \cup \{\infty\}$
 \begin{equation} \label{eq:Mddef}
     M(d) := \begin{cases}
-        \max\{n : \lambda_{n,d} > E(d)\}, & E(d) > 0, \\
+        \min\{n \in \natzero : \lambda_{n+1,d} \le E(d)\}, & E(d) > 0, \\
         \infty, & E(d) = 0.
@@
 \[
-\begin{cases}
-\lambda_{1,d}\ge  \cdots \ge \lambda_{M(d),d} > E(d) \ge\lambda_{M(d)+1,d}, \quad
-(\lambda_{1,d}^{-1},d), \ldots, (\lambda^{-1}_{M(d),d},d)  \in \Omega, & E(d) > 0, \\
-\lambda_{1,d}\ge \lambda_{2,d}\ge \cdots  > 0, \quad
-(\lambda_{1,d}^{-1},d), (\lambda_{2,d}^{-1},d), \ldots \in \Omega, & E(d) = 0.
-\end{cases}
+\left \{
+\begin{array}{lll}
+&(\lambda_{1,d}^{-1},d), (\lambda_{2,d}^{-1},d), \ldots \notin \Omega, & M(d) = 0, \\
+\lambda_{1,d}\ge  \cdots \ge \lambda_{M(d),d} > E(d) \ge\lambda_{M(d)+1,d}, &
+(\lambda_{1,d}^{-1},d), \ldots, (\lambda^{-1}_{M(d),d},d)  \in \Omega, & 0 < M(d) < \infty, \\
+&
+(\lambda_{1,d}^{-1},d), (\lambda_{2,d}^{-1},d), \ldots \in \Omega, & M(d) = \infty.
+\end{array}
+\right .
 \]
@@
 \hI_{d}:=\begin{cases} 
-\{1,\ldots, M(d)\}, & M(d) < \infty, \\
+\emptyset, & M(d) = 0, \\
+\{1,\ldots, M(d)\}, & 0 < M(d) < \infty, \\
 \naturals, & M(d) = \infty.
@@
 \end{equation}
-From the definition of $M(d)$ it follows that 
+From the definition of $M(d)$ it follows that $(\lambda_{i,d}^{-1},d) \in \Omega  \iff i \in \hI_d$, and
 \[
@@
 \]
+
+The equivalent conditions for (strong) $T$-tractability on a restricted domain in Theorems \ref{thm_main_rest_strong_tract} and \ref{thm_main_rest_tract} mimic the conditions given in Theorems \ref{thm_main_strong_tract2} and \ref{thm_main_tract2}, except that the upper limits on the sums now correspond to $M(d)$ rather than $\infty$.
+The proofs are a bit more delicate, but similar arguments are used.
+
+We note that it may be possible to define $\Omega$ such that $\lambda_{1,d} > E(d)$ for all $d \in \naturals$.
+In this case, $M(d) = 0$ for all $d \in \naturals$, the equivalent conditions for (strong) tractability are trivially satisfied, and the zero algorithm satisfies the error tolerance.
 
@@
 \end{equation}
+By convention, if $M(d) = 0$, the sum is zero.
+
 If \eqref{eq:strong_rest_tractiff} holds for some $\vp$, let  $\widetilde{\cp}_{\textup{rstrct}} : = \{\vp^* : \eqref{eq:strong_rest_tractiff} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty})\}$.
@@
 \textbf{Sufficient condition:}\newline
-We make the first part of the argument in some generality so that it can be reused in the proof of Theorem \ref{thm_main_tract2} for tractability.  Fix any $\varepsilon > 0$ and any $d \in \naturals$.
+Following the argument for the sufficient condition in Theorem \ref{thm_main_strong_tract2} it follows that for all $d' \in \naturals$ and integers $n$ and $N$ with $1 \le N \le n \le M(d)$
 
@@
 
-\begin{theorem}\label{thm_main_rest_tract2}
+\begin{theorem}\label{thm_main_rest_tract}
 Let $T$ be a tractability function as specified in \eqref{eq:Tspec} and satisfying \eqref{eq:Tconditions} and \eqref{eq:ptauassume}.

### 2023-06-05 GeneralizedTractability_230529.tex
Updates from Overleaf

@@
 \textbf{Sufficient condition:}\newline
-Following the argument for the sufficient condition in Theorem \ref{thm_main_strong_tract2} it follows that for all $d' \in \naturals$ and integers $n$ and $N$ with $1 \le N \le n \le M(d)$
-
-Since the $\lambda_{i,d}$ are non-increasing in $i$, it follows that the $T(\lambda_{i,d}^{-1},d',\vp)$ are non-decreasing in $i$ for any $d'\in\naturals$.
-In particular, for  any $N\in\naturals$ with $n\ge N$, we have
+Fix $d$.
+For the case where $M(d)> 0$, following the argument for the sufficient condition in Theorem \ref{thm_main_strong_tract2} it follows that for all $d' \in \naturals$ and integers $n$ and $N$ with $1 \le N \le n \le M(d)$, we have
 \begin{align*}
@@
     \le &\frac{1}{n-N+1} \sum_{i=N}^n  \frac{1}{T(\lambda_{i, d}^{-1},d',\vp) }
-    \le \frac{1}{n-N+1} \sum_{i=N}^\infty  \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)}.
+    \le \frac{1}{n-N+1} \sum_{i=N}^{M(d)}  \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)}.
 \end{align*}
 Thus, we can conclude from the previous line that
-\begin{multline} \label{eq:implicate_a}
-    n - N +1 \ge T(\varepsilon^{-1},d',\vp) \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} \\
+\begin{multline} \label{eq:implicate_a_rest}
+    n - N +1 \ge T(\varepsilon^{-1},d',\vp) \sum_{i=N}^{M(d)} \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} \\
    \implies   \frac{1}{T(\lambda_{n+1, d}^{-1},d',\vp)} \le
-   \frac{1}{n-N+1} \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d',\vp) } \le \frac{1}{T(\varepsilon^{-1},d',\vp)} \\ \forall d', n, N \in \naturals.
+   \frac{1}{n-N+1} \sum_{i=N}^{M(d)} \frac{1}{T(\lambda_{i, d}^{-1},d',\vp) } \le \frac{1}{T(\varepsilon^{-1},d',\vp)} \\ \forall d', n, N \in \naturals, \ N \le n \le M(d).
 \end{multline}
-We note that the left side of the implication implies $n \ge N$ automatically since $n$ is an integer  $n - N +1$ is assumed to be positive.
 

### 2023-06-06 GeneralizedTractability_230529.tex
Updates from Overleaf

@@
 
-\section{Tractability on a Restricted Domain}
+\section{(Strong) Tractability on a Restricted Domain}
 
@@
 \begin{equation}
-    \Omega  := \{(\varepsilon^{-1},d) : \varepsilon > E(d), \ d \in \naturals \}, \qquad \text{where }E : \naturals \to [0,\infty).
+    \Omega  := \{(\varepsilon^{-1},d) : (E(d),\infty), \ d \in \naturals \}, \qquad \text{where }E : \naturals \to [0,\infty).
 \end{equation}
@@
 \end{equation}
-This means that 
-\[
-\left \{
-\begin{array}{lll}
-&(\lambda_{1,d}^{-1},d), (\lambda_{2,d}^{-1},d), \ldots \notin \Omega, & M(d) = 0, \\
-\lambda_{1,d}\ge  \cdots \ge \lambda_{M(d),d} > E(d) \ge\lambda_{M(d)+1,d}, &
-(\lambda_{1,d}^{-1},d), \ldots, (\lambda^{-1}_{M(d),d},d)  \in \Omega, & 0 < M(d) < \infty, \\
-&
-(\lambda_{1,d}^{-1},d), (\lambda_{2,d}^{-1},d), \ldots \in \Omega, & M(d) = \infty.
-\end{array}
-\right .
-\]
 Also, for each $d \in \naturals$ define the interval 
@@
 From the definition of $M(d)$ it follows that $(\lambda_{i,d}^{-1},d) \in \Omega  \iff i \in \hI_d$, and
-\[
-\comp(\varepsilon,d) \in \hI_d \qquad \forall (\varepsilon^{-1},d) \in \Omega.
-\]
+\begin{equation} \label{eq:comprestr}
+  \comp(\varepsilon,d) \begin{cases}
+= 0, & M(d) = 0, \\
+    \in \hI_d, & M(d) > 0, 
+\end{cases}
+\qquad \forall (\varepsilon^{-1},d) \in \Omega.
+\end{equation}
 
@@
 \end{equation}
-By convention, if $M(d) = 0$, the sum is zero.
+By convention, if $M(d) < L_{\vp}$, the sum is zero.
 
@@
 \textbf{Sufficient condition:}\newline
-Fix $d$.
-For the case where $M(d)> 0$, following the argument for the sufficient condition in Theorem \ref{thm_main_strong_tract2} it follows that for all $d' \in \naturals$ and integers $n$ and $N$ with $1 \le N \le n \le M(d)$, we have
+Fix $d$.  If $M(d) = 0$, then $\comp(\varepsilon,d) = 0 \le C_{\vp}\, T(\varepsilon^{-1},1,\vp)$ automatically for all $\varepsilon \in [E(d), \infty)$.
+
+For the case $M(d)> 0$, following the argument for the sufficient condition in Theorem \ref{thm_main_strong_tract2} it follows that for all $d' \in \naturals$ and integers $n, N \in \hI_d$  with $N \le n$, we have
 \begin{align*}
@@
    \implies   \frac{1}{T(\lambda_{n+1, d}^{-1},d',\vp)} \le
-   \frac{1}{n-N+1} \sum_{i=N}^{M(d)} \frac{1}{T(\lambda_{i, d}^{-1},d',\vp) } \le \frac{1}{T(\varepsilon^{-1},d',\vp)} \\ \forall d', n, N \in \naturals, \ N \le n \le M(d).
+   \frac{1}{n-N+1} \sum_{i=N}^{M(d)} \frac{1}{T(\lambda_{i, d}^{-1},d',\vp) } \le \frac{1}{T(\varepsilon^{-1},d',\vp)} \\ \forall d' \in \naturals,\  n, N \in \hI_d,   \ N \le n.
 \end{multline}
@@
 	\nonumber
-	\comp(\varepsilon, d) & = \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon\} \\
-	\nonumber
-	& = \min \biggl\{n \in \natzero : \frac{1}{T(\lambda_{n+1,d}^{-1},d',\vp)}\le \frac{1}{T(\varepsilon^{-1},d',\vp) }\biggr\} \qquad  \forall d'\in \naturals\\
-	\nonumber
-	& \le  \min \biggl\{n \in \natzero : n \ge N - 1 + T(\varepsilon^{-1},d',\vp) \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} \biggr\} \;  \forall  d', N \in \naturals, \quad \text{by \eqref{eq:implicate_a}} \\
-	& \le  T(\varepsilon^{-1},d',\vp) \Biggl [\frac{N}{T(\varepsilon^{-1},d',\vp)}  +  \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} \Biggr] \quad \forall  d', N \in \naturals.
+	\comp(\varepsilon, d) & = \min \{n \in \hI_d : \lambda_{n+1, d} \le \varepsilon\} \qquad \text{by \eqref{eq:comprestr}} \\
+	\nonumber
+	& = \min \biggl\{n \in \hI_d : \frac{1}{T(\lambda_{n+1,d}^{-1},d',\vp)}\le \frac{1}{T(\varepsilon^{-1},d',\vp) }\biggr\} \qquad  \forall d'\in \naturals\\
+	\nonumber
+	& \le  \min \biggl\{n \in \hI_d : n \ge N - 1 + T(\varepsilon^{-1},d',\vp) \sum_{i=N}^{M(d)} \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} \biggr\} \;  \forall  d', \ 1 \le N \le M(d) \\
+ \nonumber
+ & \hspace{20ex}\text{by \eqref{eq:implicate_a_rest}.} 
+ \intertext{
+ This last statement holds for all $N \le M(d)$ because $n \ge N$ automatically in the expression above.  Thus,}
+ \comp(\varepsilon,d)
+	& \le  T(\varepsilon^{-1},d',\vp) \Biggl [\frac{N}{T(\varepsilon^{-1},d',\vp)}  +  \sum_{i=N}^{M(d)} \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} \Biggr] \quad \forall  d',\ 1 \le N \le M(d).
 \label{eq:compUP}
@@
 
-Now we take this upper bound further, specializing to the case of $d'=1$ and $N=L_{\vp}$:
+Now we take this upper bound further, specializing to the case of $d'=1$ and $N = \min(L_{\vp},M(d))$:
 \begin{align*}
        \comp(\varepsilon,d)
-       & \le T(\varepsilon^{-1},1, \vp) \Biggl [ \frac{L_{\vp}}{T(\varepsilon^{-1},1, \vp)}  + \underbrace{\sum_{i=L_{\vp}}^\infty \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}}_{\le S_{\vp} <\infty\ \text{by \eqref{eq:strong_tractiff3}} }
+       & \le T(\varepsilon^{-1},1, \vp) \Biggl [ \frac{\min(L_{\vp},M(d))}{T(\varepsilon^{-1},1, \vp)}  + \underbrace{\sum_{i = \min(L_{\vp},M(d))}^{M(d)} \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}}_{\le S_{\vp} + 1/ T(\lambda_{M(d), d}^{-1},1,\vp) \text{ by \eqref{eq:strong_rest_tractiff}} }
         \Biggr] \\
-       & \le T(\varepsilon^{-1},1,\vp) \underbrace{\left[\frac{L_{\vp}}{T(0,1, \vp)} + S_{\vp} \right]}_{=:C_{\vp}}
+       & \le T(\varepsilon^{-1},1,\vp) \underbrace{\left[\frac{L_{\vp}+1}{T(0,1, \vp)} + S_{\vp} \right]}_{=:C_{\vp}}
        \qquad \text{by \eqref{eq:Tnondecreasing}}\\
        & =  C_{\vp}T(\varepsilon^{-1},1,\vp).
-%       & \le \underbrace{2 C_{1,\vp}}_{\text{since } T(\varepsilon^{-1},1,\vp) \ge 1} T(\varepsilon^{-1},1,\vp)
-%       = \underbrace{C_{\vp}}_{:=2 C_{1,\vp}}T(\varepsilon^{-1},1,\vp).
 \end{align*}
-This means that we have strong $T$-tractability via \eqref{eq:strong_tract_def}, and verifies the sufficiency of \eqref{eq:strong_tractiff3}.
+This means that we have strong $T$-tractability on the restricted domain $\Omega$ via \eqref{eq:rest_strong_tract_def}, and verifies the sufficiency of \eqref{eq:strong_rest_tractiff}.
 
@@
 Suppose that we have strong
-$T$-tractability as defined in \eqref{eq:strong_tract_def}. That is, for some $\vp \ge \vzero$ there exists a positive constant $C_{\vp}$ such that
+$T$-tractability on the restricted domain $\Omega$ as defined in \eqref{eq:rest_strong_tract_def}. That is, for some $\vp \ge \vzero$ there exists a positive constant $C_{\vp}$ such that
 \[
 \comp(\varepsilon,d)\le C_{\vp}\, T(\varepsilon^{-1},1,\vp)
-\qquad \forall \varepsilon > 0, \ d \in \mathbb{N}.
+\qquad \forall (\varepsilon^{-1}, d) \in \Omega.
 \]
 Since the sequence of eigenvalues $\lambda_{1,d}, \lambda_{2,d}, \ldots $ is non-increasing, we have
-\begin{equation}\label{eq:lambda_K_strong3}
-\lambda_{\lfloor C_{\vp}\, T(\varepsilon^{-1},1,\vp)\rfloor +1,d}\le \varepsilon \qquad \forall \varepsilon > 0, \ d \in \mathbb{N}.
-\end{equation}
-
-Define
+\begin{equation}\label{eq:lambda_K_strong4}
+\lambda_{\lfloor C_{\vp}\, T(\varepsilon^{-1},1,\vp)\rfloor +1,d}\le \varepsilon \qquad \forall \varepsilon > E(d), \ d \in \mathbb{N}.
+\end{equation}
+
+For $(\varepsilon^{-1}, d) \in \Omega$, define
 \[
@@
 \[
-i(\varepsilon,\vp)\le C_{\vp}\, T(\varepsilon^{-1},1,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,\vp),d}^{-1},1,\vp)+1, \qquad \forall \varepsilon > 0, \ d \in \mathbb{N},
+i(\varepsilon,\vp)\le C_{\vp}\, T(\varepsilon^{-1},1,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,\vp),d}^{-1},1,\vp)+1, \qquad  \forall \varepsilon > E(d), \ d \in \mathbb{N},
 \]
@@
 
-For $\varepsilon$ taking on all positive values, $i(\varepsilon,\vp)$ takes on all values greater than or equal to $i(\infty,\vp)$, so
-\[
-i\le C_{\vp} T(\lambda_{i,d}^{-1},1,\vp)+1, \qquad \forall i \ge i(\infty,\vp), \ d \in \naturals.
+For $\varepsilon$ taking on all values in $(E(d),\infty)$, $i(\varepsilon,\vp)$ takes on (at least) all values 
+\[
+I_{d,\vp}:=\begin{cases} 
+\emptyset, & i(E(d),\vp) = i(\infty,\vp) \\
+\{i(\infty,\vp),\ldots, i(E(d),\vp)-1\}, & E(d) > 0, \\
+\{i(\infty,\vp), i(\infty,\vp) + 1, \ldots\}, & E(d) = 0.
+\end{cases}
+\]
+So,
+\[
+i\le  C_{\vp} T(\lambda_{i,d}^{-1},1,\vp)+1, \qquad \forall i\in I_{d,\vp},  \ d \in \naturals.
 \]
 This implies via our technical assumption \eqref{eq:ptauassume} that
-\begin{gather*}
+\begin{gather}
+\nonumber
  K_{\vp,\tau}\,T (\lambda_{i,d}^{-1},1,\tau \vp) \ge
@@
  \ge
-  \left[\frac{(i-1)}{C_{\vp}}\right]^\tau \qquad \forall i \ge i(\infty,\vp)), \ d \in \naturals, \\
+  \left[\frac{(i-1)}{C_{\vp}}\right]^\tau \qquad i\in I_{d,\vp},  \ d \in \naturals, \\
+  \label{eq:rest_strong_ineq}
  \frac{1}{T (\lambda_{i,d}^{-1},1,\tau \vp)} \le
-\frac{K_{\vp,\tau}\, C_{\vp}^\tau}{(i-1)^\tau}\qquad \forall i \ge \max\{i(\infty,\vp),2\}), \ d \in \naturals .
-\end{gather*}
-Summing both sides of this last inequality over $i$ from $i(\infty,\vp) +1 \ge 2$ to $\vinfty$ yields
-\begin{equation*}
-\sup_{d\in\naturals} \sum_{i=i(\infty,\vp) +1 }^\infty \frac{1}{T (\lambda_{i,d}^{-1},1, \tau \vp)}
+\frac{K_{\vp,\tau}\, C_{\vp}^\tau}{(i-1)^\tau}\qquad \forall i \in I_{d,\vp} \setminus\{1\}, \ d \in \naturals .
+\end{gather}
+
+To complete the proof, we will sum both sides of \eqref{eq:rest_strong_ineq} over the range of $i$ appearing in \eqref{eq:strong_rest_tractiff}, to establish that $S_{\tau\vp}$ is finite.
+To do this we need to show that \eqref{eq:rest_strong_ineq} holds for that range.
+Choose Choose $L_{\tau\vp} = i(\infty,\vp) +1 \ge 2$.
+There are three cases.
+\begin{enumerate}
+\renewcommand{\labelenumi}{\roman{enumi})}
+
+\item If $M(d) < L_{\tau\vp}$, then 
+\[
+\sum_{i = L_{\tau\vp}}^{M(d)} \frac{1}{T (\lambda_{i,d}^{-1},1, \tau \vp)} = 0,
+\]
+which does not affect the finiteness of $S_{\tau\vp}$.
+
+\item If $M(d) \ge L_{\tau\vp}$ and $E(d) = 0$, then $\{L_{\tau\vp},  \L_{\tau\vp} + 1, \ldots \} \subseteq I_{d,\vp} \setminus \{1\}$.
+
+\item If $M(d) \ge L_{\tau\vp}$ and $E(d) >0$, then \eqref{eq:Mddef} and \eqref{eq:lambda_K_strong4} imply that
+\[
+\lambda_{i(E(d),\vp),d} \le \lambda_{M(d)+1,d} \le E(d) < \lambda_{M(d),d}.
+\]
+This means that $M(d) \le i(E(d),\vp)-1$.  So, $\{L_{\tau\vp}, \ldots, M(d)\} \subseteq I_{d,\vp} \setminus \{1\}$.
+
+In both the second and third cases,
+\begin{align*}
+S_{\tau\vp} & = \sup_{d\in\naturals} \sum_{i = L_{\tau\vp}}^{M(d)} \frac{1}{T (\lambda_{i,d}^{-1},1, \tau \vp)}
+\le 
+\sup_{d\in\naturals} \sum_{i \in I_{d,\vp} \setminus\{1\} } \frac{1}{T (\lambda_{i,d}^{-1},1, \tau \vp)} \\
+&  \le  K_{\vp,\tau}\, C_{\vp}^\tau
+\sum_{i=2}^\infty \frac{1}{(i-1)^\tau}
  \le K_{\vp,\tau}\, C_{\vp}^\tau
-\sum_{i=2}^\infty \frac{1}{(i-1)^\tau} \\
- \le K_{\vp,\tau}\, C_{\vp}^\tau
-\zeta (\tau)  < \infty,
-\end{equation*}
+\zeta (\tau) 
+ < \infty \qquad \text{by \eqref{eq:rest_strong_ineq},}
+\end{align*}
 where $\zeta$ denotes the Riemann zeta function.
-This yields \eqref{eq:strong_tractiff3} with $\vp$ replaced by $\vp' = \tau \vp$ and $L_{\vp'} = i(\infty,\vp) +1$, and so we see the necessity of $\eqref{eq:strong_tractiff3}$.
+
+\end{enumerate}
+Thus, in all cases, the assumption of strong tractability on the restricted domain implies \eqref{eq:strong_rest_tractiff} with $\vp$ replaced by $\vp' = \tau \vp$, and so we see the necessity of $\eqref{eq:strong_rest_tractiff}$.
 
 \bigskip
-\noindent \textbf{Optimality:} \\
-To complete the proof, we must show that $\cp_{\textup{strct}} = \widetilde{\cp}_{\textup{strct}}$.
-Then, the expression for  $\cp_{\textup{sopt}}$ automatically follows from its definition in \eqref{eq:Psoptdef}.
-
-First we show  that if $\vp^* \in \cp_{\textup{strct}}$, then $\vp^* \in \widetilde{\cp}_{\textup{strct}}$.
-If $\vp^* \in \cp_{\textup{strct}}$, then \eqref{eq:strong_tract_def} must hold for all $\vp' \in (\vp^*,\vinfty)$.
-For any $\vp' \in (\vp^*,\vinfty)$, we may choose $\vp$ and $\tau$ such that $\vp^* < \vp < \vp' = \tau \vp$.
-Since $\vp > \vp^*$, \eqref{eq:strong_tract_def} also holds for $\vp$, and it follows that \eqref{eq:strong_tractiff3} must hold for $\vp'$ by the proof of necessity above.
-Thus, $\vp^* \in \widetilde{\cp}_{\textup{strct}}$.
-
-Next we show that if $\vp^* \in \widetilde{\cp}_{\textup{strct}}$, then $\vp^* \in \cp_{\textup{strct}}$.
-If $\vp^* \in \widetilde{\cp}_{\textup{strct}}$, then \eqref{eq:strong_tractiff3}  holds for all $\vp \in (\vp^*,\vinfty)$.
-By the argument to prove the sufficient condition above, it follows that \eqref{eq:strong_tract_def} must also hold for all $\vp \in (\vp^*,\vinfty)$.
-Thus, $\vp^* \in \cp_{\textup{strct}}$.
+\noindent \textbf{Optimality:} 
+The proof of optimality is analogous to that for Theorem \ref{thm_main_strong_tract2} and is omitted.
 
@@
 
-\noindent This concludes the proof of  Theorem \ref{thm_main_strong_tract2}.
-
+\noindent This concludes the proof of  Theorem \ref{thm_main_rest_strong_tract}.
 \end{proof}
+
+The equivalent condition for tractability on a restricted domain is analogous to the conditions for tractability on an unrestricted domain and for strong tractability on a restricted domain.
+The proof is analogous as well.
 

### 2023-06-07 GeneralizedTractability_230529.tex
Updates from Overleaf

@@
 i(\varepsilon,\vp):= \lfloor C_{\vp}\, T(\varepsilon^{-1},1,\vp)\rfloor +1, \quad
-i(\infty,\vp) = \lim_{\varepsilon \to \infty}  i(\varepsilon,\vp) \ge 1 .
+i(\infty,\vp) =\lfloor C_{\vp}\, T(0,1,\vp)\rfloor +1.
 \]
@@
 
+\subsection{Strong Tractability on a Restricted Domain}
+
 \begin{theorem}\label{thm_main_rest_strong_tract}
@@
 	& \le  T(\varepsilon^{-1},d',\vp) \Biggl [\frac{N}{T(\varepsilon^{-1},d',\vp)}  +  \sum_{i=N}^{M(d)} \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} \Biggr] \quad \forall  d',\ 1 \le N \le M(d).
-\label{eq:compUP}
+\label{eq:compUP_rest}
 \end{align}
@@
 
-For $(\varepsilon^{-1}, d) \in \Omega$, define
+For $(\varepsilon^{-1}, d) \in \Omega$, define the positve integers
 \[
 i(\varepsilon,\vp):= \lfloor C_{\vp}\, T(\varepsilon^{-1},1,\vp)\rfloor +1, \quad
-i(\infty,\vp) = \lim_{\varepsilon \to \infty}  i(\varepsilon,\vp) \ge 1 . 
-\]
-Thus, it follows by \eqref{eq:lambda_K_strong3} that $\lambda_{i(\varepsilon,\vp),d} \le \varepsilon$.
+i(\infty,\vp) =  \lfloor C_{\vp}\, T(0,1,\vp)\rfloor +1 \ge 1 . 
+\]
+Thus, it follows by \eqref{eq:lambda_K_strong3} that $\lambda_{i(\varepsilon,\vp),d} \le \varepsilon$
+for any  $(\varepsilon^{-1}, d) \in \Omega$.
 Note furthermore that we always have
@@
 
-For $\varepsilon$ taking on all values in $(E(d),\infty)$, $i(\varepsilon,\vp)$ takes on (at least) all values 
+For $\varepsilon$ taking on all values in $(E(d),\infty)$, $i(\varepsilon,\vp)$ takes on (at least) all values in
 \[
@@
 \end{enumerate}
-Thus, in all cases, the assumption of strong tractability on the restricted domain implies \eqref{eq:strong_rest_tractiff} with $\vp$ replaced by $\vp' = \tau \vp$, and so we see the necessity of $\eqref{eq:strong_rest_tractiff}$.
+Thus, in all three cases, the assumption of strong tractability on the restricted domain implies \eqref{eq:strong_rest_tractiff} with $\vp$ replaced by $\vp' = \tau \vp$, and so we see the necessity of $\eqref{eq:strong_rest_tractiff}$.
 
@@
 
+\subsection{Tractability on a Restricted Domain}
+
 The equivalent condition for tractability on a restricted domain is analogous to the conditions for tractability on an unrestricted domain and for strong tractability on a restricted domain.
@@
 Let $T$ be a tractability function as specified in \eqref{eq:Tspec} and satisfying \eqref{eq:Tconditions} and \eqref{eq:ptauassume}.
-A problem is $T$-tractable on $\Omega$ iff there exists $\vp\ge \vzero$ and a positive integer $L_{\vp}$ such that
-\begin{equation} \label{eq:rest_tractiff4}
+A problem is $T$-tractable on the restricted domain $\Omega$ iff there exists $\vp\ge \vzero$ and a positive integer $L_{\vp}$ such that
+\begin{equation} \label{eq:rest_tractiff}
      S_{\vp}:=\sup_{d \in \naturals}
@@
 If \eqref{eq:rest_tractiff4} holds for some $\vp$, let $\widetilde{\cp}_{\textup{trct}} : = \{\vp^* : \eqref{eq:tractiff4} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty}) \}$.
-Then $\cp_{\textup{trct}} = \widetilde{\cp}_{\textup{trct}}$, and the set of optimal  tractability parameters is
-\[
-\cp_{\textup{opt}} =
-\{\vp^* \in \widetilde{\cp}_{\textup{trct}} :  \vp^* \notin [\widetilde{\vp},\boldsymbol{\infty}) \ \forall \widetilde{\vp}\in  \widetilde{\cp}_{\textup{trct}} \setminus \{\vp^*\} \}.
+Then $\cp_{\textup{rtrct}} = \widetilde{\cp}_{\textup{rtrct}}$, and the set of optimal  tractability parameters is
+\[
+\cp_{\textup{ropt}} =
+\{\vp^* \in \widetilde{\cp}_{\textup{rtrct}} :  \vp^* \notin [\widetilde{\vp},\boldsymbol{\infty}) \ \forall \widetilde{\vp}\in  \widetilde{\cp}_{\textup{rtrct}} \setminus \{\vp^*\} \}.
 \]
@@
     \textbf{Sufficient Condition:}\\
-We adapt the argument in the proof of the sufficient condition for Theorems \ref{thm_main_strong_tract2} and \ref{thm_main_tract2}.
-Suppose that \eqref{eq:rest_tractiff4} holds for some $\vp \ge 0$.
-Fix any $(\varepsilon^{-1},d) \in \Omega$.
-
-Define the interval
-\begin{equation} \label{eq:hIdef}
-\hI_{d}:=\begin{cases} 
-\{1,\ldots, M(d)\}, & M(d) < \infty, \\
-\naturals, & M(d) = \infty.
-\end{cases}
-\end{equation}
-Since the $\lambda_{i,d}$ are non-increasing in $i$, it follows that the $T(\lambda_{\cdot,d}^{-1},d,\vp)$ is non-decreasing. For any $N\in \hI_d$ and any $n \in \hI_d \setminus \{1, \ldots, N-1\}$,
-\begin{align*}
-    \lambda_{n+1,d} \le \lambda_{n,d} \le \cdots \le \lambda_{N,d}
-    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d,\vp)} \le \frac{1}{T(\lambda_{n, d}^{-1},d,\vp)} \le \cdots \le \frac{1}{T(\lambda_{N, d}^{-1},d,\vp)} \\
-     \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d,\vp) }
-    \le &\frac{1}{n-N+1} \sum_{i=N}^n  \frac{1}{T(\lambda_{i, d}^{-1},d,\vp) }
-    \le \frac{1}{n-N+1} \sum_{i=N}^{M(d)}  \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}.
-\end{align*}
-Thus, we can conclude from the previous line that
-\begin{multline} \label{eq:implicate_a_rest}
-    n - N +1 \ge T(\varepsilon^{-1},d,\vp) \sum_{i=N}^{M(d)} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)} \\
-   \implies   \frac{1}{T(\lambda_{n+1, d}^{-1},d,\vp)} \le
-   \frac{1}{n-N+1} \sum_{i=N}^{M(d)} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp) } \le \frac{1}{T(\varepsilon^{-1},d,\vp)} \\ \forall d \in \naturals, \ N \in \hI_d, \ n \in \hI_d \setminus \{1, \ldots, N-1\}.
-\end{multline}
-We note that the left side of the implication implies $n \ge N$ automatically since $n$ is an integer and $n - N +1$ is assumed to be positive.
-
-Moreover, given that $T$ is increasing in its arguments, we have the following equivalent expression for the information complexity via \eqref{eq:comp_def} for all $(\varepsilon^{-1},d) \in \Omega$:
-\begin{align} %\label{eq:comp_equiv}
-	\nonumber
-	\comp(\varepsilon, d) & = \min \{n \in \hI_d : \lambda_{n+1, d} \le \varepsilon\} \\
-	\nonumber
-	& = \min \biggl\{n \in \natzero : \frac{1}{T(\lambda_{n+1,d}^{-1},d,\vp)}\le \frac{1}{T(\varepsilon^{-1},d,\vp) }\biggr\}\\
-	\nonumber
-	& \le  \min \biggl\{n \in \natzero : n \ge N - 1 + T(\varepsilon^{-1},d,\vp) \sum_{i=N}^{M(d)} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)} \biggr\} \;  \forall N \in \naturals, \quad \text{by \eqref{eq:implicate_a_rest}} \\
-	& \le  T(\varepsilon^{-1},d,\vp) \Biggl [\frac{N}{T(\varepsilon^{-1},d,\vp)}  +  \sum_{i=N}^{M(d)} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)} \Biggr] \quad \forall N \in \naturals. \label{eq:compUP_rest}
-\end{align}
-
-it follows from \eqref{eq:compUP_rest} with $N = \lceil L_{\vp}\, T(0,d,\vp)\rceil$ that 
+Fix $d$.  If $M(d) = 0$, then $\comp(\varepsilon,d) = 0 \le C_{\vp}\, T(\varepsilon^{-1},d,\vp)$ automatically for all $\varepsilon \in [E(d), \infty)$.
+
+For the case $M(d)> 0$, we utilize upper bound \eqref{eq:compUP_rest}, specializing to the case of $d'=d$ and $N = \min\left(\lceil L_{\vp}\, T(0,d,\vp)\rceil,M(d)\right)$:
 \begin{align*}
        \comp(\varepsilon,d)
-       & \le T(\varepsilon^{-1},d,\vp) \Biggl [ 
-       \frac{\lceil L_{\vp}\, T(0,d,\vp)\rceil}{T(\varepsilon^{-1},d,\vp)}  + 
-       \underbrace{\sum_{i=\lceil L_{\vp}\, T(0,d,\vp)\rceil}^{M(d)} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}}_{\le S_{\vp} \text{ by \eqref{eq:rest_tractiff4}}}
-       \Biggr ] 
-        \quad \forall \varepsilon > 0, \ d  \in \naturals\\
-       & \le T(\varepsilon^{-1},d,\vp)\left[\frac{L_{\vp} T(0,d,\vp)+1}{T(\varepsilon^{-1},d, \vp)} +  S_{\vp} \right]
-        \qquad \forall \varepsilon > 0, \ d  \in \naturals\\
-       & \le T(\varepsilon^{-1},d,\vp)\left[\frac{L_{\vp} T(0,d,\vp)}{T(\varepsilon^{-1},d, \vp)}
-       + \frac{1}{T(0,1, \vp)} + S_{\vp}\right]
-       \qquad \text{by \eqref{eq:Tnondecreasing}}   \\
-       & \le T(\varepsilon^{-1},d,\vp) 
-       \underbrace{\left [  L_{\vp} + \frac{1}{T(0,1, \vp)} + S_{\vp} \right]}_{=:C_{\vp}}
-       \qquad \text{by \eqref{eq:Tnondecreasing}}  
+       & \le T(\varepsilon^{-1},d, \vp) \Biggl [ \frac{\min\left(\lceil L_{\vp}\, T(0,d,\vp)\rceil,M(d)\right)}{T(\varepsilon^{-1},d, \vp)}  + \underbrace{\sum_{i = \min\left(\lceil L_{\vp}\, T(0,d,\vp)\rceil,M(d)\right)}^{M(d)} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}}_{\le S_{\vp} + 1/ T(\lambda_{M(d), d}^{-1},d,\vp) \text{ by \eqref{eq:strong_rest_tractiff}} }
+        \Biggr] \\
+       & \le T(\varepsilon^{-1},d,\vp)\left[\frac{ L_{\vp}\, T(0,d,\vp)+1}{T(0,d, \vp)} + S_{\vp} + \frac{1}{T(\lambda_{M(d), d}^{-1},d,\vp)} \right]
+       \qquad \text{by \eqref{eq:Tnondecreasing}}\\
+       & \le T(\varepsilon^{-1},d,\vp) \underbrace{\left[L_{\vp} + \frac{2}{T(0,1, \vp)} + S_{\vp} \right]}_{=:C_{\vp}}
+       \qquad \text{by \eqref{eq:Tnondecreasing}}\\
+       & =  C_{\vp}T(\varepsilon^{-1},d,\vp).
 \end{align*}
-It follows that we have $T$-tractability, which shows sufficiency of \eqref{eq:rest_tractiff4}.
+This means that we have strong $T$-tractability on the restricted domain $\Omega$ via \eqref{eq:rest_tract_def}, and verifies the sufficiency of \eqref{eq:rest_tractiff}.
 
@@
 Suppose that we have
-$T$-tractability. That is, for some $\vp \ge \vzero$, there exists a positive constant $C_{\vp}$ such that
+$T$-tractability on the restricted domain. That is, for some $\vp \ge \vzero$, there exists a positive constant $C_{\vp}$ such that
 \[
@@
 	\lambda_{\lfloor C_{\vp}\, T(\varepsilon^{-1},d,\vp)\rfloor +1,d}\le \varepsilon \qquad 
- \forall (\varepsilon^{-1}, d) \in \Omega.
-\end{equation}
-
-For $(\varepsilon^{-1}, d) \in \Omega$, define the integers 
+ \forall \varepsilon > E(d),\ d \in \naturals.
+\end{equation}
+
+For $(\varepsilon^{-1}, d) \in \Omega$, define the positive integers 
 \[
@@
 \[
-i(\varepsilon,d,\vp)\le C_{\vp}\, T(\varepsilon^{-1},d,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,d,\vp),d}^{-1},d,\vp)+1, \qquad \forall (\varepsilon^{-1},d)\in\Omega.
-\]
-For $\varepsilon$ taking on all values in $(E(d),\infty)$, $i(\varepsilon,d,\vp)$ takes on (at least) all values 
-\[
-I_{d}:=\begin{cases} 
-\{i(\infty,d,\vp),\ldots, i(E(d),d,\vp)-1\}, & E(d) > 0, \\
-\{i(\infty,d,\vp), i(\infty,d,\vp) + 1, \ldots\}, & E(d) = 0.
+i(\varepsilon,d,\vp)\le C_{\vp}\, T(\varepsilon^{-1},d,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,d,\vp),d}^{-1},d,\vp)+1, \qquad \forall \varepsilon > E(d),\ d \in \naturals.
+\]
+For $\varepsilon$ taking on all values in $(E(d),\infty)$, $i(\varepsilon,d,\vp)$ takes on (at least) all values in
+\[
+I_{d,\vp}:=\begin{cases} 
+\emptyset, & i(E(d),\vp) = i(\infty,\vp) \\
+\{i(\infty,\vp),\ldots, i(E(d),\vp)-1\}, & E(d) > 0, \\
+\{i(\infty,\vp), i(\infty,\vp) + 1, \ldots\}, & E(d) = 0.
 \end{cases}
-\]
-So,
+\]So,
 \[
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+For $\varepsilon$ taking on all values in $(E(d),\infty)$, $i(\varepsilon,\vp)$ takes on (at least) all values 
+\[
+I_{d,\vp}:=\begin{cases} 
+\emptyset, & i(E(d),\vp) = i(\infty,\vp) \\
+\{i(\infty,\vp),\ldots, i(E(d),\vp)-1\}, & E(d) > 0, \\
+\{i(\infty,\vp), i(\infty,\vp) + 1, \ldots\}, & E(d) = 0.
+\end{cases}
+\]
+So,
+\[
+i\le  C_{\vp} T(\lambda_{i,d}^{-1},1,\vp)+1, \qquad \forall i\in I_{d,\vp},  \ d \in \naturals.
+\]
+This implies via our technical assumption \eqref{eq:ptauassume} that
+\begin{gather}
+\nonumber
+ K_{\vp,\tau}\,T (\lambda_{i,d}^{-1},1,\tau \vp) \ge
+ [T(\lambda_{i,d}^{-1},1, \vp)]^\tau
+ \ge
+  \left[\frac{(i-1)}{C_{\vp}}\right]^\tau \qquad i\in I_{d,\vp},  \ d \in \naturals, \\
+  \label{eq:rest_strong_ineq}
+ \frac{1}{T (\lambda_{i,d}^{-1},1,\tau \vp)} \le
+\frac{K_{\vp,\tau}\, C_{\vp}^\tau}{(i-1)^\tau}\qquad \forall i \in I_{d,\vp} \setminus\{1\}, \ d \in \naturals .
+\end{gather}
+
+To complete the proof, we will sum both sides of \eqref{eq:rest_strong_ineq} over the range of $i$ appearing in \eqref{eq:strong_rest_tractiff}, to establish that $S_{\tau\vp}$ is finite.
+To do this we need to show that \eqref{eq:rest_strong_ineq} holds for that range.
+Choose Choose $L_{\tau\vp} = i(\infty,\vp) +1 \ge 2$.
+There are three cases.
+\begin{enumerate}
+\renewcommand{\labelenumi}{\roman{enumi})}
+
+\item If $M(d) < L_{\tau\vp}$, then 
+\[
+\sum_{i = L_{\tau\vp}}^{M(d)} \frac{1}{T (\lambda_{i,d}^{-1},1, \tau \vp)} = 0,
+\]
+which does not affect the finiteness of $S_{\tau\vp}$.
+
+\item If $M(d) \ge L_{\tau\vp}$ and $E(d) = 0$, then $\{L_{\tau\vp},  \L_{\tau\vp} + 1, \ldots \} \subseteq I_{d,\vp} \setminus \{1\}$.
+
+\item If $M(d) \ge L_{\tau\vp}$ and $E(d) >0$, then \eqref{eq:Mddef} and \eqref{eq:lambda_K_strong4} imply that
+\[
+\lambda_{i(E(d),\vp),d} \le \lambda_{M(d)+1,d} \le E(d) < \lambda_{M(d),d}.
+\]
+This means that $M(d) \le i(E(d),\vp)-1$.  So, $\{L_{\tau\vp}, \ldots, M(d)\} \subseteq I_{d,\vp} \setminus \{1\}$.
+
+In both the second and third cases,
+\begin{align*}
+S_{\tau\vp} & = \sup_{d\in\naturals} \sum_{i = L_{\tau\vp}}^{M(d)} \frac{1}{T (\lambda_{i,d}^{-1},1, \tau \vp)}
+\le 
+\sup_{d\in\naturals} \sum_{i \in I_{d,\vp} \setminus\{1\} } \frac{1}{T (\lambda_{i,d}^{-1},1, \tau \vp)} \\
+&  \le  K_{\vp,\tau}\, C_{\vp}^\tau
+\sum_{i=2}^\infty \frac{1}{(i-1)^\tau}
+ \le K_{\vp,\tau}\, C_{\vp}^\tau
+\zeta (\tau) 
+ < \infty \qquad \text{by \eqref{eq:rest_strong_ineq},}
+\end{align*}
+where $\zeta$ denotes the Riemann zeta function.
+
+\end{enumerate}
+Thus, in all three cases, the assumption of strong tractability on the restricted domain implies \eqref{eq:strong_rest_tractiff} with $\vp$ replaced by $\vp' = \tau \vp$, and so we see the necessity of $\eqref{eq:strong_rest_tractiff}$.
 \bigskip

### 2023-06-07 GeneralizedTractability_230529.tex
Updates from Overleaf

@@
 Let $T$ be a tractability function as specified in \eqref{eq:Tspec} and satisfying \eqref{eq:Tconditions} and \eqref{eq:ptauassume}.
-A problem is $T$-tractable iff there exists $\vp\ge \vzero$ and a positive integer $L_{\vp}$ such that
+A problem is $T$-tractable iff there exists $\vp\ge \vzero$ and a positive constant $L_{\vp}$ such that
 \begin{equation} \label{eq:tractiff4}
@@
 
-\noindent \textbf{Optimality:}
+\noindent \textbf{Optimality:} \\
 This proof is similar to the proof for the optimality condition for strong tractability in Theorem \ref{thm_main_strong_tract2}.
@@
 \begin{gather}
-	\label{eq:Poptdef}
+	%\label{eq:rPoptdef}
 	\mathcal{P}_{\textup{ropt}} : = \{\vp^* \in \cp_{\textup{rtrct}} :  \vp^* \notin [\vp,\boldsymbol{\infty}) \ \forall \vp \in  \cp_{\textup{rtrct}} \setminus \{\vp^*\} \}, \\
-	\label{eq:Psoptdef}
+	%\label{eq:rPsoptdef}
 	\mathcal{P}_{\textup{rsopt}} : = \{\vp^* \in \cp_{\textup{rstrct}} :  \vp^* \notin [\vp,\boldsymbol{\infty}) \ \forall \vp \in  \cp_{\textup{rstrct}} \setminus \{\vp^*\} \}.
@@
 
-\item If $M(d) \ge L_{\tau\vp}$ and $E(d) = 0$, then $\{L_{\tau\vp},  \L_{\tau\vp} + 1, \ldots \} \subseteq I_{d,\vp} \setminus \{1\}$.
+\item If $M(d) \ge L_{\tau\vp}$ and $E(d) = 0$, then $\{L_{\tau\vp},  L_{\tau\vp} + 1, \ldots \} \subseteq I_{d,\vp} \setminus \{1\}$.
 
@@
 \bigskip
-\noindent \textbf{Optimality:} 
+\noindent \textbf{Optimality:} \\ 
 The proof of optimality is analogous to that for Theorem \ref{thm_main_strong_tract2} and is omitted.
@@
 Let $T$ be a tractability function as specified in \eqref{eq:Tspec} and satisfying \eqref{eq:Tconditions} and \eqref{eq:ptauassume}.
-A problem is $T$-tractable on the restricted domain $\Omega$ iff there exists $\vp\ge \vzero$ and a positive integer $L_{\vp}$ such that
+A problem is $T$-tractable on the restricted domain $\Omega$ iff there exists $\vp\ge \vzero$ and a positive constant $L_{\vp}$ such that
 \begin{equation} \label{eq:rest_tractiff}
@@
 \end{equation}
-If \eqref{eq:rest_tractiff4} holds for some $\vp$, let $\widetilde{\cp}_{\textup{trct}} : = \{\vp^* : \eqref{eq:tractiff4} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty}) \}$.
+If \eqref{eq:rest_tractiff} holds for some $\vp$, let $\widetilde{\cp}_{\textup{trct}} : = \{\vp^* : \eqref{eq:tractiff4} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty}) \}$.
 Then $\cp_{\textup{rtrct}} = \widetilde{\cp}_{\textup{rtrct}}$, and the set of optimal  tractability parameters is
@@
 Since the sequence of eigenvalues $\lambda_{1,d}, \lambda_{2,d}, \ldots $ is non-increasing, we have
-\begin{equation}\label{eq:lambda_K4}
+\begin{equation}\label{eq:rest_lambda_K4}
 	\lambda_{\lfloor C_{\vp}\, T(\varepsilon^{-1},d,\vp)\rfloor +1,d}\le \varepsilon \qquad 
@@
 \]
-It follows by \eqref{eq:lambda_K4} that $\lambda_{i(\varepsilon,d,\vp),d} \le \varepsilon$
+It follows by \eqref{eq:rest_lambda_K4} that $\lambda_{i(\varepsilon,d,\vp),d} \le \varepsilon$
 for any  $(\varepsilon^{-1}, d) \in \Omega$.
@@
 I_{d,\vp}:=\begin{cases} 
-\emptyset, & i(E(d),\vp) = i(\infty,\vp) \\
-\{i(\infty,\vp),\ldots, i(E(d),\vp)-1\}, & E(d) > 0, \\
-\{i(\infty,\vp), i(\infty,\vp) + 1, \ldots\}, & E(d) = 0.
+\emptyset, & i(E(d),d,\vp) = i(\infty,d,\vp), \\
+\{i(\infty,d,\vp),\ldots, i(E(d),d,\vp)-1\}, & E(d) > 0, \\
+\{i(\infty,d,\vp), i(\infty,d,\vp) + 1, \ldots\}, & E(d) = 0.
 \end{cases}
-\]So,
+\]
+So,
 \[
@@
 \]
-
-This upper bound on $i$ in terms of $T(\lambda_{i,d}^{-1},d,\vp)$ implies via our technical assumption \eqref{eq:ptauassume} that for any $\tau > 1$,
-\begin{equation}\label{eq:restrictKfive}
+This implies via our technical assumption \eqref{eq:ptauassume} that
+\begin{gather}
+\nonumber
  K_{\vp,\tau}\,T (\lambda_{i,d}^{-1},d,\tau \vp) \ge
@@
  \ge
-	\left[\frac{(i-1)}{C_{\vp}}\right]^\tau \qquad  \forall i\in I_{d},  \ d \in \naturals.
- \end{equation}
-To carry the argument further, we need to show that the interval $I_d$ contains the interval
-\[
-\tI_{d}:=\begin{cases} 
-\{i(\infty,d,\vp),\ldots, M(d)\}, & E(d) > 0, \\
-\{i(\infty,d,\vp), i(\infty,d,\vp) + 1, \ldots\}, & E(d) = 0.
-\end{cases}
-\]
-
-Since $I_d = \tI_d$ when $E(d) =0$, we need only consider the case where $E(d) > 0$.  In this case \eqref{eq:Mddef} and \eqref{eq:lambda_K4} imply that
-\[
-\lambda_{i(E(d),d,\vp),d} \le \lambda_{M(d)+2} \le E(d) < \lambda_{M(d)+1,d}.
-\]
-This means that $i(E(d),d,\vp)-1 \ge M(d)+1$, and so $I_d \supseteq \tI_d$.
-
- and this implies
- \[
+  \left[\frac{(i-1)}{C_{\vp}}\right]^\tau \qquad i\in I_{d,\vp},  \ d \in \naturals, \\
+  \label{eq:rest_ineq}
  \frac{1}{T (\lambda_{i,d}^{-1},d,\tau \vp)} \le
-	\frac{K_{\vp,\tau}\, C_{\vp}^\tau}{(i-1)^\tau}\qquad  \peter{\forall i\in 
- \{i(\infty,d,\vp)+1,\ldots, M(d)\}},  \ d \in \naturals.
-\]
-
-Let $\vp' = \tau \vp$. \peter{Like in the proof of Theorem \ref{thm_main_tract2}, we note that $i(\infty,d,\vp) 
-\ge i(\infty,d,\vp')$. Furthermore, we also have 
-$M(d)\le i(E(d),d,\vp)\le i(E(d),d,\vp')$. Thus,}
-summing both sides of the latter inequality over \peter{$\{i(\infty,d,\vp')+1,\ldots, M(d)\} $} it follows that
-\begin{equation*}
-	\sup_{d\in\naturals} \, \, \sum_{\peter{i=i(\infty,d,\vp')+1}}^{\peter{M(d)}} \frac{1}{T (\lambda_{i,d}^{-1},d,\vp')}
-	 \le  K_{\vp,\tau}\, C_{\vp}^\tau
-	\sum_{i=2}^{\infty} \frac{1}{(i-1)^\tau} \\
-	 \le  K_{\vp,\tau}\, C_{\vp}^\tau
-	\zeta (\tau)  < \infty,
-\end{equation*}
-where $\zeta$ denotes the Riemann zeta function.
-
-\peter{[WHAT REMAINS TO BE DONE (HOPEFULLY NOT HARD): check that the summation range above is not empty.]}
-
-Note now that, for any $d\in\naturals$,
-\begin{align*}
- i(\infty,d,\vp') +1  & = \lfloor C_{\vp'}\, T(0,d,\vp')\rfloor +2 \le  \left[C_{\vp'} + \frac{2}{T(0,d,\vp')}   \right]\, T(0,d,\vp')\\
- & \le  \underbrace{\left[C_{\vp'} + \frac{2}{T(0,1,\vp')}   \right]}_{=:L_{\vp'}}\, T(0,d,\vp')
+\frac{K_{\vp,\tau}\, C_{\vp}^\tau}{(i-1)^\tau}\qquad \forall i \in I_{d,\vp} \setminus\{1\}, \ d \in \naturals .
+\end{gather}
+
+To complete the proof, we will sum both sides of \eqref{eq:rest_ineq} over the range of $i$ appearing in \eqref{eq:rest_tractiff}, to establish that $S_{\vp'}$ is finite, where  $\vp' = \tau \vp$.
+To do this we need to show that \eqref{eq:rest_ineq} holds for that range.
+
+For any $d\in\naturals$, let
+\begin{align*}
+L_{\vp'} & := \left[C_{\vp'} + \frac{2}{T(0,1,\vp')}   \right]
+\intertext{and note that }
+ \min(i(\infty,d,\vp'),2) & \le i(\infty,d,\vp') +1  = \lfloor C_{\vp'}\, T(0,d,\vp')\rfloor +2 \le  \left[C_{\vp'} + \frac{2}{T(0,d,\vp')}   \right]\, T(0,d,\vp')\\
+ & \le  L_{\vp'}\, T(0,d,\vp')
  \le \lceil L_{\vp'} T(0,d,\vp')\rceil .
 \end{align*}
-For this choice of $L_{\vp'}$ we have
-\[
-\sup_{d\in\naturals}\,\, \sum_{i=\lceil L(\vp') T(0,d,\vp')\rceil}^{\peter{M(d)}} \frac{1}{T(\lambda_{i,d}^{-1},d, \vp')}
-\le
-\sup_{d\in\naturals} \, \, \sum_{i=i (\infty,d,\vp')+1}^\infty \frac{1}{T (\lambda_{i,d}^{-1},d,\vp')} <
-\infty.
-\]
-This yields \eqref{eq:tractiff4} with $\vp$ replaced by $\vp'$, so we see the necessity of $\eqref{eq:tractiff4}$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-For $\varepsilon$ taking on all values in $(E(d),\infty)$, $i(\varepsilon,\vp)$ takes on (at least) all values 
-\[
-I_{d,\vp}:=\begin{cases} 
-\emptyset, & i(E(d),\vp) = i(\infty,\vp) \\
-\{i(\infty,\vp),\ldots, i(E(d),\vp)-1\}, & E(d) > 0, \\
-\{i(\infty,\vp), i(\infty,\vp) + 1, \ldots\}, & E(d) = 0.
-\end{cases}
-\]
-So,
-\[
-i\le  C_{\vp} T(\lambda_{i,d}^{-1},1,\vp)+1, \qquad \forall i\in I_{d,\vp},  \ d \in \naturals.
-\]
-This implies via our technical assumption \eqref{eq:ptauassume} that
-\begin{gather}
-\nonumber
- K_{\vp,\tau}\,T (\lambda_{i,d}^{-1},1,\tau \vp) \ge
- [T(\lambda_{i,d}^{-1},1, \vp)]^\tau
- \ge
-  \left[\frac{(i-1)}{C_{\vp}}\right]^\tau \qquad i\in I_{d,\vp},  \ d \in \naturals, \\
-  \label{eq:rest_strong_ineq}
- \frac{1}{T (\lambda_{i,d}^{-1},1,\tau \vp)} \le
-\frac{K_{\vp,\tau}\, C_{\vp}^\tau}{(i-1)^\tau}\qquad \forall i \in I_{d,\vp} \setminus\{1\}, \ d \in \naturals .
-\end{gather}
-
-To complete the proof, we will sum both sides of \eqref{eq:rest_strong_ineq} over the range of $i$ appearing in \eqref{eq:strong_rest_tractiff}, to establish that $S_{\tau\vp}$ is finite.
-To do this we need to show that \eqref{eq:rest_strong_ineq} holds for that range.
-Choose Choose $L_{\tau\vp} = i(\infty,\vp) +1 \ge 2$.
+This is the inequality needed for the lower limit of the sum.
+
 There are three cases.
@@
 
-\item If $M(d) < L_{\tau\vp}$, then 
-\[
-\sum_{i = L_{\tau\vp}}^{M(d)} \frac{1}{T (\lambda_{i,d}^{-1},1, \tau \vp)} = 0,
-\]
-which does not affect the finiteness of $S_{\tau\vp}$.
-
-\item If $M(d) \ge L_{\tau\vp}$ and $E(d) = 0$, then $\{L_{\tau\vp},  \L_{\tau\vp} + 1, \ldots \} \subseteq I_{d,\vp} \setminus \{1\}$.
-
-\item If $M(d) \ge L_{\tau\vp}$ and $E(d) >0$, then \eqref{eq:Mddef} and \eqref{eq:lambda_K_strong4} imply that
-\[
-\lambda_{i(E(d),\vp),d} \le \lambda_{M(d)+1,d} \le E(d) < \lambda_{M(d),d}.
-\]
-This means that $M(d) \le i(E(d),\vp)-1$.  So, $\{L_{\tau\vp}, \ldots, M(d)\} \subseteq I_{d,\vp} \setminus \{1\}$.
+\item If $M(d) <\lceil L_{\vp'} T(0,d,\vp')\rceil$, then 
+\[
+\sum_{i = \lceil L_{\vp'} T(0,d,\vp')\rceil }^{M(d)} \frac{1}{T (\lambda_{i,d}^{-1},1, \vp')} = 0,
+\]
+which does not affect the finiteness of $S_{\vp'}$.
+
+\item If $M(d) \ge \lceil L_{\vp'} T(0,d,\vp')\rceil$ and $E(d) = 0$, then $\{\lceil L_{\vp'} T(0,d,\vp')\rceil,  \lceil L_{\vp'} T(0,d,\vp')\rceil + 1, \ldots \} \subseteq I_{d,\vp} \setminus \{1\}$.
+
+\item If $M(d) \ge \lceil L_{\vp'} T(0,d,\vp')\rceil$ and $E(d) >0$, then \eqref{eq:Mddef} and \eqref{eq:rest_lambda_K4} imply that
+\[
+\lambda_{i(E(d),d,\vp),d} \le \lambda_{M(d)+1,d} \le E(d) < \lambda_{M(d),d}.
+\]
+This means that $M(d) \le i(E(d),d,\vp)-1$.  So, $\{ \lceil L_{\vp'} T(0,d,\vp')\rceil, \ldots, M(d)\} \subseteq I_{d,\vp} \setminus \{1\}$.
 
@@
 \begin{align*}
-S_{\tau\vp} & = \sup_{d\in\naturals} \sum_{i = L_{\tau\vp}}^{M(d)} \frac{1}{T (\lambda_{i,d}^{-1},1, \tau \vp)}
+S_{\vp'} & = \sup_{d\in\naturals} \sum_{i =  \lceil L_{\vp'} T(0,d,\vp')\rceil}^{M(d)} \frac{1}{T (\lambda_{i,d}^{-1},d, \tau \vp)}
 \le 
@@
 \end{enumerate}
-Thus, in all three cases, the assumption of strong tractability on the restricted domain implies \eqref{eq:strong_rest_tractiff} with $\vp$ replaced by $\vp' = \tau \vp$, and so we see the necessity of $\eqref{eq:strong_rest_tractiff}$.
-\bigskip
-
-\noindent \textbf{Optimality:}
-This proof is similar to the proof for the optimality condition for strong tractability in Theorem \ref{thm_main_strong_tract2}.
-We must show that $\cp_{\textup{trct}} = \widetilde{\cp}_{\textup{trct}}$.
-Then, the expression for  $\cp_{\textup{opt}}$ in this theorem automatically follows from its definition in \eqref{eq:Poptdef}.
-
-First we show  that if $\vp^* \in \cp_{\textup{trct}}$, then $\vp^* \in \widetilde{\cp}_{\textup{trct}}$.
-If $\vp^* \in \cp_{\textup{trct}}$, then \eqref{eq:tract_def} must hold for all $\vp' \in (\vp^*,\vinfty)$.
-For any $\vp' \in (\vp^*,\vinfty)$, we may choose $\vp$ and $\tau$ such that $\vp^* < \vp < \vp' = \tau \vp$.
-Since $\vp > \vp^*$, \eqref{eq:tract_def} also holds for $\vp$, and it follows that \eqref{eq:tractiff4} must hold for $\vp'$ by the proof of necessity above.
-Thus, $\vp^* \in \widetilde{\cp}_{\textup{trct}}$.
-
-Next we show that if $\vp^* \in \widetilde{\cp}_{\textup{trct}}$, then $\vp^* \in \cp_{\textup{trct}}$.
-If $\vp^* \in \widetilde{\cp}_{\textup{strct}}$, then \eqref{eq:tractiff4}  holds for all $\vp \in (\vp^*,\vinfty)$.
-By the argument to prove the sufficient condition above, it follows that \eqref{eq:strong_tract_def} must also hold for all $\vp \in (\vp^*,\vinfty)$.
-Thus, $\vp^* \in \cp_{\textup{trct}}$.
-
-Thus,  $\cp_{\textup{opt}}= \widetilde{\cp}_{\textup{opt}}$.  This concludes the proof of Theorem \ref{thm_main_tract2}.
+Thus, in all three cases, the assumption of strong tractability on the restricted domain implies \eqref{eq:rest_tractiff} with $\vp$ replaced by $\vp' = \tau \vp$, and so we see the necessity of $\eqref{eq:rest_tractiff}$.
+\bigskip
+
+\bigskip
+
+\noindent \textbf{Optimality:} \\
+The proof of optimality is analogous to that for Theorem \ref{thm_main_tract2} and is omitted.
+
+\bigskip
+
+\noindent 
+This concludes the proof of Theorem \ref{thm_main_tract2}.
 \end{proof}
 
-Furthermore, for all $d \in \naturals$, let $M(d) = \min \{n : \lambda_{n+1,d} \le E(d) \}$.  This means that 
-\[
-\lambda_{1,d}^{-1} \le \cdots \le \lambda_{M(d),d}^{-1} < E^{-1}(d) \le \lambda_{M(d)+1,d}^{-1}, \qquad (\lambda_{1,d}^{-1},d), \ldots, (\lambda_{M(d),d}^{-1},d) \in \Omega.
-\]
+\fred{Are there cases that we can discuss where we do not have (strong) tractability, but we do have (strong) tractability on a restricted domain, such as $(0,\infty) \times \{1, \ldots, d_{\max}] \cup (\varepsilon_{\min}^{-1},\infty) \times \naturals$}
 

### 2023-06-07 GeneralizedTractability_230529.tex
Updates from Overleaf

@@
 \[
- \sup_{d \in \naturals} \frac{1}{\psi(d,q)} \sum_{i = \lceil L_{(p,q)\psi(d,q)}\rceil}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)} < \infty,
+ \sup_{d \in \naturals} \frac{1}{\psi(d,q)} \sum_{i = \lceil L_{(p,q)}\psi(d,q)\rceil}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)} < \infty,
 \] for some $p,q >0$ and $L_{(p,q)}\in\naturals$.
@@
 \[
- T(\varepsilon^{-1},d,\vp)= \exp\{p(\phi(\varepsilon^{-1})\, \psi(d))\}
- \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp\in [0,\infty).
-\]  with non-decreasing functions $\phi : (0,\infty) \to (0,\infty)$ and $\psi : \naturals \to (0,\infty)$ and $\vp = p$. 
+ T(\varepsilon^{-1},d,p)= \exp\{p \, \phi(\varepsilon^{-1})\, \psi(d)\} = [\exp\{ \phi(\varepsilon^{-1})\}]^{p \, \psi(d)}
+ \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, p\in [0,\infty).
+\]  with non-decreasing functions $\phi : (0,\infty) \to (0,\infty)$ and $\psi : \naturals \to (0,\infty)$. 
 We say that a problem is non-separable tractable with parameter $\vp$ iff there exists a positive $C_{\vp}$ such that
@@
 \[
-\sup_{d\in\mathbb{N}}\frac{1}{\psi(d)}\sum_{i=Lp\,\psi(d)} \phi(\lambda_{i,d})\quad \text{for some } p \geq 0, L_p \in \naturals.
-\]
-We have the following special cases of non-separable tractability. \end{example}
+%\sup_{d\in\mathbb{N}}\frac{1}{\psi(d)}\sum_{i=Lp\,\psi(d)} \phi(\lambda_{i,d})\quad \text{for some } p \geq 0, L_p \in \naturals.
+\sup_{d\in\mathbb{N}}\sum_{i=L_p\,\phi(0)^{p \, \psi(d)}} [\exp\{ \phi(\lambda_{i,d}^{-1})\}]^{p \, \psi(d)}\quad \text{for some } p \geq 0, L_p \in \naturals.
+\]
+\end{example}
+For $\phi$ and $\psi$ of special form, the condition above can be simplified further as in the following two examples of non-separable tractability. 
 \begin{example}[Algebraic quasi-polynomial tractability]
 
-As defined in \cite{GW11}, we say that a problem is \emph{quasi-polynomially tractable (QPT)} if there exist two constants $C$, $t > 0$, such that
+As adefined in \cite{GW11}, we say that a problem is \emph{quasi-polynomially tractable (QPT)} if there exist two constants $C$, $p > 0$, such that
 \begin{equation}\label{expqpt}
-    \comp(\varepsilon,d) \leq C\exp\{t(1+\log(\varepsilon^{-1}))(1+\log(d))\}
-\end{equation}
-for all $\varepsilon \in (0,1]$ and $d\in\mathbb{N}$.\\
-
-\noindent Let the tractability function, $T$,
+    \comp(\varepsilon,d) \leq C\exp\{p(1+\log(\varepsilon^{-1}))(1+\log(d))\}
+\end{equation}
+for all $\varepsilon \in (0,1]$ and $d\in\mathbb{N}$.
+
+Let the tractability function, $T$,
 be defined by
@@
 \begin{equation}
-    \Omega  := \{(\varepsilon^{-1},d) : (E(d),\infty), \ d \in \naturals \}, \qquad \text{where }E : \naturals \to [0,\infty).
+    \Omega  := \{(\varepsilon^{-1},d) : \varepsilon \in (E(d),\infty), \ d \in \naturals \}, \qquad \text{where }E : \naturals \to [0,\infty).
 \end{equation}
@@
 \begin{align*}
-L_{\vp'} & := \left[C_{\vp'} + \frac{2}{T(0,1,\vp')}   \right]
+L_{\vp'} & := C_{\vp'} + \frac{2}{T(0,1,\vp')},
 \intertext{and note that }
- \min(i(\infty,d,\vp'),2) & \le i(\infty,d,\vp') +1  = \lfloor C_{\vp'}\, T(0,d,\vp')\rfloor +2 \le  \left[C_{\vp'} + \frac{2}{T(0,d,\vp')}   \right]\, T(0,d,\vp')\\
+ \max(i(\infty,d,\vp'),2) & \le i(\infty,d,\vp') +1  = \lfloor C_{\vp'}\, T(0,d,\vp')\rfloor +2 \le  \left[C_{\vp'} + \frac{2}{T(0,d,\vp')}   \right]\, T(0,d,\vp')\\
  & \le  L_{\vp'}\, T(0,d,\vp')
@@
 \[
-\sum_{i = \lceil L_{\vp'} T(0,d,\vp')\rceil }^{M(d)} \frac{1}{T (\lambda_{i,d}^{-1},1, \vp')} = 0,
+\sum_{i = \lceil L_{\vp'} T(0,d,\vp')\rceil }^{M(d)} \frac{1}{T (\lambda_{i,d}^{-1},d, \vp')} = 0,
 \]
@@
 
-\fred{Are there cases that we can discuss where we do not have (strong) tractability, but we do have (strong) tractability on a restricted domain, such as $(0,\infty) \times \{1, \ldots, d_{\max}] \cup (\varepsilon_{\min}^{-1},\infty) \times \naturals$}
+\fred{Are there cases that we can discuss where we do not have (strong) tractability, but we do have (strong) tractability on a restricted domain, such as $(0,\infty) \times \{1, \ldots, d_{\max}] \cup (\varepsilon_{\min}^{-1},\infty) \times \naturals$?}
 

### 2023-06-19 GeneralizedTractability_230607.tex
Updates from Overleaf

--- 2023-06-07 GeneralizedTractability_230529.tex
@@
-\documentclass[11pt,a4paper]{article}
-\usepackage{latexsym,amsfonts,amsmath,graphics,mathtools,amssymb,amsthm,booktabs}
+\documentclass[sort&compress]{elsarticle}
+\usepackage{latexsym,amsfonts,amsmath,graphics,mathtools,amssymb,booktabs,xspace}
 \usepackage{epsfig}
@@
 %\usepackage[active]{srcltx}
+\usepackage{fdsymbol}
 \usepackage{enumitem}
@@
 \usepackage{algorithmic}
+\usepackage{hyperref}
+\usepackage{cleveref}
 
@@
 
+\newtheorem{theorem}{Theorem}
+\newdefinition{definition}{Definition}
+\newdefinition{example}{Example}
+\newproof{proof}{Proof}
+
 \begin{document}
 
-\newtheorem{theorem}{Theorem}
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}
-\newtheorem{example}{Example}
-
-\title{Generalized Tractability}
-\author{\fred{Fred J. Hickernell}, \peter{Peter Kritzer}, \kachi{Onyekachi Osisiogu}, and \\ Henryk Wo\'zniakwoski}
+\title{\fred{A Unified Treatment of Tractabilty of Approximation Problems}\\ \peter{[PETER: In view of the papers of Henryk and Michael, maybe we should think of a better title?]}}
+
+\author[1]{Fred J. Hickernell}
+\ead{hickernell@iit.edu}
+\author[2]{Peter Kritzer}
+\author[1]{Onyekachi Osisiogu}
 \date{\today}
+\affiliation[1]{organization={Department of Applied Mathematics, Illinois Institute of Technology},
+addressline={10 West 32${}^{\text{nd}}$ Street, Room 220},
+postcode={60616},
+city={Chicago, IL},
+country={United States}}
+
+\begin{abstract}
+    A large literature specifies conditions under which the information complexity for a sequence of numerical problems defined for dimensions $1, 2, \ldots$ grows at a moderate rate, i.e., the sequence of problems is \emph{tractable}.
+Here we focus on the situation where the space of available information consists of all linear functionals and the problems are defined as operator mappings between Hilbert spaces.
+We unify the proofs of known tractability results and generalize a number of existing results.
+These generalizations are expressed as five theorems that provide equivalent conditions for (strong) tractability in terms of sums of functions of the singular values.
+\end{abstract}
 
@@
 
+The information complexity of a problem is the number of function data required to solve the problem within the desired error tolerance.
+A problem is tractable if the information complexity does not grow too large as the dimension of the problem increases or the error threshold decreases.
+There are a number of tractability results for numerical problems beginning with \cite{?}, spawning numerous articles, and filling a series of three impressive volumes \cite{NovWoz08a,NovWoz10a,NovWoz12a}.
+The purpose of this article is to unify the many of these tractability results for approximation problems where all linear functional data is available.
+
 Let $\{\cf_d\}_{d \in \naturals}$ and $\{\cg_d\}_{d \in \naturals}$ be sequences of Hilbert spaces, and $\{\SOL_d : \cf_d \to \cg_d\}_{d \in \naturals}$ be a sequence of linear solution operators  with adjoints $\SOL_d^*$ such that $\SOL_d^*\SOL_d : \cf_d \to \cf_d$ has eigenvalues and orthonormal eigenvectors
@@
 However, since we assume non-negativity of the $\lambda_{i,d}$, the notation used here is equivalent.
-\peter{[PETER: I am wondering whether we should go back to the more common notation once the manuscript is finalized (not right away).
-It would make the paper easier to read for the IBC community.]}\fred{Fred: If we do, we introduce a lot of $\sqrt{\lambda}$ or $\varepsilon^{-2}$, which I find harder to translate in my brain.
-But I  will submit to the will of the majority.}
-The non-decreasing ordering of the eigenvalues for each $d$ facilitates the proof of conditions for tractability, but our conditions do not depend on the ordering.
+
+%The non-decreasing ordering of the eigenvalues for each $d$ facilitates the proof of conditions for tractability, but our conditions do not depend on the ordering \peter{[PETER: is that really the case?]}.
 
 We make the technical assumption that $\SOL_d$ is a compact operator.
-This implies (see, e.g., \cite{NW08}) that $\lambda_{i,d}$ converges to zero as $i$ tends to infinity for every $d$, which in turn implies that the problem is solvable by suitable algorithms.
+This implies (see, e.g., \cite{NovWoz08a}) that $\lambda_{i,d}$ converges to zero as $i$ tends to infinity for every $d$, which in turn implies that the problem is solvable by suitable algorithms.
 To avoid trivial cases, we assume that there are an infinite number of positive eigenvalues for every $d$.
@@
 The question of tractability is one of determining how fast the complexity increases as $\varepsilon$ tends to zero and/or as $d$ tends to infinity.
-We want to bound the complexity in terms of a simple function of $\varepsilon^{-1}$ and $d$ and identify simple conditions on the singular values that are equivalent to this bound holding.
-
-In this article, we investigate such a function that we refer to as the generalized tractability function, denoted by $T$:
+We want to bound the complexity in terms of a simple function, $T$, of $\varepsilon^{-1}$ and $d$ and identify simple conditions on the singular values that are equivalent to this bound holding.
+
+In this article, we investigate a \emph{generalized tractability function}, denoted by $T$:
 \begin{equation} \label{eq:Tspec}
-    T :(0,\infty) \times \mathbb{N} \times [0,\infty)^s \rightarrow (0,\infty),
+    T :(0,\infty) \times \mathbb{N} \times [0,\infty)^s \rightarrow (0,\infty).
 \end{equation}
@@
 In practice, we expect $T(\varepsilon^{-1},d,\vp)$ to increase mildly with increasing $\varepsilon^{-1}$ and/or $d$, however most of our theorems do not require such an assumption.
+
+\Cref{thm_main_strong_tract2,thm_main_tract2,thm_main_rest_strong_tract,thm_main_rest_tract} all take the form
+\begin{multline}
+  \exists C_{\vp} \text{ with }
+    \comp(\varepsilon, d) \le  C_{\vp}\, T(\varepsilon^{-1},\clubsuit,\vp) \quad \forall (\varepsilon^{-1},d) \in \Omega \\
+    \iff   \exists L_{\vp} \text{ with }
+    \sup_{d \in \naturals}
+     \sum_{i = \lceil L_{\vp}\, T(0,\clubsuit,\vp) \rceil}^{\spadesuit(d)} \frac{1}{T(\lambda^{-1}_{i,d},\clubsuit,\vp)}< \infty, \\
+     \clubsuit \in \{1,d\}, \ \varheartsuit(d) = \inf \{\varepsilon : (\varepsilon^{-1},d) \in \Omega \}, \ 
+     \spadesuit(d) = \begin{cases}
+        \min\{n \in \natzero : \lambda_{n+1,d} \le \varheartsuit(d) \}, &   \varheartsuit(d)< 0, \\
+        \infty, & \varheartsuit(d) = 0.
+        \end{cases}
+\end{multline}
+\Cref{thm:subhT} is of similar, but not equivalent, form.
 
@@
 A general reference
-for results on algebraic tractability is \cite{NW08}, for exponential tractability we refer to \cite{HKW19} and \cite{KW19}.
+for results on algebraic tractability is \cite{NovWoz08a}, for exponential tractability we refer to \cite{HicKriWoz19a} and \cite{KriWoz19a}.
 
@@
 
-Since the $\lambda_{i,d}$ are non-increasing in $i$, it follows that the $T(\lambda_{i,d}^{-1},d',\vp)$ are non-decreasing in $i$ for any $d'\in\naturals$.
+Since the $\lambda_{i,d}$ are non-increasing in $i$, it follows that the $T(\lambda_{i,d}^{-1},\clubsuit,\vp)$ are non-decreasing in $i$ for any $\clubsuit\in\naturals$.
 In particular, for  any $N\in\naturals$ with $n\ge N$, we have
@@
     \lambda_{n+1,d} \le \lambda_{n,d} \le \cdots \le \lambda_{N,d}
-    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d',\vp)} \le \frac{1}{T(\lambda_{n, d}^{-1},d',\vp)} \le \cdots \le \frac{1}{T(\lambda_{N, d}^{-1},d',\vp)} \\
-     \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d',\vp) }
-    \le &\frac{1}{n-N+1} \sum_{i=N}^n  \frac{1}{T(\lambda_{i, d}^{-1},d',\vp) }
-    \le \frac{1}{n-N+1} \sum_{i=N}^\infty  \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)}.
+    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},\clubsuit,\vp)} \le \frac{1}{T(\lambda_{n, d}^{-1},\clubsuit,\vp)} \le \cdots \le \frac{1}{T(\lambda_{N, d}^{-1},\clubsuit,\vp)} \\
+     \implies \frac{1}{T(\lambda_{n+1, d}^{-1},\clubsuit,\vp) }
+    \le &\frac{1}{n-N+1} \sum_{i=N}^n  \frac{1}{T(\lambda_{i, d}^{-1},\clubsuit,\vp) }
+    \le \frac{1}{n-N+1} \sum_{i=N}^\infty  \frac{1}{T(\lambda_{i, d}^{-1},\clubsuit,\vp)}.
 \end{align*}
@@
 \begin{multline} \label{eq:implicate_a}
-    n - N +1 \ge T(\varepsilon^{-1},d',\vp) \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} \\
-   \implies   \frac{1}{T(\lambda_{n+1, d}^{-1},d',\vp)} \le
-   \frac{1}{n-N+1} \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d',\vp) } \le \frac{1}{T(\varepsilon^{-1},d',\vp)} \\ \forall d', n, N \in \naturals.
+    n - N +1 \ge T(\varepsilon^{-1},\clubsuit,\vp) \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},\clubsuit,\vp)} \\
+   \implies   \frac{1}{T(\lambda_{n+1, d}^{-1},\clubsuit,\vp)} \le
+   \frac{1}{n-N+1} \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},\clubsuit,\vp) } \le \frac{1}{T(\varepsilon^{-1},\clubsuit,\vp)} \\ \forall \clubsuit, n, N \in \naturals.
 \end{multline}
@@
 	\nonumber
-	& = \min \biggl\{n \in \natzero : \frac{1}{T(\lambda_{n+1,d}^{-1},d',\vp)}\le \frac{1}{T(\varepsilon^{-1},d',\vp) }\biggr\} \qquad  \forall d'\in \naturals\\
+	& = \min \biggl\{n \in \natzero : \frac{1}{T(\lambda_{n+1,d}^{-1},\clubsuit,\vp)}\le \frac{1}{T(\varepsilon^{-1},\clubsuit,\vp) }\biggr\} \qquad  \forall \clubsuit\in \naturals\\
 	\nonumber
-	& \le  \min \biggl\{n \in \natzero : n \ge N - 1 + T(\varepsilon^{-1},d',\vp) \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} \biggr\} \;  \forall  d', N \in \naturals, \quad \text{by \eqref{eq:implicate_a}} \\
-	& \le  T(\varepsilon^{-1},d',\vp) \Biggl [\frac{N}{T(\varepsilon^{-1},d',\vp)}  +  \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} \Biggr] \quad \forall  d', N \in \naturals.
+	& \le  \min \biggl\{n \in \natzero : n \ge N - 1 + T(\varepsilon^{-1},\clubsuit,\vp) \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},\clubsuit,\vp)} \biggr\} \;  \forall  \clubsuit, N \in \naturals, \quad \text{by \eqref{eq:implicate_a}} \\
+	& \le  T(\varepsilon^{-1},\clubsuit,\vp) \Biggl [\frac{N}{T(\varepsilon^{-1},\clubsuit,\vp)}  +  \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},\clubsuit,\vp)} \Biggr] \quad \forall  \clubsuit, N \in \naturals.
 \label{eq:compUP}
@@
 
-Now we take this upper bound further, specializing to the case of $d'=1$ and $N=L_{\vp}$:
+Now we take this upper bound further, specializing to the case of $\clubsuit=1$ and $N=L_{\vp}$:
 \begin{align*}
@@
 
-\noindent This concludes the proof of  Theorem \ref{thm_main_strong_tract2}.
+\noindent This concludes the proof of  Theorem \ref{thm_main_strong_tract2}. \qed
 
@@
 Suppose that \eqref{eq:tractiff4} holds for some $\vp \ge 0$. 
-By the argument in the proof of the sufficient condition for Theorem \ref{thm_main_strong_tract2}, it follows from \eqref{eq:compUP} with $d'=d$ and $N = \lceil L_{\vp}\, T(0,d,\vp)\rceil$ that 
+By the argument in the proof of the sufficient condition for Theorem \ref{thm_main_strong_tract2}, it follows from \eqref{eq:compUP} with $\clubsuit=d$ and $N = \lceil L_{\vp}\, T(0,d,\vp)\rceil$ that
 \begin{align*}
@@
 
-Thus,  $\cp_{\textup{opt}}= \widetilde{\cp}_{\textup{opt}}$.  This concludes the proof of Theorem \ref{thm_main_tract2}.
+Thus,  $\cp_{\textup{opt}}= \widetilde{\cp}_{\textup{opt}}$.  This concludes the proof of Theorem \ref{thm_main_tract2}.  \qed
 \end{proof}
@@
 \section{Examples} \label{sec:examples}
-
-In this section, we illustrate Theorems \ref{thm_main_strong_tract2} and \ref{thm_main_tract2} for the types of tractability given in the table in Section \ref{sec:not}.
-
+%In this section, we illustrate Theorems \ref{thm_main_strong_tract2} and \ref{thm_main_tract2} for the types of tractability given in the table in Section \ref{sec:not}.
+In this section, we present six examples related to Theorem \ref{thm_main_strong_tract2} and Theorem \ref{thm_main_tract2} introduced in Section \ref{sec:spt}.
+We will continue to present examples in later sections.
+
+In Section 2.2 we considered strong tractability. 
 \begin{example}[Strong algebraic polynomial tractability]
@@
 Furthermore, the optimal $p$ is the infimum of all $p$ for which the above condition holds.
-This essentially recovers the result in \cite[Theorem 5.1]{NW08}.
+This essentially recovers the result in \cite[Theorem 5.1]{NovWoz08a}.
 \end{example}
@@
 \end{multline*}
-This essentially recovers the result on polynomial tractability in \cite[Theorem 5.1]{NW08} \fred{same theorem as above??, what about optimality in \cite[Theorem 5.1]{NW08}}.
+This essentially recovers the result on polynomial tractability in \cite[Theorem 5.1]{NovWoz08a} %\fred{same theorem as above??, what about optimality in \cite[Theorem 5.1]{NovWoz08a}}.
 \end{example}
@@
 
-As adefined in \cite{GW11}, we say that a problem is \emph{quasi-polynomially tractable (QPT)} if there exist two constants $C$, $p > 0$, such that
+As defined in \cite{GneWoz11a}, we say that a problem is \emph{quasi-polynomially tractable (QPT)} if there exist two constants $C$, $p > 0$, such that
 \begin{equation}\label{expqpt}
@@
 \begin{proof}
-The idea of this proof follows \cite{WW17}.
+The idea of this proof follows \cite{WerWoz17a}.
 We suppress the $\vp$ dependence in the proof, because it insignificant.
@@
 Combining this bound with the upper bound on $S_c$ in \eqref{eq:lastone} establishes the finiteness of $S_{2c}$ and completes the proof of the necessary condition.
-This concludes the proof of Theorem \ref{thm:subhT}.
+This concludes the proof of Theorem \ref{thm:subhT}.  \qed
 \end{proof}
@@
 \begin{equation}
-    \Omega  := \{(\varepsilon^{-1},d) : \varepsilon \in (E(d),\infty), \ d \in \naturals \}, \qquad \text{where }E : \naturals \to [0,\infty).
+    \Omega  := \{(\varepsilon^{-1},d) : \varepsilon \in (\varheartsuit(d),\infty), \ d \in \naturals \}, \qquad \text{where }E : \naturals \to [0,\infty).
 \end{equation}
@@
 \begin{equation} \label{eq:Mddef}
-    M(d) := \begin{cases}
-        \min\{n \in \natzero : \lambda_{n+1,d} \le E(d)\}, & E(d) > 0, \\
-        \infty, & E(d) = 0.
+    \spadesuit(d) := \begin{cases}
+        \min\{n \in \natzero : \lambda_{n+1,d} \le \varheartsuit(d)\}, & \varheartsuit(d) > 0, \\
+        \infty, & \varheartsuit(d) = 0.
     \end{cases}
@@
 \hI_{d}:=\begin{cases} 
-\emptyset, & M(d) = 0, \\
-\{1,\ldots, M(d)\}, & 0 < M(d) < \infty, \\
-\naturals, & M(d) = \infty.
+\emptyset, & \spadesuit(d) = 0, \\
+\{1,\ldots, \spadesuit(d)\}, & 0 < \spadesuit(d) < \infty, \\
+\naturals, & \spadesuit(d) = \infty.
 \end{cases}
 \end{equation}
-From the definition of $M(d)$ it follows that $(\lambda_{i,d}^{-1},d) \in \Omega  \iff i \in \hI_d$, and
+From the definition of $\spadesuit(d)$ it follows that $(\lambda_{i,d}^{-1},d) \in \Omega  \iff i \in \hI_d$, and
 \begin{equation} \label{eq:comprestr}
   \comp(\varepsilon,d) \begin{cases}
-= 0, & M(d) = 0, \\
-    \in \hI_d, & M(d) > 0, 
+= 0, & \spadesuit(d) = 0, \\
+    \in \hI_d, & \spadesuit(d) > 0, 
 \end{cases}
@@
 
-The equivalent conditions for (strong) $T$-tractability on a restricted domain in Theorems \ref{thm_main_rest_strong_tract} and \ref{thm_main_rest_tract} mimic the conditions given in Theorems \ref{thm_main_strong_tract2} and \ref{thm_main_tract2}, except that the upper limits on the sums now correspond to $M(d)$ rather than $\infty$.
+The equivalent conditions for (strong) $T$-tractability on a restricted domain in Theorems \ref{thm_main_rest_strong_tract} and \ref{thm_main_rest_tract} mimic the conditions given in Theorems \ref{thm_main_strong_tract2} and \ref{thm_main_tract2}, except that the upper limits on the sums now correspond to $\spadesuit(d)$ rather than $\infty$.
 The proofs are a bit more delicate, but similar arguments are used.
 
-We note that it may be possible to define $\Omega$ such that $\lambda_{1,d} > E(d)$ for all $d \in \naturals$.
-In this case, $M(d) = 0$ for all $d \in \naturals$, the equivalent conditions for (strong) tractability are trivially satisfied, and the zero algorithm satisfies the error tolerance.
+We note that it may be possible to define $\Omega$ such that $\lambda_{1,d} > \varheartsuit(d)$ for all $d \in \naturals$.
+In this case, $\spadesuit(d) = 0$ for all $d \in \naturals$, the equivalent conditions for (strong) tractability are trivially satisfied, and the zero algorithm satisfies the error tolerance.
 
@@
 \begin{equation} \label{eq:strong_rest_tractiff}
-     S_{\vp}:=\sup_{d \in \naturals} \sum_{i = L_{\vp}}^{M(d)} \frac{1}{T(\lambda_{i,d}^{-1},1,\vp)} < \infty.
-\end{equation}
-By convention, if $M(d) < L_{\vp}$, the sum is zero.
+     S_{\vp}:=\sup_{d \in \naturals} \sum_{i = L_{\vp}}^{\spadesuit(d)} \frac{1}{T(\lambda_{i,d}^{-1},1,\vp)} < \infty.
+\end{equation}
+By convention, if $\spadesuit(d) < L_{\vp}$, the sum is zero.
 
@@
 \textbf{Sufficient condition:}\newline
-Fix $d$.  If $M(d) = 0$, then $\comp(\varepsilon,d) = 0 \le C_{\vp}\, T(\varepsilon^{-1},1,\vp)$ automatically for all $\varepsilon \in [E(d), \infty)$.
-
-For the case $M(d)> 0$, following the argument for the sufficient condition in Theorem \ref{thm_main_strong_tract2} it follows that for all $d' \in \naturals$ and integers $n, N \in \hI_d$  with $N \le n$, we have
+Fix $d$.  If $\spadesuit(d) = 0$, then $\comp(\varepsilon,d) = 0 \le C_{\vp}\, T(\varepsilon^{-1},1,\vp)$ automatically for all $\varepsilon \in [\varheartsuit(d), \infty)$.
+
+For the case $\spadesuit(d)> 0$, following the argument for the sufficient condition in Theorem \ref{thm_main_strong_tract2} it follows that for all $\clubsuit \in \naturals$ and integers $n, N \in \hI_d$  with $N \le n$, we have
 \begin{align*}
     \lambda_{n+1,d} \le \lambda_{n,d} \le \cdots \le \lambda_{N,d}
-    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d',\vp)} \le \frac{1}{T(\lambda_{n, d}^{-1},d',\vp)} \le \cdots \le \frac{1}{T(\lambda_{N, d}^{-1},d',\vp)} \\
-     \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d',\vp) }
-    \le &\frac{1}{n-N+1} \sum_{i=N}^n  \frac{1}{T(\lambda_{i, d}^{-1},d',\vp) }
-    \le \frac{1}{n-N+1} \sum_{i=N}^{M(d)}  \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)}.
+    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},\clubsuit,\vp)} \le \frac{1}{T(\lambda_{n, d}^{-1},\clubsuit,\vp)} \le \cdots \le \frac{1}{T(\lambda_{N, d}^{-1},\clubsuit,\vp)} \\
+     \implies \frac{1}{T(\lambda_{n+1, d}^{-1},\clubsuit,\vp) }
+    \le &\frac{1}{n-N+1} \sum_{i=N}^n  \frac{1}{T(\lambda_{i, d}^{-1},\clubsuit,\vp) }
+    \le \frac{1}{n-N+1} \sum_{i=N}^{\spadesuit(d)}  \frac{1}{T(\lambda_{i, d}^{-1},\clubsuit,\vp)}.
 \end{align*}
@@
 \begin{multline} \label{eq:implicate_a_rest}
-    n - N +1 \ge T(\varepsilon^{-1},d',\vp) \sum_{i=N}^{M(d)} \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} \\
-   \implies   \frac{1}{T(\lambda_{n+1, d}^{-1},d',\vp)} \le
-   \frac{1}{n-N+1} \sum_{i=N}^{M(d)} \frac{1}{T(\lambda_{i, d}^{-1},d',\vp) } \le \frac{1}{T(\varepsilon^{-1},d',\vp)} \\ \forall d' \in \naturals,\  n, N \in \hI_d,   \ N \le n.
+    n - N +1 \ge T(\varepsilon^{-1},\clubsuit,\vp) \sum_{i=N}^{\spadesuit(d)} \frac{1}{T(\lambda_{i, d}^{-1},\clubsuit,\vp)} \\
+   \implies   \frac{1}{T(\lambda_{n+1, d}^{-1},\clubsuit,\vp)} \le
+   \frac{1}{n-N+1} \sum_{i=N}^{\spadesuit(d)} \frac{1}{T(\lambda_{i, d}^{-1},\clubsuit,\vp) } \le \frac{1}{T(\varepsilon^{-1},\clubsuit,\vp)} \\ \forall \clubsuit \in \naturals,\  n, N \in \hI_d,   \ N \le n.
 \end{multline}
@@
 	\nonumber
-	& = \min \biggl\{n \in \hI_d : \frac{1}{T(\lambda_{n+1,d}^{-1},d',\vp)}\le \frac{1}{T(\varepsilon^{-1},d',\vp) }\biggr\} \qquad  \forall d'\in \naturals\\
+	& = \min \biggl\{n \in \hI_d : \frac{1}{T(\lambda_{n+1,d}^{-1},\clubsuit,\vp)}\le \frac{1}{T(\varepsilon^{-1},\clubsuit,\vp) }\biggr\} \qquad  \forall \clubsuit\in \naturals\\
 	\nonumber
-	& \le  \min \biggl\{n \in \hI_d : n \ge N - 1 + T(\varepsilon^{-1},d',\vp) \sum_{i=N}^{M(d)} \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} \biggr\} \;  \forall  d', \ 1 \le N \le M(d) \\
+	& \le  \min \biggl\{n \in \hI_d : n \ge N - 1 + T(\varepsilon^{-1},\clubsuit,\vp) \sum_{i=N}^{\spadesuit(d)} \frac{1}{T(\lambda_{i, d}^{-1},\clubsuit,\vp)} \biggr\} \;  \forall  \clubsuit, \ 1 \le N \le \spadesuit(d) \\
  \nonumber
@@
  \intertext{
- This last statement holds for all $N \le M(d)$ because $n \ge N$ automatically in the expression above.  Thus,}
+ This last statement holds for all $N \le \spadesuit(d)$ because $n \ge N$ automatically in the expression above.  Thus,}
  \comp(\varepsilon,d)
-	& \le  T(\varepsilon^{-1},d',\vp) \Biggl [\frac{N}{T(\varepsilon^{-1},d',\vp)}  +  \sum_{i=N}^{M(d)} \frac{1}{T(\lambda_{i, d}^{-1},d',\vp)} \Biggr] \quad \forall  d',\ 1 \le N \le M(d).
+	& \le  T(\varepsilon^{-1},\clubsuit,\vp) \Biggl [\frac{N}{T(\varepsilon^{-1},\clubsuit,\vp)}  +  \sum_{i=N}^{\spadesuit(d)} \frac{1}{T(\lambda_{i, d}^{-1},\clubsuit,\vp)} \Biggr] \quad \forall  \clubsuit,\ 1 \le N \le \spadesuit(d).
 \label{eq:compUP_rest}
@@
 
-Now we take this upper bound further, specializing to the case of $d'=1$ and $N = \min(L_{\vp},M(d))$:
+Now we take this upper bound further, specializing to the case of $\clubsuit=1$ and $N = \min(L_{\vp},\spadesuit(d))$:
 \begin{align*}
        \comp(\varepsilon,d)
-       & \le T(\varepsilon^{-1},1, \vp) \Biggl [ \frac{\min(L_{\vp},M(d))}{T(\varepsilon^{-1},1, \vp)}  + \underbrace{\sum_{i = \min(L_{\vp},M(d))}^{M(d)} \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}}_{\le S_{\vp} + 1/ T(\lambda_{M(d), d}^{-1},1,\vp) \text{ by \eqref{eq:strong_rest_tractiff}} }
+       & \le T(\varepsilon^{-1},1, \vp) \Biggl [ \frac{\min(L_{\vp},\spadesuit(d))}{T(\varepsilon^{-1},1, \vp)}  + \underbrace{\sum_{i = \min(L_{\vp},\spadesuit(d))}^{\spadesuit(d)} \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}}_{\le S_{\vp} + 1/ T(\lambda_{\spadesuit(d), d}^{-1},1,\vp) \text{ by \eqref{eq:strong_rest_tractiff}} }
         \Biggr] \\
@@
 \begin{equation}\label{eq:lambda_K_strong4}
-\lambda_{\lfloor C_{\vp}\, T(\varepsilon^{-1},1,\vp)\rfloor +1,d}\le \varepsilon \qquad \forall \varepsilon > E(d), \ d \in \mathbb{N}.
+\lambda_{\lfloor C_{\vp}\, T(\varepsilon^{-1},1,\vp)\rfloor +1,d}\le \varepsilon \qquad \forall \varepsilon > \varheartsuit(d), \ d \in \mathbb{N}.
 \end{equation}
@@
 \[
-i(\varepsilon,\vp)\le C_{\vp}\, T(\varepsilon^{-1},1,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,\vp),d}^{-1},1,\vp)+1, \qquad  \forall \varepsilon > E(d), \ d \in \mathbb{N},
+i(\varepsilon,\vp)\le C_{\vp}\, T(\varepsilon^{-1},1,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,\vp),d}^{-1},1,\vp)+1, \qquad  \forall \varepsilon > \varheartsuit(d), \ d \in \mathbb{N},
 \]
@@
 
-For $\varepsilon$ taking on all values in $(E(d),\infty)$, $i(\varepsilon,\vp)$ takes on (at least) all values in
+For $\varepsilon$ taking on all values in $(\varheartsuit(d),\infty)$, $i(\varepsilon,\vp)$ takes on (at least) all values in
 \[
 I_{d,\vp}:=\begin{cases} 
-\emptyset, & i(E(d),\vp) = i(\infty,\vp) \\
-\{i(\infty,\vp),\ldots, i(E(d),\vp)-1\}, & E(d) > 0, \\
-\{i(\infty,\vp), i(\infty,\vp) + 1, \ldots\}, & E(d) = 0.
+\emptyset, & i(\varheartsuit(d),\vp) = i(\infty,\vp) \\
+\{i(\infty,\vp),\ldots, i(\varheartsuit(d),\vp)-1\}, & \varheartsuit(d) > 0, \\
+\{i(\infty,\vp), i(\infty,\vp) + 1, \ldots\}, & \varheartsuit(d) = 0.
 \end{cases}
@@
 
-\item If $M(d) < L_{\tau\vp}$, then 
-\[
-\sum_{i = L_{\tau\vp}}^{M(d)} \frac{1}{T (\lambda_{i,d}^{-1},1, \tau \vp)} = 0,
+\item If $\spadesuit(d) < L_{\tau\vp}$, then 
+\[
+\sum_{i = L_{\tau\vp}}^{\spadesuit(d)} \frac{1}{T (\lambda_{i,d}^{-1},1, \tau \vp)} = 0,
 \]
@@
 
-\item If $M(d) \ge L_{\tau\vp}$ and $E(d) = 0$, then $\{L_{\tau\vp},  L_{\tau\vp} + 1, \ldots \} \subseteq I_{d,\vp} \setminus \{1\}$.
-
-\item If $M(d) \ge L_{\tau\vp}$ and $E(d) >0$, then \eqref{eq:Mddef} and \eqref{eq:lambda_K_strong4} imply that
-\[
-\lambda_{i(E(d),\vp),d} \le \lambda_{M(d)+1,d} \le E(d) < \lambda_{M(d),d}.
-\]
-This means that $M(d) \le i(E(d),\vp)-1$.  So, $\{L_{\tau\vp}, \ldots, M(d)\} \subseteq I_{d,\vp} \setminus \{1\}$.
+\item If $\spadesuit(d) \ge L_{\tau\vp}$ and $\varheartsuit(d) = 0$, then $\{L_{\tau\vp},  L_{\tau\vp} + 1, \ldots \} \subseteq I_{d,\vp} \setminus \{1\}$.
+
+\item If $\spadesuit(d) \ge L_{\tau\vp}$ and $\varheartsuit(d) >0$, then \eqref{eq:Mddef} and \eqref{eq:lambda_K_strong4} imply that
+\[
+\lambda_{i(\varheartsuit(d),\vp),d} \le \lambda_{\spadesuit(d)+1,d} \le \varheartsuit(d) < \lambda_{\spadesuit(d),d}.
+\]
+This means that $\spadesuit(d) \le i(\varheartsuit(d),\vp)-1$.  So, $\{L_{\tau\vp}, \ldots, \spadesuit(d)\} \subseteq I_{d,\vp} \setminus \{1\}$.
 
@@
 \begin{align*}
-S_{\tau\vp} & = \sup_{d\in\naturals} \sum_{i = L_{\tau\vp}}^{M(d)} \frac{1}{T (\lambda_{i,d}^{-1},1, \tau \vp)}
+S_{\tau\vp} & = \sup_{d\in\naturals} \sum_{i = L_{\tau\vp}}^{\spadesuit(d)} \frac{1}{T (\lambda_{i,d}^{-1},1, \tau \vp)}
 \le 
@@
 
-\noindent This concludes the proof of  Theorem \ref{thm_main_rest_strong_tract}.
+\noindent This concludes the proof of  Theorem \ref{thm_main_rest_strong_tract}.  \qed
 \end{proof}
@@
      S_{\vp}:=\sup_{d \in \naturals}
-     \sum_{i = \lceil L_{\vp}\, T(0,d,\vp) \rceil}^{M(d)} \frac{1}{T(\lambda^{-1}_{i,d},d,\vp)}< \infty.
+     \sum_{i = \lceil L_{\vp}\, T(0,d,\vp) \rceil}^{\spadesuit(d)} \frac{1}{T(\lambda^{-1}_{i,d},d,\vp)}< \infty.
 \end{equation}
@@
     \textbf{Sufficient Condition:}\\
-Fix $d$.  If $M(d) = 0$, then $\comp(\varepsilon,d) = 0 \le C_{\vp}\, T(\varepsilon^{-1},d,\vp)$ automatically for all $\varepsilon \in [E(d), \infty)$.
-
-For the case $M(d)> 0$, we utilize upper bound \eqref{eq:compUP_rest}, specializing to the case of $d'=d$ and $N = \min\left(\lceil L_{\vp}\, T(0,d,\vp)\rceil,M(d)\right)$:
+Fix $d$.  If $\spadesuit(d) = 0$, then $\comp(\varepsilon,d) = 0 \le C_{\vp}\, T(\varepsilon^{-1},d,\vp)$ automatically for all $\varepsilon \in [\varheartsuit(d), \infty)$.
+
+For the case $\spadesuit(d)> 0$, we utilize upper bound \eqref{eq:compUP_rest}, specializing to the case of $\clubsuit=d$ and $N = \min\left(\lceil L_{\vp}\, T(0,d,\vp)\rceil,\spadesuit(d)\right)$:
 \begin{align*}
        \comp(\varepsilon,d)
-       & \le T(\varepsilon^{-1},d, \vp) \Biggl [ \frac{\min\left(\lceil L_{\vp}\, T(0,d,\vp)\rceil,M(d)\right)}{T(\varepsilon^{-1},d, \vp)}  + \underbrace{\sum_{i = \min\left(\lceil L_{\vp}\, T(0,d,\vp)\rceil,M(d)\right)}^{M(d)} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}}_{\le S_{\vp} + 1/ T(\lambda_{M(d), d}^{-1},d,\vp) \text{ by \eqref{eq:strong_rest_tractiff}} }
+       & \le T(\varepsilon^{-1},d, \vp) \Biggl [ \frac{\min\left(\lceil L_{\vp}\, T(0,d,\vp)\rceil,\spadesuit(d)\right)}{T(\varepsilon^{-1},d, \vp)}  + \underbrace{\sum_{i = \min\left(\lceil L_{\vp}\, T(0,d,\vp)\rceil,\spadesuit(d)\right)}^{\spadesuit(d)} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}}_{\le S_{\vp} + 1/ T(\lambda_{\spadesuit(d), d}^{-1},d,\vp) \text{ by \eqref{eq:strong_rest_tractiff}} }
         \Biggr] \\
-       & \le T(\varepsilon^{-1},d,\vp)\left[\frac{ L_{\vp}\, T(0,d,\vp)+1}{T(0,d, \vp)} + S_{\vp} + \frac{1}{T(\lambda_{M(d), d}^{-1},d,\vp)} \right]
+       & \le T(\varepsilon^{-1},d,\vp)\left[\frac{ L_{\vp}\, T(0,d,\vp)+1}{T(0,d, \vp)} + S_{\vp} + \frac{1}{T(\lambda_{\spadesuit(d), d}^{-1},d,\vp)} \right]
        \qquad \text{by \eqref{eq:Tnondecreasing}}\\
@@
 	\lambda_{\lfloor C_{\vp}\, T(\varepsilon^{-1},d,\vp)\rfloor +1,d}\le \varepsilon \qquad 
- \forall \varepsilon > E(d),\ d \in \naturals.
+ \forall \varepsilon > \varheartsuit(d),\ d \in \naturals.
 \end{equation}
@@
 \[
-i(\varepsilon,d,\vp)\le C_{\vp}\, T(\varepsilon^{-1},d,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,d,\vp),d}^{-1},d,\vp)+1, \qquad \forall \varepsilon > E(d),\ d \in \naturals.
-\]
-For $\varepsilon$ taking on all values in $(E(d),\infty)$, $i(\varepsilon,d,\vp)$ takes on (at least) all values in
+i(\varepsilon,d,\vp)\le C_{\vp}\, T(\varepsilon^{-1},d,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,d,\vp),d}^{-1},d,\vp)+1, \qquad \forall \varepsilon > \varheartsuit(d),\ d \in \naturals.
+\]
+For $\varepsilon$ taking on all values in $(\varheartsuit(d),\infty)$, $i(\varepsilon,d,\vp)$ takes on (at least) all values in
 \[
 I_{d,\vp}:=\begin{cases} 
-\emptyset, & i(E(d),d,\vp) = i(\infty,d,\vp), \\
-\{i(\infty,d,\vp),\ldots, i(E(d),d,\vp)-1\}, & E(d) > 0, \\
-\{i(\infty,d,\vp), i(\infty,d,\vp) + 1, \ldots\}, & E(d) = 0.
+\emptyset, & i(\varheartsuit(d),d,\vp) = i(\infty,d,\vp), \\
+\{i(\infty,d,\vp),\ldots, i(\varheartsuit(d),d,\vp)-1\}, & \varheartsuit(d) > 0, \\
+\{i(\infty,d,\vp), i(\infty,d,\vp) + 1, \ldots\}, & \varheartsuit(d) = 0.
 \end{cases}
@@
 
-\item If $M(d) <\lceil L_{\vp'} T(0,d,\vp')\rceil$, then 
-\[
-\sum_{i = \lceil L_{\vp'} T(0,d,\vp')\rceil }^{M(d)} \frac{1}{T (\lambda_{i,d}^{-1},d, \vp')} = 0,
+\item If $\spadesuit(d) <\lceil L_{\vp'} T(0,d,\vp')\rceil$, then 
+\[
+\sum_{i = \lceil L_{\vp'} T(0,d,\vp')\rceil }^{\spadesuit(d)} \frac{1}{T (\lambda_{i,d}^{-1},d, \vp')} = 0,
 \]
@@
 
-\item If $M(d) \ge \lceil L_{\vp'} T(0,d,\vp')\rceil$ and $E(d) = 0$, then $\{\lceil L_{\vp'} T(0,d,\vp')\rceil,  \lceil L_{\vp'} T(0,d,\vp')\rceil + 1, \ldots \} \subseteq I_{d,\vp} \setminus \{1\}$.
-
-\item If $M(d) \ge \lceil L_{\vp'} T(0,d,\vp')\rceil$ and $E(d) >0$, then \eqref{eq:Mddef} and \eqref{eq:rest_lambda_K4} imply that
-\[
-\lambda_{i(E(d),d,\vp),d} \le \lambda_{M(d)+1,d} \le E(d) < \lambda_{M(d),d}.
-\]
-This means that $M(d) \le i(E(d),d,\vp)-1$.  So, $\{ \lceil L_{\vp'} T(0,d,\vp')\rceil, \ldots, M(d)\} \subseteq I_{d,\vp} \setminus \{1\}$.
+\item If $\spadesuit(d) \ge \lceil L_{\vp'} T(0,d,\vp')\rceil$ and $\varheartsuit(d) = 0$, then $\{\lceil L_{\vp'} T(0,d,\vp')\rceil,  \lceil L_{\vp'} T(0,d,\vp')\rceil + 1, \ldots \} \subseteq I_{d,\vp} \setminus \{1\}$.
+
+\item If $\spadesuit(d) \ge \lceil L_{\vp'} T(0,d,\vp')\rceil$ and $\varheartsuit(d) >0$, then \eqref{eq:Mddef} and \eqref{eq:rest_lambda_K4} imply that
+\[
+\lambda_{i(\varheartsuit(d),d,\vp),d} \le \lambda_{\spadesuit(d)+1,d} \le \varheartsuit(d) < \lambda_{\spadesuit(d),d}.
+\]
+This means that $\spadesuit(d) \le i(\varheartsuit(d),d,\vp)-1$.  So, $\{ \lceil L_{\vp'} T(0,d,\vp')\rceil, \ldots, \spadesuit(d)\} \subseteq I_{d,\vp} \setminus \{1\}$.
 
@@
 \begin{align*}
-S_{\vp'} & = \sup_{d\in\naturals} \sum_{i =  \lceil L_{\vp'} T(0,d,\vp')\rceil}^{M(d)} \frac{1}{T (\lambda_{i,d}^{-1},d, \tau \vp)}
+S_{\vp'} & = \sup_{d\in\naturals} \sum_{i =  \lceil L_{\vp'} T(0,d,\vp')\rceil}^{\spadesuit(d)} \frac{1}{T (\lambda_{i,d}^{-1},d, \tau \vp)}
 \le 
@@
 \noindent 
-This concludes the proof of Theorem \ref{thm_main_tract2}.
+This concludes the proof of Theorem \ref{thm_main_tract2}.  \qed
 \end{proof}
@@
 
-\begin{thebibliography}{99}
-\bibitem{GW11} M. Gnewuch, H.~~Wo\'zniakowski. Quasi-polynomial tractability, J.~Complexity, 27, 312--330 2011.
-\bibitem{HKW19} F.J.~Hickernell, P. Kritzer, H.~Wo\'zniakowski.  Exponential tractability of linear tensor product problems. In:
-D.R.~Wood, J.~DeGier, C.~Praeger, T.~Tao (eds.), 2018 MATRIX Annals, 61--78, Springer, Cham, 2020.
-\bibitem{KW19} P. Kritzer, H.~Wo\'zniakowski.
-Simple characterizations of exponential tractability for linear
-multivariate problems. J.~Complexity 51, 110--128, 2019.
-\bibitem{NW08} E.~Novak, H.~Wo\'zniakowski. \textit{Tractability of Multivariate Problems, Volume I: Linear Information}.
-European Mathematical Society Publishing House, Zurich, 2008.
- \bibitem{WW17} A.G.~Werschulz, H.~Wo\'zniakowski. A new characterization of $(s,t)$-weak tractability. J. Complexity 38, 68--79, 2017.
-
-\end{thebibliography}
+\bibliography{FJHOwn23,FJH23}
+\bibliographystyle{elsarticle-num}
 

### 2023-06-20 GeneralizedTractability_230607.tex
Updates from Overleaf

@@
      \sum_{i = \lceil L_{\vp}\, T(0,\clubsuit,\vp) \rceil}^{\spadesuit(d)} \frac{1}{T(\lambda^{-1}_{i,d},\clubsuit,\vp)}< \infty, \\
-     \clubsuit \in \{1,d\}, \ \varheartsuit(d) = \inf \{\varepsilon : (\varepsilon^{-1},d) \in \Omega \}, \ 
-     \spadesuit(d) = \begin{cases}
-        \min\{n \in \natzero : \lambda_{n+1,d} \le \varheartsuit(d) \}, &   \varheartsuit(d)< 0, \\
+     \clubsuit \in \{1,d\}, \ \varheartsuit(d) := \inf \{\varepsilon : (\varepsilon^{-1},d) \in \Omega \}, \ 
+     \spadesuit(d) := \begin{cases}
+        \min\{n \in \natzero : \lambda_{n+1,d} \le \varheartsuit(d) \}, &   \varheartsuit(d) > 0, \\
         \infty, & \varheartsuit(d) = 0.
@@
 which implies that the problem is expected to be no easier by decreasing the tolerance, $\varepsilon$, or increasing the dimension, $d$.
-Furthermore, increasing $\vp$ does not decrease $T(\cdot, \cdot, \vp)$.
+(This is why we make $T$ a function of $\varepsilon^{-1}$ rather than of $\varepsilon$.) Furthermore, increasing $\vp$ does not decrease $T(\cdot, \cdot, \vp)$.
 Since there are an infinite number of positive eigenvalues, it also makes sense to assume that
@@
 Since $T(\cdot,d,\vp)$ is non-decreasing, we may define the following limit, which we assume will always be positive:
-\begin{equation}\label{eq:T0}	T(0,d,\vp):=\lim_{\varepsilon\to\infty}T(\varepsilon^{-1},d,\vp) \ge T(0,1,\vzero) > 0.
+\begin{equation}\label{eq:T0}	T(0,d,\vp):=\lim_{\varepsilon\to\infty}T(\varepsilon^{-1},d,\vp) = \inf_\varepsilon T(\varepsilon^{-1},d,\vp) \ge T(0,1,\vzero) > 0.
 \end{equation}
@@
 %In this section, we illustrate Theorems \ref{thm_main_strong_tract2} and \ref{thm_main_tract2} for the types of tractability given in the table in Section \ref{sec:not}.
-In this section, we present six examples related to Theorem \ref{thm_main_strong_tract2} and Theorem \ref{thm_main_tract2} introduced in Section \ref{sec:spt}.
+In this section, we present six examples relating to Theorem \ref{thm_main_strong_tract2} and Theorem \ref{thm_main_tract2}, both of which were introduced in Section \ref{sec:spt}, for the various types of tractability that are listed in Table \ref{tab:commonT}.
+In subsequent sections, we will continue to present various examples.
+
+%In this section, we present six examples related to Theorem \ref{thm_main_strong_tract2} and Theorem  introduced in Section \ref{sec:spt} where the types of tractability were given in the table.
 We will continue to present examples in later sections.
 
-In Section 2.2 we considered strong tractability. 
+The (strong) polynomial tractability for both the algebraic case and the exponential case will be first considered as follows: 
 \begin{example}[Strong algebraic polynomial tractability]
@@
 \end{example}
-
+We summarize the tractability notions in the previous examples in the following example. The
 \begin{example}[(Strong) Separable tractability]

### 2023-06-25 GeneralizedTractability_230607.tex
Updates from Overleaf

@@
 
+%certain important notations for key symbols
+\newcommand{\thed}{\clubsuit}
+\newcommand{\theM}{\varheartsuit}
+\newcommand{theUB}{\spadesuit}
+
 \input{FJHDef.tex}
@@
 
-\title{\fred{A Unified Treatment of Tractabilty of Approximation Problems}\\ \peter{[PETER: In view of the papers of Henryk and Michael, maybe we should think of a better title?]}}
+\title{\fred{A Unified Treatment of Tractabilty of Approximation Problems}}
 
@@
 \author[2]{Peter Kritzer}
+\ead{peter.kritzer@oeaw.ac.at}
 \author[1]{Onyekachi Osisiogu}
@@
 country={United States}}
+\affiliation[2]{organization={Johann Radon Institute for Computational and Applied Mathematics (RICAM), Austrian Academy of Sciences},
+addressline={Altenbergerstr. 69},
+postcode={4040},
+city={Linz},
+country={Austria}}
 
@@
 
+TODO: We should check for consistency of the use of the $\forall$ symbol in displayed formulas. Sometimes we use it, sometimes we do not, sometimes it is preceded by a comma, sometimes not, etc.
+
 The information complexity of a problem is the number of function data required to solve the problem within the desired error tolerance.
@@
 
-The information complexity of the problem $\SOL_d$ is given by the function $\comp:(0,\infty) \times \naturals \to \natzero$, where $\comp(\varepsilon,d)$ is the number of linear functionals required by the best algorithm to satisfy the error criterion \eqref{eq:errcrit}.
+The information complexity of the problem $\SOL_d$ is given by the function $\comp:(0,\infty) \times \naturals \to \natzero$, where $\comp(\varepsilon,d)$ is the number of linear functionals required by the best \peter{admissible} algorithm to satisfy the error criterion \eqref{eq:errcrit}.
 By definition, the complexity is non-decreasing  as $\varepsilon$ tends to zero.
@@
 \[
-\APP_d(f,\varepsilon) = \sum_{i=1}^n \SOL(u_i) \ip[\cf_d]{f}{u_i},
+\APP_d(f,\varepsilon) = \sum_{i=1}^n \peter{\SOL_d(u_{i,d})} \ip[\cf_d]{f}{u_i},
 \]
@@
 \begin{equation}\label{eq:comp_def}
-\comp(\varepsilon, d) = \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon\}, \qquad \comp:(0,\infty) \times \naturals \to \natzero.
-\end{equation}
-
-The question of tractability is one of determining how fast the complexity increases as $\varepsilon$ tends to zero and/or as $d$ tends to infinity.
+\comp(\varepsilon, d) = \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon\}.
+\end{equation}
+
+The question of tractability is one of determining how fast the \peter{information} complexity increases as $\varepsilon$ tends to zero and/or as $d$ tends to infinity.
 We want to bound the complexity in terms of a simple function, $T$, of $\varepsilon^{-1}$ and $d$ and identify simple conditions on the singular values that are equivalent to this bound holding.
+\peter{[PETER: Maybe this would be a good place to refer to the earlier work of Michael and Henryk?
+I will take care of it...
+.]}
 
@@
 \end{equation}
-The conditions we require $T$ to satisfy are described in  Section \ref{sec:not}, however, the basic idea is that we we define our approximation problem to be tractable if 
+The conditions we require $T$ to satisfy are described in  Section \ref{sec:not}, however, the basic idea is that we define our approximation problem to be tractable if 
 $\comp(\varepsilon, d) \le  C_{\vp}\, T(\varepsilon^{-1},d,\vp)$ for some constant, $C_{\vp}$, depending only on the parameter $\vp$.
-In practice, we expect $T(\varepsilon^{-1},d,\vp)$ to increase mildly with increasing $\varepsilon^{-1}$ and/or $d$, however most of our theorems do not require such an assumption.
+In practice, we expect $T(\varepsilon^{-1},d,\vp)$ to increase sub-exponentially  with increasing $\varepsilon^{-1}$ and/or $d$, however most of our theorems do not require such an assumption.
 
 \Cref{thm_main_strong_tract2,thm_main_tract2,thm_main_rest_strong_tract,thm_main_rest_tract} all take the form
+
+\peter{[PETER: Not meaning to sound too negative, but I am not sure I like the notation with the symbols below. Is it possible to use something different instead?]}
+\fred{Fred: I have now given them names above in lines 18-20, so we can experiment with different symbols or letters.}
 \begin{multline}
   \exists C_{\vp} \text{ with }
-    \comp(\varepsilon, d) \le  C_{\vp}\, T(\varepsilon^{-1},\clubsuit,\vp) \quad \forall (\varepsilon^{-1},d) \in \Omega \\
+    \comp(\varepsilon, d) \le  C_{\vp}\, T(\varepsilon^{-1},\thed,\vp) \quad \forall (\varepsilon^{-1},d) \in \Omega \\
     \iff   \exists L_{\vp} \text{ with }
     \sup_{d \in \naturals}
-     \sum_{i = \lceil L_{\vp}\, T(0,\clubsuit,\vp) \rceil}^{\spadesuit(d)} \frac{1}{T(\lambda^{-1}_{i,d},\clubsuit,\vp)}< \infty, \\
-     \clubsuit \in \{1,d\}, \ \varheartsuit(d) := \inf \{\varepsilon : (\varepsilon^{-1},d) \in \Omega \}, \ 
-     \spadesuit(d) := \begin{cases}
-        \min\{n \in \natzero : \lambda_{n+1,d} \le \varheartsuit(d) \}, &   \varheartsuit(d) > 0, \\
-        \infty, & \varheartsuit(d) = 0.
+     \sum_{i = \lceil L_{\vp}\, T(0,\thed,\vp) \rceil}^{\theUB(d)} \frac{1}{T(\lambda^{-1}_{i,d},\thed,\vp)}< \infty, \\
+     \thed \in \{1,d\}, \ \theM(d) := \inf \{\varepsilon : (\varepsilon^{-1},d) \in \Omega \}, \ 
+     \theUB(d) := \begin{cases}
+        \min\{n \in \natzero : \lambda_{n+1,d} \le \theM(d) \}, &   \theM(d) > 0, \\
+        \infty, & \theM(d) = 0.
         \end{cases}
@@
 In Section \ref{sec:spt}, we give the definitions of the considered tractability notions, in particular (strong) tractability.
-We consider the strong tractability when the information complexity is independent of the dimension, $d$.
+We consider strong tractability when the information complexity is independent of the dimension, $d$.
 We then turn to tractability  when the information complexity is polynomial in $d$ and $\varepsilon^{-1}$.
@@
 Let $T$ be a function given in \eqref{eq:Tspec}.
-A tractability function, $T$ is a function of simple form that provides an upper bound on the computational complexity of a problem.
+A tractability function $T$ is a function of simple form that provides an upper bound on the \peter{information} complexity of a problem.
 Some examples of tractability functions commonly considered are provided in Table \ref{tab:commonT}.
@@
 \begin{table} 
-    \caption{Common forms of the tractability function, $T$}
+    \caption{Common forms of the tractability function, $T$. \peter{[PETER: I changed the notation below, using ``algebraic" and ``exponential" first, to be in line with the literature.]}}
 {\small
@@
 		\toprule
-		\text{strong polynomial algebraic} & \max(1,\varepsilon^{-p}) & 1\\
-		\text{polynomial algebraic} & \max(1,\varepsilon^{-p})d^{q} & d^{q}\\
-		\text{strong polynomial exponential} &  [\max(1,\log(1 + \varepsilon^{-1})]^p & 1\\
-		\text{polynomial exponential } &
+		\text{\peter{algebraic strong polynomial}} & \max(1,\varepsilon^{-p}) & 1\\
+		\text{\peter{algebraic polynomial}} & \max(1,\varepsilon^{-p})d^{q} & d^{q}\\
+		\text{\peter{exponential strong polynomial}} &  [\max(1,\log(1 + \varepsilon^{-1})]^p & 1\\
+		\text{\peter{exponential polynomial}} &
 		[\max(1,\log(1 + \varepsilon^{-1}))]^p  d^{q} & d^{q} \\
-        \text{quasi-polynomial algebraic} & 
+        \text{\peter{algebraic quasi-polynomial}} & 
         \exp\{p(1+\log(\max(1,\varepsilon^{-1}))(1+\log(d))\} &
         \exp\{p(1+\log(d))\}\\
-        \text{quasi-polynomial exponential} & 
+        \text{\peter{exponential quasi-polynomial}} & 
         \exp\{p(1+\log(\max\{1,\log(1+\varepsilon^{-1})\}))(1+\log(d))\} &
@@
 A problem is \emph{strongly}
-$T$-tractable with parameter $\vp$ iff the complexity is independent of the dimension of the problem, that is, there exists a positive constant $C_{\vp}$, again independent of $\varepsilon$ and $d$, such that
+$T$-tractable with parameter $\vp$ iff the \peter{information} complexity is independent of the dimension of the problem, that is, there exists a positive constant $C_{\vp}$, again independent of $\varepsilon$ and $d$, such that
 \begin{equation} \label{eq:strong_tract_def}
@@
 Since there are an infinite number of positive eigenvalues, it also makes sense to assume that
-\begin{equation}
+\begin{equation}\label{eq:Tlim}
 	\lim_{\varepsilon \to 0} T(\varepsilon^{-1},d,\vp) = \infty \qquad \forall d \in \naturals, \ \vp \in [0,\infty)^s.
@@
 
-Since the $\lambda_{i,d}$ are non-increasing in $i$, it follows that the $T(\lambda_{i,d}^{-1},\clubsuit,\vp)$ are non-decreasing in $i$ for any $\clubsuit\in\naturals$.
+Since the $\lambda_{i,d}$ are non-increasing in $i$, it follows that the $T(\lambda_{i,d}^{-1},\thed,\vp)$ are non-decreasing in $i$ for any $\thed\in\naturals$.
 In particular, for  any $N\in\naturals$ with $n\ge N$, we have
@@
     \lambda_{n+1,d} \le \lambda_{n,d} \le \cdots \le \lambda_{N,d}
-    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},\clubsuit,\vp)} \le \frac{1}{T(\lambda_{n, d}^{-1},\clubsuit,\vp)} \le \cdots \le \frac{1}{T(\lambda_{N, d}^{-1},\clubsuit,\vp)} \\
-     \implies \frac{1}{T(\lambda_{n+1, d}^{-1},\clubsuit,\vp) }
-    \le &\frac{1}{n-N+1} \sum_{i=N}^n  \frac{1}{T(\lambda_{i, d}^{-1},\clubsuit,\vp) }
-    \le \frac{1}{n-N+1} \sum_{i=N}^\infty  \frac{1}{T(\lambda_{i, d}^{-1},\clubsuit,\vp)}.
+    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},\thed,\vp)} \le \frac{1}{T(\lambda_{n, d}^{-1},\thed,\vp)} \le \cdots \le \frac{1}{T(\lambda_{N, d}^{-1},\thed,\vp)} \\
+     \implies \frac{1}{T(\lambda_{n+1, d}^{-1},\thed,\vp) }
+    \le &\frac{1}{n-N+1} \sum_{i=N}^n  \frac{1}{T(\lambda_{i, d}^{-1},\thed,\vp) }
+    \le \frac{1}{n-N+1} \sum_{i=N}^\infty  \frac{1}{T(\lambda_{i, d}^{-1},\thed,\vp)}.
 \end{align*}
@@
 \begin{multline} \label{eq:implicate_a}
-    n - N +1 \ge T(\varepsilon^{-1},\clubsuit,\vp) \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},\clubsuit,\vp)} \\
-   \implies   \frac{1}{T(\lambda_{n+1, d}^{-1},\clubsuit,\vp)} \le
-   \frac{1}{n-N+1} \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},\clubsuit,\vp) } \le \frac{1}{T(\varepsilon^{-1},\clubsuit,\vp)} \\ \forall \clubsuit, n, N \in \naturals.
+    n - N +1 \ge T(\varepsilon^{-1},\thed,\vp) \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},\thed,\vp)} \\
+   \implies   \frac{1}{T(\lambda_{n+1, d}^{-1},\thed,\vp)} \le
+   \frac{1}{n-N+1} \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},\thed,\vp) } \le \frac{1}{T(\varepsilon^{-1},\thed,\vp)} \\ \forall \thed, n, N \in \naturals.
 \end{multline}
@@
 	\nonumber
-	& = \min \biggl\{n \in \natzero : \frac{1}{T(\lambda_{n+1,d}^{-1},\clubsuit,\vp)}\le \frac{1}{T(\varepsilon^{-1},\clubsuit,\vp) }\biggr\} \qquad  \forall \clubsuit\in \naturals\\
+	& = \min \biggl\{n \in \natzero : \frac{1}{T(\lambda_{n+1,d}^{-1},\thed,\vp)}\le \frac{1}{T(\varepsilon^{-1},\thed,\vp) }\biggr\} \qquad  \forall \thed\in \naturals\\
 	\nonumber
-	& \le  \min \biggl\{n \in \natzero : n \ge N - 1 + T(\varepsilon^{-1},\clubsuit,\vp) \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},\clubsuit,\vp)} \biggr\} \;  \forall  \clubsuit, N \in \naturals, \quad \text{by \eqref{eq:implicate_a}} \\
-	& \le  T(\varepsilon^{-1},\clubsuit,\vp) \Biggl [\frac{N}{T(\varepsilon^{-1},\clubsuit,\vp)}  +  \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},\clubsuit,\vp)} \Biggr] \quad \forall  \clubsuit, N \in \naturals.
+	& \le  \min \biggl\{n \in \natzero : n \ge N - 1 + T(\varepsilon^{-1},\thed,\vp) \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},\thed,\vp)} \biggr\} \;  \forall  \thed, N \in \naturals, \quad \text{by \eqref{eq:implicate_a}} \\
+	& \le  T(\varepsilon^{-1},\thed,\vp) \Biggl [\frac{N}{T(\varepsilon^{-1},\thed,\vp)}  +  \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},\thed,\vp)} \Biggr] \quad \forall  \thed, N \in \naturals.
 \label{eq:compUP}
@@
 
-Now we take this upper bound further, specializing to the case of $\clubsuit=1$ and $N=L_{\vp}$:
+Now we take this upper bound further, specializing to the case of $\thed=1$ and $N=L_{\vp}$:
 \begin{align*}
@@
 
-For $\varepsilon$ taking on all positive values, $i(\varepsilon,\vp)$ takes on all values greater than or equal to $i(\infty,\vp)$, so
+For $\varepsilon$ taking on all positive values, $i(\varepsilon,\vp)$ takes on, \peter{by \eqref{eq:Tlim},} all values greater than or equal to $i(\infty,\vp)$, so
 \[
@@
 \]
-This implies via our technical assumption \eqref{eq:ptauassume} that
+This implies via our technical assumption \eqref{eq:ptauassume} that, \peter{for any $\tau>1$,}
 \begin{gather*}
@@
 \begin{proof}
-    \textbf{Sufficient Condition:}\\
+    \textbf{Sufficient condition:}\\
 Suppose that \eqref{eq:tractiff4} holds for some $\vp \ge 0$. 
-By the argument in the proof of the sufficient condition for Theorem \ref{thm_main_strong_tract2}, it follows from \eqref{eq:compUP} with $\clubsuit=d$ and $N = \lceil L_{\vp}\, T(0,d,\vp)\rceil$ that
+By the argument in the proof of the sufficient condition for Theorem \ref{thm_main_strong_tract2}, it follows from \eqref{eq:compUP} with $\thed=d$ and $N = \lceil L_{\vp}\, T(0,d,\vp)\rceil$ that 
 \begin{align*}
@@
        \underbrace{\left [  L_{\vp} + \frac{1}{T(0,1, \vp)} + S_{\vp} \right]}_{=:C_{\vp}}
-       \qquad \text{by \eqref{eq:Tnondecreasing}}  
+       \qquad \text{by \eqref{eq:Tnondecreasing}} .
 \end{align*}
@@
 
-For $\varepsilon$ taking on all positive values, $i(\varepsilon,d,\vp)$ takes on all values greater than or equal to $i(\infty,d,\vp)$, so
+For $\varepsilon$ taking on all positive values, $i(\varepsilon,d,\vp)$ takes on, \peter{by \eqref{eq:Tlim},} all values greater than or equal to $i(\infty,d,\vp)$, so
 \[
@@
 The (strong) polynomial tractability for both the algebraic case and the exponential case will be first considered as follows:
-\begin{example}[Strong algebraic polynomial tractability]
+
+\begin{example}[\peter{Algebraic strong} polynomial tractability]
 
@@
 \[
- T(\varepsilon^{-1},d,\vp)= \max\{1,\varepsilon^{-p}\}
+ T(\varepsilon^{-1},d,\vp)= \max\{1,\varepsilon^{-\peter{\vp}}\}
  \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty),
-\]  where in this case $\vp$ is a scalar.
-Then Theorem \ref{thm_main_strong_tract2} yields the  equivalent condition for strong algebraic polynomial tractability:
-\[
- \sup_{d\in\naturals} \sum_{i=L_p}^\infty (\min\{1,\lambda_{i,d}^p\}) < \infty \text{ for some } p \ge 0, L_p \in \naturals.
+\]  
+where in this case \peter{$\vp=p$} is a scalar.
+Then Theorem \ref{thm_main_strong_tract2} yields the  equivalent condition for \peter{algebraic strong polynomial tractability}:
+\[
+ \sup_{d\in\naturals} \sum_{i=L_p}^\infty \min\{1,\lambda_{i,d}^p\} < \infty \text{ for some } p \ge 0, L_p \in \naturals.
 \]
@@
 \[
- T(\varepsilon^{-1},d,\vp)= \max\{1,\varepsilon^{-p}\}\, d^q
+ T(\varepsilon^{-1},d,\vp)= \max\{1,\varepsilon^{-\peter{\vp}}\}\, d^q
  \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty)^2, 
@@
 \[
- \sup_{d\in\naturals}\, d^{-q} \sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty (\min\{1,\lambda_{i,d}^p\})  < \infty \text{ for some } p,q \ge 0, L_{(p,q)} \in \naturals.
+ \sup_{d\in\naturals}\, d^{-q} \sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty \min\{1,\lambda_{i,d}^p\}  < \infty \text{ for some } p,q \ge 0, L_{(p,q)} \in \naturals.
 \]
@@
 
-\begin{example}[Strong exponential polynomial tractability]
+\begin{example}[\peter{Exponential strong} polynomial tractability]
 Let the tractability function, $T$,
@@
 \[
- T(\varepsilon^{-1},d,\vp)= \left[\max\{1,\log(1+\varepsilon^{-1})\}\right]^p, \quad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty),
-\]
-where $\vp$ is a scalar. Then Theorem \ref{thm_main_strong_tract2} yields the equivalent condition for strong exponential polynomial tractability \[
- \sup_{d\in\naturals} \sum_{i=L_{p} }^\infty (\min\{1,\log(1+\lambda_{i,d}\})^{p}  < \infty,\quad  \text{ for some } p \ge 0, L_{p} \in \naturals
+ T(\varepsilon^{-1},d,\vp)= \left[\max\{1,\log(1+\varepsilon^{-1})\}\right]^{\peter{\vp}}, \quad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty),
+\]
+%\kachi{Alternatively:
+%\[
+%T(\varepsilon^{-1},d,\vp) = (1+\log\max\{1,\varepsilon^{-1}\})^p
+%\]}
+where \peter{$\vp=p$} is a scalar. Then Theorem \ref{thm_main_strong_tract2} yields the equivalent condition for \peter{exponential strong polynomial tractability:} 
+\[
+ \sup_{d\in\naturals} \sum_{i=L_{p} }^\infty (\min\{1,\log(1+\lambda_{i,d}\})^{p}  < \infty,\quad  \text{ for some } p \ge 0, L_{p} \in \naturals.
 \] In this case the optimal $p$ is the infimum of all $p$ for which the above condition holds.
@@
 \end{example}
-We summarize the tractability notions in the previous examples in the following example. The
+
+\peter{[PETER: Are we sure that the conditions in Examples 3 and 4 are correct?
+And, moreover, these conditions should recover the corresponding conditions in \cite{KriWoz19a}.
+The conditions look different at first sight, but probably it can be shown that they are equivalent...
+.}
+
+In the following example, we provide a brief summary of these notions of tractability. We would like to emphasize that this example was previously known (see \cite{}). 
 \begin{example}[(Strong) Separable tractability]
@@
 \[
-\comp(\varepsilon,d) \leq  C_{\vp}\,\phi(\varepsilon^{-1},p)\, \psi(d,q)\qquad \forall \varepsilon >0, \, d\in\naturals,
-\] where $\vp = (p,q)$.
+\comp(\varepsilon,d) \leq  C_{\vp} \,  \phi(\varepsilon^{-1},p)\, \psi(d,q)\qquad \forall \varepsilon >0, \, d\in\naturals.
+\]
 A problem is strongly $T$-separable tractable with parameter $\vp$ iff the complexity is independent of $d$, that is, there exists a positive constant $C_{\vp}$ which again does not depend on $\varepsilon$ and $d$ such that
 \[
-\comp(\varepsilon,d) \leq C_{\vp}\phi(\varepsilon^{-1},p)\qquad \forall \varepsilon >0, \, d\in\naturals,
-\] where $\vp = p$ is a scalar. 
-Furthermore, we assume the following as in \eqref{eq:Tconditions} and \eqref{eq:ptauassume}. We assume that
+\comp(\varepsilon,d) \leq C_{\vp}\,\phi(\varepsilon^{-1},p)\qquad \forall \varepsilon >0, \, d\in\naturals,
+\] where in this case $\vp = p$ is a scalar. 
+Furthermore, we assume the following as in \eqref{eq:Tlim}, \eqref{eq:T0}, and \eqref{eq:ptauassume}. We assume that
+
 \[
@@
 \begin{equation*} \label{eq:strong_tractiff}
-     \sup_{d \in \naturals} \sum_{i = L_p}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)} < \infty.
+     \sup_{d \in \naturals} \sum_{i = L_p}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)} < \infty,
 \end{equation*}
+for some $p>0$ and $L_p \in \naturals$. Furthermore, the optimal $p$ is also infimum of all $p$.
 Theorem \ref{thm_main_tract2} yields the following equivalent condition for 
@@
 \end{example}
-
+Next, we will introduce another summarized notion of tractability. 
 \begin{example}[Non-separable tractability]
@@
 \]  with non-decreasing functions $\phi : (0,\infty) \to (0,\infty)$ and $\psi : \naturals \to (0,\infty)$. 
-We say that a problem is non-separable tractable with parameter $\vp$ iff there exists a positive $C_{\vp}$ such that
-
-\[\comp(\varepsilon,d) \leq  C_{\vp}\exp\{p(\phi(\varepsilon^{-1})\psi(d))\}.\]
+We say that a problem is non-separable tractable with parameter $p$ iff there exists a positive $C_{p}$ such that
+
+\[\comp(\varepsilon,d) \leq  C_{p}\exp\{p(\phi(\varepsilon^{-1})\psi(d))\}.\]
 
@@
 \[
- T(\varepsilon^{-1},d,\vp)= \exp\{p(1+\log(\max\{1,\varepsilon^{-1}\}))(1+\log (d))\}  \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty),
-\] where in this case $\vp = p$. This can be rewritten as 
-\[
-T(\varepsilon^{-1},d,\vp) = e^p[\max\{1,\varepsilon^{-1}\}]^{p(1+\log d)}d^p
+ T(\varepsilon^{-1},d,p)= \exp\{p(1+\log(\max\{1,\varepsilon^{-1}\}))(1+\log (d))\}  \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, p \in [0,\infty).
+\] This can be rewritten as 
+\[
+T(\varepsilon^{-1},d,p) = e^p[\max\{1,\varepsilon^{-1}\}]^{p(1+\log d)}d^p
 \]
@@
 \end{example}
+Next, we will consider the exponential case as follows.
 \begin{example}[Exponential quasi-polynomial tractability]
@@
 \begin{equation}
-    \Omega  := \{(\varepsilon^{-1},d) : \varepsilon \in (\varheartsuit(d),\infty), \ d \in \naturals \}, \qquad \text{where }E : \naturals \to [0,\infty).
+    \Omega  := \{(\varepsilon^{-1},d) : \varepsilon \in (\theM(d),\infty), \ d \in \naturals \}, \qquad \text{where }E : \naturals \to [0,\infty).
 \end{equation}
@@
 \begin{equation} \label{eq:Mddef}
-    \spadesuit(d) := \begin{cases}
-        \min\{n \in \natzero : \lambda_{n+1,d} \le \varheartsuit(d)\}, & \varheartsuit(d) > 0, \\
-        \infty, & \varheartsuit(d) = 0.
+    \theUB(d) := \begin{cases}
+        \min\{n \in \natzero : \lambda_{n+1,d} \le \theM(d)\}, & \theM(d) > 0, \\
+        \infty, & \theM(d) = 0.
     \end{cases}
@@
 \hI_{d}:=\begin{cases} 
-\emptyset, & \spadesuit(d) = 0, \\
-\{1,\ldots, \spadesuit(d)\}, & 0 < \spadesuit(d) < \infty, \\
-\naturals, & \spadesuit(d) = \infty.
+\emptyset, & \theUB(d) = 0, \\
+\{1,\ldots, \theUB(d)\}, & 0 < \theUB(d) < \infty, \\
+\naturals, & \theUB(d) = \infty.
 \end{cases}
 \end{equation}
-From the definition of $\spadesuit(d)$ it follows that $(\lambda_{i,d}^{-1},d) \in \Omega  \iff i \in \hI_d$, and
+From the definition of $\theUB(d)$ it follows that $(\lambda_{i,d}^{-1},d) \in \Omega  \iff i \in \hI_d$, and
 \begin{equation} \label{eq:comprestr}
   \comp(\varepsilon,d) \begin{cases}
-= 0, & \spadesuit(d) = 0, \\
-    \in \hI_d, & \spadesuit(d) > 0, 
+= 0, & \theUB(d) = 0, \\
+    \in \hI_d, & \theUB(d) > 0, 
 \end{cases}
@@
 
-The equivalent conditions for (strong) $T$-tractability on a restricted domain in Theorems \ref{thm_main_rest_strong_tract} and \ref{thm_main_rest_tract} mimic the conditions given in Theorems \ref{thm_main_strong_tract2} and \ref{thm_main_tract2}, except that the upper limits on the sums now correspond to $\spadesuit(d)$ rather than $\infty$.
+The equivalent conditions for (strong) $T$-tractability on a restricted domain in Theorems \ref{thm_main_rest_strong_tract} and \ref{thm_main_rest_tract} mimic the conditions given in Theorems \ref{thm_main_strong_tract2} and \ref{thm_main_tract2}, except that the upper limits on the sums now correspond to $\theUB(d)$ rather than $\infty$.
 The proofs are a bit more delicate, but similar arguments are used.
 
-We note that it may be possible to define $\Omega$ such that $\lambda_{1,d} > \varheartsuit(d)$ for all $d \in \naturals$.
-In this case, $\spadesuit(d) = 0$ for all $d \in \naturals$, the equivalent conditions for (strong) tractability are trivially satisfied, and the zero algorithm satisfies the error tolerance.
+We note that it may be possible to define $\Omega$ such that $\lambda_{1,d} > \theM(d)$ for all $d \in \naturals$.
+In this case, $\theUB(d) = 0$ for all $d \in \naturals$, the equivalent conditions for (strong) tractability are trivially satisfied, and the zero algorithm satisfies the error tolerance.
 
@@
 \begin{equation} \label{eq:strong_rest_tractiff}
-     S_{\vp}:=\sup_{d \in \naturals} \sum_{i = L_{\vp}}^{\spadesuit(d)} \frac{1}{T(\lambda_{i,d}^{-1},1,\vp)} < \infty.
-\end{equation}
-By convention, if $\spadesuit(d) < L_{\vp}$, the sum is zero.
+     S_{\vp}:=\sup_{d \in \naturals} \sum_{i = L_{\vp}}^{\theUB(d)} \frac{1}{T(\lambda_{i,d}^{-1},1,\vp)} < \infty.
+\end{equation}
+By convention, if $\theUB(d) < L_{\vp}$, the sum is zero.
 
@@
 \textbf{Sufficient condition:}\newline
-Fix $d$.  If $\spadesuit(d) = 0$, then $\comp(\varepsilon,d) = 0 \le C_{\vp}\, T(\varepsilon^{-1},1,\vp)$ automatically for all $\varepsilon \in [\varheartsuit(d), \infty)$.
-
-For the case $\spadesuit(d)> 0$, following the argument for the sufficient condition in Theorem \ref{thm_main_strong_tract2} it follows that for all $\clubsuit \in \naturals$ and integers $n, N \in \hI_d$  with $N \le n$, we have
+Fix $d$.  If $\theUB(d) = 0$, then $\comp(\varepsilon,d) = 0 \le C_{\vp}\, T(\varepsilon^{-1},1,\vp)$ automatically for all $\varepsilon \in [\theM(d), \infty)$.
+
+For the case $\theUB(d)> 0$, following the argument for the sufficient condition in Theorem \ref{thm_main_strong_tract2} it follows that for all $\thed \in \naturals$ and integers $n, N \in \hI_d$  with $N \le n$, we have
 \begin{align*}
     \lambda_{n+1,d} \le \lambda_{n,d} \le \cdots \le \lambda_{N,d}
-    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},\clubsuit,\vp)} \le \frac{1}{T(\lambda_{n, d}^{-1},\clubsuit,\vp)} \le \cdots \le \frac{1}{T(\lambda_{N, d}^{-1},\clubsuit,\vp)} \\
-     \implies \frac{1}{T(\lambda_{n+1, d}^{-1},\clubsuit,\vp) }
-    \le &\frac{1}{n-N+1} \sum_{i=N}^n  \frac{1}{T(\lambda_{i, d}^{-1},\clubsuit,\vp) }
-    \le \frac{1}{n-N+1} \sum_{i=N}^{\spadesuit(d)}  \frac{1}{T(\lambda_{i, d}^{-1},\clubsuit,\vp)}.
+    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},\thed,\vp)} \le \frac{1}{T(\lambda_{n, d}^{-1},\thed,\vp)} \le \cdots \le \frac{1}{T(\lambda_{N, d}^{-1},\thed,\vp)} \\
+     \implies \frac{1}{T(\lambda_{n+1, d}^{-1},\thed,\vp) }
+    \le &\frac{1}{n-N+1} \sum_{i=N}^n  \frac{1}{T(\lambda_{i, d}^{-1},\thed,\vp) }
+    \le \frac{1}{n-N+1} \sum_{i=N}^{\theUB(d)}  \frac{1}{T(\lambda_{i, d}^{-1},\thed,\vp)}.
 \end{align*}
@@
 \begin{multline} \label{eq:implicate_a_rest}
-    n - N +1 \ge T(\varepsilon^{-1},\clubsuit,\vp) \sum_{i=N}^{\spadesuit(d)} \frac{1}{T(\lambda_{i, d}^{-1},\clubsuit,\vp)} \\
-   \implies   \frac{1}{T(\lambda_{n+1, d}^{-1},\clubsuit,\vp)} \le
-   \frac{1}{n-N+1} \sum_{i=N}^{\spadesuit(d)} \frac{1}{T(\lambda_{i, d}^{-1},\clubsuit,\vp) } \le \frac{1}{T(\varepsilon^{-1},\clubsuit,\vp)} \\ \forall \clubsuit \in \naturals,\  n, N \in \hI_d,   \ N \le n.
+    n - N +1 \ge T(\varepsilon^{-1},\thed,\vp) \sum_{i=N}^{\theUB(d)} \frac{1}{T(\lambda_{i, d}^{-1},\thed,\vp)} \\
+   \implies   \frac{1}{T(\lambda_{n+1, d}^{-1},\thed,\vp)} \le
+   \frac{1}{n-N+1} \sum_{i=N}^{\theUB(d)} \frac{1}{T(\lambda_{i, d}^{-1},\thed,\vp) } \le \frac{1}{T(\varepsilon^{-1},\thed,\vp)} \\ \forall \thed \in \naturals,\  n, N \in \hI_d,   \ N \le n.
 \end{multline}
@@
 	\nonumber
-	& = \min \biggl\{n \in \hI_d : \frac{1}{T(\lambda_{n+1,d}^{-1},\clubsuit,\vp)}\le \frac{1}{T(\varepsilon^{-1},\clubsuit,\vp) }\biggr\} \qquad  \forall \clubsuit\in \naturals\\
+	& = \min \biggl\{n \in \hI_d : \frac{1}{T(\lambda_{n+1,d}^{-1},\thed,\vp)}\le \frac{1}{T(\varepsilon^{-1},\thed,\vp) }\biggr\} \qquad  \forall \thed\in \naturals\\
 	\nonumber
-	& \le  \min \biggl\{n \in \hI_d : n \ge N - 1 + T(\varepsilon^{-1},\clubsuit,\vp) \sum_{i=N}^{\spadesuit(d)} \frac{1}{T(\lambda_{i, d}^{-1},\clubsuit,\vp)} \biggr\} \;  \forall  \clubsuit, \ 1 \le N \le \spadesuit(d) \\
+	& \le  \min \biggl\{n \in \hI_d : n \ge N - 1 + T(\varepsilon^{-1},\thed,\vp) \sum_{i=N}^{\theUB(d)} \frac{1}{T(\lambda_{i, d}^{-1},\thed,\vp)} \biggr\} \;  \forall  \thed, \ 1 \le N \le \theUB(d) \\
  \nonumber
@@
  \intertext{
- This last statement holds for all $N \le \spadesuit(d)$ because $n \ge N$ automatically in the expression above.  Thus,}
+ This last statement holds for all $N \le \theUB(d)$ because $n \ge N$ automatically in the expression above.  Thus,}
  \comp(\varepsilon,d)
-	& \le  T(\varepsilon^{-1},\clubsuit,\vp) \Biggl [\frac{N}{T(\varepsilon^{-1},\clubsuit,\vp)}  +  \sum_{i=N}^{\spadesuit(d)} \frac{1}{T(\lambda_{i, d}^{-1},\clubsuit,\vp)} \Biggr] \quad \forall  \clubsuit,\ 1 \le N \le \spadesuit(d).
+	& \le  T(\varepsilon^{-1},\thed,\vp) \Biggl [\frac{N}{T(\varepsilon^{-1},\thed,\vp)}  +  \sum_{i=N}^{\theUB(d)} \frac{1}{T(\lambda_{i, d}^{-1},\thed,\vp)} \Biggr] \quad \forall  \thed,\ 1 \le N \le \theUB(d).
 \label{eq:compUP_rest}
@@
 
-Now we take this upper bound further, specializing to the case of $\clubsuit=1$ and $N = \min(L_{\vp},\spadesuit(d))$:
+Now we take this upper bound further, specializing to the case of $\thed=1$ and $N = \min(L_{\vp},\theUB(d))$:
 \begin{align*}
        \comp(\varepsilon,d)
-       & \le T(\varepsilon^{-1},1, \vp) \Biggl [ \frac{\min(L_{\vp},\spadesuit(d))}{T(\varepsilon^{-1},1, \vp)}  + \underbrace{\sum_{i = \min(L_{\vp},\spadesuit(d))}^{\spadesuit(d)} \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}}_{\le S_{\vp} + 1/ T(\lambda_{\spadesuit(d), d}^{-1},1,\vp) \text{ by \eqref{eq:strong_rest_tractiff}} }
+       & \le T(\varepsilon^{-1},1, \vp) \Biggl [ \frac{\min(L_{\vp},\theUB(d))}{T(\varepsilon^{-1},1, \vp)}  + \underbrace{\sum_{i = \min(L_{\vp},\theUB(d))}^{\theUB(d)} \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}}_{\le S_{\vp} + 1/ T(\lambda_{\theUB(d), d}^{-1},1,\vp) \text{ by \eqref{eq:strong_rest_tractiff}} }
         \Biggr] \\
@@
 \begin{equation}\label{eq:lambda_K_strong4}
-\lambda_{\lfloor C_{\vp}\, T(\varepsilon^{-1},1,\vp)\rfloor +1,d}\le \varepsilon \qquad \forall \varepsilon > \varheartsuit(d), \ d \in \mathbb{N}.
+\lambda_{\lfloor C_{\vp}\, T(\varepsilon^{-1},1,\vp)\rfloor +1,d}\le \varepsilon \qquad \forall \varepsilon > \theM(d), \ d \in \mathbb{N}.
 \end{equation}
@@
 \[
-i(\varepsilon,\vp)\le C_{\vp}\, T(\varepsilon^{-1},1,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,\vp),d}^{-1},1,\vp)+1, \qquad  \forall \varepsilon > \varheartsuit(d), \ d \in \mathbb{N},
+i(\varepsilon,\vp)\le C_{\vp}\, T(\varepsilon^{-1},1,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,\vp),d}^{-1},1,\vp)+1, \qquad  \forall \varepsilon > \theM(d), \ d \in \mathbb{N},
 \]
@@
 
-For $\varepsilon$ taking on all values in $(\varheartsuit(d),\infty)$, $i(\varepsilon,\vp)$ takes on (at least) all values in
+For $\varepsilon$ taking on all values in $(\theM(d),\infty)$, $i(\varepsilon,\vp)$ takes on (at least) all values in
 \[
 I_{d,\vp}:=\begin{cases} 
-\emptyset, & i(\varheartsuit(d),\vp) = i(\infty,\vp) \\
-\{i(\infty,\vp),\ldots, i(\varheartsuit(d),\vp)-1\}, & \varheartsuit(d) > 0, \\
-\{i(\infty,\vp), i(\infty,\vp) + 1, \ldots\}, & \varheartsuit(d) = 0.
+\emptyset, & i(\theM(d),\vp) = i(\infty,\vp) \\
+\{i(\infty,\vp),\ldots, i(\theM(d),\vp)-1\}, & \theM(d) > 0, \\
+\{i(\infty,\vp), i(\infty,\vp) + 1, \ldots\}, & \theM(d) = 0.
 \end{cases}
@@
 
-\item If $\spadesuit(d) < L_{\tau\vp}$, then 
-\[
-\sum_{i = L_{\tau\vp}}^{\spadesuit(d)} \frac{1}{T (\lambda_{i,d}^{-1},1, \tau \vp)} = 0,
+\item If $\theUB(d) < L_{\tau\vp}$, then 
+\[
+\sum_{i = L_{\tau\vp}}^{\theUB(d)} \frac{1}{T (\lambda_{i,d}^{-1},1, \tau \vp)} = 0,
 \]
@@
 
-\item If $\spadesuit(d) \ge L_{\tau\vp}$ and $\varheartsuit(d) = 0$, then $\{L_{\tau\vp},  L_{\tau\vp} + 1, \ldots \} \subseteq I_{d,\vp} \setminus \{1\}$.
-
-\item If $\spadesuit(d) \ge L_{\tau\vp}$ and $\varheartsuit(d) >0$, then \eqref{eq:Mddef} and \eqref{eq:lambda_K_strong4} imply that
-\[
-\lambda_{i(\varheartsuit(d),\vp),d} \le \lambda_{\spadesuit(d)+1,d} \le \varheartsuit(d) < \lambda_{\spadesuit(d),d}.
-\]
-This means that $\spadesuit(d) \le i(\varheartsuit(d),\vp)-1$.  So, $\{L_{\tau\vp}, \ldots, \spadesuit(d)\} \subseteq I_{d,\vp} \setminus \{1\}$.
+\item If $\theUB(d) \ge L_{\tau\vp}$ and $\theM(d) = 0$, then $\{L_{\tau\vp},  L_{\tau\vp} + 1, \ldots \} \subseteq I_{d,\vp} \setminus \{1\}$.
+
+\item If $\theUB(d) \ge L_{\tau\vp}$ and $\theM(d) >0$, then \eqref{eq:Mddef} and \eqref{eq:lambda_K_strong4} imply that
+\[
+\lambda_{i(\theM(d),\vp),d} \le \lambda_{\theUB(d)+1,d} \le \theM(d) < \lambda_{\theUB(d),d}.
+\]
+This means that $\theUB(d) \le i(\theM(d),\vp)-1$.  So, $\{L_{\tau\vp}, \ldots, \theUB(d)\} \subseteq I_{d,\vp} \setminus \{1\}$.
 
@@
 \begin{align*}
-S_{\tau\vp} & = \sup_{d\in\naturals} \sum_{i = L_{\tau\vp}}^{\spadesuit(d)} \frac{1}{T (\lambda_{i,d}^{-1},1, \tau \vp)}
+S_{\tau\vp} & = \sup_{d\in\naturals} \sum_{i = L_{\tau\vp}}^{\theUB(d)} \frac{1}{T (\lambda_{i,d}^{-1},1, \tau \vp)}
 \le 
@@
      S_{\vp}:=\sup_{d \in \naturals}
-     \sum_{i = \lceil L_{\vp}\, T(0,d,\vp) \rceil}^{\spadesuit(d)} \frac{1}{T(\lambda^{-1}_{i,d},d,\vp)}< \infty.
+     \sum_{i = \lceil L_{\vp}\, T(0,d,\vp) \rceil}^{\theUB(d)} \frac{1}{T(\lambda^{-1}_{i,d},d,\vp)}< \infty.
 \end{equation}
@@
     \textbf{Sufficient Condition:}\\
-Fix $d$.  If $\spadesuit(d) = 0$, then $\comp(\varepsilon,d) = 0 \le C_{\vp}\, T(\varepsilon^{-1},d,\vp)$ automatically for all $\varepsilon \in [\varheartsuit(d), \infty)$.
-
-For the case $\spadesuit(d)> 0$, we utilize upper bound \eqref{eq:compUP_rest}, specializing to the case of $\clubsuit=d$ and $N = \min\left(\lceil L_{\vp}\, T(0,d,\vp)\rceil,\spadesuit(d)\right)$:
+Fix $d$.  If $\theUB(d) = 0$, then $\comp(\varepsilon,d) = 0 \le C_{\vp}\, T(\varepsilon^{-1},d,\vp)$ automatically for all $\varepsilon \in [\theM(d), \infty)$.
+
+For the case $\theUB(d)> 0$, we utilize upper bound \eqref{eq:compUP_rest}, specializing to the case of $\thed=d$ and $N = \min\left(\lceil L_{\vp}\, T(0,d,\vp)\rceil,\theUB(d)\right)$:
 \begin{align*}
        \comp(\varepsilon,d)
-       & \le T(\varepsilon^{-1},d, \vp) \Biggl [ \frac{\min\left(\lceil L_{\vp}\, T(0,d,\vp)\rceil,\spadesuit(d)\right)}{T(\varepsilon^{-1},d, \vp)}  + \underbrace{\sum_{i = \min\left(\lceil L_{\vp}\, T(0,d,\vp)\rceil,\spadesuit(d)\right)}^{\spadesuit(d)} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}}_{\le S_{\vp} + 1/ T(\lambda_{\spadesuit(d), d}^{-1},d,\vp) \text{ by \eqref{eq:strong_rest_tractiff}} }
+       & \le T(\varepsilon^{-1},d, \vp) \Biggl [ \frac{\min\left(\lceil L_{\vp}\, T(0,d,\vp)\rceil,\theUB(d)\right)}{T(\varepsilon^{-1},d, \vp)}  + \underbrace{\sum_{i = \min\left(\lceil L_{\vp}\, T(0,d,\vp)\rceil,\theUB(d)\right)}^{\theUB(d)} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}}_{\le S_{\vp} + 1/ T(\lambda_{\theUB(d), d}^{-1},d,\vp) \text{ by \eqref{eq:strong_rest_tractiff}} }
         \Biggr] \\
-       & \le T(\varepsilon^{-1},d,\vp)\left[\frac{ L_{\vp}\, T(0,d,\vp)+1}{T(0,d, \vp)} + S_{\vp} + \frac{1}{T(\lambda_{\spadesuit(d), d}^{-1},d,\vp)} \right]
+       & \le T(\varepsilon^{-1},d,\vp)\left[\frac{ L_{\vp}\, T(0,d,\vp)+1}{T(0,d, \vp)} + S_{\vp} + \frac{1}{T(\lambda_{\theUB(d), d}^{-1},d,\vp)} \right]
        \qquad \text{by \eqref{eq:Tnondecreasing}}\\
@@
 	\lambda_{\lfloor C_{\vp}\, T(\varepsilon^{-1},d,\vp)\rfloor +1,d}\le \varepsilon \qquad 
- \forall \varepsilon > \varheartsuit(d),\ d \in \naturals.
+ \forall \varepsilon > \theM(d),\ d \in \naturals.
 \end{equation}
@@
 \[
-i(\varepsilon,d,\vp)\le C_{\vp}\, T(\varepsilon^{-1},d,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,d,\vp),d}^{-1},d,\vp)+1, \qquad \forall \varepsilon > \varheartsuit(d),\ d \in \naturals.
-\]
-For $\varepsilon$ taking on all values in $(\varheartsuit(d),\infty)$, $i(\varepsilon,d,\vp)$ takes on (at least) all values in
+i(\varepsilon,d,\vp)\le C_{\vp}\, T(\varepsilon^{-1},d,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,d,\vp),d}^{-1},d,\vp)+1, \qquad \forall \varepsilon > \theM(d),\ d \in \naturals.
+\]
+For $\varepsilon$ taking on all values in $(\theM(d),\infty)$, $i(\varepsilon,d,\vp)$ takes on (at least) all values in
 \[
 I_{d,\vp}:=\begin{cases} 
-\emptyset, & i(\varheartsuit(d),d,\vp) = i(\infty,d,\vp), \\
-\{i(\infty,d,\vp),\ldots, i(\varheartsuit(d),d,\vp)-1\}, & \varheartsuit(d) > 0, \\
-\{i(\infty,d,\vp), i(\infty,d,\vp) + 1, \ldots\}, & \varheartsuit(d) = 0.
+\emptyset, & i(\theM(d),d,\vp) = i(\infty,d,\vp), \\
+\{i(\infty,d,\vp),\ldots, i(\theM(d),d,\vp)-1\}, & \theM(d) > 0, \\
+\{i(\infty,d,\vp), i(\infty,d,\vp) + 1, \ldots\}, & \theM(d) = 0.
 \end{cases}
@@
 
-\item If $\spadesuit(d) <\lceil L_{\vp'} T(0,d,\vp')\rceil$, then 
-\[
-\sum_{i = \lceil L_{\vp'} T(0,d,\vp')\rceil }^{\spadesuit(d)} \frac{1}{T (\lambda_{i,d}^{-1},d, \vp')} = 0,
+\item If $\theUB(d) <\lceil L_{\vp'} T(0,d,\vp')\rceil$, then 
+\[
+\sum_{i = \lceil L_{\vp'} T(0,d,\vp')\rceil }^{\theUB(d)} \frac{1}{T (\lambda_{i,d}^{-1},d, \vp')} = 0,
 \]
@@
 
-\item If $\spadesuit(d) \ge \lceil L_{\vp'} T(0,d,\vp')\rceil$ and $\varheartsuit(d) = 0$, then $\{\lceil L_{\vp'} T(0,d,\vp')\rceil,  \lceil L_{\vp'} T(0,d,\vp')\rceil + 1, \ldots \} \subseteq I_{d,\vp} \setminus \{1\}$.
-
-\item If $\spadesuit(d) \ge \lceil L_{\vp'} T(0,d,\vp')\rceil$ and $\varheartsuit(d) >0$, then \eqref{eq:Mddef} and \eqref{eq:rest_lambda_K4} imply that
-\[
-\lambda_{i(\varheartsuit(d),d,\vp),d} \le \lambda_{\spadesuit(d)+1,d} \le \varheartsuit(d) < \lambda_{\spadesuit(d),d}.
-\]
-This means that $\spadesuit(d) \le i(\varheartsuit(d),d,\vp)-1$.  So, $\{ \lceil L_{\vp'} T(0,d,\vp')\rceil, \ldots, \spadesuit(d)\} \subseteq I_{d,\vp} \setminus \{1\}$.
+\item If $\theUB(d) \ge \lceil L_{\vp'} T(0,d,\vp')\rceil$ and $\theM(d) = 0$, then $\{\lceil L_{\vp'} T(0,d,\vp')\rceil,  \lceil L_{\vp'} T(0,d,\vp')\rceil + 1, \ldots \} \subseteq I_{d,\vp} \setminus \{1\}$.
+
+\item If $\theUB(d) \ge \lceil L_{\vp'} T(0,d,\vp')\rceil$ and $\theM(d) >0$, then \eqref{eq:Mddef} and \eqref{eq:rest_lambda_K4} imply that
+\[
+\lambda_{i(\theM(d),d,\vp),d} \le \lambda_{\theUB(d)+1,d} \le \theM(d) < \lambda_{\theUB(d),d}.
+\]
+This means that $\theUB(d) \le i(\theM(d),d,\vp)-1$.  So, $\{ \lceil L_{\vp'} T(0,d,\vp')\rceil, \ldots, \theUB(d)\} \subseteq I_{d,\vp} \setminus \{1\}$.
 
@@
 \begin{align*}
-S_{\vp'} & = \sup_{d\in\naturals} \sum_{i =  \lceil L_{\vp'} T(0,d,\vp')\rceil}^{\spadesuit(d)} \frac{1}{T (\lambda_{i,d}^{-1},d, \tau \vp)}
+S_{\vp'} & = \sup_{d\in\naturals} \sum_{i =  \lceil L_{\vp'} T(0,d,\vp')\rceil}^{\theUB(d)} \frac{1}{T (\lambda_{i,d}^{-1},d, \tau \vp)}
 \le 

### 2023-07-06 GeneralizedTractability_230607.tex
Updates from Overleaf

@@
 \usepackage{hyperref}
+\usepackage{mathrsfs}
 \usepackage{cleveref}
@@
 %certain important notations for key symbols
-\newcommand{\thed}{\clubsuit}
-\newcommand{\theM}{\varheartsuit}
-\newcommand{theUB}{\spadesuit}
+%\newcommand{\thed}{\clubsuit}
+%\newcommand{\theM}{\varheartsuit}
+%\newcommand{\theUB}{\spadesuit}
+\newcommand{\thed}{\delta}
+\newcommand{\theM}{\mathscr{E}}
+\newcommand{\theUB}{\mathscr{U}}
 
@@
 
-\title{\fred{A Unified Treatment of Tractabilty of Approximation Problems}}
+\title{\fred{A Unified Treatment of Tractability of Approximation Problems}}
 
@@
 \ead{peter.kritzer@oeaw.ac.at}
-\author[1]{Onyekachi Osisiogu}
+\author[1]{Onyekachi Osisiogu}\ead{oosisiogu@iit.edu}
 \date{\today}
@@
 
-TODO: We need to check the relation of our work to that of Michael Gnewuch and Henryk.
-We do not need tensor product structure: do they need that assumption?
-The summation conditions on the eigenvalues might be a significant difference between our results and theirs.
-
 \medskip
@@
 TODO: We should check for consistency of the use of the $\forall$ symbol in displayed formulas. Sometimes we use it, sometimes we do not, sometimes it is preceded by a comma, sometimes not, etc.
+
+TODO: We should check consistency of notation when using $\max$ or $\min$. Sometimes we use ``$(\ldots)$'' for the argument, sometimes we use ``$\{\ldots\}$''
+
+\bigskip
 
@@
 \end{equation}
+\peter{
+Strictly speaking, we are considering the \textit{absolute} error criterion in this paper. 
+Alternatively, one could also consider the \textit{normalized} error criterion, where the error in \eqref{eq:errcrit} is divided by the so-called \textit{initial error}, which is the error without sampling the function, or, equivalently, the operator norm of $\SOL_d$.
+In the latter case, it is known (see, e.g., \cite{NovWoz08a}) that the information complexity is given by
+\[
+\comp^{\rm norm}(\varepsilon, d) = \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon\, \lambda_{1, d}\}.
+\]
+This means that, essentially, in the tractability analysis below, all criteria would be normalized by the first eigenvalue $\lambda_{1,d}$.
+
+For the sake of brevity and clarity of notation, we restrict ourselves to the absolute error criterion here, but presumably, analogous results hold for the normalized setting. 
+}
 
@@
 We want to bound the complexity in terms of a simple function, $T$, of $\varepsilon^{-1}$ and $d$ and identify simple conditions on the singular values that are equivalent to this bound holding.
-\peter{[PETER: Maybe this would be a good place to refer to the earlier work of Michael and Henryk?
-I will take care of it...
-.]}
+\peter{We would like to point out that generalized tractability specified by function $T$ has been considered before in the literature.
+In particular, there are several papers by Gnewuch and Wo\'{z}niakowski (see \cite{GW06,GW08,GW09,GneWoz11a} ), and also \cite[Chapter 8]{NovWoz08a} is devoted to this topic.
+To our best knowledge, however, these references mainly focus on the special case tensor product problems, which we do not do here, and the conditions for tractability derived there are mostly in terms of properties of the function $T$, and not in terms of sums of (functions of) the eigenvalues of a problem.
+Hence, we consider the present paper an addition to what is presently known on this subject.}
 
@@
 \end{equation}
-The conditions we require $T$ to satisfy are described in  Section \ref{sec:not}, however, the basic idea is that we define our approximation problem to be tractable if 
-$\comp(\varepsilon, d) \le  C_{\vp}\, T(\varepsilon^{-1},d,\vp)$ for some constant, $C_{\vp}$, depending only on the parameter $\vp$.
-In practice, we expect $T(\varepsilon^{-1},d,\vp)$ to increase sub-exponentially  with increasing $\varepsilon^{-1}$ and/or $d$, however most of our theorems do not require such an assumption.
+The conditions we require $T$ to satisfy are described in  Section \ref{sec:not}, however, the basic idea is that we define our approximation problem to be tractable if $\comp(\varepsilon, d) \le  C_{\vp}\, T(\varepsilon^{-1},d,\vp)$ for some constant, $C_{\vp}$, depending only on the parameter $\vp$.
+In practice, we expect $T(\varepsilon^{-1},d,\vp)$ to increase sub-exponentially  with increasing $\varepsilon^{-1}$ and/or $d$, however, most of our theorems do not require such an assumption.
 
 \Cref{thm_main_strong_tract2,thm_main_tract2,thm_main_rest_strong_tract,thm_main_rest_tract} all take the form
-
-\peter{[PETER: Not meaning to sound too negative, but I am not sure I like the notation with the symbols below. Is it possible to use something different instead?]}
-\fred{Fred: I have now given them names above in lines 18-20, so we can experiment with different symbols or letters.}
 \begin{multline}
-  \exists C_{\vp} \text{ with }
+  \exists \,C_{\vp} > 0 \text{ with }
     \comp(\varepsilon, d) \le  C_{\vp}\, T(\varepsilon^{-1},\thed,\vp) \quad \forall (\varepsilon^{-1},d) \in \Omega \\
@@
 an ordering of the parameters $\vp$.}\\
-%\kachi{Throughout the article, we use the following notation.}\\
+\\
 
@@
 Let $T$ be a function given in \eqref{eq:Tspec}.
-A tractability function $T$ is a function of simple form that provides an upper bound on the \peter{information} complexity of a problem.
+A tractability function $T$ is a function of a simple form that provides an upper bound on the \peter{information} complexity of a problem.
 Some examples of tractability functions commonly considered are provided in Table \ref{tab:commonT}.
-
+\kachi{}
 \begin{table} 
@@
 %In this section, we illustrate Theorems \ref{thm_main_strong_tract2} and \ref{thm_main_tract2} for the types of tractability given in the table in Section \ref{sec:not}.
-In this section, we present six examples relating to Theorem \ref{thm_main_strong_tract2} and Theorem \ref{thm_main_tract2}, both of which were introduced in Section \ref{sec:spt}, for the various types of tractability that are listed in Table \ref{tab:commonT}.
+In this section, we present six examples relating to Theorem \ref{thm_main_strong_tract2} and Theorem \ref{thm_main_tract2}, both of which were introduced in Section \ref{sec:spt}, for the various notions of tractability that are listed in Table \ref{tab:commonT}.
 In subsequent sections, we will continue to present various examples.
@@
 \[
- T(\varepsilon^{-1},d,\vp)= \left[\max\{1,\log(1+\varepsilon^{-1})\}\right]^{\peter{\vp}}, \quad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty),
-\]
-%\kachi{Alternatively:
-%\[
-%T(\varepsilon^{-1},d,\vp) = (1+\log\max\{1,\varepsilon^{-1}\})^p
-%\]}
+ T(\varepsilon^{-1},d,\vp)= [\max\{1,\log(1+\varepsilon^{-1})\}]^{\peter{\vp}}, \quad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty),
+\]
+
 where \peter{$\vp=p$} is a scalar. Then Theorem \ref{thm_main_strong_tract2} yields the equivalent condition for \peter{exponential strong polynomial tractability:} 
-\[
- \sup_{d\in\naturals} \sum_{i=L_{p} }^\infty (\min\{1,\log(1+\lambda_{i,d}\})^{p}  < \infty,\quad  \text{ for some } p \ge 0, L_{p} \in \naturals.
-\] In this case the optimal $p$ is the infimum of all $p$ for which the above condition holds.
+\begin{equation}\label{eq:exp_spt}
+ \sup_{d\in\naturals} \sum_{i=L_{p} }^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^{p}}  < \infty,\quad  \text{ for some } p \ge 0, L_{p} \in \naturals.
+\end{equation}
+In this case the optimal $p$ is the infimum of all $p$ for which the above condition holds.
 \end{example}
@@
 \[
- T(\varepsilon^{-1},d,\vp)=\left[\max\{1,\log(1+\varepsilon^{-1}\})\right]^p\, d^q, \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty)^2, 
-\] where $\vp = (p,q)$. Then Theorem \ref{thm_main_tract2} yields  the equivalent condition for exponential polynomial tractability
-\[
- \sup_{d\in\naturals}\, d^{-q} \sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty [\min\{1,\log(1+\lambda_{i,d}\})]^p < \infty  \text{ for some } p,q \ge 0, L_{(p,q)} \in \naturals.
-\]
+ T(\varepsilon^{-1},d,\vp)=\left[\max\{1,\log(1+\varepsilon^{-1})\}\right]^p\, d^q, \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty)^2, 
+\] where $\vp = (p,q)$. Then Theorem \ref{thm_main_tract2} yields  the equivalent condition for exponential polynomial tractability:
+\begin{equation}\label{eq:exp_pt}
+ \sup_{d\in\naturals}\, d^{-q} \sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p} < \infty  \text{ for some } p,q \ge 0, L_{(p,q)} \in \naturals.
+\end{equation}
 \end{example}
 
-\peter{[PETER: Are we sure that the conditions in Examples 3 and 4 are correct?
-And, moreover, these conditions should recover the corresponding conditions in \cite{KriWoz19a}.
-The conditions look different at first sight, but probably it can be shown that they are equivalent...
-.}
-
-In the following example, we provide a brief summary of these notions of tractability. We would like to emphasize that this example was previously known (see \cite{}). 
+\peter{
+In the paper \cite{KriWoz19a}, the authors derived conditions equivalent to exponential strong polynomial tractability and exponential polynomial tractability, respectively.
+These conditions read (with notation adapted to our present paper) as follows:
+\begin{itemize}
+    \item We have exponential strong polynomial tractability iff there exists a $\tau>0$ and a 
+    a $C\in\naturals$ such that
+    \begin{equation}\label{eq:KW_exp_spt}
+        \sup_{d\in\naturals} \sum_{i=C}^{\infty} \lambda_{i,d}^{i^{-\tau}} < \infty. 
+    \end{equation}
+    \item We have exponential polynomial tractability iff there exist $\tau_1,\tau_3\ge 0$ and $\tau_2, C>0$ such that
+    \begin{equation}\label{eq:KW_exp_pt}
+        \sup_{d\in\naturals} d^{-\tau_1} \sum_{i=\lceil C d^{\tau_3} \rceil}^{\infty} \lambda_{i,d}^{i^{-\tau}} < \infty. 
+    \end{equation}
+\end{itemize}
+It should be noted that, e.g., the condition \eqref{eq:exp_spt} is easier to check in practice than the condition \eqref{eq:KW_exp_spt}.
+Indeed, since in \eqref{eq:KW_exp_spt} the summation indices $i$ show up in the exponents of the summands, we need the exact ordering of the eigenvalues $\lambda_{i,d}$, whereas in \eqref{eq:exp_spt} we only have a summation of the values of $1/T(\lambda_{i,d}^{-1},t,\vp)$, and the exact order of the eigenvalues can be neglected.
+
+Secondly, we would like to show that the conditions \eqref{exp_spt} and \eqref{eq:KW_exp_spt}, as well as the conditions \eqref{exp_pt} and \eqref{eq:KW_exp_pt} are indeed equivalent.
+We do this for the latter two conditions, i.e., for the conditions on exponential polynomial tractability.
+The case of exponential strong polynomial tractability is simpler and can be treated analogously.
+We thus show equivalence of \eqref{eq:exp_pt} and \eqref{eq:KW_exp_pt} in the following.
+
+Let us first assume that \eqref{eq:KW_exp_pt} holds, i.e.,
+\[
+M:=\sup_{d\in\naturals} d^{-\tau_1} \sum_{i=\lceil C d^{\tau_3} \rceil}^{\infty} \lambda_{i,d}^{i^{-\tau}} < \infty. 
+\]
+Define
+\[
+B_d:=\left\{i\in\naturals \colon i\ge \left\lceil Cd^{\tau_3}\right\rceil\quad\mbox{and}\quad 
+\lambda_{i,d}^{i^{-\tau_2}}>\frac{1}{e}\right\}
+\]
+Due to our assumption, we see that $\abs{B_d} < M\,e\,d^{\tau_1}$ and $\abs{B_d}\le \lfloor M\,e\,d^{\tau_1} \rfloor$.
+Suppose now that $i\ge \lceil C d^{\tau_3}\rceil$ but $i\not\in B_d$, which means that
+\[\lambda_{i,d}^{i^{-\tau_2}} \le \frac{1}{e} \Leftrightarrow \log (\lambda_{i,d}^{-1})\ge i^{\tau_2}.\]
+Now, choose $p> 1/\tau_2$, $q=\max\{\tau_1,\tau_3\}$, and $L_{(p,q)}=\max\{C, M\, e\}$, which implies that $\lceil L_{(p,q)} d^{q}\rceil \ge M\, e\, d^{\tau_1}$. Then, for any $d\in\naturals$, 
+\begin{eqnarray*}
+d^{-q} \sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p}&=&d^{-q} \sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\in B_d}}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p}\\
+&& + d^{-q} \sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\not\in B_d}}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p}\\
+&\le& d^{-q} M\, e\, d^{\tau_1} + d^{-q}\sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\not\in B_d}}^\infty \frac{1}{[\log (\lambda_{i,d}^{-1})]^p}\\
+&\le& 1 + d^{-q}\sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\not\in B_d}}^\infty \frac{1}{i^{\tau_2 p}}\\
+&\le & 1 + \zeta (\tau_2 p).
+\end{eqnarray*}
+Since $p$ was chosen to be strictly larger than $1/\tau_2$, it follows that the latter expression is finite and its value is independent of $d$. Therefore, Condition \eqref{eq:exp_pt} holds.
+
+Conversely, let us now assume that Condition \eqref{eq:exp_pt} holds.
+We will show next that this implies Condition \eqref{eq:KW_exp_pt}.
+Indeed, due to \eqref{eq:exp_pt}, there exists a positive constant $M$ (w.l.o.g., we can assume that $M\ge 1$) such that for all $d\in\naturals$,
+\[
+d^{-q} 
+\sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p} \le M,
+\]
+which is equivalent to 
+\[
+\sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p} \le d^q M. 
+\]
+Similarly to the proof of Theorem \ref{thm_main_strong_tract2}, we see that for any $n > \lceil L_{(p,q)} d^{q}\rceil $, 
+\[
+\frac{1}{T(\lambda_{n+1,d}^{-1},1,\vp)} \le \frac{1}{n-\lceil L_{(p,q)} d^{q}\rceil +1 }
+\sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty  \frac{1}{T(\lambda_{i,d}^{-1},1,\vp)}
+\le \frac{d^q M}{n-\lceil L_{(p,q)} d^{q}\rceil +1 }
+\]
+This implies that
+\[
+\frac{n}{d^q M}-\frac{L_{(p,q)}}{M}\le\frac{n-\lceil L_{(p,q)} d^{q}\rceil +1 }{d^q M} \le [\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p 
+\le [1 + \log(1+\lambda_{i,d}^{-1})]^p.
+\]
+Since both $L_{(p,q)}$ and $M$ in the latter chain of inequalities are independent of $d$ and $n$, there 
+exists a positive constant $K$ such that 
+\[
+\frac{n}{d^q K} \le [1 + \log(1+\lambda_{n,d}^{-1})]^p,
+\]
+which implies 
+\[
+\frac{n^{1/p}}{d^{q/p} K^{1/p}} -1 \le \log(1+\lambda_{n,d}^{-1}).
+\]
+This, in turn, implies the existence of another constant $\widetilde{K}>0$ such that 
+\[
+\lambda_{n,d} \le \exp\left(-\frac{n^{1/p}}{\widetilde{K}^{1/p} d^{q/p}}\right)
+\quad \forall n > \lceil L_{(p,q)} d^{q}\rceil,
+\]
+which is essentially the situation described in \cite[p.~118]{KriWoz19a}. We can then choose $\tau_2\in (0,1/p)$, 
+and proceed as in \cite{KriWoz19a} to obtain 
+\[
+\sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty \lambda_{i,d}^{i^{-\tau_2}}=\mathcal{O}(d^{q/(1-\tau_2 p)}),
+\]
+with the implied factor in the $\mathcal{O}$-notation independent of $d$. Then, we can choose $\tau_1=q/(1-\tau_2 p)$ and $\tau_3=q$ and see that \eqref{eq:KW_exp_pt} holds.
+
+This concludes the proof of the equivalence of \eqref{eq:exp_pt} and \eqref{eq:KW_exp_pt}.
+
+\bigskip
+
+[PLEASE CHECK CAREFULLY.]}
+
+\kachi{In the following example, we provide a brief summary of these notions of tractability.
+We would like to emphasize that this example was previously known (see \cite{?}) where in this case, the roles of $\varepsilon^{-1}$ and $d$ are separated.
+In order to accomplish this, we will first define two functions $\phi$ and $\psi$ with positive values that are increasing in both of their arguments.
+This will allow us to take into account a variety of possible exponents of $\varepsilon^{-1}$ and $d$.
+%To do this, we introduce two positive-value functions that are increasing in both arguments so as to take possibly different exponents of $\varepsilon^{-1}$ and $d$.
+The equivalent conditions for this example are assumed to take the same form as those in Theorems \ref{thm_main_strong_tract2} and \ref{thm_main_tract2}.}
+
+\peter{[PETER: Kachi, can you work a bit more on this introductory text, please? Right now, it does not contain much information.]}
+\kachi{[KACHI: Done. Although I am having trouble adding references, do you have any suggestions.]}
+
 \begin{example}[(Strong) Separable tractability]
@@
  T(\varepsilon^{-1},d,\vp)= \phi(\varepsilon^{-1},p)\, \psi(d,q)
- \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty)^2.
+ \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty)^2,
 \]
@@
 
-We say that a problem is defined as $T$-separable tractable with parameter $\vp$ iff there exists a positive constant $C_{\vp}$ which does not depend on $\varepsilon$ and $d$ such that
+We say that a problem is defined as $T$-separable tractable \peter{[PETER: I am wondering if ``$T$-separably tractable'' is better?
+But obviously, you know that better than me.]} with parameter $\vp$ iff there exists a positive constant $C_{\vp}$ which does not depend on $\varepsilon$ and $d$ such that
 \[
@@
 \] where in this case $\vp = p$ is a scalar. 
-Furthermore, we assume the following as in \eqref{eq:Tlim}, \eqref{eq:T0}, and \eqref{eq:ptauassume}. We assume that
-
-\[
-\lim_{\varepsilon\rightarrow0}\phi(\varepsilon^{-1},p) = \infty \qquad \forall d\in\naturals, p >0.
-\] since there are an infinite number of positive eigenvalues. Furthermore, we have that $\phi(\cdot,p)$ is non-decreasing hence we define the following limit
-\[ \lim_{\varepsilon \rightarrow \infty}\phi(\varepsilon^{-1},p)\geq 1.
-\] 
-Additionally, we have the following technical assumptions.
-Suppose that, for any real $\tau_1, \tau_2>0$ and any $p,q>0$, we have that there exists $\hat{K}_{p,\tau_1}$ and $\hat{K}_{q\tau_2}$ such that
+Furthermore, we assume the following, \peter{which corresponds to the conditions} in \eqref{eq:Tlim}, \eqref{eq:T0}, and \eqref{eq:ptauassume}. We assume that
+\[
+\lim_{\varepsilon\rightarrow0}\phi(\varepsilon^{-1},p) = \infty \qquad \forall d\in\naturals, p >0,
+\] 
+since there are an infinite number of positive eigenvalues. Furthermore, we have that $\phi(\cdot,p)$ is non-decreasing hence we define the following limit
+\[ 
+\lim_{\varepsilon \rightarrow \infty}\phi(\varepsilon^{-1},p) \peter{>0.}
+\] 
+Additionally, we have the following technical assumptions. Suppose that, for any real $\tau_1, \tau_2>0$ and any $p,q>0$, we have that 
 \begin{align*}
-     [\phi(\varepsilon^{-1},p)]^{\tau_1} &\le \hat{K}_{p,\tau_1} \phi (\varepsilon^{-1},\tau_1 p)\\
-      [\psi(d,q)]^{\tau_2} &\le \hat{K}_{q,\tau_2} \psi (d,\tau_2 q) \qquad \forall \, \varepsilon \in (0,\infty),\, d\in \naturals.
+     [\phi(\varepsilon^{-1},p)]^{\tau_1} \le \hat{K}_{p,\tau_1} \phi (\varepsilon^{-1},\tau_1 p)
+     \quad \mbox{and} \quad
+      [\psi(d,q)]^{\tau_2} \le \hat{K}_{q,\tau_2} \psi (d,\tau_2 q) \qquad \forall \, \varepsilon \in (0,\infty),\, d\in \naturals,
 \end{align*} where $\hat{K}_{p,\tau_1}>0$ is a constant that may depend on $p$ and $\tau_1$, but is independent of $\varepsilon$, and where $\hat{K}_{q,\tau_2}>0$ is a constant that may depend on $q$ and $\tau_2$, but is independent of $d$.
 
-Thus, Theorem \ref{thm_main_strong_tract2} yields the following equivalent condition for strongly $T$-separable tractability
+Theorem \ref{thm_main_strong_tract2} yields the following equivalent condition for strong $T$-separable tractability:
 \begin{equation*} \label{eq:strong_tractiff}
@@
 \end{example}
-Next, we will introduce another summarized notion of tractability. 
+\kachi{Next, we will introduce another summarized notion of tractability.
+In the following, we will define two functions $\hat{\phi}$ and $\hat{\psi}$ that take the roles of $\varepsilon^{-1}$ and $d$.
+As will be seen below, this tractability function is equivalent to the so-called \emph{quasi-polynomial tractability}.}
+\peter{[PETER: Also here, Kachi, please work on the introductory text.]}
 \begin{example}[Non-separable tractability]
@@
 \[
- T(\varepsilon^{-1},d,p)= \exp\{p \, \phi(\varepsilon^{-1})\, \psi(d)\} = [\exp\{ \phi(\varepsilon^{-1})\}]^{p \, \psi(d)}
- \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, p\in [0,\infty).
-\]  with non-decreasing functions $\phi : (0,\infty) \to (0,\infty)$ and $\psi : \naturals \to (0,\infty)$. 
-We say that a problem is non-separable tractable with parameter $p$ iff there exists a positive $C_{p}$ such that
-
-\[\comp(\varepsilon,d) \leq  C_{p}\exp\{p(\phi(\varepsilon^{-1})\psi(d))\}.\]
-
-Hence we can apply Theorem \ref{thm_main_tract2} as follows. We have the following equivalent condition for non-separable tractability
-\[
-%\sup_{d\in\mathbb{N}}\frac{1}{\psi(d)}\sum_{i=Lp\,\psi(d)} \phi(\lambda_{i,d})\quad \text{for some } p \geq 0, L_p \in \naturals.
-\sup_{d\in\mathbb{N}}\sum_{i=L_p\,\phi(0)^{p \, \psi(d)}} [\exp\{ \phi(\lambda_{i,d}^{-1})\}]^{p \, \psi(d)}\quad \text{for some } p \geq 0, L_p \in \naturals.
-\]
+ T(\varepsilon^{-1},d,p)= \exp (p \, \hat{\phi}(\varepsilon^{-1})\, \hat{\psi}(d)) = [\exp( \hat{\phi}(\varepsilon^{-1}))]^{p \, \hat{\psi}(d)}
+ \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, p\in [0,\infty),
+\]  with non-decreasing functions $\hat{\phi} : (0,\infty) \to (0,\infty)$ and $\hat{\psi} : \naturals \to (0,\infty)$. 
+We say that a problem is non-separable tractable with \peter{scalar} parameter $p$ iff there exists a positive $C_{p}$ such that
+
+\[\comp(\varepsilon,d) 
+\leq  C_{p}\exp (p(\hat{\phi}(\varepsilon^{-1})\hat{\psi}(d))).\]
+
+Hence we can apply Theorem \ref{thm_main_tract2} as follows. We have the following equivalent condition for non-separable tractability:
+\[
+\sup_{d\in\mathbb{N}}\sum_{i=L_p\,\hat{\phi}(0)^{p \, \hat{\psi}(d)}} [\exp ( \hat{\phi}(\lambda_{i,d}^{-1}))]^{-p \, \hat{\psi}(d)}\quad \text{for some } p \geq 0, L_p \in \naturals.
+\]
+
 \end{example}
-For $\phi$ and $\psi$ of special form, the condition above can be simplified further as in the following two examples of non-separable tractability. 
-\begin{example}[Algebraic quasi-polynomial tractability]
-
-As defined in \cite{GneWoz11a}, we say that a problem is \emph{quasi-polynomially tractable (QPT)} if there exist two constants $C$, $p > 0$, such that
+For $\hat{\phi}$ and $\hat{\psi}$ of special form, the condition above can be simplified further as in the following two examples of non-separable tractability. 
+\kachi{We first define the notion of quasi-polynomial tractability as in \cite{GneWoz11a}.
+\begin{definition}
+     A problem is \emph{quasi-polynomially tractable (QPT)} if there exist two constants $C$, $p > 0$, such that
 \begin{equation}\label{expqpt}
@@
 for all $\varepsilon \in (0,1]$ and $d\in\mathbb{N}$.
+\end{definition}}
+
+\begin{example}[Algebraic quasi-polynomial tractability]
+
+%we say that a problem is \emph{quasi-polynomially tractable (QPT)} if there exist two constants $C$, $p > 0$, such that
+%\begin{equation}\label{expqpt}
+ %   \comp(\varepsilon,d) \leq C\exp\{p(1+\log(\varepsilon^{-1}))(1+\log(d))\}
+%\end{equation}
+%for all $\varepsilon \in (0,1]$ and $d\in\mathbb{N}$.
 
@@
 \[
- T(\varepsilon^{-1},d,p)= \exp\{p(1+\log(\max\{1,\varepsilon^{-1}\}))(1+\log (d))\}  \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, p \in [0,\infty).
-\] This can be rewritten as 
-\[
-T(\varepsilon^{-1},d,p) = e^p[\max\{1,\varepsilon^{-1}\}]^{p(1+\log d)}d^p
-\]
-Observe that the function $T$ is a function of $\max\{1,\varepsilon^{-1}\}$ and $d$ which are, polynomial or not exponential in powers of $\max\{1,\varepsilon^{-1}\}$ and $d$.
-Hence we can apply Theorem \ref{thm_main_tract2} as follows.
-We have the following equivalent condition for quasi-polynomial tractability in the algebraic case
-\[
-\sup_{d\in\mathbb{N}}\,d^{-p}\sum_{i=Lp\,d^{p}} \left(\min\{1,\lambda_{i,d}\} \right)^{p(1+\ln d)} < \infty \qquad \text{for some } p \geq 0, L_p \in \naturals.\]
+ T(\varepsilon^{-1},d,p)= \exp[ p(1+\log(\max\{1,\varepsilon^{-1}\}))(1+\log (d))]  \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, p \in [0,\infty).
+\]
+This can be rewritten as 
+\[
+T(\varepsilon^{-1},d,p) = e^p[\max\{1,\varepsilon^{-1}\}]^{p(1+\log d)}d^p.
+\]
+%Observe that the function $T$ is a function of $\max\{1,\varepsilon^{-1}\}$ and $d$ which are, polynomial or not exponential in powers of $\max\{1,\varepsilon^{-1}\}$ and $d$ \peter{[This sentence sounds a bit confusing to me---what exactly is meant by it?]}.
+Then Theorem \ref{thm_main_tract2} yields the following equivalent condition for quasi-polynomial tractability in the algebraic case:
+\[
+\sup_{d\in\mathbb{N}}\,d^{-p}\sum_{i=L_p\,d^{p}} \left(\min\{1,\lambda_{i,d}\} \right)^{p(1+\log d)} < \infty \qquad \text{for some } p \geq 0, L_p \in \naturals.\]
 \end{example}
@@
 \[
- T(\varepsilon^{-1},d,\vp)= \exp\{p(1+\log(\max\{1,\log(1+\varepsilon^{-1})\}))(1+\log (d))\}  \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty),
+ T(\varepsilon^{-1},d,\vp)= \exp [p(1+\log(\max\{1,\log(1+\varepsilon^{-1})\}))(1+\log (d))]  \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty),
 \] where in this case $\vp = p$. This can be rewritten as 
@@
 \]
-Observe that the function $T$ is a function of $\max\{1,\log(1+\varepsilon^{-1})\}$ and $d$.
-Hence we can apply Theorem \ref{thm_main_tract2} as follows.
-We have the following equivalent condition for quasi-polynomial tractability in the exponential case
-\[
-\sup_{d\in\mathbb{N}}\,d^{-p}\sum_{i=Lp\,d^{p}} \left(\min\{1,\log(1+\lambda_{i,d})\} \right)^{p(1+\ln d)}e^{-p} < \infty \quad \text{for some } p \geq 0, L_p \in \naturals.
+%Observe that the function $T$ is a function of $\max\{1,\log(1+\varepsilon^{-1})\}$ and $d$.
+Hence we can apply Theorem \ref{thm_main_tract2} as follows. We have the following equivalent condition for quasi-polynomial tractability in the exponential case:
+\[
+\sup_{d\in\mathbb{N}}\,d^{-p}\sum_{i=L_p\,d^{p}} \left(\min\{1,\log(1+\lambda_{i,d})\} \right)^{p(1+\log d)}e^{-p} < \infty \quad \text{for some } p \geq 0, L_p \in \naturals.
 \]
@@
 \section{Sub-$h$ Tractability}\label{sec:subh}
-In this section we generalize the concept of weak tractability \cite{}.  Let  $h:[0,\infty) \to [1,\infty)$ satisfy
+In this section we generalize the concept of weak tractability \peter{(see again\cite{NovWoz08a}--\cite{NovWoz12a})}.  Let  $h:[0,\infty) \to [1,\infty)$ satisfy
 \begin{equation} \label{eq:h_cond}
@@
 The idea of this proof follows \cite{WerWoz17a}.
-We suppress the $\vp$ dependence in the proof, because it insignificant.
-
-\bigskip
-
-\noindent \textbf{Sufficient Condition:}\\
+We suppress the $\vp$ dependence in the proof, because it is insignificant.
+
+\bigskip
+
+\noindent \textbf{Sufficient condition:}\\
 Suppose that $S_c <\infty$ for all $c>0$.  Since the terms of the series in the definition of $S_c$ are non-increasing, we have
 	\[
-		\frac{n}{h(cT(\lambda_{n,d}^{-1},d))}\le S_c \qquad \forall n,d \in \naturals.
+		\frac{n}{h(cT(\lambda_{n,d}^{-1},d))}\le S_c \qquad \forall n,d \in \naturals,
 	\]
@@
 	\[
-	T(\lambda_{n,d}^{-s},d) \ge T(\varepsilon^{-1},d) \qquad \forall \varepsilon > 0, \, d \in \naturals.
+	T(\lambda_{n,d}^{-1},d) \ge T(\varepsilon^{-1},d) \qquad \forall \varepsilon > 0, \, d \in \naturals.
 	\]
@@
 
-Since $S_c \ge 1/h(cT(0,1))$ by definition, it follows that $S_c \, h(cT(0,1)) \, h(cT(\varepsilon^{-1},d))  \ge 1$ and so
+Since $S_c \ge 1/h(cT(0,1))$ by definition \peter{[PETER: why do we know this?
+Could it be that we need to replace $T(0,1)$ by $T(\lambda_{1,1}^{-1},1)$?]}, it follows that $S_c \, h(cT(0,1)) \, h(cT(\varepsilon^{-1},d))  \ge 1$ and so
 \begin{align*}
@@
 The finiteness of $S_c$ implies that $\lim_{\varepsilon \to 0} T(\varepsilon^{-1},d) = \infty$ for all $d \in \naturals$.
-Together with  the hypothesis on $\lim_{d \to \infty} T(\varepsilon^{-1},d)$ in \eqref{eq:h_cond}, it follows that $\lim_{\varepsilon^{-1} + d \to \infty} T(\varepsilon^{-1},d) = \infty$.
-Therefore
+Together with  the hypothesis on $\lim_{d \to \infty} T(\varepsilon^{-1},d)$ in \eqref{eq:h_cond}
+\peter{[PETER: Is the reference to \eqref{eq:h_cond} correct?]}, it follows that $\lim_{\varepsilon^{-1} + d \to \infty} T(\varepsilon^{-1},d) = \infty$.  Therefore
 \begin{equation*}
@@
 
-\noindent \textbf{Necessary Condition:}\\
-Suppose that the problem is  sub-$h \circ T$ tractable. Then by \eqref{eq:comp_slow_hcT}, for any $c>0$ there exists a positive integer $V_c$ such that
+\noindent \textbf{Necessary condition:}\\
+Suppose that the problem is  sub-$h$-$T$ tractable. Then by \eqref{eq:comp_slow_hcT}, for any $c>0$ there exists a positive integer $V_c$ such that
 \begin{equation*}
@@
 \end{equation}
-By varying $\varepsilon^{-1}$ in the interval $[\varepsilon^{-1}_{\max}(d,c),\infty)$,  the integer $n(\varepsilon,d,c)$ attains all values greater than or equal to $n^*(d,c)$.
+\peter{[PETER: We do not have $\lambda_{\max}$ anymore... . Do we need it?]}
+By varying $\varepsilon^{-1}$ in the interval $[\varepsilon^{-1}_{\max}(d,c),\infty)$,  the integer $n(\varepsilon,d,c)$ attains, \peter{by Assumption \eqref{eq:Tlim},} all values greater than or equal to $n^*(d,c)$.
 Thus, by \eqref{eq:nedcbound},
@@
 \varepsilon^{-1}_{\max}(d,c) = \max(V_c - d,\lambda_{\max}^{-1})
-= \begin{cases} V_c - d \le V_c, & d \in \{1, \ldots, d^*_c : = \lfloor V_c - \lambda_{\max}^{-1} \rfloor\} \\
-\lambda_{\max}^{-1}, & d \in \{d^*_c+1, \ldots\}
+= \begin{cases} V_c - d \le V_c, & d \in \{1, \ldots, d^*_c : = \lfloor V_c - \lambda_{\max}^{-1} \rfloor\}, \\
+\lambda_{\max}^{-1}, & d \in \{d^*_c+1, \ldots\}.
 \end{cases}
@@
 	\]
-	The expression on the left is the notion of $(s,t)$-weak tractability \cite{??}, and the condition on the right was derived in \cite{??}.
+	The expression on the left is the notion of $(s,t)$-weak tractability \peter{introduced in \cite{SW15}}, and the condition on the right was derived in \peter{\cite[Theorem 3.1]{WW17}}.
 Weak tractability corresponds to $(s,t)=(1,1)$, and uniform weak tractability corresponds to the case when a problem is weakly tractable for all positive $s$ and $t$.
@@
 A problem is 
-$T$-tractable with parameter $\vp$ \emph{on the restricted domain $\Omega$} iff the complexity is independent of the dimension of the problem, that is, there exists a positive constant $C_{\vp}$, again independent of $\varepsilon$ and $d$, such that
+$T$-tractable with parameter $\vp$ \emph{on the restricted domain $\Omega$} iff there exists a positive constant $C_{\vp}$, again independent of $\varepsilon$ and $d$, such that
 \begin{equation} \label{eq:rest_tract_def}
@@
 \end{equation}
-Also, for each $d \in \naturals$ define the interval 
+Also, for each $d \in \naturals$ define the \peter{set}
 \begin{equation} \label{eq:hIdef}
@@
 
-We note that it may be possible to define $\Omega$ such that $\lambda_{1,d} > \theM(d)$ for all $d \in \naturals$.
+We note that it may be possible to define $\Omega$ such that $\lambda_{1,d} > \theM(d)$ 
+\peter{[should it not be $\lambda_{1,d} \le \theM(d)$ ?]}
+for all $d \in \naturals$.
 In this case, $\theUB(d) = 0$ for all $d \in \naturals$, the equivalent conditions for (strong) tractability are trivially satisfied, and the zero algorithm satisfies the error tolerance.
@@
 \]
-Thus, it follows by \eqref{eq:lambda_K_strong3} that $\lambda_{i(\varepsilon,\vp),d} \le \varepsilon$
+Thus, it follows by \peter{\eqref{eq:lambda_K_strong4}} that $\lambda_{i(\varepsilon,\vp),d} \le \varepsilon$
 for any  $(\varepsilon^{-1}, d) \in \Omega$.
@@
  \ge
-  \left[\frac{(i-1)}{C_{\vp}}\right]^\tau \qquad i\in I_{d,\vp},  \ d \in \naturals, \\
+  \left[\frac{(i-1)}{C_{\vp}}\right]^\tau \qquad \forall i\in I_{d,\vp},  \ d \in \naturals, \\
   \label{eq:rest_strong_ineq}
@@
 To do this we need to show that \eqref{eq:rest_strong_ineq} holds for that range.
-Choose Choose $L_{\tau\vp} = i(\infty,\vp) +1 \ge 2$.
+Choose $L_{\tau\vp} = i(\infty,\vp) +1 \ge 2$.
 There are three cases.
@@
 \]
+\peter{
+[PETER. In the above chain of inequalities, I am not quite sure that I understand the first one. Is it because...
+\begin{itemize}
+    \item $\lambda_{i(\varepsilon,\vp),d)} \le \varepsilon$ for all $\varepsilon>\theM(d)$, and so it must also hold in the limit for $\varepsilon$ tending to $\theM(d)$, and
+    \item $\theUB (d) +1$ is the smallest index such that $\lambda_{\theUB (d) +1} \le \theM(d)$ ?
+\end{itemize}]
+
+}
 This means that $\theUB(d) \le i(\theM(d),\vp)-1$.  So, $\{L_{\tau\vp}, \ldots, \theUB(d)\} \subseteq I_{d,\vp} \setminus \{1\}$.
@@
 \begin{proof}
-    \textbf{Sufficient Condition:}\\
+    \textbf{Sufficient condition:}\\
 Fix $d$.  If $\theUB(d) = 0$, then $\comp(\varepsilon,d) = 0 \le C_{\vp}\, T(\varepsilon^{-1},d,\vp)$ automatically for all $\varepsilon \in [\theM(d), \infty)$.
 
-For the case $\theUB(d)> 0$, we utilize upper bound \eqref{eq:compUP_rest}, specializing to the case of $\thed=d$ and $N = \min\left(\lceil L_{\vp}\, T(0,d,\vp)\rceil,\theUB(d)\right)$:
+For the case $\theUB(d)> 0$, we utilize \peter{the} upper bound \eqref{eq:compUP_rest}, specializing to the case of $\thed=d$ and $N = \min\left(\lceil L_{\vp}\, T(0,d,\vp)\rceil,\theUB(d)\right)$:
 \begin{align*}
@@
  \ge
-  \left[\frac{(i-1)}{C_{\vp}}\right]^\tau \qquad i\in I_{d,\vp},  \ d \in \naturals, \\
+  \left[\frac{(i-1)}{C_{\vp}}\right]^\tau, \qquad \forall i\in I_{d,\vp},  \ d \in \naturals, \\
   \label{eq:rest_ineq}
  \frac{1}{T (\lambda_{i,d}^{-1},d,\tau \vp)} \le
-\frac{K_{\vp,\tau}\, C_{\vp}^\tau}{(i-1)^\tau}\qquad \forall i \in I_{d,\vp} \setminus\{1\}, \ d \in \naturals .
+\frac{K_{\vp,\tau}\, C_{\vp}^\tau}{(i-1)^\tau},\qquad \forall i \in I_{d,\vp} \setminus\{1\}, \ d \in \naturals .
 \end{gather}
@@
  \max(i(\infty,d,\vp'),2) & \le i(\infty,d,\vp') +1  = \lfloor C_{\vp'}\, T(0,d,\vp')\rfloor +2 \le  \left[C_{\vp'} + \frac{2}{T(0,d,\vp')}   \right]\, T(0,d,\vp')\\
- & \le  L_{\vp'}\, T(0,d,\vp')
+ & \peter{=}  L_{\vp'}\, T(0,d,\vp')
  \le \lceil L_{\vp'} T(0,d,\vp')\rceil .
@@
 \]
+\peter{[PETER: Here, I have the same question as in the previous proof.]}
+
 This means that $\theUB(d) \le i(\theM(d),d,\vp)-1$.  So, $\{ \lceil L_{\vp'} T(0,d,\vp')\rceil, \ldots, \theUB(d)\} \subseteq I_{d,\vp} \setminus \{1\}$.
@@
 \noindent 
-This concludes the proof of Theorem \ref{thm_main_tract2}.  \qed
+This concludes the proof of Theorem \ref{thm_main_rest_tract}.  \qed
 \end{proof}
@@
 \begin{itemize}
-\item Do we consider the case of normalized error?
-\peter{What would most likely change then, is: we would normalize all eigenvalues by dividing by the values of the $\lambda_{1,d}$, and all summations in the conditions could start with the index 1.
-It might be a bit more tricky for sub-$h$ tractability, where we would maybe make sure that all functions are still suitably defined.
-However, I would not expect new proof ideas.
-Maybe a remark along the lines of ``presumably everything works analogously'' is sufficient?}
 \item Are there cases of $T$ that do not correspond to known tractability measures? (Kachi)
@@
 
-\bibliography{FJHOwn23,FJH23}
+\bibliography{FJHOwn23,FJH23,Further_references}
 \bibliographystyle{elsarticle-num}

### 2023-07-06 Older_versions/GeneralizedTractability_230529.tex
Updates from Overleaf

--- 2023-06-07 GeneralizedTractability_230529.tex
@@
 
+%Comment these out when we get the J Complexity
 \setlength{\textheight}{24cm} \setlength{\textwidth}{16cm}
@@
 
-As adefined in \cite{GW11}, we say that a problem is \emph{quasi-polynomially tractable (QPT)} if there exist two constants $C$, $p > 0$, such that
+As defined in \cite{GW11}, we say that a problem is \emph{quasi-polynomially tractable (QPT)} if there exist two constants $C$, $p > 0$, such that
 \begin{equation}\label{expqpt}
@@
 \end{align*}
-Combining this bound with the upper bound on $S_c$ in \eqref{eq:lastone} establishes the finiteness of $S_{2c}$ and completes the proof of the necessary condition.
+Combining this bound with the upper bound on \peter{$S_{2c}$} in \eqref{eq:lastone} establishes the finiteness of $S_{2c}$ and completes the proof of the necessary condition.
 This concludes the proof of Theorem \ref{thm:subhT}.
@@
 
-\begin{example}[Weak Tractability]
+\begin{example}[Weak tractability]
 	Suppose that

### 2023-07-17 GeneralizedTractability_230607.tex
Updates from Overleaf

@@
 \DeclareMathOperator{\APP}{APP}
-\renewcommand{\hI}{\ci}
+\renewcommand{\hI}{\mathcal{I}}
 
@@
 \newcommand{\fred}[1]{\begingroup\color{blue}#1\endgroup}
-\newcommand{\peter}[1]{\begingroup\color{purple}#1\endgroup}
+\newcommand{\peter}[1]{\begingroup\color{violet}#1\endgroup}
 \newcommand{\kachi}[1]{\begingroup\color{ForestGreen}#1\endgroup}
@@
 
-TODO: Check in how far our conditions coincide with existing conditions for less general tractability notions (polynomial tractability, etc.).
-
-\medskip
-
 TODO: We should check for consistency of the use of the $\forall$ symbol in displayed formulas. Sometimes we use it, sometimes we do not, sometimes it is preceded by a comma, sometimes not, etc.
 
-TODO: We should check consistency of notation when using $\max$ or $\min$. Sometimes we use ``$(\ldots)$'' for the argument, sometimes we use ``$\{\ldots\}$''
+TODO: We should check consistency of notation when using $\max$ or $\min$. Sometimes we use ``$(\ldots)$'' for the argument, sometimes we use ``$\{\ldots\}$''  \fred{Fred will do this.}
 
@@
 A problem is tractable if the information complexity does not grow too large as the dimension of the problem increases or the error threshold decreases.
-There are a number of tractability results for numerical problems beginning with \cite{?}, spawning numerous articles, and filling a series of three impressive volumes \cite{NovWoz08a,NovWoz10a,NovWoz12a}.
+There are a number of tractability results for numerical problems beginning with \cite{W94a,W94b}, spawning numerous articles, and filling a series of three impressive volumes \cite{NovWoz08a,NovWoz10a,NovWoz12a}.
 The purpose of this article is to unify the many of these tractability results for approximation problems where all linear functional data is available.
@@
 \begin{equation}\label{eq:comp_def}
-\comp(\varepsilon, d) = \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon\}.
-\end{equation}
+\comp(\varepsilon, d) = \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon\},
+\end{equation}
+\peter{see \cite{NovWoz08a}.}
 \peter{
@@
 Alternatively, one could also consider the \textit{normalized} error criterion, where the error in \eqref{eq:errcrit} is divided by the so-called \textit{initial error}, which is the error without sampling the function, or, equivalently, the operator norm of $\SOL_d$.
-In the latter case, it is known (see, e.g., \cite{NovWoz08a}) that the information complexity is given by
+In the latter case, it is known (see, e.g., again \cite{NovWoz08a}) that the information complexity is given by
 \[
@@
 This means that, essentially, in the tractability analysis below, all criteria would be normalized by the first eigenvalue $\lambda_{1,d}$.
-
-For the sake of brevity and clarity of notation, we restrict ourselves to the absolute error criterion here, but presumably, analogous results hold for the normalized setting. 
+For the sake of brevity and clarity of notation, we restrict ourselves to the absolute error criterion here, but presumably analogous results hold for the normalized setting.
 }
@@
 We want to bound the complexity in terms of a simple function, $T$, of $\varepsilon^{-1}$ and $d$ and identify simple conditions on the singular values that are equivalent to this bound holding.
-\peter{We would like to point out that generalized tractability specified by function $T$ has been considered before in the literature.
+\peter{We would like to point out that generalized tractability specified by a function $T$ has been considered before in the literature.
 In particular, there are several papers by Gnewuch and Wo\'{z}niakowski (see \cite{GW06,GW08,GW09,GneWoz11a} ), and also \cite[Chapter 8]{NovWoz08a} is devoted to this topic.
-To our best knowledge, however, these references mainly focus on the special case tensor product problems, which we do not do here, and the conditions for tractability derived there are mostly in terms of properties of the function $T$, and not in terms of sums of (functions of) the eigenvalues of a problem.
+To our best knowledge, however, these references mainly focus on the special case of tensor product problems, which we do not do here, and the conditions for tractability derived there are mostly in terms of properties of the function $T$, and not in terms of sums of (functions of) the eigenvalues of a problem.
 Hence, we consider the present paper an addition to what is presently known on this subject.}
@@
 The conditions we require $T$ to satisfy are described in  Section \ref{sec:not}, however, the basic idea is that we define our approximation problem to be tractable if $\comp(\varepsilon, d) \le  C_{\vp}\, T(\varepsilon^{-1},d,\vp)$ for some constant, $C_{\vp}$, depending only on the parameter $\vp$.
-In practice, we expect $T(\varepsilon^{-1},d,\vp)$ to increase sub-exponentially  with increasing $\varepsilon^{-1}$ and/or $d$, however, most of our theorems do not require such an assumption.
+\kachi{The parameter $\vp$ is a $s$-dimensional vector, where $\vp \geq 0$ implies that each component of $\vp$ is nonnegative.} In practice, we expect $T(\varepsilon^{-1},d,\vp)$ to increase sub-exponentially  with increasing $\varepsilon^{-1}$ and/or $d$, however, most of our theorems do not require such an assumption.
 
@@
 \peter{TODO: Maybe add a short paragraph on the notation used in the paper and on its structure? In particular, we should introduce
-an ordering of the parameters $\vp$.}\\
-\\
-
+an ordering of the parameters $\vp$.}[\kachi{KACHI: I will take care of this}]
+
+\kachi{[KACHI: I will write about notations used in this paper. Is there are need to change notations like $[1,\infty)$ to $\naturals$ and $[0,\infty)$ to $\naturals_0$]}
+
+\kachi{We denote the set of positive integers by $\naturals$ and and the set of non-negative integers by $\naturals_0$.}
 In Section \ref{sec:spt}, we give the definitions of the considered tractability notions, in particular (strong) tractability.
 We consider strong tractability when the information complexity is independent of the dimension, $d$.
-We then turn to tractability  when the information complexity is polynomial in $d$ and $\varepsilon^{-1}$.
-In Section \ref{sec:examples} we provide examples of strong(tractability) functions for both the algebraic and exponential cases.
+We then turn to tractability  when the information complexity \peter{may depend on both} $d$ and $\varepsilon^{-1}$.
+In Section \ref{sec:examples} we provide examples of \peter{tractability functions} for both the algebraic and exponential cases.
 We also consider other notions of tractability such as quasi-polynomial tractability, and a generalized notion of weak tractability.
-In the case of the generalized weak tractability, we give the necessary and sufficient conditions on the notion of exponential tractability in Section \ref{sec:subh}.
+In the case of generalized weak tractability, we give the necessary and sufficient conditions on the notion of exponential tractability in Section \ref{sec:subh} \peter{[I think I do not quite understand what we mean by the last sentence.]}.
 
@@
 A tractability function $T$ is a function of a simple form that provides an upper bound on the \peter{information} complexity of a problem.
-Some examples of tractability functions commonly considered are provided in Table \ref{tab:commonT}.
+Some examples of tractability functions commonly considered are provided in Table \ref{tab:commonT} \peter{[I think we can remove the latter sentence, as it is repeated below.]}.
 \kachi{}
@@
 
-We first consider the simpler case when the complexity is essentially independent of the dimension, $d$.
+We first consider the simpler case when the \peter{information} complexity is essentially independent of the dimension, $d$.
 The proof also introduces the line of argument used for the case where there is $d$-dependence.
@@
 We make the first part of the argument in some generality so that it can be reused in the proof of Theorem \ref{thm_main_tract2} for tractability.  Fix any $\varepsilon > 0$ and any $d \in \naturals$.
-
+\kachi{[KACHI: It seems the notation of the dimension has change from $d$ to $\delta$. I will work on this.]}
 Since the $\lambda_{i,d}$ are non-increasing in $i$, it follows that the $T(\lambda_{i,d}^{-1},\thed,\vp)$ are non-decreasing in $i$ for any $\thed\in\naturals$.
@@
  \ge
-  \left[\frac{(i-1)}{C_{\vp}}\right]^\tau \qquad \forall i \ge i(\infty,\vp)), \ d \in \naturals, \\
+  \left[\frac{(i-1)}{C_{\vp}}\right]^\tau \qquad \forall i \ge i(\infty,\vp), \ d \in \naturals, \\
  \frac{1}{T (\lambda_{i,d}^{-1},1,\tau \vp)} \le
-\frac{K_{\vp,\tau}\, C_{\vp}^\tau}{(i-1)^\tau}\qquad \forall i \ge \max\{i(\infty,\vp),2\}), \ d \in \naturals .
+\frac{K_{\vp,\tau}\, C_{\vp}^\tau}{(i-1)^\tau}\qquad \forall i \ge \max\{i(\infty,\vp),2\}, \ d \in \naturals .
 \end{gather*}
@@
 The argument proving equivalent conditions for tractability is similar to, but somewhat more involved than the proof of Theorem \ref{thm_main_strong_tract2}.
-Moreover, the specification of the set of optimal parameters is not as precise as in Theorem \ref{thm_main_strong_tract2}.
+Moreover, the specification of the set of optimal parameters is not as precise as in Theorem \ref{thm_main_strong_tract2} \peter{[Is the latter sentence still true?]}.
 
@@
     \textbf{Sufficient condition:}\\
-Suppose that \eqref{eq:tractiff4} holds for some $\vp \ge 0$. 
+Suppose that \eqref{eq:tractiff4} holds for some $\vp \ge \boldsymbol{0}$. 
 By the argument in the proof of the sufficient condition for Theorem \ref{thm_main_strong_tract2}, it follows from \eqref{eq:compUP} with $\thed=d$ and $N = \lceil L_{\vp}\, T(0,d,\vp)\rceil$ that 
@@
 
-The (strong) polynomial tractability for both the algebraic case and the exponential case will be first considered as follows:
+The \peter{concept of} (strong) polynomial tractability for both the algebraic case and the exponential case will be first considered as follows:
 
@@
 \end{multline*}
-This essentially recovers the result on polynomial tractability in \cite[Theorem 5.1]{NovWoz08a} %\fred{same theorem as above??, what about optimality in \cite[Theorem 5.1]{NovWoz08a}}.
+\peter{[Is the latter statement still correct?]}
+This essentially recovers the result on polynomial tractability in \cite[Theorem 5.1]{NovWoz08a}. %\fred{same theorem as above??, what about optimality in \cite[Theorem 5.1]{NovWoz08a}}.
 \end{example}
@@
 \]
-
 where \peter{$\vp=p$} is a scalar. Then Theorem \ref{thm_main_strong_tract2} yields the equivalent condition for \peter{exponential strong polynomial tractability:} 
@@
     \begin{equation}\label{eq:KW_exp_pt}
-        \sup_{d\in\naturals} d^{-\tau_1} \sum_{i=\lceil C d^{\tau_3} \rceil}^{\infty} \lambda_{i,d}^{i^{-\tau}} < \infty. 
+        \sup_{d\in\naturals} d^{-\tau_1} \sum_{i=\lceil C d^{\tau_3} \rceil}^{\infty} \lambda_{i,d}^{i^{-\tau_2}} < \infty. 
     \end{equation}
 \end{itemize}
-It should be noted that, e.g., the condition \eqref{eq:exp_spt} is easier to check in practice than the condition \eqref{eq:KW_exp_spt}.
-Indeed, since in \eqref{eq:KW_exp_spt} the summation indices $i$ show up in the exponents of the summands, we need the exact ordering of the eigenvalues $\lambda_{i,d}$, whereas in \eqref{eq:exp_spt} we only have a summation of the values of $1/T(\lambda_{i,d}^{-1},t,\vp)$, and the exact order of the eigenvalues can be neglected.
-
-Secondly, we would like to show that the conditions \eqref{exp_spt} and \eqref{eq:KW_exp_spt}, as well as the conditions \eqref{exp_pt} and \eqref{eq:KW_exp_pt} are indeed equivalent.
+Firstly, it should be noted that the condition \eqref{eq:exp_spt} is easier to check in practice than the condition \eqref{eq:KW_exp_spt}.
+Indeed, since in \eqref{eq:KW_exp_spt} the summation indices $i$ show up in the exponents of the summands, we need the exact ordering of the eigenvalues $\lambda_{i,d}$, whereas in \eqref{eq:exp_spt} we only have a summation of the values of $1/T(\lambda_{i,d}^{-1},d,\vp)$, and the exact order of the eigenvalues can be neglected.
+A similar
+observation holds for \eqref{eq:exp_pt} and \eqref{eq:KW_exp_pt}.
+
+Secondly, we would like to show that the conditions \eqref{eq:exp_spt} and \eqref{eq:KW_exp_spt}, as well as the conditions \eqref{eq:exp_pt} and \eqref{eq:KW_exp_pt} are indeed equivalent.
 We do this for the latter two conditions, i.e., for the conditions on exponential polynomial tractability.
@@
 \[
-M:=\sup_{d\in\naturals} d^{-\tau_1} \sum_{i=\lceil C d^{\tau_3} \rceil}^{\infty} \lambda_{i,d}^{i^{-\tau}} < \infty. 
-\]
+M:=\sup_{d\in\naturals} d^{-\tau_1} \sum_{i=\lceil C d^{\tau_3} \rceil}^{\infty} \lambda_{i,d}^{i^{-\tau_2}} < \infty 
+\]
+for some $\tau_1,\tau_3\ge 0$ and $\tau_2, C>0$.
 Define
@@
 B_d:=\left\{i\in\naturals \colon i\ge \left\lceil Cd^{\tau_3}\right\rceil\quad\mbox{and}\quad 
-\lambda_{i,d}^{i^{-\tau_2}}>\frac{1}{e}\right\}
-\]
-Due to our assumption, we see that $\abs{B_d} < M\,e\,d^{\tau_1}$ and $\abs{B_d}\le \lfloor M\,e\,d^{\tau_1} \rfloor$.
+\lambda_{i,d}^{i^{-\tau_2}}>\frac{1}{e}\right\}.
+\]
+Due to our assumption, we see that $\abs{B_d} < e\,M\,d^{\tau_1}$ and $\abs{B_d}\le \lfloor e\,M\,d^{\tau_1} \rfloor$.
 Suppose now that $i\ge \lceil C d^{\tau_3}\rceil$ but $i\not\in B_d$, which means that
 \[\lambda_{i,d}^{i^{-\tau_2}} \le \frac{1}{e} \Leftrightarrow \log (\lambda_{i,d}^{-1})\ge i^{\tau_2}.\]
-Now, choose $p> 1/\tau_2$, $q=\max\{\tau_1,\tau_3\}$, and $L_{(p,q)}=\max\{C, M\, e\}$, which implies that $\lceil L_{(p,q)} d^{q}\rceil \ge M\, e\, d^{\tau_1}$. Then, for any $d\in\naturals$, 
+Now, choose $p> 1/\tau_2$, $q=\max\{\tau_1,\tau_3\}$, and $L_{(p,q)}=\max\{C, e\, M\}$, which implies that $\lceil L_{(p,q)} d^{q}\rceil \ge e\, M\, d^{\tau_1}$. Then, for any $d\in\naturals$, 
 \begin{eqnarray*}
@@
 && + d^{-q} \sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\not\in B_d}}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p}\\
-&\le& d^{-q} M\, e\, d^{\tau_1} + d^{-q}\sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\not\in B_d}}^\infty \frac{1}{[\log (\lambda_{i,d}^{-1})]^p}\\
-&\le& 1 + d^{-q}\sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\not\in B_d}}^\infty \frac{1}{i^{\tau_2 p}}\\
-&\le & 1 + \zeta (\tau_2 p).
+&\le& d^{-q} e\, M\, d^{\tau_1} + d^{-q}\sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\not\in B_d}}^\infty \frac{1}{[\log (\lambda_{i,d}^{-1})]^p}\\
+&\le& e\, M + d^{-q}\sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\not\in B_d}}^\infty \frac{1}{i^{\tau_2 p}}\\
+&\le & e\, M + \zeta (\tau_2 p).
 \end{eqnarray*}
@@
 We will show next that this implies Condition \eqref{eq:KW_exp_pt}.
-Indeed, due to \eqref{eq:exp_pt}, there exists a positive constant $M$ (w.l.o.g., we can assume that $M\ge 1$) such that for all $d\in\naturals$,
+Indeed, due to \eqref{eq:exp_pt}, there exists a positive constant $M$ (w.l.o.g., we can assume that $M\ge 1$), and $p\ge 0$ (again, w.l.o.g., let us assume $p>0$), $q\ge 0$, and $L_{(p,q)}>0$ such that for all $d\in\naturals$,
 \[
@@
 \sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty  \frac{1}{T(\lambda_{i,d}^{-1},1,\vp)}
-\le \frac{d^q M}{n-\lceil L_{(p,q)} d^{q}\rceil +1 }
+\le \frac{d^q M}{n-\lceil L_{(p,q)} d^{q}\rceil +1 }.
 \]
@@
 \[
-\frac{n}{d^q M}-\frac{L_{(p,q)}}{M}\le\frac{n-\lceil L_{(p,q)} d^{q}\rceil +1 }{d^q M} \le [\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p 
-\le [1 + \log(1+\lambda_{i,d}^{-1})]^p.
+\frac{n}{d^q M}-\frac{L_{(p,q)}}{M}\le\frac{n-\lceil L_{(p,q)} d^{q}\rceil +1 }{d^q M} \le [\max\{1,\log(1+\lambda_{n+1,d}^{-1})\}]^p 
+\le [1 + \log(1+\lambda_{n+1,d}^{-1})]^p.
 \]
@@
 \[
-\frac{n}{d^q K} \le [1 + \log(1+\lambda_{n,d}^{-1})]^p,
+\frac{n}{d^q K} \le [1 + \log(1+\lambda_{n+1,d}^{-1})]^p\quad \forall n > \lceil L_{(p,q)} d^{q}\rceil,
 \]
@@
 \[
-\frac{n^{1/p}}{d^{q/p} K^{1/p}} -1 \le \log(1+\lambda_{n,d}^{-1}).
+\frac{n^{1/p}}{d^{q/p} K^{1/p}} -1 \le \log(1+\lambda_{n+1,d}^{-1})\quad \forall n > \lceil L_{(p,q)} d^{q}\rceil.
 \]
@@
 \lambda_{n,d} \le \exp\left(-\frac{n^{1/p}}{\widetilde{K}^{1/p} d^{q/p}}\right)
-\quad \forall n > \lceil L_{(p,q)} d^{q}\rceil,
+\quad \forall n > \lceil L_{(p,q)} d^{q}\rceil-1,
 \]
@@
 
-\kachi{In the following example, we provide a brief summary of these notions of tractability.
-We would like to emphasize that this example was previously known (see \cite{?}) where in this case, the roles of $\varepsilon^{-1}$ and $d$ are separated.
+\kachi{In the following example, we provide a brief summary of these \peter{[What does ``these'' refer to?]} notions of tractability.
+We would like to emphasize that this example was previously known (see, e.g., \cite{GW06}) where in this case, the roles of $\varepsilon^{-1}$ and $d$ are separated.
 In order to accomplish this, we will first define two functions $\phi$ and $\psi$ with positive values that are increasing in both of their arguments.
@@
 %To do this, we introduce two positive-value functions that are increasing in both arguments so as to take possibly different exponents of $\varepsilon^{-1}$ and $d$.
-The equivalent conditions for this example are assumed to take the same form as those in Theorems \ref{thm_main_strong_tract2} and \ref{thm_main_tract2}.}
-
-\peter{[PETER: Kachi, can you work a bit more on this introductory text, please? Right now, it does not contain much information.]}
-\kachi{[KACHI: Done. Although I am having trouble adding references, do you have any suggestions.]}
+The equivalent conditions for this example are assumed to \peter{[Why ``are assumed to?'']} take the same form as those in Theorems \ref{thm_main_strong_tract2} and \ref{thm_main_tract2}.}
 
@@
 
-We say that a problem is defined as $T$-separable tractable \peter{[PETER: I am wondering if ``$T$-separably tractable'' is better?
+We say that a problem is $T$-separable tractable \peter{[PETER: I am wondering if ``$T$-separably tractable'' is better?
 But obviously, you know that better than me.]} with parameter $\vp$ iff there exists a positive constant $C_{\vp}$ which does not depend on $\varepsilon$ and $d$ such that
@@
 \end{equation*}
-for some $p>0$ and $L_p \in \naturals$. Furthermore, the optimal $p$ is also infimum of all $p$.
-Theorem \ref{thm_main_tract2} yields the following equivalent condition for 
-separable tractability
+for some $p>0$ and $L_p \in \naturals$. Furthermore, the optimal $p$ is also the infimum of all $p$ \peter{satisfying the latter condition}.
+Theorem \ref{thm_main_tract2} yields the following equivalent condition for separable tractability:
 \[
  \sup_{d \in \naturals} \frac{1}{\psi(d,q)} \sum_{i = \lceil L_{(p,q)}\psi(d,q)\rceil}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)} < \infty,
-\] for some $p,q >0$ and $L_{(p,q)}\in\naturals$.
+\] for some $p,q >0$ and \peter{a positive constant $L_{(p,q)}$}.
 \end{example}
-\kachi{Next, we will introduce another summarized notion of tractability.
+\kachi{Next, we will introduce another summarized \peter{[what do we mean by ``summarized''?]} notion of tractability.
 In the following, we will define two functions $\hat{\phi}$ and $\hat{\psi}$ that take the roles of $\varepsilon^{-1}$ and $d$.
-As will be seen below, this tractability function is equivalent to the so-called \emph{quasi-polynomial tractability}.}
-\peter{[PETER: Also here, Kachi, please work on the introductory text.]}
+As will be seen below, this tractability function is equivalent \peter{[[I am not sure it is equivalent.]]} to the so-called \emph{quasi-polynomial tractability}.}
+\
 \begin{example}[Non-separable tractability]
@@
 \[
-\sup_{d\in\mathbb{N}}\sum_{i=L_p\,\hat{\phi}(0)^{p \, \hat{\psi}(d)}} [\exp ( \hat{\phi}(\lambda_{i,d}^{-1}))]^{-p \, \hat{\psi}(d)}\quad \text{for some } p \geq 0, L_p \in \naturals.
+\sup_{d\in\mathbb{N}}\sum_{\peter{i=\lceil L_p\,\hat{\phi}(0)^{p \, \hat{\psi}(d)}\rceil}} [\exp ( \hat{\phi}(\lambda_{i,d}^{-1}))]^{-p \, \hat{\psi}(d)}\quad \text{for some } p \geq 0, \peter{L_p >0}.
 \]
@@
 for all $\varepsilon \in (0,1]$ and $d\in\mathbb{N}$.
-\end{definition}}
+\end{definition}
+Note that the following examples are given below such that they equivalent to the definition in \cite{GneWoz11a}
+}
 
@@
 \[
-\sup_{d\in\mathbb{N}}\,d^{-p}\sum_{i=L_p\,d^{p}} \left(\min\{1,\lambda_{i,d}\} \right)^{p(1+\log d)} < \infty \qquad \text{for some } p \geq 0, L_p \in \naturals.\]
+\sup_{d\in\mathbb{N}}\,d^{-p}\sum_{\peter{i=\lceil L_p\,d^{p}}\rceil} \left(\min\{1,\lambda_{i,d}\} \right)^{p(1+\log d)} < \infty \qquad \text{for some } p \geq 0, \peter{L_p >0}.\]
 \end{example}
+\peter{This essentially recovers \cite[Theorem 23.1]{NovWoz12a}.
+}
 Next, we will consider the exponential case as follows.
@@
 \[
-\sup_{d\in\mathbb{N}}\,d^{-p}\sum_{i=L_p\,d^{p}} \left(\min\{1,\log(1+\lambda_{i,d})\} \right)^{p(1+\log d)}e^{-p} < \infty \quad \text{for some } p \geq 0, L_p \in \naturals.
-\]
+\sup_{d\in\mathbb{N}}\,d^{-p}\sum_{\peter{i=\lceil L_p\,d^{p}\rceil}} \frac{1}{\left(\max\{1,\log(1+\lambda_{i,d}^{-1})\} \right)^{p(1+\log d)}}< \infty \quad \text{for some } p \geq 0, \peter{L_p >0}.
+\]
+\peter{This essentially recovers \cite[Theorem 2]{KriWoz19a}.
+}
 \end{example}
@@
 \section{Sub-$h$ Tractability}\label{sec:subh}
-In this section we generalize the concept of weak tractability \peter{(see again\cite{NovWoz08a}--\cite{NovWoz12a})}.  Let  $h:[0,\infty) \to [1,\infty)$ satisfy
+In this section we generalize the concept of weak tractability \peter{(see again \cite{NovWoz08a}--\cite{NovWoz12a})}.  Let  $h:[0,\infty) \to [1,\infty)$ satisfy
 \begin{equation} \label{eq:h_cond}
@@
 Furthermore, let us denote the inverse function of $h$ by $h^{-1}$.
-Then, for arbitrary $z,w \in [1,\infty)$ we choose $x=h^{-1}(z)$ and $y=h^{-1}(w)$, to obtain
+Then, for arbitrary $z,w \in [1,\infty)$ we choose $x=h^{-1}(z)$ and $y=h^{-1}(w)$, to obtain \peter{from \eqref{eq:h_cond}}
 \[
@@
 \\
-&  \le  h^{-1} (2 S_c) + cT (\varepsilon^{-1},d).
+&  \le  h^{-1} (2 S_c) + cT (\varepsilon^{-1},d),
 \quad \forall c, \varepsilon > 0, \, d \in \naturals.
@@
 \end{equation}
-\peter{[PETER: We do not have $\lambda_{\max}$ anymore... . Do we need it?]}
+\peter{[PETER: We do not have $\lambda_{\max}$ anymore, and it could be unbounded, right?
+But I think this can be fixed: I keep the black (current) version, and provide a purple (new) version below, with only few changes.
+Please check carefully whether we can use the purple one.]}
 By varying $\varepsilon^{-1}$ in the interval $[\varepsilon^{-1}_{\max}(d,c),\infty)$,  the integer $n(\varepsilon,d,c)$ attains, \peter{by Assumption \eqref{eq:Tlim},} all values greater than or equal to $n^*(d,c)$.
@@
 Combining this bound with the upper bound on $S_c$ in \eqref{eq:lastone} establishes the finiteness of $S_{2c}$ and completes the proof of the necessary condition.
-This concludes the proof of Theorem \ref{thm:subhT}.  \qed
+This concludes the proof of Theorem \ref{thm:subhT}.
+
+\bigskip
+
+\peter{***ALTERNATIVE VERSION OF THE LAST PART OF THE PROOF - PLEASE CHECK (essentially just by replacing $\lambda_{\max}$ by something different***}
+
+\bigskip
+
+\peter{
+For a fixed $c$ and $d$, define
+\begin{equation} \label{eq:nstardef}
+	\varepsilon^{-1}_{\max}(d,c) := \max(V_c - d,\lambda_{1,d}^{-1}), \qquad n^*(d,c) : = n(\varepsilon^{-1}_{\max}(d,c),d,c) \le h(cT(\varepsilon^{-1}_{\max}(d,c),d)) +1.
+\end{equation}
+By varying $\varepsilon^{-1}$ in the interval $[\varepsilon^{-1}_{\max}(d,c),\infty)$,  the integer $n(\varepsilon,d,c)$ attains, \peter{by Assumption \eqref{eq:Tlim},} all values greater than or equal to $n^*(d,c)$.
+Thus, by \eqref{eq:nedcbound},
+\begin{align}
+		n &\le h(cT(\lambda^{-1}_{n,d},d)) \qquad  \forall n \ge n^*(d,c), \label{eq:subhTneq}\\
+		\nonumber
+		\frac{1}{h(2 cT(\lambda^{-1}_{n,d},d)) } & \le \frac{1}{[h(cT(\lambda^{-1}_{n,d},d))]^{2}}  \le \frac 1{n^2}   \qquad  \forall n \ge n^*(d,c) \qquad \text{by \eqref{eq:h_cond}}. \\
+		\intertext{Combining this inequality with the upper bound on $n^*(d,c)$ yields}
+		\nonumber
+		S_{2c} & =\sup_{d\in\naturals}  \, \sum_{i=1}^\infty \frac1{h(2cT(\lambda_{i,d}^{-1},d))} \\
+		\nonumber
+		&  = \sup_{d\in\naturals} \left [
+		\sum_{i=1}^{n^*(d,c)-1} \frac1{h(2cT(\lambda_{i,d}^{-1},d))}
+		+ \sum_{i=n^*(d,c)}^\infty \frac1{h(2cT(\lambda_{i,d}^{-1},d))}
+		\right]\\
+		 \nonumber
+		 & \le \sup_{d\in\naturals} \left [
+\frac{n^*(d,c)-1}{h(2cT(\lambda_{1,d}^{-1},d))}
++ \sum_{i=1}^\infty \frac1{n^2}
+\right]
+ \qquad \text{by \eqref{eq:subhTneq}}\\
+ \label{eq:lastone}
+		 & \le \sup_{d\in\naturals} \left [
+		 \frac{ h(cT(\varepsilon^{-1}_{\max}(d,c),d))}{h(2cT(\lambda_{1,d}^{-1},d))}
+		\right] + \frac{\pi^2}{6}
+		\qquad \text{by \eqref{eq:nstardef}.}
+\end{align}
+
+Note that
+\[
+\varepsilon^{-1}_{\max}(d,c) = \max(V_c - d,\lambda_{1,d}^{-1})
+= \begin{cases} V_c - d \le V_c, & d \in \{1, \ldots, d^*_c : = \lfloor V_c - \lambda_{1,d}^{-1} \rfloor\}, \\
+\lambda_{1,d}^{-1}, & d \in \{d^*_c+1, \ldots\}.
+\end{cases}
+\]
+Note that it follows from above that we always have $d^*_c\le \lfloor V_c \rfloor$
+
+Recalling that $T$ is non-decreasing in its arguments, this implies that
+\begin{align*}
+    \MoveEqLeft{\sup_{d\in\naturals} \,
+		 \frac{ h(cT(\varepsilon^{-1}_{\max}(d,c),d))}{h(2cT(\lambda_{1,d}^{-1},d))}}\\
+  &\le \max \left \{
+  \sup_{d \in \{1, \ldots, d^*_c\}} \,
+		 \frac{ h(cT(\varepsilon^{-1}_{\max}(d,c),d))}{h(2cT(\lambda_{1,d}^{-1},d))},
+  \sup_{d\in \{d^*_c+1, \ldots \}} \,
+		 \frac{ h(cT(\varepsilon^{-1}_{\max}(d,c),d))}{h(2cT(\lambda_{1,d}^{-1},d))}
+  \right \} \\
+  & \le \max \left \{
+  \sup_{d \in \{1, \ldots, d^*_c\}}  \,
+		 \frac{ h(cT(V_c,d))}{h(2cT(\lambda_{1,d}^{-1},d))}
+  ,
+  \sup_{d\in \{d^*_c+1, \ldots \}}  \,
+		 \frac{ h(cT(\lambda_{1,d}^{-1},d))}{h(2cT(\lambda_{1,d}^{-1},d))}
+  \right \}
+  \\
+  & \le \max \left \{
+		 \frac{ h(cT(V_c,d^*_c))}{h(2cT(\lambda_{1,d}^{-1},1))},
+  \sup_{d\in \{d^*_c+1, \ldots \}}  \,
+		 \frac{ h(cT(\lambda_{1,d}^{-1},d))}{[h(cT(\lambda_{1,d}^{-1},d))]^2}
+  \right \} \\
+  & = \max \left \{
+		 \frac{ h(cT(V_c,d^*_c))}{h(2cT(\lambda_{1,d}^{-1},1))},
+		 \frac{1}{h(cT(\lambda_{1,d}^{-1},d_c^*+1))}
+  \right \} \\
+  & \le \max \left \{
+		 \frac{ h(cT(V_c,\lfloor d^*_c \rfloor))}{1},
+		 1
+  \right \} \\
+  & = h(cT(V_c,\lfloor V_c \rfloor))
+		  \\
+  & < \infty,
+\end{align*}
+where we used that $h(\cdot)$ is always at least 1.
+Combining this bound with the upper bound on $S_c$ in \eqref{eq:lastone} establishes the finiteness of $S_{2c}$ and completes the proof of the necessary condition.
+This concludes the proof of Theorem \ref{thm:subhT}.
+}
+
+\qed
 \end{proof}
@@
 \begin{equation}
-    \Omega  := \{(\varepsilon^{-1},d) : \varepsilon \in (\theM(d),\infty), \ d \in \naturals \}, \qquad \text{where }E : \naturals \to [0,\infty).
-\end{equation}
-We then expect that the equivalent conditions for (strong) tractability will be similar in form, but weaker than, the conditions in Theorems  \ref{thm_main_strong_tract2} and \ref{thm_main_tract2}.
+    \Omega  := \{(\varepsilon^{-1},d) : \varepsilon \in (\theM(d),\infty), \ d \in \naturals \}, \qquad \text{where }\theM : \naturals \to [0,\infty).
+\end{equation}
+We then expect that the equivalent conditions for (strong) tractability will be similar in form, but weaker than the conditions in Theorems  \ref{thm_main_strong_tract2} and \ref{thm_main_tract2}.
 
@@
 
-Define $M: \naturals \to \natzero \cup \{\infty\}$
+Define $\theUB: \naturals \to \natzero \cup \{\infty\}$
 \begin{equation} \label{eq:Mddef}
@@
 \begin{equation} \label{eq:hIdef}
-\hI_{d}:=\begin{cases} 
+\mathcal{I}_d :=\begin{cases} 
 \emptyset, & \theUB(d) = 0, \\
@@
 \end{equation}
+\peter{[I have no idea why the $\mathcal{I}_d$ is not displayed correctly above.]}
 From the definition of $\theUB(d)$ it follows that $(\lambda_{i,d}^{-1},d) \in \Omega  \iff i \in \hI_d$, and
@@
 
-Moreover, given that $T$ is increasing in its arguments, we have the following equivalent expression for the complexity via \eqref{eq:comp_def}:
+Moreover, given that $T$ is increasing in its arguments, we have the following equivalent expression for the complexity via 
+\eqref{eq:comp_def} \peter{[Again, no clue why the $\mathcal{I}_d$ is not displayed correctly below]}:
 \begin{align} %\label{eq:comp_equiv}
@@
 
-For $(\varepsilon^{-1}, d) \in \Omega$, define the positve integers
+For $(\varepsilon^{-1}, d) \in \Omega$, define the positive integers
 \[
@@
 
-\fred{
+\fred{Fred will draft something.
 \begin{itemize}

### 2023-07-17 GeneralizedTractability2023July17.tex
Updates from Overleaf
Fred M2 2023 Mac Updates

--- 2023-07-17 GeneralizedTractability_230607.tex
@@
 
-\title{\fred{A Unified Treatment of Tractability of Approximation Problems}}
+\title{A Unified Treatment of Tractability of Approximation Problems Defined on Hilbert Spaces}
 
@@
 
-TODO: We should check consistency of notation when using $\max$ or $\min$. Sometimes we use ``$(\ldots)$'' for the argument, sometimes we use ``$\{\ldots\}$''  \fred{Fred will do this.}
+%TODO: We should check consistency of notation when using $\max$ or $\min$. Sometimes we use ``$(\ldots)$'' for the argument, sometimes we use ``$\{\ldots\}$''  \fred{Fred will do this.}
 
@@
 
-The information complexity of the problem $\SOL_d$ is given by the function $\comp:(0,\infty) \times \naturals \to \natzero$, where $\comp(\varepsilon,d)$ is the number of linear functionals required by the best \peter{admissible} algorithm to satisfy the error criterion \eqref{eq:errcrit}.
+The information complexity of the problem $\SOL_d$ is given by the function $\comp:(0,\infty) \times \naturals \to \natzero$, where $\comp(\varepsilon,d)$ is the number of linear functionals required by the best admissible algorithm to satisfy the error criterion \eqref{eq:errcrit}.
 By definition, the complexity is non-decreasing  as $\varepsilon$ tends to zero.
@@
 \[
-\APP_d(f,\varepsilon) = \sum_{i=1}^n \peter{\SOL_d(u_{i,d})} \ip[\cf_d]{f}{u_i},
+\APP_d(f,\varepsilon) = \sum_{i=1}^n \SOL_d(u_{i,d}) \ip[\cf_d]{f}{u_i},
 \]
@@
 \end{equation}
-\peter{see \cite{NovWoz08a}.}
-\peter{
+see \cite{NovWoz08a}.
+
 Strictly speaking, we are considering the \textit{absolute} error criterion in this paper.
@@
 For the sake of brevity and clarity of notation, we restrict ourselves to the absolute error criterion here, but presumably analogous results hold for the normalized setting.
-}
-
-The question of tractability is one of determining how fast the \peter{information} complexity increases as $\varepsilon$ tends to zero and/or as $d$ tends to infinity.
+
+The question of tractability is one of determining how fast the information complexity increases as $\varepsilon$ tends to zero and/or as $d$ tends to infinity.
 We want to bound the complexity in terms of a simple function, $T$, of $\varepsilon^{-1}$ and $d$ and identify simple conditions on the singular values that are equivalent to this bound holding.
-\peter{We would like to point out that generalized tractability specified by a function $T$ has been considered before in the literature.
+We would like to point out that generalized tractability specified by a function $T$ has been considered before in the literature.
 In particular, there are several papers by Gnewuch and Wo\'{z}niakowski (see \cite{GW06,GW08,GW09,GneWoz11a} ), and also \cite[Chapter 8]{NovWoz08a} is devoted to this topic.
 To our best knowledge, however, these references mainly focus on the special case of tensor product problems, which we do not do here, and the conditions for tractability derived there are mostly in terms of properties of the function $T$, and not in terms of sums of (functions of) the eigenvalues of a problem.
-Hence, we consider the present paper an addition to what is presently known on this subject.}
+Hence, we consider the present paper an addition to what is presently known on this subject.
 
@@
 We consider strong tractability when the information complexity is independent of the dimension, $d$.
-We then turn to tractability  when the information complexity \peter{may depend on both} $d$ and $\varepsilon^{-1}$.
-In Section \ref{sec:examples} we provide examples of \peter{tractability functions} for both the algebraic and exponential cases.
+We then turn to tractability  when the information complexity may depend on both $d$ and $\varepsilon^{-1}$.
+In Section \ref{sec:examples} we provide examples of tractability functions for both the algebraic and exponential cases.
 We also consider other notions of tractability such as quasi-polynomial tractability, and a generalized notion of weak tractability.
@@
 Let $T$ be a function given in \eqref{eq:Tspec}.
-A tractability function $T$ is a function of a simple form that provides an upper bound on the \peter{information} complexity of a problem.
-Some examples of tractability functions commonly considered are provided in Table \ref{tab:commonT} \peter{[I think we can remove the latter sentence, as it is repeated below.]}.
-\kachi{}
+A tractability function $T$ is a function of a simple form that provides an upper bound on the information complexity of a problem.
+
+\begin{definition}
+    A problem is defined as $T$-tractable with parameter $\vp$ iff there exists a positive constant $C_{\vp}$, which is independent of $\varepsilon$ and $d$, such that
+\begin{equation} \label{eq:tract_def}
+	\comp(\varepsilon,d) \le C_{\vp}\, T(\varepsilon^{-1},d,\vp) \qquad \forall \varepsilon >0, \ d \in \mathbb{N}.
+\end{equation}
+A problem is \emph{strongly}
+$T$-tractable with parameter $\vp$ iff the \peter{information} complexity is independent of the dimension of the problem, that is, there exists a positive constant $C_{\vp}$, again independent of $\varepsilon$ and $d$, such that
+\begin{equation} \label{eq:strong_tract_def}
+	\comp(\varepsilon,d) \le C_{\vp}\, T(\varepsilon^{-1},1,\vp) \qquad \forall \varepsilon >0 , \ d \in \mathbb{N}.
+\end{equation}
+We allow $\vp$ to be a scalar or vector as the situation dictates.
+\end{definition}
+
+For this definition of tractability to make sense we assume that
+\begin{subequations} \label{eq:Tconditions}
+\begin{equation} \label{eq:Tnondecreasing}
+	T \text{ is non-decreasing in all variables,}
+\end{equation}
+which implies that the problem is expected to be no easier by decreasing the tolerance, $\varepsilon$, or increasing the dimension, $d$.
+(This is why we make $T$ a function of $\varepsilon^{-1}$ rather than of $\varepsilon$.) Furthermore, increasing $\vp$ does not decrease $T(\cdot, \cdot, \vp)$.
+Since there are an infinite number of positive eigenvalues, it also makes sense to assume that
+\begin{equation}\label{eq:Tlim}
+	\lim_{\varepsilon \to 0} T(\varepsilon^{-1},d,\vp) = \infty \qquad \forall d \in \naturals, \ \vp \in [0,\infty)^s.
+\end{equation}
+Since $T(\cdot,d,\vp)$ is non-decreasing, we may define the following limit, which we assume will always be positive:
+\begin{equation}\label{eq:T0}	T(0,d,\vp):=\lim_{\varepsilon\to\infty}T(\varepsilon^{-1},d,\vp) = \inf_\varepsilon T(\varepsilon^{-1},d,\vp) \ge T(0,1,\vzero) > 0.
+\end{equation}
+\end{subequations}
+Finally, there is a technical assumption required for our analysis.  There exists a $K_{\vp,\tau}$ depending on $\vp$ and $\tau$, but  independent of $\varepsilon$ and $d$, such that
+\begin{equation} \label{eq:ptauassume}
+	[T(\varepsilon^{-1},d,\vp)]^\tau \le K_{\vp,\tau} T(\varepsilon^{-1},d,\tau \vp),   \quad \forall \varepsilon \in (0,\infty), \ d \in \naturals, \ \vp\in[0,\infty)^s, \ \tau\in [1,\infty).
+\end{equation}
+
+Certain common notions of tractability  covered by the general situation described above are provided in Table \ref{tab:commonT}.
+Here, $\vp = (p,q)$ in some cases and $\vp$ is a scalar in other cases.
+A general reference
+for results on algebraic tractability is \cite{NovWoz08a}, for exponential tractability we refer to \cite{HicKriWoz19a} and \cite{KriWoz19a}.
+
 \begin{table}
-    \caption{Common forms of the tractability function, $T$. \peter{[PETER: I changed the notation below, using ``algebraic" and ``exponential" first, to be in line with the literature.]}}
+    \caption{Common forms of the tractability function, $T$.}
 {\small
@@
 		\toprule
-		\text{\peter{algebraic strong polynomial}} & \max(1,\varepsilon^{-p}) & 1\\
-		\text{\peter{algebraic polynomial}} & \max(1,\varepsilon^{-p})d^{q} & d^{q}\\
-		\text{\peter{exponential strong polynomial}} &  [\max(1,\log(1 + \varepsilon^{-1})]^p & 1\\
+		\text{\peter{algebraic strong polynomial}} & \max\{1,\varepsilon^{-p}\} & 1\\
+		\text{\peter{algebraic polynomial}} & \max\{1,\varepsilon^{-p}\}d^{q} & d^{q}\\
+		\text{\peter{exponential strong polynomial}} &  [\max\{1,\log(1 + \varepsilon^{-1}\}]^p & 1\\
 		\text{\peter{exponential polynomial}} &
-		[\max(1,\log(1 + \varepsilon^{-1}))]^p  d^{q} & d^{q} \\
+		[\max\{1,\log(1 + \varepsilon^{-1})\}]^p  d^{q} & d^{q} \\
         \text{\peter{algebraic quasi-polynomial}} &
-        \exp\{p(1+\log(\max(1,\varepsilon^{-1}))(1+\log(d))\} &
+        \exp\{p(1+\log(\max\{1,\log(1 + \varepsilon^{-1})\})(1+\log(d))\} &
         \exp\{p(1+\log(d))\}\\
@@
 \end{table}
-
-\begin{definition}
-    A problem is defined as $T$-tractable with parameter $\vp$ iff there exists a positive constant $C_{\vp}$, which is independent of $\varepsilon$ and $d$, such that
-\begin{equation} \label{eq:tract_def}
-	\comp(\varepsilon,d) \le C_{\vp}\, T(\varepsilon^{-1},d,\vp) \qquad \forall \varepsilon >0, \ d \in \mathbb{N}.
-\end{equation}
-A problem is \emph{strongly}
-$T$-tractable with parameter $\vp$ iff the \peter{information} complexity is independent of the dimension of the problem, that is, there exists a positive constant $C_{\vp}$, again independent of $\varepsilon$ and $d$, such that
-\begin{equation} \label{eq:strong_tract_def}
-	\comp(\varepsilon,d) \le C_{\vp}\, T(\varepsilon^{-1},1,\vp) \qquad \forall \varepsilon >0 , \ d \in \mathbb{N}.
-\end{equation}
-We allow $\vp$ to be a scalar or vector as the situation dictates.
-\end{definition}
-
-For this definition of tractability to make sense we assume that
-\begin{subequations} \label{eq:Tconditions}
-\begin{equation} \label{eq:Tnondecreasing}
-	T \text{ is non-decreasing in all variables,}
-\end{equation}
-which implies that the problem is expected to be no easier by decreasing the tolerance, $\varepsilon$, or increasing the dimension, $d$.
-(This is why we make $T$ a function of $\varepsilon^{-1}$ rather than of $\varepsilon$.) Furthermore, increasing $\vp$ does not decrease $T(\cdot, \cdot, \vp)$.
-Since there are an infinite number of positive eigenvalues, it also makes sense to assume that
-\begin{equation}\label{eq:Tlim}
-	\lim_{\varepsilon \to 0} T(\varepsilon^{-1},d,\vp) = \infty \qquad \forall d \in \naturals, \ \vp \in [0,\infty)^s.
-\end{equation}
-Since $T(\cdot,d,\vp)$ is non-decreasing, we may define the following limit, which we assume will always be positive:
-\begin{equation}\label{eq:T0}	T(0,d,\vp):=\lim_{\varepsilon\to\infty}T(\varepsilon^{-1},d,\vp) = \inf_\varepsilon T(\varepsilon^{-1},d,\vp) \ge T(0,1,\vzero) > 0.
-\end{equation}
-\end{subequations}
-Finally, there is a technical assumption required for our analysis.  There exists a $K_{\vp,\tau}$ depending on $\vp$ and $\tau$, but  independent of $\varepsilon$ and $d$, such that
-\begin{equation} \label{eq:ptauassume}
-	[T(\varepsilon^{-1},d,\vp)]^\tau \le K_{\vp,\tau} T(\varepsilon^{-1},d,\tau \vp),   \quad \forall \varepsilon \in (0,\infty), \ d \in \naturals, \ \vp\in[0,\infty)^s, \ \tau\in [1,\infty).
-\end{equation}
-
-Certain common notions of tractability  covered by the general situation described above are provided in Table \ref{tab:commonT}.
-Here, $\vp = (p,q)$ in some cases and $\vp$ is a scalar in other cases.
-A general reference
-for results on algebraic tractability is \cite{NovWoz08a}, for exponential tractability we refer to \cite{HicKriWoz19a} and \cite{KriWoz19a}.
 
@@
 
-We first consider the simpler case when the \peter{information} complexity is essentially independent of the dimension, $d$.
+We first consider the simpler case when the information complexity is essentially independent of the dimension, $d$.
 The proof also introduces the line of argument used for the case where there is $d$-dependence.
@@
 
-For $\varepsilon$ taking on all positive values, $i(\varepsilon,\vp)$ takes on, \peter{by \eqref{eq:Tlim},} all values greater than or equal to $i(\infty,\vp)$, so
+For $\varepsilon$ taking on all positive values, $i(\varepsilon,\vp)$ takes on, by \eqref{eq:Tlim}, all values greater than or equal to $i(\infty,\vp)$, so
 \[
@@
 \]
-This implies via our technical assumption \eqref{eq:ptauassume} that, \peter{for any $\tau>1$,}
+This implies via our technical assumption \eqref{eq:ptauassume} that, for any $\tau>1$,
 \begin{gather*}
@@
 
-For $\varepsilon$ taking on all positive values, $i(\varepsilon,d,\vp)$ takes on, \peter{by \eqref{eq:Tlim},} all values greater than or equal to $i(\infty,d,\vp)$, so
+For $\varepsilon$ taking on all positive values, $i(\varepsilon,d,\vp)$ takes on, by \eqref{eq:Tlim}, all values greater than or equal to $i(\infty,d,\vp)$, so
 \[
@@
 
-The \peter{concept of} (strong) polynomial tractability for both the algebraic case and the exponential case will be first considered as follows:
-
-\begin{example}[\peter{Algebraic strong} polynomial tractability]
+The concept of (strong) polynomial tractability for both the algebraic case and the exponential case will be first considered as follows:
+
+\begin{example}[Algebraic strong polynomial tractability]
 
@@
 \[
- T(\varepsilon^{-1},d,\vp)= \max\{1,\varepsilon^{-\peter{\vp}}\}
+ T(\varepsilon^{-1},d,\vp)= \max\{1,\varepsilon^{-\vp}\}
  \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty),
 \]
-where in this case \peter{$\vp=p$} is a scalar.
-Then Theorem \ref{thm_main_strong_tract2} yields the  equivalent condition for \peter{algebraic strong polynomial tractability}:
+where in this case $\vp=p$ is a scalar.
+Then Theorem \ref{thm_main_strong_tract2} yields the  equivalent condition for algebraic strong polynomial tractability:
 \[
@@
 \[
- T(\varepsilon^{-1},d,\vp)= \max\{1,\varepsilon^{-\peter{\vp}}\}\, d^q
+ T(\varepsilon^{-1},d,\vp)= \max\{1,\varepsilon^{-\vp}\}\, d^q
  \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty)^2,
@@
 
-\begin{example}[\peter{Exponential strong} polynomial tractability]
+\begin{example}[Exponential strong polynomial tractability]
 Let the tractability function, $T$,
@@
 \[
- T(\varepsilon^{-1},d,\vp)= [\max\{1,\log(1+\varepsilon^{-1})\}]^{\peter{\vp}}, \quad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty),
-\]
-where \peter{$\vp=p$} is a scalar. Then Theorem \ref{thm_main_strong_tract2} yields the equivalent condition for \peter{exponential strong polynomial tractability:} 
+ T(\varepsilon^{-1},d,\vp)= [\max\{1,\log(1+\varepsilon^{-1})\}]^{\vp}, \quad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty),
+\]
+where $\vp=p$ is a scalar. Then Theorem \ref{thm_main_strong_tract2} yields the equivalent condition for exponential strong polynomial tractability:
 \begin{equation}\label{eq:exp_spt}
@@
 \] where in this case $\vp = p$ is a scalar.
-Furthermore, we assume the following, \peter{which corresponds to the conditions} in \eqref{eq:Tlim}, \eqref{eq:T0}, and \eqref{eq:ptauassume}. We assume that
+Furthermore, we assume the following, which corresponds to the conditions in \eqref{eq:Tlim}, \eqref{eq:T0}, and \eqref{eq:ptauassume}. We assume that
 \[
@@
 \[
-\lim_{\varepsilon \rightarrow \infty}\phi(\varepsilon^{-1},p) \peter{>0.}
+\lim_{\varepsilon \rightarrow \infty}\phi(\varepsilon^{-1},p) >0.
 \]
@@
 \end{equation*}
-for some $p>0$ and $L_p \in \naturals$. Furthermore, the optimal $p$ is also the infimum of all $p$ \peter{satisfying the latter condition}.
+for some $p>0$ and $L_p \in \naturals$. Furthermore, the optimal $p$ is also the infimum of all $p$ satisfying the latter condition.
 Theorem \ref{thm_main_tract2} yields the following equivalent condition for separable tractability:
@@
  \sup_{d \in \naturals} \frac{1}{\psi(d,q)} \sum_{i = \lceil L_{(p,q)}\psi(d,q)\rceil}^\infty \frac{1}{\phi(\lambda_{i, d}^{-1},p)} < \infty,
-\] for some $p,q >0$ and \peter{a positive constant $L_{(p,q)}$}.
+\] for some $p,q >0$ and a positive constant $L_{(p,q)}$.
 \end{example}
@@
 	\iff
-	 \sup_{d\in\naturals}  \, \sum_{i=1}^\infty \exp(-c\, (\min(1,\lambda_{i,d})^{s} + d^t )) <\infty \qquad \forall c > 0.
+	 \sup_{d\in\naturals}  \, \sum_{i=1}^\infty \exp(-c\, (\min\{1,\lambda_{i,d}\}^{s} + d^t )) <\infty \qquad \forall c > 0.
 	\]
@@
 \end{equation}
-Also, for each $d \in \naturals$ define the \peter{set}
+Also, for each $d \in \naturals$ define the set
 \begin{equation} \label{eq:hIdef}
@@
 
-Now we take this upper bound further, specializing to the case of $\thed=1$ and $N = \min(L_{\vp},\theUB(d))$:
+Now we take this upper bound further, specializing to the case of $\thed=1$ and $N = \min\{L_{\vp},\theUB(d)\}$:
 \begin{align*}
        \comp(\varepsilon,d)
-       & \le T(\varepsilon^{-1},1, \vp) \Biggl [ \frac{\min(L_{\vp},\theUB(d))}{T(\varepsilon^{-1},1, \vp)}  + \underbrace{\sum_{i = \min(L_{\vp},\theUB(d))}^{\theUB(d)} \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}}_{\le S_{\vp} + 1/ T(\lambda_{\theUB(d), d}^{-1},1,\vp) \text{ by \eqref{eq:strong_rest_tractiff}} }
+       & \le T(\varepsilon^{-1},1, \vp) \Biggl [ \frac{\min\{L_{\vp},\theUB(d)\}}{T(\varepsilon^{-1},1, \vp)}  + \underbrace{\sum_{i = \min\{L_{\vp},\theUB(d)\}}^{\theUB(d)} \frac{1}{T(\lambda_{i, d}^{-1},1,\vp)}}_{\le S_{\vp} + 1/ T(\lambda_{\theUB(d), d}^{-1},1,\vp) \text{ by \eqref{eq:strong_rest_tractiff}} }
         \Biggr] \\
@@
 \]
-Thus, it follows by \peter{\eqref{eq:lambda_K_strong4}} that $\lambda_{i(\varepsilon,\vp),d} \le \varepsilon$
+Thus, it follows by \eqref{eq:lambda_K_strong4} that $\lambda_{i(\varepsilon,\vp),d} \le \varepsilon$
 for any  $(\varepsilon^{-1}, d) \in \Omega$.
@@
 
-For the case $\theUB(d)> 0$, we utilize \peter{the} upper bound \eqref{eq:compUP_rest}, specializing to the case of $\thed=d$ and $N = \min\left(\lceil L_{\vp}\, T(0,d,\vp)\rceil,\theUB(d)\right)$:
+For the case $\theUB(d)> 0$, we utilize the upper bound \eqref{eq:compUP_rest}, specializing to the case of $\thed=d$ and $N = \min\left\{\right\}\lceil L_{\vp}\, T(0,d,\vp)\rceil,\theUB(d)\right\}$:
 \begin{align*}
        \comp(\varepsilon,d)
-       & \le T(\varepsilon^{-1},d, \vp) \Biggl [ \frac{\min\left(\lceil L_{\vp}\, T(0,d,\vp)\rceil,\theUB(d)\right)}{T(\varepsilon^{-1},d, \vp)}  + \underbrace{\sum_{i = \min\left(\lceil L_{\vp}\, T(0,d,\vp)\rceil,\theUB(d)\right)}^{\theUB(d)} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}}_{\le S_{\vp} + 1/ T(\lambda_{\theUB(d), d}^{-1},d,\vp) \text{ by \eqref{eq:strong_rest_tractiff}} }
+       & \le T(\varepsilon^{-1},d, \vp) \Biggl [ \frac{\min\left{}\lceil L_{\vp}\, T(0,d,\vp)\rceil,\theUB(d)\right\}}{T(\varepsilon^{-1},d, \vp)}  + \underbrace{\sum_{i = \min\left\{\lceil L_{\vp}\, T(0,d,\vp)\rceil,\theUB(d)\right\}}^{\theUB(d)} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}}_{\le S_{\vp} + 1/ T(\lambda_{\theUB(d), d}^{-1},d,\vp) \text{ by \eqref{eq:strong_rest_tractiff}} }
         \Biggr] \\
@@
 \intertext{and note that }
- \max(i(\infty,d,\vp'),2) & \le i(\infty,d,\vp') +1  = \lfloor C_{\vp'}\, T(0,d,\vp')\rfloor +2 \le  \left[C_{\vp'} + \frac{2}{T(0,d,\vp')}   \right]\, T(0,d,\vp')\\
- & \peter{=}  L_{\vp'}\, T(0,d,\vp')
+ \max\{i(\infty,d,\vp'),2\} & \le i(\infty,d,\vp') +1  = \lfloor C_{\vp'}\, T(0,d,\vp')\rfloor +2 \le  \left[C_{\vp'} + \frac{2}{T(0,d,\vp')}   \right]\, T(0,d,\vp')\\
+ & =  L_{\vp'}\, T(0,d,\vp')
  \le \lceil L_{\vp'} T(0,d,\vp')\rceil .

### 2023-07-18 GeneralizedTractability2023July17.tex
Fred M2 2023 Mac Updates

@@
 %\usepackage[active]{srcltx}
-\usepackage{fdsymbol}
+%\usepackage{fdsymbol} %removing this package solves the problem with \mathcal{I} not showing up properly.
 \usepackage{enumitem}
@@
 
-%TODO: We should check consistency of notation when using $\max$ or $\min$. Sometimes we use ``$(\ldots)$'' for the argument, sometimes we use ``$\{\ldots\}$''  \fred{Fred will do this.}
-
 \bigskip
@@
 
-\kachi{We denote the set of positive integers by $\naturals$ and and the set of non-negative integers by $\naturals_0$.}
+We denote the set of positive integers by $\naturals$ and and the set of non-negative integers by $\naturals_0$.
 In Section \ref{sec:spt}, we give the definitions of the considered tractability notions, in particular (strong) tractability.
@@
 A problem is \emph{strongly}
-$T$-tractable with parameter $\vp$ iff the \peter{information} complexity is independent of the dimension of the problem, that is, there exists a positive constant $C_{\vp}$, again independent of $\varepsilon$ and $d$, such that
+$T$-tractable with parameter $\vp$ iff the information complexity is independent of the dimension of the problem, that is, there exists a positive constant $C_{\vp}$, again independent of $\varepsilon$ and $d$, such that
 \begin{equation} \label{eq:strong_tract_def}
@@
 which implies that the problem is expected to be no easier by decreasing the tolerance, $\varepsilon$, or increasing the dimension, $d$.
-(This is why we make $T$ a function of $\varepsilon^{-1}$ rather than of $\varepsilon$.) Furthermore, increasing $\vp$ does not decrease $T(\cdot, \cdot, \vp)$.
+(This is why we make $T$ a function of $\varepsilon^{-1}$ rather than of $\varepsilon$.) Furthermore, increasing $\vp$ allows for a possibly looser bound on the information complexity.
 Since there are an infinite number of positive eigenvalues, it also makes sense to assume that
@@
 Certain common notions of tractability  covered by the general situation described above are provided in Table \ref{tab:commonT}.
-Here, $\vp = (p,q)$ in some cases and $\vp$ is a scalar in other cases.
+Here, $\vp = (p,q)$ in some cases, and $\vp$ is a scalar in other cases.
 A general reference
-for results on algebraic tractability is \cite{NovWoz08a}, for exponential tractability we refer to \cite{HicKriWoz19a} and \cite{KriWoz19a}.
+for results on algebraic tractability is \cite{NovWoz08a}.  For exponential tractability we refer to \cite{HicKriWoz19a} and \cite{KriWoz19a}.
 
@@
 		\toprule
-		\text{\peter{algebraic strong polynomial}} & \max\{1,\varepsilon^{-p}\} & 1\\
-		\text{\peter{algebraic polynomial}} & \max\{1,\varepsilon^{-p}\}d^{q} & d^{q}\\
-		\text{\peter{exponential strong polynomial}} &  [\max\{1,\log(1 + \varepsilon^{-1}\}]^p & 1\\
-		\text{\peter{exponential polynomial}} &
+		\text{algebraic strong polynomial} & \max\{1,\varepsilon^{-p}\} & 1\\
+		\text{algebraic polynomial} & \max\{1,\varepsilon^{-p}\}d^{q} & d^{q}\\
+		\text{exponential strong polynomial} &  [\max\{1,\log(1 + \varepsilon^{-1}\}]^p & 1\\
+		\text{exponential polynomial} &
 		[\max\{1,\log(1 + \varepsilon^{-1})\}]^p  d^{q} & d^{q} \\
-        \text{\peter{algebraic quasi-polynomial}} &
+        \text{algebraic quasi-polynomial} &
         \exp\{p(1+\log(\max\{1,\log(1 + \varepsilon^{-1})\})(1+\log(d))\} &
         \exp\{p(1+\log(d))\}\\
-        \text{\peter{exponential quasi-polynomial}} &
+        \text{exponential quasi-polynomial} &
         \exp\{p(1+\log(\max\{1,\log(1+\varepsilon^{-1})\}))(1+\log(d))\} &
@@
 \textbf{Sufficient condition:}\newline
-We make the first part of the argument in some generality so that it can be reused in the proof of Theorem \ref{thm_main_tract2} for tractability.  Fix any $\varepsilon > 0$ and any $d \in \naturals$.
-\kachi{[KACHI: It seems the notation of the dimension has change from $d$ to $\delta$. I will work on this.]}
-Since the $\lambda_{i,d}$ are non-increasing in $i$, it follows that the $T(\lambda_{i,d}^{-1},\thed,\vp)$ are non-decreasing in $i$ for any $\thed\in\naturals$.
-In particular, for  any $N\in\naturals$ with $n\ge N$, we have
+We make the first part of the argument in some generality so that it can be reused in the proof of Theorem \ref{thm_main_tract2} for tractability.
+Fix any $\varepsilon > 0$ and any $d \in \naturals$, and let $\thed \in \naturals$ be arbitrary.
+%\delta replaced d'
+Since the $\lambda_{i,d}$ are non-increasing in $i$, it follows that the $T(\lambda_{i,d}^{-1},\thed,\vp)$ are non-decreasing in $i$. In particular, for  any $N\in\naturals$ with $n\ge N$, we have
 \begin{align*}
@@
 The argument proving equivalent conditions for tractability is similar to, but somewhat more involved than the proof of Theorem \ref{thm_main_strong_tract2}.
-Moreover, the specification of the set of optimal parameters is not as precise as in Theorem \ref{thm_main_strong_tract2} \peter{[Is the latter sentence still true?]}.
+The lower limit on the sum is somewhat more complicated as well.
 
@@
 Suppose now that $i\ge \lceil C d^{\tau_3}\rceil$ but $i\not\in B_d$, which means that
-\[\lambda_{i,d}^{i^{-\tau_2}} \le \frac{1}{e} \Leftrightarrow \log (\lambda_{i,d}^{-1})\ge i^{\tau_2}.\]
+\[\lambda_{i,d}^{i^{-\tau_2}} \le \frac{1}{e} \iff \log (\lambda_{i,d}^{-1})\ge i^{\tau_2}.\]
 Now, choose $p> 1/\tau_2$, $q=\max\{\tau_1,\tau_3\}$, and $L_{(p,q)}=\max\{C, e\, M\}$, which implies that $\lceil L_{(p,q)} d^{q}\rceil \ge e\, M\, d^{\tau_1}$. Then, for any $d\in\naturals$,
-\begin{eqnarray*}
-d^{-q} \sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p}&=&d^{-q} \sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\in B_d}}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p}\\
-&& + d^{-q} \sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\not\in B_d}}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p}\\
-&\le& d^{-q} e\, M\, d^{\tau_1} + d^{-q}\sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\not\in B_d}}^\infty \frac{1}{[\log (\lambda_{i,d}^{-1})]^p}\\
-&\le& e\, M + d^{-q}\sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\not\in B_d}}^\infty \frac{1}{i^{\tau_2 p}}\\
-&\le & e\, M + \zeta (\tau_2 p).
-\end{eqnarray*}
+\begin{align*}
+d^{-q} \sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p}&=d^{-q} \sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\in B_d}}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p}\\
+&\qquad  + d^{-q} \sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\not\in B_d}}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p}\\
+&\le d^{-q} e\, M\, d^{\tau_1} + d^{-q}\sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\not\in B_d}}^\infty \frac{1}{[\log (\lambda_{i,d}^{-1})]^p}\\
+&\le e\, M + d^{-q}\sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\not\in B_d}}^\infty \frac{1}{i^{\tau_2 p}}\\
+&\le  e\, M + \zeta (\tau_2 p).
+\end{align*}
 Since $p$ was chosen to be strictly larger than $1/\tau_2$, it follows that the latter expression is finite and its value is independent of $d$. Therefore, Condition \eqref{eq:exp_pt} holds.
@@
 \]  with non-decreasing functions $\hat{\phi} : (0,\infty) \to (0,\infty)$ and $\hat{\psi} : \naturals \to (0,\infty)$.
-We say that a problem is non-separable tractable with \peter{scalar} parameter $p$ iff there exists a positive $C_{p}$ such that
+We say that a problem is non-separable tractable with scalar parameter $p$ iff there exists a positive $C_{p}$ such that
 
@@
 \[
-\sup_{d\in\mathbb{N}}\sum_{\peter{i=\lceil L_p\,\hat{\phi}(0)^{p \, \hat{\psi}(d)}\rceil}} [\exp ( \hat{\phi}(\lambda_{i,d}^{-1}))]^{-p \, \hat{\psi}(d)}\quad \text{for some } p \geq 0, \peter{L_p >0}.
+\sup_{d\in\mathbb{N}}\sum_{i=\lceil L_p\,\hat{\phi}(0)^{p \, \hat{\psi}(d)}\rceil} [\exp ( \hat{\phi}(\lambda_{i,d}^{-1}))]^{-p \, \hat{\psi}(d)}\quad \text{for some } p \geq 0, L_p >0.
 \]
@@
 \[
-\sup_{d\in\mathbb{N}}\,d^{-p}\sum_{\peter{i=\lceil L_p\,d^{p}}\rceil} \left(\min\{1,\lambda_{i,d}\} \right)^{p(1+\log d)} < \infty \qquad \text{for some } p \geq 0, \peter{L_p >0}.\]
+\sup_{d\in\mathbb{N}}\,d^{-p}\sum_{i=\lceil L_p\,d^{p}\rceil} \left(\min\{1,\lambda_{i,d}\} \right)^{p(1+\log d)} < \infty \qquad \text{for some } p \geq 0, L_p >0.\]
 \end{example}
-\peter{This essentially recovers \cite[Theorem 23.1]{NovWoz12a}.
-}
+This essentially recovers \cite[Theorem 23.1]{NovWoz12a}.
+
 Next, we will consider the exponential case as follows.
@@
 \[
-\sup_{d\in\mathbb{N}}\,d^{-p}\sum_{\peter{i=\lceil L_p\,d^{p}\rceil}} \frac{1}{\left(\max\{1,\log(1+\lambda_{i,d}^{-1})\} \right)^{p(1+\log d)}}< \infty \quad \text{for some } p \geq 0, \peter{L_p >0}.
-\]
-\peter{This essentially recovers \cite[Theorem 2]{KriWoz19a}.
-}
+\sup_{d\in\mathbb{N}}\,d^{-p}\sum_{i=\lceil L_p\,d^{p}\rceil} \frac{1}{\left(\max\{1,\log(1+\lambda_{i,d}^{-1})\} \right)^{p(1+\log d)}}< \infty \quad \text{for some } p \geq 0, L_p >0.
+\]
+This essentially recovers \cite[Theorem 2]{KriWoz19a}.
 \end{example}
@@
 \section{Sub-$h$ Tractability}\label{sec:subh}
-In this section we generalize the concept of weak tractability \peter{(see again \cite{NovWoz08a}--\cite{NovWoz12a})}.  Let  $h:[0,\infty) \to [1,\infty)$ satisfy
+In this section we generalize the concept of weak tractability (see again \cite{NovWoz08a}--\cite{NovWoz12a}).  Let  $h:[0,\infty) \to [1,\infty)$ satisfy
 \begin{equation} \label{eq:h_cond}
@@
 Furthermore, let us denote the inverse function of $h$ by $h^{-1}$.
-Then, for arbitrary $z,w \in [1,\infty)$ we choose $x=h^{-1}(z)$ and $y=h^{-1}(w)$, to obtain \peter{from \eqref{eq:h_cond}}
+Then, for arbitrary $z,w \in [1,\infty)$ we choose $x=h^{-1}(z)$ and $y=h^{-1}(w)$, to obtain from \eqref{eq:h_cond}
 \[
@@
 or equivalently
-\[
+\begin{equation} \label{eq:Sclb}
 	n\le S_c \, h(cT(\lambda_{n,d}^{-1},d))   \qquad \forall n,d \in \naturals.
-\]
+\end{equation}
 This implies that for the special choice
@@
 S_c \, h(cT(\varepsilon^{-1},d))
-\right\rceil \le   \lceil \underbrace{
-S_c \, h(cT(0,1))}_{=: \widetilde{S}_c/2} \, h(cT(\varepsilon^{-1},d))
+\right\rceil \le   \lceil
+S_c \, h(cT(\lambda_{1,1}^{-1},1)) \, h(cT(\varepsilon^{-1},d))
 \rceil\qquad \forall c, \varepsilon > 0, \, d \in \naturals.
 \]
-
-Since $S_c \ge 1/h(cT(0,1))$ by definition \peter{[PETER: why do we know this?
-Could it be that we need to replace $T(0,1)$ by $T(\lambda_{1,1}^{-1},1)$?]}, it follows that $S_c \, h(cT(0,1)) \, h(cT(\varepsilon^{-1},d))  \ge 1$ and so
-\begin{align*}
+because $h$ is no smaller than $1$.
+
+Since $S_c \ge 1/h(cT(\lambda_{1,1}^{-1},1))$ by \eqref{eq:Sclb}, it follows that $S_c \, h(cT(0,1)) \, h(cT(\varepsilon^{-1},d))  \ge 1$.
+Define $\widetilde{S} : = 2 S_c \, h(cT(\lambda_{1,1}^{-1},1))$, and note that $\widetilde{S}_c$ must also be finite for all $c > 0$.
+It follows that
+\begin{equation*}
 \max(1,\comp(\varepsilon,d))
-& \le  \lceil  S_c \, h(cT(0,1)) \, h(cT(\varepsilon^{-1},d))   \rceil
- =  \lceil
+ \le \lceil
 (\widetilde{S}_c/2) \, h(cT(\varepsilon^{-1},d))
-\rceil \\
-& \le   \widetilde{S}_c \, h(cT(\varepsilon^{-1},d))
+\rceil  \le   \widetilde{S}_c \, h(cT(\varepsilon^{-1},d))
 \qquad\forall c, \varepsilon > 0, \, d \in \naturals.
-\end{align*}
+\end{equation*}
 Since $h$ is strictly increasing, so is $h^{-1}$, and thus by \eqref{eq:submult_h_inverse},
@@
 \\
-&  \le  h^{-1} (2 S_c) + cT (\varepsilon^{-1},d),
+&  \le  h^{-1}  (\widetilde{S}_c) + cT (\varepsilon^{-1},d),
 \quad \forall c, \varepsilon > 0, \, d \in \naturals.
@@
 
-The finiteness of $S_c$ implies that $\lim_{\varepsilon \to 0} T(\varepsilon^{-1},d) = \infty$ for all $d \in \naturals$.
-Together with  the hypothesis on $\lim_{d \to \infty} T(\varepsilon^{-1},d)$ in \eqref{eq:h_cond}
-\peter{[PETER: Is the reference to \eqref{eq:h_cond} correct?]}, it follows that $\lim_{\varepsilon^{-1} + d \to \infty} T(\varepsilon^{-1},d) = \infty$.  Therefore
+Since $\lim_{\varepsilon \to 0} T(\varepsilon^{-1},d) = \infty$ for all $d \in \naturals$ by \eqref{eq:Tlim}, and  $\lim_{d \to \infty} T(\varepsilon^{-1},d) = \infty$ by the hypothesis of this theorem, it follows that $\lim_{\varepsilon^{-1} + d \to \infty} T(\varepsilon^{-1},d) = \infty$.
+Therefore
 \begin{equation*}
@@
 \begin{equation} \label{eq:hIdef}
-\mathcal{I}_d :=\begin{cases}
+\hI = \mathcal{I}_d :=\begin{cases}
 \emptyset, & \theUB(d) = 0, \\

### 2023-07-18 GeneralizedTractability2023July17.tex
Fred M2 2023 Mac Updates

@@
 
-\title{A Unified Treatment of Tractability of Approximation Problems Defined on Hilbert Spaces}
+\title{A Unified Treatment of Tractability for Approximation Problems Defined on Hilbert Spaces}
 
@@
 
-Define
-\[
+For all positive $\varepsilon$, define
+\begin{equation}\label{eq:iepsp}
 i(\varepsilon,\vp):= \lfloor C_{\vp}\, T(\varepsilon^{-1},1,\vp)\rfloor +1, \quad
 i(\infty,\vp) =\lfloor C_{\vp}\, T(0,1,\vp)\rfloor +1.
-\]
+\end{equation}
 Thus, it follows by \eqref{eq:lambda_K_strong3} that $\lambda_{i(\varepsilon,\vp),d} \le \varepsilon$.
@@
 
-For a fixed $c$ and $d$, define
-\begin{equation} \label{eq:nstardef}
-	\varepsilon^{-1}_{\max}(d,c) := \max(V_c - d,\lambda_{\max}^{-1}), \qquad n^*(d,c) : = n(\varepsilon^{-1}_{\max}(d,c),d,c) \le h(cT(\varepsilon^{-1}_{\max}(d,c),d)) +1.
-\end{equation}
-\peter{[PETER: We do not have $\lambda_{\max}$ anymore, and it could be unbounded, right?
-But I think this can be fixed: I keep the black (current) version, and provide a purple (new) version below, with only few changes.
-Please check carefully whether we can use the purple one.]}
-By varying $\varepsilon^{-1}$ in the interval $[\varepsilon^{-1}_{\max}(d,c),\infty)$,  the integer $n(\varepsilon,d,c)$ attains, \peter{by Assumption \eqref{eq:Tlim},} all values greater than or equal to $n^*(d,c)$.
-Thus, by \eqref{eq:nedcbound},
-\begin{align}
-		n &\le h(cT(\lambda^{-1}_{n,d},d)) \qquad  \forall n \ge n^*(d,c), \label{eq:subhTneq}\\
-		\nonumber
-		\frac{1}{h(2 cT(\lambda^{-1}_{n,d},d)) } & \le \frac{1}{[h(cT(\lambda^{-1}_{n,d},d))]^{2}}  \le \frac 1{n^2}   \qquad  \forall n \ge n^*(d,c) \qquad \text{by \eqref{eq:h_cond}}. \\
-		\intertext{Combining this inequality with the upper bound on $n^*(d,c)$ yields}
-		\nonumber
-		S_{2c} & =\sup_{d\in\naturals}  \, \sum_{i=1}^\infty \frac1{h(2cT(\lambda_{i,d}^{-1},d))} \\
-		\nonumber
-		&  = \sup_{d\in\naturals} \left [
-		\sum_{i=1}^{n^*(d,c)-1} \frac1{h(2cT(\lambda_{i,d}^{-1},d))}
-		+ \sum_{i=n^*(d,c)}^\infty \frac1{h(2cT(\lambda_{i,d}^{-1},d))}
-		\right]\\
-		 \nonumber
-		 & \le \sup_{d\in\naturals} \left [
-\frac{n^*(d,c)-1}{h(2cT(\lambda_{\max}^{-1},d))}
-+ \sum_{i=1}^\infty \frac1{n^2}
-\right]
- \qquad \text{by \eqref{eq:subhTneq}}\\
- \label{eq:lastone}
-		 & \le \sup_{d\in\naturals} \left [
-		 \frac{ h(cT(\varepsilon^{-1}_{\max}(d,c),d))}{h(2cT(\lambda_{\max}^{-1},d))}
-		\right] + \frac{\pi^2}{6}
-		\qquad \text{by \eqref{eq:nstardef}.}
-\end{align}
-
-Note that
-\[
-\varepsilon^{-1}_{\max}(d,c) = \max(V_c - d,\lambda_{\max}^{-1})
-= \begin{cases} V_c - d \le V_c, & d \in \{1, \ldots, d^*_c : = \lfloor V_c - \lambda_{\max}^{-1} \rfloor\}, \\
-\lambda_{\max}^{-1}, & d \in \{d^*_c+1, \ldots\}.
-\end{cases}
-\]
-Recalling that $T$ is non-decreasing in its arguments, this implies that
-\begin{align*}
-    \MoveEqLeft{\sup_{d\in\naturals} \,
-		 \frac{ h(cT(\varepsilon^{-1}_{\max}(d,c),d))}{h(2cT(\lambda_{\max}^{-1},d))}}\\
-  &\le \max \left \{
-  \sup_{d \in \{1, \ldots, d^*_c\}} \,
-		 \frac{ h(cT(\varepsilon^{-1}_{\max}(d,c),d))}{h(2cT(\lambda_{\max}^{-1},d))},
-  \sup_{d\in \{d^*_c+1, \ldots \}} \,
-		 \frac{ h(cT(\varepsilon^{-1}_{\max}(d,c),d))}{h(2cT(\lambda_{\max}^{-1},d))}
-  \right \} \\
-  & \le \max \left \{
-  \sup_{d \in \{1, \ldots, d^*_c\}}  \,
-		 \frac{ h(cT(V_c,d))}{h(2cT(\lambda_{\max}^{-1},d))}
-  ,
-  \sup_{d\in \{d^*_c+1, \ldots \}}  \,
-		 \frac{ h(cT(\lambda_{\max}^{-1},d))}{h(2cT(\lambda_{\max}^{-1},d))}
-  \right \}
-  \\
-  & \le \max \left \{
-		 \frac{ h(cT(V_c,d^*_c))}{h(2cT(\lambda_{\max}^{-1},1))},
-  \sup_{d\in \{d^*_c+1, \ldots \}}  \,
-		 \frac{ h(cT(\lambda_{\max}^{-1},d))}{[h(cT(\lambda_{\max}^{-1},d))]^2}
-  \right \} \\
-  & = \max \left \{
-		 \frac{ h(cT(V_c,d^*_c))}{h(2cT(\lambda_{\max}^{-1},1))},
-		 \frac{1}{h(cT(\lambda_{\max}^{-1},d_c^*+1))}
-  \right \} \\
-  & < \infty.
-\end{align*}
-Combining this bound with the upper bound on $S_c$ in \eqref{eq:lastone} establishes the finiteness of $S_{2c}$ and completes the proof of the necessary condition.
-This concludes the proof of Theorem \ref{thm:subhT}.
-
-\bigskip
-
-\peter{***ALTERNATIVE VERSION OF THE LAST PART OF THE PROOF - PLEASE CHECK (essentially just by replacing $\lambda_{\max}$ by something different***}
-
-\bigskip
-
-\peter{
 For a fixed $c$ and $d$, define
@@
 = \begin{cases} V_c - d \le V_c, & d \in \{1, \ldots, d^*_c : = \lfloor V_c - \lambda_{1,d}^{-1} \rfloor\}, \\
-\lambda_{1,d}^{-1}, & d \in \{d^*_c+1, \ldots\}.
+\lambda_{1,d}^{-1}, & d \in \{d^*_c+1, \ldots\},
 \end{cases}
 \]
-Note that it follows from above that we always have $d^*_c\le \lfloor V_c \rfloor$
-
+and furthermore, it follows from above that we always have $d^*_c\le \lfloor V_c \rfloor$.
 Recalling that $T$ is non-decreasing in its arguments, this implies that
@@
 This concludes the proof of Theorem \ref{thm:subhT}.
-}
-
 \qed
@@
 	\]
-	The expression on the left is the notion of $(s,t)$-weak tractability \peter{introduced in \cite{SW15}}, and the condition on the right was derived in \peter{\cite[Theorem 3.1]{WW17}}.
+	The expression on the left is the notion of $(s,t)$-weak tractability introduced in \cite{SW15}, and the condition on the right was derived in \cite[Theorem 3.1]{WW17}.
 Weak tractability corresponds to $(s,t)=(1,1)$, and uniform weak tractability corresponds to the case when a problem is weakly tractable for all positive $s$ and $t$.
@@
 \begin{equation} \label{eq:hIdef}
-\hI = \mathcal{I}_d :=\begin{cases}
+\mathcal{I}_d :=\begin{cases}
 \emptyset, & \theUB(d) = 0, \\
@@
 \end{equation}
-\peter{[I have no idea why the $\mathcal{I}_d$ is not displayed correctly above.]}
+%\peter{[I have no idea why the $\mathcal{I}_d$ is not displayed correctly above.]}
 From the definition of $\theUB(d)$ it follows that $(\lambda_{i,d}^{-1},d) \in \Omega  \iff i \in \hI_d$, and
@@
 
-We note that it may be possible to define $\Omega$ such that $\lambda_{1,d} > \theM(d)$
-\peter{[should it not be $\lambda_{1,d} \le \theM(d)$ ?]}
+We note that it may be possible to define $\Omega$ such that  $\lambda_{1,d} \le \theM(d)$
 for all $d \in \naturals$.
@@
 Moreover, given that $T$ is increasing in its arguments, we have the following equivalent expression for the complexity via
-\eqref{eq:comp_def} \peter{[Again, no clue why the $\mathcal{I}_d$ is not displayed correctly below]}:
+\eqref{eq:comp_def}:
 \begin{align} %\label{eq:comp_equiv}
@@
 
-For $(\varepsilon^{-1}, d) \in \Omega$, define the positive integers
+For  all $\varepsilon > 0$, define the positive integers
 \[
 i(\varepsilon,\vp):= \lfloor C_{\vp}\, T(\varepsilon^{-1},1,\vp)\rfloor +1, \quad
-i(\infty,\vp) =  \lfloor C_{\vp}\, T(0,1,\vp)\rfloor +1 \ge 1 .
-\]
-Thus, it follows by \eqref{eq:lambda_K_strong4} that $\lambda_{i(\varepsilon,\vp),d} \le \varepsilon$
-for any  $(\varepsilon^{-1}, d) \in \Omega$.
+i(\infty,\vp) =  \lfloor C_{\vp}\, T(0,1,\vp)\rfloor +1 \ge 1,
+\]
+just as in \eqref{eq:iepsp}.
+Thus, it follows by \eqref{eq:lambda_K_strong4} that
+\begin{equation} \label{eq:lambdaiep}
+\lambda_{i(\varepsilon,\vp),d} \le \varepsilon \qquad
+ \forall (\varepsilon^{-1}, d) \in \Omega.
+\end{equation}
 Note furthermore that we always have
@@
 \[
-I_{d,\vp}:=\begin{cases}
-\emptyset, & i(\theM(d),\vp) = i(\infty,\vp) \\
+\mathscr{I}_{d,\vp}:=\begin{cases}
+\emptyset, & i(\theM(d),\vp) = i(\infty,\vp), \\
 \{i(\infty,\vp),\ldots, i(\theM(d),\vp)-1\}, & \theM(d) > 0, \\
@@
 \[
-i\le  C_{\vp} T(\lambda_{i,d}^{-1},1,\vp)+1, \qquad \forall i\in I_{d,\vp},  \ d \in \naturals.
+i\le  C_{\vp} T(\lambda_{i,d}^{-1},1,\vp)+1, \qquad \forall i\in \mathscr{I}_{d,\vp},  \ d \in \naturals.
 \]
@@
  \ge
-  \left[\frac{(i-1)}{C_{\vp}}\right]^\tau \qquad \forall i\in I_{d,\vp},  \ d \in \naturals, \\
+  \left[\frac{(i-1)}{C_{\vp}}\right]^\tau \qquad \forall i\in \mathscr{I}_{d,\vp},  \ d \in \naturals, \\
   \label{eq:rest_strong_ineq}
  \frac{1}{T (\lambda_{i,d}^{-1},1,\tau \vp)} \le
-\frac{K_{\vp,\tau}\, C_{\vp}^\tau}{(i-1)^\tau}\qquad \forall i \in I_{d,\vp} \setminus\{1\}, \ d \in \naturals .
+\frac{K_{\vp,\tau}\, C_{\vp}^\tau}{(i-1)^\tau}\qquad \forall i \in \mathscr{I}_{d,\vp} \setminus\{1\}, \ d \in \naturals .
 \end{gather}
@@
 
-\item If $\theUB(d) \ge L_{\tau\vp}$ and $\theM(d) = 0$, then $\{L_{\tau\vp},  L_{\tau\vp} + 1, \ldots \} \subseteq I_{d,\vp} \setminus \{1\}$.
-
-\item If $\theUB(d) \ge L_{\tau\vp}$ and $\theM(d) >0$, then \eqref{eq:Mddef} and \eqref{eq:lambda_K_strong4} imply that
-\[
-\lambda_{i(\theM(d),\vp),d} \le \lambda_{\theUB(d)+1,d} \le \theM(d) < \lambda_{\theUB(d),d}.
-\]
-\peter{
-[PETER. In the above chain of inequalities, I am not quite sure that I understand the first one. Is it because...
-\begin{itemize}
-    \item $\lambda_{i(\varepsilon,\vp),d)} \le \varepsilon$ for all $\varepsilon>\theM(d)$, and so it must also hold in the limit for $\varepsilon$ tending to $\theM(d)$, and
-    \item $\theUB (d) +1$ is the smallest index such that $\lambda_{\theUB (d) +1} \le \theM(d)$ ?
-\end{itemize}]
-
-}
-This means that $\theUB(d) \le i(\theM(d),\vp)-1$.  So, $\{L_{\tau\vp}, \ldots, \theUB(d)\} \subseteq I_{d,\vp} \setminus \{1\}$.
+\item If $\theUB(d) \ge L_{\tau\vp}$ and $\theM(d) = 0$, then $\{L_{\tau\vp},  L_{\tau\vp} + 1, \ldots \} \subseteq \mathscr{I}_{d,\vp} \setminus \{1\}$.
+
+\item If $\theUB(d) \ge L_{\tau\vp}$ and $\theM(d) >0$, then \eqref{eq:Mddef} implies that $\lambda_{\theUB(d)+1,d} \le \theM(d) < \lambda_{\theUB(d),d}$.
+Moreover, there must be some $\varepsilon^*$ satisfying $\theM(d) < \varepsilon^* < \lambda_{\theUB(d),d}$, such for which $\lambda_{i(\varepsilon^*,\vp)} \le \varepsilon^* < \lambda_{\theUB(d),d}$ by \eqref{eq:lambdaiep}.
+Because of the ordering of the singular values, this implies that  $i(\varepsilon^*,\vp) \ge \theUB(d)+1$.
+Since $i(\cdot,\vp)$ is nonincreasing, $i(\theM(b),\vp) \ge \theUB(d)+1$.
+This means that $\theUB(d) \le i(\theM(d),\vp)-1$.  So, $\{L_{\tau\vp}, \ldots, \theUB(d)\} \subseteq \mathscr{I}_{d,\vp} \setminus \{1\}$.
+
+\bigskip
 
@@
 \le
-\sup_{d\in\naturals} \sum_{i \in I_{d,\vp} \setminus\{1\} } \frac{1}{T (\lambda_{i,d}^{-1},1, \tau \vp)} \\
+\sup_{d\in\naturals} \sum_{i \in \mathscr{I}_{d,\vp} \setminus\{1\} } \frac{1}{T (\lambda_{i,d}^{-1},1, \tau \vp)} \\
 &  \le  K_{\vp,\tau}\, C_{\vp}^\tau
@@
 \[
-I_{d,\vp}:=\begin{cases}
+\mathscr{I}_{d,\vp}:=\begin{cases}
 \emptyset, & i(\theM(d),d,\vp) = i(\infty,d,\vp), \\
@@
 \[
-i\le  C_{\vp} T(\lambda_{i,d}^{-1},d,\vp)+1, \qquad \forall i\in I_{d},  \ d \in \naturals.
+i\le  C_{\vp} T(\lambda_{i,d}^{-1},d,\vp)+1, \qquad \forall i\in \mathscr{I}_{d},  \ d \in \naturals.
 \]
@@
  \ge
-  \left[\frac{(i-1)}{C_{\vp}}\right]^\tau, \qquad \forall i\in I_{d,\vp},  \ d \in \naturals, \\
+  \left[\frac{(i-1)}{C_{\vp}}\right]^\tau, \qquad \forall i\in \mathscr{I}_{d,\vp},  \ d \in \naturals, \\
   \label{eq:rest_ineq}
  \frac{1}{T (\lambda_{i,d}^{-1},d,\tau \vp)} \le
-\frac{K_{\vp,\tau}\, C_{\vp}^\tau}{(i-1)^\tau},\qquad \forall i \in I_{d,\vp} \setminus\{1\}, \ d \in \naturals .
+\frac{K_{\vp,\tau}\, C_{\vp}^\tau}{(i-1)^\tau},\qquad \forall i \in \mathscr{I}_{d,\vp} \setminus\{1\}, \ d \in \naturals .
 \end{gather}
@@
 
-\item If $\theUB(d) \ge \lceil L_{\vp'} T(0,d,\vp')\rceil$ and $\theM(d) = 0$, then $\{\lceil L_{\vp'} T(0,d,\vp')\rceil,  \lceil L_{\vp'} T(0,d,\vp')\rceil + 1, \ldots \} \subseteq I_{d,\vp} \setminus \{1\}$.
+\item If $\theUB(d) \ge \lceil L_{\vp'} T(0,d,\vp')\rceil$ and $\theM(d) = 0$, then $\{\lceil L_{\vp'} T(0,d,\vp')\rceil,  \lceil L_{\vp'} T(0,d,\vp')\rceil + 1, \ldots \} \subseteq \mathscr{I}_{d,\vp} \setminus \{1\}$.
 
@@
 \]
-\peter{[PETER: Here, I have the same question as in the previous proof.]}
-
-This means that $\theUB(d) \le i(\theM(d),d,\vp)-1$.  So, $\{ \lceil L_{\vp'} T(0,d,\vp')\rceil, \ldots, \theUB(d)\} \subseteq I_{d,\vp} \setminus \{1\}$.
+By the same argument as in the proof of strong tractability, $\theUB(d) \le i(\theM(d),d,\vp)-1$.
+So, $\{ \lceil L_{\vp'} T(0,d,\vp')\rceil, \ldots, \theUB(d)\} \subseteq \mathscr{I}_{d,\vp} \setminus \{1\}$.
+
+\bigskip
 

### 2023-07-18 GeneralizedTractability2023July17.tex
Updates from Overleaf

@@
 
-For the case $\theUB(d)> 0$, we utilize the upper bound \eqref{eq:compUP_rest}, specializing to the case of $\thed=d$ and $N = \min\left\{\right\}\lceil L_{\vp}\, T(0,d,\vp)\rceil,\theUB(d)\right\}$:
+For the case $\theUB(d)> 0$, we utilize the upper bound \eqref{eq:compUP_rest}, specializing to the case of $\thed=d$ and $N = \min\left\{\lceil L_{\vp}\, T(0,d,\vp)\rceil,\theUB(d)\right\}$:
 \begin{align*}
        \comp(\varepsilon,d)
-       & \le T(\varepsilon^{-1},d, \vp) \Biggl [ \frac{\min\left{}\lceil L_{\vp}\, T(0,d,\vp)\rceil,\theUB(d)\right\}}{T(\varepsilon^{-1},d, \vp)}  + \underbrace{\sum_{i = \min\left\{\lceil L_{\vp}\, T(0,d,\vp)\rceil,\theUB(d)\right\}}^{\theUB(d)} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}}_{\le S_{\vp} + 1/ T(\lambda_{\theUB(d), d}^{-1},d,\vp) \text{ by \eqref{eq:strong_rest_tractiff}} }
+       & \le T(\varepsilon^{-1},d, \vp) \Biggl [ \frac{\min\left\{\lceil L_{\vp}\, T(0,d,\vp)\rceil,\theUB(d)\right\}}{T(\varepsilon^{-1},d, \vp)}  + \underbrace{\sum_{i = \min\left\{\lceil L_{\vp}\, T(0,d,\vp)\rceil,\theUB(d)\right\}}^{\theUB(d)} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}}_{\le S_{\vp} + 1/ T(\lambda_{\theUB(d), d}^{-1},d,\vp) \text{ by \eqref{eq:strong_rest_tractiff}} }
         \Biggr] \\

### 2023-07-18 Older_versions/GeneralizedTractability_230607.tex
Updates from Overleaf

--- 2023-07-17 GeneralizedTractability_230607.tex
@@
 \kachi{[KACHI: It seems the notation of the dimension has change from $d$ to $\delta$. I will work on this.]}
-Since the $\lambda_{i,d}$ are non-increasing in $i$, it follows that the $T(\lambda_{i,d}^{-1},\thed,\vp)$ are non-decreasing in $i$ for any $\thed\in\naturals$.
+Since the $\lambda_{i,d}$ are non-increasing in $i$, it follows that the $T(\lambda_{i,d}^{-1},d,\vp)$ are non-decreasing in $i$ for any $\thed\in\naturals$.
 In particular, for  any $N\in\naturals$ with $n\ge N$, we have

### 2023-07-19 GeneralizedTractability2023July17.tex
Updates from Overleaf

@@
 \DeclareMathOperator*{\esssup}{ess\,sup}
+\DeclareMathOperator{\card}{card}
 
@@
     A large literature specifies conditions under which the information complexity for a sequence of numerical problems defined for dimensions $1, 2, \ldots$ grows at a moderate rate, i.e., the sequence of problems is \emph{tractable}.
-Here we focus on the situation where the space of available information consists of all linear functionals and the problems are defined as operator mappings between Hilbert spaces.
+Here, we focus on the situation where the space of available information consists of all linear functionals and the problems are defined as operator mappings between Hilbert spaces.
 We unify the proofs of known tractability results and generalize a number of existing results.
@@
 A problem is tractable if the information complexity does not grow too large as the dimension of the problem increases or the error threshold decreases.
-There are a number of tractability results for numerical problems beginning with \cite{W94a,W94b}, spawning numerous articles, and filling a series of three impressive volumes \cite{NovWoz08a,NovWoz10a,NovWoz12a}.
-The purpose of this article is to unify the many of these tractability results for approximation problems where all linear functional data is available.
-
-Let $\{\cf_d\}_{d \in \naturals}$ and $\{\cg_d\}_{d \in \naturals}$ be sequences of Hilbert spaces, and $\{\SOL_d : \cf_d \to \cg_d\}_{d \in \naturals}$ be a sequence of linear solution operators  with adjoints $\SOL_d^*$ such that $\SOL_d^*\SOL_d : \cf_d \to \cf_d$ has eigenvalues and orthonormal eigenvectors
+There are a number of tractability results for numerical problems, beginning in the 1990s with \cite{W94a,W94b}, spawning numerous articles since then, and filling a series of three impressive volumes \cite{NovWoz08a,NovWoz10a,NovWoz12a}.
+Research on tractability continues at a vigorous pace.
+This article aims to unify and generalize many existing tractability results for approximation problems where all linear functional data is available.
+
+Let $\{\cf_d\}_{d \in \naturals}$ and $\{\cg_d\}_{d \in \naturals}$ be sequences of Hilbert spaces, and let $\{\SOL_d : \cf_d \to \cg_d\}_{d \in \naturals}$ be a sequence of linear solution operators  with adjoints $\SOL_d^*$ such that $\SOL_d^*\SOL_d : \cf_d \to \cf_d$ has eigenvalues and orthonormal eigenvectors
 \begin{equation} \label{eq:eigenvalues}
@@
 
-The goal is to find a sequence of approximate solution operators, $\{\APP_d:\cb_d \times (0,\infty) \to \cg_d\}_{d \in \naturals}$ satisfying
+The goal is to find a sequence of approximate solution operators, $\{\APP_d:\cb_d \times (0,\infty) \to \cg_d\}_{d \in \naturals}$, defined on the unit ball of functions in $\cf_d$, denoted $\cb_d$, which  satisfy an absolute error criterion:
 \begin{equation}
     \label{eq:errcrit}
-    \norm[\cg_d]{\SOL_d(f) - \APP_d(f,\varepsilon)} \le \varepsilon \qquad \forall f \in \cb_d, \ \varepsilon \in (0,\infty),
-\end{equation}
-where $\cb_d$ is the unit ball in $\cf_d$ and $\APP_d(f,\varepsilon)$ is allowed to depend on arbitrary linear functionals.
-Note that we also allow adaptive information, i.e., the linear functionals may sequentially depend on each other.
-
-The information complexity of the problem $\SOL_d$ is given by the function $\comp:(0,\infty) \times \naturals \to \natzero$, where $\comp(\varepsilon,d)$ is the number of linear functionals required by the best admissible algorithm to satisfy the error criterion \eqref{eq:errcrit}.
+    \norm[\cg_d]{\SOL_d(f) - \APP_d(f,\varepsilon)} \le \varepsilon \qquad \forall f \in \cb_d, \ \varepsilon \in (0,\infty).
+\end{equation}
+Here, $\APP_d(f,\varepsilon)$ is allowed to depend on arbitrary linear functionals.  Note that we also allow adaptive information, i.e., the linear functionals may sequentially depend on each other.
+
+The information complexity of the problem $\SOL_d$ is given by the function 
+\[
+\comp:(0,\infty) \times \naturals \to \natzero, 
+\]
+where $\comp(\varepsilon,d)$ is the number of linear functionals required by the best admissible algorithm to satisfy the error criterion \eqref{eq:errcrit}.
 By definition, the complexity is non-decreasing  as $\varepsilon$ tends to zero.
-We also expect it to be non-decreasing as $d$ tends to infinity, since $d$ is typically the number of variables for the functions in $\cf_d$.
-
-For this case where arbitrary linear functionals are allowed, the optimal solution operator is
+We also expect it to be non-decreasing as $d$ tends to infinity since $d$ is typically the number of variables for the functions in $\cf_d$.
+
+For this case where arbitrary linear functionals are allowed, the optimal solution operator is known to be
 \[
@@
 The question of tractability is one of determining how fast the information complexity increases as $\varepsilon$ tends to zero and/or as $d$ tends to infinity.
-We want to bound the complexity in terms of a simple function, $T$, of $\varepsilon^{-1}$ and $d$ and identify simple conditions on the singular values that are equivalent to this bound holding.
-We would like to point out that generalized tractability specified by a function $T$ has been considered before in the literature.
-In particular, there are several papers by Gnewuch and Wo\'{z}niakowski (see \cite{GW06,GW08,GW09,GneWoz11a} ), and also \cite[Chapter 8]{NovWoz08a} is devoted to this topic.
-To our best knowledge, however, these references mainly focus on the special case of tensor product problems, which we do not do here, and the conditions for tractability derived there are mostly in terms of properties of the function $T$, and not in terms of sums of (functions of) the eigenvalues of a problem.
-Hence, we consider the present paper an addition to what is presently known on this subject.
+Although \eqref{eq:comp_def} has a relatively simple in form, its dependence on the ordering of the singular values means that it is not obvious what the behavior of $\comp(\varepsilon, d)$ is as $\varepsilon^{-1}$ and/or $d$ tend to infinity.
+
+We want to bound the information complexity in terms of a simple function, $T$, of $\varepsilon^{-1}$ and $d$ and identify conditions on the singular values that are easier to verify that are equivalent to this bound on the information complexity holding.
+We note that generalized tractability specified by a function $T$ has been considered before in the literature.
+In particular, there are several papers by Gnewuch and Wo\'{z}niakowski (see \cite{GW06,GW08,GW09,GneWoz11a}), and also \cite[Chapter 8]{NovWoz08a} is devoted to this topic.
+To our understanding, however, these references mainly focus on the special case of tensor product problems, a restriction we do not make.
+Moreover, the conditions for tractability derived there are mostly in terms of properties of the function $T$, and not in terms of sums of (functions of) the eigenvalues of a problem.
+Hence, the present paper an adds to what is presently known on this subject.
 
@@
 The conditions we require $T$ to satisfy are described in  Section \ref{sec:not}, however, the basic idea is that we define our approximation problem to be tractable if $\comp(\varepsilon, d) \le  C_{\vp}\, T(\varepsilon^{-1},d,\vp)$ for some constant, $C_{\vp}$, depending only on the parameter $\vp$.
-\kachi{The parameter $\vp$ is a $s$-dimensional vector, where $\vp \geq 0$ implies that each component of $\vp$ is nonnegative.} In practice, we expect $T(\varepsilon^{-1},d,\vp)$ to increase sub-exponentially  with increasing $\varepsilon^{-1}$ and/or $d$, however, most of our theorems do not require such an assumption.
-
-\Cref{thm_main_strong_tract2,thm_main_tract2,thm_main_rest_strong_tract,thm_main_rest_tract} all take the form
+The parameter $\vp$ is an $s$-dimensional vector, where $\vp \geq 0$ implies that each component of $\vp$ is nonnegative.
+In practice, we expect $T(\varepsilon^{-1},d,\vp)$ to increase sub-exponentially  with increasing $\varepsilon^{-1}$ and/or $d$, however, most of our theorems do not require such an assumption.
+
+\Cref{thm_main_strong_tract2,thm_main_tract2,thm_main_rest_strong_tract,thm_main_rest_tract} below all take the form
 \begin{multline}
@@
 \end{multline}
-\Cref{thm:subhT} is of similar, but not equivalent, form.
+The differences in these theorems of are in the choices of $\thed$, $\Omega$, $\theM$, and $\theUB$.
+Although some of these theorems are special cases of others, we prove each separately to allow the reader to become familiar with the arguments used as additional layers of complexity are added.
+\Cref{thm:subhT} has a somewhat different form than above.
 
@@
 \end{subequations}
-Finally, there is a technical assumption required for our analysis.  There exists a $K_{\vp,\tau}$ depending on $\vp$ and $\tau$, but  independent of $\varepsilon$ and $d$, such that
+Finally, there is a technical assumption required for our analysis in \Cref{sec:spt,sec:restricted}.
+There exists a $K_{\vp,\tau}$ depending on $\vp$ and $\tau$, but  independent of $\varepsilon$ and $d$, such that
 \begin{equation} \label{eq:ptauassume}
@@
 \end{equation*}
+If $\vp^* \in \cp_{\textup{(s)trct}}$, (strong) tractability may not hold for $\vp = \vp^*$, but it must hold for any $\vp$ whose components are all greater than the corresonding components of $\vp^*$.
 
@@
 
-Moreover, given that $T$ is increasing in its arguments, we have the following equivalent expression for the complexity via \eqref{eq:comp_def}:
+Moreover, given that $T$ is increasing in its arguments, we have the following equivalent expression for the information complexity via \eqref{eq:comp_def}:
 \begin{align} %\label{eq:comp_equiv}
@@
 \end{itemize}
-Firstly, it should be noted that the condition \eqref{eq:exp_spt} is easier to check in practice than the condition \eqref{eq:KW_exp_spt}.
-Indeed, since in \eqref{eq:KW_exp_spt} the summation indices $i$ show up in the exponents of the summands, we need the exact ordering of the eigenvalues $\lambda_{i,d}$, whereas in \eqref{eq:exp_spt} we only have a summation of the values of $1/T(\lambda_{i,d}^{-1},d,\vp)$, and the exact order of the eigenvalues can be neglected.
+
+\fred{Fred: Where does $p$ and/or $q$ come in conditions \eqref{eq:KW_exp_spt} and \eqref{eq:KW_exp_pt}?}
+
+Firstly, it should be noted that our condition \eqref{eq:exp_spt} is easier to check in practice than condition \eqref{eq:KW_exp_spt}.
+Since in \eqref{eq:KW_exp_spt} the summation indices $i$ show up in the exponents of the summands, we need the exact ordering of the eigenvalues $\lambda_{i,d}$, whereas in \eqref{eq:exp_spt} we only have a summation of the values of $1/T(\lambda_{i,d}^{-1},d,\vp)$, and the exact order of the eigenvalues can be neglected.
 A similar
@@
 \]
-Due to our assumption, we see that $\abs{B_d} < e\,M\,d^{\tau_1}$ and $\abs{B_d}\le \lfloor e\,M\,d^{\tau_1} \rfloor$.
+Due to our assumption, we see that $\card(B_d) < e\,M\,d^{\tau_1}$ and $\card(B_d)\le \lfloor e\,M\,d^{\tau_1} \rfloor$.
 Suppose now that $i\ge \lceil C d^{\tau_3}\rceil$ but $i\not\in B_d$, which means that
@@
 \]
-A problem is strongly $T$-separable tractable with parameter $\vp$ iff the complexity is independent of $d$, that is, there exists a positive constant $C_{\vp}$ which again does not depend on $\varepsilon$ and $d$ such that
+A problem is strongly $T$-separable tractable with parameter $\vp$ iff the information complexity is independent of $d$, that is, there exists a positive constant $C_{\vp}$ which again does not depend on $\varepsilon$ and $d$ such that
 \[
@@
 
-\section{(Strong) Tractability on a Restricted Domain}
+\section{(Strong) Tractability on a Restricted Domain} \label{sec:restricted}
 
@@
     A problem is strongly
-$T$-tractable with parameter $\vp$ \emph{on the restricted domain $\Omega$} iff the complexity is independent of the dimension of the problem, that is, there exists a positive constant $C_{\vp}$, again independent of $\varepsilon$ and $d$, such that
+$T$-tractable with parameter $\vp$ \emph{on the restricted domain $\Omega$} iff the information complexity is independent of the dimension of the problem, that is, there exists a positive constant $C_{\vp}$, again independent of $\varepsilon$ and $d$, such that
 \begin{equation} \label{eq:rest_strong_tract_def}
@@
 
-Moreover, given that $T$ is increasing in its arguments, we have the following equivalent expression for the complexity via
+Moreover, given that $T$ is increasing in its arguments, we have the following equivalent expression for the information complexity via
 \eqref{eq:comp_def}:

### 2023-07-19 Older_versions/GeneralizedTractability_230607.tex
Updates from Overleaf

@@
 The information complexity of the problem $\SOL_d$ is given by the function $\comp:(0,\infty) \times \naturals \to \natzero$, where $\comp(\varepsilon,d)$ is the number of linear functionals required by the best \peter{admissible} algorithm to satisfy the error criterion \eqref{eq:errcrit}.
-By definition, the complexity is non-decreasing  as $\varepsilon$ tends to zero.
+By definition, the \kachi{information} complexity is non-decreasing  as $\varepsilon$ tends to zero.
 We also expect it to be non-decreasing as $d$ tends to infinity, since $d$ is typically the number of variables for the functions in $\cf_d$.
@@
 The conditions we require $T$ to satisfy are described in  Section \ref{sec:not}, however, the basic idea is that we define our approximation problem to be tractable if $\comp(\varepsilon, d) \le  C_{\vp}\, T(\varepsilon^{-1},d,\vp)$ for some constant, $C_{\vp}$, depending only on the parameter $\vp$.
-\kachi{The parameter $\vp$ is a $s$-dimensional vector, where $\vp \geq 0$ implies that each component of $\vp$ is nonnegative.} In practice, we expect $T(\varepsilon^{-1},d,\vp)$ to increase sub-exponentially  with increasing $\varepsilon^{-1}$ and/or $d$, however, most of our theorems do not require such an assumption.
+\kachi{The parameter $\vp$ is a $s$-dimensional vector, for $s \geq 1$, where $\vp \geq 0$ implies that each component of $\vp$ is non-negative.} In practice, we expect $T(\varepsilon^{-1},d,\vp)$ to increase sub-exponentially  with increasing $\varepsilon^{-1}$ and/or $d$, however, most of our theorems do not require such an assumption.
 
@@
 
-\peter{TODO: Maybe add a short paragraph on the notation used in the paper and on its structure? In particular, we should introduce
-an ordering of the parameters $\vp$.}[\kachi{KACHI: I will take care of this}]
-
-\kachi{[KACHI: I will write about notations used in this paper. Is there are need to change notations like $[1,\infty)$ to $\naturals$ and $[0,\infty)$ to $\naturals_0$]}
-
-\kachi{We denote the set of positive integers by $\naturals$ and and the set of non-negative integers by $\naturals_0$.}
+\kachi{In Table \ref{tab:commonT} below we give common forms of the tractability function, $T$ considered in this paper.}
+
+%\peter{TODO: Maybe add a short paragraph on the notation used in the paper and on its structure?
+In particular, we should introducean ordering of the parameters $\vp$.}[\kachi{KACHI: I will take care of this}]
+
+%\kachi{[KACHI: I will write about notations used in this paper. Is there are need to change notations like $[1,\infty)$ to $\naturals$ and $[0,\infty)$ to $\naturals_0$]}
+
+\kachi{We denote the set of positive integers by $\naturals$ and and the set of non-negative integers by $\naturals_0$. The remainder of this paper is organized as follows.}
 In Section \ref{sec:spt}, we give the definitions of the considered tractability notions, in particular (strong) tractability.
@@
 \kachi{[KACHI: It seems the notation of the dimension has change from $d$ to $\delta$. I will work on this.]}
-Since the $\lambda_{i,d}$ are non-increasing in $i$, it follows that the $T(\lambda_{i,d}^{-1},d,\vp)$ are non-decreasing in $i$ for any $\thed\in\naturals$.
+Since the $\lambda_{i,d}$ are non-increasing in $i$, it follows that the $T(\lambda_{i,d}^{-1},d,\vp)$ are non-decreasing in $i$ for any $d\in\naturals$.
 In particular, for  any $N\in\naturals$ with $n\ge N$, we have
@@
     \lambda_{n+1,d} \le \lambda_{n,d} \le \cdots \le \lambda_{N,d}
-    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},\thed,\vp)} \le \frac{1}{T(\lambda_{n, d}^{-1},\thed,\vp)} \le \cdots \le \frac{1}{T(\lambda_{N, d}^{-1},\thed,\vp)} \\
-     \implies \frac{1}{T(\lambda_{n+1, d}^{-1},\thed,\vp) }
-    \le &\frac{1}{n-N+1} \sum_{i=N}^n  \frac{1}{T(\lambda_{i, d}^{-1},\thed,\vp) }
-    \le \frac{1}{n-N+1} \sum_{i=N}^\infty  \frac{1}{T(\lambda_{i, d}^{-1},\thed,\vp)}.
+    & \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d,\vp)} \le \frac{1}{T(\lambda_{n, d}^{-1},d,\vp)} \le \cdots \le \frac{1}{T(\lambda_{N, d}^{-1},d,\vp)} \\
+     \implies \frac{1}{T(\lambda_{n+1, d}^{-1},d,\vp) }
+    \le &\frac{1}{n-N+1} \sum_{i=N}^n  \frac{1}{T(\lambda_{i, d}^{-1},d,\vp) }
+    \le \frac{1}{n-N+1} \sum_{i=N}^\infty  \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}.
 \end{align*}
@@
 \begin{multline} \label{eq:implicate_a}
-    n - N +1 \ge T(\varepsilon^{-1},\thed,\vp) \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},\thed,\vp)} \\
-   \implies   \frac{1}{T(\lambda_{n+1, d}^{-1},\thed,\vp)} \le
-   \frac{1}{n-N+1} \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},\thed,\vp) } \le \frac{1}{T(\varepsilon^{-1},\thed,\vp)} \\ \forall \thed, n, N \in \naturals.
+    n - N +1 \ge T(\varepsilon^{-1},d,\vp) \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)} \\
+   \implies   \frac{1}{T(\lambda_{n+1, d}^{-1},d,\vp)} \le
+   \frac{1}{n-N+1} \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d,\vp) } \le \frac{1}{T(\varepsilon^{-1},d,\vp)} \\ \forall d, n, N \in \naturals.
 \end{multline}
@@
 	\nonumber
-	& = \min \biggl\{n \in \natzero : \frac{1}{T(\lambda_{n+1,d}^{-1},\thed,\vp)}\le \frac{1}{T(\varepsilon^{-1},\thed,\vp) }\biggr\} \qquad  \forall \thed\in \naturals\\
-	\nonumber
-	& \le  \min \biggl\{n \in \natzero : n \ge N - 1 + T(\varepsilon^{-1},\thed,\vp) \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},\thed,\vp)} \biggr\} \;  \forall  \thed, N \in \naturals, \quad \text{by \eqref{eq:implicate_a}} \\
-	& \le  T(\varepsilon^{-1},\thed,\vp) \Biggl [\frac{N}{T(\varepsilon^{-1},\thed,\vp)}  +  \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},\thed,\vp)} \Biggr] \quad \forall  \thed, N \in \naturals.
-\label{eq:compUP}
+	& = \min \biggl\{n \in \natzero : \frac{1}{T(\lambda_{n+1,d}^{-1},d,\vp)}\le \frac{1}{T(\varepsilon^{-1},d,\vp) }\biggr\} \qquad  \forall d\in \naturals\\
+	\nonumber
+	& \le  \min \biggl\{n \in \natzero : n \ge N - 1 + T(\varepsilon^{-1},d,\vp) \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)} \biggr\} \;  \forall  d, N \in \naturals, \quad \text{by \eqref{eq:implicate_a}} \\
+	& \le  T(\varepsilon^{-1},d,\vp) \Biggl [\frac{N}{T(\varepsilon^{-1},d,\vp)}  +  \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)} \Biggr] \quad \forall  d, N \in \naturals. \label{eq:compUP}
 \end{align}
 
-Now we take this upper bound further, specializing to the case of $\thed=1$ and $N=L_{\vp}$:
+Now we take this upper bound further, specializing to the case of $d=1$ and $N=L_{\vp}$:
 \begin{align*}
@@
 	\[
-	T(\varepsilon^{-1},d,s,t) = \max(1,\varepsilon^{-1})^s + d^t, \quad \forall \varepsilon,s,t > 0, \, d \in \naturals, \qquad h(x) = \exp(x) \quad \forall x \ge 0.
+	T(\varepsilon^{-1},d,\kachi{(s,t)}) = \max(1,\varepsilon^{-1})^s + d^t, \quad \forall \varepsilon,s,t > 0, \, d \in \naturals, \qquad h(x) = \exp(x) \quad \forall x \ge 0.
 	\]

### 2023-07-20 GeneralizedTractability2023July17.tex
Updates from Overleaf

@@
 %\newcommand{\theUB}{\spadesuit}
-\newcommand{\thed}{\delta}
+\newcommand{\thed}{\mathscr{D}}
 \newcommand{\theM}{\mathscr{E}}
@@
 
-TODO: We should check for consistency of the use of the $\forall$ symbol in displayed formulas. Sometimes we use it, sometimes we do not, sometimes it is preceded by a comma, sometimes not, etc.
+TODO: We should check for consistency of the use of the $\forall$ symbol in displayed formulas.
+Sometimes we use it, sometimes we do not, sometimes it is preceded by a comma, sometimes not, etc.
+\fred{Thanks, Kachi}
 
@@
 where $\comp(\varepsilon,d)$ is the number of linear functionals required by the best admissible algorithm to satisfy the error criterion \eqref{eq:errcrit}.
-By definition, the complexity is non-decreasing  as $\varepsilon$ tends to zero.
+By definition, the \kachi{information }complexity is non-decreasing  as $\varepsilon$ tends to zero.
 We also expect it to be non-decreasing as $d$ tends to infinity since $d$ is typically the number of variables for the functions in $\cf_d$.
@@
 The conditions we require $T$ to satisfy are described in  Section \ref{sec:not}, however, the basic idea is that we define our approximation problem to be tractable if $\comp(\varepsilon, d) \le  C_{\vp}\, T(\varepsilon^{-1},d,\vp)$ for some constant, $C_{\vp}$, depending only on the parameter $\vp$.
-The parameter $\vp$ is an $s$-dimensional vector, where $\vp \geq 0$ implies that each component of $\vp$ is nonnegative.
+The parameter $\vp$ is an $s$-dimensional vector with $s \geq 1$, where $\vp \geq \vzero$ implies that each component of $\vp$ is non-negative.
 In practice, we expect $T(\varepsilon^{-1},d,\vp)$ to increase sub-exponentially  with increasing $\varepsilon^{-1}$ and/or $d$, however, most of our theorems do not require such an assumption.
@@
 
-\kachi{[KACHI: I will write about notations used in this paper. Is there are need to change notations like $[1,\infty)$ to $\naturals$ and $[0,\infty)$ to $\naturals_0$]}
+\kachi{[KACHI: I will write about notations used in this paper. Is there a need to change notations like $[1,\infty)$ to $\naturals$ and $[0,\infty)$ to $\naturals_0$]}
 
 We denote the set of positive integers by $\naturals$ and and the set of non-negative integers by $\naturals_0$.
+The remainder of this paper is organized as follows.
 In Section \ref{sec:spt}, we give the definitions of the considered tractability notions, in particular (strong) tractability.
@@
 Next we show that if $\vp^* \in \widetilde{\cp}_{\textup{trct}}$, then $\vp^* \in \cp_{\textup{trct}}$.
-If $\vp^* \in \widetilde{\cp}_{\textup{strct}}$, then \eqref{eq:tractiff4}  holds for all $\vp \in (\vp^*,\vinfty)$.
+If \kachi{$\vp^* \in \widetilde{\cp}_{\textup{trct}}$}, then \eqref{eq:tractiff4}  holds for all $\vp \in (\vp^*,\vinfty)$.
 By the argument to prove the sufficient condition above, it follows that \eqref{eq:strong_tract_def} must also hold for all $\vp \in (\vp^*,\vinfty)$.
@@
 
-Thus,  $\cp_{\textup{opt}}= \widetilde{\cp}_{\textup{opt}}$.  This concludes the proof of Theorem \ref{thm_main_tract2}.  \qed
+\bigskip
+\noindent This concludes the proof of Theorem \ref{thm_main_tract2}.  \qed
 \end{proof}
@@
 \[
- T(\varepsilon^{-1},d,\vp)= \max\{1,\varepsilon^{-\vp}\}\, d^q
+ T(\varepsilon^{-1},d,\vp)= \max\{1,\varepsilon^{-p}\}\, d^q
  \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty)^2,
@@
 \]
+\kachi{[KACHI: I have questions regarding $\vp$.]}
 Furthermore, the set of optimal $(p,q)$ is a subset of
@@
 \end{multline*}
-\peter{[Is the latter statement still correct?]}
+\peter{[Is the latter statement still correct?] \kachi{[I think not.]}}
 This essentially recovers the result on polynomial tractability in \cite[Theorem 5.1]{NovWoz08a}. %\fred{same theorem as above??, what about optimality in \cite[Theorem 5.1]{NovWoz08a}}.
@@
 \begin{equation}\label{eq:exp_spt}
- \sup_{d\in\naturals} \sum_{i=L_{p} }^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^{p}}  < \infty,\quad  \text{ for some } p \ge 0, L_{p} \in \naturals.
+ \sup_{d\in\naturals} \sum_{i=L_{p} }^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p}< \infty,\quad  \text{ for some } p \ge 0, L_{p} \in \naturals.
 \end{equation}
@@
 \begin{itemize}
-    \item We have exponential strong polynomial tractability iff there exists a $\tau>0$ and a
+    \item We have exponential strong polynomial tractability iff there exists a $\tau>0$ and
     a $C\in\naturals$ such that
@@
 
-\fred{Fred: Where does $p$ and/or $q$ come in conditions \eqref{eq:KW_exp_spt} and \eqref{eq:KW_exp_pt}?}
+\fred{Fred: Where does $p$ and/or $q$ come in conditions \eqref{eq:KW_exp_spt} and \eqref{eq:KW_exp_pt}?} \kachi{[Kachi: I believe for \eqref{eq:KW_exp_spt} $p$ corresponds to $\tau$ and for \eqref{eq:KW_exp_pt} $p$ corresponds to $\tau_2$ and $q$ corresponds to both $\tau_1$ and $\tau_3$.]}
 
@@
 \]
-for some $\tau_1,\tau_3\ge 0$ and $\tau_2, C>0$.
-Define
+for some $\tau_1,\tau_3\ge 0$ and $\tau_2, C>0$. Here, $M$ and other constants above may depend on $\tau_1$, $\tau_2$, and $\tau_3$.
+Define $B_d$ as the set of indices that are contained in the above sum and for which the terms in the sum are relatively large:
 \[
@@
 Due to our assumption, we see that $\card(B_d) < e\,M\,d^{\tau_1}$ and $\card(B_d)\le \lfloor e\,M\,d^{\tau_1} \rfloor$. 
-Suppose now that $i\ge \lceil C d^{\tau_3}\rceil$ but $i\not\in B_d$, which means that
-\[\lambda_{i,d}^{i^{-\tau_2}} \le \frac{1}{e} \iff \log (\lambda_{i,d}^{-1})\ge i^{\tau_2}.\]
-Now, choose $p> 1/\tau_2$, $q=\max\{\tau_1,\tau_3\}$, and $L_{(p,q)}=\max\{C, e\, M\}$, which implies that $\lceil L_{(p,q)} d^{q}\rceil \ge e\, M\, d^{\tau_1}$. Then, for any $d\in\naturals$,
+Suppose now that $i\ge \lceil C d^{\tau_3}\rceil$ but $i\not\in B_d$, which means that the term in the above sum is relatively small:
+\begin{equation}
+    \lambda_{i,d}^{i^{-\tau_2}} \le \frac{1}{e} \iff \log (\lambda_{i,d}^{-1})\ge i^{\tau_2}.
+\label{eq:logandi}
+\end{equation}
+
+Now, choose $p> 1/\tau_2$, $q=\max\{\tau_1,\tau_3\}$, and $L_{(p,q)}=\max\{C, e\, M\}$, which implies that $\lceil L_{(p,q)} d^{q}\rceil \ge e\, M\, d^{\tau_1}$.
+Then, for any $d\in\naturals$, the desired sum in \eqref{eq:exp_pt} can be bounded by splitting it into the sum of the larger terms and the sum of the smaller terms:
 \begin{align*}
-d^{-q} \sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p}&=d^{-q} \sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\in B_d}}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p}\\
-&\qquad  + d^{-q} \sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\not\in B_d}}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p}\\
+\MoveEqLeft{d^{-q} \sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p}} \\
+&=d^{-q} \sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\in B_d}}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p} + d^{-q} \sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\not\in B_d}}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p}\\
 &\le d^{-q} e\, M\, d^{\tau_1} + d^{-q}\sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\not\in B_d}}^\infty \frac{1}{[\log (\lambda_{i,d}^{-1})]^p}\\
-&\le e\, M + d^{-q}\sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\not\in B_d}}^\infty \frac{1}{i^{\tau_2 p}}\\
+&\le e\, M + d^{-q}\sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\not\in B_d}}^\infty \frac{1}{i^{\tau_2 p}} \qquad \text{by \eqref{eq:logandi}}\\
 &\le  e\, M + \zeta (\tau_2 p).
@@
 
-Conversely, let us now assume that Condition \eqref{eq:exp_pt} holds.
+Conversely, let us now assume that Condition \eqref{eq:exp_pt} holds for some $p> 0$ and $q\ge 0$ that are assumed to be fixed.
+All constants in this part of the proof may depend on $p$ and $q$.
 We will show next that this implies Condition \eqref{eq:KW_exp_pt}.
-Indeed, due to \eqref{eq:exp_pt}, there exists a positive constant $M$ (w.l.o.g., we can assume that $M\ge 1$), and $p\ge 0$ (again, w.l.o.g., let us assume $p>0$), $q\ge 0$, and $L_{(p,q)}>0$ such that for all $d\in\naturals$,
+Indeed, due to \eqref{eq:exp_pt}, there exist constants $M > 1$ and $L_{(p,q)}>0$ such that for all $d\in\naturals$,
 \[
@@
 \]
-Similarly to the proof of Theorem \ref{thm_main_strong_tract2}, we see that for any $n > \lceil L_{(p,q)} d^{q}\rceil $,
+Similarly to the proof of the sufficient condition in Theorem \ref{thm_main_strong_tract2}, we see that for any $n > \lceil L_{(p,q)} d^{q}\rceil $,
 \[
@@
 \]
-This implies that
+This inequality implies for our specific choice of $T$ that
 \[
@@
 
-\kachi{In the following example, we provide a brief summary of these \peter{[What does ``these'' refer to?]} notions of tractability.
+\kachi{In the following example, we provide a brief summary of the above examples \peter{[What does ``these'' refer to?]} of tractability.
 We would like to emphasize that this example was previously known (see, e.g., \cite{GW06}) where in this case, the roles of $\varepsilon^{-1}$ and $d$ are separated.
-In order to accomplish this, we will first define two functions $\phi$ and $\psi$ with positive values that are increasing in both of their arguments.
-This will allow us to take into account a variety of possible exponents of $\varepsilon^{-1}$ and $d$.
+In order to accomplish this, we will first define two functions $\phi$ and $\psi$ with positive values that are increasing in both of their arguments which will allow to take into account a variety of possible exponents of $\varepsilon^{-1}$ and $d$.
 %To do this, we introduce two positive-value functions that are increasing in both arguments so as to take possibly different exponents of $\varepsilon^{-1}$ and $d$.
@@
      \quad \mbox{and} \quad
-      [\psi(d,q)]^{\tau_2} \le \hat{K}_{q,\tau_2} \psi (d,\tau_2 q) \qquad \forall \, \varepsilon \in (0,\infty),\, d\in \naturals,
+      [\psi(d,q)]^{\tau_2} \le \hat{K}_{q,\tau_2} \psi (d,\tau_2 q) \qquad \forall \, \varepsilon >0,\, d\in \naturals,
 \end{align*} where $\hat{K}_{p,\tau_1}>0$ is a constant that may depend on $p$ and $\tau_1$, but is independent of $\varepsilon$, and where $\hat{K}_{q,\tau_2}>0$ is a constant that may depend on $q$ and $\tau_2$, but is independent of $d$.
@@
 \end{equation*}
-for some $p>0$ and $L_p \in \naturals$. Furthermore, the optimal $p$ is also the infimum of all $p$ satisfying the latter condition.
-Theorem \ref{thm_main_tract2} yields the following equivalent condition for separable tractability:
+for some $p>0$ and $L_p \in \naturals$. Furthermore, the optimal $p$ is also the infimum of all $p$ satisfying the latter condition. Also,
+Theorem \ref{thm_main_tract2} yields the following equivalent condition for $T$-separable tractability:
 \[
@@
 \end{example}
-\kachi{Next, we will introduce another summarized \peter{[what do we mean by ``summarized''?]} notion of tractability.
+\kachi{Next, we introduce a generalized \peter{[what do we mean by ``summarized''?]} notion of tractability.
 In the following, we will define two functions $\hat{\phi}$ and $\hat{\psi}$ that take the roles of $\varepsilon^{-1}$ and $d$.
@@
 \begin{equation}\label{expqpt}
-    \comp(\varepsilon,d) \leq C\exp\{p(1+\log(\varepsilon^{-1}))(1+\log(d))\}
+    \comp(\varepsilon,d) \leq C\exp[p(1+\log(\varepsilon^{-1}))(1+\log(d))]
 \end{equation}
@@
 \end{definition}
-Note that the following examples are given below such that they equivalent to the definition in \cite{GneWoz11a}
+Note that the following examples are given below such that they equivalent to the definition in \cite{GneWoz11a}.
 }
@@
 \begin{example}[Algebraic quasi-polynomial tractability]
-
-%we say that a problem is \emph{quasi-polynomially tractable (QPT)} if there exist two constants $C$, $p > 0$, such that
-%\begin{equation}\label{expqpt}
- %   \comp(\varepsilon,d) \leq C\exp\{p(1+\log(\varepsilon^{-1}))(1+\log(d))\}
-%\end{equation}
-%for all $\varepsilon \in (0,1]$ and $d\in\mathbb{N}$.
-
 Let the tractability function, $T$,
@@
 \[
-T(\varepsilon^{-1},d,p) = e^p[\max\{1,\varepsilon^{-1}\}]^{p(1+\log d)}d^p.
+T(\varepsilon^{-1},d,p) = e^p(\max\{1,\varepsilon^{-1}\})^{p(1+\log d)}d^p.
 \]
@@
 \[
-\sup_{d\in\mathbb{N}}\,d^{-p}\sum_{i=\lceil L_p\,d^{p}\rceil} \left(\min\{1,\lambda_{i,d}\} \right)^{p(1+\log d)} < \infty \qquad \text{for some } p \geq 0, L_p >0.\]
+\sup_{d\in\mathbb{N}}\,d^{-p}\sum_{i=\lceil L_p\,d^{p}\rceil} \frac{1}{\left(\max\{1,\lambda_{i,d}\}\right)^{p(1+\log d)}} < \infty \qquad \text{for some } p \geq 0, L_p >0.\]
 \end{example}
@@
  T(\varepsilon^{-1},d,\vp)= \exp [p(1+\log(\max\{1,\log(1+\varepsilon^{-1})\}))(1+\log (d))]  \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty),
-\] where in this case $\vp = p$. This can be rewritten as
-\[
-T(\varepsilon^{-1},d,\vp) = e^p[\max\{1,\log(1+\varepsilon^{-1}\})]^{p(1+\log d)}d^p.
+\] where in this case $\vp = p$ is a scalar. This can be rewritten as
+\[
+T(\varepsilon^{-1},d,\vp) = e^p(\max\{1,\log(1+\varepsilon^{-1})\})^{p(1+\log d)}d^p.
 \]
@@
 \section{Acknowledgments}
+\kachi{The authors gratefully acknowledge the contributions of H. Wo\'{z}niakowski and E. Novak. P. Kritzer acknowledges the support of the Austrian Science Fund, Project ---, which is part of the
+Special Research Program “Quasi-Monte Carlo Methods: Theory and Applications”.}
+
 Thank Henryk and Erich.

### 2023-09-21 GeneralizedTractability2023August10.tex
Updates from Overleaf

--- 2023-07-20 GeneralizedTractability2023July17.tex
@@
 \newtheorem{theorem}{Theorem}
+\newtheorem{proposition}{Proposition}
 \newdefinition{definition}{Definition}
@@
 
+\author[1]{Onyekachi Emenike}
+\ead{kachi.emenike12@gmail.com}
 \author[1]{Fred J. Hickernell}
@@
 \ead{peter.kritzer@oeaw.ac.at}
-\author[1]{Onyekachi Osisiogu}\ead{oosisiogu@iit.edu}
+
 \date{\today}
@@
     A large literature specifies conditions under which the information complexity for a sequence of numerical problems defined for dimensions $1, 2, \ldots$ grows at a moderate rate, i.e., the sequence of problems is \emph{tractable}.
-Here, we focus on the situation where the space of available information consists of all linear functionals and the problems are defined as operator mappings between Hilbert spaces.
+Here, we focus on the situation where the space of available information consists of all linear functionals and the problems are defined as linear operator mappings between Hilbert spaces.
 We unify the proofs of known tractability results and generalize a number of existing results.
-These generalizations are expressed as five theorems that provide equivalent conditions for (strong) tractability in terms of sums of functions of the singular values.
+These generalizations are expressed as five theorems that provide equivalent conditions for (strong) tractability in terms of sums of functions of the singular values of the solution operators.
 \end{abstract}
@@
 
-\medskip
-
-TODO: We should check for consistency of the use of the $\forall$ symbol in displayed formulas.
-Sometimes we use it, sometimes we do not, sometimes it is preceded by a comma, sometimes not, etc.
-\fred{Thanks, Kachi}
-
-\bigskip
-
-The information complexity of a problem is the number of function data required to solve the problem within the desired error tolerance.
+\noindent The information complexity of a problem is the number of function data required to solve the problem within the desired error tolerance.
 A problem is tractable if the information complexity does not grow too large as the dimension of the problem increases or the error threshold decreases.
@@
     \label{eq:errcrit}
-    \norm[\cg_d]{\SOL_d(f) - \APP_d(f,\varepsilon)} \le \varepsilon \qquad \forall f \in \cb_d, \ \varepsilon \in (0,\infty).
+    \norm[\cg_d]{\SOL_d(f) - \APP_d(f,\varepsilon)} \le \varepsilon \qquad \forall f \in \cb_d, \ \varepsilon \in (0,\infty)\footnote{We note that the radius of the $\cb_d$ could be taken to be an arbitrary positive value, $R$, in which case the problem becomes equivalent to the original one with the tolerance $\varepsilon$ replaced by $\varepsilon/R$ since the problem and the optimal approximate soluion are both linear (see below).}.
 \end{equation}
@@
 where $\comp(\varepsilon,d)$ is the number of linear functionals required by the best admissible algorithm to satisfy the error criterion \eqref{eq:errcrit}.
-By definition, the \kachi{information }complexity is non-decreasing  as $\varepsilon$ tends to zero.
+By definition, the information complexity is non-decreasing  as $\varepsilon$ tends to zero.
 We also expect it to be non-decreasing as $d$ tends to infinity since $d$ is typically the number of variables for the functions in $\cf_d$.
 
-For this case where arbitrary linear functionals are allowed, the optimal solution operator is known to be
+For this case where arbitrary linear functionals are allowed, the optimal approximate solution operator is known to be
 \[
@@
 \]
-This means that, essentially, in the tractability analysis below, all criteria would be normalized by the first eigenvalue $\lambda_{1,d}$.
+This means that, essentially, in the tractability analysis below, all criteria would be normalized by the first \peter{singular value} $\lambda_{1,d}$.
 For the sake of brevity and clarity of notation, we restrict ourselves to the absolute error criterion here, but presumably analogous results hold for the normalized setting.
@@
 The question of tractability is one of determining how fast the information complexity increases as $\varepsilon$ tends to zero and/or as $d$ tends to infinity.
-Although \eqref{eq:comp_def} has a relatively simple in form, its dependence on the ordering of the singular values means that it is not obvious what the behavior of $\comp(\varepsilon, d)$ is as $\varepsilon^{-1}$ and/or $d$ tend to infinity.
-
-We want to bound the information complexity in terms of a simple function, $T$, of $\varepsilon^{-1}$ and $d$ and identify conditions on the singular values that are easier to verify that are equivalent to this bound on the information complexity holding.
+Although \eqref{eq:comp_def} has a relatively simple form, its dependence on the ordering of the singular values means that it is not obvious what the behavior of $\comp(\varepsilon, d)$ is as $\varepsilon^{-1}$ and/or $d$ tend to infinity.
+
+We want to bound the information complexity in terms of a simple function, $T$, of $\varepsilon^{-1}$ and $d$, and identify conditions on the singular values that are easier to verify that are equivalent to this bound on the information complexity holding.
 We note that generalized tractability specified by a function $T$ has been considered before in the literature.
@@
 To our understanding, however, these references mainly focus on the special case of tensor product problems, a restriction we do not make.
-Moreover, the conditions for tractability derived there are mostly in terms of properties of the function $T$, and not in terms of sums of (functions of) the eigenvalues of a problem.
-Hence, the present paper an adds to what is presently known on this subject.
-
+Moreover, the conditions for tractability derived there focus mostly on relating the properties of the function $T$ to the different varieties of tractability, and not in terms of sums of (functions of) the \peter{singular values} of a problem.
+Hence, the present paper adds to what is presently known on this subject.
 In this article, we investigate a \emph{generalized tractability function}, denoted by $T$:
@@
     \comp(\varepsilon, d) \le  C_{\vp}\, T(\varepsilon^{-1},\thed,\vp) \quad \forall (\varepsilon^{-1},d) \in \Omega \\
-    \iff   \exists L_{\vp} \text{ with }
+    \iff   \exists L_{\vp} \peter{>0} \text{ with }
     \sup_{d \in \naturals}
@@
 \end{multline}
-The differences in these theorems of are in the choices of $\thed$, $\Omega$, $\theM$, and $\theUB$.
+The differences in these theorems are in the choices of $\thed$ and $\Omega$.
 Although some of these theorems are special cases of others, we prove each separately to allow the reader to become familiar with the arguments used as additional layers of complexity are added.
@@
 
-\peter{TODO: Maybe add a short paragraph on the notation used in the paper and on its structure? In particular, we should introduce
-an ordering of the parameters $\vp$.}[\kachi{KACHI: I will take care of this}]
-
-\kachi{[KACHI: I will write about notations used in this paper. Is there a need to change notations like $[1,\infty)$ to $\naturals$ and $[0,\infty)$ to $\naturals_0$]}
-
-We denote the set of positive integers by $\naturals$ and and the set of non-negative integers by $\naturals_0$.
+In the following, we will denote the set of positive integers by $\naturals$ and the set of non-negative integers by $\naturals_0$.
+We write $\vzero$ to denote a vector with all components equal to zero, and $\vinfty$ to denote a vector with all components equal to $\infty$.
+Furthermore, for two vectors $\vp=(p_1,\ldots,p_s)$ and $ \vp'=(p_1',\ldots,p_s')$ in $[0,\infty)^s$, 
+we write $\vp\ge \vp'$ if $p_j\ge p'_j$ for all $j\in \{1,\ldots,s\}$. Furthermore, $\vp > \vp'$ 
+if $p_j> p'_j$ for all $j\in \{1,\ldots,s\}$. The expression $\vp\in (\vp',\vp'')$ is to be interpreted as 
+$\vp' < \vp < \vp''$ in that sense, and analogously for half-closed or closed intervals.
+
 The remainder of this paper is organized as follows.
 In Section \ref{sec:spt}, we give the definitions of the considered tractability notions, in particular (strong) tractability.
-We consider strong tractability when the information complexity is independent of the dimension, $d$.
-We then turn to tractability  when the information complexity may depend on both $d$ and $\varepsilon^{-1}$.
+We consider strong tractability when there is an upper bound on the information complexity that is independent of the dimension, $d$.
+We then turn to tractability  when the bound on the information complexity may depend on both $d$ and $\varepsilon^{-1}$.
 In Section \ref{sec:examples} we provide examples of tractability functions for both the algebraic and exponential cases.
-We also consider other notions of tractability such as quasi-polynomial tractability, and a generalized notion of weak tractability.
-In the case of generalized weak tractability, we give the necessary and sufficient conditions on the notion of exponential tractability in Section \ref{sec:subh} \peter{[I think I do not quite understand what we mean by the last sentence.]}.
+We also consider other notions of tractability such as quasi-polynomial tractability, and introduce other notions of tractability.
+A generalized notion of weak tractability is given in Section \ref{sec:subh}.
+In Section \ref{sec:restricted}, we consider \peter{tractability on} a restricted domain .
 
@@
 \end{equation}
-which implies that the problem is expected to be no easier by decreasing the tolerance, $\varepsilon$, or increasing the dimension, $d$.
-(This is why we make $T$ a function of $\varepsilon^{-1}$ rather than of $\varepsilon$.) Furthermore, increasing $\vp$ allows for a possibly looser bound on the information complexity.
-Since there are an infinite number of positive eigenvalues, it also makes sense to assume that
+which implies that the problem is expected to be no easier by decreasing the tolerance, $\varepsilon$, or increasing the dimension, $d$\footnote{This is why we make $T$ a function of $\varepsilon^{-1}$ rather than of $\varepsilon$.} Furthermore, increasing $\vp$ allows for a possibly looser bound on the information complexity.
+Since there are an infinite number of positive \peter{singular values}, it also makes sense to assume that
 \begin{equation}\label{eq:Tlim}
@@
 \begin{equation} \label{eq:ptauassume}
-	[T(\varepsilon^{-1},d,\vp)]^\tau \le K_{\vp,\tau} T(\varepsilon^{-1},d,\tau \vp),   \quad \forall \varepsilon \in (0,\infty), \ d \in \naturals, \ \vp\in[0,\infty)^s, \ \tau\in [1,\infty).
+	[T(\varepsilon^{-1},d,\vp)]^\tau \le K_{\vp,\tau} T(\varepsilon^{-1},d,\tau \vp)   \quad \forall \varepsilon \in (0,\infty), \ d \in \naturals, \ \vp\in[0,\infty)^s, \ \tau\in [1,\infty).
 \end{equation}
@@
 		\toprule
-		\text{algebraic strong polynomial} & \max\{1,\varepsilon^{-p}\} & 1\\
+		%\text{algebraic strong polynomial} & \max\{1,\varepsilon^{-p}\} & 1\\
 		\text{algebraic polynomial} & \max\{1,\varepsilon^{-p}\}d^{q} & d^{q}\\
-		\text{exponential strong polynomial} &  [\max\{1,\log(1 + \varepsilon^{-1}\}]^p & 1\\
+		%\text{exponential strong polynomial} &  [\max\{1,\log(1 + \varepsilon^{-1}\}]^p & 1\\
 		\text{exponential polynomial} &
@@
 \end{equation*}
-If $\vp^* \in \cp_{\textup{(s)trct}}$, (strong) tractability may not hold for $\vp = \vp^*$, but it must hold for any $\vp$ whose components are all greater than the corresonding components of $\vp^*$.
+If $\vp^* \in \cp_{\textup{(s)trct}}$, (strong) tractability may not hold for $\vp = \vp^*$, but it must hold for any $\vp$ whose components are all greater than the corresponding components of $\vp^*$.
 
@@
 \end{multline}
-We note that the left side of the implication implies $n \ge N$ automatically since $n$ is an integer  $n - N +1$ is assumed to be positive.
+We note that the left side of the implication implies $n \ge N$ automatically since $n$ is an integer \peter{and} $n - N +1$ is assumed to be positive.
 
@@
 \]
-Since the sequence of eigenvalues $\lambda_{1,d}, \lambda_{2,d}, \ldots $ is non-increasing, we have
+Since the sequence of \peter{singular values} $\lambda_{1,d}, \lambda_{2,d}, \ldots $ is non-increasing, we have
 \begin{equation}\label{eq:lambda_K_strong3}
@@
 \[
-i(\varepsilon,\vp)\le C_{\vp}\, T(\varepsilon^{-1},1,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,\vp),d}^{-1},1,\vp)+1, \qquad \forall \varepsilon > 0, \ d \in \mathbb{N},
+i(\varepsilon,\vp)\le C_{\vp}\, T(\varepsilon^{-1},1,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,\vp),d}^{-1},1,\vp)+1 \qquad \forall \varepsilon > 0, \ d \in \mathbb{N},
 \]
@@
 \[
-i\le C_{\vp} T(\lambda_{i,d}^{-1},1,\vp)+1, \qquad \forall i \ge i(\infty,\vp), \ d \in \naturals.
+i\le C_{\vp} T(\lambda_{i,d}^{-1},1,\vp)+1 \qquad \forall i \ge i(\infty,\vp), \ d \in \naturals.
 \]
@@
 \end{gather*}
-Summing both sides of this last inequality over $i$ from $i(\infty,\vp) +1 \ge 2$ to $\vinfty$ yields
+Summing both sides of this last inequality over $i$ from $i(\infty,\vp) +1 \ge 2$ to $\infty$ yields
 \begin{equation*}
@@
 \]
-Since the sequence of eigenvalues $\lambda_{1,d}, \lambda_{2,d}, \ldots $ is non-increasing, we have
+Since the sequence of \peter{singular values} $\lambda_{1,d}, \lambda_{2,d}, \ldots $ is non-increasing, we have
 \begin{equation}\label{eq:lambda_K4}
@@
 \[
-i(\varepsilon,d,\vp)\le C_{\vp}\, T(\varepsilon^{-1},d,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,d,\vp),d}^{-1},d,\vp)+1, \qquad \forall \varepsilon > 0, \ d \in \naturals,
+i(\varepsilon,d,\vp)\le C_{\vp}\, T(\varepsilon^{-1},d,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,d,\vp),d}^{-1},d,\vp)+1 \qquad \forall \varepsilon > 0, \ d \in \naturals,
 \]
@@
 \[
-i\le C_{\vp}\, T(\varepsilon^{-1},d,\vp)+1 \le C_{\vp} T(\lambda_{i,d}^{-1},d,\vp)+1, \qquad \forall i \ge i(\infty,d,\vp),  \ d \in \naturals.
+i\le C_{\vp}\, T(\varepsilon^{-1},d,\vp)+1 \le C_{\vp} T(\lambda_{i,d}^{-1},d,\vp)+1 \qquad \forall i \ge i(\infty,d,\vp),  \ d \in \naturals.
 \]
@@
 \[
-\sup_{d\in\naturals}\,\, \sum_{i=\lceil L(\vp') T(0,d,\vp')\rceil}^\infty \frac{1}{T(\lambda_{i,d}^{-1},d, \vp')}
+\sup_{d\in\naturals}\,\, \sum_{i=\lceil \kachi{L_{\vp'}} T(0,d,\vp')\rceil}^\infty \frac{1}{T(\lambda_{i,d}^{-1},d, \vp')}
 \le
@@
 If \kachi{$\vp^* \in \widetilde{\cp}_{\textup{trct}}$}, then \eqref{eq:tractiff4}  holds for all $\vp \in (\vp^*,\vinfty)$.
-By the argument to prove the sufficient condition above, it follows that \eqref{eq:strong_tract_def} must also hold for all $\vp \in (\vp^*,\vinfty)$.
+By the argument to prove the sufficient condition above, it follows that \eqref{eq:tract_def} must also hold for all $\vp \in (\vp^*,\vinfty)$.
 Thus, $\vp^* \in \cp_{\textup{trct}}$.
@@
 %In this section, we illustrate Theorems \ref{thm_main_strong_tract2} and \ref{thm_main_tract2} for the types of tractability given in the table in Section \ref{sec:not}.
-In this section, we present six examples relating to Theorem \ref{thm_main_strong_tract2} and Theorem \ref{thm_main_tract2}, both of which were introduced in Section \ref{sec:spt}, for the various notions of tractability that are listed in Table \ref{tab:commonT}.
-In subsequent sections, we will continue to present various examples.
+In this section, we present six examples relating to Theorem \ref{thm_main_strong_tract2} and Theorem \ref{thm_main_tract2}, both of which were \peter{shown} in Section \ref{sec:spt}, for the various notions of tractability that are listed in Table \ref{tab:commonT}.
+In \peter{the} subsequent sections, we will continue to present various examples.
 
@@
 
-\begin{example}[Algebraic strong polynomial tractability]
-
-Let the tractability function, $T$,
-be defined by
-\[
- T(\varepsilon^{-1},d,\vp)= \max\{1,\varepsilon^{-\vp}\}
- \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty),
-\]
-where in this case $\vp=p$ is a scalar.
-Then Theorem \ref{thm_main_strong_tract2} yields the  equivalent condition for algebraic strong polynomial tractability:
-\[
- \sup_{d\in\naturals} \sum_{i=L_p}^\infty \min\{1,\lambda_{i,d}^p\} < \infty \text{ for some } p \ge 0, L_p \in \naturals.
-\]
-Furthermore, the optimal $p$ is the infimum of all $p$ for which the above condition holds.
-This essentially recovers the result in \cite[Theorem 5.1]{NovWoz08a}.
-\end{example}
+%\begin{example}[Algebraic strong polynomial tractability]
+
+%
+%\end{example}
 
@@
 \[
- \sup_{d\in\naturals}\, d^{-q} \sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty \min\{1,\lambda_{i,d}^p\}  < \infty \text{ for some } p,q \ge 0, L_{(p,q)} \in \naturals.
-\]
-\kachi{[KACHI: I have questions regarding $\vp$.]}
-Furthermore, the set of optimal $(p,q)$ is a subset of
-\begin{multline*}
-\{(p^*,q^*) : \text{the above condition holds for all }(p,q) \in (p^*,\infty) \times (q^*,\infty) \\
-\text{but not for any }(p,q) \in [0,p^*/2) \times [0,q^*/2)\}.
-\end{multline*}
-\peter{[Is the latter statement still correct?] \kachi{[I think not.]}}
-This essentially recovers the result on polynomial tractability in \cite[Theorem 5.1]{NovWoz08a}. %\fred{same theorem as above??, what about optimality in \cite[Theorem 5.1]{NovWoz08a}}.
+ \sup_{d\in\naturals}\, d^{-q} \sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty \min\{1,\lambda_{i,d}^p\}  < \infty \text{ for some } p,q \ge 0, L_{(p,q)} \peter{>0}.
+\]
+Furthermore, for optimality, let $\widetilde{\cp}_{\textup{ALG-trct}} : = \{(p^*,q^*) : \text{the above condition holds }\forall (p,q) \in (p^*,\infty)\times(q^*,\infty) \}$.
+Therefore, the set of optimal $(p,q)$ is the set
+\[
+    \{(p^*,q^*) \in \widetilde{\cp}_{\textup{ALG-trct}} : (p^*,q^*) \notin [\widetilde{p},\infty) \times [\widetilde{q},\infty)\, \, \forall (\widetilde{p},\widetilde{q}) \in \widetilde{\cp}_{\textup{ALG-trct}}\setminus \{p^*,q^*\}  \}.
+\]
+This essentially recovers the result on polynomial tractability in \cite[Theorem 5.1]{NovWoz08a}.
+
+Having defined the tractability function \peter{as above}, we will now examine a specific case where we always set $d=1$,i.e.,
+\[
+T(\varepsilon^{-1},1,\vp)= \max\{1,\varepsilon^{-\vp}\}\qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty),
+\]
+where in this case $\vp=p$ is a scalar.
+
+%\peter{[But this is not what we discussed on Wednesday.
+The idea is that we use the same tractability function as for algebraic polynomial tractability, but consider the special case where we always set $d=1$,i.e., we use
+%\[
+ %T(\varepsilon^{-1},1,\vp)= \max\{1,\varepsilon^{-p}\}\\qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty)^2,\]
+%as an upper bound on the information complexity.
+Then everything would correspond to our definitions of $T$-tractability and strong $T$-tractability.
+Kachi, can you please make this change here and also in Example 2?
+So, please make it clear that the tractability function for strong polynomial tractability is a specialization of the tractability function for polynomial tractability.]
+%}
+
+Then Theorem \ref{thm_main_strong_tract2} yields the equivalent condition for algebraic strong polynomial tractability:
+\[
+\sup_{d\in\naturals} \sum_{i=L_p}^\infty \min\{1,\lambda_{i,d}^p\} < \infty \text{ for some } p \ge 0, L_p \in \naturals.
+\]
+Furthermore, the optimal $p$ is the infimum of all $p$ for which the above condition holds. This essentially recovers the result in \cite[Theorem 5.1]{NovWoz08a}.
 \end{example}
-
-\begin{example}[Exponential strong polynomial tractability]
+Next, we consider the exponential case where we replace $\varepsilon^{-1}$ by $\log(1+\varepsilon^{-1})$ and consider the same notions of tractability as for the algebraic case.
+\begin{example}[Exponential polynomial tractability]
 Let the tractability function, $T$,
@@
 \[
- T(\varepsilon^{-1},d,\vp)= [\max\{1,\log(1+\varepsilon^{-1})\}]^{\vp}, \quad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty),
-\]
+ T(\varepsilon^{-1},d,\vp)=\left[\max\{1,\log(1+\varepsilon^{-1})\}\right]^p\, d^q \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty)^2,
+\] where $\vp = (p,q)$. Then Theorem \ref{thm_main_tract2} yields  the equivalent condition for exponential polynomial tractability:
+\begin{equation}\label{eq:exp_pt}
+ \sup_{d\in\naturals}\, d^{-q} \sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p} < \infty  \text{ for some } p,q \ge 0, L_{(p,q)} \peter{>0}.
+\end{equation}
+Furthermore, for optimality, let $\widetilde{\cp}_{\textup{EXP-trct}} : = \{(p^*,q^*) : \text{the above condition holds }\forall (p,q) \in (p^*,\infty)\times(q^*,\infty) \}$.
+Therefore, the set of optimal $(p,q)$ is the set
+\[
+    \{(p^*,q^*) \in \widetilde{\cp}_{\textup{EXP-trct}} : (p^*,q^*) \notin [\widetilde{p},\infty) \times [\widetilde{q},\infty)\, \, \forall (\widetilde{p},\widetilde{q}) \in \widetilde{\cp}_{\textup{ALG-trct}}\setminus \{p^*,q^*\}  \}.
+\]
+Again, we will look at \peter{the} special case in which we always set $d=1$. In this case, we will define $T$ as follows.
+\[
+T(\varepsilon^{-1},1,p)= [\max\{1,\log(1+\varepsilon^{-1})\}]^{\vp} \quad \forall \varepsilon > 0, \,  d \in \naturals, \, p \in [0,\infty),\]
 where $\vp=p$ is a scalar. Then Theorem \ref{thm_main_strong_tract2} yields the equivalent condition for exponential strong polynomial tractability:
@@
 \end{equation}
-In this case the optimal $p$ is the infimum of all $p$ for which the above condition holds.
+In this case, the optimal $p$ is the infimum of all $p$ for which the above condition holds.
 \end{example}
-\begin{example}[Exponential polynomial tractability]
-Let the tractability function, $T$,
-be defined by
-\[
- T(\varepsilon^{-1},d,\vp)=\left[\max\{1,\log(1+\varepsilon^{-1})\}\right]^p\, d^q, \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty)^2,
-\] where $\vp = (p,q)$. Then Theorem \ref{thm_main_tract2} yields  the equivalent condition for exponential polynomial tractability:
-\begin{equation}\label{eq:exp_pt}
- \sup_{d\in\naturals}\, d^{-q} \sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p} < \infty  \text{ for some } p,q \ge 0, L_{(p,q)} \in \naturals.
-\end{equation}
-\end{example}
-
-\peter{
+%\peter{TODO: Include a statement on optimality like in Ex. 2.}
 In the paper \cite{KriWoz19a}, the authors derived conditions equivalent to exponential strong polynomial tractability and exponential polynomial tractability, respectively.
-These conditions read (with notation adapted to our present paper) as follows:
+These conditions read (with notation slightly adapted to our present paper) as follows:
 \begin{itemize}
@@
 
-\fred{Fred: Where does $p$ and/or $q$ come in conditions \eqref{eq:KW_exp_spt} and \eqref{eq:KW_exp_pt}?} \kachi{[Kachi: I believe for \eqref{eq:KW_exp_spt} $p$ corresponds to $\tau$ and for \eqref{eq:KW_exp_pt} $p$ corresponds to $\tau_2$ and $q$ corresponds to both $\tau_1$ and $\tau_3$.]}
-
-Firstly, it should be noted that our condition \eqref{eq:exp_spt} is easier to check in practice than condition \eqref{eq:KW_exp_spt}.
-Since in \eqref{eq:KW_exp_spt} the summation indices $i$ show up in the exponents of the summands, we need the exact ordering of the eigenvalues $\lambda_{i,d}$, whereas in \eqref{eq:exp_spt} we only have a summation of the values of $1/T(\lambda_{i,d}^{-1},d,\vp)$, and the exact order of the eigenvalues can be neglected.
+\peter{Firstly, we remark that the role of $L_p$ in  \eqref{eq:exp_spt} corresponds to that of $C$ in \eqref{eq:KW_exp_spt}.
+Moreover, $q$ in \eqref{eq:exp_pt} has a similar role as $\tau_1$ and $\tau_3$ in \eqref{eq:KW_exp_pt} (i.e., \eqref{eq:KW_exp_pt} is slightly more precise than \eqref{eq:exp_pt} regarding the exponents of $d$, but this is just a minor difference); furthermore $L_{(p,q)}$ in \eqref{eq:exp_pt} corresponds to $C$ in \eqref{eq:KW_exp_pt}.}
+
+Secondly, it should be noted that our condition \eqref{eq:exp_spt} is easier to check in practice than condition \eqref{eq:KW_exp_spt}.
+Since in \eqref{eq:KW_exp_spt} the summation indices $i$ show up in the exponents of the summands, we need the exact ordering of the \peter{singular values} $\lambda_{i,d}$, whereas in \eqref{eq:exp_spt} we only have a summation of the values of $1/T(\lambda_{i,d}^{-1},d,\vp)$, and the exact order of the \peter{singular values} can be neglected.
 A similar
@@
 
-Secondly, we would like to show that the conditions \eqref{eq:exp_spt} and \eqref{eq:KW_exp_spt}, as well as the conditions \eqref{eq:exp_pt} and \eqref{eq:KW_exp_pt} are indeed equivalent.
-We do this for the latter two conditions, i.e., for the conditions on exponential polynomial tractability.
-The case of exponential strong polynomial tractability is simpler and can be treated analogously.
-We thus show equivalence of \eqref{eq:exp_pt} and \eqref{eq:KW_exp_pt} in the following.
-
-Let us first assume that \eqref{eq:KW_exp_pt} holds, i.e.,
-\[
-M:=\sup_{d\in\naturals} d^{-\tau_1} \sum_{i=\lceil C d^{\tau_3} \rceil}^{\infty} \lambda_{i,d}^{i^{-\tau_2}} < \infty
-\]
-for some $\tau_1,\tau_3\ge 0$ and $\tau_2, C>0$. Here, $M$ and other constants above may depend on $\tau_1$, $\tau_2$, and $\tau_3$.
-Define $B_d$ as the set of indices that are contained in the above sum and for which the terms in the sum are relatively large:
-\[
-B_d:=\left\{i\in\naturals \colon i\ge \left\lceil Cd^{\tau_3}\right\rceil\quad\mbox{and}\quad
-\lambda_{i,d}^{i^{-\tau_2}}>\frac{1}{e}\right\}.
-\]
-Due to our assumption, we see that $\card(B_d) < e\,M\,d^{\tau_1}$ and $\card(B_d)\le \lfloor e\,M\,d^{\tau_1} \rfloor$. 
-Suppose now that $i\ge \lceil C d^{\tau_3}\rceil$ but $i\not\in B_d$, which means that the term in the above sum is relatively small:
-\begin{equation}
-    \lambda_{i,d}^{i^{-\tau_2}} \le \frac{1}{e} \iff \log (\lambda_{i,d}^{-1})\ge i^{\tau_2}.
-\label{eq:logandi}
-\end{equation}
-
-Now, choose $p> 1/\tau_2$, $q=\max\{\tau_1,\tau_3\}$, and $L_{(p,q)}=\max\{C, e\, M\}$, which implies that $\lceil L_{(p,q)} d^{q}\rceil \ge e\, M\, d^{\tau_1}$.
-Then, for any $d\in\naturals$, the desired sum in \eqref{eq:exp_pt} can be bounded by splitting it into the sum of the larger terms and the sum of the smaller terms:
-\begin{align*}
-\MoveEqLeft{d^{-q} \sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p}} \\
-&=d^{-q} \sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\in B_d}}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p} + d^{-q} \sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\not\in B_d}}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p}\\
-&\le d^{-q} e\, M\, d^{\tau_1} + d^{-q}\sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\not\in B_d}}^\infty \frac{1}{[\log (\lambda_{i,d}^{-1})]^p}\\
-&\le e\, M + d^{-q}\sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\not\in B_d}}^\infty \frac{1}{i^{\tau_2 p}} \qquad \text{by \eqref{eq:logandi}}\\
-&\le  e\, M + \zeta (\tau_2 p).
-\end{align*}
-Since $p$ was chosen to be strictly larger than $1/\tau_2$, it follows that the latter expression is finite and its value is independent of $d$. Therefore, Condition \eqref{eq:exp_pt} holds.
-
-Conversely, let us now assume that Condition \eqref{eq:exp_pt} holds for some $p> 0$ and $q\ge 0$ that are assumed to be fixed.
-All constants in this part of the proof may depend on $p$ and $q$.
-We will show next that this implies Condition \eqref{eq:KW_exp_pt}.
-Indeed, due to \eqref{eq:exp_pt}, there exist constants $M > 1$ and $L_{(p,q)}>0$ such that for all $d\in\naturals$,
-\[
-d^{-q}
-\sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p} \le M,
-\]
-which is equivalent to
-\[
-\sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p} \le d^q M.
-\]
-Similarly to the proof of the sufficient condition in Theorem \ref{thm_main_strong_tract2}, we see that for any $n > \lceil L_{(p,q)} d^{q}\rceil $,
-\[
-\frac{1}{T(\lambda_{n+1,d}^{-1},1,\vp)} \le \frac{1}{n-\lceil L_{(p,q)} d^{q}\rceil +1 }
-\sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty  \frac{1}{T(\lambda_{i,d}^{-1},1,\vp)}
-\le \frac{d^q M}{n-\lceil L_{(p,q)} d^{q}\rceil +1 }.
-\]
-This inequality implies for our specific choice of $T$ that
-\[
-\frac{n}{d^q M}-\frac{L_{(p,q)}}{M}\le\frac{n-\lceil L_{(p,q)} d^{q}\rceil +1 }{d^q M} \le [\max\{1,\log(1+\lambda_{n+1,d}^{-1})\}]^p
-\le [1 + \log(1+\lambda_{n+1,d}^{-1})]^p.
-\]
-Since both $L_{(p,q)}$ and $M$ in the latter chain of inequalities are independent of $d$ and $n$, there
-exists a positive constant $K$ such that
-\[
-\frac{n}{d^q K} \le [1 + \log(1+\lambda_{n+1,d}^{-1})]^p\quad \forall n > \lceil L_{(p,q)} d^{q}\rceil,
-\]
-which implies
-\[
-\frac{n^{1/p}}{d^{q/p} K^{1/p}} -1 \le \log(1+\lambda_{n+1,d}^{-1})\quad \forall n > \lceil L_{(p,q)} d^{q}\rceil.
-\]
-This, in turn, implies the existence of another constant $\widetilde{K}>0$ such that
-\[
-\lambda_{n,d} \le \exp\left(-\frac{n^{1/p}}{\widetilde{K}^{1/p} d^{q/p}}\right)
-\quad \forall n > \lceil L_{(p,q)} d^{q}\rceil-1,
-\]
-which is essentially the situation described in \cite[p.~118]{KriWoz19a}. We can then choose $\tau_2\in (0,1/p)$,
-and proceed as in \cite{KriWoz19a} to obtain
-\[
-\sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty \lambda_{i,d}^{i^{-\tau_2}}=\mathcal{O}(d^{q/(1-\tau_2 p)}),
-\]
-with the implied factor in the $\mathcal{O}$-notation independent of $d$. Then, we can choose $\tau_1=q/(1-\tau_2 p)$ and $\tau_3=q$ and see that \eqref{eq:KW_exp_pt} holds.
-
-This concludes the proof of the equivalence of \eqref{eq:exp_pt} and \eqref{eq:KW_exp_pt}.
-
-\bigskip
-
-[PLEASE CHECK CAREFULLY.]}
-
-\kachi{In the following example, we provide a brief summary of the above examples \peter{[What does ``these'' refer to?]} of tractability.
-We would like to emphasize that this example was previously known (see, e.g., \cite{GW06}) where in this case, the roles of $\varepsilon^{-1}$ and $d$ are separated.
-In order to accomplish this, we will first define two functions $\phi$ and $\psi$ with positive values that are increasing in both of their arguments which will allow to take into account a variety of possible exponents of $\varepsilon^{-1}$ and $d$.
-%To do this, we introduce two positive-value functions that are increasing in both arguments so as to take possibly different exponents of $\varepsilon^{-1}$ and $d$.
-The equivalent conditions for this example are assumed to \peter{[Why ``are assumed to?'']} take the same form as those in Theorems \ref{thm_main_strong_tract2} and \ref{thm_main_tract2}.}
+\peter{The following proposition states that the conditions \eqref{eq:exp_spt} and \eqref{eq:KW_exp_spt}, as well as the conditions \eqref{eq:exp_pt} and \eqref{eq:KW_exp_pt} are indeed equivalent. 
+The proof of this result is deferred to the appendix, where we will prove this statement for the latter two conditions, i.e., for the conditions on exponential polynomial tractability.
+The case of exponential strong polynomial tractability is not explicitly included, as it is actually simpler and can be treated analogously.
+\begin{proposition}\label{prop:equiv_conditions}
+The conditions \eqref{eq:exp_spt} and \eqref{eq:KW_exp_spt} are equivalent. Furthermore, the conditions \eqref{eq:exp_pt} and \eqref{eq:KW_exp_pt} are equivalent.
+\end{proposition}
+}
+In the following example, we provide a brief summary of the above examples of tractability.
+We would like to emphasize that this example was previously known (see, e.g., \cite{GW06}) where in this case the roles of $\varepsilon^{-1}$ and $d$ are separated.
+In order to accomplish this, we will first define two functions $\phi$ and $\psi$ with positive values that are increasing in both of their arguments which will allow to take into account a variety of possible exponents of $\varepsilon^{-1}$ and $d$ \peter{[Is this really what we would like to express in this context?]}.
+The equivalent conditions for this example take the same form as those in Theorems \ref{thm_main_strong_tract2} and \ref{thm_main_tract2}.
 
@@
 
-We say that a problem is $T$-separable tractable \peter{[PETER: I am wondering if ``$T$-separably tractable'' is better?
-But obviously, you know that better than me.]} with parameter $\vp$ iff there exists a positive constant $C_{\vp}$ which does not depend on $\varepsilon$ and $d$ such that
+We say that a problem is \peter{$T$-separably} tractable with parameter $\vp$ iff there exists a positive constant $C_{\vp}$ which does not depend on $\varepsilon$ and $d$ such that
 \[
@@
 \]
-A problem is strongly $T$-separable tractable with parameter $\vp$ iff the information complexity is independent of $d$, that is, there exists a positive constant $C_{\vp}$ which again does not depend on $\varepsilon$ and $d$ such that
+A problem is strongly \peter{$T$-separably} tractable with parameter $\vp$ iff the information complexity is independent of $d$, that is, there exists a positive constant $C_{\vp}$ which again does not depend on $\varepsilon$ and $d$ such that
 \[
@@
 \]
-since there are an infinite number of positive eigenvalues. Furthermore, we have that $\phi(\cdot,p)$ is non-decreasing hence we define the following limit
+since there are an infinite number of positive \peter{singular values}. Furthermore, we have that $\phi(\cdot,p)$ is non-decreasing, hence we define the following limit
 \[
@@
 \end{example}
-\kachi{Next, we introduce a generalized \peter{[what do we mean by ``summarized''?]} notion of tractability.
+\kachi{Next, we introduce another notion of tractability called \emph{non-separable tractability}. See \cite{GW08}, which is probably where the term ``non-separable tractability" was first introduced.
 In the following, we will define two functions $\hat{\phi}$ and $\hat{\psi}$ that take the roles of $\varepsilon^{-1}$ and $d$.
-As will be seen below, this tractability function is equivalent \peter{[[I am not sure it is equivalent.]]} to the so-called \emph{quasi-polynomial tractability}.}
+As will be seen below, this kind of tractability function \peter{includes the special case} of the so-called \emph{quasi-polynomial tractability}.}
 \
@@
 \]  with non-decreasing functions $\hat{\phi} : (0,\infty) \to (0,\infty)$ and $\hat{\psi} : \naturals \to (0,\infty)$.
-We say that a problem is non-separable tractable with scalar parameter $p$ iff there exists a positive $C_{p}$ such that
+We say that a problem is \peter{non-separably} tractable with scalar parameter $p$ iff there exists a positive $C_{p}$ such that
 
@@
 \end{example}
-For $\hat{\phi}$ and $\hat{\psi}$ of special form, the condition above can be simplified further as in the following two examples of non-separable tractability.
-\kachi{We first define the notion of quasi-polynomial tractability as in \cite{GneWoz11a}.
-\begin{definition}
-     A problem is \emph{quasi-polynomially tractable (QPT)} if there exist two constants $C$, $p > 0$, such that
-\begin{equation}\label{expqpt}
-    \comp(\varepsilon,d) \leq C\exp[p(1+\log(\varepsilon^{-1}))(1+\log(d))]
-\end{equation}
-for all $\varepsilon \in (0,1]$ and $d\in\mathbb{N}$.
-\end{definition}
-Note that the following examples are given below such that they equivalent to the definition in \cite{GneWoz11a}.
-}
+For $\hat{\phi}$ and $\hat{\psi}$ of special form, the condition above can be simplified further as in the following two \peter{special cases} of non-separable tractability.
+%\kachi{We first define the notion of quasi-polynomial tractability as in \cite{GneWoz11a}.
+%\begin{definition}
+%     A problem is \emph{quasi-polynomially tractable (QPT)} if there exist two constants $C$, $p > 0$, such that
+%\begin{equation}\label{expqpt}
+  %  \comp(\varepsilon,d) \leq C\exp[p(1+\log(\varepsilon^{-1}))(1+\log(d))]
+%\end{equation}
+%for all $\varepsilon \in (0,1]$ and $d\in\mathbb{N}$.
+%\end{definition}
+%Note that the following examples are given below such that they equivalent to the definition in \cite{GneWoz11a}.
+
+%\peter{[We should think about whether it makes sense to introduce Def. 3 and Example 7? Maybe just one of them is enough?]}
 
@@
  T(\varepsilon^{-1},d,p)= \exp[ p(1+\log(\max\{1,\varepsilon^{-1}\}))(1+\log (d))]  \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, p \in [0,\infty).
-\]
-This can be rewritten as
+\] We note that the choice of $T$ is equivalent to the definition in \cite{GneWoz11a}. This can be rewritten as
 \[
@@
 \[
- T(\varepsilon^{-1},d,\vp)= \exp [p(1+\log(\max\{1,\log(1+\varepsilon^{-1})\}))(1+\log (d))]  \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty),
-\] where in this case $\vp = p$ is a scalar. This can be rewritten as
-\[
-T(\varepsilon^{-1},d,\vp) = e^p(\max\{1,\log(1+\varepsilon^{-1})\})^{p(1+\log d)}d^p.
+ T(\varepsilon^{-1},d,\peter{p})= \exp [p(1+\log(\max\{1,\log(1+\varepsilon^{-1})\}))(1+\log (d))]  \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \peter{p} \in [0,\infty).
+\] This can be rewritten as
+\[
+T(\varepsilon^{-1},d,\peter{p}) = e^p(\max\{1,\log(1+\varepsilon^{-1})\})^{p(1+\log d)}d^p.
 \]
@@
 \begin{theorem}\label{thm:subhT}
-	Let $T$ be a tractability function as specified in \eqref{eq:Tspec} and satisfying \eqref{eq:Tconditions}.
-Moreover, let $\lim_{d \to \infty} T(\varepsilon^{-1},d,\vp) = \infty$ for all $\varepsilon > 0$, $\vp > \vzero$.
-The problem is sub-$h$-$T$ tractable if and only if
+	Let $T$ be a tractability function as specified in \eqref{eq:Tspec} and satisfying \eqref{eq:Tconditions}.  \peter{Moreover, assume that 
+    $\lim_{\varepsilon^{-1} + d \to \infty} T(\varepsilon^{-1},d,\vp) = \infty$
+    for all $\vp > \vzero$.}  The problem is sub-$h$-$T$ tractable if and only if
 	\[
@@
 \end{theorem}
+%\peter{[I am thinking that we need to assume slightly more in the hypothesis of the theorem, namely 
+%$$
+%\lim_{\varepsilon^{-1} + d \to \infty} T(\varepsilon^{-1},d,\vp) = \infty. 
+%$$
+%Why do I think so?
+Because it is not always true that $\lim_{\varepsilon \to 0} T(\varepsilon^{-1},d) = \infty$ for all $d \in \naturals$, and  $\lim_{d \to \infty} T(\varepsilon^{-1},d) = \infty$ for all $\varepsilon>0$ implly $\lim_{\varepsilon^{-1} + d \to \infty} T(\varepsilon^{-1},d) = \infty$.
+As a counter-example, let
+%$$
+%T(\varepsilon^{-1},d)=(d+\varepsilon^{-1})/\sqrt{d \varepsilon^{-1}}.
+%$$
+%Then $\lim_{\varepsilon \to 0} T(\varepsilon^{-1},d) = \infty$ for all $d \in \naturals$, and  $\lim_{d \to \infty} T(\varepsilon^{-1},d) = \infty$ for all $\varepsilon>0$ is fulfilled.
+However, if you choose $\varepsilon=1/d$ for all $d$, then for this particular $\varepsilon$ you always have $T(\varepsilon^{-1},d)=2$.]
+%}
+
 \begin{proof}
@@
 S_c \, h(cT(\lambda_{1,1}^{-1},1)) \, h(cT(\varepsilon^{-1},d))
-\rceil\qquad \forall c, \varepsilon > 0, \, d \in \naturals.
+\rceil\qquad \forall c, \varepsilon > 0, \, d \in \naturals
 \]
@@
 
-Since $S_c \ge 1/h(cT(\lambda_{1,1}^{-1},1))$ by \eqref{eq:Sclb}, it follows that $S_c \, h(cT(0,1)) \, h(cT(\varepsilon^{-1},d))  \ge 1$.
-Define $\widetilde{S} : = 2 S_c \, h(cT(\lambda_{1,1}^{-1},1))$, and note that $\widetilde{S}_c$ must also be finite for all $c > 0$.
+As $S_c \ge 1/h(cT(\lambda_{1,1}^{-1},1))$ by \eqref{eq:Sclb}, it follows that $S_c \, h(cT(0,1)) \, h(cT(\varepsilon^{-1},d))  \ge 1$.
+Define $\peter{\widetilde{S_c}} : = 2 S_c \, h(cT(\lambda_{1,1}^{-1},1))$, and note that $\widetilde{S}_c$ must also be finite for all $c > 0$.
 It follows that
@@
 \\
-&  \le  h^{-1}  (\widetilde{S}_c) + cT (\varepsilon^{-1},d),
+&  \le  h^{-1}  (\widetilde{S}_c) + cT (\varepsilon^{-1},d)
 \quad \forall c, \varepsilon > 0, \, d \in \naturals.
@@
 
-Since $\lim_{\varepsilon \to 0} T(\varepsilon^{-1},d) = \infty$ for all $d \in \naturals$ by \eqref{eq:Tlim}, and  $\lim_{d \to \infty} T(\varepsilon^{-1},d) = \infty$ by the hypothesis of this theorem, it follows that $\lim_{\varepsilon^{-1} + d \to \infty} T(\varepsilon^{-1},d) = \infty$.
-Therefore
+\peter{By the hypothesis of this theorem, $\lim_{\varepsilon^{-1} + d \to \infty} T(\varepsilon^{-1},d) = \infty$.}  Therefore
 \begin{equation*}
@@
 \frac{n^*(d,c)-1}{h(2cT(\lambda_{1,d}^{-1},d))}
-+ \sum_{i=1}^\infty \frac1{n^2}
++ \sum_{i=1}^\infty \frac1{\peter{i}^2}
 \right]
@@
   & \le \max \left \{
-		 \frac{ h(cT(V_c,d^*_c))}{h(2cT(\lambda_{1,d}^{-1},1))},
+		 \frac{ h(cT(V_c,d^*_c))}{\peter{1}},
   \sup_{d\in \{d^*_c+1, \ldots \}}  \,
@@
   \right \} \\
-  & = \max \left \{
-		 \frac{ h(cT(V_c,d^*_c))}{h(2cT(\lambda_{1,d}^{-1},1))},
-		 \frac{1}{h(cT(\lambda_{1,d}^{-1},d_c^*+1))}
-  \right \} \\
+%  & = \max \left \{
+%		 \frac{ h(cT(V_c,d^*_c))}{h(2cT(\lambda_{1,d}^{-1},1))},
+%		 \frac{1}{h(cT(\lambda_{1,d}^{-1},d_c^*+1))}
+%  \right \} \\
   & \le \max \left \{
@@
 	\[
-	T(\varepsilon^{-1},d,s,t) = \max(1,\varepsilon^{-1})^s + d^t, \quad \forall \varepsilon,s,t > 0, \, d \in \naturals, \qquad h(x) = \exp(x) \quad \forall x \ge 0.
+	T(\varepsilon^{-1},d,s,t) = \max(1,\varepsilon^{-1})^s + d^t \quad \forall \varepsilon,s,t > 0, \, d \in \naturals, \qquad h(x) = \exp(x) \quad \forall x \ge 0.
 	\]
@@
 	\]
-	The expression on the left is the notion of $(s,t)$-weak tractability introduced in \cite{SW15}, and the condition on the right was derived in \cite[Theorem 3.1]{WW17}.
+	The expression on the left is the notion of $(s,t)$-weak tractability introduced in \cite{SW15}, and the condition on the right was derived in \cite[Theorem 3.1]{WerWoz17a}.
 Weak tractability corresponds to $(s,t)=(1,1)$, and uniform weak tractability corresponds to the case when a problem is weakly tractable for all positive $s$ and $t$.
@@
 \]
-Since the sequence of eigenvalues $\lambda_{1,d}, \lambda_{2,d}, \ldots $ is non-increasing, we have
+Since the sequence of \peter{singular values} $\lambda_{1,d}, \lambda_{2,d}, \ldots $ is non-increasing, we have
 \begin{equation}\label{eq:lambda_K_strong4}
 \lambda_{\lfloor C_{\vp}\, T(\varepsilon^{-1},1,\vp)\rfloor +1,d}\le \varepsilon \qquad \forall \varepsilon > \theM(d), \ d \in \mathbb{N}.
+\peter{\quad [\mbox{why not write $\forall (\varepsilon^{-1}, d) \in \Omega$?}]}
 \end{equation}
@@
 \[
-i(\varepsilon,\vp)\le C_{\vp}\, T(\varepsilon^{-1},1,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,\vp),d}^{-1},1,\vp)+1, \qquad  \forall \varepsilon > \theM(d), \ d \in \mathbb{N},
+i(\varepsilon,\vp)\le C_{\vp}\, T(\varepsilon^{-1},1,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,\vp),d}^{-1},1,\vp)+1 \qquad  \forall \varepsilon > \theM(d), \ d \in \mathbb{N},\peter{\quad [\mbox{why not write $\forall (\varepsilon^{-1}, d) \in \Omega$?}]}
 \]
@@
 \[
-i\le  C_{\vp} T(\lambda_{i,d}^{-1},1,\vp)+1, \qquad \forall i\in \mathscr{I}_{d,\vp},  \ d \in \naturals.
+i\le  C_{\vp} T(\lambda_{i,d}^{-1},1,\vp)+1 \qquad \forall i\in \mathscr{I}_{d,\vp},  \ d \in \naturals.
 \]
@@
 \item If $\theUB(d) \ge L_{\tau\vp}$ and $\theM(d) >0$, then \eqref{eq:Mddef} implies that $\lambda_{\theUB(d)+1,d} \le \theM(d) < \lambda_{\theUB(d),d}$.
-Moreover, there must be some $\varepsilon^*$ satisfying $\theM(d) < \varepsilon^* < \lambda_{\theUB(d),d}$, such for which $\lambda_{i(\varepsilon^*,\vp)} \le \varepsilon^* < \lambda_{\theUB(d),d}$ by \eqref{eq:lambdaiep}.
+Moreover, there must be some $\varepsilon^*$ satisfying $\theM(d) < \varepsilon^* < \lambda_{\theUB(d),d}$, for which $\lambda_{i(\varepsilon^*,\vp)} \le \varepsilon^* < \lambda_{\theUB(d),d}$ by \eqref{eq:lambdaiep}.
 Because of the ordering of the singular values, this implies that  $i(\varepsilon^*,\vp) \ge \theUB(d)+1$.
-Since $i(\cdot,\vp)$ is nonincreasing, $i(\theM(b),\vp) \ge \theUB(d)+1$.
+Since $i(\cdot,\vp)$ is nonincreasing, $i(\theM(d),\vp) \ge \theUB(d)+1$.
 This means that $\theUB(d) \le i(\theM(d),\vp)-1$.  So, $\{L_{\tau\vp}, \ldots, \theUB(d)\} \subseteq \mathscr{I}_{d,\vp} \setminus \{1\}$.
@@
 \end{equation}
-If \eqref{eq:rest_tractiff} holds for some $\vp$, let $\widetilde{\cp}_{\textup{trct}} : = \{\vp^* : \eqref{eq:tractiff4} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty}) \}$.
+If \eqref{eq:rest_tractiff} holds for some $\vp$, let $\peter{\widetilde{\cp}_{\textup{rtrct}}} : = \{\vp^* : \peter{\eqref{eq:rest_tractiff}} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty}) \}$.
 Then $\cp_{\textup{rtrct}} = \widetilde{\cp}_{\textup{rtrct}}$, and the set of optimal  tractability parameters is
@@
 \]
-Since the sequence of eigenvalues $\lambda_{1,d}, \lambda_{2,d}, \ldots $ is non-increasing, we have
+Since the sequence of \peter{singular values} $\lambda_{1,d}, \lambda_{2,d}, \ldots $ is non-increasing, we have
 \begin{equation}\label{eq:rest_lambda_K4}
@@
  \forall \varepsilon > \theM(d),\ d \in \naturals.
+ \peter{\quad [\mbox{why not write $\forall (\varepsilon^{-1}, d) \in \Omega$?}]}
 \end{equation}
@@
 \[
-i(\varepsilon,d,\vp)\le C_{\vp}\, T(\varepsilon^{-1},d,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,d,\vp),d}^{-1},d,\vp)+1, \qquad \forall \varepsilon > \theM(d),\ d \in \naturals.
+i(\varepsilon,d,\vp)\le C_{\vp}\, T(\varepsilon^{-1},d,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,d,\vp),d}^{-1},d,\vp)+1 \qquad \forall \varepsilon > \theM(d),\ d \in \naturals.\peter{\quad [\mbox{why not write $\forall (\varepsilon^{-1}, d) \in \Omega$?}]}
 \]
@@
  \ge
-  \left[\frac{(i-1)}{C_{\vp}}\right]^\tau, \qquad \forall i\in \mathscr{I}_{d,\vp},  \ d \in \naturals, \\
+  \left[\frac{(i-1)}{C_{\vp}}\right]^\tau \qquad \forall i\in \mathscr{I}_{d,\vp},  \ d \in \naturals, \\
   \label{eq:rest_ineq}
  \frac{1}{T (\lambda_{i,d}^{-1},d,\tau \vp)} \le
-\frac{K_{\vp,\tau}\, C_{\vp}^\tau}{(i-1)^\tau},\qquad \forall i \in \mathscr{I}_{d,\vp} \setminus\{1\}, \ d \in \naturals .
+\frac{K_{\vp,\tau}\, C_{\vp}^\tau}{(i-1)^\tau}\qquad \forall i \in \mathscr{I}_{d,\vp} \setminus\{1\}, \ d \in \naturals .
 \end{gather}
@@
 \le
-\sup_{d\in\naturals} \sum_{i \in \mathscr{I}_{d,\vp} \setminus\{1\} } \frac{1}{T (\lambda_{i,d}^{-1},1, \tau \vp)} \\
+\sup_{d\in\naturals} \sum_{i \in \mathscr{I}_{d,\vp} \setminus\{1\} } \frac{1}{T (\lambda_{i,d}^{-1},\peter{d}, \tau \vp)} \\
 &  \le  K_{\vp,\tau}\, C_{\vp}^\tau
@@
 \zeta (\tau)
- < \infty \qquad \text{by \eqref{eq:rest_strong_ineq},}
+ < \infty \qquad \text{by \peter{\eqref{eq:rest_ineq}},}
 \end{align*}
@@
 
-\fred{Are there cases that we can discuss where we do not have (strong) tractability, but we do have (strong) tractability on a restricted domain, such as $(0,\infty) \times \{1, \ldots, d_{\max}] \cup (\varepsilon_{\min}^{-1},\infty) \times \naturals$?}
-
 \section{Discussion and Summary}
 
-\fred{Fred will draft something.
+We have shown that a number of proofs of equivalent conditions for (strong) tractability of various types can be unified into a handful of proofs.
+Even the arguments underlying these handful of proofs are quite similar and could be consolidated even further.
+However some questions remain for further work:
 \begin{itemize}
-\item Are there cases of $T$ that do not correspond to known tractability measures? (Kachi)
-\item Restricted domain? (Fred)
-\end{itemize}}
+    \item What interesting cases of $T$ do not correspond to known tractability measures? 
+    \item What interesting cases are there where there is no (strong) tractability on an unrestricted domain, but there is (strong) tractability on a nontrivial restricted domain, such as $(0,\infty) \times \{1, \ldots, d_{\max}] \cup (\varepsilon_{\min}^{-1},\infty) \times \naturals$?
+    \item For Hilbert spaces and solution operators, $\{\SOL_d : \cf_d \to \cg_d\}_{d \in \naturals}$, of tensor product form, how can the equivalent conditions for (strong) tractability be simplified, even when $T(a_1 \cdots a_d,d,\vp) \ne T_1(a_1,d,\vp)\cdots T_1(a_d,d,\vp)$ for some $T_1$?
+    \item For information complexity defined over cones of functions rather than balls (see e.g., \cite{DinHic20a,DinEtal20a}), what can be said about equivalent conditions for (strong) tractability?
+\end{itemize}
 
 \section{Acknowledgments}
-\kachi{The authors gratefully acknowledge the contributions of H. Wo\'{z}niakowski and E. Novak. P. Kritzer acknowledges the support of the Austrian Science Fund, Project ---, which is part of the
-Special Research Program “Quasi-Monte Carlo Methods: Theory and Applications”.}
-
-Thank Henryk and Erich.
+The authors gratefully acknowledge the fruitful discussions with Henryk Wo\'{z}niakowski and Erich Novak.
+Fred Hickernell acknowledges support by the United States National Science Foundation under Award No.\ 2316011.
+Peter Kritzer was supportedd by the Austrian Science Fund (FWF) Project P34808.
+For the purpose of open access, the authors have applied a CC BY public copyright licence to any author accepted manuscript version arising from this submission.
 
@@
 
+\peter{
+\section*{Appendix}
+
+We give the proof of Proposition \ref{prop:equiv_conditions} here.
+\begin{proof}[Proposition 1]
+We will give the proof of equivalence of the conditions \eqref{eq:exp_pt} and \eqref{eq:KW_exp_pt}.
+The proof of the equivalence of \eqref{eq:exp_spt} and \eqref{eq:KW_exp_spt} is analogous and simpler (actually, the latter proof can be seen as a special case of the former, by assuming all exponents of $d$ to be zero).
+
+Let us first assume that \eqref{eq:KW_exp_pt} holds, i.e.,
+\[
+M:=\sup_{d\in\naturals} d^{-\tau_1} \sum_{i=\lceil C d^{\tau_3} \rceil}^{\infty} \lambda_{i,d}^{i^{-\tau_2}} < \infty
+\]
+for some $\tau_1,\tau_3\ge 0$ and $\tau_2, C>0$. Here, $M$ and other constants above may depend on $\tau_1$, $\tau_2$, and $\tau_3$.
+Define $B_d$ as the set of indices that are contained in the above sum and for which the terms in the sum are relatively large:
+\[
+B_d:=\left\{i\in\naturals \colon i\ge \left\lceil Cd^{\tau_3}\right\rceil\quad\mbox{and}\quad
+\lambda_{i,d}^{i^{-\tau_2}}>\frac{1}{e}\right\}.
+\]
+Due to our assumption, we see that $\card(B_d) < e\,M\,d^{\tau_1}$ and $\card(B_d)\le \lfloor e\,M\,d^{\tau_1} \rfloor$. 
+Suppose now that $i\ge \lceil C d^{\tau_3}\rceil$ but $i\not\in B_d$, which means that the term in the above sum is relatively small:
+\begin{equation}
+    \lambda_{i,d}^{i^{-\tau_2}} \le \frac{1}{e} \iff \log (\lambda_{i,d}^{-1})\ge i^{\tau_2}.
+\label{eq:logandi}
+\end{equation}
+
+Now, choose $p> 1/\tau_2$, $q=\max\{\tau_1,\tau_3\}$, and $L_{(p,q)}=\max\{C, e\, M\}$, which implies that $\lceil L_{(p,q)} d^{q}\rceil \ge e\, M\, d^{\tau_1}$.
+Then, for any $d\in\naturals$, the desired sum in \eqref{eq:exp_pt} can be bounded by splitting it into the sum of the larger terms and the sum of the smaller terms:
+\begin{align*}
+\MoveEqLeft{d^{-q} \sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p}} \\
+&=d^{-q} \sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\in B_d}}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p} + d^{-q} \sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\not\in B_d}}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p}\\
+&\le d^{-q} e\, M\, d^{\tau_1} + d^{-q}\sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\not\in B_d}}^\infty \frac{1}{[\log (\lambda_{i,d}^{-1})]^p}\\
+&\le e\, M + d^{-q}\sum_{\substack{i=\lceil L_{(p,q)} d^{q}\rceil\\ i\not\in B_d}}^\infty \frac{1}{i^{\tau_2 p}} \qquad \text{by \eqref{eq:logandi}}\\
+&\le  e\, M + \zeta (\tau_2 p).
+\end{align*}
+Since $p$ was chosen to be strictly larger than $1/\tau_2$, it follows that the latter expression is finite and its value is independent of $d$. Therefore, Condition \eqref{eq:exp_pt} holds.
+
+Conversely, let us now assume that Condition \eqref{eq:exp_pt} holds for some $p> 0$ and $q\ge 0$ that are assumed to be fixed.
+All constants in this part of the proof may depend on $p$ and $q$.
+We will show next that this implies Condition \eqref{eq:KW_exp_pt}.
+Indeed, due to \eqref{eq:exp_pt}, there exist constants $M > 1$ and $L_{(p,q)}>0$ such that for all $d\in\naturals$,
+\[
+d^{-q}
+\sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p} \le M,
+\]
+which is equivalent to
+\[
+\sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p} \le d^q M.
+\]
+Similarly to the proof of the sufficient condition in Theorem \ref{thm_main_strong_tract2}, we see that for any $n > \lceil L_{(p,q)} d^{q}\rceil $,
+\[
+\frac{1}{T(\lambda_{n+1,d}^{-1},1,\vp)} \le \frac{1}{n-\lceil L_{(p,q)} d^{q}\rceil +1 }
+\sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty  \frac{1}{T(\lambda_{i,d}^{-1},1,\vp)}
+\le \frac{d^q M}{n-\lceil L_{(p,q)} d^{q}\rceil +1 }.
+\]
+This inequality implies for our specific choice of $T$ that
+\[
+\frac{n}{d^q M}-\frac{L_{(p,q)}}{M}\le\frac{n-\lceil L_{(p,q)} d^{q}\rceil +1 }{d^q M} \le [\max\{1,\log(1+\lambda_{n+1,d}^{-1})\}]^p
+\le [1 + \log(1+\lambda_{n+1,d}^{-1})]^p.
+\]
+Since both $L_{(p,q)}$ and $M$ in the latter chain of inequalities are independent of $d$ and $n$, there
+exists a positive constant $K$ such that
+\[
+\frac{n}{d^q K} \le [1 + \log(1+\lambda_{n+1,d}^{-1})]^p\quad \forall n > \lceil L_{(p,q)} d^{q}\rceil,
+\]
+which implies
+\[
+\frac{n^{1/p}}{d^{q/p} K^{1/p}} -1 \le \log(1+\lambda_{n+1,d}^{-1})\quad \forall n > \lceil L_{(p,q)} d^{q}\rceil.
+\]
+This, in turn, implies the existence of another constant $\widetilde{K}>0$ such that
+\[
+\lambda_{n,d} \le \exp\left(-\frac{n^{1/p}}{\widetilde{K}^{1/p} d^{q/p}}\right)
+\quad \forall n > \lceil L_{(p,q)} d^{q}\rceil-1,
+\]
+which is essentially the situation described in \cite[p.~118]{KriWoz19a}. We can then choose $\tau_2\in (0,1/p)$,
+and proceed as in \cite{KriWoz19a} to obtain
+\[
+\sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty \lambda_{i,d}^{i^{-\tau_2}}=\mathcal{O}(d^{q/(1-\tau_2 p)}),
+\]
+with the implied factor in the $\mathcal{O}$-notation independent of $d$. Then, we can choose $\tau_1=q/(1-\tau_2 p)$ and $\tau_3=q$ and see that \eqref{eq:KW_exp_pt} holds.
+
+This concludes the proof of the equivalence of \eqref{eq:exp_pt} and \eqref{eq:KW_exp_pt}. \qed
+
+\end{proof}
+}
+
 \end{document}
+z

### 2023-09-21 Older_versions/GeneralizedTractability2023July17.tex
Updates from Overleaf

--- 2023-07-20 GeneralizedTractability2023July17.tex
@@
 where $\comp(\varepsilon,d)$ is the number of linear functionals required by the best admissible algorithm to satisfy the error criterion \eqref{eq:errcrit}.
-By definition, the \kachi{information }complexity is non-decreasing  as $\varepsilon$ tends to zero.
+By definition, the information complexity is non-decreasing  as $\varepsilon$ tends to zero.
 We also expect it to be non-decreasing as $d$ tends to infinity since $d$ is typically the number of variables for the functions in $\cf_d$.
@@
 \]
-\kachi{[KACHI: I have questions regarding $\vp$.]}
+
 Furthermore, the set of optimal $(p,q)$ is a subset of
@@
 \[
- T(\varepsilon^{-1},d,\vp)= [\max\{1,\log(1+\varepsilon^{-1})\}]^{\vp}, \quad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty),
+ T(\varepsilon^{-1},d,\vp)= [\max\{1,\log(1+\varepsilon^{-1})\}]^{\vp} \quad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty),
 \]
@@
 \[
- T(\varepsilon^{-1},d,\vp)=\left[\max\{1,\log(1+\varepsilon^{-1})\}\right]^p\, d^q, \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty)^2,
+ T(\varepsilon^{-1},d,\vp)=\left[\max\{1,\log(1+\varepsilon^{-1})\}\right]^p\, d^q \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty)^2,
 \] where $\vp = (p,q)$. Then Theorem \ref{thm_main_tract2} yields  the equivalent condition for exponential polynomial tractability:
@@
 \[
-i(\varepsilon,\vp)\le C_{\vp}\, T(\varepsilon^{-1},1,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,\vp),d}^{-1},1,\vp)+1, \qquad  \forall \varepsilon > \theM(d), \ d \in \mathbb{N},
+i(\varepsilon,\vp)\le C_{\vp}\, T(\varepsilon^{-1},1,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,\vp),d}^{-1},1,\vp)+1 \qquad  \forall \varepsilon > \theM(d), \ d \in \mathbb{N},
 \]
@@
 \[
-i(\varepsilon,d,\vp)\le C_{\vp}\, T(\varepsilon^{-1},d,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,d,\vp),d}^{-1},d,\vp)+1, \qquad \forall \varepsilon > \theM(d),\ d \in \naturals.
+i(\varepsilon,d,\vp)\le C_{\vp}\, T(\varepsilon^{-1},d,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,d,\vp),d}^{-1},d,\vp)+1 \qquad \forall \varepsilon > \theM(d),\ d \in \naturals.
 \]
@@
 \end{document}
+z

### 2023-11-15 GeneralizedTractability2023Sept21.tex
Updates from Overleaf

--- 2023-09-21 GeneralizedTractability2023August10.tex
@@
 
-\title{A Unified Treatment of Tractability for Approximation Problems Defined on Hilbert Spaces}
+\title{A Unified Treatment of Tractability for \\ Approximation Problems Defined on Hilbert Spaces}
 
@@
 
-%The non-decreasing ordering of the eigenvalues for each $d$ facilitates the proof of conditions for tractability, but our conditions do not depend on the ordering \peter{[PETER: is that really the case?]}.
-
 We make the technical assumption that $\SOL_d$ is a compact operator.
 This implies (see, e.g., \cite{NovWoz08a}) that $\lambda_{i,d}$ converges to zero as $i$ tends to infinity for every $d$, which in turn implies that the problem is solvable by suitable algorithms.
-To avoid trivial cases, we assume that there are an infinite number of positive eigenvalues for every $d$.
+To avoid trivial cases, we assume that there are an infinite number of positive singular values for every $d$.
 
@@
 \]
-This means that, essentially, in the tractability analysis below, all criteria would be normalized by the first \peter{singular value} $\lambda_{1,d}$.
+This means that, essentially, in the tractability analysis below, all criteria would be normalized by the first singular value $\lambda_{1,d}$.
 For the sake of brevity and clarity of notation, we restrict ourselves to the absolute error criterion here, but presumably analogous results hold for the normalized setting.
@@
 To our understanding, however, these references mainly focus on the special case of tensor product problems, a restriction we do not make.
-Moreover, the conditions for tractability derived there focus mostly on relating the properties of the function $T$ to the different varieties of tractability, and not in terms of sums of (functions of) the \peter{singular values} of a problem.
+Moreover, the conditions for tractability derived there focus mostly on relating the properties of the function $T$ to the different varieties of tractability, and not in terms of sums of (functions of) the singular values of a problem.
 Hence, the present paper adds to what is presently known on this subject.
@@
 
-\Cref{thm_main_strong_tract2,thm_main_tract2,thm_main_rest_strong_tract,thm_main_rest_tract} below all take the form
+\Cref{thm_main_strong_tract2,thm_main_tract2,thm_main_rest_strong_tract,thm_main_rest_tract} below all take the following form:  for a given $\thed \in \{1,d\}$ and $\Omega \subseteq (0,\infty) \times \mathbb{N}$,
 \begin{multline}
@@
     \comp(\varepsilon, d) \le  C_{\vp}\, T(\varepsilon^{-1},\thed,\vp) \quad \forall (\varepsilon^{-1},d) \in \Omega \\
-    \iff   \exists L_{\vp} \peter{>0} \text{ with }
+    \iff   \exists L_{\vp} >0 \text{ with }
     \sup_{d \in \naturals}
      \sum_{i = \lceil L_{\vp}\, T(0,\thed,\vp) \rceil}^{\theUB(d)} \frac{1}{T(\lambda^{-1}_{i,d},\thed,\vp)}< \infty, \\
-     \thed \in \{1,d\}, \ \theM(d) := \inf \{\varepsilon : (\varepsilon^{-1},d) \in \Omega \}, \
+     \text{where } \theM(d) := \inf \{\varepsilon : (\varepsilon^{-1},d) \in \Omega \}, \
      \theUB(d) := \begin{cases}
@@
 \end{multline}
-The differences in these theorems are in the choices of $\thed$ and $\Omega$.
+%The differences in these theorems are in the choices of $\thed$ and $\Omega$. 
 Although some of these theorems are special cases of others, we prove each separately to allow the reader to become familiar with the arguments used as additional layers of complexity are added.
@@
 A generalized notion of weak tractability is given in Section \ref{sec:subh}.
-In Section \ref{sec:restricted}, we consider \peter{tractability on} a restricted domain .
+In Section \ref{sec:restricted}, we consider tractability on a restricted domain, $\Omega$.
 
@@
 \end{equation}
-which implies that the problem is expected to be no easier by decreasing the tolerance, $\varepsilon$, or increasing the dimension, $d$\footnote{This is why we make $T$ a function of $\varepsilon^{-1}$ rather than of $\varepsilon$.} Furthermore, increasing $\vp$ allows for a possibly looser bound on the information complexity.
-Since there are an infinite number of positive \peter{singular values}, it also makes sense to assume that
+which implies that the problem is expected to be no easier by decreasing $\varepsilon$, the tolerance, or increasing $d$, the dimension\footnote{This is why we make $T$ a function of $\varepsilon^{-1}$ rather than of $\varepsilon$.}.
+Furthermore, increasing $\vp$ allows for a possibly looser bound on the information complexity.
+Since there are an infinite number of positive singular values, it also makes sense to assume that
 \begin{equation}\label{eq:Tlim}
@@
         \text{algebraic quasi-polynomial} &
-        \exp\{p(1+\log(\max\{1,\log(1 + \varepsilon^{-1})\})(1+\log(d))\} &
+        \exp\{p(1+\log(\max\{1, \varepsilon^{-1}\}))(1+\log(d))\} &
         \exp\{p(1+\log(d))\}\\
@@
 \end{multline}
-We note that the left side of the implication implies $n \ge N$ automatically since $n$ is an integer \peter{and} $n - N +1$ is assumed to be positive.
+We note that the left side of the implication implies $n \ge N$ automatically since $n$ is an integer and $n - N +1$ is assumed to be positive.
 
@@
 \]
-Since the sequence of \peter{singular values} $\lambda_{1,d}, \lambda_{2,d}, \ldots $ is non-increasing, we have
+Since the sequence of singular values $\lambda_{1,d}, \lambda_{2,d}, \ldots $ is non-increasing, we have
 \begin{equation}\label{eq:lambda_K_strong3}
@@
 \]
-Since the sequence of \peter{singular values} $\lambda_{1,d}, \lambda_{2,d}, \ldots $ is non-increasing, we have
+Since the sequence of singular values $\lambda_{1,d}, \lambda_{2,d}, \ldots $ is non-increasing, we have
 \begin{equation}\label{eq:lambda_K4}
@@
 \[
-\sup_{d\in\naturals}\,\, \sum_{i=\lceil \kachi{L_{\vp'}} T(0,d,\vp')\rceil}^\infty \frac{1}{T(\lambda_{i,d}^{-1},d, \vp')}
+\sup_{d\in\naturals}\,\, \sum_{i=\lceil L_{\vp'}T(0,d,\vp')\rceil}^\infty \frac{1}{T(\lambda_{i,d}^{-1},d, \vp')}
 \le
@@
 Next we show that if $\vp^* \in \widetilde{\cp}_{\textup{trct}}$, then $\vp^* \in \cp_{\textup{trct}}$.
-If \kachi{$\vp^* \in \widetilde{\cp}_{\textup{trct}}$}, then \eqref{eq:tractiff4}  holds for all $\vp \in (\vp^*,\vinfty)$.
+If $\vp^* \in \widetilde{\cp}_{\textup{trct}}$, then \eqref{eq:tractiff4}  holds for all $\vp \in (\vp^*,\vinfty)$.
 By the argument to prove the sufficient condition above, it follows that \eqref{eq:tract_def} must also hold for all $\vp \in (\vp^*,\vinfty)$.
@@
 %In this section, we illustrate Theorems \ref{thm_main_strong_tract2} and \ref{thm_main_tract2} for the types of tractability given in the table in Section \ref{sec:not}.
-In this section, we present six examples relating to Theorem \ref{thm_main_strong_tract2} and Theorem \ref{thm_main_tract2}, both of which were \peter{shown} in Section \ref{sec:spt}, for the various notions of tractability that are listed in Table \ref{tab:commonT}.
-In \peter{the} subsequent sections, we will continue to present various examples.
+In this section, we present six examples relating to Theorem \ref{thm_main_strong_tract2} and Theorem \ref{thm_main_tract2}, both of which were shown in Section \ref{sec:spt}, for the various notions of tractability that are listed in Table \ref{tab:commonT}.
+In the subsequent sections, we will continue to present various examples.
 
@@
 \[
- \sup_{d\in\naturals}\, d^{-q} \sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty \min\{1,\lambda_{i,d}^p\}  < \infty \text{ for some } p,q \ge 0, L_{(p,q)} \peter{>0}.
+ \sup_{d\in\naturals}\, d^{-q} \sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty \min\{1,\lambda_{i,d}^p\}  < \infty \text{ for some } p,q \ge 0, L_{(p,q)} >0.
 \]
@@
 
-Having defined the tractability function \peter{as above}, we will now examine a specific case where we always set $d=1$,i.e.,
+Having defined the tractability function as above, we will now examine a specific case where we always set $d=1$, i.e.,
 \[
@@
 where in this case $\vp=p$ is a scalar.
-
-%\peter{[But this is not what we discussed on Wednesday.
-The idea is that we use the same tractability function as for algebraic polynomial tractability, but consider the special case where we always set $d=1$,i.e., we use
-%\[
- %T(\varepsilon^{-1},1,\vp)= \max\{1,\varepsilon^{-p}\}\\qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \vp \in [0,\infty)^2,\]
-%as an upper bound on the information complexity.
-Then everything would correspond to our definitions of $T$-tractability and strong $T$-tractability.
-Kachi, can you please make this change here and also in Example 2?
-So, please make it clear that the tractability function for strong polynomial tractability is a specialization of the tractability function for polynomial tractability.]
-%}
 
@@
 \end{example}
-Next, we consider the exponential case where we replace $\varepsilon^{-1}$ by $\log(1+\varepsilon^{-1})$ and consider the same notions of tractability as for the algebraic case.
+Next, we study the exponential case where we replace $\varepsilon^{-1}$ by $\log(1+\varepsilon^{-1})$ and consider the same notions of tractability as for the algebraic case.
 \begin{example}[Exponential polynomial tractability]
@@
 \begin{equation}\label{eq:exp_pt}
- \sup_{d\in\naturals}\, d^{-q} \sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p} < \infty  \text{ for some } p,q \ge 0, L_{(p,q)} \peter{>0}.
+ \sup_{d\in\naturals}\, d^{-q} \sum_{i=\lceil L_{(p,q)} d^{q}\rceil}^\infty \frac{1}{[\max\{1,\log(1+\lambda_{i,d}^{-1})\}]^p} < \infty  \text{ for some } p,q \ge 0, L_{(p,q)} >0.
 \end{equation}
@@
 \[
-    \{(p^*,q^*) \in \widetilde{\cp}_{\textup{EXP-trct}} : (p^*,q^*) \notin [\widetilde{p},\infty) \times [\widetilde{q},\infty)\, \, \forall (\widetilde{p},\widetilde{q}) \in \widetilde{\cp}_{\textup{ALG-trct}}\setminus \{p^*,q^*\}  \}.
-\]
-Again, we will look at \peter{the} special case in which we always set $d=1$. In this case, we will define $T$ as follows.
+    \{(p^*,q^*) \in \widetilde{\cp}_{\textup{EXP-trct}} : (p^*,q^*) \notin [\widetilde{p},\infty) \times [\widetilde{q},\infty)\, \, \forall (\widetilde{p},\widetilde{q}) \in \widetilde{\cp}_{\textup{EXP-trct}}\setminus \{p^*,q^*\}  \}.
+\]
+Again, we will look at the special case in which we always set $d=1$. In this case, we will define $T$ as follows.
 \[
@@
 \end{example}
-%\peter{TODO: Include a statement on optimality like in Ex. 2.}
+
 In the paper \cite{KriWoz19a}, the authors derived conditions equivalent to exponential strong polynomial tractability and exponential polynomial tractability, respectively.
@@
 
-\peter{Firstly, we remark that the role of $L_p$ in  \eqref{eq:exp_spt} corresponds to that of $C$ in \eqref{eq:KW_exp_spt}.
-Moreover, $q$ in \eqref{eq:exp_pt} has a similar role as $\tau_1$ and $\tau_3$ in \eqref{eq:KW_exp_pt} (i.e., \eqref{eq:KW_exp_pt} is slightly more precise than \eqref{eq:exp_pt} regarding the exponents of $d$, but this is just a minor difference); furthermore $L_{(p,q)}$ in \eqref{eq:exp_pt} corresponds to $C$ in \eqref{eq:KW_exp_pt}.}
+Firstly, we remark that the role of $L_p$ in  \eqref{eq:exp_spt} corresponds to that of $C$ in \eqref{eq:KW_exp_spt}.
+Moreover, $q$ in \eqref{eq:exp_pt} has a similar role as $\tau_1$ and $\tau_3$ in \eqref{eq:KW_exp_pt} (i.e., \eqref{eq:KW_exp_pt} is slightly more precise than \eqref{eq:exp_pt} regarding the exponents of $d$, but this is just a minor difference); furthermore $L_{(p,q)}$ in \eqref{eq:exp_pt} corresponds to $C$ in \eqref{eq:KW_exp_pt}.
 
 Secondly, it should be noted that our condition \eqref{eq:exp_spt} is easier to check in practice than condition \eqref{eq:KW_exp_spt}.
-Since in \eqref{eq:KW_exp_spt} the summation indices $i$ show up in the exponents of the summands, we need the exact ordering of the \peter{singular values} $\lambda_{i,d}$, whereas in \eqref{eq:exp_spt} we only have a summation of the values of $1/T(\lambda_{i,d}^{-1},d,\vp)$, and the exact order of the \peter{singular values} can be neglected.
+Since in \eqref{eq:KW_exp_spt} the summation indices $i$ show up in the exponents of the summands, we need the exact ordering of the singular values $\lambda_{i,d}$, whereas in \eqref{eq:exp_spt} we only have a summation of the values of $1/T(\lambda_{i,d}^{-1},d,\vp)$, and the exact order of the singular values can be neglected.
 A similar
@@
 
-\peter{The following proposition states that the conditions \eqref{eq:exp_spt} and \eqref{eq:KW_exp_spt}, as well as the conditions \eqref{eq:exp_pt} and \eqref{eq:KW_exp_pt} are indeed equivalent. 
+The following proposition states that the conditions \eqref{eq:exp_spt} and \eqref{eq:KW_exp_spt}, as well as the conditions \eqref{eq:exp_pt} and \eqref{eq:KW_exp_pt}, are indeed equivalent. 
 The proof of this result is deferred to the appendix, where we will prove this statement for the latter two conditions, i.e., for the conditions on exponential polynomial tractability.
@@
 \end{proposition}
-}
+
 In the following example, we provide a brief summary of the above examples of tractability.
 We would like to emphasize that this example was previously known (see, e.g., \cite{GW06}) where in this case the roles of $\varepsilon^{-1}$ and $d$ are separated.
-In order to accomplish this, we will first define two functions $\phi$ and $\psi$ with positive values that are increasing in both of their arguments which will allow to take into account a variety of possible exponents of $\varepsilon^{-1}$ and $d$ \peter{[Is this really what we would like to express in this context?]}.
+In order to accomplish this, we will first define two functions $\phi$ and $\psi$ with positive values that are increasing in both of their arguments.
 The equivalent conditions for this example take the same form as those in Theorems \ref{thm_main_strong_tract2} and \ref{thm_main_tract2}.
@@
 
-We say that a problem is \peter{$T$-separably} tractable with parameter $\vp$ iff there exists a positive constant $C_{\vp}$ which does not depend on $\varepsilon$ and $d$ such that
+We say that a problem is $T$-separably tractable with parameter $\vp$ iff there exists a positive constant $C_{\vp}$ which does not depend on $\varepsilon$ and $d$ such that
 \[
@@
 \]
-A problem is strongly \peter{$T$-separably} tractable with parameter $\vp$ iff the information complexity is independent of $d$, that is, there exists a positive constant $C_{\vp}$ which again does not depend on $\varepsilon$ and $d$ such that
+A problem is strongly $T$-separably tractable with parameter $\vp$ iff the information complexity is independent of $d$, that is, there exists a positive constant $C_{\vp}$ which again does not depend on $\varepsilon$ and $d$ such that
 \[
@@
 \]
-since there are an infinite number of positive \peter{singular values}. Furthermore, we have that $\phi(\cdot,p)$ is non-decreasing, hence we define the following limit
+since there are an infinite number of positive singular values. Furthermore, we have that $\phi(\cdot,p)$ is non-decreasing, hence we define the following limit
 \[
@@
 \end{example}
-\kachi{Next, we introduce another notion of tractability called \emph{non-separable tractability}. See \cite{GW08}, which is probably where the term ``non-separable tractability" was first introduced.
+Next, we introduce another notion of tractability called \emph{non-separable tractability}. See \cite{GW08}, which is probably where the term ``non-separable tractability" was first introduced.
 In the following, we will define two functions $\hat{\phi}$ and $\hat{\psi}$ that take the roles of $\varepsilon^{-1}$ and $d$.
-As will be seen below, this kind of tractability function \peter{includes the special case} of the so-called \emph{quasi-polynomial tractability}.}
+As will be seen below, this kind of tractability function includes the special case of the so-called \emph{quasi-polynomial tractability}.
 \
@@
 \]  with non-decreasing functions $\hat{\phi} : (0,\infty) \to (0,\infty)$ and $\hat{\psi} : \naturals \to (0,\infty)$.
-We say that a problem is \peter{non-separably} tractable with scalar parameter $p$ iff there exists a positive $C_{p}$ such that
+We say that a problem is non-separably tractable with scalar parameter $p$ iff there exists a positive $C_{p}$ such that
 
@@
 \end{example}
-For $\hat{\phi}$ and $\hat{\psi}$ of special form, the condition above can be simplified further as in the following two \peter{special cases} of non-separable tractability.
-%\kachi{We first define the notion of quasi-polynomial tractability as in \cite{GneWoz11a}.
-%\begin{definition}
-%     A problem is \emph{quasi-polynomially tractable (QPT)} if there exist two constants $C$, $p > 0$, such that
-%\begin{equation}\label{expqpt}
-  %  \comp(\varepsilon,d) \leq C\exp[p(1+\log(\varepsilon^{-1}))(1+\log(d))]
-%\end{equation}
-%for all $\varepsilon \in (0,1]$ and $d\in\mathbb{N}$.
-%\end{definition}
-%Note that the following examples are given below such that they equivalent to the definition in \cite{GneWoz11a}.
-
-%\peter{[We should think about whether it makes sense to introduce Def. 3 and Example 7? Maybe just one of them is enough?]}
+For $\hat{\phi}$ and $\hat{\psi}$ of special form, the condition above can be simplified further as in the following two special cases of non-separable tractability.
 
@@
 \[
- T(\varepsilon^{-1},d,p)= \exp[ p(1+\log(\max\{1,\varepsilon^{-1}\}))(1+\log (d))]  \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, p \in [0,\infty).
+ T(\varepsilon^{-1},d,p)= \exp\{ p(1+\log(\max\{1,\varepsilon^{-1}\}))(1+\log (d))\}  \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, p \in [0,\infty).
 \] We note that the choice of $T$ is equivalent to the definition in \cite{GneWoz11a}. This can be rewritten as
 \[
-T(\varepsilon^{-1},d,p) = e^p(\max\{1,\varepsilon^{-1}\})^{p(1+\log d)}d^p.
-\]
-%Observe that the function $T$ is a function of $\max\{1,\varepsilon^{-1}\}$ and $d$ which are, polynomial or not exponential in powers of $\max\{1,\varepsilon^{-1}\}$ and $d$ \peter{[This sentence sounds a bit confusing to me---what exactly is meant by it?]}.
+T(\varepsilon^{-1},d,p) = e^p(\max\{1,\varepsilon^{-1}\})^{p(1+\log (d))}d^p.
+\]
+
 Then Theorem \ref{thm_main_tract2} yields the following equivalent condition for quasi-polynomial tractability in the algebraic case:
 \[
-\sup_{d\in\mathbb{N}}\,d^{-p}\sum_{i=\lceil L_p\,d^{p}\rceil} \frac{1}{\left(\max\{1,\lambda_{i,d}\}\right)^{p(1+\log d)}} < \infty \qquad \text{for some } p \geq 0, L_p >0.\]
+\sup_{d\in\mathbb{N}}\,d^{-p}\sum_{i=\lceil L_p\,d^{p}\rceil} \frac{1}{\left(\max\{1,\lambda_{i,d}\}\right)^{p(1+\log (d))}} < \infty \qquad \text{for some } p \geq 0, L_p >0.\]
 \end{example}
@@
 \[
- T(\varepsilon^{-1},d,\peter{p})= \exp [p(1+\log(\max\{1,\log(1+\varepsilon^{-1})\}))(1+\log (d))]  \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, \peter{p} \in [0,\infty).
+ T(\varepsilon^{-1},d,p)= \exp \{p(1+\log(\max\{1,\log(1+\varepsilon^{-1})\}))(1+\log (d))\}  \qquad \forall \varepsilon > 0, \,  d \in \naturals, \, p\in [0,\infty).
 \] This can be rewritten as
 \[
-T(\varepsilon^{-1},d,\peter{p}) = e^p(\max\{1,\log(1+\varepsilon^{-1})\})^{p(1+\log d)}d^p.
+T(\varepsilon^{-1},d,p) = e^p(\max\{1,\log(1+\varepsilon^{-1})\})^{p(1+\log (d))}d^p.
 \]
@@
 \[
-\sup_{d\in\mathbb{N}}\,d^{-p}\sum_{i=\lceil L_p\,d^{p}\rceil} \frac{1}{\left(\max\{1,\log(1+\lambda_{i,d}^{-1})\} \right)^{p(1+\log d)}}< \infty \quad \text{for some } p \geq 0, L_p >0.
+\sup_{d\in\mathbb{N}}\,d^{-p}\sum_{i=\lceil L_p\,d^{p}\rceil} \frac{1}{\left(\max\{1,\log(1+\lambda_{i,d}^{-1})\} \right)^{p(1+\log (d))}}< \infty \quad \text{for some } p \geq 0, L_p >0.
 \]
@@
 \begin{theorem}\label{thm:subhT}
-	Let $T$ be a tractability function as specified in \eqref{eq:Tspec} and satisfying \eqref{eq:Tconditions}.  \peter{Moreover, assume that 
+	Let $T$ be a tractability function as specified in \eqref{eq:Tspec} and satisfying \eqref{eq:Tconditions}.  Moreover, assume that 
     $\lim_{\varepsilon^{-1} + d \to \infty} T(\varepsilon^{-1},d,\vp) = \infty$
-    for all $\vp > \vzero$.}  The problem is sub-$h$-$T$ tractable if and only if
+    for all $\vp > \vzero$.  The problem is sub-$h$-$T$ tractable if and only if
 	\[
@@
 \end{theorem}
-%\peter{[I am thinking that we need to assume slightly more in the hypothesis of the theorem, namely 
-%$$
-%\lim_{\varepsilon^{-1} + d \to \infty} T(\varepsilon^{-1},d,\vp) = \infty. 
-%$$
-%Why do I think so?
-Because it is not always true that $\lim_{\varepsilon \to 0} T(\varepsilon^{-1},d) = \infty$ for all $d \in \naturals$, and  $\lim_{d \to \infty} T(\varepsilon^{-1},d) = \infty$ for all $\varepsilon>0$ implly $\lim_{\varepsilon^{-1} + d \to \infty} T(\varepsilon^{-1},d) = \infty$.
-As a counter-example, let
-%$$
-%T(\varepsilon^{-1},d)=(d+\varepsilon^{-1})/\sqrt{d \varepsilon^{-1}}.
-%$$
-%Then $\lim_{\varepsilon \to 0} T(\varepsilon^{-1},d) = \infty$ for all $d \in \naturals$, and  $\lim_{d \to \infty} T(\varepsilon^{-1},d) = \infty$ for all $\varepsilon>0$ is fulfilled.
-However, if you choose $\varepsilon=1/d$ for all $d$, then for this particular $\varepsilon$ you always have $T(\varepsilon^{-1},d)=2$.]
-%}
-
 \begin{proof}
@@
 As $S_c \ge 1/h(cT(\lambda_{1,1}^{-1},1))$ by \eqref{eq:Sclb}, it follows that $S_c \, h(cT(0,1)) \, h(cT(\varepsilon^{-1},d))  \ge 1$.
-Define $\peter{\widetilde{S_c}} : = 2 S_c \, h(cT(\lambda_{1,1}^{-1},1))$, and note that $\widetilde{S}_c$ must also be finite for all $c > 0$.
+Define $\widetilde{S_c}: = 2 S_c \, h(cT(\lambda_{1,1}^{-1},1))$, and note that $\widetilde{S}_c$ must also be finite for all $c > 0$.
 It follows that
@@
 
-\peter{By the hypothesis of this theorem, $\lim_{\varepsilon^{-1} + d \to \infty} T(\varepsilon^{-1},d) = \infty$.}  Therefore
+By the hypothesis of this theorem, $\lim_{\varepsilon^{-1} + d \to \infty} T(\varepsilon^{-1},d) = \infty$. Therefore
 \begin{equation*}
@@
 \end{equation}
-By varying $\varepsilon^{-1}$ in the interval $[\varepsilon^{-1}_{\max}(d,c),\infty)$,  the integer $n(\varepsilon,d,c)$ attains, \peter{by Assumption \eqref{eq:Tlim},} all values greater than or equal to $n^*(d,c)$.
+By varying $\varepsilon^{-1}$ in the interval $[\varepsilon^{-1}_{\max}(d,c),\infty)$,  the integer $n(\varepsilon,d,c)$ attains, by Assumption \eqref{eq:Tlim}, all values greater than or equal to $n^*(d,c)$.
 Thus, by \eqref{eq:nedcbound},
@@
 \frac{n^*(d,c)-1}{h(2cT(\lambda_{1,d}^{-1},d))}
-+ \sum_{i=1}^\infty \frac1{\peter{i}^2}
++ \sum_{i=1}^\infty \frac1{i^2}
 \right]
@@
   & \le \max \left \{
-		 \frac{ h(cT(V_c,d^*_c))}{\peter{1}},
+		 \frac{ h(cT(V_c,d^*_c))}{1},
   \sup_{d\in \{d^*_c+1, \ldots \}}  \,
@@
 \end{equation}
-%\peter{[I am wondering whether this makes sense if $E$ depends on $d$? Do Gnewuch and Wo\'{z}niakowski allow dependence of $E$ on $d$?]}
+
 A problem is
@@
 \end{equation}
-%\peter{[I have no idea why the $\mathcal{I}_d$ is not displayed correctly above.]}
+
 From the definition of $\theUB(d)$ it follows that $(\lambda_{i,d}^{-1},d) \in \Omega  \iff i \in \hI_d$, and
@@
 \]
-Since the sequence of \peter{singular values} $\lambda_{1,d}, \lambda_{2,d}, \ldots $ is non-increasing, we have
+Since the sequence of singular values $\lambda_{1,d}, \lambda_{2,d}, \ldots $ is non-increasing, we have
 \begin{equation}\label{eq:lambda_K_strong4}
-\lambda_{\lfloor C_{\vp}\, T(\varepsilon^{-1},1,\vp)\rfloor +1,d}\le \varepsilon \qquad \forall \varepsilon > \theM(d), \ d \in \mathbb{N}.
-\peter{\quad [\mbox{why not write $\forall (\varepsilon^{-1}, d) \in \Omega$?}]}
+\lambda_{\lfloor C_{\vp}\, T(\varepsilon^{-1},1,\vp)\rfloor +1,d}\le \varepsilon \qquad\forall (\varepsilon^{-1}, d) \in \Omega.
 \end{equation}
@@
 \[
-i(\varepsilon,\vp)\le C_{\vp}\, T(\varepsilon^{-1},1,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,\vp),d}^{-1},1,\vp)+1 \qquad  \forall \varepsilon > \theM(d), \ d \in \mathbb{N},\peter{\quad [\mbox{why not write $\forall (\varepsilon^{-1}, d) \in \Omega$?}]}
+i(\varepsilon,\vp)\le C_{\vp}\, T(\varepsilon^{-1},1,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,\vp),d}^{-1},1,\vp)+1 \qquad  \forall (\varepsilon^{-1}, d)\in \Omega,
 \]
@@
 \end{equation}
-If \eqref{eq:rest_tractiff} holds for some $\vp$, let $\peter{\widetilde{\cp}_{\textup{rtrct}}} : = \{\vp^* : \peter{\eqref{eq:rest_tractiff}} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty}) \}$.
+If \eqref{eq:rest_tractiff} holds for some $\vp$, let $\widetilde{\cp}_{\textup{rtrct}} : = \{\vp^* : \eqref{eq:rest_tractiff} \text{ holds }\forall \vp \in (\vp^*,\boldsymbol{\infty}) \}$.
 Then $\cp_{\textup{rtrct}} = \widetilde{\cp}_{\textup{rtrct}}$, and the set of optimal  tractability parameters is
@@
 \]
-Since the sequence of \peter{singular values} $\lambda_{1,d}, \lambda_{2,d}, \ldots $ is non-increasing, we have
+Since the sequence of singular values $\lambda_{1,d}, \lambda_{2,d}, \ldots $ is non-increasing, we have
 \begin{equation}\label{eq:rest_lambda_K4}
 	\lambda_{\lfloor C_{\vp}\, T(\varepsilon^{-1},d,\vp)\rfloor +1,d}\le \varepsilon \qquad
- \forall \varepsilon > \theM(d),\ d \in \naturals.
- \peter{\quad [\mbox{why not write $\forall (\varepsilon^{-1}, d) \in \Omega$?}]}
+ \forall (\varepsilon^{-1}, d) \in \Omega.
 \end{equation}
@@
 \[
-i(\varepsilon,d,\vp)\le C_{\vp}\, T(\varepsilon^{-1},d,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,d,\vp),d}^{-1},d,\vp)+1 \qquad \forall \varepsilon > \theM(d),\ d \in \naturals.\peter{\quad [\mbox{why not write $\forall (\varepsilon^{-1}, d) \in \Omega$?}]}
+i(\varepsilon,d,\vp)\le C_{\vp}\, T(\varepsilon^{-1},d,\vp)+1 \le C_{\vp} T(\lambda_{i(\varepsilon,d,\vp),d}^{-1},d,\vp)+1 \qquad \forall (\varepsilon^{-1}, d) \in \Omega.
 \]
@@
 \le
-\sup_{d\in\naturals} \sum_{i \in \mathscr{I}_{d,\vp} \setminus\{1\} } \frac{1}{T (\lambda_{i,d}^{-1},\peter{d}, \tau \vp)} \\
+\sup_{d\in\naturals} \sum_{i \in \mathscr{I}_{d,\vp} \setminus\{1\} } \frac{1}{T (\lambda_{i,d}^{-1},d, \tau \vp)} \\
 &  \le  K_{\vp,\tau}\, C_{\vp}^\tau
@@
 \zeta (\tau)
- < \infty \qquad \text{by \peter{\eqref{eq:rest_ineq}},}
+ < \infty \qquad \text{by \eqref{eq:rest_ineq}},
 \end{align*}
@@
 
-\section{Discussion and Summary}
-
-We have shown that a number of proofs of equivalent conditions for (strong) tractability of various types can be unified into a handful of proofs.
-Even the arguments underlying these handful of proofs are quite similar and could be consolidated even further.
-However some questions remain for further work:
+\section{Discussion and Further Work}
+
+We have shown that many proofs of equivalent conditions for (strong) tractability of various types can be unified into a handful of proofs.
+Even the arguments underlying these handful are quite similar and could be consolidated even further.
+This unification simplifies our understanding of these equivalent conditions and spotlights the key ideas about what makes a class of problems hard.
+
+However, some questions remain:
 \begin{itemize}
@@
     \item What interesting cases are there where there is no (strong) tractability on an unrestricted domain, but there is (strong) tractability on a nontrivial restricted domain, such as $(0,\infty) \times \{1, \ldots, d_{\max}] \cup (\varepsilon_{\min}^{-1},\infty) \times \naturals$?
-    \item For Hilbert spaces and solution operators, $\{\SOL_d : \cf_d \to \cg_d\}_{d \in \naturals}$, of tensor product form, how can the equivalent conditions for (strong) tractability be simplified, even when $T(a_1 \cdots a_d,d,\vp) \ne T_1(a_1,d,\vp)\cdots T_1(a_d,d,\vp)$ for some $T_1$?
+     \item For Hilbert spaces and solution operators, $\{\SOL_d : \cf_d \to \cg_d\}_{d \in \naturals}$, of tensor product form, the singular values take the form $\lambda_{i,d} = \lambda_{i,d,1} \cdots  \lambda_{i,d,d}$.
+What more can be said about the  equivalent conditions  for (strong) tractability in this case?
     \item For information complexity defined over cones of functions rather than balls (see e.g., \cite{DinHic20a,DinEtal20a}), what can be said about equivalent conditions for (strong) tractability?
@@
 Fred Hickernell acknowledges support by the United States National Science Foundation under Award No.\ 2316011.
-Peter Kritzer was supportedd by the Austrian Science Fund (FWF) Project P34808.
+Peter Kritzer was supported by the Austrian Science Fund (FWF) Project P34808.
 For the purpose of open access, the authors have applied a CC BY public copyright licence to any author accepted manuscript version arising from this submission.
@@
 
-\peter{
 \section*{Appendix}
@@
 \end{proof}
-}
 

### 2023-11-15 Older_versions/GeneralizedTractability2023August10.tex
Updates from Overleaf

--- 2023-09-21 GeneralizedTractability2023August10.tex
@@
 In Section \ref{sec:examples} we provide examples of tractability functions for both the algebraic and exponential cases.
-We also consider other notions of tractability such as quasi-polynomial tractability, and introduce other notions of tractability.
+We also consider other notions of tractability such as quasi-polynomial tractability, \ and introduce other notions of tractability.
 A generalized notion of weak tractability is given in Section \ref{sec:subh}.
-In Section \ref{sec:restricted}, we consider \peter{tractability on} a restricted domain .
+In Section \ref{sec:restricted}, we consider \peter{tractability on} a restricted domain.
 
@@
 \end{equation}
-which implies that the problem is expected to be no easier by decreasing the tolerance, $\varepsilon$, or increasing the dimension, $d$\footnote{This is why we make $T$ a function of $\varepsilon^{-1}$ rather than of $\varepsilon$.} Furthermore, increasing $\vp$ allows for a possibly looser bound on the information complexity.
+which implies that the problem is expected to be no easier by decreasing the tolerance, $\varepsilon$, or increasing the dimension, $d$\footnote{This is why we make $T$ a function of $\varepsilon^{-1}$ rather than of $\varepsilon$.}.
+Furthermore, increasing $\vp$ allows for a possibly looser bound on the information complexity.
 Since there are an infinite number of positive \peter{singular values}, it also makes sense to assume that
@@
 We would like to emphasize that this example was previously known (see, e.g., \cite{GW06}) where in this case the roles of $\varepsilon^{-1}$ and $d$ are separated.
-In order to accomplish this, we will first define two functions $\phi$ and $\psi$ with positive values that are increasing in both of their arguments which will allow to take into account a variety of possible exponents of $\varepsilon^{-1}$ and $d$ \peter{[Is this really what we would like to express in this context?]}.
+In order to accomplish this, we will first define two functions $\phi$ and $\psi$ with positive values that are increasing in both of their arguments.
 The equivalent conditions for this example take the same form as those in Theorems \ref{thm_main_strong_tract2} and \ref{thm_main_tract2}.

### 2023-11-15 arxiv_copy.tex
Updates from Overleaf

--- 2023-11-15 GeneralizedTractability2023Sept21.tex
@@
-\documentclass[sort&compress]{elsarticle}
-\usepackage{latexsym,amsfonts,amsmath,graphics,mathtools,amssymb,booktabs,xspace}
+\documentclass[11pt,a4paper]{article}
+\usepackage{latexsym,amsfonts,amsmath,graphics,mathtools,amssymb,amsthm,booktabs}
 \usepackage{epsfig}
@@
 \newtheorem{proposition}{Proposition}
-\newdefinition{definition}{Definition}
-\newdefinition{example}{Example}
-\newproof{proof}{Proof}
+\theoremstyle{definition}
+\newtheorem{definition}{Definition}
+\newtheorem{example}{Example}
+%\newdefinition{definition}{Definition}
+%\newdefinition{example}{Example}
+%\newproof{proof}{Proof}
 
@@
 
-\author[1]{Onyekachi Emenike}
-\ead{kachi.emenike12@gmail.com}
-\author[1]{Fred J. Hickernell}
-\ead{hickernell@iit.edu}
-\author[2]{Peter Kritzer}
-\ead{peter.kritzer@oeaw.ac.at}
+\author{Onyekachi Emenike, Fred J. Hickernell, Peter Kritzer}
+%\ead{kachi.emenike12@gmail.com}
+%\author[1]{Fred J. Hickernell}
+%\ead{hickernell@iit.edu}
+%\author[2]{Peter Kritzer}
+%\ead{peter.kritzer@oeaw.ac.at}
 
 \date{\today}
-\affiliation[1]{organization={Department of Applied Mathematics, Illinois Institute of Technology},
-addressline={10 West 32${}^{\text{nd}}$ Street, Room 220},
-postcode={60616},
-city={Chicago, IL},
-country={United States}}
-\affiliation[2]{organization={Johann Radon Institute for Computational and Applied Mathematics (RICAM), Austrian Academy of Sciences},
-addressline={Altenbergerstr. 69},
-postcode={4040},
-city={Linz},
-country={Austria}}
+%\affiliation[1]{organization={Department of Applied Mathematics, Illinois Institute of Technology},
+%addressline={10 West 32${}^{\text{nd}}$ Street, Room 220},
+%postcode={60616},
+%city={Chicago, IL},
+%country={United States}}
+%\affiliation[2]{organization={Johann Radon Institute for Computational and Applied Mathematics (RICAM), Austrian Academy of Sciences},
+%addressline={Altenbergerstr. 69},
+%postcode={4040},
+%city={Linz},
+%country={Austria}}
+\maketitle
 
@@
 
-\maketitle
+%\maketitle
 
@@
 We give the proof of Proposition \ref{prop:equiv_conditions} here.
-\begin{proof}[Proposition 1]
+\begin{proof}
+%[Proposition 1]
 We will give the proof of equivalence of the conditions \eqref{eq:exp_pt} and \eqref{eq:KW_exp_pt}.

### 2024-03-12 reply_reviewers.tex
Updates from Overleaf

\documentclass[11pt,a4paper]{article}
\usepackage{latexsym,amsfonts,amsmath,graphics,mathtools,amssymb,amsthm,booktabs}
\usepackage{epsfig}
%\usepackage[notref,notcite]{showkeys}
%\usepackage[active]{srcltx}
\usepackage{enumitem}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}

\usepackage{algorithmic}

%\input{common-macros}
%\input{common-macros2}

\input{FJHDef.tex}

\usepackage[normalem]{ulem}
\usepackage{algorithmic}
\usepackage{hyperref}
\usepackage{mathrsfs}
\usepackage{cleveref}

\setlength{\textheight}{24cm} \setlength{\textwidth}{16cm}
\setlength{\hoffset}{-1.3cm} \setlength{\voffset}{-1.8cm}

\newcommand{\supp}{\operatorname{supp}}

\newcommand{\tpmod}[1]{{\;(\operatorname{mod}\;#1)}}

\newcommand{\thed}{\mathscr{D}}
\newcommand{\theM}{\mathscr{E}}
\newcommand{\theUB}{\mathscr{U}}

\DeclareMathOperator*{\esssup}{ess\,sup}

%\DeclareMathOperator{\comp}{comp}
\DeclareMathOperator{\SOL}{SOL}
\DeclareMathOperator{\APP}{APP}

\allowdisplaybreaks

\newcommand{\fred}[1]{\begingroup\color{blue}Fred: #1\endgroup}
\newcommand{\peter}[1]{\begingroup\color{purple}Peter: #1\endgroup}
\newcommand{\kachi}[1]{\begingroup\color{ForestGreen}#1\endgroup}

\begin{document}

\newtheorem{theorem}{Theorem}
\theoremstyle{definition}
\newtheorem{definition}{Definition}

\begin{center}
    {\Large Response to the reviewers of the manuscript\\``A Unified Treatment of Tractability for \\ Approximation Problems Defined on Hilbert Spaces''}
\end{center}

We would like to thank the referees for their careful review and their valuable suggestions. Following the advice of the referees, we give an overview of the changes made in the manuscript

\subsection*{Referee Report 1 (1 page):}
\begin{itemize}
    \item We are not quite sure whether we understood this remark correctly, but we have tried to reformulate the corresponding sentence in the introduction. 
    \item We assume the referee means p.~2. We have re-formulated this sentence. 
    \item We assume the referee means p.~2. We have added a footnote with an explanation. 
    \item We have added another appendix (now, Appendix 1), where we show an example of how the condition for strong exponential tractability derived in our paper (which is different to what had been known before) can be applied to a concrete problem setting. The proof of Proposition 1 has been moved to Appendix 2. 
\end{itemize}
\medskip

\subsection*{Referee Report 2 (3 pages):}
\begin{itemize}
    \item[1.] We have shortened the paragraph. 
    \item[2.] We have added explanations to the introductory parts of the paper, and we have followed the suggestion of the referee to include a simplified version of the table for illustration. 
    \item[3.] We have re-formulated the sentence that was on p.~2, line~25. 
    \item[4.] A statement has been added as regards the role of $\vp$.
    \item[5.] Page 3, towards the top an explanation has been added.
    \item[6.] Page 2 (footnote) we explain that for problems where $\SOL_d$ has large singular values, a large error tolerance may be a reasonable expectation.  Thus we do not want to put an upper bound on $\varepsilon$.
    \item[7.] We have added a corresponding statement on page 3. 
    \item[8.] We have added a comment on this. 
    \item[9.] We have added a corresponding statement. 
    \item[10.] Done. 
    \item[11.] The referee is right. We have made the corresponding corrections. 
    \item[12.] We have removed the statement. 
    \item[13.] We added the precise equation we are using.
    \item[14.] We would like to emphasize that we intend to utilize equation (41) prior to establishing $\thed$ = 1. Indeed, we will make use of (41) in its general form in the proof of Theorem 5. 
    \item[15.] Again, the referee is right. We have made the formulation more precise. 
    \item[16.] Page 16, line -9: Done.
    \item[17.] This typo has been corrected. That is, we have changed ``Equation (39)'' to ``Equation (45)''.
    \item[18.] Done.
\end{itemize}
\end{document}

### 2024-03-12 GeneralizedTractability20240201_rev1.tex
Updates from Overleaf

--- 2023-11-15 GeneralizedTractability2023Sept21.tex
@@
 \usepackage{epsfig}
-\usepackage[notref,notcite]{showkeys}
+%\usepackage[notref,notcite]{showkeys}
 %\usepackage[active]{srcltx}
@@
 \newcommand{\theUB}{\mathscr{U}}
+
+\newcommand{\bsa}{\boldsymbol{a}}
+\newcommand{\bsb}{\boldsymbol{b}}
+\newcommand{\bsh}{\boldsymbol{h}}
+\newcommand{\kor}{{\mathrm{kor}}}
+\newcommand{\ZZ}{{\mathbb{Z}}}
+\newcommand{\NN}{{\mathbb{N}}}
+%\newcommand{\norm}[1]{\left\Vert#1\right\Vert}
 
@@
     A large literature specifies conditions under which the information complexity for a sequence of numerical problems defined for dimensions $1, 2, \ldots$ grows at a moderate rate, i.e., the sequence of problems is \emph{tractable}.
-Here, we focus on the situation where the space of available information consists of all linear functionals and the problems are defined as linear operator mappings between Hilbert spaces.
+Here, we focus on the situation where the space of available information consists of all linear functionals, and the problems are defined as linear operator mappings between Hilbert spaces.
 We unify the proofs of known tractability results and generalize a number of existing results.
@@
 Research on tractability continues at a vigorous pace.
-This article aims to unify and generalize many existing tractability results for approximation problems where all linear functional data is available.
+
+\fred{The authors have identified common themes in the proofs of necessary and sufficient conditions for tractability that appear in the literature.
+By abstracting these themes, this article aims to unify and generalize many existing tractability results for approximation problems where all possible linear functional data are available.
+This is done in a series of five theorems, which provide necessary and sufficient conditions for (strong) tractability.}
 
 Let $\{\cf_d\}_{d \in \naturals}$ and $\{\cg_d\}_{d \in \naturals}$ be sequences of Hilbert spaces, and let $\{\SOL_d : \cf_d \to \cg_d\}_{d \in \naturals}$ be a sequence of linear solution operators  with adjoints $\SOL_d^*$ such that $\SOL_d^*\SOL_d : \cf_d \to \cf_d$ has eigenvalues and orthonormal eigenvectors
-\begin{equation} \label{eq:eigenvalues}
+\begin{equation*} %\label{eq:eigenvalues}
  \lambda_{1,d}^2 \ge \lambda_{2,d}^2 \ge \cdots, \qquad u_{1,d}, u_{2,d}, \ldots, \qquad d \in \naturals.
-\end{equation}
-This means that the non-negative $\lambda_{i,d}$ are the singular values of the operator $\SOL_d$.
+\end{equation*}
+\fred{Here, $\naturals$ denotes the set of positive integers.}  This means that \peter{the singular values of the operator $\SOL_d$ are the non-negative $\lambda_{i,d}$}.
 We remark that in the literature on Information-Based Complexity the singular values of $\SOL_d$ are often denoted by $\sqrt{\lambda_{i,d}}$ instead of $\lambda_{i,d}$.
@@
     \label{eq:errcrit}
-    \norm[\cg_d]{\SOL_d(f) - \APP_d(f,\varepsilon)} \le \varepsilon \qquad \forall f \in \cb_d, \ \varepsilon \in (0,\infty)\footnote{We note that the radius of the $\cb_d$ could be taken to be an arbitrary positive value, $R$, in which case the problem becomes equivalent to the original one with the tolerance $\varepsilon$ replaced by $\varepsilon/R$ since the problem and the optimal approximate soluion are both linear (see below).}.
+    \norm[\cg_d]{\SOL_d(f) - \APP_d(f,\varepsilon)} \le \varepsilon \qquad \forall f \in \cb_d, \ \varepsilon \in (0,\infty)\footnote{We note that the radius of the $\cb_d$ could be taken to be an arbitrary positive value, $R$, in which case the problem becomes equivalent to the original one with the tolerance $\varepsilon$ replaced by $\varepsilon/R$ since the problem and the optimal approximate solution are both linear (see below).
+\fred{We allow the error tolerance, $\varepsilon$, to be arbitrarily large because if $\SOL_d$ has large singular values, a large error tolerance may be a reasonable expectation.}}.
 \end{equation}
@@
 \]
-where $\comp(\varepsilon,d)$ is the number of linear functionals required by the best admissible algorithm to satisfy the error criterion \eqref{eq:errcrit}.
+where $\comp(\varepsilon,d)$ is the number of linear functionals required by the best admissible algorithm to satisfy the error criterion \eqref{eq:errcrit}\fred{, and  $\naturals_0$ denotes the set of non-negative integers}.
 By definition, the information complexity is non-decreasing  as $\varepsilon$ tends to zero.
@@
 
-Strictly speaking, we are considering the \textit{absolute} error criterion in this paper.
-Alternatively, one could also consider the \textit{normalized} error criterion, where the error in \eqref{eq:errcrit} is divided by the so-called \textit{initial error}, which is the error without sampling the function, or, equivalently, the operator norm of $\SOL_d$.
-In the latter case, it is known (see, e.g., again \cite{NovWoz08a}) that the information complexity is given by
-\[
-\comp^{\rm norm}(\varepsilon, d) = \min \{n \in \natzero : \lambda_{n+1, d} \le \varepsilon\, \lambda_{1, d}\}.
-\]
-This means that, essentially, in the tractability analysis below, all criteria would be normalized by the first singular value $\lambda_{1,d}$.
-For the sake of brevity and clarity of notation, we restrict ourselves to the absolute error criterion here, but presumably analogous results hold for the normalized setting.
+\peter{Strictly speaking, we are considering the \textit{absolute} error criterion in this paper.
+Alternatively, one could also consider the \textit{normalized} error criterion, where the error in \eqref{eq:errcrit} is divided by the so-called \textit{initial error}, which is the error without sampling the function, or, equivalently, the operator norm of $\SOL_d$ (see \cite{NovWoz08a} for details).
+For the sake of brevity, we restrict ourselves to the absolute error criterion here, but presumably analogous results hold for the normalized setting (all criteria would then be normalized by the first singular value $\lambda_{1,d}$).}
 
@@
 
-We want to bound the information complexity in terms of a simple function, $T$, of $\varepsilon^{-1}$ and $d$, and identify conditions on the singular values that are easier to verify that are equivalent to this bound on the information complexity holding.
+\peter{We want to bound the information complexity in terms of a simple function, $T$, of $\varepsilon^{-1}$, \kachi{$d$, and some parameter $\vp$}, and then identify conditions on the singular values that are equivalent to the fact that this bound holds, and are easier to verify than showing the bound directly.
+By ``simple'' we mean that $T$ takes a form such that the conditions in the theorems of this paper can be checked effectively; however, we remark that this is also related to the singular values $\lambda_{i,d}$ of the solution operator.
+Depending on those, a function $T$ may be useful for one particular problem setting but not for another.} \kachi{In Table \ref{tab:sampleT}, we present various common notions of tractability studied in the literature, characterized by $T$.}
+\begin{table}[hbt!]
+    \caption{\kachi{Common notions of tractability}}
+{\small
+\begin{equation*}
+	\begin{array}{r@{\quad}c@{\quad}cc}
+		\text{Tractability type} & T(\varepsilon^{-1},d,\vp)
+		\\
+		\toprule
+		\text{algebraic strong polynomial} & \max\{1,\varepsilon^{-p}\} \\
+		\text{algebraic polynomial} & \max\{1,\varepsilon^{-p}\}d^{q} \\
+		\text{exponential strong polynomial} &  [\max\{1,\log(1 + \varepsilon^{-1}\}]^p \\
+		\text{exponential polynomial} &
+		[\max\{1,\log(1 + \varepsilon^{-1})\}]^p  d^{q} \\
+        \text{algebraic quasi-polynomial} &
+        \exp\{p(1+\log(\max\{1, \varepsilon^{-1}\}))(1+\log(d))\} \\
+        \text{exponential quasi-polynomial} &
+        \exp\{p(1+\log(\max\{1,\log(1+\varepsilon^{-1})\}))(1+\log(d))\} 
+	\end{array}
+\end{equation*}}
+\label{tab:sampleT}
+\end{table}
+
 We note that generalized tractability specified by a function $T$ has been considered before in the literature.
@@
 Hence, the present paper adds to what is presently known on this subject.
+
 In this article, we investigate a \emph{generalized tractability function}, denoted by $T$:
@@
 \end{equation}
-The conditions we require $T$ to satisfy are described in  Section \ref{sec:not}, however, the basic idea is that we define our approximation problem to be tractable if $\comp(\varepsilon, d) \le  C_{\vp}\, T(\varepsilon^{-1},d,\vp)$ for some constant, $C_{\vp}$, depending only on the parameter $\vp$.
-The parameter $\vp$ is an $s$-dimensional vector with $s \geq 1$, where $\vp \geq \vzero$ implies that each component of $\vp$ is non-negative.
+The conditions we require $T$ to satisfy are described in  Section \ref{sec:not}, however, the basic idea is that we define our approximation problem to be tractable if $\comp(\varepsilon, d) \le  C_{\vp}\, T(\varepsilon^{-1},d,\vp)$ for some constant\footnote{\peter{By ``constant'' we mean that the term is independent of the \emph{variables} $\varepsilon$ and $d$, but may depend on the \emph{parameter} $\vp$.}}, $C_{\vp}$, depending only on the parameter $\vp$.
+\kachi{For instance, when considering (algebraic) polynomial tractability, the parameter $\vp$ represents the exponents $(p,q)$ of $\varepsilon$ and $d$, as illustrated in Table 1}.
 In practice, we expect $T(\varepsilon^{-1},d,\vp)$ to increase sub-exponentially with increasing $\varepsilon^{-1}$ and/or $d$, however, most of our theorems do not require such an assumption.
 
+The parameter $\vp$ is an $s$-dimensional vector with $s \geq 1$.
+\fred{We write $\vzero$ to denote a vector with all components equal to zero, and $\vinfty$ to denote a vector with all components equal to $\infty$.
+Furthermore, for two vectors $\vp=(p_1,\ldots,p_s)$ and $ \vp'=(p_1',\ldots,p_s')$ in $[0,\infty)^s$, 
+we write $\vp\ge \vp'$ if $p_j\ge p'_j$ for all $j\in \{1,\ldots,s\}$. Furthermore, $\vp > \vp'$ 
+if $p_j> p'_j$ for all $j\in \{1,\ldots,s\}$. The expression $\vp\in (\vp',\vp'')$ is to be interpreted as 
+$\vp' < \vp < \vp''$ in that sense, and analogously for half-closed or closed intervals.}
+
 \Cref{thm_main_strong_tract2,thm_main_tract2,thm_main_rest_strong_tract,thm_main_rest_tract} below all take the following form:  for a given $\thed \in \{1,d\}$ and $\Omega \subseteq (0,\infty) \times \mathbb{N}$,
-\begin{multline}
+\begin{multline} \label{eq:metatheorem}
   \exists \,C_{\vp} > 0 \text{ with }
@@
         \min\{n \in \natzero : \lambda_{n+1,d} \le \theM(d) \}, &   \theM(d) > 0, \\
-        \infty, & \theM(d) = 0.
+        \infty, & \theM(d) = 0,
         \end{cases}
@@
 %The differences in these theorems are in the choices of $\thed$ and $\Omega$. 
-Although some of these theorems are special cases of others, we prove each separately to allow the reader to become familiar with the arguments used as additional layers of complexity are added.
-\Cref{thm:subhT} has a somewhat different form than above.
-
-In the following, we will denote the set of positive integers by $\naturals$ and the set of non-negative integers by $\naturals_0$.
-We write $\vzero$ to denote a vector with all components equal to zero, and $\vinfty$ to denote a vector with all components equal to $\infty$.
-Furthermore, for two vectors $\vp=(p_1,\ldots,p_s)$ and $ \vp'=(p_1',\ldots,p_s')$ in $[0,\infty)^s$, 
-we write $\vp\ge \vp'$ if $p_j\ge p'_j$ for all $j\in \{1,\ldots,s\}$. Furthermore, $\vp > \vp'$ 
-if $p_j> p'_j$ for all $j\in \{1,\ldots,s\}$. The expression $\vp\in (\vp',\vp'')$ is to be interpreted as 
-$\vp' < \vp < \vp''$ in that sense, and analogously for half-closed or closed intervals.
+\peter{where $T(0,\thed,\vp)$ is defined as in \eqref{eq:T0} below.}  \fred{These theorems say essentially that \emph{(strong) tractability is equivalent to summability conditions on the singular values.} A more stringent form of tractability resulting from a smaller $T$ is equivalent to a more stringent summability condition since the terms being summed become larger.}
+
+Although some of \Cref{thm_main_strong_tract2,thm_main_tract2,thm_main_rest_strong_tract,thm_main_rest_tract} are special cases of others, we prove each separately to allow the reader to become familiar with the arguments used as additional layers of complexity are added.
+\peter{(This may be, e.g., additional
+dependence on $d$ when going from strong tractability to tractability in Subsection~\ref{sec:tractability}, or a restriction of the domain of $\varepsilon$ for which we define tractability in Section 
+~\ref{sec:restricted}).}  \Cref{thm:subhT} has a somewhat different form than \eqref{eq:metatheorem} above.
+
+\fred{Although in many cases $\Omega$ is chosen to be all of $(0,\infty) \times \mathbb{N}$, there are situations where it makes sense to choose $\Omega$ as a proper subset of all possible values of $\varepsilon^{-1}$ and $d$.
+For some problems with unbounded $d$---as in finance---there may be no need for arbitrarily small error tolerances, so $\Omega = (0,\varepsilon_{\min}^{-1}] \times \mathbb{N}$ may be appropriate.
+For other problems with a moderate upper bound on $d$, $\Omega = (0,\infty) \times \{1, \ldots, d_{\max}\}$ may be appropriate.
+}
 
@@
 In Section \ref{sec:restricted}, we consider tractability on a restricted domain, $\Omega$.
+\peter{There are two appendices to the paper.
+Appendix 1 contains an example that shows how we can make use of one of the findings in this paper in a concrete example.
+Appendix 2 contains the technical proof of Proposition \ref{prop:equiv_conditions}}.
 
@@
 \end{equation}
+\peter{We remark that the latter assumption is quite natural, and is, for example fullfilled for all tractability types in Table~\ref{tab:commonT}.}
 
@@
     \le &\frac{1}{n-N+1} \sum_{i=N}^n  \frac{1}{T(\lambda_{i, d}^{-1},\thed,\vp) }
-    \le \frac{1}{n-N+1} \sum_{i=N}^\infty  \frac{1}{T(\lambda_{i, d}^{-1},\thed,\vp)}.
+    \le \frac{1}{n-N+1} \sum_{i=N}^\infty  \frac{1}{T(\lambda_{i, d}^{-1},\thed,\vp)},
 \end{align*}
+\peter{where the infinite sum is guaranteed to exist by the condition \eqref{eq:strong_tractiff3}.}
 Thus, we can conclude from the previous line that
@@
    \implies   \frac{1}{T(\lambda_{n+1, d}^{-1},\thed,\vp)} \le
-   \frac{1}{n-N+1} \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},\thed,\vp) } \le \frac{1}{T(\varepsilon^{-1},\thed,\vp)} \\ \forall \thed, n, N \in \naturals.
+   \frac{1}{n-N+1} \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},\thed,\vp) } \le \frac{1}{T(\varepsilon^{-1},\thed,\vp)} \\ \forall \thed, N \in \naturals\ \peter{\mbox{and}\ n\ge N}.
 \end{multline}
-We note that the left side of the implication implies $n \ge N$ automatically since $n$ is an integer and $n - N +1$ is assumed to be positive.
+%We note that the left side of the implication implies $n \ge N$ automatically since $n$ is an integer and $n - N +1$ is assumed to be positive.
 
@@
 The following proposition states that the conditions \eqref{eq:exp_spt} and \eqref{eq:KW_exp_spt}, as well as the conditions \eqref{eq:exp_pt} and \eqref{eq:KW_exp_pt}, are indeed equivalent. 
-The proof of this result is deferred to the appendix, where we will prove this statement for the latter two conditions, i.e., for the conditions on exponential polynomial tractability.
+The proof of this result is deferred to \peter{Appendix 2} where we will prove this statement for the latter two conditions, i.e., for the conditions on exponential polynomial tractability.
 The case of exponential strong polynomial tractability is not explicitly included, as it is actually simpler and can be treated analogously.
+\peter{We give a short example of how we can apply the condition \eqref{eq:exp_spt} to a concrete problem in Appendix 1.}
+
 \begin{proposition}\label{prop:equiv_conditions}
@@
 
+\fred{Help!  I do not understand how we give and example of a summary of examples above.}
 In the following example, we provide a brief summary of the above examples of tractability.
@@
    \implies   \frac{1}{T(\lambda_{n+1, d}^{-1},\thed,\vp)} \le
-   \frac{1}{n-N+1} \sum_{i=N}^{\theUB(d)} \frac{1}{T(\lambda_{i, d}^{-1},\thed,\vp) } \le \frac{1}{T(\varepsilon^{-1},\thed,\vp)} \\ \forall \thed \in \naturals,\  n, N \in \hI_d,   \ N \le n.
+   \frac{1}{n-N+1} \sum_{i=N}^{\theUB(d)} \frac{1}{T(\lambda_{i, d}^{-1},\thed,\vp) } \le \frac{1}{T(\varepsilon^{-1},\thed,\vp)} \\ \forall \thed \in \naturals,\  N \in \hI_d, \ \peter{\mbox{and}\ n\ge N}
 \end{multline}
@@
 \]
-This implies via our technical assumption \eqref{eq:ptauassume} that
+This implies via our technical assumption \eqref{eq:ptauassume} that, \peter{for $\tau>1$,}
 \begin{gather}
@@
        \comp(\varepsilon,d)
-       & \le T(\varepsilon^{-1},d, \vp) \Biggl [ \frac{\min\left\{\lceil L_{\vp}\, T(0,d,\vp)\rceil,\theUB(d)\right\}}{T(\varepsilon^{-1},d, \vp)}  + \underbrace{\sum_{i = \min\left\{\lceil L_{\vp}\, T(0,d,\vp)\rceil,\theUB(d)\right\}}^{\theUB(d)} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}}_{\le S_{\vp} + 1/ T(\lambda_{\theUB(d), d}^{-1},d,\vp) \text{ by \eqref{eq:strong_rest_tractiff}} }
+       & \le T(\varepsilon^{-1},d, \vp) \Biggl [ \frac{\min\left\{\lceil L_{\vp}\, T(0,d,\vp)\rceil,\theUB(d)\right\}}{T(\varepsilon^{-1},d, \vp)}  + \underbrace{\sum_{i = \min\left\{\lceil L_{\vp}\, T(0,d,\vp)\rceil,\theUB(d)\right\}}^{\theUB(d)} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}}_{\le S_{\vp} + 1/ T(\lambda_{\theUB(d), d}^{-1},d,\vp) \text{ by \kachi{\eqref{eq:rest_tractiff}}} }
         \Biggr] \\
@@
  \ge
-  \left[\frac{(i-1)}{C_{\vp}}\right]^\tau \qquad \forall i\in \mathscr{I}_{d,\vp},  \ d \in \naturals, \\
+  \left[\frac{(i-1)}{C_{\vp}}\right]^\tau \qquad \forall i\in \mathscr{I}_{d,\vp},  \ d \in \naturals,\\
   \label{eq:rest_ineq}
@@
 
-\section*{Appendix}
-
-We give the proof of Proposition \ref{prop:equiv_conditions} here.
+\section*{\peter{Appendix 1: A concrete example}}
+
+\peter{
+We define the weighted Korobov space $\ch_{\kor,d,\bsa,\bsb}$ below. 
+This space contains real-analytic functions, and has been studied in the context of exponential tractability in, e.g., \cite{DKPW14, KPW17}, where the reader can find further details on this space.
+
+Let $\bsa=\{a_j\}_{j \ge 1}$ and
+$\bsb=\{b_j\}_{j \ge 1}$ be two sequences of real positive weights
+such that
+\begin{equation}\label{eq:cond_a_b}
+b_\ast:=\inf_j b_j> 0\ \ \ \ \ \mbox{and}\ \ \ \ \
+a_\ast:=\inf_j a_j>0.
+\end{equation}
+We assume, without loss of generality, that the $a_j$ are ordered in a non-decreasing way, i.e., $a_\ast=a_1$.
+Fix $\omega\in(0,1)$, and write 
+\[
+r_{d,\bsa,\bsb} (\bsh):=\omega^{-\sum_{j=1}^{d}a_j \abs{h_j}^{b_j}}
+\qquad\mbox{for}\qquad \bsh=(h_1,h_2,\dots,h_d)\in\ZZ^d.
+\]
+
+We define $\ch_{\kor,d,\bsa,\bsb}$ as the space of all one-periodic functions $f$ with absolutely convergent Fourier series, 
+and with finite norm 
+$||f||_{\kor,d,\bsa,\bsb}:=\langle f, f\rangle_{\kor,d,\bsa,\bsb}^{1/2}$,
+where the inner product is given by
+\[
+ \langle f, g\rangle_{\kor,d,\bsa,\bsb}:=
+ \sum_{\bsh\in\ZZ^d} r_{d,\bsa,\bsb} (\bsh) 
+ \widehat{f} (\bsh) \overline{\widehat{g}(\bsh)}.
+\]
+Let us consider $L_2$-approximation, i.e., $\SOL_d:\ch_{\kor,d,\bsa,\bsb}\to L_2([0,1]^d)$, $\SOL_d(f)=f$, and let us assume
+$\Lambda^{\rm all}$ as the information class. One can show that the singular values  for this choice of $\SOL_d$ are given by
+\begin{equation}\label{eq:eigenvalues}
+ \left\{\lambda_{n,d}\colon n\in\NN\right\}=\left\{\left(r_{d,\bsa,\bsb} (\bsh)\right)^{-1/2}\colon \bsh\in\ZZ^d\right\}
+ =\left\{\omega^{\frac{1}{2}\sum_{j=1}^{d}a_j \abs{h_j}^{b_j}}\colon \bsh\in\ZZ^d\right\}.
+\end{equation}
+
+If, for instance, we would like to find out whether $L_2$-approximation on $\ch_{\kor,d,\bsa,\bsb}$ satisfies 
+exponential strong tractability, we would use condition \eqref{eq:KW_exp_spt}, which previously existed in the literature.
+A slight drawback of this condition, however, is that we need to know everything about the order of the singular values, since we need to study summability of $\lambda_{i,d}^{i^{-\tau}}$ in \eqref{eq:KW_exp_spt}.
+This is technically rather involved, and was implicitly done in \cite{DKPW14} (we remark that the concise form
+of the condition \eqref{eq:KW_exp_spt} was not yet known when \cite{DKPW14} was written, and the proof idea in \cite{DKPW14} is less 
+straightforward than just checking \eqref{eq:KW_exp_spt}.
+
+Alternatively, we can use the newly derived condition \eqref{eq:exp_spt} instead of \eqref{eq:KW_exp_spt} and study the expression
+\[
+ \sum_{i=1}^\infty \frac{1}{T\left(\lambda_{i,d}^{-1},1,(p,0)\right)}\kachi{,}
+\]
+for a real $p>0$. Inserting the singular values as in \eqref{eq:eigenvalues}, yields
+\[
+  \sum_{i=1}^\infty \frac{1}{T\left(\lambda_{i,d}^{-1},1,(p,0)\right)}
+  = \sum_{\bsh\in\ZZ^d} \frac{1}{\left(1+ \log \left(\omega^{-\frac{1}{2}\sum_{j=1}^d a_j \abs{h_j}^{b_j}}\right)\right)^p}\, .
+\]
+It is then not hard to show that the two conditions 
+\[
+ \sum_{j=1}^\infty \frac{1}{b_j} <\infty \quad \mbox{and}\quad \alpha^*:=\liminf_{j\to\infty}\frac{\log a_j}{j}>0
+\]
+are sufficient to achieve exponential strong tractability (for details we refer to \cite{K24}), and this is in accordance with the findings in \cite{DKPW14}.
+Note, however, that this result in \cite{DKPW14} was technically much harder to show than
+the analysis of the previous sum is.
+
+}
+
+\section*{\peter{Appendix 2: Proof of Proposition~\ref{prop:equiv_conditions}}}
+
 \begin{proof}[Proposition 1]

### 2024-03-12 Older_versions/GeneralizedTractability2023Sept21.tex
Updates from Overleaf

--- 2023-11-15 GeneralizedTractability2023Sept21.tex
@@
     \label{eq:errcrit}
-    \norm[\cg_d]{\SOL_d(f) - \APP_d(f,\varepsilon)} \le \varepsilon \qquad \forall f \in \cb_d, \ \varepsilon \in (0,\infty)\footnote{We note that the radius of the $\cb_d$ could be taken to be an arbitrary positive value, $R$, in which case the problem becomes equivalent to the original one with the tolerance $\varepsilon$ replaced by $\varepsilon/R$ since the problem and the optimal approximate soluion are both linear (see below).}.
+    \norm[\cg_d]{\SOL_d(f) - \APP_d(f,\varepsilon)} \le \varepsilon \qquad \forall f \in \cb_d, \ \varepsilon \in (0,\infty)\footnote{We note that the radius of the $\cb_d$ could be taken to be an arbitrary positive value, $R$, in which case the problem becomes equivalent to the original one with the tolerance $\varepsilon$ replaced by $\varepsilon/R$ since the problem and the optimal approximate solution are both linear (see below).}.
 \end{equation}
@@
 
-We want to bound the information complexity in terms of a simple function, $T$, of $\varepsilon^{-1}$ and $d$, and identify conditions on the singular values that are easier to verify that are equivalent to this bound on the information complexity holding.
+We want to bound the information complexity in terms of a simple function, $T$, \kachi{which depends of three variables} $\varepsilon^{-1}$, \kachi{ $d$ and some parameter $\vp$},  and identify conditions on the singular values that are easier to verify that are equivalent to this bound on the information complexity holding.
 We note that generalized tractability specified by a function $T$ has been considered before in the literature.
@@
        \comp(\varepsilon,d)
+       & \le  \kachi{T(\varepsilon^{-1},\thed,\vp) \Biggl [\frac{N}{T(\varepsilon^{-1},\thed,\vp)}  +  \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},\thed,\vp)} \Biggr] \quad \forall  \thed, N \in \naturals}
+       \\
       & \le T(\varepsilon^{-1},d,\vp) \Biggl [

### 2024-04-21 reply_reviewers.tex
Updates from Overleaf

@@
 
-We would like to thank the referees for their careful review and their valuable suggestions. Following the advice of the referees, we give an overview of the changes made in the manuscript
+We would like to thank the referees for their careful review and their valuable suggestions. Following the advice of the referees, we give an overview of the changes made in the manuscript.
 
@@
 \end{itemize}
+
+\bigskip
+
+Apart from these changes, we removed a few typos and minor errors from the manuscript.
+
+\medskip
+
+We hope that these modifications address the concerns of the referees in a satisfactory manner. 
+All relevant changes are marked in blue in the revised version.\\
+
+\noindent With kind regards,\\[0.25cm]
+
+\noindent O.~Emenike, F.J.~Hickernell, P.~Kritzer
+
 \end{document}

### 2024-04-21 GeneralizedTractability_rev_2.tex
Updates from Overleaf

--- 2024-03-12 GeneralizedTractability20240201_rev1.tex
@@
 \newcommand{\bsh}{\boldsymbol{h}}
+\newcommand{\bsx}{\boldsymbol{x}}
 \newcommand{\kor}{{\mathrm{kor}}}
@@
 \input{FJHDef.tex}
+% Modify the elsarticle-num-names bibliography style to sort references alphabetically
+\makeatletter
+\renewcommand\@biblabel[1]{#1.}
+\makeatother
 
@@
 \newcommand{\peter}[1]{\begingroup\color{violet}#1\endgroup}
-\newcommand{\kachi}[1]{\begingroup\color{ForestGreen}#1\endgroup}
+\newcommand{\kachi}[1]
+{\begingroup\color{ForestGreen}#1\endgroup}
+\newcommand{\review}[1]{\begingroup\color{blue}#1\endgroup}
 
@@
 
-\fred{The authors have identified common themes in the proofs of necessary and sufficient conditions for tractability that appear in the literature.
+The authors have identified common themes in the proofs of necessary and sufficient conditions for tractability that appear in the literature.
 By abstracting these themes, this article aims to unify and generalize many existing tractability results for approximation problems where all possible linear functional data are available.
-This is done in a series of five theorems, which provide necessary and sufficient conditions for (strong) tractability.}
+This is done in a series of five theorems, which provide necessary and sufficient conditions for (strong) tractability.
 
@@
 \end{equation*}
-\fred{Here, $\naturals$ denotes the set of positive integers.}  This means that \peter{the singular values of the operator $\SOL_d$ are the non-negative $\lambda_{i,d}$}.
+Here, $\naturals$ denotes the set of positive integers.
+This means that the singular values of the operator $\SOL_d$ are the non-negative $\lambda_{i,d}$.
 We remark that in the literature on Information-Based Complexity the singular values of $\SOL_d$ are often denoted by $\sqrt{\lambda_{i,d}}$ instead of $\lambda_{i,d}$.
@@
     \label{eq:errcrit}
-    \norm[\cg_d]{\SOL_d(f) - \APP_d(f,\varepsilon)} \le \varepsilon \qquad \forall f \in \cb_d, \ \varepsilon \in (0,\infty)\footnote{We note that the radius of the $\cb_d$ could be taken to be an arbitrary positive value, $R$, in which case the problem becomes equivalent to the original one with the tolerance $\varepsilon$ replaced by $\varepsilon/R$ since the problem and the optimal approximate solution are both linear (see below).
-\fred{We allow the error tolerance, $\varepsilon$, to be arbitrarily large because if $\SOL_d$ has large singular values, a large error tolerance may be a reasonable expectation.}}.
+    \norm[\cg_d]{\SOL_d(f) - \APP_d(f,\varepsilon)} \le \varepsilon \qquad \forall f \in \cb_d, \ \varepsilon \in (0,\infty).\footnote{We note that the radius of the $\cb_d$ could be taken to be an arbitrary positive value, $R$, in which case the problem becomes equivalent to the original one with the tolerance $\varepsilon$ replaced by $\varepsilon/R$ since the problem and the optimal approximate solution are both linear (see below).
+We allow the error tolerance, $\varepsilon$, to be arbitrarily large because if $\SOL_d$ has large singular values, a large error tolerance may be a reasonable expectation.}
 \end{equation}
@@
 \]
-where $\comp(\varepsilon,d)$ is the number of linear functionals required by the best admissible algorithm to satisfy the error criterion \eqref{eq:errcrit}\fred{, and  $\naturals_0$ denotes the set of non-negative integers}.
+where $\comp(\varepsilon,d)$ is the number of linear functionals required by the best admissible algorithm to satisfy the error criterion \eqref{eq:errcrit}, and  $\naturals_0$ denotes the set of non-negative integers.
 By definition, the information complexity is non-decreasing as $\varepsilon$ tends to zero.
@@
 
-\peter{Strictly speaking, we are considering the \textit{absolute} error criterion in this paper.
+Strictly speaking, we are considering the \textit{absolute} error criterion in this paper.
 Alternatively, one could also consider the \textit{normalized} error criterion, where the error in \eqref{eq:errcrit} is divided by the so-called \textit{initial error}, which is the error without sampling the function, or, equivalently, the operator norm of $\SOL_d$ (see \cite{NovWoz08a} for details).
-For the sake of brevity, we restrict ourselves to the absolute error criterion here, but presumably analogous results hold for the normalized setting (all criteria would then be normalized by the first singular value $\lambda_{1,d}$).}
+For the sake of brevity, we restrict ourselves to the absolute error criterion here, but presumably, analogous results hold for the normalized setting (all criteria would then be normalized by the first singular value $\lambda_{1,d}$).
 
@@
 
-\peter{We want to bound the information complexity in terms of a simple function, $T$, of $\varepsilon^{-1}$, \kachi{$d$, and some parameter $\vp$}, and then identify conditions on the singular values that are equivalent to the fact that this bound holds, and are easier to verify than showing the bound directly.
+We want to bound the information complexity in terms of a simple function, $T$, of $\varepsilon^{-1}$, $d$, and some parameter $\vp$, and then identify conditions on the singular values that are equivalent to the fact that this bound holds, and are easier to verify than showing the bound directly.
 By ``simple'' we mean that $T$ takes a form such that the conditions in the theorems of this paper can be checked effectively; however, we remark that this is also related to the singular values $\lambda_{i,d}$ of the solution operator.
-Depending on those, a function $T$ may be useful for one particular problem setting but not for another.} \kachi{In Table \ref{tab:sampleT}, we present various common notions of tractability studied in the literature, characterized by $T$.}
+Depending on those, a function $T$ may be useful for one particular problem setting but not for another.
+In Table \ref{tab:sampleT}, we present various common notions of tractability studied in the literature, characterized by $T$.
 \begin{table}[hbt!]
-    \caption{\kachi{Common notions of tractability}}
+    \caption{Common notions of tractability}
 {\small
@@
 \end{equation}
-The conditions we require $T$ to satisfy are described in  Section \ref{sec:not}, however, the basic idea is that we define our approximation problem to be tractable if $\comp(\varepsilon, d) \le  C_{\vp}\, T(\varepsilon^{-1},d,\vp)$ for some constant\footnote{\peter{By ``constant'' we mean that the term is independent of the \emph{variables} $\varepsilon$ and $d$, but may depend on the \emph{parameter} $\vp$.}}, $C_{\vp}$, depending only on the parameter $\vp$.
-\kachi{For instance, when considering (algebraic) polynomial tractability, the parameter $\vp$ represents the exponents $(p,q)$ of $\varepsilon$ and $d$, as illustrated in Table 1}.
+The conditions we require $T$ to satisfy are described in  Section \ref{sec:not}, however, the basic idea is that we define our approximation problem to be tractable if $\comp(\varepsilon, d) \le  C_{\vp}\, T(\varepsilon^{-1},d,\vp)$ for some constant\footnote{By ``constant'' we mean that the term is independent of the \emph{variables} $\varepsilon$ and $d$, but may depend on the \emph{parameter} $\vp$.}, $C_{\vp}$, depending only on the parameter $\vp$.
+For instance, when considering (algebraic) polynomial tractability, the parameter $\vp$ represents the exponents $(p,q)$ of $\varepsilon$ and $d$, as illustrated in Table \ref{tab:sampleT}.
 In practice, we expect $T(\varepsilon^{-1},d,\vp)$ to increase sub-exponentially with increasing $\varepsilon^{-1}$ and/or $d$, however, most of our theorems do not require such an assumption.
@@
 The parameter $\vp$ is an $s$-dimensional vector with $s \geq 1$.
-\fred{We write $\vzero$ to denote a vector with all components equal to zero, and $\vinfty$ to denote a vector with all components equal to $\infty$.
+We write $\vzero$ to denote a vector with all components equal to zero, and $\vinfty$ to denote a vector with all components equal to $\infty$.
 Furthermore, for two vectors $\vp=(p_1,\ldots,p_s)$ and $ \vp'=(p_1',\ldots,p_s')$ in $[0,\infty)^s$, 
@@
 if $p_j> p'_j$ for all $j\in \{1,\ldots,s\}$. The expression $\vp\in (\vp',\vp'')$ is to be interpreted as 
-$\vp' < \vp < \vp''$ in that sense, and analogously for half-closed or closed intervals.}
+$\vp' < \vp < \vp''$ in that sense, and analogously for half-closed or closed intervals.
 
@@
 %The differences in these theorems are in the choices of $\thed$ and $\Omega$. 
-\peter{where $T(0,\thed,\vp)$ is defined as in \eqref{eq:T0} below.}  \fred{These theorems say essentially that \emph{(strong) tractability is equivalent to summability conditions on the singular values.} A more stringent form of tractability resulting from a smaller $T$ is equivalent to a more stringent summability condition since the terms being summed become larger.}
+where $T(0,\thed,\vp)$ is defined as in \eqref{eq:T0} below.
+These theorems say essentially that \emph{(strong) tractability is equivalent to summability conditions on the singular values.} A more stringent form of tractability resulting from a smaller $T$ is equivalent to a more stringent summability condition since the terms being summed become larger.
 
 Although some of \Cref{thm_main_strong_tract2,thm_main_tract2,thm_main_rest_strong_tract,thm_main_rest_tract} are special cases of others, we prove each separately to allow the reader to become familiar with the arguments used as additional layers of complexity are added.
-\peter{(This may be, e.g., additional
+(This may be, e.g., additional
 dependence on $d$ when going from strong tractability to tractability in Subsection~\ref{sec:tractability}, or a restriction of the domain of $\varepsilon$ for which we define tractability in Section 
-~\ref{sec:restricted}).}  \Cref{thm:subhT} has a somewhat different form than \eqref{eq:metatheorem} above.
-
-\fred{Although in many cases $\Omega$ is chosen to be all of $(0,\infty) \times \mathbb{N}$, there are situations where it makes sense to choose $\Omega$ as a proper subset of all possible values of $\varepsilon^{-1}$ and $d$.
+~\ref{sec:restricted}).  \Cref{thm:subhT} has a somewhat different form than \eqref{eq:metatheorem} above.
+
+Although in many cases $\Omega$ is chosen to be all of $(0,\infty) \times \mathbb{N}$, there are situations where it makes sense to choose $\Omega$ as a proper subset of all possible values of $\varepsilon^{-1}$ and $d$.
 For some problems with unbounded $d$---as in finance---there may be no need for arbitrarily small error tolerances, so $\Omega = (0,\varepsilon_{\min}^{-1}] \times \mathbb{N}$ may be appropriate.
 For other problems with a moderate upper bound on $d$, $\Omega = (0,\infty) \times \{1, \ldots, d_{\max}\}$ may be appropriate.
-}
 
@@
 In Section \ref{sec:restricted}, we consider tractability on a restricted domain, $\Omega$.
-\peter{There are two appendices to the paper.
+There are two appendices to the paper.
 Appendix 1 contains an example that shows how we can make use of one of the findings in this paper in a concrete example.
-Appendix 2 contains the technical proof of Proposition \ref{prop:equiv_conditions}}.
+Appendix 2 contains the technical proof of Proposition \ref{prop:equiv_conditions}.
 
@@
 \end{equation}
-\peter{We remark that the latter assumption is quite natural, and is, for example fullfilled for all tractability types in Table~\ref{tab:commonT}.}
+We remark that the latter assumption is quite natural, and is, for example fulfilled for all tractability types in Table~\ref{tab:commonT}.
 
@@
 \end{align*}
-\peter{where the infinite sum is guaranteed to exist by the condition \eqref{eq:strong_tractiff3}.}
+where the infinite sum is guaranteed to exist by the condition \eqref{eq:strong_tractiff3}.
 Thus, we can conclude from the previous line that
@@
    \implies   \frac{1}{T(\lambda_{n+1, d}^{-1},\thed,\vp)} \le
-   \frac{1}{n-N+1} \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},\thed,\vp) } \le \frac{1}{T(\varepsilon^{-1},\thed,\vp)} \\ \forall \thed, N \in \naturals\ \peter{\mbox{and}\ n\ge N}.
+   \frac{1}{n-N+1} \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},\thed,\vp) } \le \frac{1}{T(\varepsilon^{-1},\thed,\vp)} \\ \forall \thed, N \in \naturals\ \mbox{and}\ n\ge N.
 \end{multline}
@@
 The following proposition states that the conditions \eqref{eq:exp_spt} and \eqref{eq:KW_exp_spt}, as well as the conditions \eqref{eq:exp_pt} and \eqref{eq:KW_exp_pt}, are indeed equivalent. 
-The proof of this result is deferred to \peter{Appendix 2} where we will prove this statement for the latter two conditions, i.e., for the conditions on exponential polynomial tractability.
+The proof of this result is deferred to Appendix 2 where we will prove this statement for the latter two conditions, i.e., for the conditions on exponential polynomial tractability.
 The case of exponential strong polynomial tractability is not explicitly included, as it is actually simpler and can be treated analogously.
-\peter{We give a short example of how we can apply the condition \eqref{eq:exp_spt} to a concrete problem in Appendix 1.}
+We give a short example of how we can apply the condition \eqref{eq:exp_spt} to a concrete problem in Appendix 1.
 
@@
 
-\fred{Help!  I do not understand how we give and example of a summary of examples above.}
-In the following example, we provide a brief summary of the above examples of tractability.
+%\review{Help!  I do not understand how we give and example of a summary of examples above.}
+Next, we provide a generalization of the above examples of tractability.
 We would like to emphasize that this example was previously known (see, e.g., \cite{GW06}) where in this case the roles of $\varepsilon^{-1}$ and $d$ are separated.
@@
    \implies   \frac{1}{T(\lambda_{n+1, d}^{-1},\thed,\vp)} \le
-   \frac{1}{n-N+1} \sum_{i=N}^{\theUB(d)} \frac{1}{T(\lambda_{i, d}^{-1},\thed,\vp) } \le \frac{1}{T(\varepsilon^{-1},\thed,\vp)} \\ \forall \thed \in \naturals,\  N \in \hI_d, \ \peter{\mbox{and}\ n\ge N}
+   \frac{1}{n-N+1} \sum_{i=N}^{\theUB(d)} \frac{1}{T(\lambda_{i, d}^{-1},\thed,\vp) } \le \frac{1}{T(\varepsilon^{-1},\thed,\vp)} \\ \forall \thed \in \naturals,\  N \in \hI_d, \ \mbox{and}\ n\ge N
 \end{multline}
@@
 \]
-This implies via our technical assumption \eqref{eq:ptauassume} that, \peter{for $\tau>1$,}
+This implies via our technical assumption \eqref{eq:ptauassume} that, for $\tau>1$,
 \begin{gather}
@@
        \comp(\varepsilon,d)
-       & \le T(\varepsilon^{-1},d, \vp) \Biggl [ \frac{\min\left\{\lceil L_{\vp}\, T(0,d,\vp)\rceil,\theUB(d)\right\}}{T(\varepsilon^{-1},d, \vp)}  + \underbrace{\sum_{i = \min\left\{\lceil L_{\vp}\, T(0,d,\vp)\rceil,\theUB(d)\right\}}^{\theUB(d)} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}}_{\le S_{\vp} + 1/ T(\lambda_{\theUB(d), d}^{-1},d,\vp) \text{ by \kachi{\eqref{eq:rest_tractiff}}} }
+       & \le T(\varepsilon^{-1},d, \vp) \Biggl [ \frac{\min\left\{\lceil L_{\vp}\, T(0,d,\vp)\rceil,\theUB(d)\right\}}{T(\varepsilon^{-1},d, \vp)}  + \underbrace{\sum_{i = \min\left\{\lceil L_{\vp}\, T(0,d,\vp)\rceil,\theUB(d)\right\}}^{\theUB(d)} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}}_{\le S_{\vp} + 1/ T(\lambda_{\theUB(d), d}^{-1},d,\vp) \text{ by \eqref{eq:rest_tractiff}}}
         \Biggr] \\
@@
 The authors gratefully acknowledge the fruitful discussions with Henryk Wo\'{z}niakowski and Erich Novak.
+Moreover, we thank two anonymous referees for their suggestions.
 Fred Hickernell acknowledges support by the United States National Science Foundation under Award No.\ 2316011.
@@
 
-\bibliography{FJHOwn23,FJH23,Further_references}
-\bibliographystyle{elsarticle-num}
-
-\section*{\peter{Appendix 1: A concrete example}}
-
-\peter{
+\section*{Appendix 1: A concrete example}
+
 We define the weighted Korobov space $\ch_{\kor,d,\bsa,\bsb}$ below. 
@@
 Let $\bsa=\{a_j\}_{j \ge 1}$ and
-$\bsb=\{b_j\}_{j \ge 1}$ be two sequences of real positive weights
-such that
-\begin{equation}\label{eq:cond_a_b}
-b_\ast:=\inf_j b_j> 0\ \ \ \ \ \mbox{and}\ \ \ \ \
-a_\ast:=\inf_j a_j>0.
-\end{equation}
-We assume, without loss of generality, that the $a_j$ are ordered in a non-decreasing way, i.e., $a_\ast=a_1$.
+$\bsb=\{b_j\}_{j \ge 1}$ be two non-decreasing sequences of real positive weights.
+%such that 
+%\fred{why don't we say that these are non-decreasing sequences of weight, in which case we do not need to define $a_\ast$ and $b_\bst$?
+In fact, do you really need  $a_\ast$ and $b_\bst$ at all in the discussion?}
+%\begin{equation}\label{eq:cond_a_b}
+% a_\ast:=\inf_j a_j>0\ \ \ \ \ \mbox{and}\ \ \ \ \
+% b_\ast:=\inf_j b_j> 0.
+% \end{equation}
+%We assume, without loss of generality, that the $a_j$ are ordered in a non-decreasing way, i.e., $a_\ast=a_1$.
 Fix $\omega\in(0,1)$, and write 
@@
 
-We define $\ch_{\kor,d,\bsa,\bsb}$ as the space of all one-periodic functions $f$ with absolutely convergent Fourier series, 
+We define $\ch_{\kor,d,\bsa,\bsb}$ as the space of all one-periodic functions $f$ with absolutely convergent Fourier series given by $f(\bsx) = \sum_{\bsh \in \ZZ^d} \widehat{f}(\bsh) \exp(2 \pi \sqrt{-1}\bsh'\bsx)$,
 and with finite norm 
@@
 \]
-Let us consider $L_2$-approximation, i.e., $\SOL_d:\ch_{\kor,d,\bsa,\bsb}\to L_2([0,1]^d)$, $\SOL_d(f)=f$, and let us assume
-$\Lambda^{\rm all}$ as the information class. One can show that the singular values  for this choice of $\SOL_d$ are given by
+%where $\widehat{f}$ and $\widehat{g}$ denote the Fourier coefficients of $f$ and $g$, respectively.
+Let us consider $L_2$-approximation, i.e., $\SOL_d:\ch_{\kor,d,\bsa,\bsb}\to L_2([0,1]^d)$, $\SOL_d(f)=f$, and let us allow arbitrary continuous linear functionals as information.
+One can show that the singular values  for this choice of $\SOL_d$ are given by
 \begin{equation}\label{eq:eigenvalues}
@@
 exponential strong tractability, we would use condition \eqref{eq:KW_exp_spt}, which previously existed in the literature.
-A slight drawback of this condition, however, is that we need to know everything about the order of the singular values, since we need to study summability of $\lambda_{i,d}^{i^{-\tau}}$ in \eqref{eq:KW_exp_spt}.
+A slight drawback of this condition, however, is that we need to know everything about the \emph{order} of the singular values, since we need to study summability of $\lambda_{i,d}^{i^{-\tau}}$ in \eqref{eq:KW_exp_spt}.
 This is technically rather involved, and was implicitly done in \cite{DKPW14} (we remark that the concise form
@@
 \[
- \sum_{i=1}^\infty \frac{1}{T\left(\lambda_{i,d}^{-1},1,(p,0)\right)}\kachi{,}
+ \sum_{i=1}^\infty \frac{1}{T\left(\lambda_{i,d}^{-1},1,(p,0)\right)},
 \]
 for a real $p>0$. Inserting the singular values as in \eqref{eq:eigenvalues}, yields
-\[
+\begin{eqnarray*}
   \sum_{i=1}^\infty \frac{1}{T\left(\lambda_{i,d}^{-1},1,(p,0)\right)}
-  = \sum_{\bsh\in\ZZ^d} \frac{1}{\left(1+ \log \left(\omega^{-\frac{1}{2}\sum_{j=1}^d a_j \abs{h_j}^{b_j}}\right)\right)^p}\, .
-\]
+  &=&
+\sum_{\bsh\in\ZZ^d}
+\frac{1}{\left[\max\left\{1,\log\left(1+\omega^{-\frac{1}{2}\sum_{j=1}^d a_j \abs{h_j}^{b_j}}\right)
+\right\}\right]^p}\\
+&\le&1 +\sum_{\bsh\in\ZZ^d\setminus \{\boldsymbol{0}\}} \frac{1}{\left(\log \left(\omega^{-\frac{1}{2}\sum_{j=1}^d a_j \abs{h_j}^{b_j}}\right)\right)^p} \, .
+\end{eqnarray*}
 It is then not hard to show that the two conditions 
 \[
- \sum_{j=1}^\infty \frac{1}{b_j} <\infty \quad \mbox{and}\quad \alpha^*:=\liminf_{j\to\infty}\frac{\log a_j}{j}>0
+ \liminf_{j\to\infty}\frac{\log a_j}{j}>0 \quad \mbox{and}\quad \sum_{j=1}^\infty \frac{1}{b_j} <\infty 
 \]
@@
 
-}
-
-\section*{\peter{Appendix 2: Proof of Proposition~\ref{prop:equiv_conditions}}}
+\section*{Appendix 2: Proof of Proposition~\ref{prop:equiv_conditions}}
 
@@
 
+\bibliography{FJHOwn23,FJH23,Further_references}
+%\bibliographystyle{elsarticle-num}
+\bibliographystyle{plain}
+%\bibliographystyle{elsarticle-harv}
+%\bibliographystyle{elsarticle-num-names}
+
 \end{document}
-z

### 2024-04-21 Older_versions/GeneralizedTractability20240201_rev1.tex
Updates from Overleaf

--- 2024-03-12 GeneralizedTractability20240201_rev1.tex
@@
 \end{equation}
-\peter{We remark that the latter assumption is quite natural, and is, for example fullfilled for all tractability types in Table~\ref{tab:commonT}.}
+\peter{We remark that the latter assumption is quite natural, and is, for example fulfilled for all tractability types in Table~\ref{tab:commonT}.}
 
@@
 
-\fred{Help!  I do not understand how we give and example of a summary of examples above.}
-In the following example, we provide a brief summary of the above examples of tractability.
+%\fred{Help!  I do not understand how we give and example of a summary of examples above.}
+\kachi{Next}, we provide a \kachi{generalization} of the above examples of tractability.
 We would like to emphasize that this example was previously known (see, e.g., \cite{GW06}) where in this case the roles of $\varepsilon^{-1}$ and $d$ are separated.
@@
 Let $\bsa=\{a_j\}_{j \ge 1}$ and
-$\bsb=\{b_j\}_{j \ge 1}$ be two sequences of real positive weights
-such that
-\begin{equation}\label{eq:cond_a_b}
-b_\ast:=\inf_j b_j> 0\ \ \ \ \ \mbox{and}\ \ \ \ \
-a_\ast:=\inf_j a_j>0.
-\end{equation}
-We assume, without loss of generality, that the $a_j$ are ordered in a non-decreasing way, i.e., $a_\ast=a_1$.
+$\bsb=\{b_j\}_{j \ge 1}$ be two \fred{non-decreasing} sequences of real positive weights\fred{.}
+%such that 
+%\fred{why don't we say that these are non-decreasing sequences of weight, in which case we do not need to define $a_\ast$ and $b_\bst$?
+In fact, do you really need  $a_\ast$ and $b_\bst$ at all in the discussion?}
+%\begin{equation}\label{eq:cond_a_b}
+% a_\ast:=\inf_j a_j>0\ \ \ \ \ \mbox{and}\ \ \ \ \
+% b_\ast:=\inf_j b_j> 0.
+% \end{equation}
+%We assume, without loss of generality, that the $a_j$ are ordered in a non-decreasing way, i.e., $a_\ast=a_1$.
 Fix $\omega\in(0,1)$, and write 
@@
 
-We define $\ch_{\kor,d,\bsa,\bsb}$ as the space of all one-periodic functions $f$ with absolutely convergent Fourier series, 
+We define $\ch_{\kor,d,\bsa,\bsb}$ as the space of all one-periodic functions $f$ with absolutely convergent Fourier series \fred{given by $f(\bsx) = \sum_{\bsh \in \ZZ^d} \widehat{f}(\bsh) \exp(2 \pi \sqrt{-1}\bsh'\bsx)$},
 and with finite norm 
@@
 \]
+%where $\widehat{f}$ and $\widehat{g}$ denote the Fourier coefficients of $f$ and $g$, respectively.
 Let us consider $L_2$-approximation, i.e., $\SOL_d:\ch_{\kor,d,\bsa,\bsb}\to L_2([0,1]^d)$, $\SOL_d(f)=f$, and let us assume
@@
 for a real $p>0$. Inserting the singular values as in \eqref{eq:eigenvalues}, yields
-\[
+\begin{eqnarray*}
   \sum_{i=1}^\infty \frac{1}{T\left(\lambda_{i,d}^{-1},1,(p,0)\right)}
-  = \sum_{\bsh\in\ZZ^d} \frac{1}{\left(1+ \log \left(\omega^{-\frac{1}{2}\sum_{j=1}^d a_j \abs{h_j}^{b_j}}\right)\right)^p}\, .
-\]
+  &=&
+\sum_{\bsh\in\ZZ^d}
+\frac{1}{\left[\max\left\{1,\log\left(1+\omega^{-\frac{1}{2}\sum_{j=1}^d a_j \abs{h_j}^{b_j}}\right)
+\right\}\right]^p}\\
+&\le&1 +\sum_{\bsh\in\ZZ^d\setminus \{\boldsymbol{0}\}} \frac{1}{\left(\log \left(\omega^{-\frac{1}{2}\sum_{j=1}^d a_j \abs{h_j}^{b_j}}\right)\right)^p} \, .
+\end{eqnarray*}
 It is then not hard to show that the two conditions 
 \[
- \sum_{j=1}^\infty \frac{1}{b_j} <\infty \quad \mbox{and}\quad \alpha^*:=\liminf_{j\to\infty}\frac{\log a_j}{j}>0
+ \liminf_{j\to\infty}\frac{\log a_j}{j}>0 \quad \mbox{and}\quad \sum_{j=1}^\infty \frac{1}{b_j} <\infty 
 \]

### 2024-04-21 Older_versions/GeneralizedTractability_colored.tex
Updates from Overleaf

--- 2024-04-21 Older_versions/GeneralizedTractability20240201_rev1.tex
@@
 
-\fred{The authors have identified common themes in the proofs of necessary and sufficient conditions for tractability that appear in the literature.
+\review{The authors have identified common themes in the proofs of necessary and sufficient conditions for tractability that appear in the literature.
 By abstracting these themes, this article aims to unify and generalize many existing tractability results for approximation problems where all possible linear functional data are available.
@@
 \end{equation*}
-\fred{Here, $\naturals$ denotes the set of positive integers.}  This means that \peter{the singular values of the operator $\SOL_d$ are the non-negative $\lambda_{i,d}$}.
+\review{Here, $\naturals$ denotes the set of positive integers.}  This means that \review{the singular values of the operator $\SOL_d$ are the non-negative $\lambda_{i,d}$}.
 We remark that in the literature on Information-Based Complexity the singular values of $\SOL_d$ are often denoted by $\sqrt{\lambda_{i,d}}$ instead of $\lambda_{i,d}$.
@@
     \norm[\cg_d]{\SOL_d(f) - \APP_d(f,\varepsilon)} \le \varepsilon \qquad \forall f \in \cb_d, \ \varepsilon \in (0,\infty)\footnote{We note that the radius of the $\cb_d$ could be taken to be an arbitrary positive value, $R$, in which case the problem becomes equivalent to the original one with the tolerance $\varepsilon$ replaced by $\varepsilon/R$ since the problem and the optimal approximate solution are both linear (see below).
-\fred{We allow the error tolerance, $\varepsilon$, to be arbitrarily large because if $\SOL_d$ has large singular values, a large error tolerance may be a reasonable expectation.}}.
+\review{We allow the error tolerance, $\varepsilon$, to be arbitrarily large because if $\SOL_d$ has large singular values, a large error tolerance may be a reasonable expectation.}}.
 \end{equation}
@@
 \]
-where $\comp(\varepsilon,d)$ is the number of linear functionals required by the best admissible algorithm to satisfy the error criterion \eqref{eq:errcrit}\fred{, and  $\naturals_0$ denotes the set of non-negative integers}.
+where $\comp(\varepsilon,d)$ is the number of linear functionals required by the best admissible algorithm to satisfy the error criterion \eqref{eq:errcrit}\review{, and  $\naturals_0$ denotes the set of non-negative integers}.
 By definition, the information complexity is non-decreasing  as $\varepsilon$ tends to zero.
@@
 
-\peter{Strictly speaking, we are considering the \textit{absolute} error criterion in this paper.
+\review{Strictly speaking, we are considering the \textit{absolute} error criterion in this paper.
 Alternatively, one could also consider the \textit{normalized} error criterion, where the error in \eqref{eq:errcrit} is divided by the so-called \textit{initial error}, which is the error without sampling the function, or, equivalently, the operator norm of $\SOL_d$ (see \cite{NovWoz08a} for details).
@@
 
-\peter{We want to bound the information complexity in terms of a simple function, $T$, of $\varepsilon^{-1}$, \kachi{$d$, and some parameter $\vp$}, and then identify conditions on the singular values that are equivalent to the fact that this bound holds, and are easier to verify than showing the bound directly.
+\review{We want to bound the information complexity in terms of a simple function, $T$, of $\varepsilon^{-1}$, \review{$d$, and some parameter $\vp$}, and then identify conditions on the singular values that are equivalent to the fact that this bound holds, and are easier to verify than showing the bound directly.
 By ``simple'' we mean that $T$ takes a form such that the conditions in the theorems of this paper can be checked effectively; however, we remark that this is also related to the singular values $\lambda_{i,d}$ of the solution operator.
-Depending on those, a function $T$ may be useful for one particular problem setting but not for another.} \kachi{In Table \ref{tab:sampleT}, we present various common notions of tractability studied in the literature, characterized by $T$.}
+Depending on those, a function $T$ may be useful for one particular problem setting but not for another.} \review{In Table \ref{tab:sampleT}, we present various common notions of tractability studied in the literature, characterized by $T$.}
 \begin{table}[hbt!]
-    \caption{\kachi{Common notions of tractability}}
+    \caption{\review{Common notions of tractability}}
 {\small
@@
 \end{equation}
-The conditions we require $T$ to satisfy are described in  Section \ref{sec:not}, however, the basic idea is that we define our approximation problem to be tractable if $\comp(\varepsilon, d) \le  C_{\vp}\, T(\varepsilon^{-1},d,\vp)$ for some constant\footnote{\peter{By ``constant'' we mean that the term is independent of the \emph{variables} $\varepsilon$ and $d$, but may depend on the \emph{parameter} $\vp$.}}, $C_{\vp}$, depending only on the parameter $\vp$.
-\kachi{For instance, when considering (algebraic) polynomial tractability, the parameter $\vp$ represents the exponents $(p,q)$ of $\varepsilon$ and $d$, as illustrated in Table 1}.
+The conditions we require $T$ to satisfy are described in  Section \ref{sec:not}, however, the basic idea is that we define our approximation problem to be tractable if $\comp(\varepsilon, d) \le  C_{\vp}\, T(\varepsilon^{-1},d,\vp)$ for some constant\footnote{\review{By ``constant'' we mean that the term is independent of the \emph{variables} $\varepsilon$ and $d$, but may depend on the \emph{parameter} $\vp$.}}, $C_{\vp}$, depending only on the parameter $\vp$.
+\review{For instance, when considering (algebraic) polynomial tractability, the parameter $\vp$ represents the exponents $(p,q)$ of $\varepsilon$ and $d$, as illustrated in Table 1}.
 In practice, we expect $T(\varepsilon^{-1},d,\vp)$ to increase sub-exponentially with increasing $\varepsilon^{-1}$ and/or $d$, however, most of our theorems do not require such an assumption.
@@
 The parameter $\vp$ is an $s$-dimensional vector with $s \geq 1$.
-\fred{We write $\vzero$ to denote a vector with all components equal to zero, and $\vinfty$ to denote a vector with all components equal to $\infty$.
+\review{We write $\vzero$ to denote a vector with all components equal to zero, and $\vinfty$ to denote a vector with all components equal to $\infty$.
 Furthermore, for two vectors $\vp=(p_1,\ldots,p_s)$ and $ \vp'=(p_1',\ldots,p_s')$ in $[0,\infty)^s$, 
@@
 %The differences in these theorems are in the choices of $\thed$ and $\Omega$. 
-\peter{where $T(0,\thed,\vp)$ is defined as in \eqref{eq:T0} below.}  \fred{These theorems say essentially that \emph{(strong) tractability is equivalent to summability conditions on the singular values.} A more stringent form of tractability resulting from a smaller $T$ is equivalent to a more stringent summability condition since the terms being summed become larger.}
+\review{where $T(0,\thed,\vp)$ is defined as in \eqref{eq:T0} below.}  \review{These theorems say essentially that \emph{(strong) tractability is equivalent to summability conditions on the singular values.} A more stringent form of tractability resulting from a smaller $T$ is equivalent to a more stringent summability condition since the terms being summed become larger.}
 
 Although some of \Cref{thm_main_strong_tract2,thm_main_tract2,thm_main_rest_strong_tract,thm_main_rest_tract} are special cases of others, we prove each separately to allow the reader to become familiar with the arguments used as additional layers of complexity are added.
-\peter{(This may be, e.g., additional
+\review{(This may be, e.g., additional
 dependence on $d$ when going from strong tractability to tractability in Subsection~\ref{sec:tractability}, or a restriction of the domain of $\varepsilon$ for which we define tractability in Section 
@@
 
-\fred{Although in many cases $\Omega$ is chosen to be all of $(0,\infty) \times \mathbb{N}$, there are situations where it makes sense to choose $\Omega$ as a proper subset of all possible values of $\varepsilon^{-1}$ and $d$.
+\review{Although in many cases $\Omega$ is chosen to be all of $(0,\infty) \times \mathbb{N}$, there are situations where it makes sense to choose $\Omega$ as a proper subset of all possible values of $\varepsilon^{-1}$ and $d$.
 For some problems with unbounded $d$---as in finance---there may be no need for arbitrarily small error tolerances, so $\Omega = (0,\varepsilon_{\min}^{-1}] \times \mathbb{N}$ may be appropriate.
@@
 In Section \ref{sec:restricted}, we consider tractability on a restricted domain, $\Omega$.
-\peter{There are two appendices to the paper.
+\review{There are two appendices to the paper.
 Appendix 1 contains an example that shows how we can make use of one of the findings in this paper in a concrete example.
@@
 \end{equation}
-\peter{We remark that the latter assumption is quite natural, and is, for example fulfilled for all tractability types in Table~\ref{tab:commonT}.}
+\review{We remark that the latter assumption is quite natural, and is, for example fulfilled for all tractability types in Table~\ref{tab:commonT}.}
 
@@
 \end{align*}
-\peter{where the infinite sum is guaranteed to exist by the condition \eqref{eq:strong_tractiff3}.}
+\review{where the infinite sum is guaranteed to exist by the condition \eqref{eq:strong_tractiff3}.}
 Thus, we can conclude from the previous line that
@@
    \implies   \frac{1}{T(\lambda_{n+1, d}^{-1},\thed,\vp)} \le
-   \frac{1}{n-N+1} \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},\thed,\vp) } \le \frac{1}{T(\varepsilon^{-1},\thed,\vp)} \\ \forall \thed, N \in \naturals\ \peter{\mbox{and}\ n\ge N}.
+   \frac{1}{n-N+1} \sum_{i=N}^\infty \frac{1}{T(\lambda_{i, d}^{-1},\thed,\vp) } \le \frac{1}{T(\varepsilon^{-1},\thed,\vp)} \\ \forall \thed, N \in \naturals\ \review{\mbox{and}\ n\ge N}.
 \end{multline}
@@
 The following proposition states that the conditions \eqref{eq:exp_spt} and \eqref{eq:KW_exp_spt}, as well as the conditions \eqref{eq:exp_pt} and \eqref{eq:KW_exp_pt}, are indeed equivalent. 
-The proof of this result is deferred to \peter{Appendix 2} where we will prove this statement for the latter two conditions, i.e., for the conditions on exponential polynomial tractability.
+The proof of this result is deferred to \review{Appendix 2} where we will prove this statement for the latter two conditions, i.e., for the conditions on exponential polynomial tractability.
 The case of exponential strong polynomial tractability is not explicitly included, as it is actually simpler and can be treated analogously.
-\peter{We give a short example of how we can apply the condition \eqref{eq:exp_spt} to a concrete problem in Appendix 1.}
+\review{We give a short example of how we can apply the condition \eqref{eq:exp_spt} to a concrete problem in Appendix 1.}
 
@@
 
-%\fred{Help!  I do not understand how we give and example of a summary of examples above.}
-\kachi{Next}, we provide a \kachi{generalization} of the above examples of tractability.
+%\review{Help!  I do not understand how we give and example of a summary of examples above.}
+\review{Next}, we provide a \review{generalization} of the above examples of tractability.
 We would like to emphasize that this example was previously known (see, e.g., \cite{GW06}) where in this case the roles of $\varepsilon^{-1}$ and $d$ are separated.
@@
    \implies   \frac{1}{T(\lambda_{n+1, d}^{-1},\thed,\vp)} \le
-   \frac{1}{n-N+1} \sum_{i=N}^{\theUB(d)} \frac{1}{T(\lambda_{i, d}^{-1},\thed,\vp) } \le \frac{1}{T(\varepsilon^{-1},\thed,\vp)} \\ \forall \thed \in \naturals,\  N \in \hI_d, \ \peter{\mbox{and}\ n\ge N}
+   \frac{1}{n-N+1} \sum_{i=N}^{\theUB(d)} \frac{1}{T(\lambda_{i, d}^{-1},\thed,\vp) } \le \frac{1}{T(\varepsilon^{-1},\thed,\vp)} \\ \forall \thed \in \naturals,\  N \in \hI_d, \ \review{\mbox{and}\ n\ge N}
 \end{multline}
@@
 \]
-This implies via our technical assumption \eqref{eq:ptauassume} that, \peter{for $\tau>1$,}
+This implies via our technical assumption \eqref{eq:ptauassume} that, \review{for $\tau>1$,}
 \begin{gather}
@@
        \comp(\varepsilon,d)
-       & \le T(\varepsilon^{-1},d, \vp) \Biggl [ \frac{\min\left\{\lceil L_{\vp}\, T(0,d,\vp)\rceil,\theUB(d)\right\}}{T(\varepsilon^{-1},d, \vp)}  + \underbrace{\sum_{i = \min\left\{\lceil L_{\vp}\, T(0,d,\vp)\rceil,\theUB(d)\right\}}^{\theUB(d)} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}}_{\le S_{\vp} + 1/ T(\lambda_{\theUB(d), d}^{-1},d,\vp) \text{ by \kachi{\eqref{eq:rest_tractiff}}} }
+       & \le T(\varepsilon^{-1},d, \vp) \Biggl [ \frac{\min\left\{\lceil L_{\vp}\, T(0,d,\vp)\rceil,\theUB(d)\right\}}{T(\varepsilon^{-1},d, \vp)}  + \underbrace{\sum_{i = \min\left\{\lceil L_{\vp}\, T(0,d,\vp)\rceil,\theUB(d)\right\}}^{\theUB(d)} \frac{1}{T(\lambda_{i, d}^{-1},d,\vp)}}_{\le S_{\vp} + 1/ T(\lambda_{\theUB(d), d}^{-1},d,\vp) \text{ by \review{\eqref{eq:rest_tractiff}}} }
         \Biggr] \\
@@
 
-\section*{\peter{Appendix 1: A concrete example}}
-
-\peter{
+\section*{\review{Appendix 1: A concrete example}}
+
+\review{
 We define the weighted Korobov space $\ch_{\kor,d,\bsa,\bsb}$ below. 
@@
 Let $\bsa=\{a_j\}_{j \ge 1}$ and
-$\bsb=\{b_j\}_{j \ge 1}$ be two \fred{non-decreasing} sequences of real positive weights\fred{.}
+$\bsb=\{b_j\}_{j \ge 1}$ be two \review{non-decreasing} sequences of real positive weights\review{.}
 %such that 
@@
 
-We define $\ch_{\kor,d,\bsa,\bsb}$ as the space of all one-periodic functions $f$ with absolutely convergent Fourier series \fred{given by $f(\bsx) = \sum_{\bsh \in \ZZ^d} \widehat{f}(\bsh) \exp(2 \pi \sqrt{-1}\bsh'\bsx)$},
+We define $\ch_{\kor,d,\bsa,\bsb}$ as the space of all one-periodic functions $f$ with absolutely convergent Fourier series \review{given by $f(\bsx) = \sum_{\bsh \in \ZZ^d} \widehat{f}(\bsh) \exp(2 \pi \sqrt{-1}\bsh'\bsx)$},
 and with finite norm 
@@
 \[
- \sum_{i=1}^\infty \frac{1}{T\left(\lambda_{i,d}^{-1},1,(p,0)\right)}\kachi{,}
+ \sum_{i=1}^\infty \frac{1}{T\left(\lambda_{i,d}^{-1},1,(p,0)\right)}\review{,}
 \]
@@
 
-\section*{\peter{Appendix 2: Proof of Proposition~\ref{prop:equiv_conditions}}}
+\section*{\review{Appendix 2: Proof of Proposition~\ref{prop:equiv_conditions}}}
 

### 2024-04-21 Older_versions/Generalized_Tractability_Submission_2.tex
Updates from Overleaf

--- 2024-04-21 GeneralizedTractability_rev_2.tex
@@
 \input{FJHDef.tex}
-% Modify the elsarticle-num-names bibliography style to sort references alphabetically
-\makeatletter
-\renewcommand\@biblabel[1]{#1.}
-\makeatother
 
@@
 
+\bibliography{FJHOwn23,FJH23,Further_references}
+\bibliographystyle{elsarticle-num}
+
 \section*{Appendix 1: A concrete example}
@@
 %where $\widehat{f}$ and $\widehat{g}$ denote the Fourier coefficients of $f$ and $g$, respectively.
-Let us consider $L_2$-approximation, i.e., $\SOL_d:\ch_{\kor,d,\bsa,\bsb}\to L_2([0,1]^d)$, $\SOL_d(f)=f$, and let us allow arbitrary continuous linear functionals as information.
-One can show that the singular values  for this choice of $\SOL_d$ are given by
+Let us consider $L_2$-approximation, i.e., $\SOL_d:\ch_{\kor,d,\bsa,\bsb}\to L_2([0,1]^d)$, $\SOL_d(f)=f$, and let us assume
+$\Lambda^{\rm all}$ as the information class. One can show that the singular values  for this choice of $\SOL_d$ are given by
 \begin{equation}\label{eq:eigenvalues}
@@
 
-\bibliography{FJHOwn23,FJH23,Further_references}
-%\bibliographystyle{elsarticle-num}
-\bibliographystyle{plain}
-%\bibliographystyle{elsarticle-harv}
-%\bibliographystyle{elsarticle-num-names}
-
 \end{document}
+z
